---
output: 
  html_document:
  keep_tex: true
  fig_caption: false
  number_sections: false
  toc: false 
  latex_engine: pdflatex
  template: C:/Users/skybl/OneDrive/Documents/Notes_for_733/svm-latex-ms.tex
fontsize: 12pt
#bibliography: references.bib

title: "Problem Set 4"
author: 
  - name: "Donald Moratz"
abstract: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
graphics: true
endnote: no
header-includes:
  - \usepackage{setspace}\doublespacing
  - \usepackage{fancyhdr}
  - \setlength{\headheight}{14.5pt}
  - \pagestyle{fancy}
  - \fancyhf{}
  - \fancyhead[L]{Problem Set 1}
  - \fancyhead[R]{Moratz | p \thepage}
---

```{r setup, include=FALSE}
# Set up Code Chunk

knitr::opts_chunk$set(echo = TRUE)
options(scipen = 3, digits = 3)

rm(list = ls())
library(pacman)
p_load(foreign, haven, ggplot2, broom, plyr, DataCombine, plm, estimatr, gsynth, reshape2, zoo, stargazer, did, here, etwfe, modelsummary, interflex, sandwich, multcomp, lmtest, kableExtra, texreg, fastDummies, ggdag, AER, MatchIt, cobalt, MCMCpack,coda,stats, dplyr, gt)
library(ggplot2)
library(stringdist)
library(stringr)
library(knitr)
library(lubridate)
library(tidyr)
library(plotly)
library(glmnet)
library(caret)
library(scales)
library(openxlsx)
library(kableExtra)
library(pBrackets)
library(zoo)
library(ggpubr)
library(tinytex)
library(Rmisc)
library(purrr)
library(here)
library(readr)
library(data.table)
library(dplyr)
library(stargazer)
library(pander)
library(estimatr)
library(tseries)
library(plm)
library(lmtest)
library(cowplot)
library(grid)
library(gridExtra)
library(rdrobust)
library(lfe)
library(modelsummary)
library(tidyverse)
library(patchwork)
library(stargazer)
library(fixest)
library(VGAM)

set.seed(3184)

```

## Function Creation

```{r}
# --- Robust Date-Time Cleaning Function ---

#' Robustly converts a character column to a POSIXct datetime object.
#' 
#' It handles two formats: YYYY-MM-DD HH:MM:SS (full time) and YYYY-MM-DD (date only).
#' If the time component is missing, it defaults the time to 12:00:00 (noon).
#'
#' @param date_col A character vector column containing dates.
#' @return A POSIXct date-time vector.
clean_datetime_col <- function(date_col) {
  
  # A typical full date-time string length is 19 characters ("YYYY-MM-DD HH:MM:SS")
  # A date-only string length is 10 characters ("YYYY-MM-DD")
  
  # Use dplyr::if_else for efficient, vectorized conditional cleaning
  result <- date_col %>%
    
    # 1. Check for the length of the string to see if the time component is present
    {
      if_else(
        # Condition: String length suggests a full date-time stamp
        str_length(.) > 10,
        
        # TRUE (Time is present): Use the standard ymd_hms function
        ymd_hms(.),
        
        # FALSE (Time is missing/only date is present):
        # Use ymd() to parse the date, then add 12 hours (noon)
        # Note: period() is used to add time components easily.
        ymd(.) + hours(12)
      )
    }
}
```


```{r}
# Load Data

data_1 <- read.csv("GPTcoded_final_rus_articles.csv")%>%
  dplyr::select(date_publish,source_domain,country,title_translated,first_two_sentences,Russian.Involvement,Sentiment,Topic)

data_2 <- read.csv("secondhalf_GPTcoded_final_rus_articles.csv")%>%
  dplyr::select(date_publish,source_domain,country,title_translated,first_two_sentences,Russian.Involvement,Sentiment,Topic)

data <- as.data.frame(rbind(data_1,data_2))
 
# Clean Date data
data$date_publish_continuous <- clean_datetime_col(data$date_publish)

View(data[which(is.na(data$date_publish_continuous)),])

data$date_publish <- as.Date(data$date_publish)

# Drop NA Dates
data <- data %>%
  filter(!is.na(date_publish))

# Drop NAs
data <- data %>%
  filter(!Sentiment == "nan") %>%
  filter(!is.na(Sentiment))

# Clean Sentiment to be -1,0,1
data$sentiment_clean <- -1
data$sentiment_clean[data$Sentiment == "Positive"] <- 1
data$sentiment_clean[data$Sentiment %in% c("Natural","Neutral","neutral")] <-0

# Clean Topic to be 1 of 5 topics

unique(data$Topic)

data$topic_clean <- "Other"
data$topic_clean[data$Topic %in% c("Military","Miliary")] <- "Military"
data$topic_clean[data$Topic %in% c("Politics","Political","Policy","Politic")] <- "Political"
data$topic_clean[data$Topic %in% c("Economic")] <- "Economic"
data$topic_clean[data$Topic %in% c("Cultural","Culture","Sports","Sport")] <- "Culture"


# Create treatment variable
data$treatment <- 0
data$treatment[data$date_publish>"2022-02-23"] <- 1

# Create a running variable
data <- data %>%
    mutate(running = as.numeric(date_publish - as.Date("2022-02-24")),
           running_continuous = as.numeric(date_publish_continuous - ymd_hms("2022-02-24 00:00:00")))

# Create an indicator for state owned
state_owned <- c("zviazda.by", "sb.by","1lurer.am","agenda.ge","azerbaijan-news.az","azertag.az", "en.armradio.am", "eng.belta.by", "kazpravda.kz", "ktrk.kg", "lajme.rtsh.al", "magyarnemzet.hu", "moldova-suverana.md", "qazaqstan.tv", "rtklive.com", "rts.rs", "top-channel.tv", "rthaber.com", "ukrinform.net", "uza.uz","trthaber.com")

data$state_owned <- ifelse(data$source_domain %in% state_owned, 1, 0)

# Create a column for each of 4 unique groups
data$indicator <- ifelse(data$treatment == 0 & data$state_owned == 0, 1, # if both are 0
                        ifelse(data$treatment == 0 & data$state_owned == 1, 2, # if first is 0 and second is 1
                               ifelse(data$treatment == 1 & data$state_owned == 0, 3, 4)))


```


# Main RDD Analysis

## Hypothesis 1

```{r}
# Omit Ukraine in baseline
data_non_ukraine_ind <- data %>%
  filter(!country %in% c("Ukraine")) %>%
  filter(state_owned == 0)
```


```{r}
# Different Slope model

model1_basic <- felm(sentiment_clean ~ running*treatment | 0 | 0 | source_domain, data = data_non_ukraine_ind)

summary(model1_basic)

rdplot(y = data_non_ukraine_ind$sentiment_clean, x = data_non_ukraine_ind$running)

```

```{r}
# Estimate with RD robust
model1_basic_rdrobust <- rdrobust(data_non_ukraine_ind$sentiment_clean, 
                                  data_non_ukraine_ind$running_continuous)

summary(model1_basic_rdrobust)

rdplot(y = data_non_ukraine_ind$sentiment_clean, x = data_non_ukraine_ind$running_continuous)
```


```{r}
# With Country Fixed Effects
model1_country_fe <- felm(sentiment_clean ~ running*treatment | country | 0 | source_domain, data = data_non_ukraine_ind)

summary(model1_country_fe)
```

```{r}
# With Country/Source Fixed Effects
model1_country_source_fe <- felm(sentiment_clean ~ running*treatment | country + source_domain | 0 | source_domain, data = data_non_ukraine_ind)

summary(model1_country_source_fe)
```


```{r}
# FELM Model with clustered standard errors
model1_full <- felm(sentiment_clean ~ running*treatment | country + source_domain + topic_clean | 0 | source_domain, data = data_non_ukraine_ind)

summary(model1_full)
```

```{r}
sd_sentiment <- sd(data_non_ukraine_ind$sentiment_clean)

mean(data_non_ukraine_ind$sentiment_clean)

mean(data_non_ukraine_ind[which(data_non_ukraine_ind$running < 0),"sentiment_clean"], na.rm = TRUE)

mean(data_non_ukraine_ind[which(data_non_ukraine_ind$running > -1),"sentiment_clean"], na.rm = TRUE)

coef_model1_full <- summary(model1_full)$coef[2]

coef_model1_full/sd_sentiment

```

```{r}
# Visualization

invasion_on_sentiment_graph <- data_non_ukraine_ind %>%
  mutate_at(c("treatment"),as.factor) %>%
  ggplot(aes(x = running, y = sentiment_clean, group = `treatment`, color = `treatment`)) +
  geom_point(data= data_non_ukraine_ind %>% 
              group_by(running) %>% 
              summarize(sentiment_clean = mean(sentiment_clean),
                        num_obs = n()),
             aes(x = running, y = sentiment_clean, size=num_obs), alpha=.2, inherit.aes=F) +
  geom_smooth(method="lm") +
  scale_color_manual(values=c("dodgerblue", "red4"), name = "Post Invasion") +
  scale_size(name = "Observations") +
  geom_vline(xintercept=0, linetype="dashed", alpha=.7) +
  theme_classic() +
  labs(title = "Effect of Invasion on Sentiment",
      subtitle = "All Sources and Topics",
      x = "Days Pre/Post Invasion",
      y = "Sentiment")

invasion_on_sentiment_graph

ggsave(plot = invasion_on_sentiment_graph, "figures/invasion_on_sentiment.png")
```

```{r}
# Visualization

data_non_ukraine_ind %>%
  mutate_at(c("treatment"),as.factor) %>%
  ggplot(aes(x = running, y = sentiment_clean, group = `treatment`, color = `treatment`)) +
  geom_point(data= data_non_ukraine_ind %>% 
              group_by(running) %>% 
              summarize(sentiment_clean = mean(sentiment_clean),
                        num_obs = n()),
             aes(x = running, y = sentiment_clean, size=num_obs), alpha=.2, inherit.aes=F) +
  geom_smooth(method="gam") +
  scale_color_manual(values=c("dodgerblue", "red4"), name = "Post Invasion") +
  scale_size(name = "Observations") +
  geom_vline(xintercept=0, linetype="dashed", alpha=.7) +
  theme_classic() +
  labs(title = "Figure 2 Appendix: Effect of Invasion on Sentiment",
      subtitle = "All Sources and Topics",
      x = "Days Pre/Post Invasion",
      y = "Sentiment")
```


```{r}
# Using Optimal Bandwidth
summary(rdbwselect(y = data_non_ukraine_ind$sentiment_clean, x = data_non_ukraine_ind$running, cluster = data_non_ukraine_ind$source_domain, kernel = "triangular", p = 1, bwselect = "mserd"))

optimal_bandwidth_data <- data_non_ukraine_ind %>%
  filter(running < 32) %>%
  filter(running > -32)

model1_opt <- felm(sentiment_clean ~ running*treatment | country + source_domain + topic_clean | 0 | source_domain, data = optimal_bandwidth_data)

summary(model1_opt)


```


## Hypothesis 1A and Supplementary Analysis

```{r}
# Drop military as a topic
# FELM Model with clustered standard errors
data_non_mil_ind <- data_non_ukraine_ind %>%
  filter(!topic_clean == "Military")
model1b <- felm(sentiment_clean ~ running*treatment | country + source_domain + topic_clean | 0 | source_domain, data = data_non_mil_ind)

summary(model1b)
```

```{r}
# Standard Deviation Analysis
sd_sentiment_non_mil_ind <- sd(data_non_mil_ind$sentiment_clean)

coef_model1b <- summary(model1b)$coef[2]

coef_model1b/sd_sentiment_non_mil_ind

```

```{r}
# Visualization of non-military

invasion_on_sentiment_non_mil_graph <- data_non_mil_ind %>%
  mutate_at(c("treatment"),as.factor) %>%
  ggplot(aes(x = running, y = sentiment_clean, group = `treatment`, color = `treatment`)) +
  geom_point(data= data_non_mil_ind %>% 
              group_by(running) %>% 
              summarize(sentiment_clean = mean(sentiment_clean),
                        num_obs = n()),
             aes(x = running, y = sentiment_clean, size=num_obs), alpha=.2, inherit.aes=F) +
  geom_smooth(method="lm") +
  scale_color_manual(values=c("dodgerblue", "red4"), name = "Post Invasion") +
  scale_size(name = "Observations") +
  geom_vline(xintercept=0, linetype="dashed", alpha=.7) +
  theme_classic() +
  labs(title = "Effect of Invasion on Sentiment",
      subtitle = "Non-Military Topics",
      x = "Days Pre/Post Invasion",
      y = "Sentiment")

invasion_on_sentiment_non_mil_graph

ggsave(plot = invasion_on_sentiment_non_mil_graph, "figures/invasion_on_sentiment_non_mil.png")
```

```{r}
# Only Nato Countries
data_nato_ind <- data_non_ukraine_ind %>%
  filter(country %in% c("Albania","Turkey","Hungary"))

# FELM Model with clustered standard errors
model1c <- felm(sentiment_clean ~ running*treatment | country + source_domain + topic_clean | 0 | source_domain, data = data_nato_ind)

summary(model1c)
```

```{r}
# Visualization of non-military

data_nato_ind %>%
  mutate_at(c("treatment"),as.factor) %>%
  ggplot(aes(x = running, y = sentiment_clean, group = `treatment`, color = `treatment`)) +
  geom_point(data= data_nato_ind %>% 
              group_by(running) %>% 
              summarize(sentiment_clean = mean(sentiment_clean),
                        num_obs = n()),
             aes(x = running, y = sentiment_clean, size=num_obs), alpha=.2, inherit.aes=F) +
  geom_smooth(method="lm") +
  scale_color_manual(values=c("dodgerblue", "red4"), name = "Post Invasion") +
  scale_size(name = "Observations") +
  geom_vline(xintercept=0, linetype="dashed", alpha=.7) +
  theme_classic() +
  labs(title = "Figure 2C: Effect of Invasion on Sentiment",
      subtitle = "NATO Countries",
      x = "Days Pre/Post Invasion",
      y = "Sentiment")
```

```{r}
# Only Non-Nato Countries
data_non_nato_ind <- data_non_ukraine_ind %>%
  filter(!country %in% c("Albania","Turkey","Hungary","Ukraine"))

# FELM Model with clustered standard errors
model1d <- felm(sentiment_clean ~ running*treatment | country + source_domain + topic_clean | 0 | source_domain, data = data_non_nato_ind)

summary(model1d)
```

```{r}
# Visualization of non-military

data_non_nato_ind %>%
  mutate_at(c("treatment"),as.factor) %>%
  ggplot(aes(x = running, y = sentiment_clean, group = `treatment`, color = `treatment`)) +
  geom_point(data= data_non_nato_ind %>% 
              group_by(running) %>% 
              summarize(sentiment_clean = mean(sentiment_clean),
                        num_obs = n()),
             aes(x = running, y = sentiment_clean, size=num_obs), alpha=.2, inherit.aes=F) +
  geom_smooth(method="lm") +
  scale_color_manual(values=c("dodgerblue", "red4"), name = "Post Invasion") +
  scale_size(name = "Observations") +
  geom_vline(xintercept=0, linetype="dashed", alpha=.7) +
  theme_classic() +
  labs(title = "Figure 2D: Effect of Invasion on Sentiment",
      subtitle = "Non-NATO Countries",
      x = "Days Pre/Post Invasion",
      y = "Sentiment")
```


```{r}
# State Only
# FELM Model with clustered standard errors
data_state <- data %>%
  filter(state_owned == 1) %>%
  filter(!country %in% c("Ukraine"))
model1e <- felm(sentiment_clean ~ running*treatment | country + source_domain + topic_clean | 0 | source_domain, data = data_state)

summary(model1e)
```


```{r}
# Visualization

data_state %>%
  mutate_at(c("treatment"),as.factor) %>%
  ggplot(aes(x = running, y = sentiment_clean, group = `treatment`, color = `treatment`)) +
  geom_point(data= data_state %>% 
              group_by(running) %>% 
              summarize(sentiment_clean = mean(sentiment_clean),
                        num_obs = n()),
             aes(x = running, y = sentiment_clean, size=num_obs), alpha=.2, inherit.aes=F) +
  geom_smooth(method="lm") +
  scale_color_manual(values=c("forestgreen", "darkorange"), name = "Post Invasion") +
  scale_size(name = "Observations") +
  geom_vline(xintercept=0, linetype="dashed", alpha=.7) +
  theme_classic() +
  labs(title = "Figure 2E: Effect of Invasion on Sentiment",
      subtitle = "State Owned Media",
      x = "Days Pre/Post Invasion",
      y = "Sentiment")
```

```{r}
# Dropping Belarus
# FELM Model with clustered standard errors
data_non_involved_ind <- data_non_ukraine_ind %>%
  filter(!country %in% c("Belarus"))
model1f <- felm(sentiment_clean ~ running*treatment | country + source_domain + topic_clean | 0 | source_domain, data = data_non_involved_ind)

summary(model1f)
```


```{r}
# Visualization

data_non_involved_ind %>%
  mutate_at(c("treatment"),as.factor) %>%
  ggplot(aes(x = running, y = sentiment_clean, group = `treatment`, color = `treatment`)) +
  geom_point(data= data_non_involved_ind %>% 
              group_by(running) %>% 
              summarize(sentiment_clean = mean(sentiment_clean),
                        num_obs = n()),
             aes(x = running, y = sentiment_clean, size=num_obs), alpha=.2, inherit.aes=F) +
  geom_smooth(method="lm") +
  scale_color_manual(values=c("dodgerblue", "red4"), name = "Post Invasion") +
  scale_size(name = "Observations") +
  geom_vline(xintercept=0, linetype="dashed", alpha=.7) +
  theme_classic() +
  labs(title = "Figure 2F: Effect of Invasion on Sentiment",
      subtitle = "Ukraine and Belarus Removed",
      x = "Days Pre/Post Invasion",
      y = "Sentiment")
```

```{r}
# Ukraine Only
data_ukraine <- data %>%
  filter(country == "Ukraine")

model1g <- felm(sentiment_clean ~ running*treatment | country + source_domain + topic_clean | 0 | source_domain, data = data_ukraine)

summary(model1g)

```


```{r}
# Visualization

data_ukraine %>%
  mutate_at(c("treatment"),as.factor) %>%
  ggplot(aes(x = running, y = sentiment_clean, group = `treatment`, color = `treatment`)) +
  geom_point(data= data_ukraine %>% 
              group_by(running) %>% 
              summarize(sentiment_clean = mean(sentiment_clean),
                        num_obs = n()),
             aes(x = running, y = sentiment_clean, size=num_obs), alpha=.2, inherit.aes=F) +
  geom_smooth(method="lm") +
  scale_color_manual(values=c("dodgerblue", "red4"), name = "Post Invasion") +
  scale_size(name = "Observations") +
  geom_vline(xintercept=0, linetype="dashed", alpha=.7) +
  theme_classic() +
  labs(title = "Figure 2G: Effect of Invasion on Sentiment",
      subtitle = "Ukraine Only",
      x = "Days Pre/Post Invasion",
      y = "Sentiment")
```

```{r}
rows <- tibble::tribble(~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7,
  'State FEs', '-', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', 'X', 'X', 'X', 'X',
  'Topic FEs', '-', '-', '-', 'X', 'X', 'X')
attr(rows, 'position') <- c(3,4,5)

# note
note_text <- "All standard errors are clustered at the source level. Model 2 uses the triangular kernel within the optimal bandwidth. Model 3 omits NATO allies. Model 4 omits military-related articles. Model 5 omits military-related articles and only uses articles that were classified as primarily Russian Related."

# Wrap note into 80-character lines
note_wrapped <- str_wrap(note_text, width = 80)

table_1 <- modelsummary(list(model1_basic, model1_country_fe, model1_country_source_fe, model1_full, model1_opt, model1d),
             output ="gt",
             fmt = fmt_significant(2),
             stars = TRUE,
             coef_map = c("treatment" = "Invasion"),
             gof_omit = "BIC|AIC|RMSE|Std.Errors",
             title = "Difference in Difference Analysis",
             add_rows = rows,
             notes = note_wrapped)

table_1

#gtsave(table_1, "figures/table_1.html")
```

# Diff-in-Discs Analysis

```{r}
# FELM Model with clustered standard errors
data_non_ukraine <- data %>%
  filter(!country %in% c("Ukraine"))

model2a <- felm(sentiment_clean ~ running*treatment*state_owned | country + source_domain + topic_clean | 0 | source_domain, data = data_non_ukraine)

summary(model2a)

```

Using Ordered Logit (the correct way to do this analysis)

```{r}
data_non_ukraine_test <- data_non_ukraine
data_non_ukraine_test$sentiment_clean <- factor(data_non_ukraine_test$sentiment_clean, levels = c(-1,0,1))
model2a_test <- vglm(sentiment_clean ~ running*treatment*state_owned, data = data_non_ukraine_test, family = cumulative(parallel = TRUE, reverse = TRUE))

summary(model2a_test)
```


```{r}
# Visualization

invasion_discs_graph <- data_non_ukraine %>%
  mutate_at(c("indicator"),as.factor) %>%
  mutate(indicator = fct_recode(indicator,
    "Ind. Pre." = "1",
    "State Pre." = "2",
    "Ind. Post" = "3",
    "State Post" = "4"
  )) %>%
  ggplot(aes(x = running, y = sentiment_clean, group = `indicator`, color = `indicator`)) +
  geom_point(data= data_non_ukraine %>% 
              group_by(running,state_owned) %>% 
              summarize(sentiment_clean = mean(sentiment_clean),
                        num_obs = n()),
             aes(x = running, y = sentiment_clean, size=num_obs), alpha=.2, inherit.aes=F) +
  geom_smooth(method="lm") +
  scale_color_manual(values=c("dodgerblue","forestgreen", "red4","darkorange"), name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept=0, linetype="dashed", alpha=.7) +
  theme_classic() +
  labs(title = "Effect of Invasion on Sentiment",
      subtitle = "Difference in Discontinuities",
      x = "Days Pre/Post Invasion",
      y = "Sentiment")


invasion_discs_graph

ggsave(plot = invasion_discs_graph, "figures/invasion_discs_graph.png")
```

```{r}
# Standard Deviation Analysis
sd_sentiment_non_ukraine <- sd(data_non_ukraine$sentiment_clean)

coef_model2a_all <- summary(model2a)$coef[2]

# Effect on all Media
coef_model2a_all/sd_sentiment_non_ukraine

# Effect on just state media
coef_model2a_state <- summary(model2a)$coef[6]

coef_model2a_state/sd_sentiment_non_ukraine


mean(data_non_ukraine[which(data_non_ukraine_ind$running < 0),"sentiment_clean"], na.rm = TRUE)

mean(data_non_ukraine[which(data_non_ukraine_ind$running > -1),"sentiment_clean"], na.rm = TRUE)
```

```{r}
# Visualization

data_non_ukraine %>%
  mutate_at(c("indicator"),as.factor) %>%
  mutate(indicator = fct_recode(indicator,
    "Ind. Pre." = "1",
    "State Pre." = "2",
    "Ind. Post" = "3",
    "State Post" = "4"
  )) %>%
  ggplot(aes(x = running, y = sentiment_clean, group = `indicator`, color = `indicator`)) +
  geom_point(data= data_non_ukraine %>% 
              group_by(running,state_owned) %>% 
              summarize(sentiment_clean = mean(sentiment_clean),
                        num_obs = n()),
             aes(x = running, y = sentiment_clean, size=num_obs), alpha=.2, inherit.aes=F) +
  geom_smooth(method="gam") +
  scale_color_manual(values=c("dodgerblue","forestgreen", "red4","darkorange"), name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept=0, linetype="dashed", alpha=.7) +
  theme_classic() +
  labs(title = "Figure 4 Appendix: Effect of Invasion on Sentiment",
      subtitle = "Difference in Discontinuities",
      x = "Days Pre/Post Invasion",
      y = "Sentiment")
```


```{r}
# FELM Model with clustered standard errors
# optimal bandwidth select

data_non_ukraine <- data_non_ukraine %>%
  mutate_at(c("country","source_domain","topic_clean"), as.factor)

summary(rdbwselect(y = data_non_ukraine$sentiment_clean, x = data_non_ukraine$running, kernel = "triangular", cluster = data_non_ukraine$source_domain, p = 1, bwselect = "mserd"))

optimal_bandwidth_data <- data_non_ukraine %>%
  filter(running < 39) %>%
  filter(running > -39)

model2a_opt <- felm(sentiment_clean ~ running*treatment*state_owned | country + source_domain + topic_clean | 0 | source_domain, data = optimal_bandwidth_data)

summary(model2a_opt)

```

```{r}
# Visualization

optimal_bandwidth_data %>%
  mutate_at(c("indicator"),as.factor) %>%
  mutate(indicator = fct_recode(indicator,
    "Ind. Pre." = "1",
    "State Pre." = "2",
    "Ind. Post" = "3",
    "State Post" = "4"
  )) %>%
  ggplot(aes(x = running, y = sentiment_clean, group = `indicator`, color = `indicator`)) +
  geom_point(data= optimal_bandwidth_data %>% 
              group_by(running,state_owned) %>% 
              summarize(sentiment_clean = mean(sentiment_clean),
                        num_obs = n()),
             aes(x = running, y = sentiment_clean, size=num_obs), alpha=.2, inherit.aes=F) +
  geom_smooth(method="lm") +
  scale_color_manual(values=c("dodgerblue","forestgreen", "red4","darkorange"), name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept=0, linetype="dashed", alpha=.7) +
  theme_classic() +
  labs(title = "Figure 4 Optimal: Effect of Invasion on Sentiment",
      subtitle = "Difference in Discontinuities",
      x = "Days Pre/Post Invasion",
      y = "Sentiment")
```


```{r}
# Non-Military Topics Only
# FELM Model with clustered standard errors
data_non_mil <- data_non_ukraine %>%
  filter(!topic_clean %in% c("Military"))
model2b <- felm(sentiment_clean ~ running*treatment*state_owned | country + source_domain + topic_clean | 0 | source_domain, data = data_non_mil)

summary(model2b)

```

```{r}
# Visualization

invasion_discs_non_mil_graph <- data_non_mil %>%
  mutate_at(c("indicator"),as.factor) %>%
  mutate(indicator = fct_recode(indicator,
    "Ind. Pre." = "1",
    "State Pre." = "2",
    "Ind. Post" = "3",
    "State Post" = "4"
  )) %>%
  ggplot(aes(x = running, y = sentiment_clean, group = `indicator`, color = `indicator`)) +
  geom_point(data= data_non_mil %>% 
              group_by(running,state_owned) %>% 
              summarize(sentiment_clean = mean(sentiment_clean),
                        num_obs = n()),
             aes(x = running, y = sentiment_clean, size=num_obs), alpha=.2, inherit.aes=F) +
  geom_smooth(method="lm") +
  scale_color_manual(values=c("dodgerblue","forestgreen", "red4","darkorange"), name = "Source Ty[e") +
  scale_size(name = "Observations") +
  geom_vline(xintercept=0, linetype="dashed", alpha=.7) +
  theme_classic() +
  labs(title = "Effect of Invasion on Sentiment",
      subtitle = "Non-Military Topics",
      x = "Days Pre/Post Invasion",
      y = "Sentiment")

invasion_discs_non_mil_graph

ggsave(plot = invasion_discs_non_mil_graph, "figures/invasion_discs_non_mil.png")
```

```{r}
# Standard Deviation Analysis
sd_sentiment_non_ukraine_non_mil <- sd(data_non_mil$sentiment_clean)

coef_model2b_all <- summary(model2b)$coef[2]

# Effect on all Media
coef_model2b_all/sd_sentiment_non_ukraine_non_mil

# Effect on just state media
coef_model2b_state <- summary(model2b)$coef[6]

coef_model2b_state/sd_sentiment_non_ukraine

```

```{r}
# Russian Aligned Only
# FELM Model with clustered standard errors
data_non_nato <- data_non_ukraine %>%
  filter(!country %in% c("Albania","Turkey","Hungary"))
model2d <- felm(sentiment_clean ~ running*treatment*state_owned | country + source_domain + topic_clean | 0 | source_domain, data = data_non_nato)

summary(model2d)

```

```{r}
# Visualization

data_non_nato %>%
  mutate_at(c("indicator"),as.factor) %>%
  mutate(indicator = fct_recode(indicator,
    "Ind. Pre." = "1",
    "State Pre." = "2",
    "Ind. Post" = "3",
    "State Post" = "4"
  )) %>%
  ggplot(aes(x = running, y = sentiment_clean, group = `indicator`, color = `indicator`)) +
  geom_point(data= data_non_nato %>% 
              group_by(running,state_owned) %>% 
              summarize(sentiment_clean = mean(sentiment_clean),
                        num_obs = n()),
             aes(x = running, y = sentiment_clean, size=num_obs), alpha=.2, inherit.aes=F) +
  geom_smooth(method="lm") +
  scale_color_manual(values=c("dodgerblue","forestgreen", "red4","darkorange"), name = "Source Ty[e") +
  scale_size(name = "Observations") +
  geom_vline(xintercept=0, linetype="dashed", alpha=.7) +
  theme_classic() +
  labs(title = "Figure 3D: Effect of Invasion on Sentiment",
      subtitle = "Non Nato Countries",
      x = "Days Pre/Post Invasion",
      y = "Sentiment")
```

```{r}
# Omitting Ukraine and Belarus
# FELM Model with clustered standard errors
data_non_involved <- data_non_ukraine %>%
  filter(!country %in% c("Belarus"))
model2g <- felm(sentiment_clean ~ running*treatment*state_owned | country + source_domain + topic_clean | 0 | source_domain, data = data_non_involved)

summary(model2g)

data_non_involved_non_mil <- data_non_involved %>%
  filter(!topic_clean == "Military")

model2g_non_mil <- felm(sentiment_clean ~ running*treatment*state_owned | country + source_domain + topic_clean | 0 | source_domain, data = data_non_involved_non_mil)

summary(model2g_non_mil)


```

```{r}
# Visualization

data_non_involved %>%
  mutate_at(c("indicator"),as.factor) %>%
  mutate(indicator = fct_recode(indicator,
    "Ind. Pre." = "1",
    "State Pre." = "2",
    "Ind. Post" = "3",
    "State Post" = "4"
  )) %>%
  ggplot(aes(x = running, y = sentiment_clean, group = `indicator`, color = `indicator`)) +
  geom_point(data= data_non_involved %>% 
              group_by(running,state_owned) %>% 
              summarize(sentiment_clean = mean(sentiment_clean),
                        num_obs = n()),
             aes(x = running, y = sentiment_clean, size=num_obs), alpha=.2, inherit.aes=F) +
  geom_smooth(method="lm") +
  scale_color_manual(values=c("dodgerblue","forestgreen", "red4","darkorange"), name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept=0, linetype="dashed", alpha=.7) +
  theme_classic() +
  labs(title = "Figure 3G: Effect of Invasion on Sentiment",
      subtitle = "Ukraine and Belarus Removed",
      x = "Days Pre/Post Invasion",
      y = "Sentiment")
```

```{r}
# Ukraine Only
# FELM Model with clustered standard errors
model2h <- felm(sentiment_clean ~ running*treatment*state_owned | country + source_domain + topic_clean | 0 | source_domain, data = data_ukraine)

summary(model2h)

```

```{r}
# Visualization

data_ukraine %>%
  mutate_at(c("indicator"),as.factor) %>%
  mutate(indicator = fct_recode(indicator,
    "Ind. Pre." = "1",
    "State Pre." = "2",
    "Ind. Post" = "3",
    "State Post" = "4"
  )) %>%
  ggplot(aes(x = running, y = sentiment_clean, group = `indicator`, color = `indicator`)) +
  geom_point(data= data_ukraine %>% 
              group_by(running,state_owned) %>% 
              summarize(sentiment_clean = mean(sentiment_clean),
                        num_obs = n()),
             aes(x = running, y = sentiment_clean, size=num_obs), alpha=.2, inherit.aes=F) +
  geom_smooth(method="lm") +
  scale_color_manual(values=c("dodgerblue","forestgreen", "red4","darkorange"), name = "Post Invasion") +
  scale_size(name = "Observations") +
  geom_vline(xintercept=0, linetype="dashed", alpha=.7) +
  theme_classic() +
  labs(title = "Figure 3G: Effect of Invasion on Sentiment",
      subtitle = "Ukraine Only",
      x = "Days Pre/Post Invasion",
      y = "Sentiment")
```

# Diff-in-Diff Analysis

### Diff-in-Diff Regression
```{r}
# Use Optimal Bandwidth Data

model_diff_in_diff <- felm(sentiment_clean ~ treatment*state_owned | country + source_domain + topic_clean | 0 | source_domain, data = optimal_bandwidth_data)

summary(model_diff_in_diff)

```
### Event Study

```{r}
# # Create a factor variable for the running variable
# optimal_data_event <- optimal_bandwidth_data %>%
#     mutate(
#       event_time_factor = factor(running)
#     )
# 
# # Run the regression
# es_model <- feols(sentiment_clean ~ i(state_owned, event_time_factor) | source_domain + topic_clean + country,
#                   data = optimal_data_event, 
#                   vcov = cluster~source_domain)
# 
# summary(es_model)
```


```{r}
# plot_es <- iplot(
#     es_model, 
#     main = "Event Study Plot (Test for Parallel Trends)",
#     xlab = "Periods Relative to Treatment (Days/Months/Years)", 
#     ylab = "Effect on Sentiment (Coefficients $\\gamma_k$)",
#     # Adjust horizontal line at y=0
#     ref.line = 0,
#     # Adjust vertical line at treatment onset (t=0)
#     ref.point = -0.5,
#     col = c("blue", "red"), # Custom colors for pre/post treatment periods
#     lwd = 1.5
# )
# 
# es_tidy <- tidy(es_model) %>%
#   filter(grepl("event_time_factor", term)) %>%
#   mutate(
#     # Extract the event time number
#     event_time = as.numeric(gsub("event_time_factor::", "", term)),
#     # Calculate upper/lower bounds for the 95% CI
#     conf.low = estimate - 1.96 * std.error,
#     conf.high = estimate + 1.96 * std.error
#   ) %>%
#   # Filter out the baseline (-1)
#   filter(event_time != -1)
# 
# custom_plot <- ggplot(es_tidy, aes(x = event_time, y = estimate)) +
#   # Add the confidence intervals
#   geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0, linewidth = 0.8, color = "darkgray") +
#   # Add the coefficients as points, colored by pre/post
#   geom_point(aes(color = event_time < 0), size = 3) +
#   scale_color_manual(values = c("TRUE" = "#1f78b4", "FALSE" = "#e31a1c"), name = "Period", labels = c("Post-Treatment", "Pre-Treatment")) +
#   # Add a horizontal line at 0 (null effect)
#   geom_hline(yintercept = 0, linetype = "dashed", color = "black", alpha = 0.7) +
#   # Add a vertical line marking the start of treatment (between -1 and 0)
#   geom_vline(xintercept = -0.5, linetype = "dotted", color = "black", alpha = 0.7) +
#   labs(
#     title = "Event Study: Sentiment Effect Over Time (Non-Staggered Correction)",
#     subtitle = "Feols syntax fixed. Time FE removed, Group Dummy and Unit FE retained.",
#     x = "Periods Relative to Treatment (t=0 is Treatment Period)",
#     y = "Estimated Treatment Effect (Sentiment $\\gamma_k$)"
#   ) +
#   theme_minimal(base_size = 14) +
#   theme(legend.position = "none")
# 
# print(custom_plot)

```


# Without "Non-Russian"

```{r}
# Without "Non-Russian
data_russian_related <- data %>%
  filter(!Russian.Involvement == "Not") %>%
  filter(!country %in% c("Ukraine")) %>%
  filter(!topic_clean %in% c("Military"))
# FELM Model with clustered standard errors
model3a <- felm(sentiment_clean ~ running*treatment*state_owned | country + source_domain + topic_clean | 0 | source_domain, data = data_russian_related)

summary(model3a)

```

```{r}
# Visualization

data_russian_related %>%
  mutate_at(c("indicator"),as.factor) %>%
  ggplot(aes(x = running, y = sentiment_clean, group = `indicator`, color = `indicator`)) +
  geom_point(data= data_russian_related %>% 
              group_by(running,state_owned) %>% 
              summarize(sentiment_clean = mean(sentiment_clean),
                        num_obs = n()),
             aes(x = running, y = sentiment_clean, size=num_obs), alpha=.2, inherit.aes=F) +
  geom_smooth(method="lm") +
  scale_color_manual(values=c("dodgerblue","forestgreen", "red4","darkorange"), name = "Post Invasion") +
  scale_size(name = "Observations") +
  geom_vline(xintercept=0, linetype="dashed", alpha=.7) +
  theme_classic() +
  ggtitle("Figure 4 Russia Only: Effect of Invasion on Sentiment, Diff-in-Discs") + 
  xlab("Days Pre/Post Invasion") + 
  ylab("Sentiment")
```

```{r}
rows <- tibble::tribble(~row1, ~row2, ~row3, ~row4, ~row5, ~row6,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', 'X', 'X', 'X', 'X', 'X',
  'Topic FEs', 'X', 'X', 'X', 'X', 'X')
attr(rows, 'position') <- c(5,6,7)

# note text
note_text <- "All standard errors are clustered at the source level. Model 2 uses the triangular kernel within the optimal bandwidth. Model 3 omits NATO allies. Model 4 omits military-related articles.  Model 5 omits military-related articles and only uses articles that were classified as primarily Russian Related."

# Wrap note into 80-character lines
note_wrapped <- str_wrap(note_text, width = 80)

table_2 <- modelsummary(list(model2a, model2a_opt, model2d, model2b, model3a),
             output ="gt",
             fmt = fmt_significant(2),
             stars = TRUE,
             coef_map = c("treatment" = "Invasion",
                          "treatment:state_owned" = "State Owned x Treatment"),
             gof_omit = "BIC|AIC|RMSE|Std.Errors",
             title = "Difference in Discontinuity Analysis",
             add_rows = rows,
             notes = note_wrapped
             )

table_2

#gtsave(table_2, "figures/table_2.html")
```

## December 7th Analysis

```{r}
data_dec <- data %>%
  filter(date_publish < "2022-02-19") %>%
  mutate(running = as.numeric(date_publish - as.Date("2021-12-07"))) %>%
  mutate(treatment = ifelse(date_publish < as.Date("2021-12-07"),
                            0,
                            1))
  

# FELM Model with clustered standard errors
model4a <- felm(sentiment_clean ~ running*treatment | country + source_domain + Topic | 0 | source_domain, data = data_dec)

summary(model4a)
```

```{r}
# Visualization

data_dec %>%
  mutate_at(c("treatment"),as.factor) %>%
  ggplot(aes(x = running, y = sentiment_clean, group = `treatment`, color = `treatment`)) +
  geom_point(data= data_dec %>% 
              group_by(running) %>% 
              summarize(sentiment_clean = mean(sentiment_clean),
                        num_obs = n()),
             aes(x = running, y = sentiment_clean, size=num_obs), alpha=.2, inherit.aes=F) +
  geom_smooth(method="lm") +
  scale_color_manual(values=c("dodgerblue", "red4"), name = "Post Invasion") +
  scale_size(name = "Observations") +
  geom_vline(xintercept=0, linetype="dashed", alpha=.7) +
  theme_classic() +
  ggtitle("Figure 3: Effect of Announcement on Sentiment") + 
  xlab("Days Pre/Post Announcement") + 
  ylab("Sentiment")
```

# Explanation of State Variance

## Alignment with Russia. Neutral vs CSTO

```{r}
# Create alignment variables
csto <- c("Armenia", "Azerbaijan", "Belarus", "Kazakhstan")
nato <- c("Albania", "Ukraine", "Turkey", "Hungary")
neutral <- c("Georgia", "Moldova", "Kosovo", "Serbia")

data$csto <- ifelse(data$country %in% csto, 1, 0)
data$nato <- ifelse(data$country %in% nato, 1, 0)
data$neutral <- ifelse(data$country %in% neutral, 1, 0)

data_align <- data %>%
  filter(nato == 0)

data_align <- data_align %>%
  mutate(align_indicator = factor(case_when(
                                     indicator == 1 & csto == 1 ~ "Pre. Ind. CSTO",
                                     indicator == 1 & csto == 0 ~ "Pre. Ind. Neut",
                                     indicator == 2 & csto == 1 ~ "Pre. State CSTO",
                                     indicator == 2 & csto == 0 ~ "Pre. State Neut",
                                     indicator == 3 & csto == 1 ~ "Post Ind. CSTO",
                                     indicator == 3 & csto == 0 ~ "Post Ind. Neut",
                                     indicator == 4 & csto == 1 ~ "Post State CSTO",
                                     indicator == 4 & csto == 0 ~ "Post State Neut"),
         levels = c("Pre. Ind. CSTO", "Pre. Ind. Neut", "Pre. State CSTO", 
                    "Pre. State Neut", "Post Ind. CSTO", "Post Ind. Neut", 
                    "Post State CSTO", "Post State Neut")))
```


```{r}
# Alignment Independent media graph

data_align %>%
  filter(state_owned == 0) %>%
  ggplot(aes(x = running, y = sentiment_clean, group = `align_indicator`, color = `align_indicator`)) +
  geom_point(data= data_align %>%
              filter(state_owned == 0) %>%
              group_by(running, csto) %>% 
              summarize(sentiment_clean = mean(sentiment_clean),
                        num_obs = n()),
             aes(x = running, y = sentiment_clean, size=num_obs), alpha=.2, inherit.aes=F) +
  geom_smooth(method="lm") +
  scale_color_manual(values=c("dodgerblue","forestgreen", "red4","darkorange"), name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept=0, linetype="dashed", alpha=.7) +
  theme_classic() +
  labs(title = "Figure 6: Effect of Invasion on Indpendent Media Sentiment",
      subtitle = "Neutral VS Russia Aligned, Difference in Discontinuities",
      x = "Days Pre/Post Invasion",
      y = "Sentiment")

```


```{r}
# Alignment State Owned media graph

state_align_discs_graph <- data_align %>%
  filter(state_owned == 1) %>%
  ggplot(aes(x = running, y = sentiment_clean, group = `align_indicator`, color = `align_indicator`)) +
  geom_point(data= data_align %>%
              filter(state_owned == 1) %>%
              group_by(running, csto) %>% 
              summarize(sentiment_clean = mean(sentiment_clean),
                        num_obs = n()),
             aes(x = running, y = sentiment_clean, size=num_obs), alpha=.2, inherit.aes=F) +
  geom_smooth(method="lm") +
  scale_color_manual(values=c("dodgerblue","forestgreen", "red4","darkorange"), name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept=0, linetype="dashed", alpha=.7) +
  theme_classic() +
  labs(title = "Effect of Invasion on State Media Sentiment",
      subtitle = "Neutral VS Russia Aligned, Difference in Discontinuities",
      x = "Days Pre/Post Invasion",
      y = "Sentiment")

state_align_discs_graph

ggsave(plot = state_align_discs_graph, "figures/state_align_discs.png")

```


```{r}
# Alignment State Owned media graph, non-military

data_align %>%
  filter(state_owned == 1) %>%
  filter(!topic_clean %in% "Military") %>%
  ggplot(aes(x = running, y = sentiment_clean, group = `align_indicator`, color = `align_indicator`)) +
  geom_point(data= data_align %>%
              filter(state_owned == 1) %>%
              group_by(running, csto) %>% 
              summarize(sentiment_clean = mean(sentiment_clean),
                        num_obs = n()),
             aes(x = running, y = sentiment_clean, size=num_obs), alpha=.2, inherit.aes=F) +
  geom_smooth(method="lm") +
  scale_color_manual(values=c("dodgerblue","forestgreen", "red4","darkorange"), name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept=0, linetype="dashed", alpha=.7) +
  theme_classic() +
  labs(title = "Figure 7A: Effect of Invasion on State Media Sentiment",
      subtitle = "Neutral VS Russia Aligned, Difference in Discontinuities, Non-Mil Topics",
      x = "Days Pre/Post Invasion",
      y = "Sentiment")

```

### State Differences Regression

```{r}
# State Owned Media, CSTO Regression

data_align_state <- data_align %>%
  filter(state_owned == 1) %>%
  filter(csto == 1)

#model5a <- felm(sentiment_clean ~ running*treatment*csto | country + topic_clean | 0 | source_domain, data = data_align_state)

model5a_state <- felm(sentiment_clean ~ running*treatment | source_domain + topic_clean | 0 | source_domain, data = data_align_state)

summary(model5a_state)
```

```{r}
# State Owned Media, Neutral Regression

data_align_state <- data_align %>%
  filter(state_owned == 1) %>%
  filter(csto == 0)

#model5a <- felm(sentiment_clean ~ running*treatment*csto | country + topic_clean | 0 | source_domain, data = data_align_state)

model5a_neutral <- felm(sentiment_clean ~ running*treatment | source_domain + topic_clean | 0 | source_domain, data = data_align_state)

summary(model5a_neutral)
```

```{r}
# State Owned Media Regression, Diff in Discs

data_align_state <- data_align %>%
  filter(state_owned == 1)

#model5a <- felm(sentiment_clean ~ running*treatment*csto | country + topic_clean | 0 | source_domain, data = data_align_state)

model5a <- felm(sentiment_clean ~ running*treatment*csto | 0 | 0 | source_domain, data = data_align_state)

summary(model5a)
```


```{r}
data_align %>%
  filter(state_owned == 1 & csto == 0) %>%
  ggplot(aes(x = running, y = sentiment_clean, group = `align_indicator`, color = `align_indicator`)) +
  #geom_point(data= data_align %>%
  #            filter(state_owned == 1) %>%
  #            group_by(running, csto) %>% 
  #            summarize(sentiment_clean = mean(sentiment_clean),
  #                      num_obs = n()),
  #           aes(x = running, y = sentiment_clean, size=num_obs), alpha=.2, inherit.aes=F) +
  geom_smooth(method="lm") +
  scale_color_manual(values=c("red4","darkorange"), name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept=0, linetype="dashed", alpha=.7) +
  theme_classic() +
  labs(title = "Figure 7 Extra: Effect of Invasion on State Media Sentiment",
      subtitle = "Neutral VS Russia Aligned, Difference in Discontinuities",
      x = "Days Pre/Post Invasion",
      y = "Sentiment")
```

```{r}
test_model <- lm(sentiment_clean ~ running*treatment + factor(topic_clean) + factor(country), data = data_align_state)

# Pull running values
running_pre <- data_align_state$running[data_align_state$running < 0]
running_post <- data_align_state$running[data_align_state$running > 0]

# Compute fitted values using model coefficients
fitted_pre <- test_model$coefficients["running"] * running_pre

fitted_post <- test_model$coefficients["running"] * running_post +
               test_model$coefficients["running:treatment"] * running_post +
               test_model$coefficients["treatment"]

# Combine into one dataframe
fitted_df <- bind_rows(
  tibble(running = running_pre, fitted = fitted_pre, group = "Pre"),
  tibble(running = running_post, fitted = fitted_post, group = "Post")
)

ggplot(fitted_df, aes(x = running, y = fitted, color = group)) +
  geom_line(size = 1) +
  labs(
    title = "Predicted Outcomes by Running Variable",
    x = "Running Variable",
    y = "Fitted Value",
    color = "Treatment Period"
  ) +
  theme_minimal()
```

```{r}

# Pull running values
running_pre <- data_align_state$running[data_align_state$running < 0]
running_post <- data_align_state$running[data_align_state$running > 0]

# Compute fitted values using model coefficients
fitted_pre_ind <- model2a$coefficients["running",] * running_pre

fitted_pre_state <- model2a$coefficients["running",] * running_pre + 
  model2a$coefficients["running:state_owned",] * running_pre

fitted_post_ind <- model2a$coefficients["running",] * running_post +
               model2a$coefficients["running:treatment",] * running_post +
               model2a$coefficients["treatment",]

fitted_post_state <- model2a$coefficients["running",] * running_post +
               model2a$coefficients["running:treatment",] * running_post +
               model2a$coefficients["running:treatment:state_owned",] * running_post +
               model2a$coefficients["treatment",] +
               model2a$coefficients["treatment:state_owned",]

# Combine into one dataframe
fitted_df <- bind_rows(
  tibble(running = running_pre, fitted = fitted_pre_ind, group = "Pre Ind"),
  tibble(running = running_pre, fitted = fitted_pre_state, group = "Pre State"),
  tibble(running = running_post, fitted = fitted_post_ind, group = "Post Ind"),
  tibble(running = running_post, fitted = fitted_post_state, group = "Post State")
)

ggplot(fitted_df, aes(x = running, y = fitted, color = group)) +
  geom_line(size = 1) +
  labs(
    title = "Predicted Outcomes by Running Variable",
    x = "Running Variable",
    y = "Fitted Value",
    color = "Treatment Period"
  ) +
  theme_minimal()
```



### State Differences Optimal Bandwidth

```{r}
# State Owned Media regression Optimal Bandwidth

summary(rdbwselect(y = data_align_state$sentiment_clean, x = data_align_state$running, kernel = "triangular", cluster = data_align_state$source_domain, p = 1, bwselect = "mserd"))

optimal_bandwidth_data_state <- data_align_state %>%
  filter(running < 55) %>%
  filter(running > -55)

model5a_opt <- felm(sentiment_clean ~ running*treatment*csto | 0 | 0 | source_domain, data = optimal_bandwidth_data_state)

summary(model5a_opt)
```

```{r}
# SD analysis
sd_state_owned <- sd(data_align_state$sentiment_clean)

sd_state_owned

summary(model5a_opt)$coef[7]/sd_state_owned
```


```{r}
# Alignment State Owned media graph

data_align_state %>%
  filter(running < 50) %>%
  filter(running > -50) %>%
  ggplot(aes(x = running, y = sentiment_clean, group = `align_indicator`, color = `align_indicator`)) +
  geom_point(data= data_align_state %>%
              filter(running < 50) %>%
              filter(running > -50) %>%
              group_by(running, csto) %>% 
              summarize(sentiment_clean = mean(sentiment_clean),
                        num_obs = n()),
             aes(x = running, y = sentiment_clean, size=num_obs), alpha=.2, inherit.aes=F) +
  geom_smooth(method="lm") +
  scale_color_manual(values=c("dodgerblue","forestgreen", "red4","darkorange"), name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept=0, linetype="dashed", alpha=.7) +
  theme_classic() +
  labs(title = "Figure 7B: Effect of Invasion on State Media Sentiment",
      subtitle = "Neutral VS Russia Aligned, Difference in Discontinuities, Non-Mil Topics",
      x = "Days Pre/Post Invasion",
      y = "Sentiment")

```


### Russian Alignment, non-military

```{r}
# State Owned Media Regression, Diff in Discs

data_align_state_non_mil <- data_align_state %>%
  filter(!topic_clean %in% "Military")

#model5a <- felm(sentiment_clean ~ running*treatment*csto | country + topic_clean | 0 | source_domain, data = data_align_state)

model5a_non_mil <- felm(sentiment_clean ~ running*treatment*csto | 0 | 0 | source_domain, data = data_align_state_non_mil)

summary(model5a_non_mil)
```

```{r}
# Alignment State Owned media graph, non-military

data_align_state %>%
  filter(!topic_clean %in% "Military") %>%
  ggplot(aes(x = running, y = sentiment_clean, group = `align_indicator`, color = `align_indicator`)) +
  geom_point(data= data_align_state %>%
              filter(running < 50 & running > -50) %>%
              group_by(running, csto) %>% 
              summarize(sentiment_clean = mean(sentiment_clean),
                        num_obs = n()),
             aes(x = running, y = sentiment_clean, size=num_obs), alpha=.2, inherit.aes=F) +
  geom_smooth(method="lm") +
  scale_color_manual(values=c("dodgerblue","forestgreen", "red4","darkorange"), name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept=0, linetype="dashed", alpha=.7) +
  theme_classic() +
  labs(title = "Figure 7C: Effect of Invasion on State Media Sentiment",
      subtitle = "Neutral VS Russia Aligned, Difference in Discontinuities, Non-Mil Topics",
      x = "Days Pre/Post Invasion",
      y = "Sentiment")

```

### Russian Alignment, non-military, russia only

```{r}
# State Owned Media Regression, Diff in Discs

data_align_state_non_mil_russia <- data_align_state_non_mil %>%
  filter(!Russian.Involvement %in% "Not")

model5a_non_mil_russia <- felm(sentiment_clean ~ running*treatment*csto | 0 | 0 | source_domain, data = data_align_state_non_mil_russia)

summary(model5a_non_mil_russia)
```

### Russian Alignment Table

```{r}
# note text
note_text <- "All standard errors are clustered at the source level. Model 2 uses the triangular kernel within the optimal bandwidth. Model 3 omits military-related articles."

# Wrap note into 80-character lines
note_wrapped <- str_wrap(note_text, width = 80)

table_3 <- modelsummary(list(model5a, model5a_opt, model5a_non_mil),
             output ="gt",
             fmt = fmt_significant(2),
             stars = TRUE,
             coef_map = c("treatment" = "Invasion",
                          "treatment:csto" = "CSTO x Treatment"),
             gof_omit = "BIC|AIC|RMSE|Std.Errors",
             title = "Russian Alignment: Difference in Discontinuity Analysis",
             #add_rows = rows,
             notes = note_wrapped
             )

table_3

#save_kable(table_3, "table_3.html", format = "html")

#gtsave(table_3, "figures/table_3.html")
```


```{r}

# Note text, wrapped with <br>
note_text <- "All standard errors are clustered at the source level. Model 2 uses the triangular kernel within the optimal bandwidth. Model 3 omits military-related articles."
note_wrapped <- gsub("\n", "<br>", str_wrap(note_text, width = 80))

# Save as HTML
stargazer(model5a, model5a_opt, model5a_non_mil,
          type = "html",
          out = "figures/table_3.html",
          title = "Russian Alignment: Difference in Discontinuity Analysis",
          covariate.labels = c("Invasion", "CSTO x Treatment"),
          dep.var.labels = "Sentiment",
          notes = note_wrapped,
          notes.align = "l",
          omit.stat = c("aic", "bic", "f", "ll", "ser"))
```


## Russian Ethnic Population
### Threshold of 3%

```{r}
# Create alignment variables
high_russian <- c("Moldova", "Belarus", "Kazakhstan", "Georgia")
low_russian <- c("Azerbaijan", "Armenia", "Kosovo", "Serbia")

data$high_russia <- ifelse(data$country %in% high_russian, 1, 0)

data_ethnic <- data %>%
  filter(nato == 0)

data_ethnic <- data_ethnic %>%
  mutate(ethnic_indicator = factor(case_when(
                                     indicator == 1 & high_russia == 1 ~ "Pre. Ind. High Rus",
                                     indicator == 1 & high_russia == 0 ~ "Pre. Ind. Low Rus",
                                     indicator == 2 & high_russia == 1 ~ "Pre. State High Rus",
                                     indicator == 2 & high_russia == 0 ~ "Pre. State Low Rus",
                                     indicator == 3 & high_russia == 1 ~ "Post Ind. High Rus",
                                     indicator == 3 & high_russia == 0 ~ "Post Ind. Low Rus",
                                     indicator == 4 & high_russia == 1 ~ "Post State High Rus",
                                     indicator == 4 & high_russia == 0 ~ "Post State Low Rus"),
                                     levels = c("Pre. Ind. High Rus", "Pre. Ind. Low Rus", "Pre. State High Rus", "Pre. State Low Rus", "Post Ind. High Rus", "Post Ind. Low Rus", "Post State High Rus", "Post State Low Rus")))

```


```{r}
# Ethnic Independent media graph

data_ethnic %>%
  filter(state_owned == 0) %>%
  ggplot(aes(x = running, y = sentiment_clean, group = `ethnic_indicator`, color = `ethnic_indicator`)) +
  geom_point(data= data_ethnic %>%
              filter(state_owned == 0) %>%
              group_by(running, csto) %>% 
              summarize(sentiment_clean = mean(sentiment_clean),
                        num_obs = n()),
             aes(x = running, y = sentiment_clean, size=num_obs), alpha=.2, inherit.aes=F) +
  geom_smooth(method="lm") +
  scale_color_manual(values=c("dodgerblue","forestgreen", "red4","darkorange"), name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept=0, linetype="dashed", alpha=.7) +
  theme_classic() +
  labs(title = "Figure 8: Effect of Invasion on Indpendent Media Sentiment",
      subtitle = "High VS Low Ethnic Russian, Difference in Discontinuities",
      x = "Days Pre/Post Invasion",
      y = "Sentiment")

```


```{r}
# Ethnic State Owned media graph

ethnic_discs_graph <- data_ethnic %>%
  filter(state_owned == 1) %>%
  ggplot(aes(x = running, y = sentiment_clean, group = `ethnic_indicator`, color = `ethnic_indicator`)) +
  geom_point(data= data_ethnic %>%
              filter(state_owned == 1) %>%
              group_by(running, csto) %>% 
              summarize(sentiment_clean = mean(sentiment_clean),
                        num_obs = n()),
             aes(x = running, y = sentiment_clean, size=num_obs), alpha=.2, inherit.aes=F) +
  geom_smooth(method="lm") +
  scale_color_manual(values=c("dodgerblue","forestgreen", "red4","darkorange"), name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept=0, linetype="dashed", alpha=.7) +
  theme_classic() +
  labs(title = "Effect of Invasion on State Media Sentiment",
      subtitle = "High VS Low Ethnic Russian, Difference in Discontinuities",
      x = "Days Pre/Post Invasion",
      y = "Sentiment")

ethnic_discs_graph

ggsave(plot = ethnic_discs_graph, "figures/ethnic_discs.png")
```


### Regresion Result

```{r}
# State Owned Media Regression, Diff in Discs

data_ethnic_state <- data_ethnic %>%
  filter(state_owned == 1)

model6a <- felm(sentiment_clean ~ running*treatment*high_russia | 0 | 0 | 0, data = data_ethnic_state)

summary(model6a)
```


## State Motivation

```{r}
# Ethnic State Owned media graph

data <- data %>%
  mutate(state_indicator = factor(paste(country, treatment, sep = ", ")))

# Create alliance for faceting
data_long <- data %>%
  pivot_longer(cols = c(nato, csto, neutral),
               names_to = "alliance",
               values_to = "membership") %>%
  filter(membership == 1) %>%
  mutate(alliance = factor(alliance, levels = c("nato", "csto", "neutral")))

data_long %>%
  filter(state_owned == 1) %>%
  ggplot(aes(x = running, y = sentiment_clean, group = state_indicator, color = country)) +
  geom_smooth(method = "lm", se = FALSE) +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  scale_size(name = "Observations") +
  theme_classic() +
  facet_wrap(~alliance, nrow = 2) +
  labs(
    title = "Figure 9: Effect of Invasion on State Media Sentiment",
    subtitle = "High VS Low Ethnic Russian, Difference in Discontinuities",
    x = "Days Pre/Post Invasion",
    y = "Sentiment"
  )

```

```{r}
# Prepare the data
sentiment_table <- data %>%
  filter(running >= -10 & running <= 10) %>%
  filter(state_owned == 1) %>%
  mutate(window = case_when(
    running < 0 ~ "Before Invasion",
    running > 0 ~ "After Invasion"
  )) %>%
  group_by(country, window) %>%
  summarize(mean_sentiment = mean(sentiment_clean, na.rm = TRUE), .groups = "drop") %>%
  pivot_wider(
    names_from = window,
    values_from = mean_sentiment
  ) %>%
  mutate(across(c(`Before Invasion`, `After Invasion`), ~round(., 3))) %>%
  select(-"NA") %>%
  mutate(Difference = `After Invasion` - `Before Invasion`) %>%
  select(country, "Before Invasion", "After Invasion", Difference)

# Make the gt table
gt_table <- sentiment_table %>%
  gt() %>%
  tab_header(
    title = "Mean Sentiment Before and After Invasion",
    subtitle = "By Country, within ±10 Day Window"
  ) %>%
  cols_label(
    country = "Country",
    `Before Invasion` = "Mean Sentiment (Before)",
    `After Invasion` = "Mean Sentiment (After)",
    `Difference` = "Difference"
  ) %>%
  fmt_number(
    columns = c(`Before Invasion`, `After Invasion`, `Difference`),
    decimals = 3
  )

gt_table
```


```{r}
# Define a function to get mean, SE, and p-value for each country
summarize_stats <- function(df) {
  before <- df %>% filter(running >= -14 & running < 0)
  after  <- df %>% filter(running > 0 & running <= 14)
  
  # Paired t-test
  ttest <- t.test(before$sentiment_clean, after$sentiment_clean, paired = FALSE)
  
  tibble(
    mean_before = mean(before$sentiment_clean, na.rm = TRUE),
    se_before = sd(before$sentiment_clean, na.rm = TRUE) / sqrt(nrow(before)),
    mean_after = mean(after$sentiment_clean, na.rm = TRUE),
    se_after = sd(after$sentiment_clean, na.rm = TRUE) / sqrt(nrow(after)),
    diff = - mean(before$sentiment_clean, na.rm = TRUE) + mean(after$sentiment_clean, na.rm = TRUE),
    p_value = ttest$p.value
  )
}

# Apply to each country
sentiment_summary <- data %>%
  filter(running >= -14 & running <= 14) %>%
  filter(state_owned == 1) %>%
  group_by(country) %>%
  group_modify(~summarize_stats(.x)) %>%
  ungroup()

# Add significance stars
sentiment_summary <- sentiment_summary %>%
  mutate(
    stars = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01 ~ "**",
      p_value < 0.05 ~ "*",
      is.na(p_value) ~ "",
      TRUE ~ ""
    ),
    diff_label = paste0(round(diff, 3), " ", stars),
    before_label = paste0(round(mean_before, 3), "\n(", round(se_before, 3), ")"),
    after_label = paste0(round(mean_after, 3), "\n(", round(se_after, 3), ")")
  )


country_table <- sentiment_summary %>%
  select(country, before_label, after_label, diff_label) %>%
  gt() %>%
  tab_header(
    title = "Mean Sentiment Before and After Invasion",
    subtitle = "With Standard Errors and Significance Stars (±2 Week Window)"
  ) %>%
  cols_label(
    country = "Country",
    before_label = "Before",
    after_label = "After",
    diff_label = "Diff (After - Before)"
  ) %>%
  tab_style(
    style = cell_text(align = "center"),
    locations = cells_body()
  )

country_table


#gtsave(country_table, "figures/country_table.html")
```


```{r}
# Hand check

test_kazakhstan_before <- data_non_ukraine %>%
  filter(country %in% "Kazakhstan" & treatment == 0 & state_owned == 1) %>%
  filter(running >= -14 & running < 0)

test_kazakhstan_after <- data_non_ukraine %>%
  filter(country %in% "Kazakhstan" & treatment == 1 & state_owned == 1) %>% 
  filter(running > 0 & running <= 14)

t.test(test_kazakhstan_before$sentiment_clean,test_kazakhstan_after$sentiment_clean)
```

# Summary statistics and descriptive analysis

## Basic Summary statistics
```{r}

# Create summary stats
sample_summary <- tibble(
  `Total articles` = nrow(data_non_ukraine),
  `Number of countries` = n_distinct(data_non_ukraine$country),
  `Date range` = paste0(
    format(min(data_non_ukraine$date_publish, na.rm = TRUE), "%Y-%m-%d"),
    " to ",
    format(max(data_non_ukraine$date_publish, na.rm = TRUE), "%Y-%m-%d")
  ),
  `Mean sentiment` = round(mean(data_non_ukraine$sentiment_clean, na.rm = TRUE), 3),
  `Sentiment SD` = round(sd(data_non_ukraine$sentiment_clean, na.rm = TRUE), 3),
  `State-owned %` = round(mean(data_non_ukraine$state_owned, na.rm = TRUE) * 100, 1),
  `Independent %` = round(100 - mean(data_non_ukraine$state_owned, na.rm = TRUE) * 100, 1),
  `Number of unique sources` = n_distinct(data_non_ukraine$source_domain),
  `Number of topics` = n_distinct(data_non_ukraine$topic_clean)
) %>%
  mutate(across(everything(), as.character))  # Convert all to character

summary_statistics_table <- sample_summary %>%
  pivot_longer(everything(), names_to = "Statistic", values_to = "Value") %>%
  gt() %>%
  tab_header(
    title = "Descriptive Overview of News Article Dataset"
  ) %>%
  cols_label(
    Statistic = "Statistic",
    Value = "Value"
  ) %>%
  tab_style(
    style = cell_text(align = "left"),
    locations = cells_body(columns = Statistic)
  )

summary_statistics_table

gtsave(summary_statistics_table, "figures/summary_statistics_table.html")
```


## Distribution by Topic

```{r}

# Step 1: Create a before/after indicator
data_topic_counts <- data_non_ukraine %>%
  filter(!is.na(topic_clean)) %>%
  mutate(
    topic_clean = factor(topic_clean, levels = c("Political", "Military", "Economic", "Culture", "Other")),
    period = case_when(
    running < 0 ~ "Before Invasion",
    running > 0 ~ "After Invasion",
    TRUE ~ NA_character_
  )) %>%
  filter(!is.na(period)) %>%
  group_by(topic_clean, period) %>%
  summarize(article_count = n(), .groups = "drop")


# Make plot
topic_all <- ggplot(data_topic_counts, aes(x = topic_clean, y = article_count, fill = period)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(
    title = "Distribution of Articles by Topic",
    subtitle = "Before and After Invasion",
    x = "Topic",
    y = "Number of Articles",
    fill = "Period"
  ) +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "bottom"
  )


topic_all

ggsave(plot = topic_all, "figures/topic_distribution.png")
```

## Distribution by Topic, State vs Independent

```{r}
# Step 1: Create a before/after indicator
data_topic_counts_state <- data_non_ukraine %>%
  filter(!is.na(topic_clean)) %>%
  filter(state_owned == 1) %>%
  mutate(topic_clean = factor(topic_clean, levels = c("Political", "Military", "Economic", "Culture", "Other")),
    period = case_when(
    running < 0 ~ "Before Invasion",
    running > 0 ~ "After Invasion",
    TRUE ~ NA_character_
  )) %>%
  filter(!is.na(period)) %>%
  group_by(topic_clean, period) %>%
  summarize(article_count = n(), .groups = "drop")

data_topic_counts_ind <- data_non_ukraine %>%
  filter(!is.na(topic_clean)) %>%
  filter(state_owned == 0) %>%
  mutate(topic_clean = factor(topic_clean, levels = c("Political", "Military", "Economic", "Culture", "Other")),
    period = case_when(
    running < 0 ~ "Before Invasion",
    running > 0 ~ "After Invasion",
    TRUE ~ NA_character_
  )) %>%
  filter(!is.na(period)) %>%
  group_by(topic_clean, period) %>%
  summarize(article_count = n(), .groups = "drop")

# Make both plots with legends turned **on**, but hide legend in one
topic_state <- ggplot(data_topic_counts_state, aes(x = topic_clean, y = article_count, fill = period)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(
    title = "Distribution of Articles by Topic",
    subtitle = "State Media",
    x = "Topic",
    y = "Number of Articles",
    fill = "Period"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "bottom"
  )

topic_ind <- ggplot(data_topic_counts_ind, aes(x = topic_clean, y = article_count, fill = period)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(
    title = "",
    subtitle = "Independent Media",
    x = "Topic",
    y = "Number of Articles",
    fill = "Period"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "none"
  )

# Combine with patchwork: one legend at bottom
topic_split <- (topic_state | topic_ind) + plot_layout(guides = "collect") & theme(legend.position = "bottom")

topic_split

ggsave(plot = topic_split, "figures/topic_split.png")

```

## Sentiment by Topic

```{r}
# Desired topic order
topic_order <- c("Political", "Military", "Economic", "Culture", "Other")

# Step 1: Summary stats by topic and period
sentiment_topic_stats <- data_non_ukraine %>%
  filter(!is.na(topic_clean), topic_clean %in% topic_order) %>%
  mutate(
    period = case_when(
      running < 0 ~ "Before",
      running > 0 ~ "After",
      TRUE ~ NA_character_
    )
  ) %>%
  filter(!is.na(period)) %>%
  group_by(topic_clean, period) %>%
  summarize(
    mean_sentiment = mean(sentiment_clean, na.rm = TRUE),
    sd_sentiment = sd(sentiment_clean, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    label = paste0(round(mean_sentiment, 3), "\n(", round(sd_sentiment, 3), ")")
  ) %>%
  select(topic_clean, period, label) %>%
  pivot_wider(names_from = period, values_from = label)

# Step 2: Compute After - Before difference and p-values
diff_stats <- data_non_ukraine %>%
  filter(!is.na(topic_clean), topic_clean %in% topic_order) %>%
  mutate(
    period = case_when(
      running < 0 ~ "Before",
      running > 0 ~ "After",
      TRUE ~ NA_character_
    )
  ) %>%
  filter(!is.na(period)) %>%
  group_by(topic_clean) %>%
  group_modify(~ {
    before_vals <- .x$sentiment_clean[.x$period == "Before"]
    after_vals  <- .x$sentiment_clean[.x$period == "After"]
    
    t_result <- t.test(after_vals, before_vals, paired = FALSE)

    tibble(
      after_mean = mean(after_vals, na.rm = TRUE),
      before_mean = mean(before_vals, na.rm = TRUE),
      diff = after_mean - before_mean,
      p_value = t_result$p.value
    )
  }) %>%
  mutate(
    stars = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01 ~ "**",
      p_value < 0.05 ~ "*",
      TRUE ~ ""
    ),
    Difference = paste0(round(diff, 3), " ", stars)
  ) %>%
  select(topic_clean, Difference)

# Step 3: Merge and reorder columns
summary_table <- sentiment_topic_stats %>%
  left_join(diff_stats, by = "topic_clean") %>%
  mutate(topic_clean = factor(topic_clean, levels = topic_order)) %>%
  arrange(topic_clean) %>%
  select(topic_clean, Before, After, Difference)

# Make the table

sentiment_by_topic_table <- summary_table %>%
  gt() %>%
  tab_header(
    title = "Sentiment by Topic: Before and After Invasion",
    subtitle = "Mean Sentiment with Standard Deviations and Significance (After - Before)"
  ) %>%
  cols_label(
    topic_clean = "Topic",
    Before = "Before",
    After = "After",
    Difference = "Difference"
  ) %>%
  tab_style(
    style = cell_text(align = "center"),
    locations = cells_body(columns = c(Before, After, Difference))
  ) %>%
  tab_style(
    style = cell_text(align = "left"),
    locations = cells_body(columns = topic_clean)
  )

sentiment_by_topic_table

gtsave(sentiment_by_topic_table, "figures/sentiment_by_topic.html")
```


```{r}
# Hand check

test_political_before <- data_non_ukraine %>%
  filter(topic_clean == "Political" & treatment == 0)

test_political_after <- data_non_ukraine %>%
  filter(topic_clean == "Political" & treatment == 1)

t.test(test_political_before$sentiment_clean,test_political_after$sentiment_clean)
```

## Articles per Day Graph

```{r}
# Step 1: Prepare daily article counts by media type
articles_per_day_by_ownership <- data %>%
  filter(!is.na(date_publish)) %>%
  mutate(
    media_type = ifelse(state_owned == 1, "State-Owned", "Independent")
  ) %>%
  group_by(date = as.Date(date_publish), media_type) %>%
  summarize(article_count = n(), .groups = "drop")

# Step 2: Plot
articles_per_day_plot <- ggplot(articles_per_day_by_ownership, aes(x = date, y = article_count, color = media_type)) +
  geom_line(size = 1) +
  geom_vline(xintercept = as.Date("2022-02-24"), linetype = "dashed", color = "black", linewidth = 1) +
  labs(
    title = "Articles Over Time by Media Ownership",
    subtitle = "Black dashed line = Day of Invasion (2022-02-24)",
    x = "Date",
    y = "Number of Articles",
    color = "Media Type"
  ) +
  theme_bw() +
  theme(
    legend.position = "bottom",
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10)
  )

articles_per_day_plot

ggsave(plot = articles_per_day_plot, "figures/articles_per_day.png")
```

```{r}
# Get article count for independent media on 2021-09-20
highlight_point <- articles_per_day_by_ownership %>%
  filter(date == as.Date("2021-09-20"), media_type == "Independent")

articles_per_day_plot_annotated <- ggplot(articles_per_day_by_ownership, aes(x = date, y = article_count, color = media_type)) +
  geom_line(size = 1) +

  # Black dashed line for invasion
  geom_vline(xintercept = as.Date("2022-02-24"), linetype = "dashed", color = "black", linewidth = 1) +

  # Text label above the arrow
  annotate(
    "text",
    x = as.Date("2021-09-20"),
    y = highlight_point$article_count + 500,
    label = "Perm State University Shooting\n& Russian Election",
    hjust = 0.5,
    size = 3.5,
    color = "black"
  ) +

  # Proper arrow pointing down
  geom_curve(
  aes(x = as.Date("2021-09-20"), xend = as.Date("2021-09-20"),
      y = highlight_point$article_count + 300, yend = highlight_point$article_count + 25),
  arrow = arrow(type = "closed", length = unit(0.15, "inches")),
  color = "goldenrod1",
  curvature = 0,        # straight line (not curved)
  linewidth = 0.75,
  inherit.aes = FALSE
  ) +

  labs(
    title = "Articles Over Time by Media Ownership",
    subtitle = "Black dashed line = Day of Invasion (2022-02-24)",
    x = "Date",
    y = "Number of Articles",
    color = "Media Type"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10)
  )

articles_per_day_plot_annotated

ggsave(plot = articles_per_day_plot_annotated, "figures/articles_per_day_anno.png")
```


## Tables for State Behavior

```{r}
# Intersection function
get_group <- function(russian_group, security_group) {
  paste(intersect(russian_group, security_group), collapse = ", ")
}

# Create table data
table_data <- data.frame(
  `Ethnic Russian Population` = c("Low Ethnic", "High Ethnic"),
  `Low Russia Aligned` = c(
    get_group(low_russian, neutral),
    get_group(high_russian, neutral)
  ),
  `High Russia Aligned` = c(
    get_group(low_russian, csto),
    get_group(high_russian, csto)
  )
)

# Create GT table

main_table <- table_data %>%
  gt() %>%
  tab_header(
    title = "Ethnic Russian Population × Russia Security Alignment",
    subtitle = "Potential Comparisons"
  ) %>%
  cols_label(
    Ethnic.Russian.Population = "",
    Low.Russia.Aligned = "Low Alignment",
    High.Russia.Aligned = "High Alignment"
  ) %>%
  fmt_markdown(everything()) %>%
  
  # Vertical divider between the two alignment columns
  tab_style(
    style = cell_borders(
      sides = "right",
      color = "black",
      weight = px(2)
    ),
    locations = cells_body(columns = "Low.Russia.Aligned")
  ) %>%
  
  # Horizontal divider between the two ethnic population rows
  tab_style(
    style = cell_borders(
      sides = "bottom",
      color = "black",
      weight = px(2)
    ),
    locations = cells_body(rows = 1, columns = 2:3)
  ) %>%
  
  # Outline top of the top row
  tab_style(
    style = cell_borders(
      sides = "top",
      color = "black",
      weight = px(2)
    ),
    locations = cells_body(rows = 1, columns = 2:3)
  ) %>%
  
  # Outline bottom of the bottom row
  tab_style(
    style = cell_borders(
      sides = "bottom",
      color = "black",
      weight = px(2)
    ),
    locations = cells_body(rows = 2, columns = 2:3)
  ) %>%
  
  # Outline left of first column in result cells
  tab_style(
    style = cell_borders(
      sides = "left",
      color = "black",
      weight = px(2)
    ),
    locations = cells_body(rows = 1:2, columns = 2)
  ) %>%
  
  # Outline right of second column in result cells
  tab_style(
    style = cell_borders(
      sides = "right",
      color = "black",
      weight = px(2)
    ),
    locations = cells_body(rows = 1:2, columns = 3)
  )

main_table

gtsave(main_table, "figures/comparison_table.html")
```


```{r}
# Alignment table
# Create GT table

alignment_table <- table_data %>%
  gt() %>%
  tab_header(
    title = "Ethnic Russian Population × Russia Security Alignment",
    subtitle = "Alignment Comparison"
  ) %>%
  cols_label(
    Ethnic.Russian.Population = "",
    Low.Russia.Aligned = "Low Alignment",
    High.Russia.Aligned = "High Alignment"
  ) %>%
  fmt_markdown(everything()) %>%
  
  # Vertical divider between the two alignment columns
  tab_style(
    style = cell_borders(
      sides = "right",
      color = "black",
      weight = px(2)
    ),
    locations = cells_body(columns = "Low.Russia.Aligned")
  ) %>%
  
  # Horizontal divider between the two ethnic population rows
  tab_style(
    style = cell_borders(
      sides = "bottom",
      color = "white",
      weight = px(2)
    ),
    locations = cells_body(rows = 1, columns = 2:3)
  ) %>%
  
  # Outline top of the top row
  tab_style(
    style = cell_borders(
      sides = "top",
      color = "black",
      weight = px(2)
    ),
    locations = cells_body(rows = 1, columns = 2:3)
  ) %>%
  
  # Outline bottom of the bottom row
  tab_style(
    style = cell_borders(
      sides = "bottom",
      color = "black",
      weight = px(2)
    ),
    locations = cells_body(rows = 2, columns = 2:3)
  ) %>%
  
  # Outline left of first column in result cells
  tab_style(
    style = cell_borders(
      sides = "left",
      color = "black",
      weight = px(2)
    ),
    locations = cells_body(rows = 1:2, columns = 2)
  ) %>%
  
  # Outline right of second column in result cells
  tab_style(
    style = cell_borders(
      sides = "right",
      color = "black",
      weight = px(2)
    ),
    locations = cells_body(rows = 1:2, columns = 3)
  )

alignment_table

gtsave(alignment_table, "figures/alignment_table.html")
```


```{r}
# Ethnic table
# Create GT table

ethnic_table <- table_data %>%
  gt() %>%
  tab_header(
    title = "Ethnic Russian Population × Russia Security Alignment",
    subtitle = "Ethnic Comparison"
  ) %>%
  cols_label(
    Ethnic.Russian.Population = "",
    Low.Russia.Aligned = "Low Alignment",
    High.Russia.Aligned = "High Alignment"
  ) %>%
  fmt_markdown(everything()) %>%
  
  # Vertical divider between the two alignment columns
  tab_style(
    style = cell_borders(
      sides = "right",
      color = "white  ",
      weight = px(2)
    ),
    locations = cells_body(columns = "Low.Russia.Aligned")
  ) %>%
  
  # Horizontal divider between the two ethnic population rows
  tab_style(
    style = cell_borders(
      sides = "bottom",
      color = "black",
      weight = px(2)
    ),
    locations = cells_body(rows = 1, columns = 2:3)
  ) %>%
  
  # Outline top of the top row
  tab_style(
    style = cell_borders(
      sides = "top",
      color = "black",
      weight = px(2)
    ),
    locations = cells_body(rows = 1, columns = 2:3)
  ) %>%
  
  # Outline bottom of the bottom row
  tab_style(
    style = cell_borders(
      sides = "bottom",
      color = "black",
      weight = px(2)
    ),
    locations = cells_body(rows = 2, columns = 2:3)
  ) %>%
  
  # Outline left of first column in result cells
  tab_style(
    style = cell_borders(
      sides = "left",
      color = "black",
      weight = px(2)
    ),
    locations = cells_body(rows = 1:2, columns = 2)
  ) %>%
  
  # Outline right of second column in result cells
  tab_style(
    style = cell_borders(
      sides = "right",
      color = "black",
      weight = px(2)
    ),
    locations = cells_body(rows = 1:2, columns = 3)
  )

ethnic_table

gtsave(ethnic_table, "figures/ethnic_table.html")
```