---
title: "Archived - Non-Parametric Saturation Check (Main RDD, H1)"
author: "Donald Moratz"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

# Overview

This is an **archived** robustness diagnostic that was lifted out of the main RDD analysis
(`04*_main_rdd_analysis*`). It cross-checks the RDD discontinuity for a single country by
building a fully non-parametric, hierarchically-weighted RD estimate (source-topic → source →
country) and comparing it against several `rdrobust` specifications. It is retained here for
reference and is **not** part of the main pipeline.

The code below uses the probabilistic running variable (`running_probabilistic`), matching the
primary (prob) analysis. To reproduce the day or drop variants, swap the running variable and
input data accordingly.

**Inputs:**
- `data/intermediate/02_data_non_ukraine.rds`

```{r setup-archive}
source(here::here("scripts", "00_setup.R"))

set.seed(3184)
```

```{r load-archive}
data_non_ukraine <- readRDS(file.path(DATA_INTERMEDIATE, "02_data_non_ukraine.rds"))
data_non_ukraine <- data_non_ukraine %>%
  mutate(across(c(topic_clean, country, source_domain), as.factor))

# rdrobust selects the bandwidth internally, so the full sample is used as-is
optimal_bandwidth_data <- data_non_ukraine
```

# Robustness: Non-Parametric Saturation Check

```{r nonparam-check}
country_name <- "Kosovo"

country_data <- optimal_bandwidth_data %>%
  filter(country == country_name)

bw_select <- rdbwselect(y = country_data$sentiment_clean,
                        x = country_data$running_probabilistic,
                        cluster = country_data$source_domain,
                        kernel = "triangular",
                        p = 1,
                        bwselect = "mserd")

# Extract bandwidth
optimal_bw <- bw_select$bws[1, 1]
cat("\nOptimal bandwidth:", round(optimal_bw, 1), "hours\n")

# Filter to optimal bandwidth
country_data <- country_data %>%
  filter(running_probabilistic < optimal_bw) %>%
  filter(running_probabilistic > -optimal_bw)

cat("Observations within optimal bandwidth:", nrow(country_data), "\n")

# Step 1: Source-topic level - calculate average sentiment just before and after discontinuity
source_topic_rd <- country_data %>%
  mutate(post = ifelse(running_probabilistic >= 0, 1, 0)) %>%
  group_by(source_domain, topic_clean, post) %>%
  summarize(
    mean_sentiment = mean(sentiment_clean, na.rm = TRUE),
    n_articles = n(),
    .groups = "drop"
  ) %>%
  pivot_wider(
    names_from = post,
    values_from = c(mean_sentiment, n_articles)
  ) %>%
  mutate(
    # Discontinuity for this source-topic
    rd_effect = mean_sentiment_1 - mean_sentiment_0,
    total_articles = n_articles_0 + n_articles_1
  )

# Step 2: Source level - weighted average across topics
source_rd <- source_topic_rd %>%
  group_by(source_domain) %>%
  summarize(
    source_rd_effect = weighted.mean(rd_effect, w = total_articles, na.rm = TRUE),
    total_articles = sum(total_articles, na.rm = TRUE),
    .groups = "drop"
  )

# Step 3: Country level - weighted average across sources
country_rd <- source_rd %>%
  summarize(
    country_rd_effect = weighted.mean(source_rd_effect, w = total_articles, na.rm = TRUE)
  )

print(paste("Non-parametric RD estimate for", country_name, ":", country_rd$country_rd_effect))
```

```{r nonparam-compare}
# RD robust versions
# Version 1: Local constant (p=0), uniform kernel, no covariates
# This should match the non-parametric estimate most closely
model_rd_v1 <- rdrobust(
  y = country_data$sentiment_clean,
  x = country_data$running_probabilistic,
  cluster = country_data$source_domain,
  h = optimal_bw,
  kernel = "uniform",
  p = 0
)

# Version 2: Local constant, uniform kernel, with covariates
covs_matrix_country <- model.matrix(~ source_domain + topic_clean - 1, data = country_data)
model_rd_v2 <- rdrobust(
  y = country_data$sentiment_clean,
  x = country_data$running_probabilistic,
  covs = covs_matrix_country,
  cluster = country_data$source_domain,
  h = optimal_bw,
  kernel = "uniform",
  p = 0
)

# Version 3: Your original spec - local linear, triangular kernel, with covariates
model_rd_v3 <- rdrobust(
  y = country_data$sentiment_clean,
  x = country_data$running_probabilistic,
  covs = covs_matrix_country,
  cluster = country_data$source_domain,
  h = optimal_bw  # Using same bandwidth for fair comparison
)

# Compare
comparison <- data.frame(
  Method = c(
    "Non-parametric",
    "rdrobust (p=0, uniform, no covs)",
    "rdrobust (p=0, uniform, with covs)",
    "rdrobust (p=1, triangular, with covs)"
  ),
  Estimate = c(
    country_rd$country_rd_effect,
    model_rd_v1$coef[1],
    model_rd_v2$coef[1],
    model_rd_v3$coef[1]
  )
)

print(comparison)
```

```{r nonparam-coef}
print("Model 1 coef:")
print(model_rd_v1$coef)
print(length(model_rd_v1$coef))

print("Model 2 coef:")
print(model_rd_v2$coef)
print(length(model_rd_v2$coef))

print("Model 3 coef:")
print(model_rd_v3$coef)
print(length(model_rd_v3$coef))

print("Non-parametric:")
print(country_rd$country_discontinuity)
print(length(country_rd$country_discontinuity))
```
