---
title: "Archived - Non-Parametric Saturation Check (Diff-in-Disc, H2)"
author: "Donald Moratz"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

# Overview

This is an **archived** robustness diagnostic that was lifted out of the diff-in-disc
analysis (`05*_diff_in_disc_analysis*`). For a single country it builds a fully
non-parametric, hierarchically-weighted diff-in-disc estimate (source-topic → source →
state-ownership) and compares the state-ownership treatment effect against several `feols`
specifications. It is retained here for reference and is **not** part of the main pipeline.

The code uses the probabilistic running variable (`running_probabilistic`) to match the
primary (prob) analysis. To reproduce the day or drop variants, swap the running variable and
input data accordingly.

**Inputs:**
- `data/intermediate/02_data_non_ukraine.rds`

```{r setup-archive}
source(here::here("scripts", "00_setup.R"))

set.seed(3184)
```

```{r load-archive}
data_non_ukraine <- readRDS(file.path(DATA_INTERMEDIATE, "02_data_non_ukraine.rds"))
data_non_ukraine <- data_non_ukraine %>%
  mutate(across(c(topic_clean, country, source_domain), as.factor))

# Reconstruct the non-military, non-NATO optimal-bandwidth sample used by the check
# (mirrors the Non-NATO section of the 05 diff-in-disc analysis).
data_non_mil <- data_non_ukraine %>%
  filter(!topic_clean %in% c("Military"))

data_non_nato <- data_non_mil %>%
  filter(!country %in% NATO_COUNTRIES)

# Residualize the dependent variable for fixed effects to do bandwidth selection
resid_y <- feols(sentiment_clean ~ 1 | topic_clean + state_owned,
                 data = data_non_nato)$residuals

bw_align_non_nato <- rdbwselect(y = resid_y,
                                x = data_non_nato$running_probabilistic,
                                kernel = "triangular",
                                cluster = data_non_nato$source_domain,
                                p = 1,
                                bwselect = "mserd")

optimal_bw_align_non_nato <- bw_align_non_nato$bws[1, 1]

optimal_bandwidth_data_non_nato <- data_non_nato %>%
  filter(running_probabilistic < optimal_bw_align_non_nato,
         running_probabilistic > -optimal_bw_align_non_nato) %>%
  droplevels()
```

# Non-Parametric Saturation Check

```{r nonparam-check}
country_name <- "Kosovo"
country_data <- optimal_bandwidth_data_non_nato %>%
  filter(country == country_name)

# Filter to only source-topic combinations with both pre and post data
balanced_data <- country_data %>%
  group_by(source_domain, topic_clean) %>%
  mutate(
    has_pre = any(treatment == 0),
    has_post = any(treatment == 1)
  ) %>%
  filter(has_pre & has_post) %>%
  select(-has_pre, -has_post) %>%
  ungroup()

# Step 1: Source-topic level - pre vs post difference in means
source_topic_effects <- balanced_data %>%
  group_by(source_domain, topic_clean, treatment) %>%
  summarize(
    mean_sentiment = mean(sentiment_clean, na.rm = TRUE),
    n_articles = n(),
    .groups = "drop"
  ) %>%
  pivot_wider(
    names_from = treatment,
    values_from = c(mean_sentiment, n_articles)
  ) %>%
  mutate(
    # Pre-post difference for this source-topic
    diff = mean_sentiment_1 - mean_sentiment_0,
    # Total articles for this source-topic (for weighting)
    total_articles = n_articles_0 + n_articles_1
  )

# Step 2: Source level - weighted average across topics
source_effects <- source_topic_effects %>%
  group_by(source_domain) %>%
  summarize(
    source_effect = weighted.mean(diff, w = total_articles, na.rm = TRUE),
    total_articles = sum(total_articles, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  left_join(
    country_data %>% distinct(source_domain, state_owned),
    by = "source_domain"
  )

# Step 3: Country-state_owned level - weighted average within state ownership
state_owned_effects <- source_effects %>%
  group_by(state_owned) %>%
  summarize(
    state_owned_effect = weighted.mean(source_effect, w = total_articles, na.rm = TRUE),
    total_articles = sum(total_articles, na.rm = TRUE),
    .groups = "drop"
  )

print("State-owned effects:")
print(state_owned_effects)

# Step 4: The treatment effect of state ownership - do it manually
effect_independent <- state_owned_effects$state_owned_effect[state_owned_effects$state_owned == 0]
effect_state_owned <- state_owned_effects$state_owned_effect[state_owned_effects$state_owned == 1]

treatment_effect <- effect_state_owned - effect_independent

print(paste("Non-parametric treatment effect of state ownership:", treatment_effect))


```

```{r nonparam-compare}
# Now run the regression comparisons
model_simple <- feols(
  sentiment_clean ~ treatment * state_owned |
    source_domain^topic_clean + topic_clean^treatment,
  cluster = ~source_domain,
  data = balanced_data
)

model_full <- feols(
  sentiment_clean ~ running * treatment * state_owned |
    source_domain^topic_clean + topic_clean^treatment,
  cluster = ~source_domain,
  data = balanced_data
)

# Model WITHOUT topic:treatment FE
model_exact <- feols(
  sentiment_clean ~ treatment * state_owned |
    source_domain^topic_clean,
  cluster = ~source_domain,
  data = balanced_data
)

# Compare
comparison <- data.frame(
  Method = c("Non-parametric",
             "Regression (without topic:treatment FE)",
             "Regression (Simple - with topic:treatment FE)",
             "Regression (Full)"),
  Estimate = c(
    treatment_effect,
    coef(model_exact)["treatment:state_owned"],
    coef(model_simple)["treatment:state_owned"],
    coef(model_full)["treatment:state_owned"]
  )
)

print(comparison)
```

```{r nonparam-distribution}
# Check the distribution of articles
print("Distribution of articles by source-topic-treatment:")
distribution_check <- country_data %>%
  group_by(source_domain, topic_clean, treatment) %>%
  summarize(n = n(), .groups = "drop") %>%
  summary()
print(distribution_check)

# Check if any source-topic combinations are missing pre or post data
missing_check <- country_data %>%
  group_by(source_domain, topic_clean, treatment) %>%
  summarize(n = n(), .groups = "drop") %>%
  pivot_wider(names_from = treatment, values_from = n, names_prefix = "treatment_") %>%
  filter(is.na(treatment_0) | is.na(treatment_1))

print("Source-topic combinations missing pre or post data:")
print(missing_check)
```
