---
title: "Archived - Non-Parametric Saturation Check (Alignment, H3a)"
author: "Donald Moratz"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

# Overview

This is an **archived** robustness diagnostic that was lifted out of the Russian alignment
analysis (`06*_russian_alignment_analysis*`). Using one CSTO and one non-CSTO country, it
builds a fully non-parametric, hierarchically-weighted estimate of the CSTO treatment effect
(source-topic → source → country → CSTO vs non-CSTO) and compares it against several `feols`
specifications. It is retained here for reference and is **not** part of the main pipeline.

The code uses the day running variable (`running`) to match the base (day) analysis. To
reproduce the probabilistic or drop variants, swap the running variable and input data
accordingly.

**Inputs:**
- `data/intermediate/02_cleaned_data.rds`

```{r setup-archive}
source(here::here("scripts", "00_setup.R"))

set.seed(3184)
```

```{r load-archive}
data <- readRDS(file.path(DATA_INTERMEDIATE, "02_cleaned_data.rds"))
data <- data %>% mutate(across(c(topic_clean, country, source_domain), as.factor))

# Reconstruct the state-owned, non-military, optimal-bandwidth alignment sample
# (mirrors the Non-Military section of the 06 alignment analysis).
data_align <- data %>%
  filter(nato == 0) %>%
  drop_na()

data_align_state_non_mil <- data_align %>%
  filter(state_owned == 1, !topic_clean %in% "Military")

# Residualize the dependent variable for fixed effects to do bandwidth selection
resid_y <- feols(sentiment_clean ~ 1 | topic_clean + source_domain + csto,
                 data = data_align_state_non_mil)$residuals

bw_align_non_mil <- rdbwselect(y = resid_y,
                               x = data_align_state_non_mil$running,
                               kernel = "triangular",
                               cluster = data_align_state_non_mil$source_domain,
                               p = 1,
                               bwselect = "mserd")

optimal_bw_align_non_mil <- bw_align_non_mil$bws[1, 1]

optimal_bandwidth_data_state_non_mil <- data_align_state_non_mil %>%
  filter(running < optimal_bw_align_non_mil, running > -optimal_bw_align_non_mil)
```

# Non-Parametric Saturation Check

```{r nonparam-check}
# Select one CSTO country and one non-CSTO country
csto_country <- "Armenia"  # Replace with actual CSTO country
non_csto_country <- "Kosovo"  # Replace with actual non-CSTO country

two_country_data <- optimal_bandwidth_data_state_non_mil %>%
  filter(country %in% c(csto_country, non_csto_country))

# Check the structure
table(two_country_data$country, two_country_data$csto)

# Step 1: Source-topic level - pre vs post difference
source_topic_effects <- two_country_data %>%
  group_by(source_domain, topic_clean, treatment, csto, country) %>%
  summarize(
    mean_sentiment = mean(sentiment_clean, na.rm = TRUE),
    n_articles = n(),
    .groups = "drop"
  ) %>%
  pivot_wider(
    names_from = treatment,
    values_from = c(mean_sentiment, n_articles)
  ) %>%
  mutate(
    diff = mean_sentiment_1 - mean_sentiment_0,
    total_articles = n_articles_0 + n_articles_1
  )

# Step 2: Source level - weighted average across topics
source_effects <- source_topic_effects %>%
  group_by(source_domain, csto, country) %>%
  summarize(
    source_effect = weighted.mean(diff, w = total_articles, na.rm = TRUE),
    total_articles = sum(total_articles, na.rm = TRUE),
    .groups = "drop"
  )

# Step 3: Country level - weighted average across sources (if multiple sources per country)
country_effects <- source_effects %>%
  group_by(country, csto) %>%
  summarize(
    country_effect = weighted.mean(source_effect, w = total_articles, na.rm = TRUE),
    total_articles = sum(total_articles, na.rm = TRUE),
    .groups = "drop"
  )

# Step 4: CSTO vs non-CSTO difference
csto_effect <- country_effects %>%
  filter(csto == 1) %>%
  pull(country_effect)

non_csto_effect <- country_effects %>%
  filter(csto == 0) %>%
  pull(country_effect)

treatment_effect_csto <- csto_effect - non_csto_effect

print(paste("Non-parametric treatment effect of CSTO:", treatment_effect_csto))

```

```{r nonparam-compare}
# Now run the regression on just these two countries
model_two_countries <- feols(
  sentiment_clean ~ treatment * csto,
  cluster = ~source_domain,
  data = two_country_data
)

model_two_countries_fe <- feols(
  sentiment_clean ~ treatment * csto | topic_clean + source_domain,
  cluster = ~source_domain,
  data = two_country_data
)

model_two_countries_sat <- feols(
  sentiment_clean ~ treatment * csto |
    source_domain^topic_clean + topic_clean^treatment,
  cluster = ~source_domain,
  data = two_country_data
)


# Compare
comparison <- data.frame(
  Method = c("Non-parametric", "Regression", "Regression FE", "Regression Sat."),
  Estimate = c(treatment_effect_csto,
               coef(model_two_countries)["treatment:csto"],
               coef(model_two_countries_fe)["treatment:csto"],
               coef(model_two_countries_sat)["treatment:csto"])
)

print(comparison)
```
