---
title: "01 - Data Loading"
author: "Donald Moratz"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

# Overview

This script loads the raw GPT-coded article data and performs initial inspection.

**Inputs:**
- `data/processed/GPTcoded_final_rus_articles.csv`
- `data/processed/secondhalf_GPTcoded_final_rus_articles.csv`

**Outputs:**
- `data/intermediate/01_raw_data.rds`

```{r setup, include=FALSE}
# Load shared setup
source("00_setup.R")
```

# Load Data

Load the two GPT-coded article datasets.

```{r load-data}
# Load first half of data
data_1 <- read.csv(file.path(DATA_PROCESSED, "GPTcoded_final_rus_articles.csv")) %>%
  dplyr::select(
    date_publish,
    source_domain,
    country,
    title_translated,
    first_two_sentences,
    Russian.Involvement,
    Sentiment,
    Topic
  )

cat("First dataset loaded:", nrow(data_1), "rows\n")

# Load second half of data
data_2 <- read.csv(file.path(DATA_PROCESSED, "secondhalf_GPTcoded_final_rus_articles.csv")) %>%
  dplyr::select(
    date_publish,
    source_domain,
    country,
    title_translated,
    first_two_sentences,
    Russian.Involvement,
    Sentiment,
    Topic
  )

cat("Second dataset loaded:", nrow(data_2), "rows\n")

# Combine datasets
data_raw <- as.data.frame(rbind(data_1, data_2))

cat("\nCombined dataset:", nrow(data_raw), "rows\n")
```

# Initial Inspection

## Dataset Structure

```{r structure}
# View structure
str(data_raw)
```

## Sample Records

```{r sample}
# View first few rows
head(data_raw, 10) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

## Summary Statistics

```{r summary}
# Summary of each column
summary(data_raw)
```

## Unique Values

```{r unique-values}
cat("Unique countries:", n_distinct(data_raw$country), "\n")
cat("Countries:", paste(unique(data_raw$country), collapse = ", "), "\n\n")

cat("Unique sources:", n_distinct(data_raw$source_domain), "\n\n")

cat("Unique sentiments:", paste(unique(data_raw$Sentiment), collapse = ", "), "\n\n")

cat("Unique topics:", paste(unique(data_raw$Topic), collapse = ", "), "\n\n")

cat("Unique Russian involvement:", paste(unique(data_raw$Russian.Involvement), collapse = ", "), "\n")
```

## Date Range

```{r date-range}
# Parse dates for inspection
dates_parsed <- as.Date(data_raw$date_publish)

cat("Date range:",
    as.character(min(dates_parsed, na.rm = TRUE)), "to",
    as.character(max(dates_parsed, na.rm = TRUE)), "\n")

cat("NA dates:", sum(is.na(dates_parsed)), "\n")
```

## Missing Values

```{r missing}
# Check for missing values
missing_summary <- data.frame(
  Column = names(data_raw),
  Missing = colSums(is.na(data_raw)),
  Percent = round(colSums(is.na(data_raw)) / nrow(data_raw) * 100, 2)
)

missing_summary %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

# Data Validation

```{r validation}
validate_data(data_raw, "01 - Raw Data Loading")
```

# Save Output

Save the combined raw data for the next step.

```{r save}
# Save as RDS for efficient loading
saveRDS(data_raw, file.path(DATA_INTERMEDIATE, "01_raw_data.rds"))

cat("Data saved to:", file.path(DATA_INTERMEDIATE, "01_raw_data.rds"), "\n")
cat("File size:", round(file.size(file.path(DATA_INTERMEDIATE, "01_raw_data.rds")) / 1024^2, 2), "MB\n")
```

# Session Info

```{r session-info}
print_session_info()
```
