---
title: "02 - Data Cleaning"
author: "Donald Moratz"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

# Overview

This script cleans the raw data and creates analysis variables.

**Inputs:**
- `data/intermediate/01_raw_data.rds`

**Outputs:**
- `data/intermediate/02_cleaned_data.rds`

```{r setup, include=FALSE}
source("00_setup.R")
```

# Load Raw Data

```{r load}
data <- readRDS(file.path(DATA_INTERMEDIATE, "01_raw_data.rds"))
cat("Loaded", nrow(data), "rows\n")
```

# Date Cleaning

## Parse Dates

```{r clean-dates}
# Create continuous datetime variable
data$date_publish_continuous <- clean_datetime_col(data$date_publish)

# Check for parsing failures
na_dates <- sum(is.na(data$date_publish_continuous))
cat("Dates that failed to parse:", na_dates, "\n")

# Convert to Date type
data$date_publish <- as.Date(data$date_publish)

# Drop rows with NA dates
n_before <- nrow(data)
data <- data %>%
  filter(!is.na(date_publish))
n_after <- nrow(data)

cat("Dropped", n_before - n_after, "rows with missing dates\n")
cat("Remaining rows:", n_after, "\n")
```

## Validate Date Range

```{r validate-dates}
cat("Date range:",
    as.character(min(data$date_publish)), "to",
    as.character(max(data$date_publish)), "\n")

# Check for suspicious dates
suspicious <- data %>%
  filter(date_publish < "2020-01-01" | date_publish > "2024-01-01")

if (nrow(suspicious) > 0) {
  cat("Warning:", nrow(suspicious), "rows with suspicious dates\n")
}
```

# Sentiment Cleaning

## Original Values

```{r sentiment-original}
cat("Original sentiment values:\n")
table(data$Sentiment, useNA = "ifany")
```

## Clean Sentiment

```{r clean-sentiment}
# Drop NA and "nan" sentiments
n_before <- nrow(data)
data <- data %>%
  filter(!Sentiment == "nan") %>%
  filter(!is.na(Sentiment))
n_after <- nrow(data)

cat("Dropped", n_before - n_after, "rows with invalid sentiment\n")

# Create clean sentiment variable (-1, 0, 1)
data$sentiment_clean <- -1
data$sentiment_clean[data$Sentiment == "Positive"] <- 1
data$sentiment_clean[data$Sentiment %in% c("Natural", "Neutral", "neutral")] <- 0

cat("\nCleaned sentiment distribution:\n")
table(data$sentiment_clean)
```

## Validate Sentiment

```{r validate-sentiment}
# Check mapping is complete
unmapped <- data %>%
  filter(is.na(sentiment_clean))

if (nrow(unmapped) > 0) {
  cat("Warning:", nrow(unmapped), "rows with unmapped sentiment\n")
  print(unique(unmapped$Sentiment))
} else {
  cat("All sentiment values successfully mapped\n")
}
```

# Topic Cleaning

## Original Values

```{r topic-original}
cat("Original topic values:\n")
table(data$Topic, useNA = "ifany")
```

## Clean Topics

```{r clean-topics}
# Create clean topic variable (5 categories)
data$topic_clean <- "Other"
data$topic_clean[data$Topic %in% c("Military", "Miliary")] <- "Military"
data$topic_clean[data$Topic %in% c("Politics", "Political", "Policy", "Politic")] <- "Political"
data$topic_clean[data$Topic %in% c("Economic")] <- "Economic"
data$topic_clean[data$Topic %in% c("Cultural", "Culture", "Sports", "Sport")] <- "Culture"

cat("\nCleaned topic distribution:\n")
table(data$topic_clean)
```

# Create Treatment Variables

## Invasion Treatment

```{r treatment}
# Create binary treatment variable (post Feb 24, 2022)
data$treatment <- 0
data$treatment[data$date_publish > "2022-02-23"] <- 1

cat("Treatment distribution:\n")
table(data$treatment)
cat("\nPre-invasion articles:", sum(data$treatment == 0), "\n")
cat("Post-invasion articles:", sum(data$treatment == 1), "\n")
```

## Running Variable

```{r running}
# Create running variable (days from invasion)
data <- data %>%
  mutate(
    running = as.numeric(date_publish - as.Date("2022-02-24")),
    running_continuous = as.numeric(date_publish_continuous - ymd_hms("2022-02-24 00:00:00"))
  )

cat("Running variable range:",
    min(data$running), "to",
    max(data$running), "days\n")
```

# Create Media Ownership Variables

## State-Owned Indicator

```{r state-owned}
# Create state-owned indicator
data$state_owned <- ifelse(data$source_domain %in% STATE_OWNED_SOURCES, 1, 0)

cat("Media ownership distribution:\n")
cat("State-owned:", sum(data$state_owned == 1), "\n")
cat("Independent:", sum(data$state_owned == 0), "\n")
cat("State-owned percentage:", round(mean(data$state_owned) * 100, 1), "%\n")
```

## Interaction Indicator

```{r indicator}
# Create indicator for 4 groups (treatment x state_owned)
data$indicator <- ifelse(data$treatment == 0 & data$state_owned == 0, 1,
                  ifelse(data$treatment == 0 & data$state_owned == 1, 2,
                  ifelse(data$treatment == 1 & data$state_owned == 0, 3, 4)))

cat("Group distribution:\n")
cat("1 (Pre, Independent):", sum(data$indicator == 1), "\n")
cat("2 (Pre, State):", sum(data$indicator == 2), "\n")
cat("3 (Post, Independent):", sum(data$indicator == 3), "\n")
cat("4 (Post, State):", sum(data$indicator == 4), "\n")
```

# Create Country/Alliance Variables

## Alliance Indicators

```{r alliance}
# Create alliance indicators
data$csto <- ifelse(data$country %in% CSTO_COUNTRIES, 1, 0)
data$nato <- ifelse(data$country %in% NATO_COUNTRIES, 1, 0)
data$neutral <- ifelse(data$country %in% NEUTRAL_COUNTRIES, 1, 0)

cat("Alliance distribution:\n")
cat("CSTO countries:", sum(data$csto == 1), "\n")
cat("NATO countries:", sum(data$nato == 1), "\n")
cat("Neutral countries:", sum(data$neutral == 1), "\n")
```

## Ethnic Russian Population

```{r ethnic}
# Create ethnic Russian population indicator
data$high_russia <- ifelse(data$country %in% HIGH_RUSSIAN_POP, 1, 0)

cat("\nEthnic Russian population distribution:\n")
cat("High Russian pop:", sum(data$high_russia == 1), "\n")
cat("Low Russian pop:", sum(data$high_russia == 0), "\n")
```

# Final Validation

## Data Summary

```{r final-summary}
cat("Final dataset summary:\n")
cat("Total rows:", nrow(data), "\n")
cat("Columns:", ncol(data), "\n")
cat("Date range:", as.character(min(data$date_publish)), "to",
    as.character(max(data$date_publish)), "\n")
cat("Countries:", n_distinct(data$country), "\n")
cat("Sources:", n_distinct(data$source_domain), "\n")
```

## Variable Types

```{r types}
# Check variable types
cat("\nVariable types:\n")
sapply(data, class)
```

## Validation Check

```{r validate-final}
validate_data(data, "02 - Cleaned Data")
```

## Create Analysis Subsets

For convenience, create common subsets used in analysis.

```{r subsets}
# Non-Ukraine data (main analysis sample)
data_non_ukraine <- data %>%
  filter(!country %in% c("Ukraine"))

cat("Analysis subsets:\n")
cat("Non-Ukraine sample:", nrow(data_non_ukraine), "rows\n")

# Non-Ukraine, independent media only
data_non_ukraine_ind <- data_non_ukraine %>%
  filter(state_owned == 0)

cat("Non-Ukraine, independent:", nrow(data_non_ukraine_ind), "rows\n")
```

# Save Output

```{r save}
# Save main cleaned dataset
saveRDS(data, file.path(DATA_INTERMEDIATE, "02_cleaned_data.rds"))

# Also save common analysis subsets
saveRDS(data_non_ukraine, file.path(DATA_INTERMEDIATE, "02_data_non_ukraine.rds"))
saveRDS(data_non_ukraine_ind, file.path(DATA_INTERMEDIATE, "02_data_non_ukraine_ind.rds"))

cat("\nData saved:\n")
cat("- 02_cleaned_data.rds:",
    round(file.size(file.path(DATA_INTERMEDIATE, "02_cleaned_data.rds")) / 1024^2, 2), "MB\n")
cat("- 02_data_non_ukraine.rds:",
    round(file.size(file.path(DATA_INTERMEDIATE, "02_data_non_ukraine.rds")) / 1024^2, 2), "MB\n")
cat("- 02_data_non_ukraine_ind.rds:",
    round(file.size(file.path(DATA_INTERMEDIATE, "02_data_non_ukraine_ind.rds")) / 1024^2, 2), "MB\n")
```

# Session Info

```{r session-info}
print_session_info()
```
