---
title: "03 - Descriptive Analysis"
author: "Donald Moratz"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

# Overview

This script produces descriptive statistics, summary tables, and exploratory visualizations.

**Inputs:**
- `data/intermediate/02_cleaned_data.rds`
- `data/intermediate/02_data_non_ukraine.rds`

**Outputs:**
- Summary statistics tables
- Distribution plots
- Time series visualizations

```{r setup, include=FALSE}
source("00_setup.R")
```

# Load Data

```{r load}
data <- readRDS(file.path(DATA_INTERMEDIATE, "02_cleaned_data.rds"))
data_non_ukraine <- readRDS(file.path(DATA_INTERMEDIATE, "02_data_non_ukraine.rds"))

cat("Full data:", nrow(data), "rows\n")
cat("Non-Ukraine data:", nrow(data_non_ukraine), "rows\n")
```

# Summary Statistics Table

## Overall Sample Statistics

```{r summary-stats}
# Create summary stats
sample_summary <- tibble(
  `Total articles` = nrow(data_non_ukraine),
  `Number of countries` = n_distinct(data_non_ukraine$country),
  `Date range` = paste0(
    format(min(data_non_ukraine$date_publish, na.rm = TRUE), "%Y-%m-%d"),
    " to ",
    format(max(data_non_ukraine$date_publish, na.rm = TRUE), "%Y-%m-%d")
  ),
  `Mean sentiment` = round(mean(data_non_ukraine$sentiment_clean, na.rm = TRUE), 3),
  `Sentiment SD` = round(sd(data_non_ukraine$sentiment_clean, na.rm = TRUE), 3),
  `State-owned %` = round(mean(data_non_ukraine$state_owned, na.rm = TRUE) * 100, 1),
  `Independent %` = round(100 - mean(data_non_ukraine$state_owned, na.rm = TRUE) * 100, 1),
  `Number of unique sources` = n_distinct(data_non_ukraine$source_domain),
  `Number of topics` = n_distinct(data_non_ukraine$topic_clean)
) %>%
  mutate(across(everything(), as.character))

summary_statistics_table <- sample_summary %>%
  pivot_longer(everything(), names_to = "Statistic", values_to = "Value") %>%
  gt() %>%
  tab_header(
    title = "Descriptive Overview of News Article Dataset"
  ) %>%
  cols_label(
    Statistic = "Statistic",
    Value = "Value"
  ) %>%
  tab_style(
    style = cell_text(align = "left"),
    locations = cells_body(columns = Statistic)
  )

summary_statistics_table

# Save table
gtsave(summary_statistics_table, file.path(FIGURES_DIR, "summary_statistics_table.html"))
```

# Distribution by Country

```{r country-dist}
country_counts <- data_non_ukraine %>%
  group_by(country) %>%
  summarize(
    n_articles = n(),
    n_state = sum(state_owned),
    n_independent = sum(state_owned == 0),
    pct_state = round(mean(state_owned) * 100, 1),
    mean_sentiment = round(mean(sentiment_clean), 3),
    .groups = "drop"
  ) %>%
  arrange(desc(n_articles))

country_counts %>%
  gt() %>%
  tab_header(title = "Article Distribution by Country") %>%
  cols_label(
    country = "Country",
    n_articles = "Total Articles",
    n_state = "State-Owned",
    n_independent = "Independent",
    pct_state = "% State",
    mean_sentiment = "Mean Sentiment"
  )
```

# Distribution by Topic

## Overall Topic Distribution

```{r topic-dist}
data_topic_counts <- data_non_ukraine %>%
  filter(!is.na(topic_clean)) %>%
  mutate(
    topic_clean = factor(topic_clean, levels = c("Political", "Military", "Economic", "Culture", "Other")),
    period = case_when(
      running < 0 ~ "Before Invasion",
      running > 0 ~ "After Invasion",
      TRUE ~ NA_character_
    )
  ) %>%
  filter(!is.na(period)) %>%
  group_by(topic_clean, period) %>%
  summarize(article_count = n(), .groups = "drop")

topic_all <- ggplot(data_topic_counts, aes(x = topic_clean, y = article_count, fill = period)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(
    title = "Distribution of Articles by Topic",
    subtitle = "Before and After Invasion",
    x = "Topic",
    y = "Number of Articles",
    fill = "Period"
  ) +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "bottom"
  )

topic_all

ggsave(plot = topic_all, file.path(FIGURES_DIR, "topic_distribution.png"),
       width = 8, height = 6)
```

## Topic by Media Type

```{r topic-by-media}
# State media
data_topic_counts_state <- data_non_ukraine %>%
  filter(!is.na(topic_clean), state_owned == 1) %>%
  mutate(
    topic_clean = factor(topic_clean, levels = c("Political", "Military", "Economic", "Culture", "Other")),
    period = case_when(
      running < 0 ~ "Before Invasion",
      running > 0 ~ "After Invasion",
      TRUE ~ NA_character_
    )
  ) %>%
  filter(!is.na(period)) %>%
  group_by(topic_clean, period) %>%
  summarize(article_count = n(), .groups = "drop")

# Independent media
data_topic_counts_ind <- data_non_ukraine %>%
  filter(!is.na(topic_clean), state_owned == 0) %>%
  mutate(
    topic_clean = factor(topic_clean, levels = c("Political", "Military", "Economic", "Culture", "Other")),
    period = case_when(
      running < 0 ~ "Before Invasion",
      running > 0 ~ "After Invasion",
      TRUE ~ NA_character_
    )
  ) %>%
  filter(!is.na(period)) %>%
  group_by(topic_clean, period) %>%
  summarize(article_count = n(), .groups = "drop")

# Create both plots
topic_state <- ggplot(data_topic_counts_state, aes(x = topic_clean, y = article_count, fill = period)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Distribution of Articles by Topic", subtitle = "State Media",
       x = "Topic", y = "Number of Articles", fill = "Period") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

topic_ind <- ggplot(data_topic_counts_ind, aes(x = topic_clean, y = article_count, fill = period)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "", subtitle = "Independent Media",
       x = "Topic", y = "Number of Articles", fill = "Period") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "none")

# Combine plots
topic_split <- (topic_state | topic_ind) + plot_layout(guides = "collect") &
  theme(legend.position = "bottom")

topic_split

ggsave(plot = topic_split, file.path(FIGURES_DIR, "topic_split.png"),
       width = 12, height = 6)
```

# Sentiment by Topic

```{r sentiment-by-topic}
topic_order <- c("Political", "Military", "Economic", "Culture", "Other")

# Summary stats by topic and period
sentiment_topic_stats <- data_non_ukraine %>%
  filter(!is.na(topic_clean), topic_clean %in% topic_order) %>%
  mutate(
    period = case_when(
      running < 0 ~ "Before",
      running > 0 ~ "After",
      TRUE ~ NA_character_
    )
  ) %>%
  filter(!is.na(period)) %>%
  group_by(topic_clean, period) %>%
  summarize(
    mean_sentiment = mean(sentiment_clean, na.rm = TRUE),
    sd_sentiment = sd(sentiment_clean, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    label = paste0(round(mean_sentiment, 3), "\n(", round(sd_sentiment, 3), ")")
  ) %>%
  select(topic_clean, period, label) %>%
  pivot_wider(names_from = period, values_from = label)

# Compute differences and p-values
diff_stats <- data_non_ukraine %>%
  filter(!is.na(topic_clean), topic_clean %in% topic_order) %>%
  mutate(
    period = case_when(
      running < 0 ~ "Before",
      running > 0 ~ "After",
      TRUE ~ NA_character_
    )
  ) %>%
  filter(!is.na(period)) %>%
  group_by(topic_clean) %>%
  group_modify(~ {
    before_vals <- .x$sentiment_clean[.x$period == "Before"]
    after_vals <- .x$sentiment_clean[.x$period == "After"]
    t_result <- t.test(after_vals, before_vals, paired = FALSE)
    tibble(
      diff = mean(after_vals, na.rm = TRUE) - mean(before_vals, na.rm = TRUE),
      p_value = t_result$p.value
    )
  }) %>%
  mutate(
    stars = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01 ~ "**",
      p_value < 0.05 ~ "*",
      TRUE ~ ""
    ),
    Difference = paste0(round(diff, 3), " ", stars)
  ) %>%
  select(topic_clean, Difference)

# Merge and create table
summary_table <- sentiment_topic_stats %>%
  left_join(diff_stats, by = "topic_clean") %>%
  mutate(topic_clean = factor(topic_clean, levels = topic_order)) %>%
  arrange(topic_clean) %>%
  select(topic_clean, Before, After, Difference)

sentiment_by_topic_table <- summary_table %>%
  gt() %>%
  tab_header(
    title = "Sentiment by Topic: Before and After Invasion",
    subtitle = "Mean Sentiment with Standard Deviations and Significance (After - Before)"
  ) %>%
  cols_label(
    topic_clean = "Topic",
    Before = "Before",
    After = "After",
    Difference = "Difference"
  ) %>%
  tab_style(
    style = cell_text(align = "center"),
    locations = cells_body(columns = c(Before, After, Difference))
  )

sentiment_by_topic_table

gtsave(sentiment_by_topic_table, file.path(FIGURES_DIR, "sentiment_by_topic.html"))
```

# Articles Over Time

## Time Series Plot

```{r articles-time}
articles_per_day_by_ownership <- data %>%
  filter(!is.na(date_publish)) %>%
  mutate(
    media_type = ifelse(state_owned == 1, "State-Owned", "Independent")
  ) %>%
  group_by(date = as.Date(date_publish), media_type) %>%
  summarize(article_count = n(), .groups = "drop")

articles_per_day_plot <- ggplot(articles_per_day_by_ownership,
                                 aes(x = date, y = article_count, color = media_type)) +
  geom_line(linewidth = 1) +
  geom_vline(xintercept = as.Date("2022-02-24"), linetype = "dashed",
             color = "black", linewidth = 1) +
  labs(
    title = "Articles Over Time by Media Ownership",
    subtitle = "Black dashed line = Day of Invasion (2022-02-24)",
    x = "Date",
    y = "Number of Articles",
    color = "Media Type"
  ) +
  theme_bw() +
  theme(
    legend.position = "bottom"
  )

articles_per_day_plot

ggsave(plot = articles_per_day_plot, file.path(FIGURES_DIR, "articles_per_day.png"),
       width = 10, height = 6)
```

## Annotated Version

```{r articles-annotated}
highlight_point <- articles_per_day_by_ownership %>%
  filter(date == as.Date("2021-09-20"), media_type == "Independent")

if (nrow(highlight_point) > 0) {
  articles_per_day_plot_annotated <- ggplot(articles_per_day_by_ownership,
                                             aes(x = date, y = article_count, color = media_type)) +
    geom_line(linewidth = 1) +
    geom_vline(xintercept = as.Date("2022-02-24"), linetype = "dashed",
               color = "black", linewidth = 1) +
    annotate(
      "text",
      x = as.Date("2021-09-20"),
      y = highlight_point$article_count + 500,
      label = "Perm State University Shooting\n& Russian Election",
      hjust = 0.5, size = 3.5, color = "black"
    ) +
    geom_curve(
      aes(x = as.Date("2021-09-20"), xend = as.Date("2021-09-20"),
          y = highlight_point$article_count + 300, yend = highlight_point$article_count + 25),
      arrow = arrow(type = "closed", length = unit(0.15, "inches")),
      color = "goldenrod1", curvature = 0, linewidth = 0.75, inherit.aes = FALSE
    ) +
    labs(
      title = "Articles Over Time by Media Ownership",
      subtitle = "Black dashed line = Day of Invasion (2022-02-24)",
      x = "Date", y = "Number of Articles", color = "Media Type"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom")

  articles_per_day_plot_annotated

  ggsave(plot = articles_per_day_plot_annotated,
         file.path(FIGURES_DIR, "articles_per_day_anno.png"),
         width = 10, height = 6)
}
```

# Country-Level Sentiment Change

```{r country-sentiment}
# Compute sentiment change within 2-week window
summarize_stats <- function(df) {
  before <- df %>% filter(running >= -14 & running < 0)
  after <- df %>% filter(running > 0 & running <= 14)

  if (nrow(before) < 2 | nrow(after) < 2) {
    return(tibble(
      mean_before = NA, se_before = NA,
      mean_after = NA, se_after = NA,
      diff = NA, p_value = NA
    ))
  }

  ttest <- t.test(before$sentiment_clean, after$sentiment_clean, paired = FALSE)

  tibble(
    mean_before = mean(before$sentiment_clean, na.rm = TRUE),
    se_before = sd(before$sentiment_clean, na.rm = TRUE) / sqrt(nrow(before)),
    mean_after = mean(after$sentiment_clean, na.rm = TRUE),
    se_after = sd(after$sentiment_clean, na.rm = TRUE) / sqrt(nrow(after)),
    diff = mean(after$sentiment_clean) - mean(before$sentiment_clean),
    p_value = ttest$p.value
  )
}

sentiment_summary <- data %>%
  filter(running >= -14 & running <= 14, state_owned == 1) %>%
  group_by(country) %>%
  group_modify(~summarize_stats(.x)) %>%
  ungroup() %>%
  filter(!is.na(diff))

sentiment_summary <- sentiment_summary %>%
  mutate(
    stars = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01 ~ "**",
      p_value < 0.05 ~ "*",
      is.na(p_value) ~ "",
      TRUE ~ ""
    ),
    diff_label = paste0(round(diff, 3), " ", stars),
    before_label = paste0(round(mean_before, 3), "\n(", round(se_before, 3), ")"),
    after_label = paste0(round(mean_after, 3), "\n(", round(se_after, 3), ")")
  )

country_table <- sentiment_summary %>%
  select(country, before_label, after_label, diff_label) %>%
  gt() %>%
  tab_header(
    title = "Mean Sentiment Before and After Invasion (State Media)",
    subtitle = "With Standard Errors and Significance Stars (2 Week Window)"
  ) %>%
  cols_label(
    country = "Country",
    before_label = "Before",
    after_label = "After",
    diff_label = "Diff (After - Before)"
  ) %>%
  tab_style(
    style = cell_text(align = "center"),
    locations = cells_body()
  )

country_table
```

# Session Info

```{r session-info}
print_session_info()
```
