---
title: "04A_main_rdd_analysis_continuous"
author: "Donald Moratz"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

# Overview

This script performs the main Regression Discontinuity Design (RDD) analysis for Hypothesis 1: The effect of the Russian invasion on media sentiment using time as a continuous variable instead of by day.

**Inputs:**
- `data/intermediate/02_data_non_ukraine.rds`

**Outputs:**
- Main RDD regression results
- Visualizations of the discontinuity
- Table 1

```{r setup, include=FALSE}
source("00_setup.R")
```

# Load Data

```{r load}
# Load non-Ukraine, independent media data (main analysis sample)
data_non_ukraine <- readRDS(file.path(DATA_INTERMEDIATE, "02_data_non_ukraine.rds"))

cat("Analysis sample:", nrow(data_non_ukraine), "articles\n")
cat("Date range:", as.character(min(data_non_ukraine$date_publish)), "to",
    as.character(max(data_non_ukraine$date_publish)), "\n")
```

# Main Linear RDD Models

## Model 1: Basic RDD (Different Slopes)

```{r model1-basic}
model1_basic <- felm(sentiment_clean ~ running_continuous * treatment | 0 | 0 | source_domain,
                     data = data_non_ukraine)

summary(model1_basic)
```

## Model 2: With Country Fixed Effects

```{r model1-country}
model1_country_fe <- felm(sentiment_clean ~ running_continuous * treatment | country | 0 | source_domain,
                          data = data_non_ukraine)

summary(model1_country_fe)
```

## Model 3: With Country and Source Fixed Effects

```{r model1-source}
model1_country_source_fe <- felm(sentiment_clean ~ running_continuous * treatment | country + source_domain | 0 | source_domain,
                                  data = data_non_ukraine)

summary(model1_country_source_fe)
```

## Model 4: Full Model (Country + Source + Topic FE)

```{r model1-full}
model1_full_linear <- felm(sentiment_clean ~ running_continuous * treatment | country + source_domain + topic_clean | 0 | source_domain,
                    data = data_non_ukraine)

summary(model1_full_linear)
```

# Effect Size Calculation

```{r effect-size}
sd_sentiment <- sd(data_non_ukraine$sentiment_clean)

cat("Standard deviation of sentiment:", round(sd_sentiment, 3), "\n\n")

# Mean sentiment before/after
mean_pre <- mean(data_non_ukraine$sentiment_clean[data_non_ukraine$running_continuous < 0], na.rm = TRUE)
mean_post <- mean(data_non_ukraine$sentiment_clean[data_non_ukraine$running_continuous >= 0], na.rm = TRUE)

cat("Mean sentiment (pre-invasion):", round(mean_pre, 3), "\n")
cat("Mean sentiment (post-invasion):", round(mean_post, 3), "\n\n")

# Effect size in SD units
coef_treatment <- summary(model1_full)$coef["treatment", "Estimate"]
effect_size <- coef_treatment / sd_sentiment

cat("Treatment coefficient:", round(coef_treatment, 4), "\n")
cat("Effect size (in SD units):", round(effect_size, 3), "\n")
```

# Main RDD Models

## RD Robust Estimation

```{r rdrobust}
model1_rdrobust <- rdrobust(data_non_ukraine$sentiment_clean,
                            data_non_ukraine$running_continuous)

summary(model1_rdrobust)
```

## Optimal Bandwidth Selection

```{r optimal-bandwidth}
# Select optimal bandwidth
bw_select <- rdbwselect(y = data_non_ukraine$sentiment_clean,
                        x = data_non_ukraine$running_continuous,
                        cluster = data_non_ukraine$source_domain,
                        kernel = "triangular",
                        p = 1,
                        bwselect = "mserd")

summary(bw_select)

# Extract bandwidth
optimal_bw <- bw_select$bws[1, 1]
cat("\nOptimal bandwidth:", round(optimal_bw, 1), "days\n")

# Filter to optimal bandwidth
optimal_bandwidth_data <- data_non_ukraine %>%
  filter(running_continuous < optimal_bw) %>%
  filter(running_continuous > -optimal_bw)

cat("Observations within optimal bandwidth:", nrow(optimal_bandwidth_data), "\n")
```

### Model 1: Basic RDD

```{r model1-optimal}
model1_opt <- felm(sentiment_clean ~ running_continuous * treatment | 0 | 0 | source_domain,
                   data = optimal_bandwidth_data)

summary(model1_opt)
```

### Model 2: With Country Fixed Effects

```{r model1-optimal}
model2_opt <- felm(sentiment_clean ~ running_continuous * treatment | country | 0 | source_domain,
                   data = optimal_bandwidth_data)

summary(model2_opt)
```

### Model 3: With Country and Source Fixed Effects

```{r model1-optimal}
model3_opt <- felm(sentiment_clean ~ running_continuous * treatment | country + source_domain | 0 | source_domain,
                   data = optimal_bandwidth_data)

summary(model3_opt)
```

### Model 4: Full Model (Country + Source + Topic FE)

```{r model1-optimal}
model4_opt <- felm(sentiment_clean ~ running_continuous * treatment | country + source_domain + topic_clean | 0 | source_domain,
                   data = optimal_bandwidth_data)

summary(model4_opt)
```

# Visualizations

## Main RDD Plot

```{r rdd-plot, fig.width=10, fig.height=7}
# Aggregate data for points
agg_data <- data_non_ukraine %>%
  group_by(running_continuous) %>%
  summarize(
    sentiment_clean = mean(sentiment_clean, na.rm = TRUE),
    num_obs = n(),
    .groups = "drop"
  )

invasion_on_sentiment_graph <- data_non_ukraine %>%
  mutate(treatment = as.factor(treatment)) %>%
  ggplot(aes(x = running_continuous, y = sentiment_clean, group = treatment, color = treatment)) +
  geom_point(data = agg_data,
             aes(x = running_continuous, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = c("dodgerblue", "red4"), name = "Post Invasion") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on Sentiment",
    subtitle = "All Sources and Topics",
    x = "Days Pre/Post Invasion",
    y = "Sentiment"
  )

invasion_on_sentiment_graph

ggsave(plot = invasion_on_sentiment_graph,
       file.path(FIGURES_DIR, "invasion_on_sentiment_continuous.png"),
       width = 10, height = 7)
```

## GAM Smoothed Version (Appendix)

```{r rdd-gam, fig.width=10, fig.height=7}
invasion_on_sentiment_graph_smooth <- data_non_ukraine %>%
  mutate(treatment = as.factor(treatment)) %>%
  ggplot(aes(x = running_continuous, y = sentiment_clean, group = treatment, color = treatment)) +
  geom_point(data = agg_data,
             aes(x = running_continuous, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "gam") +
  scale_color_manual(values = c("dodgerblue", "red4"), name = "Post Invasion") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Figure 2 Appendix: Effect of Invasion on Sentiment",
    subtitle = "All Sources and Topics (GAM Smoothed)",
    x = "Days Pre/Post Invasion",
    y = "Sentiment"
  )

invasion_on_sentiment_graph_smooth

ggsave(plot = invasion_on_sentiment_graph,
       file.path(FIGURES_DIR, "invasion_on_sentiment_smooth_continuous.png"),
       width = 10, height = 7)
```

## RD Plot

```{r rd-plot}
rdplot(y = data_non_ukraine$sentiment_clean,
       x = data_non_ukraine$running_continuous,
       title = "RD Plot: Sentiment around Invasion",
       x.label = "Days from Invasion",
       y.label = "Sentiment")
```

# Robustness: Non-Military Topics Only

```{r non-military}
data_non_mil <- data_non_ukraine %>%
  filter(!topic_clean == "Military")

cat("Non-military sample:", nrow(data_non_mil), "articles\n")

model1b <- felm(sentiment_clean ~ running_continuous * treatment | country + source_domain + topic_clean | 0 | source_domain,
                data = data_non_mil)

summary(model1b)
```

## Effect Size (Non-Military)

```{r effect-non-mil}
sd_sentiment_non_mil <- sd(data_non_mil$sentiment_clean)
coef_model1b <- summary(model1b)$coef["treatment", "Estimate"]

cat("Effect size (non-military, in SD units):", round(coef_model1b / sd_sentiment_non_mil, 3), "\n")
```

## Visualization (Non-Military)

```{r plot-non-mil, fig.width=10, fig.height=7}
agg_data_non_mil <- data_non_mil %>%
  group_by(running_continuous) %>%
  summarize(sentiment_clean = mean(sentiment_clean), num_obs = n(), .groups = "drop")

invasion_on_sentiment_non_mil_graph <- data_non_mil_ind %>%
  mutate(treatment = as.factor(treatment)) %>%
  ggplot(aes(x = running_continuous, y = sentiment_clean, group = treatment, color = treatment)) +
  geom_point(data = agg_data_non_mil,
             aes(x = running_continuous, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = c("dodgerblue", "red4"), name = "Post Invasion") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on Sentiment",
    subtitle = "Non-Military Topics",
    x = "Days Pre/Post Invasion",
    y = "Sentiment"
  )

invasion_on_sentiment_non_mil_graph

ggsave(plot = invasion_on_sentiment_non_mil_graph,
       file.path(FIGURES_DIR, "invasion_on_sentiment_non_mil_continuous.png"),
       width = 10, height = 7)
```

# Robustness: Non-NATO Countries Only

```{r non-nato}
data_non_nato <- data_non_ukraine %>%
  filter(!country %in% NATO_COUNTRIES)

model1d <- felm(sentiment_clean ~ running_continuous * treatment | country + source_domain + topic_clean | 0 | source_domain,
                data = data_non_nato)

summary(model1d)
```

# Summary Table (Table 1)

```{r table1}
rows <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6,
  'State FEs', '-', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', 'X', 'X', 'X', 'X',
  'Topic FEs', '-', '-', '-', 'X', 'X', 'X'
)
attr(rows, 'position') <- c(3, 4, 5)

note_text <- "All standard errors are clustered at the source level. Models 1-4 uses the optimal bandwidth. Model 5 uses a linear specification with the full set of articles. Model 6 omits NATO allies."
note_wrapped <- str_wrap(note_text, width = 80)

table_1 <- modelsummary(
  list(model1_opt, model2_opt, model3_opt, model4_opt, model1_full_linear, model1d),
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c("treatment" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors",
  title = "Hypothesis 1: RDD Analysis with Continous Time Running Variable",
  add_rows = rows,
  notes = note_wrapped
)

table_1
```

# Save Results

```{r save-results}
# Save model objects for later use
results_h1_continuous <- list(
  model1_basic = model1_basic,
  model1_country_fe = model1_country_fe,
  model1_country_source_fe = model1_country_source_fe,
  model1_full = model1_full,
  model1_opt = model1_opt,
  model2_opt = model2_opt,
  model3_opt = model3_opt,
  model4_opt = model4_opt,
  model1_non_nato = model1d,
  model1_non_mil = model1b,
  optimal_bandwidth = optimal_bw
)

saveRDS(results_h1_continuous, file.path(DATA_INTERMEDIATE, "04_h1_results_continuous.rds"))
cat("Results saved to:", file.path(DATA_INTERMEDIATE, "04_h1_results_continuous.rds"), "\n")
```

# Session Info

```{r session-info}
print_session_info()
```
