---
title: "04B - Main RDD Analysis with Continuous Running Variable - Drop No-Time Articles (Hypothesis 1)"
author: "Donald Moratz"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

# Overview

This script performs the main Regression Discontinuity Design (RDD) analysis for Hypothesis 1: The effect of the Russian invasion on media sentiment using time as a continuous variable instead of by day. This version drops articles that do not have publication times.

**Inputs:**
- `data/intermediate/02_data_non_ukraine.rds`

**Outputs:**
- Main RDD regression results
- Visualizations of the discontinuity
- Table 1D

```{r setup-drop, include=FALSE}
source("00_setup.R")
knitr::opts_chunk$set(fig.path = paste0(FIGURES_RDD_DROP, "/"))
```

# Load Data

```{r load-drop}
# Load non-Ukraine, independent media data (main analysis sample)
data_non_ukraine <- readRDS(file.path(DATA_INTERMEDIATE, "02_data_non_ukraine.rds"))

cat("Full sample:", nrow(data_non_ukraine), "articles\n")

# Drop articles without publication times
data_non_ukraine <- data_non_ukraine %>% filter(has_time == TRUE)

cat("After dropping no-time articles:", nrow(data_non_ukraine), "articles\n")
cat("Date range:", as.character(min(data_non_ukraine$date_publish)), "to",
    as.character(max(data_non_ukraine$date_publish)), "\n")

# Compute within-source z-score of sentiment
data_non_ukraine <- data_non_ukraine %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                       sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()
```

# Full Data RDD

## Model 1: Basic RDD (Different Slopes)

```{r model1-basic-drop}
model1_basic <- feols(sentiment_clean ~ running_continuous * treatment,
                      cluster = ~source_domain,
                      data = data_non_ukraine)

summary(model1_basic)
```

## Model 2: With Country Fixed Effects

```{r model1-country-drop}
model1_country_fe <- feols(sentiment_clean ~ running_continuous * treatment | country,
                           cluster = ~source_domain,
                           data = data_non_ukraine)

summary(model1_country_fe)
```

## Model 3: With Country and Source Fixed Effects

```{r model1-source-drop}
model1_country_source_fe <- feols(sentiment_clean ~ running_continuous * treatment | country + source_domain,
                                   cluster = ~source_domain,
                                   data = data_non_ukraine)

summary(model1_country_source_fe)
```

## Model 4: Full Model (Country + Source + Topic FE)

```{r model1-full-drop}
model1_full_linear <- feols(sentiment_clean ~ running_continuous * treatment | country + source_domain + topic_clean,
                    cluster = ~source_domain,
                    data = data_non_ukraine)

summary(model1_full_linear)
```

### Linear Effect Size Calculation

```{r effect-size-linear-drop}
sd_sentiment <- sd(data_non_ukraine$sentiment_clean)

cat("Standard deviation of sentiment:", round(sd_sentiment, 3), "\n\n")

# Mean sentiment before/after
mean_pre <- mean(data_non_ukraine$sentiment_clean[data_non_ukraine$running_continuous < 0], na.rm = TRUE)
mean_post <- mean(data_non_ukraine$sentiment_clean[data_non_ukraine$running_continuous >= 0], na.rm = TRUE)

cat("Mean sentiment (pre-invasion):", round(mean_pre, 3), "\n")
cat("Mean sentiment (post-invasion):", round(mean_post, 3), "\n\n")

# Effect size in SD units
coef_treatment <- model1_full_linear$coeftable["treatment","Estimate"]
effect_size <- coef_treatment / sd_sentiment

cat("Treatment coefficient:", round(coef_treatment, 4), "\n")
cat("Effect size (in SD units):", round(effect_size, 3), "\n")
```


## Model 5: Z-Score Model (Topic FE)

```{r model1-z-drop}
model1_z <- feols(sentiment_z ~ running_continuous * treatment | topic_clean,
                    cluster = ~source_domain,
                    data = data_non_ukraine)

summary(model1_z)
```


# Main RDD Models

## RD Robust Estimation

```{r rdrobust-drop}
model1_rdrobust <- rdrobust(data_non_ukraine$sentiment_clean,
                            data_non_ukraine$running_continuous)

summary(model1_rdrobust)
```

## Optimal Bandwidth Selection

```{r optimal-bandwidth-drop}
# Select optimal bandwidth
bw_select <- rdbwselect(y = data_non_ukraine$sentiment_clean,
                        x = data_non_ukraine$running_continuous,
                        cluster = data_non_ukraine$source_domain,
                        kernel = "triangular",
                        p = 1,
                        bwselect = "mserd")

summary(bw_select)

# Extract bandwidth
optimal_bw <- bw_select$bws[1, 1]
cat("\nOptimal bandwidth:", round(optimal_bw, 1), "hours\n")

# Filter to optimal bandwidth, removed since rdrobust does this automatically
optimal_bandwidth_data <- data_non_ukraine

cat("Observations within optimal bandwidth:", nrow(optimal_bandwidth_data), "\n")
```

## Model 1: Basic RDD

```{r model1-optimal-drop}
model1_opt <- rdrobust(
  y = optimal_bandwidth_data$sentiment_clean,
  x = optimal_bandwidth_data$running_continuous,
  cluster = optimal_bandwidth_data$source_domain
)

summary(model1_opt)
```

## Model 2: With Country Fixed Effects

```{r model2-optimal-drop}
# Only country fixed effects as covariates
covs_matrix <- model.matrix(~ country - 1, data = optimal_bandwidth_data)

model2_opt <- rdrobust(
  y = optimal_bandwidth_data$sentiment_clean,
  x = optimal_bandwidth_data$running_continuous,
  covs = covs_matrix,
  cluster = optimal_bandwidth_data$source_domain
)

summary(model2_opt)
```

## Model 3: With Country and Source Fixed Effects

```{r model3-optimal-drop}
# Only country and source domain fixed effects as covariates
covs_matrix <- model.matrix(~ country + source_domain - 1, data = optimal_bandwidth_data)

model3_opt <- rdrobust(
  y = optimal_bandwidth_data$sentiment_clean,
  x = optimal_bandwidth_data$running_continuous,
  covs = covs_matrix,
  cluster = optimal_bandwidth_data$source_domain
)

summary(model3_opt)
```

## Model 4: Full Model (Country + Source + Topic FE)

```{r model4-optimal-drop}
# All covariates
covs_matrix <- model.matrix(~ country + source_domain + topic_clean - 1, data = optimal_bandwidth_data)

model4_opt <- rdrobust(
  y = optimal_bandwidth_data$sentiment_clean,
  x = optimal_bandwidth_data$running_continuous,
  covs = covs_matrix,
  cluster = optimal_bandwidth_data$source_domain
)

summary(model4_opt)
```

### RDRobust Effect Size Calculation

```{r effect-size-rdrobust-drop}
sd_sentiment <- sd(data_non_ukraine$sentiment_clean)

cat("Standard deviation of sentiment:", round(sd_sentiment, 3), "\n\n")

# Mean sentiment before/after
mean_pre <- mean(data_non_ukraine$sentiment_clean[data_non_ukraine$running_continuous < 0], na.rm = TRUE)
mean_post <- mean(data_non_ukraine$sentiment_clean[data_non_ukraine$running_continuous >= 0], na.rm = TRUE)

cat("Mean sentiment (pre-invasion):", round(mean_pre, 3), "\n")
cat("Mean sentiment (post-invasion):", round(mean_post, 3), "\n\n")

# Effect size in SD units
coef_treatment <- model4_opt$coef["Conventional", "Coeff"]
effect_size <- coef_treatment / sd_sentiment

cat("Treatment coefficient:", round(coef_treatment, 4), "\n")
cat("Effect size (in SD units):", round(effect_size, 3), "\n")
```


## Model 5: Z-Score Model (Topic FE)

```{r model5-optimal-drop}
# All covariates
covs_matrix <- model.matrix(~ topic_clean - 1, data = optimal_bandwidth_data)

model5_opt <- rdrobust(
  y = optimal_bandwidth_data$sentiment_z,
  x = optimal_bandwidth_data$running_continuous,
  covs = covs_matrix,
  cluster = optimal_bandwidth_data$source_domain
)

summary(model5_opt)
```

## Non-Mil Models

### Model 6: Non-Military Topics Only

```{r non-military-drop}
data_non_mil <- optimal_bandwidth_data %>%
  filter(topic_clean != "Military")

cat("Non-military sample:", nrow(data_non_mil), "articles\n")

covs_matrix <- model.matrix(~ country + source_domain + topic_clean - 1, data = data_non_mil)

model6_nonmil <- rdrobust(
  y = data_non_mil$sentiment_clean,
  x = data_non_mil$running_continuous,
  covs = covs_matrix,
  cluster = data_non_mil$source_domain
)

summary(model6_nonmil)
```

#### Effect Size (Non-Military)

```{r effect-non-mil-drop}
sd_sentiment_non_mil <- sd(data_non_mil$sentiment_clean)
coef_model6_nonmil <- model6_nonmil$coef["Conventional", "Coeff"]

cat("Effect size (non-military, in SD units):", round(coef_model6_nonmil / sd_sentiment_non_mil, 3), "\n")
```

### Model 6A: Z-Score Model (Topic FE)

```{r model6a-nonmil-drop}
# All covariates
covs_matrix <- model.matrix(~ topic_clean - 1, data = data_non_mil)

model6a_nonmil <- rdrobust(
  y = data_non_mil$sentiment_z,
  x = data_non_mil$running_continuous,
  covs = covs_matrix,
  cluster = data_non_mil$source_domain
)

summary(model6a_nonmil)
```

## Non-Nato Models

### Model 7: Non-NATO Countries, Non-Mil Only

```{r non-nato-drop}
data_non_nato <- data_non_mil %>%
  filter(!country %in% NATO_COUNTRIES)

covs_matrix <- model.matrix(~ country + source_domain + topic_clean - 1, data = data_non_nato)

model7_nonnato <- rdrobust(
  y = data_non_nato$sentiment_clean,
  x = data_non_nato$running_continuous,
  covs = covs_matrix,
  cluster = data_non_nato$source_domain
)

summary(model7_nonnato)
```

### Model 7A: Z-Score Model (Topic FE)

```{r model7a-nonnato-drop}
# All covariates
covs_matrix <- model.matrix(~ topic_clean - 1, data = data_non_nato)

model7a_nonnato <- rdrobust(
  y = data_non_nato$sentiment_z,
  x = data_non_nato$running_continuous,
  covs = covs_matrix,
  cluster = data_non_nato$source_domain
)

summary(model7a_nonnato)
```

# By Topic RDD

## RDD Sentiment Clean Topics

```{r topic-subsets-drop}
# Create by topic data

optimal_bandwidth_data_pol <- optimal_bandwidth_data %>%
  filter(topic_clean == "Political")

optimal_bandwidth_data_mil <- optimal_bandwidth_data %>%
  filter(topic_clean == "Military")

optimal_bandwidth_data_econ <- optimal_bandwidth_data %>%
  filter(topic_clean == "Economic")

optimal_bandwidth_data_cult <- optimal_bandwidth_data %>%
  filter(topic_clean == "Culture")

optimal_bandwidth_data_oth <- optimal_bandwidth_data %>%
  filter(topic_clean == "Other")
```

### Political Model

```{r model4-optimal-pol-drop}
# All covariates
covs_matrix <- model.matrix(~ country + source_domain - 1, data = optimal_bandwidth_data_pol)

model4_opt_pol <- rdrobust(
  y = optimal_bandwidth_data_pol$sentiment_clean,
  x = optimal_bandwidth_data_pol$running_continuous,
  covs = covs_matrix,
  cluster = optimal_bandwidth_data_pol$source_domain
)

summary(model4_opt_pol)
```

### Military Model

```{r model4-optimal-mil-drop}
# All covariates
covs_matrix <- model.matrix(~ country + source_domain - 1, data = optimal_bandwidth_data_mil)

model4_opt_mil <- rdrobust(
  y = optimal_bandwidth_data_mil$sentiment_clean,
  x = optimal_bandwidth_data_mil$running_continuous,
  covs = covs_matrix,
  cluster = optimal_bandwidth_data_mil$source_domain
)

summary(model4_opt_mil)
```

### Economic Model

```{r model4-optimal-econ-drop}
# All covariates
covs_matrix <- model.matrix(~ country + source_domain - 1, data = optimal_bandwidth_data_econ)

model4_opt_econ <- rdrobust(
  y = optimal_bandwidth_data_econ$sentiment_clean,
  x = optimal_bandwidth_data_econ$running_continuous,
  covs = covs_matrix,
  cluster = optimal_bandwidth_data_econ$source_domain
)

summary(model4_opt_econ)
```

### Cultural Model

```{r model4-optimal-cult-drop}
# All covariates
covs_matrix <- model.matrix(~ country + source_domain - 1, data = optimal_bandwidth_data_cult)

model4_opt_cult <- rdrobust(
  y = optimal_bandwidth_data_cult$sentiment_clean,
  x = optimal_bandwidth_data_cult$running_continuous,
  covs = covs_matrix,
  cluster = optimal_bandwidth_data_cult$source_domain
)

summary(model4_opt_cult)
```

### Other Model

```{r model4-optimal-other-drop}
# All covariates
covs_matrix <- model.matrix(~ country + source_domain - 1, data = optimal_bandwidth_data_oth)

model4_opt_oth <- rdrobust(
  y = optimal_bandwidth_data_oth$sentiment_clean,
  x = optimal_bandwidth_data_oth$running_continuous,
  covs = covs_matrix,
  cluster = optimal_bandwidth_data_oth$source_domain
)

summary(model4_opt_oth)
```

## RDD Z-Score Topics

### Political Model

```{r model5-optimal-pol-drop}
covs_matrix <- model.matrix(~ country + source_domain - 1, data = optimal_bandwidth_data_pol)

model5_opt_pol <- rdrobust(
  y = optimal_bandwidth_data_pol$sentiment_z,
  x = optimal_bandwidth_data_pol$running_continuous,
  cluster = optimal_bandwidth_data_pol$source_domain
)

summary(model5_opt_pol)
```

### Military Model

```{r model5-optimal-mil-drop}
covs_matrix <- model.matrix(~ country + source_domain - 1, data = optimal_bandwidth_data_mil)

model5_opt_mil <- rdrobust(
  y = optimal_bandwidth_data_mil$sentiment_z,
  x = optimal_bandwidth_data_mil$running_continuous,
  cluster = optimal_bandwidth_data_mil$source_domain
)

summary(model5_opt_mil)
```

### Economic Model

```{r model5-optimal-econ-drop}
covs_matrix <- model.matrix(~ country + source_domain - 1, data = optimal_bandwidth_data_econ)

model5_opt_econ <- rdrobust(
  y = optimal_bandwidth_data_econ$sentiment_z,
  x = optimal_bandwidth_data_econ$running_continuous,
  cluster = optimal_bandwidth_data_econ$source_domain
)

summary(model5_opt_econ)
```

### Cultural Model

```{r model5-optimal-cult-drop}
covs_matrix <- model.matrix(~ country + source_domain - 1, data = optimal_bandwidth_data_cult)

model5_opt_cult <- rdrobust(
  y = optimal_bandwidth_data_cult$sentiment_z,
  x = optimal_bandwidth_data_cult$running_continuous,
  cluster = optimal_bandwidth_data_cult$source_domain
)

summary(model5_opt_cult)
```

### Other Model

```{r model5-optimal-other-drop}
covs_matrix <- model.matrix(~ country + source_domain - 1, data = optimal_bandwidth_data_oth)

model5_opt_oth <- rdrobust(
  y = optimal_bandwidth_data_oth$sentiment_z,
  x = optimal_bandwidth_data_oth$running_continuous,
  cluster = optimal_bandwidth_data_oth$source_domain
)

summary(model5_opt_oth)
```


# Visualizations

## Main RDD Plot

```{r rdd-plot-cont-drop, fig.width=10, fig.height=7}
# Aggregate data for points
agg_data <- data_non_ukraine %>%
  group_by(running_continuous) %>%
  summarize(
    sentiment_clean = mean(sentiment_clean, na.rm = TRUE),
    num_obs = n(),
    .groups = "drop"
  )

invasion_on_sentiment_graph <- data_non_ukraine %>%
  mutate(treatment = as.factor(treatment)) %>%
  ggplot(aes(x = running_continuous, y = sentiment_clean, group = treatment, color = treatment)) +
  geom_point(data = agg_data,
             aes(x = running_continuous, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = c("dodgerblue", "red4"), name = "Post Invasion") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on Sentiment (Drop No-Time)",
    subtitle = "All Sources and Topics",
    x = "Hours Pre/Post Invasion",
    y = "Sentiment"
  )

invasion_on_sentiment_graph

ggsave(plot = invasion_on_sentiment_graph,
       file.path(FIGURES_RDD_DROP, "invasion_on_sentiment_cont_drop.png"),
       width = 10, height = 7)
```

## GAM Smoothed Version (Appendix)

```{r rdd-gam-cont-drop, fig.width=10, fig.height=7}
invasion_on_sentiment_graph_smooth <- data_non_ukraine %>%
  mutate(treatment = as.factor(treatment)) %>%
  ggplot(aes(x = running_continuous, y = sentiment_clean, group = treatment, color = treatment)) +
  geom_point(data = agg_data,
             aes(x = running_continuous, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "gam") +
  scale_color_manual(values = c("dodgerblue", "red4"), name = "Post Invasion") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Figure 2 Appendix: Effect of Invasion on Sentiment (Drop No-Time)",
    subtitle = "All Sources and Topics (GAM Smoothed)",
    x = "Hours Pre/Post Invasion",
    y = "Sentiment"
  )

invasion_on_sentiment_graph_smooth

ggsave(plot = invasion_on_sentiment_graph_smooth,
       file.path(FIGURES_RDD_DROP, "invasion_on_sentiment_smooth_cont_drop.png"),
       width = 10, height = 7)
```

## RD Plot

```{r rd-plot-cont-drop}
rdplot(y = data_non_ukraine$sentiment_clean,
       x = data_non_ukraine$running_continuous,
       title = "RD Plot: Sentiment around Invasion (Drop No-Time Articles)",
       x.label = "Hours from Invasion",
       y.label = "Sentiment")
```

## RDD Topic Plots

### Political

```{r rdd-plot-pol-cont-drop, fig.width=10, fig.height=7}
# Aggregate data for points
agg_data <- optimal_bandwidth_data_pol %>%
  group_by(running_continuous) %>%
  summarize(
    sentiment_clean = mean(sentiment_clean, na.rm = TRUE),
    num_obs = n(),
    .groups = "drop"
  )

invasion_on_sentiment_graph_pol <- optimal_bandwidth_data_pol %>%
  mutate(treatment = as.factor(treatment)) %>%
  ggplot(aes(x = running_continuous, y = sentiment_clean, group = treatment, color = treatment)) +
  geom_point(data = agg_data,
             aes(x = running_continuous, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = c("dodgerblue", "red4"), name = "Post Invasion") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on Sentiment (Drop No-Time)",
    subtitle = "Political Articles",
    x = "Hours Pre/Post Invasion",
    y = "Sentiment"
  )

invasion_on_sentiment_graph_pol

ggsave(plot = invasion_on_sentiment_graph_pol,
       file.path(FIGURES_RDD_DROP, "invasion_on_sentiment_pol_cont_drop.png"),
       width = 10, height = 7)
```

### Military

```{r rdd-plot-mil-cont-drop, fig.width=10, fig.height=7}
# Aggregate data for points
agg_data <- optimal_bandwidth_data_mil %>%
  group_by(running_continuous) %>%
  summarize(
    sentiment_clean = mean(sentiment_clean, na.rm = TRUE),
    num_obs = n(),
    .groups = "drop"
  )

invasion_on_sentiment_graph_mil <- optimal_bandwidth_data_mil %>%
  mutate(treatment = as.factor(treatment)) %>%
  ggplot(aes(x = running_continuous, y = sentiment_clean, group = treatment, color = treatment)) +
  geom_point(data = agg_data,
             aes(x = running_continuous, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = c("dodgerblue", "red4"), name = "Post Invasion") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on Sentiment (Drop No-Time)",
    subtitle = "Military Articles",
    x = "Hours Pre/Post Invasion",
    y = "Sentiment"
  )

invasion_on_sentiment_graph_mil

ggsave(plot = invasion_on_sentiment_graph_mil,
       file.path(FIGURES_RDD_DROP, "invasion_on_sentiment_mil_cont_drop.png"),
       width = 10, height = 7)
```

### Economic

```{r rdd-plot-econ-cont-drop, fig.width=10, fig.height=7}
# Aggregate data for points
agg_data <- optimal_bandwidth_data_econ %>%
  group_by(running_continuous) %>%
  summarize(
    sentiment_clean = mean(sentiment_clean, na.rm = TRUE),
    num_obs = n(),
    .groups = "drop"
  )

invasion_on_sentiment_graph_econ <- optimal_bandwidth_data_econ %>%
  mutate(treatment = as.factor(treatment)) %>%
  ggplot(aes(x = running_continuous, y = sentiment_clean, group = treatment, color = treatment)) +
  geom_point(data = agg_data,
             aes(x = running_continuous, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = c("dodgerblue", "red4"), name = "Post Invasion") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on Sentiment (Drop No-Time)",
    subtitle = "Economic Articles",
    x = "Hours Pre/Post Invasion",
    y = "Sentiment"
  )

invasion_on_sentiment_graph_econ

ggsave(plot = invasion_on_sentiment_graph_econ,
       file.path(FIGURES_RDD_DROP, "invasion_on_sentiment_econ_cont_drop.png"),
       width = 10, height = 7)
```

### Cultural

```{r rdd-plot-cult-cont-drop, fig.width=10, fig.height=7}
# Aggregate data for points
agg_data <- optimal_bandwidth_data_cult %>%
  group_by(running_continuous) %>%
  summarize(
    sentiment_clean = mean(sentiment_clean, na.rm = TRUE),
    num_obs = n(),
    .groups = "drop"
  )

invasion_on_sentiment_graph_cult <- optimal_bandwidth_data_cult %>%
  mutate(treatment = as.factor(treatment)) %>%
  ggplot(aes(x = running_continuous, y = sentiment_clean, group = treatment, color = treatment)) +
  geom_point(data = agg_data,
             aes(x = running_continuous, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = c("dodgerblue", "red4"), name = "Post Invasion") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on Sentiment (Drop No-Time)",
    subtitle = "Cultural Articles",
    x = "Hours Pre/Post Invasion",
    y = "Sentiment"
  )

invasion_on_sentiment_graph_cult

ggsave(plot = invasion_on_sentiment_graph_cult,
       file.path(FIGURES_RDD_DROP, "invasion_on_sentiment_cult_cont_drop.png"),
       width = 10, height = 7)
```

### Other

```{r rdd-plot-oth-cont-drop, fig.width=10, fig.height=7}
# Aggregate data for points
agg_data <- optimal_bandwidth_data_oth %>%
  group_by(running_continuous) %>%
  summarize(
    sentiment_clean = mean(sentiment_clean, na.rm = TRUE),
    num_obs = n(),
    .groups = "drop"
  )

invasion_on_sentiment_graph_oth <- optimal_bandwidth_data_oth %>%
  mutate(treatment = as.factor(treatment)) %>%
  ggplot(aes(x = running_continuous, y = sentiment_clean, group = treatment, color = treatment)) +
  geom_point(data = agg_data,
             aes(x = running_continuous, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = c("dodgerblue", "red4"), name = "Post Invasion") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on Sentiment (Drop No-Time)",
    subtitle = "Other Articles",
    x = "Hours Pre/Post Invasion",
    y = "Sentiment"
  )

invasion_on_sentiment_graph_oth

ggsave(plot = invasion_on_sentiment_graph_oth,
       file.path(FIGURES_RDD_DROP, "invasion_on_sentiment_oth_cont_drop.png"),
       width = 10, height = 7)
```

## Visualization (Non-Military)

```{r plot-non-mil-cont-drop, fig.width=10, fig.height=7}
agg_data_non_mil <- data_non_mil %>%
  group_by(running_continuous) %>%
  summarize(sentiment_clean = mean(sentiment_clean), num_obs = n(), .groups = "drop")

invasion_on_sentiment_non_mil_graph <- data_non_mil %>%
  mutate(treatment = as.factor(treatment)) %>%
  ggplot(aes(x = running_continuous, y = sentiment_clean, group = treatment, color = treatment)) +
  geom_point(data = agg_data_non_mil,
             aes(x = running_continuous, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = c("dodgerblue", "red4"), name = "Post Invasion") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on Sentiment (Drop No-Time)",
    subtitle = "Non-Military Topics",
    x = "Hours Pre/Post Invasion",
    y = "Sentiment"
  )

invasion_on_sentiment_non_mil_graph

ggsave(plot = invasion_on_sentiment_non_mil_graph,
       file.path(FIGURES_RDD_DROP, "invasion_on_sentiment_non_mil_cont_drop.png"),
       width = 10, height = 7)
```


# Placebo Test: December 7th Announcement

## FE Model, Non Mil

```{r placebo-dec-drop}
data_dec <- data_non_ukraine %>%
  filter(date_publish < "2022-02-19") %>%
  mutate(
    running_continuous = as.numeric(difftime(date_publish_continuous, as.POSIXct("2021-12-07 00:00:00", tz = "UTC"), units = "secs")),
    treatment = ifelse(date_publish_continuous < as.POSIXct("2021-12-07 00:00:00", tz = "UTC"), 0, 1)
  ) %>%
  filter(topic_clean != "Military")

# Full model specification using rdrobust (matches model4_opt)
covs_matrix_dec <- model.matrix(~ country + source_domain + topic_clean - 1,
                                data = data_dec)

model_placebo <- rdrobust(
  y = data_dec$sentiment_clean,
  x = data_dec$running_continuous,
  covs = covs_matrix_dec,
  cluster = data_dec$source_domain
)

summary(model_placebo)
cat("\nNote: Non-significant treatment effect suggests parallel trends assumption holds.\n")
```

## Z-Score Model

```{r placebo-dec-z-drop}
data_dec <- data_non_ukraine %>%
  filter(date_publish < "2022-02-19") %>%
  mutate(
    running_continuous = as.numeric(difftime(date_publish_continuous, as.POSIXct("2021-12-07 00:00:00", tz = "UTC"), units = "secs")),
    treatment = ifelse(date_publish_continuous < as.POSIXct("2021-12-07 00:00:00", tz = "UTC"), 0, 1)
  )

# Full model specification using rdrobust (matches model5_opt)
covs_matrix_dec <- model.matrix(~ topic_clean - 1,
                                data = data_dec)

model_placebo_z <- rdrobust(
  y = data_dec$sentiment_z,
  x = data_dec$running_continuous,
  covs = covs_matrix_dec,
  cluster = data_dec$source_domain
)

summary(model_placebo_z)
cat("\nNote: Non-significant treatment effect suggests parallel trends assumption holds.\n")
```


# Robustness: Heavily Saturated Full Model with Re-Optimized Bandwidth

## Using FELM

```{r saturated-model-drop}
optimal_bw <- model4_opt$bws[1, 1]

# Using optimal bandwidth from model4_opt
optimal_bandwidth_data_filtered <- optimal_bandwidth_data %>%
  filter(abs(running_continuous) <= optimal_bw) %>%
  mutate(post = ifelse(running_continuous >= 0, 1, 0))

# Fully saturated feols RDD model
model4_felm_saturated <- feols(
  sentiment_clean ~ post + running_continuous + running_continuous:post |
    source_domain^topic_clean,
  cluster = ~source_domain,
  data = optimal_bandwidth_data_filtered
)

summary(model4_felm_saturated)
```


# Summary Table (Table 1D)

```{r table1d-drop}
rows <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7,
  'Topic FEs', '-', '-', '-', 'X', 'X', 'X', 'X',
  'State FEs', '-', 'X', 'X', 'X', '-', '-', '-',
  'Source FEs', '-', '-', 'X', 'X', '-', '-', '-',
  'Source Z-Score', '-', '-', '-', '-', 'X', 'X', 'X'
)
attr(rows, 'position') <- c(3, 4, 5, 6)

note_text <- "All standard errors are clustered at the source level. Models 1-4 uses the optimal bandwidth. Models 5-7 uses a Z-Score adjustment instead of fixed effects. Model 6 omits Military Topics. Model 7 omits NATO allies. This version drops articles without recorded publication times."
note_wrapped <- str_wrap(note_text, width = 80)

table_1d <- modelsummary(
  list(model1_opt, model2_opt, model3_opt, model4_opt, model5_opt, model6a_nonmil, model7a_nonnato),
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c("treatment" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors",
  title = "Hypothesis 1: RDD Analysis with Continuous Time Running Variable (Drop No-Time)",
  add_rows = rows,
  notes = note_wrapped
)

table_1d
```

# Save Results

```{r save-results-drop}
# Save model objects for later use
results_h1_drop <- list(
  model1_basic = model1_basic,
  model1_country_fe = model1_country_fe,
  model1_country_source_fe = model1_country_source_fe,
  model1_full_linear = model1_full_linear,
  model1_z = model1_z,
  model1_opt = model1_opt,
  model2_opt = model2_opt,
  model3_opt = model3_opt,
  model4_opt = model4_opt,
  model5_opt = model5_opt,
  model7_non_nato = model7_nonnato,
  model7a_nonnato = model7a_nonnato,
  model6_non_mil = model6_nonmil,
  model6a_nonmil = model6a_nonmil,
  model4_felm_saturated = model4_felm_saturated,
  model4_opt_pol = model4_opt_pol,
  model4_opt_mil = model4_opt_mil,
  model4_opt_econ = model4_opt_econ,
  model4_opt_cult = model4_opt_cult,
  model4_opt_oth = model4_opt_oth,
  model5_opt_pol = model5_opt_pol,
  model5_opt_mil = model5_opt_mil,
  model5_opt_econ = model5_opt_econ,
  model5_opt_cult = model5_opt_cult,
  model5_opt_oth = model5_opt_oth,
  optimal_bandwidth = optimal_bw,
  model_placebo = model_placebo,
  model_placebo_z = model_placebo_z
)

saveRDS(results_h1_drop, file.path(DATA_INTERMEDIATE, "04_h1_results_drop.rds"))
cat("Results saved to:", file.path(DATA_INTERMEDIATE, "04_h1_results_drop.rds"), "\n")
```

# Session Info

```{r session-info-drop}
print_session_info()
```
