---
title: "04C - Main RDD Analysis with Probabilistic Time Assignment (Hypothesis 1)"
author: "Donald Moratz"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

# Overview

This script performs the main Regression Discontinuity Design (RDD) analysis for Hypothesis 1: The effect of the Russian invasion on media sentiment using probabilistic time assignment for articles missing publication times.

**Inputs:**
- `data/intermediate/02_data_non_ukraine.rds`

**Outputs:**
- Main RDD regression results
- Visualizations of the discontinuity
- Table 1F

```{r setup-prob, include=FALSE}
source("00_setup.R")
```

# Load Data

```{r load-prob}
# Load non-Ukraine, independent media data (main analysis sample)
data_non_ukraine <- readRDS(file.path(DATA_INTERMEDIATE, "02_data_non_ukraine.rds"))

cat("Analysis sample:", nrow(data_non_ukraine), "articles\n")
cat("Date range:", as.character(min(data_non_ukraine$date_publish)), "to",
    as.character(max(data_non_ukraine$date_publish)), "\n")
```

# Main Linear RDD Models

## Model 1: Basic RDD (Different Slopes)

```{r model1-basic-prob}
model1_basic <- felm(sentiment_clean ~ running_probabilistic * treatment | 0 | 0 | source_domain,
                     data = data_non_ukraine)

summary(model1_basic)
```

## Model 2: With Country Fixed Effects

```{r model1-country-prob}
model1_country_fe <- felm(sentiment_clean ~ running_probabilistic * treatment | country | 0 | source_domain,
                          data = data_non_ukraine)

summary(model1_country_fe)
```

## Model 3: With Country and Source Fixed Effects

```{r model1-source-prob}
model1_country_source_fe <- felm(sentiment_clean ~ running_probabilistic * treatment | country + source_domain | 0 | source_domain,
                                  data = data_non_ukraine)

summary(model1_country_source_fe)
```

## Model 4: Full Model (Country + Source + Topic FE)

```{r model1-full-prob}
model1_full_linear <- felm(sentiment_clean ~ running_probabilistic * treatment | country + source_domain + topic_clean | 0 | source_domain,
                    data = data_non_ukraine)

summary(model1_full_linear)
```

# Linear Effect Size Calculation

```{r effect-size-linear-prob}
sd_sentiment <- sd(data_non_ukraine$sentiment_clean)

cat("Standard deviation of sentiment:", round(sd_sentiment, 3), "\n\n")

# Mean sentiment before/after
mean_pre <- mean(data_non_ukraine$sentiment_clean[data_non_ukraine$running_probabilistic < 0], na.rm = TRUE)
mean_post <- mean(data_non_ukraine$sentiment_clean[data_non_ukraine$running_probabilistic >= 0], na.rm = TRUE)

cat("Mean sentiment (pre-invasion):", round(mean_pre, 3), "\n")
cat("Mean sentiment (post-invasion):", round(mean_post, 3), "\n\n")

# Effect size in SD units
coef_treatment <- summary(model1_full_linear)$coef["treatment", "Estimate"]
effect_size <- coef_treatment / sd_sentiment

cat("Treatment coefficient:", round(coef_treatment, 4), "\n")
cat("Effect size (in SD units):", round(effect_size, 3), "\n")
```

# Main RDD Models

## RD Robust Estimation

```{r rdrobust-prob}
model1_rdrobust <- rdrobust(data_non_ukraine$sentiment_clean,
                            data_non_ukraine$running_probabilistic)

summary(model1_rdrobust)
```

## Optimal Bandwidth Selection

```{r optimal-bandwidth-prob}
# Select optimal bandwidth
bw_select <- rdbwselect(y = data_non_ukraine$sentiment_clean,
                        x = data_non_ukraine$running_probabilistic,
                        cluster = data_non_ukraine$source_domain,
                        kernel = "triangular",
                        p = 1,
                        bwselect = "mserd")

summary(bw_select)

# Extract bandwidth
optimal_bw <- bw_select$bws[1, 1]
cat("\nOptimal bandwidth:", round(optimal_bw, 1), "hours\n")

# rdrobust handles bandwidth internally
optimal_bandwidth_data <- data_non_ukraine

cat("Total observations:", nrow(optimal_bandwidth_data), "\n")
```

### Model 1: Basic RDD

```{r model1-optimal-prob}
model1_opt <- rdrobust(
  y = optimal_bandwidth_data$sentiment_clean,
  x = optimal_bandwidth_data$running_probabilistic,
  cluster = optimal_bandwidth_data$source_domain
)

summary(model1_opt)
```

### Model 2: With Country Fixed Effects

```{r model2-optimal-prob}
# Only country fixed effects as covariates
covs_matrix <- model.matrix(~ country - 1, data = optimal_bandwidth_data)

model2_opt <- rdrobust(
  y = optimal_bandwidth_data$sentiment_clean,
  x = optimal_bandwidth_data$running_probabilistic,
  covs = covs_matrix,
  cluster = optimal_bandwidth_data$source_domain
)

summary(model2_opt)
```

### Model 3: With Country and Source Fixed Effects

```{r model3-optimal-prob}
# Only country and source domain fixed effects as covariates
covs_matrix <- model.matrix(~ country + source_domain - 1, data = optimal_bandwidth_data)

model3_opt <- rdrobust(
  y = optimal_bandwidth_data$sentiment_clean,
  x = optimal_bandwidth_data$running_probabilistic,
  covs = covs_matrix,
  cluster = optimal_bandwidth_data$source_domain
)

summary(model3_opt)
```

### Model 4: Full Model (Country + Source + Topic FE)

```{r model4-optimal-prob}
# All covariates
covs_matrix <- model.matrix(~ country + source_domain + topic_clean - 1, data = optimal_bandwidth_data)

model4_opt <- rdrobust(
  y = optimal_bandwidth_data$sentiment_clean,
  x = optimal_bandwidth_data$running_probabilistic,
  covs = covs_matrix,
  cluster = optimal_bandwidth_data$source_domain
)

summary(model4_opt)
```

# RDRobust Effect Size Calculation

```{r effect-size-rdrobust-prob}
sd_sentiment <- sd(data_non_ukraine$sentiment_clean)

cat("Standard deviation of sentiment:", round(sd_sentiment, 3), "\n\n")

# Mean sentiment before/after
mean_pre <- mean(data_non_ukraine$sentiment_clean[data_non_ukraine$running_probabilistic < 0], na.rm = TRUE)
mean_post <- mean(data_non_ukraine$sentiment_clean[data_non_ukraine$running_probabilistic >= 0], na.rm = TRUE)

cat("Mean sentiment (pre-invasion):", round(mean_pre, 3), "\n")
cat("Mean sentiment (post-invasion):", round(mean_post, 3), "\n\n")

# Effect size in SD units
coef_treatment <- model4_opt$coef[1]
effect_size <- coef_treatment / sd_sentiment

cat("Treatment coefficient:", round(coef_treatment, 4), "\n")
cat("Effect size (in SD units):", round(effect_size, 3), "\n")
```

# RDD Models By Topic

```{r topic-subsets-prob}
# Create by topic data
optimal_bandwidth_data_pol <- optimal_bandwidth_data %>%
  filter(topic_clean == "Political")

optimal_bandwidth_data_mil <- optimal_bandwidth_data %>%
  filter(topic_clean == "Military")

optimal_bandwidth_data_econ <- optimal_bandwidth_data %>%
  filter(topic_clean == "Economic")

optimal_bandwidth_data_cult <- optimal_bandwidth_data %>%
  filter(topic_clean == "Culture")

optimal_bandwidth_data_oth <- optimal_bandwidth_data %>%
  filter(topic_clean == "Other")
```

## Political Model

```{r model4-optimal-pol-prob}
covs_matrix <- model.matrix(~ country + source_domain - 1, data = optimal_bandwidth_data_pol)

model4_opt_pol <- rdrobust(
  y = optimal_bandwidth_data_pol$sentiment_clean,
  x = optimal_bandwidth_data_pol$running_probabilistic,
  covs = covs_matrix,
  cluster = optimal_bandwidth_data_pol$source_domain
)

summary(model4_opt_pol)
```

## Military Model

```{r model4-optimal-mil-prob}
covs_matrix <- model.matrix(~ country + source_domain - 1, data = optimal_bandwidth_data_mil)

model4_opt_mil <- rdrobust(
  y = optimal_bandwidth_data_mil$sentiment_clean,
  x = optimal_bandwidth_data_mil$running_probabilistic,
  covs = covs_matrix,
  cluster = optimal_bandwidth_data_mil$source_domain
)

summary(model4_opt_mil)
```

## Economic Model

```{r model4-optimal-econ-prob}
covs_matrix <- model.matrix(~ country + source_domain - 1, data = optimal_bandwidth_data_econ)

model4_opt_econ <- rdrobust(
  y = optimal_bandwidth_data_econ$sentiment_clean,
  x = optimal_bandwidth_data_econ$running_probabilistic,
  covs = covs_matrix,
  cluster = optimal_bandwidth_data_econ$source_domain
)

summary(model4_opt_econ)
```

## Cultural Model

```{r model4-optimal-cult-prob}
covs_matrix <- model.matrix(~ country + source_domain - 1, data = optimal_bandwidth_data_cult)

model4_opt_cult <- rdrobust(
  y = optimal_bandwidth_data_cult$sentiment_clean,
  x = optimal_bandwidth_data_cult$running_probabilistic,
  covs = covs_matrix,
  cluster = optimal_bandwidth_data_cult$source_domain
)

summary(model4_opt_cult)
```

## Other Model

```{r model4-optimal-other-prob}
covs_matrix <- model.matrix(~ country + source_domain - 1, data = optimal_bandwidth_data_oth)

model4_opt_oth <- rdrobust(
  y = optimal_bandwidth_data_oth$sentiment_clean,
  x = optimal_bandwidth_data_oth$running_probabilistic,
  covs = covs_matrix,
  cluster = optimal_bandwidth_data_oth$source_domain
)

summary(model4_opt_oth)
```

# Visualizations

## Main RDD Plot

```{r rdd-plot-cont-prob, fig.width=10, fig.height=7}
# Aggregate data for points
agg_data <- data_non_ukraine %>%
  group_by(running_probabilistic) %>%
  summarize(
    sentiment_clean = mean(sentiment_clean, na.rm = TRUE),
    num_obs = n(),
    .groups = "drop"
  )

invasion_on_sentiment_graph <- data_non_ukraine %>%
  mutate(treatment = as.factor(treatment)) %>%
  ggplot(aes(x = running_probabilistic, y = sentiment_clean, group = treatment, color = treatment)) +
  geom_point(data = agg_data,
             aes(x = running_probabilistic, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = c("dodgerblue", "red4"), name = "Post Invasion") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on Sentiment (Probabilistic Time Assignment)",
    subtitle = "All Sources and Topics",
    x = "Hours Pre/Post Invasion",
    y = "Sentiment"
  )

invasion_on_sentiment_graph

ggsave(plot = invasion_on_sentiment_graph,
       file.path(FIGURES_RDD, "invasion_on_sentiment_cont_prob.png"),
       width = 10, height = 7)
```

## GAM Smoothed Version (Appendix)

```{r rdd-gam-cont-prob, fig.width=10, fig.height=7}
invasion_on_sentiment_graph_smooth <- data_non_ukraine %>%
  mutate(treatment = as.factor(treatment)) %>%
  ggplot(aes(x = running_probabilistic, y = sentiment_clean, group = treatment, color = treatment)) +
  geom_point(data = agg_data,
             aes(x = running_probabilistic, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "gam") +
  scale_color_manual(values = c("dodgerblue", "red4"), name = "Post Invasion") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Figure 2 Appendix: Effect of Invasion on Sentiment (Probabilistic Time Assignment)",
    subtitle = "All Sources and Topics (GAM Smoothed)",
    x = "Hours Pre/Post Invasion",
    y = "Sentiment"
  )

invasion_on_sentiment_graph_smooth

ggsave(plot = invasion_on_sentiment_graph_smooth,
       file.path(FIGURES_RDD, "invasion_on_sentiment_smooth_cont_prob.png"),
       width = 10, height = 7)
```

## RD Plot

```{r rd-plot-cont-prob}
rdplot(y = data_non_ukraine$sentiment_clean,
       x = data_non_ukraine$running_probabilistic,
       title = "RD Plot: Sentiment around Invasion (Probabilistic Time Assignment)",
       x.label = "Hours from Invasion",
       y.label = "Sentiment")
```

## RDD Topic Plots

### Political

```{r rdd-plot-pol-cont-prob, fig.width=10, fig.height=7}
agg_data <- optimal_bandwidth_data_pol %>%
  group_by(running_probabilistic) %>%
  summarize(
    sentiment_clean = mean(sentiment_clean, na.rm = TRUE),
    num_obs = n(),
    .groups = "drop"
  )

invasion_on_sentiment_graph_pol <- optimal_bandwidth_data_pol %>%
  mutate(treatment = as.factor(treatment)) %>%
  ggplot(aes(x = running_probabilistic, y = sentiment_clean, group = treatment, color = treatment)) +
  geom_point(data = agg_data,
             aes(x = running_probabilistic, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = c("dodgerblue", "red4"), name = "Post Invasion") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on Sentiment (Probabilistic Time Assignment)",
    subtitle = "Political Articles",
    x = "Hours Pre/Post Invasion",
    y = "Sentiment"
  )

invasion_on_sentiment_graph_pol

ggsave(plot = invasion_on_sentiment_graph_pol,
       file.path(FIGURES_RDD, "invasion_on_sentiment_pol_cont_prob.png"),
       width = 10, height = 7)
```

### Military

```{r rdd-plot-mil-cont-prob, fig.width=10, fig.height=7}
agg_data <- optimal_bandwidth_data_mil %>%
  group_by(running_probabilistic) %>%
  summarize(
    sentiment_clean = mean(sentiment_clean, na.rm = TRUE),
    num_obs = n(),
    .groups = "drop"
  )

invasion_on_sentiment_graph_mil <- optimal_bandwidth_data_mil %>%
  mutate(treatment = as.factor(treatment)) %>%
  ggplot(aes(x = running_probabilistic, y = sentiment_clean, group = treatment, color = treatment)) +
  geom_point(data = agg_data,
             aes(x = running_probabilistic, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = c("dodgerblue", "red4"), name = "Post Invasion") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on Sentiment (Probabilistic Time Assignment)",
    subtitle = "Military Articles",
    x = "Hours Pre/Post Invasion",
    y = "Sentiment"
  )

invasion_on_sentiment_graph_mil

ggsave(plot = invasion_on_sentiment_graph_mil,
       file.path(FIGURES_RDD, "invasion_on_sentiment_mil_cont_prob.png"),
       width = 10, height = 7)
```

### Economic

```{r rdd-plot-econ-cont-prob, fig.width=10, fig.height=7}
agg_data <- optimal_bandwidth_data_econ %>%
  group_by(running_probabilistic) %>%
  summarize(
    sentiment_clean = mean(sentiment_clean, na.rm = TRUE),
    num_obs = n(),
    .groups = "drop"
  )

invasion_on_sentiment_graph_econ <- optimal_bandwidth_data_econ %>%
  mutate(treatment = as.factor(treatment)) %>%
  ggplot(aes(x = running_probabilistic, y = sentiment_clean, group = treatment, color = treatment)) +
  geom_point(data = agg_data,
             aes(x = running_probabilistic, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = c("dodgerblue", "red4"), name = "Post Invasion") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on Sentiment (Probabilistic Time Assignment)",
    subtitle = "Economic Articles",
    x = "Hours Pre/Post Invasion",
    y = "Sentiment"
  )

invasion_on_sentiment_graph_econ

ggsave(plot = invasion_on_sentiment_graph_econ,
       file.path(FIGURES_RDD, "invasion_on_sentiment_econ_cont_prob.png"),
       width = 10, height = 7)
```

### Cultural

```{r rdd-plot-cult-cont-prob, fig.width=10, fig.height=7}
agg_data <- optimal_bandwidth_data_cult %>%
  group_by(running_probabilistic) %>%
  summarize(
    sentiment_clean = mean(sentiment_clean, na.rm = TRUE),
    num_obs = n(),
    .groups = "drop"
  )

invasion_on_sentiment_graph_cult <- optimal_bandwidth_data_cult %>%
  mutate(treatment = as.factor(treatment)) %>%
  ggplot(aes(x = running_probabilistic, y = sentiment_clean, group = treatment, color = treatment)) +
  geom_point(data = agg_data,
             aes(x = running_probabilistic, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = c("dodgerblue", "red4"), name = "Post Invasion") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on Sentiment (Probabilistic Time Assignment)",
    subtitle = "Cultural Articles",
    x = "Hours Pre/Post Invasion",
    y = "Sentiment"
  )

invasion_on_sentiment_graph_cult

ggsave(plot = invasion_on_sentiment_graph_cult,
       file.path(FIGURES_RDD, "invasion_on_sentiment_cult_cont_prob.png"),
       width = 10, height = 7)
```

### Other

```{r rdd-plot-oth-cont-prob, fig.width=10, fig.height=7}
agg_data <- optimal_bandwidth_data_oth %>%
  group_by(running_probabilistic) %>%
  summarize(
    sentiment_clean = mean(sentiment_clean, na.rm = TRUE),
    num_obs = n(),
    .groups = "drop"
  )

invasion_on_sentiment_graph_oth <- optimal_bandwidth_data_oth %>%
  mutate(treatment = as.factor(treatment)) %>%
  ggplot(aes(x = running_probabilistic, y = sentiment_clean, group = treatment, color = treatment)) +
  geom_point(data = agg_data,
             aes(x = running_probabilistic, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = c("dodgerblue", "red4"), name = "Post Invasion") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on Sentiment (Probabilistic Time Assignment)",
    subtitle = "Other Articles",
    x = "Hours Pre/Post Invasion",
    y = "Sentiment"
  )

invasion_on_sentiment_graph_oth

ggsave(plot = invasion_on_sentiment_graph_oth,
       file.path(FIGURES_RDD, "invasion_on_sentiment_oth_cont_prob.png"),
       width = 10, height = 7)
```

# Robustness: Non-Military Topics Only

```{r non-military-prob}
data_non_mil <- optimal_bandwidth_data %>%
  filter(!topic_clean == "Military")

cat("Non-military sample:", nrow(data_non_mil), "articles\n")

covs_matrix <- model.matrix(~ country + source_domain + topic_clean - 1, data = data_non_mil)

model4_opt_nonmil <- rdrobust(
  y = data_non_mil$sentiment_clean,
  x = data_non_mil$running_probabilistic,
  covs = covs_matrix,
  cluster = data_non_mil$source_domain
)

summary(model4_opt_nonmil)
```

## Effect Size (Non-Military)

```{r effect-non-mil-prob}
sd_sentiment_non_mil <- sd(data_non_mil$sentiment_clean)
coef_model4_opt_nonmil <- model4_opt_nonmil$coef[1]

cat("Effect size (non-military, in SD units):", round(coef_model4_opt_nonmil / sd_sentiment_non_mil, 3), "\n")
```

## Visualization (Non-Military)

```{r plot-non-mil-cont-prob, fig.width=10, fig.height=7}
agg_data_non_mil <- data_non_mil %>%
  group_by(running_probabilistic) %>%
  summarize(sentiment_clean = mean(sentiment_clean), num_obs = n(), .groups = "drop")

invasion_on_sentiment_non_mil_graph <- data_non_mil %>%
  mutate(treatment = as.factor(treatment)) %>%
  ggplot(aes(x = running_probabilistic, y = sentiment_clean, group = treatment, color = treatment)) +
  geom_point(data = agg_data_non_mil,
             aes(x = running_probabilistic, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = c("dodgerblue", "red4"), name = "Post Invasion") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on Sentiment (Probabilistic Time Assignment)",
    subtitle = "Non-Military Topics",
    x = "Hours Pre/Post Invasion",
    y = "Sentiment"
  )

invasion_on_sentiment_non_mil_graph

ggsave(plot = invasion_on_sentiment_non_mil_graph,
       file.path(FIGURES_RDD, "invasion_on_sentiment_non_mil_cont_prob.png"),
       width = 10, height = 7)
```

# Robustness: Non-NATO Countries Only

```{r non-nato-prob}
data_non_nato <- data_non_ukraine %>%
  filter(!country %in% NATO_COUNTRIES)

covs_matrix <- model.matrix(~ country + source_domain + topic_clean - 1, data = data_non_nato)

model4_opt_nonnato <- rdrobust(
  y = data_non_nato$sentiment_clean,
  x = data_non_nato$running_probabilistic,
  covs = covs_matrix,
  cluster = data_non_nato$source_domain
)

summary(model4_opt_nonnato)
```

# Placebo Test: December 7th Announcement

```{r placebo-dec-prob}
data_dec <- data_non_ukraine %>%
  filter(date_publish < "2022-02-19") %>%
  mutate(
    running_probabilistic = as.numeric(difftime(date_time_publish, as.POSIXct("2021-12-07 00:00:00", tz = "UTC"), units = "secs")),
    treatment = ifelse(date_time_publish < as.POSIXct("2021-12-07 00:00:00", tz = "UTC"), 0, 1)
  )

# Full model specification using rdrobust (matches model4_opt)
covs_matrix_dec <- model.matrix(~ country + source_domain + topic_clean - 1,
                                data = data_dec)

model_placebo <- rdrobust(
  y = data_dec$sentiment_clean,
  x = data_dec$running_probabilistic,
  covs = covs_matrix_dec,
  cluster = data_dec$source_domain
)

summary(model_placebo)
cat("\nNote: Non-significant treatment effect suggests parallel trends assumption holds.\n")
```

# Summary Table (Table 1F)

```{r table1f-prob}
rows <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7,
  'State FEs', '-', 'X', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', 'X', 'X', 'X', 'X', 'X',
  'Topic FEs', '-', '-', '-', 'X', 'X', 'X', 'X'
)
attr(rows, 'position') <- c(3, 4, 5)

note_text <- "All standard errors are clustered at the source level. Models 1-4 uses the optimal bandwidth. Model 5 uses a linear specification with the full set of articles. Model 6 omits Military Topics. Model 7 omits NATO allies."
note_wrapped <- str_wrap(note_text, width = 80)

table_1f <- modelsummary(
  list(model1_opt, model2_opt, model3_opt, model4_opt, model1_full_linear, model4_opt_nonmil, model4_opt_nonnato),
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c("treatment" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors",
  title = "Hypothesis 1: RDD Analysis with Probabilistic Time Assignment Running Variable",
  add_rows = rows,
  notes = note_wrapped
)

table_1f
```

# Save Results

```{r save-results-prob}
# Save model objects for later use
results_h1_prob <- list(
  model1_basic = model1_basic,
  model1_country_fe = model1_country_fe,
  model1_country_source_fe = model1_country_source_fe,
  model1_full_linear = model1_full_linear,
  model1_opt = model1_opt,
  model2_opt = model2_opt,
  model3_opt = model3_opt,
  model4_opt = model4_opt,
  model4_non_nato = model4_opt_nonnato,
  model4_non_mil = model4_opt_nonmil,
  model4_opt_pol = model4_opt_pol,
  model4_opt_mil = model4_opt_mil,
  model4_opt_econ = model4_opt_econ,
  model4_opt_cult = model4_opt_cult,
  model4_opt_oth = model4_opt_oth,
  optimal_bandwidth = optimal_bw,
  model_placebo = model_placebo
)

saveRDS(results_h1_prob, file.path(DATA_INTERMEDIATE, "04_h1_results_prob.rds"))
cat("Results saved to:", file.path(DATA_INTERMEDIATE, "04_h1_results_prob.rds"), "\n")
```

# Session Info

```{r session-info-prob}
print_session_info()
```
