---
title: "05 - Difference-in-Discontinuities Analysis (Hypothesis 2)"
author: "Donald Moratz"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

# Overview

This script performs the Difference-in-Discontinuities analysis comparing state-owned vs independent media responses to the invasion.

**Inputs:**
- `data/intermediate/02_data_non_ukraine.rds`
- `data/intermediate/02_cleaned_data.rds`

**Outputs:**
- Diff-in-disc regression results
- Visualizations
- Table 2

```{r setup, include=FALSE}
source("00_setup.R")
```

# Load Data

```{r load}
data_non_ukraine <- readRDS(file.path(DATA_INTERMEDIATE, "02_data_non_ukraine.rds"))
data <- readRDS(file.path(DATA_INTERMEDIATE, "02_cleaned_data.rds"))

cat("Non-Ukraine sample:", nrow(data_non_ukraine), "articles\n")
cat("State-owned:", sum(data_non_ukraine$state_owned), "\n")
cat("Independent:", sum(data_non_ukraine$state_owned == 0), "\n")
```

# Main Diff-in-Disc Model

## Model 2a: Full Triple Interaction

```{r model2a}
model2a <- felm(sentiment_clean ~ running * treatment * state_owned | country + source_domain + topic_clean | 0 | source_domain,
                data = data_non_ukraine)

summary(model2a)
```

## Effect Size Analysis

```{r effect-size-discs}
sd_sentiment_non_ukraine <- sd(data_non_ukraine$sentiment_clean)

cat("Standard deviation:", round(sd_sentiment_non_ukraine, 3), "\n\n")

# Effect on all media
coef_all <- summary(model2a)$coef["treatment", "Estimate"]
cat("Effect on all media (in SD):", round(coef_all / sd_sentiment_non_ukraine, 3), "\n")

# Effect on state media specifically
coef_state <- summary(model2a)$coef["treatment:state_owned", "Estimate"]
cat("Additional effect on state media (in SD):", round(coef_state / sd_sentiment_non_ukraine, 3), "\n")
```

# Visualization: Main Diff-in-Disc Plot

```{r plot-discs, fig.width=10, fig.height=7}
# Aggregate data
agg_data_discs <- data_non_ukraine %>%
  group_by(running, state_owned) %>%
  summarize(
    sentiment_clean = mean(sentiment_clean, na.rm = TRUE),
    num_obs = n(),
    .groups = "drop"
  )

invasion_discs_graph <- data_non_ukraine %>%
  mutate(indicator = as.factor(indicator)) %>%
  mutate(indicator = fct_recode(indicator,
    "Ind. Pre." = "1",
    "State Pre." = "2",
    "Ind. Post" = "3",
    "State Post" = "4"
  )) %>%
  ggplot(aes(x = running, y = sentiment_clean, group = indicator, color = indicator)) +
  geom_point(data = agg_data_discs,
             aes(x = running, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = COLORS_DISCS, name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on Sentiment",
    subtitle = "Difference in Discontinuities",
    x = "Days Pre/Post Invasion",
    y = "Sentiment"
  )

invasion_discs_graph

ggsave(plot = invasion_discs_graph,
       file.path(FIGURES_DIFF_DISC, "invasion_discs_graph.png"),
       width = 10, height = 7)
```

# Optimal Bandwidth Selection

```{r optimal-bw}
data_non_ukraine <- data_non_ukraine %>%
  mutate(across(c("country", "source_domain", "topic_clean"), as.factor))

bw_select <- rdbwselect(y = data_non_ukraine$sentiment_clean,
                        x = data_non_ukraine$running,
                        kernel = "triangular",
                        cluster = data_non_ukraine$source_domain,
                        p = 1,
                        bwselect = "mserd")

summary(bw_select)

optimal_bw <- bw_select$bws[1, 1]
cat("Optimal bandwidth:", round(optimal_bw, 1), "days\n")

optimal_bandwidth_data <- data_non_ukraine %>%
  filter(running < optimal_bw) %>%
  filter(running > -optimal_bw)

cat("Observations within bandwidth:", nrow(optimal_bandwidth_data), "\n")
```

## Model with Optimal Bandwidth

```{r model2a-opt}
model2a_opt <- felm(sentiment_clean ~ running * treatment * state_owned | country + source_domain + topic_clean | 0 | source_domain,
                    data = optimal_bandwidth_data)

summary(model2a_opt)
```

# Robustness: Non-Military Topics

```{r non-mil}
data_non_mil <- data_non_ukraine %>%
  filter(!topic_clean %in% c("Military"))

model2b <- felm(sentiment_clean ~ running * treatment * state_owned | country + source_domain + topic_clean | 0 | source_domain,
                data = data_non_mil)

summary(model2b)
```

## Visualization (Non-Military)

```{r plot-non-mil, fig.width=10, fig.height=7}
agg_data_non_mil <- data_non_mil %>%
  group_by(running, state_owned) %>%
  summarize(sentiment_clean = mean(sentiment_clean), num_obs = n(), .groups = "drop")

invasion_discs_non_mil_graph <- data_non_mil %>%
  mutate(indicator = as.factor(indicator)) %>%
  mutate(indicator = fct_recode(indicator,
    "Ind. Pre." = "1",
    "State Pre." = "2",
    "Ind. Post" = "3",
    "State Post" = "4"
  )) %>%
  ggplot(aes(x = running, y = sentiment_clean, group = indicator, color = indicator)) +
  geom_point(data = agg_data_non_mil,
             aes(x = running, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = COLORS_DISCS, name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on Sentiment",
    subtitle = "Non-Military Topics",
    x = "Days Pre/Post Invasion",
    y = "Sentiment"
  )

invasion_discs_non_mil_graph

ggsave(plot = invasion_discs_non_mil_graph,
       file.path(FIGURES_DIFF_DISC, "invasion_discs_non_mil.png"),
       width = 10, height = 7)
```

# Robustness: Non-NATO Countries

```{r non-nato}
data_non_nato <- data_non_ukraine %>%
  filter(!country %in% NATO_COUNTRIES)

model2d <- felm(sentiment_clean ~ running * treatment * state_owned | country + source_domain + topic_clean | 0 | source_domain,
                data = data_non_nato)

summary(model2d)
```

# Russian-Related Articles Only

```{r russian-related}
data_russian_related <- data %>%
  filter(!Russian.Involvement == "Not") %>%
  filter(!country %in% c("Ukraine")) %>%
  filter(!topic_clean %in% c("Military"))

model3a <- felm(sentiment_clean ~ running * treatment * state_owned | country + source_domain + topic_clean | 0 | source_domain,
                data = data_russian_related)

summary(model3a)
```

# Diff-in-Diff (Within Bandwidth)

```{r did}
model_did <- felm(sentiment_clean ~ treatment * state_owned | country + source_domain + topic_clean | 0 | source_domain,
                  data = optimal_bandwidth_data)

summary(model_did)
```

# Placebo Test: December 7th Announcement

```{r placebo}
data_dec <- data %>%
  filter(date_publish < "2022-02-19") %>%
  mutate(
    running = as.numeric(date_publish - as.Date("2021-12-07")),
    treatment = ifelse(date_publish < as.Date("2021-12-07"), 0, 1)
  )

model4a <- felm(sentiment_clean ~ running * treatment | country + source_domain + Topic | 0 | source_domain,
                data = data_dec)

summary(model4a)
cat("\nNote: Non-significant treatment effect suggests parallel trends assumption holds.\n")
```

## Placebo Visualization

```{r placebo-plot, fig.width=10, fig.height=7}
agg_data_dec <- data_dec %>%
  group_by(running) %>%
  summarize(sentiment_clean = mean(sentiment_clean), num_obs = n(), .groups = "drop")

data_dec %>%
  mutate(treatment = as.factor(treatment)) %>%
  ggplot(aes(x = running, y = sentiment_clean, group = treatment, color = treatment)) +
  geom_point(data = agg_data_dec,
             aes(x = running, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = c("dodgerblue", "red4"), name = "Post Dec 7") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Placebo Test: Effect of December 7th Announcement",
    subtitle = "Pre-Invasion Period Only",
    x = "Days Pre/Post Announcement",
    y = "Sentiment"
  )
```

# Summary Table (Table 2)

```{r table2}
rows <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', 'X', 'X', 'X', 'X', 'X',
  'Topic FEs', 'X', 'X', 'X', 'X', 'X'
)
attr(rows, 'position') <- c(5, 6, 7)

note_text <- "All standard errors are clustered at the source level. Model 2 uses the optimal bandwidth. Model 3 omits NATO allies. Model 4 omits military-related articles. Model 5 uses only Russian-related articles."
note_wrapped <- str_wrap(note_text, width = 80)

table_2 <- modelsummary(
  list(model2a, model2a_opt, model2d, model2b, model3a),
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors",
  title = "Hypothesis 2: Difference in Discontinuity Analysis",
  add_rows = rows,
  notes = note_wrapped
)

table_2
```

# Save Results

```{r save}
results_h2 <- list(
  model2a = model2a,
  model2a_opt = model2a_opt,
  model2d = model2d,
  model2b = model2b,
  model3a = model3a,
  model_did = model_did,
  model_placebo = model4a,
  optimal_bandwidth = optimal_bw
)

saveRDS(results_h2, file.path(DATA_INTERMEDIATE, "05_h2_results.rds"))
cat("Results saved to:", file.path(DATA_INTERMEDIATE, "05_h2_results.rds"), "\n")
```

# Session Info

```{r session-info}
print_session_info()
```
