---
title: "05a - Difference-in-Discontinuities Analysis with Probabilistic Time Assignment (Hypothesis 2)"
author: "Donald Moratz"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

# Overview

This script performs the Difference-in-Discontinuities analysis comparing state-owned vs independent media responses to the invasion, using a probabilistic time assignment for the running variable.

**Inputs:**
- `data/intermediate/02_data_non_ukraine.rds`
- `data/intermediate/02_cleaned_data.rds`

**Outputs:**
- Diff-in-disc regression results (probabilistic)
- Visualizations
- Table 2I

```{r setup-prob, include=FALSE}
source("00_setup.R")
knitr::opts_chunk$set(fig.path = paste0(FIGURES_DIFF_DISC_PROB, "/"))

set.seed(3184)
```

# Load Data

```{r load-prob}
data_non_ukraine <- readRDS(file.path(DATA_INTERMEDIATE, "02_data_non_ukraine.rds"))
data <- readRDS(file.path(DATA_INTERMEDIATE, "02_cleaned_data.rds"))

cat("Non-Ukraine sample:", nrow(data_non_ukraine), "articles\n")
cat("State-owned:", sum(data_non_ukraine$state_owned), "\n")
cat("Independent:", sum(data_non_ukraine$state_owned == 0), "\n")

# Convert factors
data_non_ukraine <- data_non_ukraine %>%
  mutate(across(c("country", "source_domain", "topic_clean"), as.factor))%>%
  drop_na()%>%
  droplevels()

data <- data %>%
  mutate(across(c("country", "source_domain", "topic_clean"), as.factor))%>%
  droplevels()

# Compute z-scored sentiment within source_domain
data_non_ukraine <- data_non_ukraine %>%
  group_by(source_domain) %>%
  filter(sd(sentiment_clean, na.rm = TRUE) > 0) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                       sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()%>%
  droplevels()

data <- data %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                       sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()%>%
  droplevels()

# Convert running variable from seconds to days
data_non_ukraine <- data_non_ukraine %>%
  mutate(running_probabilistic = running_probabilistic / 86400)

data <- data %>%
  mutate(running_probabilistic = running_probabilistic / 86400)
```

# Separate RDDs by Media Type

These analyses mirror the CSTO-only / Neutral-only separate RDDs in the
heterogeneity analysis (file 06), but applied to state vs independent media.

## State-Owned Media Only (RDD)

### Sentiment Clean
```{r state-only-rdd-prob}
# Filter to state-owned media only
data_state_only <- data_non_ukraine %>%
  filter(state_owned == 1) %>%
  filter(!topic_clean %in% "Military")%>%
  droplevels()

covs_state <- model.matrix(~ source_domain + topic_clean - 1, data = data_state_only)

model2_state_rdd <- rdrobust(
  y = data_state_only$sentiment_clean,
  x = data_state_only$running_probabilistic,
  covs = covs_state,
  cluster = data_state_only$source_domain,
  kernel = "triangular", p = 1
)

cat("State-Owned Media Only RDD (Probabilistic)\n")
summary(model2_state_rdd)
cat("N (state-owned, non-military):", nrow(data_state_only), "\n")
cat("Unique clusters:", length(unique(data_state_only$source_domain)), "\n")
```

### Sentiment Z

```{r state-only-rdd-prob-z}
model2_state_rdd_z <- rdrobust(
  y = data_state_only$sentiment_z,
  x = data_state_only$running_probabilistic,
  covs = model.matrix(~ topic_clean - 1, data = data_state_only),
  cluster = data_state_only$source_domain, kernel = "triangular", p = 1
)

cat("State-Owned Media Only RDD — Z-score (Probabilistic)\n")
summary(model2_state_rdd_z)
```

## Independent Media Only (RDD)

### Sentiment Clean

```{r ind-only-rdd-prob}
# Filter to independent media only
data_ind_only <- data_non_ukraine %>%
  filter(state_owned == 0) %>%
  filter(!topic_clean %in% "Military")%>%
  droplevels()

covs_ind <- model.matrix(~ source_domain + topic_clean - 1, data = data_ind_only)

model2_ind_rdd <- rdrobust(
  y = data_ind_only$sentiment_clean,
  x = data_ind_only$running_probabilistic,
  covs = covs_ind,
  cluster = data_ind_only$source_domain,
  kernel = "triangular", p = 1
)

cat("Independent Media Only RDD (Probabilistic)\n")
summary(model2_ind_rdd)
cat("N (independent, non-military):", nrow(data_ind_only), "\n")
cat("Unique clusters:", length(unique(data_ind_only$source_domain)), "\n")
```

### Sentiment Z

```{r ind-only-rdd-prob-z}
model2_ind_rdd_z <- rdrobust(
  y = data_ind_only$sentiment_z,
  x = data_ind_only$running_probabilistic,
  covs = model.matrix(~ topic_clean - 1, data = data_ind_only),
  cluster = data_ind_only$source_domain, kernel = "triangular", p = 1
)

cat("Independent Media Only RDD — Z-score (Probabilistic)\n")
summary(model2_ind_rdd_z)
```

# Diff-in-Disc Analysis

## Full Data

### Full Data, Topic FEs

```{r model2a-prob}
model2a <- feols(sentiment_clean ~ running_probabilistic * treatment * state_owned | topic_clean,
                 cluster = ~source_domain,
                 data = data_non_ukraine)

summary(model2a)

# Wild cluster bootstrap for model2a
boot_model2a <- run_wild_bootstrap(model2a, "treatment:state_owned")
cat("Bootstrap SE for treatment:state_owned:", boot_model2a$se, "\n")
cat("Bootstrap p-value:", boot_model2a$p_val, "\n")

# Z-score version
model2a_z <- feols(sentiment_z ~ running_probabilistic * treatment * state_owned | topic_clean,
                   cluster = ~source_domain,
                   data = data_non_ukraine)
boot_model2a_z <- run_wild_bootstrap(model2a_z, "treatment:state_owned")
cat("Z-score model2a — Bootstrap p-value:", boot_model2a_z$p_val, "\n")
```

### Full Data, Topic + Source FEs

```{r model2a-full-prob}
model2a_full <- feols(sentiment_clean ~ running_probabilistic * treatment * state_owned |
                      topic_clean + source_domain,
                      cluster = ~source_domain, data = data_non_ukraine)
boot_model2a_full <- run_wild_bootstrap(model2a_full, "treatment:state_owned")
cat("Bootstrap SE for treatment:state_owned:", boot_model2a_full$se, "\n")
cat("Bootstrap p-value:", boot_model2a_full$p_val, "\n")
```

### Effect Size

```{r effect-size-discs-prob}
sd_sentiment_non_ukraine <- sd(data_non_ukraine$sentiment_clean)

cat("Standard deviation:", round(sd_sentiment_non_ukraine, 3), "\n\n")

# Effect on all media
coef_all <- model2a$coeftable["treatment", "Estimate"]
cat("Effect on all media (in SD):", round(coef_all / sd_sentiment_non_ukraine, 3), "\n")

# Effect on state media specifically
coef_state <- model2a$coeftable["treatment:state_owned", "Estimate"]
cat("Additional effect on state media (in SD):", round(coef_state / sd_sentiment_non_ukraine, 3), "\n")
```

## Visualization: Main Diff-in-Disc Plot

```{r plot-discs-prob, fig.width=10, fig.height=7}
agg_data_discs <- data_non_ukraine %>%
  group_by(running_probabilistic, state_owned) %>%
  summarize(
    sentiment_clean = mean(sentiment_clean, na.rm = TRUE),
    num_obs = n(),
    .groups = "drop"
  )

invasion_discs_graph <- data_non_ukraine %>%
  mutate(indicator = as.factor(indicator)) %>%
  mutate(indicator = fct_recode(indicator,
    "Ind. Pre." = "1",
    "State Pre." = "2",
    "Ind. Post" = "3",
    "State Post" = "4"
  )) %>%
  ggplot(aes(x = running_probabilistic, y = sentiment_clean, group = indicator, color = indicator)) +
  geom_point(data = agg_data_discs,
             aes(x = running_probabilistic, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = COLORS_DISCS, name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on Sentiment (Probabilistic Time Assignment)",
    subtitle = "Difference in Discontinuities",
    x = "Days Pre/Post Invasion",
    y = "Raw Sentiment"
  )

invasion_discs_graph

ggsave(plot = invasion_discs_graph,
       file.path(FIGURES_DIFF_DISC_PROB, "invasion_discs_graph_prob.png"),
       width = 10, height = 7)
```

## Optimal Bandwidth

### Bandwidth Selection

```{r optimal-bw-prob}
resid_y <- feols(sentiment_clean ~ 1 | topic_clean + source_domain + state_owned,
                 data = data_non_ukraine)$residuals

bw_select <- rdbwselect(y = resid_y,
                        x = data_non_ukraine$running_probabilistic,
                        kernel = "triangular",
                        cluster = data_non_ukraine$source_domain,
                        p = 1,
                        bwselect = "mserd")

summary(bw_select)

optimal_bw <- bw_select$bws[1, 1]
cat("Optimal bandwidth:", round(optimal_bw, 1), "days\n")

optimal_bandwidth_data <- data_non_ukraine %>%
  filter(running_probabilistic < optimal_bw) %>%
  filter(running_probabilistic > -optimal_bw)%>%
  droplevels()

# Z-score for optimal bandwidth data
optimal_bandwidth_data <- optimal_bandwidth_data %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                       sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()%>%
  droplevels()

cat("Observations within bandwidth:", nrow(optimal_bandwidth_data), "\n")
```

### Optimal BW, Topic FEs

```{r model2a-opt-prob}
model2a_opt <- feols(sentiment_clean ~ running_probabilistic * treatment * state_owned | topic_clean,
                     cluster = ~source_domain,
                     data = optimal_bandwidth_data)

summary(model2a_opt)

# Wild cluster bootstrap for model2a_opt
boot_model2a_opt <- run_wild_bootstrap(model2a_opt, "treatment:state_owned")
cat("Bootstrap SE for treatment:state_owned:", boot_model2a_opt$se, "\n")
cat("Bootstrap p-value:", boot_model2a_opt$p_val, "\n")
```

### Optimal BW, Full FEs

```{r model2a-opt-full-fe-prob}
model2a_opt_full_fe <- feols(sentiment_clean ~ running_probabilistic * treatment * state_owned |
                              topic_clean + source_domain,
                              cluster = ~source_domain, data = optimal_bandwidth_data)

boot_model2a_opt_full_fe <- run_wild_bootstrap(model2a_opt_full_fe, "treatment:state_owned")
cat("Bootstrap SE for treatment:state_owned:", boot_model2a_opt_full_fe$se, "\n")
cat("Bootstrap p-value:", boot_model2a_opt_full_fe$p_val, "\n")
```

### Optimal BW, Z-Score

```{r model2a-opt-prob-z}
# Residualize the dependent variable for fixed effects to do bandwidth selection
resid_y <- feols(sentiment_z ~ 1 | topic_clean + state_owned,
                 data = data_non_ukraine)$residuals

bw_select <- rdbwselect(y = resid_y,
                        x = data_non_ukraine$running_probabilistic,
                        kernel = "triangular",
                        cluster = data_non_ukraine$source_domain,
                        p = 1,
                        bwselect = "mserd")

optimal_bw_align <- bw_select$bws[1, 1]
cat("Optimal bandwidth:", round(optimal_bw_align, 1), "days\n")

optimal_bandwidth_data_z <- data_non_ukraine %>%
  filter(running_probabilistic < optimal_bw_align, running_probabilistic > -optimal_bw_align)%>%
  droplevels()


# Z-score version
model2a_opt_z <- feols(sentiment_z ~ running_probabilistic * treatment * state_owned | topic_clean,
                       cluster = ~source_domain,
                       data = optimal_bandwidth_data_z)
boot_model2a_opt_z <- run_wild_bootstrap(model2a_opt_z, "treatment:state_owned")
cat("Z-score model2a_opt — Bootstrap p-value:", boot_model2a_opt_z$p_val, "\n")
```


### DID Within Bandwidth

```{r did-prob}
model_did <- feols(sentiment_clean ~ treatment * state_owned | topic_clean,
                   cluster = ~source_domain,
                   data = optimal_bandwidth_data)

summary(model_did)

# Wild cluster bootstrap
boot_model_did <- run_wild_bootstrap(model_did, "treatment:state_owned")
cat("Bootstrap SE for treatment:state_owned:", boot_model_did$se, "\n")
cat("Bootstrap p-value:", boot_model_did$p_val, "\n")
```

## Non-Military Topics

### Non-Military, Topic FEs

```{r non-mil-prob}
data_non_mil <- data_non_ukraine %>%
  filter(!topic_clean %in% c("Military"))

# Residualize the dependent variable for fixed effects to do bandwidth selection
resid_y <- feols(sentiment_clean ~ 1 | topic_clean + source_domain + state_owned, 
                 data = data_non_mil)$residuals

bw_align_non_mil <- rdbwselect(y = resid_y,
                               x = data_non_mil$running_probabilistic,
                               kernel = "triangular",
                               cluster = data_non_mil$source_domain,
                               p = 1,
                               bwselect = "mserd")

optimal_bw_align_non_mil <- bw_align_non_mil$bws[1, 1]
cat("Optimal bandwidth (non-mil):", round(optimal_bw_align_non_mil, 1), "days\n")

optimal_bandwidth_data_non_mil <- data_non_mil %>%
  filter(running_probabilistic < optimal_bw_align_non_mil, running_probabilistic > -optimal_bw_align_non_mil)%>%
  droplevels()

model2b <- feols(sentiment_clean ~ running_probabilistic * treatment * state_owned | topic_clean,
                 cluster = ~source_domain,
                 data = optimal_bandwidth_data_non_mil)

summary(model2b)

# Wild cluster bootstrap
boot_model2b <- run_wild_bootstrap(model2b, "treatment:state_owned")
cat("Bootstrap SE for treatment:state_owned:", boot_model2b$se, "\n")
cat("Bootstrap p-value:", boot_model2b$p_val, "\n")
```

### Non-Military, Full FEs

```{r model2b-full-fe-prob}
model2b_full_fe <- feols(sentiment_clean ~ running_probabilistic * treatment * state_owned |
                          topic_clean + source_domain,
                          cluster = ~source_domain, data = optimal_bandwidth_data_non_mil)

boot_model2b_full_fe <- run_wild_bootstrap(model2b_full_fe, "treatment:state_owned")
cat("Bootstrap SE for treatment:state_owned:", boot_model2b_full_fe$se, "\n")
cat("Bootstrap p-value:", boot_model2b_full_fe$p_val, "\n")
```

### Non-Military, Z-Score

```{r non-mil-prob-z}
# Z-score version

# Create New z score
data_non_mil <- data_non_mil %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) / 
                   sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()

# Residualize the dependent variable for fixed effects to do bandwidth selection
resid_y <- feols(sentiment_z~ 1 | topic_clean + state_owned, 
                 data = data_non_mil)$residuals

bw_align_non_mil <- rdbwselect(y = resid_y,
                               x = data_non_mil$running_probabilistic,
                               kernel = "triangular",
                               cluster = data_non_mil$source_domain,
                               p = 1,
                               bwselect = "mserd")

optimal_bw_align_non_mil <- bw_align_non_mil$bws[1, 1]
cat("Optimal bandwidth (non-mil):", round(optimal_bw_align_non_mil, 1), "days\n")

optimal_bandwidth_data_non_mil <- data_non_mil %>%
  filter(running_probabilistic < optimal_bw_align_non_mil, running_probabilistic > -optimal_bw_align_non_mil)%>%
  droplevels()

model2b_z <- feols(sentiment_z ~ running_probabilistic * treatment * state_owned | topic_clean,
                   cluster = ~source_domain,
                   data = optimal_bandwidth_data_non_mil)
boot_model2b_z <- run_wild_bootstrap(model2b_z, "treatment:state_owned")
cat("Z-score model2b — Bootstrap p-value:", boot_model2b_z$p_val, "\n")
```


### Visualization (Non-Military)

```{r plot-non-mil-prob, fig.width=10, fig.height=7}
agg_data_non_mil <- data_non_mil %>%
  group_by(running_probabilistic, state_owned) %>%
  summarize(sentiment_clean = mean(sentiment_clean), num_obs = n(), .groups = "drop")

invasion_discs_non_mil_graph <- data_non_mil %>%
  mutate(indicator = as.factor(indicator)) %>%
  mutate(indicator = fct_recode(indicator,
    "Ind. Pre." = "1",
    "State Pre." = "2",
    "Ind. Post" = "3",
    "State Post" = "4"
  )) %>%
  ggplot(aes(x = running_probabilistic, y = sentiment_clean, group = indicator, color = indicator)) +
  geom_point(data = agg_data_non_mil,
             aes(x = running_probabilistic, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = COLORS_DISCS, name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on Sentiment (Probabilistic Time Assignment)",
    subtitle = "Non-Military Topics",
    x = "Days Pre/Post Invasion",
    y = "Sentiment"
  )

invasion_discs_non_mil_graph

ggsave(plot = invasion_discs_non_mil_graph,
       file.path(FIGURES_DIFF_DISC_PROB, "invasion_discs_non_mil_prob.png"),
       width = 10, height = 7)
```

## Non-NATO Countries

### Non-Nato, Topic FE

```{r non-nato-prob}
data_non_nato <- data_non_mil %>%
  filter(!country %in% NATO_COUNTRIES)

# Residualize the dependent variable for fixed effects to do bandwidth selection
resid_y <- feols(sentiment_clean~ 1 | topic_clean + state_owned, 
                 data = data_non_nato)$residuals

bw_align_non_nato <- rdbwselect(y = resid_y,
                               x = data_non_nato$running_probabilistic,
                               kernel = "triangular",
                               cluster = data_non_nato$source_domain,
                               p = 1,
                               bwselect = "mserd")

optimal_bw_align_non_nato <- bw_align_non_nato$bws[1, 1]
cat("Optimal bandwidth (non-nato):", round(optimal_bw_align_non_nato, 1), "days\n")

optimal_bandwidth_data_non_nato <- data_non_nato %>%
  filter(running_probabilistic < optimal_bw_align_non_nato, running_probabilistic > -optimal_bw_align_non_nato)%>%
  droplevels()

model2d <- feols(sentiment_clean ~ running_probabilistic * treatment * state_owned | topic_clean,
                 cluster = ~source_domain,
                 data = optimal_bandwidth_data_non_nato)

summary(model2d)

# Wild cluster bootstrap
boot_model2d <- run_wild_bootstrap(model2d, "treatment:state_owned")
cat("Bootstrap SE for treatment:state_owned:", boot_model2d$se, "\n")
cat("Bootstrap p-value:", boot_model2d$p_val, "\n")
```

```{r}
model2d_fullfe <- feols(sentiment_clean ~ running_probabilistic * treatment * state_owned | 
                          topic_clean + source_domain,
                 cluster = ~source_domain,
                 data = optimal_bandwidth_data_non_nato)

summary(model2d_fullfe)

# Wild cluster bootstrap
boot_model2d_fullfe <- run_wild_bootstrap(model2d_fullfe, "treatment:state_owned")
cat("Bootstrap SE for treatment:state_owned:", boot_model2d_fullfe$se, "\n")
cat("Bootstrap p-value:", boot_model2d_fullfe$p_val, "\n")
```

```{r non-nato-prob-z}
# Z-score version

# Residualize the dependent variable for fixed effects to do bandwidth selection
resid_y <- feols(sentiment_z~ 1 | topic_clean + state_owned, 
                 data = data_non_nato)$residuals

bw_align_non_nato <- rdbwselect(y = resid_y,
                               x = data_non_nato$running_probabilistic,
                               kernel = "triangular",
                               cluster = data_non_nato$source_domain,
                               p = 1,
                               bwselect = "mserd")

optimal_bw_align_non_nato <- bw_align_non_nato$bws[1, 1]
cat("Optimal bandwidth (non-nato):", round(optimal_bw_align_non_nato, 1), "days\n")

optimal_bandwidth_data_non_nato <- data_non_nato %>%
  filter(running_probabilistic < optimal_bw_align_non_nato, running_probabilistic > -optimal_bw_align_non_nato)%>%
  droplevels()


model2d_z <- feols(sentiment_z ~ running_probabilistic * treatment * state_owned | topic_clean,
                   cluster = ~source_domain,
                   data = optimal_bandwidth_data_non_nato)

boot_model2d_z <- run_wild_bootstrap(model2d_z, "treatment:state_owned")
cat("Z-score model2d — Bootstrap p-value:", boot_model2d_z$p_val, "\n")
```

## Russian-Related Articles

### Russian-Related, Topic FEs

```{r russian-related-prob}
data_russian_related <- data_non_nato %>%
  filter(!Russian.Involvement == "Not")

# Z-score for Russian-related data
data_russian_related <- data_russian_related %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                       sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()

# Residualize the dependent variable for fixed effects to do bandwidth selection
resid_y <- feols(sentiment_clean~ 1 | topic_clean + state_owned, 
                 data = data_russian_related)$residuals

bw_align_russian <- rdbwselect(y = resid_y,
                               x = data_russian_related$running_probabilistic,
                               kernel = "triangular",
                               cluster = data_russian_related$source_domain,
                               p = 1,
                               bwselect = "mserd")

optimal_bw_align_russian <- bw_align_russian$bws[1, 1]
cat("Optimal bandwidth (non-nato):", round(optimal_bw_align_russian, 1), "days\n")

optimal_bandwidth_data_russian <- data_russian_related %>%
  filter(running_probabilistic < optimal_bw_align_russian, running_probabilistic > -optimal_bw_align_russian)%>%
  droplevels()

model3a_opt <- feols(sentiment_clean ~ running_probabilistic * treatment * state_owned | topic_clean,
                 cluster = ~source_domain,
                 data = optimal_bandwidth_data_russian)

summary(model3a_opt)

# Wild cluster bootstrap
boot_model3a_opt <- run_wild_bootstrap(model3a_opt, "treatment:state_owned")
cat("Bootstrap SE for treatment:state_owned:", boot_model3a_opt$se, "\n")
cat("Bootstrap p-value:", boot_model3a_opt$p_val, "\n")
```

### Russian-Related Full FEs

```{r model3a-opt-full-fe-prob}
model3a_opt_full_fe <- feols(sentiment_clean ~ running_probabilistic * treatment * state_owned |
                              topic_clean + source_domain,
                              cluster = ~source_domain, 
                             data = optimal_bandwidth_data_russian)

boot_model3a_opt_full_fe <- run_wild_bootstrap(model3a_opt_full_fe, "treatment:state_owned")
cat("Bootstrap SE for treatment:state_owned:", boot_model3a_opt_full_fe$se, "\n")
cat("Bootstrap p-value:", boot_model3a_opt_full_fe$p_val, "\n")
```


### Russian-Related, Z-score

```{r russian-related-prob-z}
# Residualize the dependent variable for fixed effects to do bandwidth selection
resid_y <- feols(sentiment_z~ 1 | topic_clean + state_owned, 
                 data = data_russian_related)$residuals

bw_align_russian <- rdbwselect(y = resid_y,
                               x = data_russian_related$running_probabilistic,
                               kernel = "triangular",
                               cluster = data_russian_related$source_domain,
                               p = 1,
                               bwselect = "mserd")

optimal_bw_align_russian <- bw_align_russian$bws[1, 1]
cat("Optimal bandwidth (non-nato):", round(optimal_bw_align_russian, 1), "days\n")

optimal_bandwidth_data_russian_z <- data_russian_related %>%
  filter(running_probabilistic < optimal_bw_align_russian, running_probabilistic > -optimal_bw_align_russian)%>%
  droplevels()


model3a_z <- feols(sentiment_z ~ running_probabilistic * treatment * state_owned | topic_clean,
                   cluster = ~source_domain,
                   data = optimal_bandwidth_data_russian_z)
summary(model3a_z)

boot_model3a_z <- run_wild_bootstrap(model3a_z, "treatment:state_owned")
cat("Z-score model3a — Bootstrap p-value:", boot_model3a_z$p_val, "\n")
```

# By-Topic Analysis

## Full Data By Topic

```{r topic-full-prob}
data_pol <- data_non_ukraine %>% filter(topic_clean == "Political")
data_mil <- data_non_ukraine %>% filter(topic_clean == "Military")
data_econ <- data_non_ukraine %>% filter(topic_clean == "Economic")
data_cult <- data_non_ukraine %>% filter(topic_clean == "Culture")
data_oth <- data_non_ukraine %>% filter(topic_clean == "Other")

model2a_full_pol <- feols(sentiment_z ~ running_probabilistic * treatment * state_owned,
                          cluster = ~source_domain,
                          data = data_pol)
model2a_full_mil <- feols(sentiment_z ~ running_probabilistic * treatment * state_owned,
                          cluster = ~source_domain,
                          data = data_mil)
model2a_full_econ <- feols(sentiment_z ~ running_probabilistic * treatment * state_owned,
                           cluster = ~source_domain,
                           data = data_econ)
model2a_full_cult <- feols(sentiment_z ~ running_probabilistic * treatment * state_owned,
                           cluster = ~source_domain,
                           data = data_cult)
model2a_full_oth <- feols(sentiment_z ~ running_probabilistic * treatment * state_owned,
                          cluster = ~source_domain,
                          data = data_oth)

summary(model2a_full_pol)

# Wild cluster bootstrap for topic-specific models (full data)
boot_model2a_full_pol <- run_wild_bootstrap(model2a_full_pol, "treatment:state_owned")
cat("Bootstrap p-value:", boot_model2a_full_pol$p_val, "\n")
boot_model2a_full_mil <- run_wild_bootstrap(model2a_full_mil, "treatment:state_owned")
cat("Bootstrap p-value:", boot_model2a_full_mil$p_val, "\n")
boot_model2a_full_econ <- run_wild_bootstrap(model2a_full_econ, "treatment:state_owned")
cat("Bootstrap p-value:", boot_model2a_full_econ$p_val, "\n")
boot_model2a_full_cult <- run_wild_bootstrap(model2a_full_cult, "treatment:state_owned")
cat("Bootstrap p-value:", boot_model2a_full_cult$p_val, "\n")
boot_model2a_full_oth <- run_wild_bootstrap(model2a_full_oth, "treatment:state_owned")
cat("Bootstrap p-value:", boot_model2a_full_oth$p_val, "\n")
```

## Per-Topic Optimal Bandwidth

```{r topic-opt-bw-prob}
# Political
resid_y_pol <- feols(sentiment_z ~ 1 | state_owned, data = data_pol)$residuals
bw_pol <- rdbwselect(y = resid_y_pol, x = data_pol$running_probabilistic,
                     kernel = "triangular", cluster = data_pol$source_domain, p = 1, bwselect = "mserd")
optimal_bw_pol <- bw_pol$bws[1, 1]
cat("Political optimal bandwidth:", round(optimal_bw_pol, 1), "days\n")
opt_data_pol <- data_pol %>% filter(running_probabilistic < optimal_bw_pol, running_probabilistic > -optimal_bw_pol)%>%
  droplevels()

# Military
resid_y_mil <- feols(sentiment_z ~ 1 | state_owned, data = data_mil)$residuals
bw_mil <- rdbwselect(y = resid_y_mil, x = data_mil$running_probabilistic,
                     kernel = "triangular", cluster = data_mil$source_domain, p = 1, bwselect = "mserd")
optimal_bw_mil <- bw_mil$bws[1, 1]
cat("Military optimal bandwidth:", round(optimal_bw_mil, 1), "days\n")
opt_data_mil <- data_mil %>% filter(running_probabilistic < optimal_bw_mil, running_probabilistic > -optimal_bw_mil)%>%
  droplevels()

# Economic
resid_y_econ <- feols(sentiment_z ~ 1 | state_owned, data = data_econ)$residuals
bw_econ <- rdbwselect(y = resid_y_econ, x = data_econ$running_probabilistic,
                      kernel = "triangular", cluster = data_econ$source_domain, p = 1, bwselect = "mserd")
optimal_bw_econ <- bw_econ$bws[1, 1]
cat("Economic optimal bandwidth:", round(optimal_bw_econ, 1), "days\n")
opt_data_econ <- data_econ %>% filter(running_probabilistic < optimal_bw_econ, running_probabilistic > -optimal_bw_econ)%>%
  droplevels()

# Culture
resid_y_cult <- feols(sentiment_z ~ 1 | state_owned, data = data_cult)$residuals
bw_cult <- rdbwselect(y = resid_y_cult, x = data_cult$running_probabilistic,
                      kernel = "triangular", cluster = data_cult$source_domain, p = 1, bwselect = "mserd")
optimal_bw_cult <- bw_cult$bws[1, 1]
cat("Culture optimal bandwidth:", round(optimal_bw_cult, 1), "days\n")
opt_data_cult <- data_cult %>% filter(running_probabilistic < optimal_bw_cult, running_probabilistic > -optimal_bw_cult)%>%
  droplevels()

# Other
resid_y_oth <- feols(sentiment_z ~ 1 | state_owned, data = data_oth)$residuals
bw_oth <- rdbwselect(y = resid_y_oth, x = data_oth$running_probabilistic,
                     kernel = "triangular", cluster = data_oth$source_domain, p = 1, bwselect = "mserd")
optimal_bw_oth <- bw_oth$bws[1, 1]
cat("Other optimal bandwidth:", round(optimal_bw_oth, 1), "days\n")
opt_data_oth <- data_oth %>% filter(running_probabilistic < optimal_bw_oth, running_probabilistic > -optimal_bw_oth)%>%
  droplevels()
```

```{r topic-opt-models-prob}
model2a_opt_pol <- feols(sentiment_z ~ running_probabilistic * treatment * state_owned,
                         cluster = ~source_domain,
                         data = opt_data_pol)
summary(model2a_opt_pol)

model2a_opt_mil <- feols(sentiment_z ~ running_probabilistic * treatment * state_owned,
                         cluster = ~source_domain,
                         data = opt_data_mil)
summary(model2a_opt_mil)

model2a_opt_econ <- feols(sentiment_z ~ running_probabilistic * treatment * state_owned,
                          cluster = ~source_domain,
                          data = opt_data_econ)
summary(model2a_opt_econ)

model2a_opt_cult <- feols(sentiment_z ~ running_probabilistic * treatment * state_owned,
                          cluster = ~source_domain,
                          data = opt_data_cult)
summary(model2a_opt_cult)

model2a_opt_oth <- feols(sentiment_z ~ running_probabilistic * treatment * state_owned,
                         cluster = ~source_domain,
                         data = opt_data_oth)
summary(model2a_opt_oth)

# Wild cluster bootstrap for topic-specific models (optimal BW)
boot_model2a_opt_pol <- run_wild_bootstrap(model2a_opt_pol, "treatment:state_owned")
cat("Bootstrap p-value:", boot_model2a_opt_pol$p_val, "\n")
boot_model2a_opt_mil <- run_wild_bootstrap(model2a_opt_mil, "treatment:state_owned")
cat("Bootstrap p-value:", boot_model2a_opt_mil$p_val, "\n")
boot_model2a_opt_econ <- run_wild_bootstrap(model2a_opt_econ, "treatment:state_owned")
cat("Bootstrap p-value:", boot_model2a_opt_econ$p_val, "\n")
boot_model2a_opt_cult <- run_wild_bootstrap(model2a_opt_cult, "treatment:state_owned")
cat("Bootstrap p-value:", boot_model2a_opt_cult$p_val, "\n")
boot_model2a_opt_oth <- run_wild_bootstrap(model2a_opt_oth, "treatment:state_owned")
cat("Bootstrap p-value:", boot_model2a_opt_oth$p_val, "\n")
```

# Robustness

## Leave-One-Out Non-Z Country Robustness

```{r loo-country-prob}
# Use non-military data recalculate optimal bandwidth each time
countries <- unique(data_non_mil$country)
loo_results <- list()

for (cntry in countries) {
  data_loo <- data_non_mil %>%
    filter(country != cntry)%>%
  droplevels()

  # Re-calculate optimal bandwidth for LOO data
  resid_y_loo <- feols(sentiment_z ~ 1 | topic_clean + state_owned,
                       data = data_loo)$residuals
  bw_loo <- rdbwselect(y = resid_y_loo,
                       x = data_loo$running_probabilistic,
                       kernel = "triangular",
                       cluster = data_loo$source_domain,
                       p = 1,
                       bwselect = "mserd")

  optimal_bw_loo <- bw_loo$bws[1, 1]

  data_loo_bw <- data_loo %>%
    filter(running_probabilistic < optimal_bw_loo, running_probabilistic > -optimal_bw_loo)%>%
  droplevels()

  model_loo <- feols(sentiment_z ~ running_probabilistic * treatment * state_owned | topic_clean,
                     cluster = ~source_domain,
                     data = data_loo_bw)

  boot_loo <- tryCatch(
    run_wild_bootstrap(model_loo, "treatment:state_owned", B = 4999),
    error = function(e) list(se = NA, p_val = NA, ci_lower = NA, ci_upper = NA, t_stat = NA)
  )
  loo_results[[cntry]] <- list(
    model = model_loo,
    bandwidth = optimal_bw_loo,
    n = nrow(data_loo_bw),
    country_dropped = cntry,
    boot_p_val = boot_loo$p_val,
    boot_se = boot_loo$se
  )
}

# Extract key coefficient (treatment:state_owned interaction)
loo_summary <- map_df(names(loo_results), function(cntry) {
  mod <- loo_results[[cntry]]$model
  tibble(
    country_dropped = cntry,
    estimate = coef(mod)["treatment:state_owned"],
    std_error = se(mod)["treatment:state_owned"],
    p_value = pvalue(mod)["treatment:state_owned"],
    n_obs = loo_results[[cntry]]$n,
    bandwidth = loo_results[[cntry]]$bandwidth
  )
})

print(loo_summary)
```

## Placebo Test (December 7th, Non-Military)

```{r placebo-prob}
data_dec <- data %>%
  filter(date_publish < "2022-02-19") %>%
  filter(!topic_clean %in% c("Military")) %>%
  mutate(
    running_probabilistic = as.numeric(difftime(date_publish_probabilistic, as.POSIXct("2021-12-07 00:00:00", tz = "UTC"), units = "secs")/86400),
    treatment = ifelse(date_publish_probabilistic < as.POSIXct("2021-12-07 00:00:00", tz = "UTC"), 0, 1)
  )%>%
  filter(!is.na(sentiment_z), !is.na(topic_clean), !is.na(state_owned))%>%
  droplevels()

# Find optimal bandwidth for placebo
resid_y_placebo <- feols(sentiment_z ~ 1 | topic_clean + state_owned,
                         data = data_dec)$residuals
bw_placebo <- rdbwselect(y = resid_y_placebo,
                         x = data_dec$running_probabilistic,
                         kernel = "triangular",
                         cluster = data_dec$source_domain,
                         p = 1,
                         bwselect = "mserd")

optimal_bw_placebo <- bw_placebo$bws[1, 1]
cat("Placebo optimal bandwidth:", round(optimal_bw_placebo, 1), "days\n")

data_dec_bw <- data_dec %>%
  filter(running_probabilistic < optimal_bw_placebo, running_probabilistic > -optimal_bw_placebo)%>%
  droplevels()

model4a <- feols(sentiment_z ~ running_probabilistic * treatment * state_owned | topic_clean,
                 cluster = ~source_domain,
                 data = data_dec_bw)

summary(model4a)

# Wild cluster bootstrap for placebo
boot_model4a <- run_wild_bootstrap(model4a, "treatment:state_owned")
cat("Bootstrap SE for treatment:state_owned:", boot_model4a$se, "\n")
cat("Bootstrap p-value:", boot_model4a$p_val, "\n")
cat("\nNote: Non-significant treatment effect suggests parallel trends assumption holds.\n")
```

```{r placebo-plot-prob, fig.width=10, fig.height=7}
agg_data_dec <- data_dec %>%
  group_by(running_probabilistic, state_owned) %>%
  summarize(sentiment_clean = mean(sentiment_clean), num_obs = n(), .groups = "drop")

data_dec %>%
  mutate(indicator = as.factor(indicator)) %>%
  mutate(indicator = fct_recode(indicator,
    "Ind. Pre." = "1",
    "State Pre." = "2",
    "Ind. Post" = "3",
    "State Post" = "4"
  )) %>%
  ggplot(aes(x = running_probabilistic, y = sentiment_clean, group = indicator, color = indicator)) +
  geom_point(data = agg_data_dec,
             aes(x = running_probabilistic, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = COLORS_DISCS, name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Placebo Test: Effect of December 7th Announcement (Probabilistic Time)",
    subtitle = "Pre-Invasion Period Only, Non-Military Topics",
    x = "Days Pre/Post Announcement",
    y = "Sentiment"
  )
```

## Neutral Media Floor Check

The H2 results show state-owned outlets in neutral countries barely moving after
the invasion. One reading of that null is mechanical rather than substantive: if
neutral state media were already at the bottom of the sentiment scale before the
invasion, they could not have fallen further, and the null would be a floor or
measurement artifact rather than evidence about behaviour.

This figure rules that out by making the starting level and the drop legible at the
same time. Panel A places both media types on the full coding scale, which runs
{-1, 0, 1}, with the floor drawn in: neutral state media sit near -0.26, nowhere
close to -1, so there was ample room to fall. Panel B zooms to the period means with
95%% confidence intervals so the magnitudes are readable: independent outlets drop by
about -0.13 while state-owned outlets move by about -0.005. Same countries, same
window, same scale -- the state-owned series simply does not move.

```{r neutral-floor-side-by-side-prob, fig.width=13, fig.height=6.5}
INVASION_DATE   <- as.Date("2022-02-24")
SENTIMENT_FLOOR <- -1     # the coding scale runs {-1, 0, 1}

# Neutral countries only: not Russia-aligned, not NATO
data_neutral_floor <- data_non_ukraine %>%
  filter(csto == 0, nato == 0) %>%
  mutate(media_type = factor(ifelse(state_owned == 1, "State-owned", "Independent"),
                             levels = c("State-owned", "Independent")),
         period = factor(ifelse(treatment == 1, "Post-invasion", "Pre-invasion"),
                         levels = c("Pre-invasion", "Post-invasion")))

COLORS_FLOOR <- c("State-owned" = "forestgreen", "Independent" = "dodgerblue")

# Daily means for the time-series panel (date granularity, paper convention)
agg_neutral_daily <- data_neutral_floor %>%
  group_by(media_type, date_publish) %>%
  summarize(sentiment_clean = mean(sentiment_clean, na.rm = TRUE),
            num_obs = n(), .groups = "drop")

# Pre/post means with normal-approximation 95% CIs
agg_neutral_period <- data_neutral_floor %>%
  group_by(media_type, period) %>%
  summarize(mean_sentiment = mean(sentiment_clean, na.rm = TRUE),
            se = sd(sentiment_clean, na.rm = TRUE) / sqrt(n()),
            n_articles = n(), .groups = "drop") %>%
  mutate(ci_lower = mean_sentiment - 1.96 * se,
         ci_upper = mean_sentiment + 1.96 * se)

print(as.data.frame(agg_neutral_period), row.names = FALSE, digits = 4)

# Pre-to-post change, used to annotate the detail panel
agg_neutral_change <- agg_neutral_period %>%
  select(media_type, period, mean_sentiment) %>%
  pivot_wider(names_from = period, values_from = mean_sentiment) %>%
  mutate(change = `Post-invasion` - `Pre-invasion`)

print(as.data.frame(agg_neutral_change), row.names = FALSE, digits = 4)

# Panel A: the full coding scale, so the distance to the floor is visible.
# Carries the shared colour legend for both panels.
panel_scale <- ggplot(agg_neutral_daily,
                      aes(x = date_publish, y = sentiment_clean, color = media_type)) +
  geom_point(aes(size = num_obs), alpha = 0.25) +
  geom_hline(yintercept = SENTIMENT_FLOOR, linetype = "solid", color = "grey40") +
  annotate("text", x = min(agg_neutral_daily$date_publish), y = SENTIMENT_FLOOR + 0.06,
           label = "Scale floor (-1)", hjust = 0, size = 3.2, color = "grey30") +
  geom_hline(yintercept = 0, linetype = "dotted", alpha = 0.5) +
  geom_vline(xintercept = INVASION_DATE, linetype = "dashed", alpha = 0.7) +
  geom_segment(data = agg_neutral_period,
               aes(x = if_else(period == "Pre-invasion",
                               min(agg_neutral_daily$date_publish), INVASION_DATE),
                   xend = if_else(period == "Pre-invasion",
                                  INVASION_DATE, max(agg_neutral_daily$date_publish)),
                   y = mean_sentiment, yend = mean_sentiment, color = media_type),
               linewidth = 1.1, inherit.aes = FALSE) +
  scale_color_manual(values = COLORS_FLOOR, name = "Media type") +
  scale_size(name = "Articles/day") +
  coord_cartesian(ylim = c(-1, 1)) +
  guides(color = guide_legend(override.aes = list(alpha = 1, size = 3))) +
  theme_classic() +
  labs(
    title = "A. Position on the full coding scale",
    subtitle = "Daily means with period means overlaid; dashed line = Feb 24, 2022",
    x = "Publication date",
    y = "Mean sentiment toward Russia"
  )

# Panel B: the same period means, zoomed, so the drops are readable. The colour
# legend is suppressed here so patchwork collects a single one from panel A.
panel_detail <- ggplot(agg_neutral_period,
                       aes(x = period, y = mean_sentiment,
                           color = media_type, group = media_type)) +
  geom_line(linewidth = 1.1) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0.08, linewidth = 0.7) +
  geom_point(size = 3.2) +
  # Value labels sit outside the centre: left of the pre point, right of the post
  geom_text(aes(label = sprintf("%.3f", mean_sentiment),
                hjust = if_else(period == "Pre-invasion", 1.4, -0.4)),
            size = 3.2, show.legend = FALSE) +
  # Change label boxed in white so it stays legible where it crosses a line
  geom_label(data = agg_neutral_change,
             aes(x = 1.5, y = (`Pre-invasion` + `Post-invasion`) / 2,
                 label = sprintf("%+.3f", change), color = media_type),
             size = 3.6, fontface = "bold", fill = "white",
             linewidth = 0, label.padding = unit(0.15, "lines"),
             inherit.aes = FALSE, show.legend = FALSE) +
  scale_color_manual(values = COLORS_FLOOR, name = "Media type", guide = "none") +
  scale_x_discrete(expand = expansion(mult = 0.25)) +
  theme_classic() +
  labs(
    title = "B. Pre/post means, detail",
    subtitle = "Error bars are 95% CIs; boxed labels give the change",
    x = NULL,
    y = "Mean sentiment toward Russia"
  )

neutral_floor_graph <- (panel_scale | panel_detail) +
  plot_layout(widths = c(1.6, 1), guides = "collect") +
  plot_annotation(
    title = "Neutral-Country Media: Starting Level and Drop (Probabilistic)",
    subtitle = paste("State-owned outlets in neutral countries start close to independent",
                     "outlets and far above the scale floor,\nso the absence of a drop is",
                     "not a floor or measurement artifact.")
  )

neutral_floor_graph

ggsave(plot = neutral_floor_graph,
       file.path(FIGURES_DIFF_DISC_PROB, "neutral_floor_side_by_side.png"),
       width = 13, height = 6.5, dpi = 300)
```

## Matching

### Initial Match

```{r matching-h2-prob}
# Subset to data of interest (non-military, optimal bandwidth)
matching_data <- optimal_bandwidth_data_non_nato %>%
  select(sentiment_clean, sentiment_z, running, running_probabilistic, treatment, state_owned,
         topic_clean, source_domain, country)

# Match on topic and publication day
ps_model <- matchit(
  state_owned ~ running + topic_clean,
  data = matching_data,
  method = "exact",
  ratio = 1,
)

summary(ps_model)
```

### Assess Balance

```{r balance-h2-prob}
# Numerical balance check
bal.tab(ps_model, un = TRUE, stats = c("m", "v"), thresholds = c(m = 0.1))

# Love plot (publication quality)
love <- love.plot(ps_model, binary = "std", thresholds = c(m = 0.1))

ggsave(plot = love,
       file.path(FIGURES_DIFF_DISC_PROB, "love_balance_state_owned.png"),
       width = 10, height = 7)
```

### Matching Analysis

```{r matched-model-h2-prob}
# Extract matched data and calculate treatment effects
matched_data <- match.data(ps_model)

matched_model <- feols(sentiment_clean ~ running_probabilistic
                                     * treatment * state_owned |
                                       topic_clean + source_domain,
                                     cluster = ~source_domain,
                                     data = matched_data
                                     )

summary(matched_model)

# Wild cluster bootstrap for matched model
boot_matched_model <- run_wild_bootstrap(matched_model, "treatment:state_owned")
cat("Bootstrap SE for treatment:state_owned:", boot_matched_model$se, "\n")
cat("Bootstrap p-value:", boot_matched_model$p_val, "\n")

# Z-score matched model
matched_model_z <- feols(sentiment_z ~ running_probabilistic * treatment * state_owned |
                          topic_clean,
                          cluster = ~source_domain, data = matched_data)

# Wild cluster bootstrap for matched model
boot_matched_model_z <- run_wild_bootstrap(matched_model_z, "treatment:state_owned")
cat("Bootstrap SE for treatment:state_owned:", boot_matched_model_z$se, "\n")
cat("Z-score matched model — Bootstrap p-value:", boot_matched_model_z$p_val, "\n")
```

## Total Effect (No Topic Adjustment)

The H2 result the paper leads with is **Table 2 Model 5** (`model2d_z`): the
non-NATO sample with topic fixed effects. Its sample descends from
`data_non_mil`, so it also **omits military coverage** — Model 5 inherits Model
4's military exclusion and then drops the NATO countries.

That matters for a total effect. Conditioning on topic measures how state and
independent outlets diverged *within* topics; the total effect lets the topic mix
move too, which is what a reader actually experiences. But the single largest
compositional shift after the invasion is toward military coverage, so a total
effect estimated on a military-excluded sample would omit most of the channel it
is meant to capture. The total effect is therefore estimated on the full non-NATO
sample, all topics included.

Because that changes the sample as well as the fixed effects, a like-for-like
comparator is needed: the same full non-NATO all-topics sample **with** topic
fixed effects. Three objects are built here, and they are reported together in
appendix table S14b:

1. `model2d_z_alltopic` — non-NATO, all topics, topic FE (the comparator);
2. `model2d_z` — non-NATO, military omitted, topic FE (the main specification,
   estimated above);
3. `model2d_z_total` — non-NATO, all topics, no topic FE (the total effect).

The outcome for the all-topics objects is `data_non_ukraine`'s source-level
z-score, computed over the full window on all topics. This is the correct
analogue of Model 5's outcome: the non-military branch re-standardizes because
its sample changed, whereas the all-topics sample is the original one.

```{r model2d-total-prob}
# Non-NATO, all topics. Following `non-nato-prob`, but without the upstream
# military filter, so this branches from data_non_ukraine rather than data_non_mil.
data_non_nato_alltopic <- data_non_ukraine %>%
  filter(!country %in% NATO_COUNTRIES)

cat("Non-NATO, all topics:", nrow(data_non_nato_alltopic), "articles\n")

# --- Comparator: same sample as the total effect, but topic-adjusted ---------
# Following `non-nato-prob` (z-score variant): residualize on the model's own FE
# structure, then select the MSE-optimal bandwidth.
resid_y_alltopic <- feols(sentiment_z ~ 1 | topic_clean + state_owned,
                          data = data_non_nato_alltopic)$residuals

bw_alltopic <- rdbwselect(y = resid_y_alltopic,
                          x = data_non_nato_alltopic$running_probabilistic,
                          kernel = "triangular",
                          cluster = data_non_nato_alltopic$source_domain,
                          p = 1,
                          bwselect = "mserd")

optimal_bw_alltopic <- bw_alltopic$bws[1, 1]
cat("All-topics (topic-adjusted) optimal bandwidth:",
    round(optimal_bw_alltopic, 1), "days\n")

optimal_bandwidth_data_alltopic <- data_non_nato_alltopic %>%
  filter(running_probabilistic < optimal_bw_alltopic,
         running_probabilistic > -optimal_bw_alltopic) %>%
  droplevels()

model2d_z_alltopic <- feols(sentiment_z ~ running_probabilistic * treatment * state_owned |
                              topic_clean,
                            cluster = ~source_domain,
                            data = optimal_bandwidth_data_alltopic)

summary(model2d_z_alltopic)

boot_model2d_z_alltopic <- run_wild_bootstrap(model2d_z_alltopic, "treatment:state_owned")
cat("Bootstrap p-value (all topics, topic-adjusted):",
    boot_model2d_z_alltopic$p_val, "\n")

# --- Total effect: same sample, topic dropped from model and bandwidth -------
resid_y_total <- feols(sentiment_z ~ 1 | state_owned,
                       data = data_non_nato_alltopic)$residuals

bw_select_total <- rdbwselect(y = resid_y_total,
                              x = data_non_nato_alltopic$running_probabilistic,
                              kernel = "triangular",
                              cluster = data_non_nato_alltopic$source_domain,
                              p = 1,
                              bwselect = "mserd")

optimal_bw_total <- bw_select_total$bws[1, 1]
cat("Total-effect optimal bandwidth:", round(optimal_bw_total, 1), "days\n")

optimal_bandwidth_data_total <- data_non_nato_alltopic %>%
  filter(running_probabilistic < optimal_bw_total,
         running_probabilistic > -optimal_bw_total) %>%
  droplevels()

model2d_z_total <- feols(sentiment_z ~ running_probabilistic * treatment * state_owned,
                         cluster = ~source_domain,
                         data = optimal_bandwidth_data_total)

summary(model2d_z_total)

boot_model2d_z_total <- run_wild_bootstrap(model2d_z_total, "treatment:state_owned")
cat("Bootstrap p-value (total):", boot_model2d_z_total$p_val, "\n")

cat("\nH2 total-effect comparison (treatment:state_owned):\n")
cat("  all topics, topic FE :", round(coef(model2d_z_alltopic)[["treatment:state_owned"]], 4),
    " N", nobs(model2d_z_alltopic), "\n")
cat("  main (Model 5)       :", round(coef(model2d_z)[["treatment:state_owned"]], 4),
    " N", nobs(model2d_z), "\n")
cat("  total (no topic FE)  :", round(coef(model2d_z_total)[["treatment:state_owned"]], 4),
    " N", nobs(model2d_z_total), "\n")
```

## Country-Level Clustering Check

The headline H2 inference clusters at the source level. Sources are nested within
countries, so if the invasion shifted coverage country-wide the source-level
bootstrap understates the true uncertainty. This chunk re-runs the same WCR
bootstrap clustered by country for the two H2 RDIDs the paper reports (the
optimal-bandwidth interaction and the matched interaction), and reports both
levels side by side. Point estimates are unchanged by construction -- clustering
affects inference only -- so any divergence in the estimate column would mean the
sample silently changed and must be investigated, not reported.

```{r country-cluster-check-h2-prob}
# Drop unused factor levels before bootstrapping: boottest() errors on cluster
# levels with no observations. This cannot move the estimate, since country
# enters neither the formula nor the fixed effects (asserted below).
optimal_bandwidth_data_z_dl <- droplevels(optimal_bandwidth_data_z)
matched_data_dl             <- droplevels(matched_data)

model2a_opt_z_dl <- feols(sentiment_z ~ running_probabilistic * treatment * state_owned |
                            topic_clean,
                          cluster = ~source_domain, data = optimal_bandwidth_data_z_dl)
matched_model_z_dl <- feols(sentiment_z ~ running_probabilistic * treatment * state_owned |
                              topic_clean,
                            cluster = ~source_domain, data = matched_data_dl)

stopifnot(
  isTRUE(all.equal(coef(model2a_opt_z_dl)[["treatment:state_owned"]],
                   coef(model2a_opt_z)[["treatment:state_owned"]], tolerance = 0)),
  isTRUE(all.equal(coef(matched_model_z_dl)[["treatment:state_owned"]],
                   coef(matched_model_z)[["treatment:state_owned"]], tolerance = 0))
)

country_cluster_check <- bind_rows(
  compare_cluster_levels(model2a_opt_z_dl, "treatment:state_owned", "H2_headline"),
  compare_cluster_levels(matched_model_z_dl, "treatment:state_owned", "H2_matched")
)

print(as.data.frame(country_cluster_check), row.names = FALSE, digits = 4)
```

## Sensitivity Analysis (OVB)

```{r sensitivity-h2-prob}
# Save the bootstrapped p-val
bootstrapped_se <- boot_matched_model$se

# Respecify the model using lm
lm_model <- lm(sentiment_z ~ running_probabilistic * treatment * state_owned +
                 factor(topic_clean),
               data = matched_data)


# Sensitivity analysis
sensitivity <- sensemakr(
  model = lm_model,
  treatment = "treatment:state_owned",
  benchmark_covariates = c("treatment"),
  kd = 1,
  ky = 1,
  reduce = TRUE
)

# Extract coefficient and bootstrapped SE
coef_interest <- coef(lm_model)["treatment:state_owned"]
boot_se <- boot_matched_model$se
dof <- df.residual(lm_model)

# Corrected t-stat using bootstrapped SE
t_corrected <- coef_interest / boot_se

# Compute robustness values using corrected t-stat
rv_point <- sensemakr::robustness_value(t_statistic = t_corrected, dof = dof, q = 1)
rv_alpha <- sensemakr::robustness_value(t_statistic = t_corrected, dof = dof, q = 1, alpha = 0.05)

cat("RV (q=1):", rv_point, "\n")
cat("RV (q=1, alpha=0.05):", rv_alpha, "\n")
```

```{r sensitivity-r2-h2-prob}
partial_r2(lm_model, covariates = c("running_probabilistic:treatment",
                                     "running_probabilistic:state_owned",
                                     "treatment",
                                     "state_owned"))

treatment_r2 <- partial_r2(lm_model, covariates = c("treatment"))
```

```{r}
cat("RV:", rv_point, "\n")
cat("Treatment partial R²:", treatment_r2, "\n")
cat("RV is", round(rv_point / treatment_r2, 1), "x the strongest observed covariate\n")

```


```{r sensitivity-plot-h2-prob, fig.width=10, fig.height=7}
# Sensitivity Plot

# Extract the data sensemakr uses for the plot
ovb_contour_data <- function(sensitivity, lim = 0.005, custom_se=NULL) {
  
  # Grid of r2dz.x and r2yz.dx values
  r2dz <- seq(0, lim, length.out = 400)
  r2yz <- seq(0, lim, length.out = 400)
  grid <- expand.grid(r2dz.x = r2dz, r2yz.dx = r2yz)
  
  # Extract key stats
  estimate <- sensitivity$sensitivity_stats$estimate
  se <- if (!is.null(custom_se)) custom_se else sensitivity$sensitivity_stats$se
  df <- sensitivity$sensitivity_stats$dof
  
  # Compute adjusted estimate across grid
  grid$adjusted <- mapply(function(r2dz, r2yz) {
    sensemakr::adjusted_estimate(
      estimate = estimate,
      se = se,
      dof = df,
      r2dz.x = r2dz,
      r2yz.dx = r2yz
    )
  }, grid$r2dz.x, grid$r2yz.dx)
  
  return(grid)
}

# Extract benchmark points
benchmark_df <- data.frame(
  r2dz.x = sensitivity$bounds$r2dz.x,
  r2yz.dx = sensitivity$bounds$r2yz.dx,
  label = sensitivity$bounds$bound_label
)

# Build contour data
# Extract actual estimate
unadj_est <- round(sensitivity$sensitivity_stats$estimate, 2)

# Build contour data
contour_data <- ovb_contour_data(sensitivity, lim = 0.35, custom_se = boot_se)

sensitivity_plot <- ggplot(contour_data, aes(x = r2dz.x, y = r2yz.dx, z = adjusted)) +
  geom_contour(colour = "grey60",
               breaks = c(-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4)) +
  geom_contour(breaks = 0,
               colour = "red",
               linetype = "dashed",
               linewidth = 0.8) +
  geom_point(data = benchmark_df,
             aes(x = r2dz.x, y = r2yz.dx),
             shape = 18, colour = "red", size = 3,
             inherit.aes = FALSE) +
  annotate("point", x = 0, y = 0, shape = 17, size = 3) +
  annotate("text", x = 0.005, y = 0.005,
           label = paste0("Unadjusted (", unadj_est, ")"),
           size = 4, hjust = 0, vjust = 0) +
  annotate("text",
           x = benchmark_df$r2dz.x[1] + 0.005,
           y = benchmark_df$r2yz.dx[1] + 0.003,
           label = "Treatment",
           size = 4, hjust = 0) +
  coord_cartesian(xlim = c(0, 0.35), ylim = c(0, 0.1)) +
  scale_x_continuous(breaks = seq(0, 0.35, by = 0.05),
                     labels = scales::number_format(accuracy = 0.01)) +
  scale_y_continuous(breaks = seq(0, 0.1, by = 0.02),
                     labels = scales::number_format(accuracy = 0.01)) +
  labs(
    x = "Partial R² of Confounder with Treatment * State-Owned",
    y = "Partial R² of Confounder with Sentiment",
    title = "Sensitivity to Unobserved Confounding, State-Owned Affiliation",
    subtitle = "Red dashed line indicates where estimate = 0"
  ) +
  theme_bw() +
  theme(
    panel.grid.minor = element_blank(),
    plot.title = element_text(face = "bold"),
    legend.position = "none"
  )

sensitivity_plot

ggsave(plot = sensitivity_plot,
       file.path(FIGURES_DIFF_DISC_PROB, "sensitivity_ovb_state_owned.png"),
       width = 10, height = 7)
```


```{r}
# At treatment's actual partial R² with CSTO, what partial R² with sentiment
# would a confounder need to nullify the estimate?
est <- sensitivity$sensitivity_stats$estimate
se <- boot_se
dof <- sensitivity$sensitivity_stats$dof
bm_r2dz <- benchmark_df$r2dz.x[1]  # 0.565

f <- function(r2yz) {
  sensemakr::adjusted_estimate(
    estimate = est, se = se, dof = dof,
    r2dz.x = bm_r2dz,
    r2yz.dx = r2yz
  )
}

r2yz_needed <- uniroot(f, interval = c(0, 0.9999))$root
bm_r2yz <- benchmark_df$r2yz.dx[1]  # 0.001

cat("Treatment's actual R²yz:", round(bm_r2yz, 5), "\n")
cat("R²yz needed to nullify at treatment's R²dz:", round(r2yz_needed, 5), "\n")
cat("Multiplier:", round(r2yz_needed / bm_r2yz, 1), "x treatment's R²yz\n")
```

## Leave-One-Out Matching Robustness

```{r matched-loo-prob}
countries_match <- unique(data_non_mil %>%
  filter(running_probabilistic < optimal_bw, running_probabilistic > -optimal_bw) %>%
  pull(country))

matched_loo_results <- list()

for (cntry in countries_match) {
  data_loo_m <- data_non_mil %>%
    filter(country != cntry) %>%
    select(sentiment_clean, sentiment_z, running, running_probabilistic, treatment, state_owned,
           topic_clean, source_domain, country)

  # Re-calculate optimal bandwidth for LOO data
  bw_loo_m <- tryCatch({
    resid_y_loo_m <- feols(sentiment_z ~ 1 | topic_clean + state_owned,
                           data = data_loo_m)$residuals
    rdbwselect(y = resid_y_loo_m,
               x = data_loo_m$running_probabilistic,
               kernel = "triangular",
               cluster = data_loo_m$source_domain,
               p = 1,
               bwselect = "mserd")
  }, error = function(e) NULL)

  if (is.null(bw_loo_m)) {
    matched_loo_results[[cntry]] <- list(
      model = NULL, bandwidth = NA, n = NA,
      country_dropped = cntry, boot_p_val = NA, boot_se = NA
    )
    next
  }

  optimal_bw_loo_m <- bw_loo_m$bws[1, 1]

  data_loo_bw_m <- data_loo_m %>%
    filter(running_probabilistic < optimal_bw_loo_m, running_probabilistic > -optimal_bw_loo_m)

  ps_model_loo <- tryCatch(
    matchit(
      state_owned ~ running + topic_clean,
      data = data_loo_bw_m,
      method = "exact",
      ratio = 1
    ),
    error = function(e) NULL
  )

  if (is.null(ps_model_loo)) {
    matched_loo_results[[cntry]] <- list(
      model = NULL, bandwidth = optimal_bw_loo_m, n = NA,
      country_dropped = cntry, boot_p_val = NA, boot_se = NA
    )
    next
  }

  matched_data_loo <- match.data(ps_model_loo)

  matched_model_loo <- feols(sentiment_z ~ running_probabilistic
                               * treatment * state_owned |
                                 topic_clean + source_domain,
                             cluster = ~source_domain,
                             data = matched_data_loo)

  matched_boot_loo <- tryCatch(
    run_wild_bootstrap(matched_model_loo, "treatment:state_owned", B = 4999),
    error = function(e) list(se = NA, p_val = NA, ci_lower = NA, ci_upper = NA, t_stat = NA)
  )

  matched_loo_results[[cntry]] <- list(
    model = matched_model_loo,
    bandwidth = optimal_bw_loo_m,
    n = nrow(matched_data_loo),
    country_dropped = cntry,
    boot_p_val = matched_boot_loo$p_val,
    boot_se = matched_boot_loo$se
  )
}

# Extract key coefficient (treatment:state_owned interaction)
matched_loo_summary <- map_df(names(matched_loo_results), function(cntry) {
  res <- matched_loo_results[[cntry]]
  if (is.null(res$model)) {
    return(tibble(
      country_dropped = cntry,
      estimate = NA_real_,
      std_error = NA_real_,
      p_value = NA_real_,
      n_obs = NA_real_,
      bandwidth = res$bandwidth
    ))
  }
  mod <- res$model
  tibble(
    country_dropped = cntry,
    estimate = coef(mod)["treatment:state_owned"],
    std_error = se(mod)["treatment:state_owned"],
    p_value = pvalue(mod)["treatment:state_owned"],
    n_obs = res$n,
    bandwidth = res$bandwidth
  )
})

print(matched_loo_summary)
```


### Saturated Model

```{r saturated-model-prob}
model3a_opt_saturated <- feols(sentiment_clean ~ running_probabilistic * treatment * state_owned |
                          source_domain^topic_clean + topic_clean^treatment,
                          cluster = ~source_domain,
                          data = optimal_bandwidth_data_russian)

summary(model3a_opt_saturated)

# Wild cluster bootstrap for saturated model
#boot_model3a_opt_saturated <- run_wild_bootstrap(model3a_opt_saturated, "treatment:state_owned")
#cat("Bootstrap SE for treatment:state_owned:", boot_model3a_opt_saturated$se, "\n")
#cat("Bootstrap p-value:", boot_model3a_opt_saturated$p_val, "\n")
```



# Summary Tables

## Table 2I: Main Results (8 columns)

```{r table2i-prob}
note_text <- "All standard errors are clustered at the source level. (1) Full data, topic FEs. (2) Full data, topic + source FEs. (3) Optimal bandwidth, topic FEs. (4) Optimal bandwidth, topic + source FEs. (5) Non-military topics, topic FEs. (6) Non-NATO countries, topic FEs. (7) Russian-related articles, combined bandwidth. (8) Saturated model with source-topic and topic-treatment FEs."
note_wrapped <- str_wrap(note_text, width = 80)

table_2i <- modelsummary(
  list(
    "(1)" = model2a,
    "(2)" = model2a_full,
    "(3)" = model2a_opt,
    "(4)" = model2a_opt_full_fe,
    "(5)" = model2b,
    "(6)" = model2d,
    "(7)" = model3a_opt,
    "(8)" = model3a_opt_saturated
  ),
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors",
  title = "Hypothesis 2: Difference in Discontinuity Analysis (Probabilistic Time Assignment)",
  notes = note_wrapped
)

table_2i
```

## Table 2I-S: Supplemental

```{r table2i-supplemental-prob}
note_text_s <- "All standard errors are clustered at the source level. (1) Non-military topics, topic + source FEs. (2) Russian-related articles, combined bandwidth, topic + source FEs."
note_wrapped_s <- str_wrap(note_text_s, width = 80)

table_2i_supplemental <- modelsummary(
  list(
    "(1)" = model2b_full_fe,
    "(2)" = model3a_opt_full_fe
  ),
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors",
  title = "Hypothesis 2 Supplemental: Full FE Models (Probabilistic Time Assignment)",
  notes = note_wrapped_s
)

table_2i_supplemental
```

## Table 2I: By Topic (Optimal Bandwidth)

```{r table2i-topic-opt-prob}
rows_topic <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-'
)
attr(rows_topic, 'position') <- c(5, 6, 7)

note_topic_opt <- "All standard errors are clustered at the source level. Each model uses a per-topic re-optimized bandwidth with country fixed effects."
note_topic_opt_wrapped <- str_wrap(note_topic_opt, width = 80)

table_2i_topic_opt <- modelsummary(
  list("Political" = model2a_opt_pol, "Military" = model2a_opt_mil,
       "Economic" = model2a_opt_econ, "Cultural" = model2a_opt_cult, "Other" = model2a_opt_oth),
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors",
  title = "Hypothesis 2: Diff-in-Disc By Topic, Z-Scored Sentiment (Per-Topic Optimal Bandwidth, Probabilistic Time Assignment)",
  add_rows = rows_topic,
  notes = note_topic_opt_wrapped
)

table_2i_topic_opt
```

## Table 2I: By Topic (Full Data)

```{r table2i-topic-full-prob}
note_topic_full <- "All standard errors are clustered at the source level. Each model uses the full dataset (no bandwidth restriction) with country fixed effects."
note_topic_full_wrapped <- str_wrap(note_topic_full, width = 80)

table_2i_topic_full <- modelsummary(
  list("Political" = model2a_full_pol, "Military" = model2a_full_mil,
       "Economic" = model2a_full_econ, "Cultural" = model2a_full_cult, "Other" = model2a_full_oth),
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors",
  title = "Hypothesis 2: Diff-in-Disc By Topic, Z-Scored Sentiment (Full Data, Probabilistic Time Assignment)",
  add_rows = rows_topic,
  notes = note_topic_full_wrapped
)

table_2i_topic_full
```


# Save Results

```{r save-prob}
results_h2_prob <- list(
  # Main models
  model2a = model2a,
  model2a_full = model2a_full,
  model2a_opt = model2a_opt,
  model2a_opt_full_fe = model2a_opt_full_fe,
  model2d = model2d,
  model2b = model2b,
  model2b_full_fe = model2b_full_fe,
  model3a_opt = model3a_opt,
  model3a_opt_full_fe = model3a_opt_full_fe,
  model3a_opt_saturated = model3a_opt_saturated,

  # DID within bandwidth
  model_did = model_did,

  # Placebo
  model_placebo = model4a,

  # Separate RDDs
  model2_state_rdd = model2_state_rdd,
  model2_ind_rdd = model2_ind_rdd,
  model2_state_rdd_z = model2_state_rdd_z,
  model2_ind_rdd_z = model2_ind_rdd_z,

  # By-topic (optimal BW)
  model2a_opt_pol = model2a_opt_pol,
  model2a_opt_mil = model2a_opt_mil,
  model2a_opt_econ = model2a_opt_econ,
  model2a_opt_cult = model2a_opt_cult,
  model2a_opt_oth = model2a_opt_oth,

  # By-topic (full data)
  model2a_full_pol = model2a_full_pol,
  model2a_full_mil = model2a_full_mil,
  model2a_full_econ = model2a_full_econ,
  model2a_full_cult = model2a_full_cult,
  model2a_full_oth = model2a_full_oth,

  # Z-score models
  model2a_z = model2a_z,
  model2a_opt_z = model2a_opt_z,
  model2b_z = model2b_z,
  model2d_z = model2d_z,
  model3a_z = model3a_z,

  # Matching
  matched_model = matched_model,
  matched_model_z = matched_model_z,

  # LOO robustness
  loo_results = loo_results,
  loo_summary = loo_summary,

  # Matched LOO robustness
  matched_loo_results = matched_loo_results,
  matched_loo_summary = matched_loo_summary,

  # Bootstrap SEs
  bootstrap_se = list(
    model2a = boot_model2a,
    model2a_full = boot_model2a_full,
    model2a_opt = boot_model2a_opt,
    model2a_opt_full_fe = boot_model2a_opt_full_fe,
    model2b = boot_model2b,
    model2b_full_fe = boot_model2b_full_fe,
    model2d = boot_model2d,
    model3a_opt = boot_model3a_opt,
    model3a_opt_full_fe = boot_model3a_opt_full_fe,
    #model3a_opt_saturated = boot_model3a_opt_saturated,
    model_did = boot_model_did,
    model_placebo = boot_model4a,
    model2d_z_alltopic = boot_model2d_z_alltopic,
    model2d_z_total = boot_model2d_z_total,
    matched_model = boot_matched_model,
    matched_model_z = boot_matched_model_z,
    # Topic models (optimal BW)
    model2a_opt_pol = boot_model2a_opt_pol,
    model2a_opt_mil = boot_model2a_opt_mil,
    model2a_opt_econ = boot_model2a_opt_econ,
    model2a_opt_cult = boot_model2a_opt_cult,
    model2a_opt_oth = boot_model2a_opt_oth,
    # Topic models (full data)
    model2a_full_pol = boot_model2a_full_pol,
    model2a_full_mil = boot_model2a_full_mil,
    model2a_full_econ = boot_model2a_full_econ,
    model2a_full_cult = boot_model2a_full_cult,
    model2a_full_oth = boot_model2a_full_oth,
    # Z-score models
    model2a_z = boot_model2a_z,
    model2a_opt_z = boot_model2a_opt_z,
    model2b_z = boot_model2b_z,
    model2d_z = boot_model2d_z,
    model3a_z = boot_model3a_z
  ),

  # Sensitivity
  sens_analysis = sensitivity,

  # Bandwidths
  optimal_bandwidth = optimal_bw,
  optimal_bandwidth_combined = optimal_bandwidth_data_non_nato,
  optimal_bw_pol = optimal_bw_pol,
  optimal_bw_mil = optimal_bw_mil,
  optimal_bw_econ = optimal_bw_econ,
  optimal_bw_cult = optimal_bw_cult,
  optimal_bw_oth = optimal_bw_oth,
  optimal_bw_placebo = optimal_bw_placebo,

  # Source- vs country-level WCR inference for the reported H2 RDIDs
  country_cluster_check = country_cluster_check,

  # Total effect at the Model-5 level, with its like-for-like all-topics
  # comparator (appendix S14b)
  model2d_z_alltopic = model2d_z_alltopic,
  model2d_z_total = model2d_z_total,
  optimal_bw_alltopic = optimal_bw_alltopic,
  optimal_bw_total = optimal_bw_total
)

saveRDS(results_h2_prob, file.path(DATA_INTERMEDIATE, "05_h2_results_prob.rds"))
cat("Results saved to:", file.path(DATA_INTERMEDIATE, "05_h2_results_prob.rds"), "\n")
```

# Session Info

```{r session-info-prob}
print_session_info()
```
