---
title: "05A - Difference-in-Discontinuities Analysis with Continuous Running Variable (Hypothesis 2)"
author: "Donald Moratz"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

# Overview

This script performs the Difference-in-Discontinuities analysis comparing state-owned vs independent media responses to the invasion, using time as a continuous running variable instead of by day.

**Inputs:**
- `data/intermediate/02_data_non_ukraine.rds`
- `data/intermediate/02_cleaned_data.rds`

**Outputs:**
- Diff-in-disc regression results (continuous)
- Visualizations
- Table 2A

```{r setup, include=FALSE}
source("00_setup.R")
knitr::opts_chunk$set(fig.path = paste0(FIGURES_DIFF_DISC_CONT, "/"))
```

# Load Data

```{r load}
data_non_ukraine <- readRDS(file.path(DATA_INTERMEDIATE, "02_data_non_ukraine.rds"))
data <- readRDS(file.path(DATA_INTERMEDIATE, "02_cleaned_data.rds"))

cat("Non-Ukraine sample:", nrow(data_non_ukraine), "articles\n")
cat("State-owned:", sum(data_non_ukraine$state_owned), "\n")
cat("Independent:", sum(data_non_ukraine$state_owned == 0), "\n")
```

# Main Diff-in-Disc Model

## Model 2a: Full Triple Interaction

```{r model2a}
model2a <- feols(sentiment_clean ~ running_continuous * treatment * state_owned | country + topic_clean,
                 cluster = ~source_domain,
                 data = data_non_ukraine)

summary(model2a)
```

## Effect Size Analysis

```{r effect-size-discs}
sd_sentiment_non_ukraine <- sd(data_non_ukraine$sentiment_clean)

cat("Standard deviation:", round(sd_sentiment_non_ukraine, 3), "\n\n")

# Effect on all media
coef_all <- model2a$coeftable["treatment", "Estimate"]
cat("Effect on all media (in SD):", round(coef_all / sd_sentiment_non_ukraine, 3), "\n")

# Effect on state media specifically
coef_state <- model2a$coeftable["treatment:state_owned", "Estimate"]
cat("Additional effect on state media (in SD):", round(coef_state / sd_sentiment_non_ukraine, 3), "\n")
```

# Visualization: Main Diff-in-Disc Plot

```{r plot-discs-cont, fig.width=10, fig.height=7}
# Aggregate data
agg_data_discs <- data_non_ukraine %>%
  group_by(running_continuous, state_owned) %>%
  summarize(
    sentiment_clean = mean(sentiment_clean, na.rm = TRUE),
    num_obs = n(),
    .groups = "drop"
  )

invasion_discs_graph <- data_non_ukraine %>%
  mutate(indicator = as.factor(indicator)) %>%
  mutate(indicator = fct_recode(indicator,
    "Ind. Pre." = "1",
    "State Pre." = "2",
    "Ind. Post" = "3",
    "State Post" = "4"
  )) %>%
  ggplot(aes(x = running_continuous, y = sentiment_clean, group = indicator, color = indicator)) +
  geom_point(data = agg_data_discs,
             aes(x = running_continuous, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = COLORS_DISCS, name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on Sentiment (Continuous)",
    subtitle = "Difference in Discontinuities",
    x = "Hours Pre/Post Invasion",
    y = "Sentiment"
  )

invasion_discs_graph

ggsave(plot = invasion_discs_graph,
       file.path(FIGURES_DIFF_DISC_CONT, "invasion_discs_graph_cont.png"),
       width = 10, height = 7)
```

# Optimal Bandwidth Selection

```{r optimal-bw}
data_non_ukraine <- data_non_ukraine %>%
  mutate(across(c("country", "source_domain", "topic_clean"), as.factor))

#covs_matrix <- model.matrix(~ country + topic_clean + state_owned - 1, data = data_non_ukraine)

bw_select <- rdbwselect(y = data_non_ukraine$sentiment_clean,
                        x = data_non_ukraine$running_continuous,
                        #covs = covs_matrix,
                        kernel = "triangular",
                        cluster = data_non_ukraine$source_domain,
                        p = 1,
                        bwselect = "mserd")

summary(bw_select)

optimal_bw <- bw_select$bws[1, 1]
cat("Optimal bandwidth:", round(optimal_bw, 1), "seconds\n")

optimal_bandwidth_data <- data_non_ukraine %>%
  filter(running_continuous < optimal_bw) %>%
  filter(running_continuous > -optimal_bw)

cat("Observations within bandwidth:", nrow(optimal_bandwidth_data), "\n")
```

## Model with Optimal Bandwidth

```{r model2a-opt}
model2a_opt <- feols(sentiment_clean ~ running_continuous * treatment * state_owned | country + topic_clean,
                     cluster = ~source_domain,
                     data = optimal_bandwidth_data)

summary(model2a_opt)
```

# Diff-in-Disc Models By Topic

## Full Data By Topic

```{r topic-full}
data_pol <- data_non_ukraine %>% filter(topic_clean == "Political")
data_mil <- data_non_ukraine %>% filter(topic_clean == "Military")
data_econ <- data_non_ukraine %>% filter(topic_clean == "Economic")
data_cult <- data_non_ukraine %>% filter(topic_clean == "Culture")
data_oth <- data_non_ukraine %>% filter(topic_clean == "Other")

model2a_full_pol <- feols(sentiment_clean ~ running_continuous * treatment * state_owned | country,
                          cluster = ~source_domain,
                          data = data_pol)
model2a_full_mil <- feols(sentiment_clean ~ running_continuous * treatment * state_owned | country,
                          cluster = ~source_domain,
                          data = data_mil)
model2a_full_econ <- feols(sentiment_clean ~ running_continuous * treatment * state_owned | country,
                           cluster = ~source_domain,
                           data = data_econ)
model2a_full_cult <- feols(sentiment_clean ~ running_continuous * treatment * state_owned | country,
                           cluster = ~source_domain,
                           data = data_cult)
model2a_full_oth <- feols(sentiment_clean ~ running_continuous * treatment * state_owned | country,
                          cluster = ~source_domain,
                          data = data_oth)
```

## Per-Topic Optimal Bandwidth

```{r topic-opt-bw}
# Political
bw_pol <- rdbwselect(y = data_pol$sentiment_clean, x = data_pol$running_continuous,
                     kernel = "triangular", cluster = data_pol$source_domain, p = 1, bwselect = "mserd")
optimal_bw_pol <- bw_pol$bws[1, 1]
cat("Political optimal bandwidth:", round(optimal_bw_pol, 1), "seconds\n")
opt_data_pol <- data_pol %>% filter(running_continuous < optimal_bw_pol, running_continuous > -optimal_bw_pol)

# Military
bw_mil <- rdbwselect(y = data_mil$sentiment_clean, x = data_mil$running_continuous,
                     kernel = "triangular", cluster = data_mil$source_domain, p = 1, bwselect = "mserd")
optimal_bw_mil <- bw_mil$bws[1, 1]
cat("Military optimal bandwidth:", round(optimal_bw_mil, 1), "seconds\n")
opt_data_mil <- data_mil %>% filter(running_continuous < optimal_bw_mil, running_continuous > -optimal_bw_mil)

# Economic
bw_econ <- rdbwselect(y = data_econ$sentiment_clean, x = data_econ$running_continuous,
                      kernel = "triangular", cluster = data_econ$source_domain, p = 1, bwselect = "mserd")
optimal_bw_econ <- bw_econ$bws[1, 1]
cat("Economic optimal bandwidth:", round(optimal_bw_econ, 1), "seconds\n")
opt_data_econ <- data_econ %>% filter(running_continuous < optimal_bw_econ, running_continuous > -optimal_bw_econ)

# Culture
bw_cult <- rdbwselect(y = data_cult$sentiment_clean, x = data_cult$running_continuous,
                      kernel = "triangular", cluster = data_cult$source_domain, p = 1, bwselect = "mserd")
optimal_bw_cult <- bw_cult$bws[1, 1]
cat("Culture optimal bandwidth:", round(optimal_bw_cult, 1), "seconds\n")
opt_data_cult <- data_cult %>% filter(running_continuous < optimal_bw_cult, running_continuous > -optimal_bw_cult)

# Other
bw_oth <- rdbwselect(y = data_oth$sentiment_clean, x = data_oth$running_continuous,
                     kernel = "triangular", cluster = data_oth$source_domain, p = 1, bwselect = "mserd")
optimal_bw_oth <- bw_oth$bws[1, 1]
cat("Other optimal bandwidth:", round(optimal_bw_oth, 1), "seconds\n")
opt_data_oth <- data_oth %>% filter(running_continuous < optimal_bw_oth, running_continuous > -optimal_bw_oth)
```

## Topic Models with Per-Topic Optimal Bandwidth

```{r topic-opt-models}
model2a_opt_pol <- feols(sentiment_clean ~ running_continuous * treatment * state_owned | country,
                         cluster = ~source_domain,
                         data = opt_data_pol)
summary(model2a_opt_pol)

model2a_opt_mil <- feols(sentiment_clean ~ running_continuous * treatment * state_owned | country,
                         cluster = ~source_domain,
                         data = opt_data_mil)
summary(model2a_opt_mil)

model2a_opt_econ <- feols(sentiment_clean ~ running_continuous * treatment * state_owned | country,
                          cluster = ~source_domain,
                          data = opt_data_econ)
summary(model2a_opt_econ)

model2a_opt_cult <- feols(sentiment_clean ~ running_continuous * treatment * state_owned | country,
                          cluster = ~source_domain,
                          data = opt_data_cult)
summary(model2a_opt_cult)

model2a_opt_oth <- feols(sentiment_clean ~ running_continuous * treatment * state_owned | country,
                         cluster = ~source_domain,
                         data = opt_data_oth)
summary(model2a_opt_oth)
```

# Robustness: Non-Military Topics

```{r non-mil}
data_non_mil <- data_non_ukraine %>%
  filter(!topic_clean %in% c("Military"))

model2b <- feols(sentiment_clean ~ running_continuous * treatment * state_owned | country + topic_clean,
                 cluster = ~source_domain,
                 data = data_non_mil)

summary(model2b)
```

## Visualization (Non-Military)

```{r plot-non-mil-cont, fig.width=10, fig.height=7}
agg_data_non_mil <- data_non_mil %>%
  group_by(running_continuous, state_owned) %>%
  summarize(sentiment_clean = mean(sentiment_clean), num_obs = n(), .groups = "drop")

invasion_discs_non_mil_graph <- data_non_mil %>%
  mutate(indicator = as.factor(indicator)) %>%
  mutate(indicator = fct_recode(indicator,
    "Ind. Pre." = "1",
    "State Pre." = "2",
    "Ind. Post" = "3",
    "State Post" = "4"
  )) %>%
  ggplot(aes(x = running_continuous, y = sentiment_clean, group = indicator, color = indicator)) +
  geom_point(data = agg_data_non_mil,
             aes(x = running_continuous, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = COLORS_DISCS, name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on Sentiment (Continuous)",
    subtitle = "Non-Military Topics",
    x = "Hours Pre/Post Invasion",
    y = "Sentiment"
  )

invasion_discs_non_mil_graph

ggsave(plot = invasion_discs_non_mil_graph,
       file.path(FIGURES_DIFF_DISC_CONT, "invasion_discs_non_mil_cont.png"),
       width = 10, height = 7)
```

# Robustness: Non-NATO Countries

```{r non-nato}
data_non_nato <- data_non_ukraine %>%
  filter(!country %in% NATO_COUNTRIES)

model2d <- feols(sentiment_clean ~ running_continuous * treatment * state_owned | country + topic_clean,
                 cluster = ~source_domain,
                 data = data_non_nato)

summary(model2d)
```

# Russian-Related Articles Only

```{r russian-related}
data_russian_related <- data %>%
  filter(!Russian.Involvement == "Not") %>%
  filter(!country %in% c("Ukraine")) %>%
  filter(!topic_clean %in% c("Military"))

model3a <- feols(sentiment_clean ~ running_continuous * treatment * state_owned | country + topic_clean,
                 cluster = ~source_domain,
                 data = data_russian_related)

summary(model3a)
```

# Robustness: Combined Filter with Re-Optimized Bandwidth

```{r combined-robust}
data_combined_filtered <- data %>%
  filter(!Russian.Involvement == "Not") %>%
  filter(!country %in% c("Ukraine")) %>%
  filter(!country %in% NATO_COUNTRIES) %>%
  filter(!topic_clean %in% c("Military"))

data_combined_filtered <- data_combined_filtered %>%
  mutate(across(c("country", "source_domain", "topic_clean"), as.factor))

bw_select_combined <- rdbwselect(y = data_combined_filtered$sentiment_clean,
                                  x = data_combined_filtered$running_continuous,
                                  kernel = "triangular",
                                  cluster = data_combined_filtered$source_domain,
                                  p = 1,
                                  bwselect = "mserd")

summary(bw_select_combined)

optimal_bw_combined <- bw_select_combined$bws[1, 1]
```


```{r combined-robust-model}
cat("Optimal bandwidth (combined filter):", round(optimal_bw_combined, 1), "seconds\n")

optimal_bw_combined_data <- data_combined_filtered %>%
  filter(running_continuous < optimal_bw_combined) %>%
  filter(running_continuous > -optimal_bw_combined)

cat("Observations within bandwidth:", nrow(optimal_bw_combined_data), "\n")

model3a_opt <- feols(sentiment_clean ~ running_continuous * treatment * state_owned | country + topic_clean,
                     cluster = ~source_domain,
                     data = optimal_bw_combined_data)

summary(model3a_opt)

# Saturated Model
model3a_opt_saturated <- feols(sentiment_clean ~ running_continuous * treatment * state_owned |
                          source_domain^topic_clean + country^state_owned + country^topic_clean^treatment,
                          cluster = ~source_domain,
                          data = optimal_bw_combined_data)

summary(model3a_opt_saturated)
```

# Diff-in-Diff (Within Bandwidth)

```{r did}
model_did <- feols(sentiment_clean ~ treatment * state_owned | country + topic_clean,
                   cluster = ~source_domain,
                   data = optimal_bandwidth_data)

summary(model_did)
```

# Placebo Test: December 7th Announcement (with Optimal Bandwidth)

```{r placebo}
data_dec <- data %>%
  filter(date_publish < "2022-02-19") %>%
  mutate(
    running_continuous = as.numeric(difftime(date_publish_continuous, as.POSIXct("2021-12-07 00:00:00", tz = "UTC"), units = "secs")),
    treatment = ifelse(date_publish_continuous < as.POSIXct("2021-12-07 00:00:00", tz = "UTC"), 0, 1)
  )

# Find optimal bandwidth for placebo
bw_placebo <- rdbwselect(y = data_dec$sentiment_clean,
                         x = data_dec$running_continuous,
                         kernel = "triangular",
                         cluster = data_dec$source_domain,
                         p = 1,
                         bwselect = "mserd")

optimal_bw_placebo <- bw_placebo$bws[1, 1]
cat("Placebo optimal bandwidth:", round(optimal_bw_placebo, 1), "seconds\n")

data_dec_bw <- data_dec %>%
  filter(running_continuous < optimal_bw_placebo, running_continuous > -optimal_bw_placebo)

model4a <- feols(sentiment_clean ~ running_continuous * treatment * state_owned | country + Topic,
                 cluster = ~source_domain,
                 data = data_dec_bw)

summary(model4a)
cat("\nNote: Non-significant treatment effect suggests parallel trends assumption holds.\n")
```

## Placebo Visualization

```{r placebo-plot-cont, fig.width=10, fig.height=7}
agg_data_dec <- data_dec %>%
  group_by(running_continuous, state_owned) %>%
  summarize(sentiment_clean = mean(sentiment_clean), num_obs = n(), .groups = "drop")

data_dec %>%
  mutate(indicator = as.factor(indicator)) %>%
  mutate(indicator = fct_recode(indicator,
    "Ind. Pre." = "1",
    "State Pre." = "2",
    "Ind. Post" = "3",
    "State Post" = "4"
  )) %>%
  ggplot(aes(x = running_continuous, y = sentiment_clean, group = indicator, color = indicator)) +
  geom_point(data = agg_data_dec,
             aes(x = running_continuous, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = COLORS_DISCS, name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Placebo Test: Effect of December 7th Announcement (Continuous)",
    subtitle = "Pre-Invasion Period Only",
    x = "Seconds Pre/Post Invasion",
    y = "Sentiment"
  )
```

# Summary Table (Table 2A)

```{r table2a}
rows <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6,
  'State FEs', 'X', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-', '-',
  'Topic FEs', 'X', 'X', 'X', 'X', 'X', 'X'
)
attr(rows, 'position') <- c(5, 6, 7)

note_text <- "All standard errors are clustered at the source level. Model 2 uses the optimal bandwidth. Model 3 omits NATO allies. Model 4 omits military-related articles. Model 5 uses only Russian-related articles. Model 6 combines all robustness filters (non-NATO, non-military, Russian-related) with a re-optimized bandwidth."
note_wrapped <- str_wrap(note_text, width = 80)

table_2a <- modelsummary(
  list(model2a, model2a_opt, model2d, model2b, model3a, model3a_opt),
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors",
  title = "Hypothesis 2: Difference in Discontinuity Analysis (Continuous Running Variable)",
  add_rows = rows,
  notes = note_wrapped
)

table_2a
```

## Summary Table: By Topic (Optimal Bandwidth)

```{r table2a-topic-opt}
rows_topic <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-'
)
attr(rows_topic, 'position') <- c(5, 6, 7)

note_topic_opt <- "All standard errors are clustered at the source level. Each model uses a per-topic re-optimized bandwidth with country fixed effects."
note_topic_opt_wrapped <- str_wrap(note_topic_opt, width = 80)

table_2a_topic_opt <- modelsummary(
  list("Political" = model2a_opt_pol, "Military" = model2a_opt_mil,
       "Economic" = model2a_opt_econ, "Cultural" = model2a_opt_cult, "Other" = model2a_opt_oth),
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors",
  title = "Hypothesis 2: Diff-in-Disc By Topic (Per-Topic Optimal Bandwidth, Continuous)",
  add_rows = rows_topic,
  notes = note_topic_opt_wrapped
)

table_2a_topic_opt
```

## Summary Table: By Topic (Full Data)

```{r table2a-topic-full}
note_topic_full <- "All standard errors are clustered at the source level. Each model uses the full dataset (no bandwidth restriction) with country fixed effects."
note_topic_full_wrapped <- str_wrap(note_topic_full, width = 80)

table_2a_topic_full <- modelsummary(
  list("Political" = model2a_full_pol, "Military" = model2a_full_mil,
       "Economic" = model2a_full_econ, "Cultural" = model2a_full_cult, "Other" = model2a_full_oth),
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors",
  title = "Hypothesis 2: Diff-in-Disc By Topic (Full Data, Continuous)",
  add_rows = rows_topic,
  notes = note_topic_full_wrapped
)

table_2a_topic_full
```

# State-Owned and Independent Media Separate RDDs

These analyses mirror the CSTO-only / Neutral-only separate RDDs in the
heterogeneity analysis (file 06), but applied to state vs independent media
within the diff-in-disc framework (continuous running variable).

## State-Owned Media Only RDD

```{r state-only-rdd-cont}
data_state_only <- data_non_ukraine %>%
  filter(state_owned == 1) %>%
  filter(!topic_clean %in% "Military")

covs_state <- model.matrix(~ source_domain + topic_clean - 1, data = data_state_only)

model2_state_rdd <- rdrobust(
  y = data_state_only$sentiment_clean,
  x = data_state_only$running_continuous,
  covs = covs_state,
  cluster = data_state_only$source_domain
)

cat("State-Owned Media Only RDD (Continuous)\n")
summary(model2_state_rdd)
cat("N (state-owned, non-military):", nrow(data_state_only), "\n")
cat("Unique clusters:", length(unique(data_state_only$source_domain)), "\n")
```

## Independent Media Only RDD

```{r ind-only-rdd-cont}
data_ind_only <- data_non_ukraine %>%
  filter(state_owned == 0) %>%
  filter(!topic_clean %in% "Military")

covs_ind <- model.matrix(~ source_domain + topic_clean - 1, data = data_ind_only)

model2_ind_rdd <- rdrobust(
  y = data_ind_only$sentiment_clean,
  x = data_ind_only$running_continuous,
  covs = covs_ind,
  cluster = data_ind_only$source_domain
)

cat("Independent Media Only RDD (Continuous)\n")
summary(model2_ind_rdd)
cat("N (independent, non-military):", nrow(data_ind_only), "\n")
cat("Unique clusters:", length(unique(data_ind_only$source_domain)), "\n")
```

# Save Results

```{r save}
results_h2_cont <- list(
  model2a = model2a,
  model2a_opt = model2a_opt,
  model2d = model2d,
  model2b = model2b,
  model3a = model3a,
  model3a_opt = model3a_opt,
  model3a_opt_saturated = model3a_opt_saturated,
  model_did = model_did,
  model_placebo = model4a,
  model2a_opt_pol = model2a_opt_pol,
  model2a_opt_mil = model2a_opt_mil,
  model2a_opt_econ = model2a_opt_econ,
  model2a_opt_cult = model2a_opt_cult,
  model2a_opt_oth = model2a_opt_oth,
  model2a_full_pol = model2a_full_pol,
  model2a_full_mil = model2a_full_mil,
  model2a_full_econ = model2a_full_econ,
  model2a_full_cult = model2a_full_cult,
  model2a_full_oth = model2a_full_oth,
  # State-only and independent-only RDDs (cluster-robust SEs via rdrobust)
  model2_state_rdd = model2_state_rdd,
  model2_ind_rdd = model2_ind_rdd,
  optimal_bandwidth = optimal_bw,
  optimal_bandwidth_combined = optimal_bw_combined,
  optimal_bw_pol = optimal_bw_pol,
  optimal_bw_mil = optimal_bw_mil,
  optimal_bw_econ = optimal_bw_econ,
  optimal_bw_cult = optimal_bw_cult,
  optimal_bw_oth = optimal_bw_oth,
  optimal_bw_placebo = optimal_bw_placebo
)

saveRDS(results_h2_cont, file.path(DATA_INTERMEDIATE, "05_h2_results_continuous.rds"))
cat("Results saved to:", file.path(DATA_INTERMEDIATE, "05_h2_results_continuous.rds"), "\n")
```

# Session Info

```{r session-info}
print_session_info()
```
