---
title: "05d - Difference-in-Discontinuities Analysis with Drop No-Time Articles (Hypothesis 2)"
author: "Donald Moratz"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

# Overview

This script performs the Difference-in-Discontinuities analysis comparing state-owned vs independent media responses to the invasion, using a probabilistic time assignment for the running variable.

**Inputs:**
- `data/intermediate/02_data_non_ukraine.rds`
- `data/intermediate/02_cleaned_data.rds`

**Outputs:**
- Diff-in-disc regression results (probabilistic)
- Visualizations
- Table 2I

```{r setup-drop, include=FALSE}
source("00_setup.R")
knitr::opts_chunk$set(fig.path = paste0(FIGURES_DIFF_DISC_DROP, "/"))

set.seed(3184)
```

# Load Data

```{r load-drop}
data_non_ukraine <- readRDS(file.path(DATA_INTERMEDIATE, "02_data_non_ukraine.rds"))
data <- readRDS(file.path(DATA_INTERMEDIATE, "02_cleaned_data.rds"))

data_non_ukraine <- data_non_ukraine %>% filter(has_time == TRUE)
cat("Non-Ukraine sample after dropping no-time articles:", nrow(data_non_ukraine), "articles\n")

data <- data %>% filter(has_time == TRUE)
cat("Full sample after dropping no-time articles:", nrow(data), "articles\n")


cat("Non-Ukraine sample:", nrow(data_non_ukraine), "articles\n")
cat("State-owned:", sum(data_non_ukraine$state_owned), "\n")
cat("Independent:", sum(data_non_ukraine$state_owned == 0), "\n")

# Convert factors
data_non_ukraine <- data_non_ukraine %>%
  mutate(across(c("country", "source_domain", "topic_clean"), as.factor))%>%
  drop_na()%>%
  droplevels()

data <- data %>%
  mutate(across(c("country", "source_domain", "topic_clean"), as.factor))%>%
  droplevels()

# Compute z-scored sentiment within source_domain
data_non_ukraine <- data_non_ukraine %>%
  group_by(source_domain) %>%
  filter(sd(sentiment_clean, na.rm = TRUE) > 0) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                       sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()%>%
  droplevels()

data <- data %>%
  group_by(source_domain) %>%
  filter(sd(sentiment_clean, na.rm = TRUE) > 0) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                       sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()%>%
  droplevels()

# Convert running variable from seconds to days
data_non_ukraine <- data_non_ukraine %>%
  mutate(running_continuous = running_continuous / 86400)

data <- data %>%
  mutate(running_continuous = running_continuous / 86400)
```

# Separate RDDs by Media Type

These analyses mirror the CSTO-only / Neutral-only separate RDDs in the
heterogeneity analysis (file 06), but applied to state vs independent media.

## State-Owned Media Only (RDD)

```{r state-only-rdd-drop}
# Filter to state-owned media only
data_state_only <- data_non_ukraine %>%
  filter(state_owned == 1) %>%
  filter(!topic_clean %in% "Military")%>%
  droplevels()

cat("N (state-owned, non-military):", nrow(data_state_only), "\n")
cat("Unique clusters:", length(unique(data_state_only$source_domain)), "\n")

model2_state_rdd_z <- rdrobust(
  y = data_state_only$sentiment_z,
  x = data_state_only$running_continuous,
  covs = model.matrix(~ topic_clean - 1, data = data_state_only),
  cluster = data_state_only$source_domain, kernel = "triangular", p = 1
)

cat("State-Owned Media Only RDD — Z-score (Drop No-Time)\n")
summary(model2_state_rdd_z)
```

## Independent Media Only (RDD)

```{r ind-only-rdd-drop}
# Filter to independent media only
data_ind_only <- data_non_ukraine %>%
  filter(state_owned == 0) %>%
  filter(!topic_clean %in% "Military")%>%
  droplevels()

cat("N (independent, non-military):", nrow(data_ind_only), "\n")
cat("Unique clusters:", length(unique(data_ind_only$source_domain)), "\n")

model2_ind_rdd_z <- rdrobust(
  y = data_ind_only$sentiment_z,
  x = data_ind_only$running_continuous,
  covs = model.matrix(~ topic_clean - 1, data = data_ind_only),
  cluster = data_ind_only$source_domain, kernel = "triangular", p = 1
)

cat("Independent Media Only RDD — Z-score (Drop No-Time)\n")
summary(model2_ind_rdd_z)
```

# Diff-in-Disc Analysis


## Visualization: Main Diff-in-Disc Plot

```{r plot-discs-drop, fig.width=10, fig.height=7}
agg_data_discs <- data_non_ukraine %>%
  group_by(running_continuous, state_owned) %>%
  summarize(
    sentiment_clean = mean(sentiment_clean, na.rm = TRUE),
    num_obs = n(),
    .groups = "drop"
  )

invasion_discs_graph <- data_non_ukraine %>%
  mutate(indicator = as.factor(indicator)) %>%
  mutate(indicator = fct_recode(indicator,
    "Ind. Pre." = "1",
    "State Pre." = "2",
    "Ind. Post" = "3",
    "State Post" = "4"
  )) %>%
  ggplot(aes(x = running_continuous, y = sentiment_clean, group = indicator, color = indicator)) +
  geom_point(data = agg_data_discs,
             aes(x = running_continuous, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = COLORS_DISCS, name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on Sentiment (Drop No-Time Articles)",
    subtitle = "Difference in Discontinuities",
    x = "Days Pre/Post Invasion",
    y = "Sentiment"
  )

invasion_discs_graph

ggsave(plot = invasion_discs_graph,
       file.path(FIGURES_DIFF_DISC_DROP, "invasion_discs_graph_drop.png"),
       width = 10, height = 7)
```

## Optimal Bandwidth

### Optimal BW, Z-Score

```{r model2a-opt-drop-z}
# Residualize the dependent variable for fixed effects to do bandwidth selection
resid_y <- feols(sentiment_z ~ 1 | topic_clean + state_owned,
                 data = data_non_ukraine)$residuals

bw_select <- rdbwselect(y = resid_y,
                        x = data_non_ukraine$running_continuous,
                        kernel = "triangular",
                        cluster = data_non_ukraine$source_domain,
                        p = 1,
                        bwselect = "mserd")

optimal_bw_align <- bw_select$bws[1, 1]
cat("Optimal bandwidth:", round(optimal_bw_align, 1), "days\n")

optimal_bandwidth_data_z <- data_non_ukraine %>%
  filter(running_continuous < optimal_bw_align, running_continuous > -optimal_bw_align)%>%
  droplevels()


# Z-score version
model2a_opt_z <- feols(sentiment_z ~ running_continuous * treatment * state_owned | topic_clean,
                       cluster = ~source_domain,
                       data = optimal_bandwidth_data_z)
boot_model2a_opt_z <- run_wild_bootstrap(model2a_opt_z, "treatment:state_owned")
cat("Z-score model2a_opt_z — Bootstrap p-value:", boot_model2a_opt_z$p_val, "\n")
```


## Non-Military Topics

### Non-Military Sample

Military coverage moves for reasons unrelated to the signalling mechanism, so
Table 2 Model 4, the non-NATO model below and the matched model are all fitted
with it omitted. This chunk builds that sample; the bandwidth is re-selected on
it in the next chunk.

```{r non-mil-drop}
data_non_mil <- data_non_ukraine %>%
  filter(!topic_clean %in% c("Military"))%>%
  droplevels()

cat("Non-military sample:", nrow(data_non_mil), "articles\n")
```

### Non-Military, Z-Score

```{r non-mil-drop-z}
# Z-score version

# Create New z score
data_non_mil <- data_non_mil %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) / 
                   sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()%>%
  droplevels()

# Residualize the dependent variable for fixed effects to do bandwidth selection
resid_y <- feols(sentiment_z~ 1 | topic_clean + state_owned, 
                 data = data_non_mil)$residuals

bw_align_non_mil <- rdbwselect(y = resid_y,
                               x = data_non_mil$running_continuous,
                               kernel = "triangular",
                               cluster = data_non_mil$source_domain,
                               p = 1,
                               bwselect = "mserd")

optimal_bw_align_non_mil <- bw_align_non_mil$bws[1, 1]
cat("Optimal bandwidth (non-mil):", round(optimal_bw_align_non_mil, 1), "days\n")

optimal_bandwidth_data_non_mil <- data_non_mil %>%
  filter(running_continuous < optimal_bw_align_non_mil, running_continuous > -optimal_bw_align_non_mil)%>%
  droplevels()

model2b_z <- feols(sentiment_z ~ running_continuous * treatment * state_owned | topic_clean,
                   cluster = ~source_domain,
                   data = optimal_bandwidth_data_non_mil)
boot_model2b_z <- run_wild_bootstrap(model2b_z, "treatment:state_owned")
cat("Z-score model2b_z — Bootstrap p-value:", boot_model2b_z$p_val, "\n")
```


### Visualization (Non-Military)

```{r plot-non-mil-drop, fig.width=10, fig.height=7}
agg_data_non_mil <- data_non_mil %>%
  group_by(running_continuous, state_owned) %>%
  summarize(sentiment_clean = mean(sentiment_clean), num_obs = n(), .groups = "drop")

invasion_discs_non_mil_graph <- data_non_mil %>%
  mutate(indicator = as.factor(indicator)) %>%
  mutate(indicator = fct_recode(indicator,
    "Ind. Pre." = "1",
    "State Pre." = "2",
    "Ind. Post" = "3",
    "State Post" = "4"
  )) %>%
  ggplot(aes(x = running_continuous, y = sentiment_clean, group = indicator, color = indicator)) +
  geom_point(data = agg_data_non_mil,
             aes(x = running_continuous, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = COLORS_DISCS, name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on Sentiment (Drop No-Time Articles)",
    subtitle = "Non-Military Topics",
    x = "Days Pre/Post Invasion",
    y = "Sentiment"
  )

invasion_discs_non_mil_graph

ggsave(plot = invasion_discs_non_mil_graph,
       file.path(FIGURES_DIFF_DISC_DROP, "invasion_discs_non_mil_cont.png"),
       width = 10, height = 7)
```

## Non-NATO Countries

### Non-NATO Sample

Table 2 Model 5 narrows the non-military sample further to non-NATO countries,
dropping the states whose media had their own reasons to turn against the
invasion. This is also the sample the matched model is drawn from.

```{r non-nato-drop}
data_non_nato <- data_non_mil %>%
  filter(!country %in% NATO_COUNTRIES)%>%
  droplevels()

cat("Non-NATO, non-military sample:", nrow(data_non_nato), "articles\n")
```

```{r non-nato-drop-z}
# Z-score version

# Residualize the dependent variable for fixed effects to do bandwidth selection
resid_y <- feols(sentiment_z~ 1 | topic_clean + state_owned, 
                 data = data_non_nato)$residuals

bw_align_non_nato <- rdbwselect(y = resid_y,
                               x = data_non_nato$running_continuous,
                               kernel = "triangular",
                               cluster = data_non_nato$source_domain,
                               p = 1,
                               bwselect = "mserd")

optimal_bw_align_non_nato <- bw_align_non_nato$bws[1, 1]
cat("Optimal bandwidth (non-nato):", round(optimal_bw_align_non_nato, 1), "days\n")

optimal_bandwidth_data_non_nato <- data_non_nato %>%
  filter(running_continuous < optimal_bw_align_non_nato, running_continuous > -optimal_bw_align_non_nato)%>%
  droplevels()


model2d_z <- feols(sentiment_z ~ running_continuous * treatment * state_owned | topic_clean,
                   cluster = ~source_domain,
                   data = optimal_bandwidth_data_non_nato)

boot_model2d_z <- run_wild_bootstrap(model2d_z, "treatment:state_owned")
cat("Z-score model2d_z — Bootstrap p-value:", boot_model2d_z$p_val, "\n")
```

# By-Topic Analysis

## By-Topic Samples

Table 3 fits one diff-in-disc per topic, each at its own optimal bandwidth. The
five topic frames are built here; the bandwidths follow. No full-data by-topic
model is fitted, since none reaches a table 10d or 11 builds.

```{r topic-full-drop}
data_pol <- data_non_ukraine %>% filter(topic_clean == "Political")
data_mil <- data_non_ukraine %>% filter(topic_clean == "Military")
data_econ <- data_non_ukraine %>% filter(topic_clean == "Economic")
data_cult <- data_non_ukraine %>% filter(topic_clean == "Culture")
data_oth <- data_non_ukraine %>% filter(topic_clean == "Other")
```

## Per-Topic Optimal Bandwidth

```{r topic-opt-bw-drop}
# Political
resid_y_pol <- feols(sentiment_z ~ 1 | state_owned, data = data_pol)$residuals
bw_pol <- rdbwselect(y = resid_y_pol, x = data_pol$running_continuous,
                     kernel = "triangular", cluster = data_pol$source_domain, p = 1, bwselect = "mserd")
optimal_bw_pol <- bw_pol$bws[1, 1]
cat("Political optimal bandwidth:", round(optimal_bw_pol, 1), "days\n")
opt_data_pol <- data_pol %>% filter(running_continuous < optimal_bw_pol, running_continuous > -optimal_bw_pol)%>%
  droplevels()

# Military
resid_y_mil <- feols(sentiment_z ~ 1 | state_owned, data = data_mil)$residuals
bw_mil <- rdbwselect(y = resid_y_mil, x = data_mil$running_continuous,
                     kernel = "triangular", cluster = data_mil$source_domain, p = 1, bwselect = "mserd")
optimal_bw_mil <- bw_mil$bws[1, 1]
cat("Military optimal bandwidth:", round(optimal_bw_mil, 1), "days\n")
opt_data_mil <- data_mil %>% filter(running_continuous < optimal_bw_mil, running_continuous > -optimal_bw_mil)%>%
  droplevels()

# Economic
resid_y_econ <- feols(sentiment_z ~ 1 | state_owned, data = data_econ)$residuals
bw_econ <- rdbwselect(y = resid_y_econ, x = data_econ$running_continuous,
                      kernel = "triangular", cluster = data_econ$source_domain, p = 1, bwselect = "mserd")
optimal_bw_econ <- bw_econ$bws[1, 1]
cat("Economic optimal bandwidth:", round(optimal_bw_econ, 1), "days\n")
opt_data_econ <- data_econ %>% filter(running_continuous < optimal_bw_econ, running_continuous > -optimal_bw_econ)%>%
  droplevels()

# Culture
resid_y_cult <- feols(sentiment_z ~ 1 | state_owned, data = data_cult)$residuals
bw_cult <- rdbwselect(y = resid_y_cult, x = data_cult$running_continuous,
                      kernel = "triangular", cluster = data_cult$source_domain, p = 1, bwselect = "mserd")
optimal_bw_cult <- bw_cult$bws[1, 1]
cat("Culture optimal bandwidth:", round(optimal_bw_cult, 1), "days\n")
opt_data_cult <- data_cult %>% filter(running_continuous < optimal_bw_cult, running_continuous > -optimal_bw_cult)%>%
  droplevels()

# Other
resid_y_oth <- feols(sentiment_z ~ 1 | state_owned, data = data_oth)$residuals
bw_oth <- rdbwselect(y = resid_y_oth, x = data_oth$running_continuous,
                     kernel = "triangular", cluster = data_oth$source_domain, p = 1, bwselect = "mserd")
optimal_bw_oth <- bw_oth$bws[1, 1]
cat("Other optimal bandwidth:", round(optimal_bw_oth, 1), "days\n")
opt_data_oth <- data_oth %>% filter(running_continuous < optimal_bw_oth, running_continuous > -optimal_bw_oth)%>%
  droplevels()
```

```{r topic-opt-models-drop}
model2a_opt_pol <- feols(sentiment_z ~ running_continuous * treatment * state_owned,
                         cluster = ~source_domain,
                         data = opt_data_pol)
summary(model2a_opt_pol)

model2a_opt_mil <- feols(sentiment_z ~ running_continuous * treatment * state_owned,
                         cluster = ~source_domain,
                         data = opt_data_mil)
summary(model2a_opt_mil)

model2a_opt_econ <- feols(sentiment_z ~ running_continuous * treatment * state_owned,
                          cluster = ~source_domain,
                          data = opt_data_econ)
summary(model2a_opt_econ)

model2a_opt_cult <- feols(sentiment_z ~ running_continuous * treatment * state_owned,
                          cluster = ~source_domain,
                          data = opt_data_cult)
summary(model2a_opt_cult)

model2a_opt_oth <- feols(sentiment_z ~ running_continuous * treatment * state_owned,
                         cluster = ~source_domain,
                         data = opt_data_oth)
summary(model2a_opt_oth)

# Wild cluster bootstrap for topic-specific models (optimal BW)
boot_model2a_opt_pol <- run_wild_bootstrap(model2a_opt_pol, "treatment:state_owned")
boot_model2a_opt_mil <- run_wild_bootstrap(model2a_opt_mil, "treatment:state_owned")
boot_model2a_opt_econ <- run_wild_bootstrap(model2a_opt_econ, "treatment:state_owned")
boot_model2a_opt_cult <- run_wild_bootstrap(model2a_opt_cult, "treatment:state_owned")
boot_model2a_opt_oth <- run_wild_bootstrap(model2a_opt_oth, "treatment:state_owned")
```

# Robustness

## Matching

### Initial Match

```{r matching-h2-drop}
# Subset to data of interest (non-military, optimal bandwidth)
matching_data <- optimal_bandwidth_data_non_nato %>%
  select(sentiment_clean, sentiment_z, running, running_continuous, treatment, state_owned,
         topic_clean, source_domain, country)

# Match on topic and publication day
ps_model <- matchit(
  state_owned ~ running + topic_clean,
  data = matching_data,
  method = "exact",
  ratio = 1,
)

summary(ps_model)
```

### Assess Balance

```{r balance-h2-drop}
# Numerical balance check
bal.tab(ps_model, un = TRUE, stats = c("m", "v"), thresholds = c(m = 0.1))

# Love plot (publication quality)
love <- love.plot(ps_model, binary = "std", thresholds = c(m = 0.1))

ggsave(plot = love,
       file.path(FIGURES_DIFF_DISC_DROP, "love_balance_state_owned.png"),
       width = 10, height = 7)
```

### Matching Analysis

```{r matched-model-h2-drop}
# Extract matched data and calculate treatment effects
matched_data <- match.data(ps_model)

# Z-score matched model
matched_model_z <- feols(sentiment_z ~ running_continuous * treatment * state_owned |
                          topic_clean,
                          cluster = ~source_domain, data = matched_data)

summary(matched_model_z)

boot_matched_model_z <- run_wild_bootstrap(matched_model_z, "treatment:state_owned")
cat("Z-score matched model — Bootstrap p-value:", boot_matched_model_z$p_val, "\n")
```

## Sensitivity Analysis (OVB)

```{r sensitivity-h2-drop}
# Respecify the model using lm for sensemakr
lm_model <- lm(sentiment_clean ~ running_continuous * treatment * state_owned +
                 factor(topic_clean) + factor(source_domain),
               data = matched_data)

# Sensitivity analysis
sensitivity <- sensemakr(
  model = lm_model,
  treatment = "treatment:state_owned",
  benchmark_covariates = c("running_continuous:treatment"),
  kd = 1,
  ky = 1,
  reduce = TRUE
)

summary(sensitivity)
```

```{r sensitivity-r2-h2-drop}
partial_r2(lm_model, covariates = c("running_continuous:treatment",
                                     "running_continuous:state_owned",
                                     "treatment",
                                     "state_owned"))

treatment_r2 <- partial_r2(lm_model, covariates = c("treatment"))
```

```{r sensitivity-plot-h2-drop, fig.width=10, fig.height=7}
# Extract the data sensemakr uses for the plot
ovb_contour_data <- function(sensitivity, lim = 0.005) {

  # Grid of r2dz.x and r2yz.dx values
  r2dz <- seq(0, lim, length.out = 400)
  r2yz <- seq(0, lim, length.out = 400)
  grid <- expand.grid(r2dz.x = r2dz, r2yz.dx = r2yz)

  # Extract key stats
  estimate <- sensitivity$sensitivity_stats$estimate
  se <- sensitivity$sensitivity_stats$se
  df <- sensitivity$sensitivity_stats$dof

  # Compute adjusted estimate across grid
  grid$adjusted <- mapply(function(r2dz, r2yz) {
    sensemakr::adjusted_estimate(
      estimate = estimate,
      se = se,
      dof = df,
      r2dz.x = r2dz,
      r2yz.dx = r2yz
    )
  }, grid$r2dz.x, grid$r2yz.dx)

  return(grid)
}

# Extract benchmark points
benchmark_df <- data.frame(
  r2dz.x = sensitivity$bounds$r2dz.x,
  r2yz.dx = sensitivity$bounds$r2yz.dx,
  label = sensitivity$bounds$bound_label
)

# Build contour data with wider x limit
contour_data <- ovb_contour_data(sensitivity, lim = 0.1)

sensitivity <- ggplot(contour_data, aes(x = r2dz.x, y = r2yz.dx, z = adjusted)) +
  geom_contour(colour = "grey60",
               breaks = c(-0.1, -0.05, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3)) +
  geom_contour(breaks = 0,
               colour = "red",
               linetype = "dashed",
               linewidth = 0.8) +
  geom_point(data = benchmark_df,
             aes(x = r2dz.x, y = r2yz.dx),
             shape = 18, colour = "red", size = 3,
             inherit.aes = FALSE) +
  annotate("point", x = 0, y = 0, shape = 17, size = 3) +
  annotate("text", x = 0.002, y = 0.003,
           label = "Unadjusted",
           size = 5, hjust = 0) +
  annotate("text", x = 0.047, y = 0.003,
           label = "running:treatment",
           size = 5, hjust = 0) +
  coord_cartesian(xlim = c(0, 0.1), ylim = c(0, 0.1)) +
  scale_x_continuous(breaks = seq(0, 0.1, by = 0.02),
                     labels = scales::number_format(accuracy = 0.01)) +
  scale_y_continuous(breaks = seq(0, 0.1, by = 0.02),
                     labels = scales::number_format(accuracy = 0.01)) +
  labs(
    x = "Partial R² of confounder with state ownership",
    y = "Partial R² of confounder with sentiment",
    title = "Sensitivity to Unobserved Confounding, State Ownership",
    subtitle = "Red dashed line indicates where estimate = 0"
  ) +
  theme_bw() +
  theme(
    panel.grid.minor = element_blank(),
    plot.title = element_text(face = "bold"),
    legend.position = "none"
  )

ggsave(plot = sensitivity,
       file.path(FIGURES_DIFF_DISC_DROP, "sensitivity_ovb_state_owned.png"),
       width = 10, height = 7)
```

# Save Results

```{r save-drop}
results_h2_drop <- list(
  # Table 2 Models 1-2: separate RDDs, state-owned and independent media
  model2_state_rdd_z = model2_state_rdd_z,
  model2_ind_rdd_z = model2_ind_rdd_z,

  # Table 2 Models 3-5: diff-in-disc at the optimal bandwidth, then military
  # omitted, then non-NATO countries only
  model2a_opt_z = model2a_opt_z,
  model2b_z = model2b_z,
  model2d_z = model2d_z,

  # Table 2 Model 6: matched
  matched_model_z = matched_model_z,

  # Table 3: one diff-in-disc per topic, each at its own optimal bandwidth
  model2a_opt_pol = model2a_opt_pol,
  model2a_opt_mil = model2a_opt_mil,
  model2a_opt_econ = model2a_opt_econ,
  model2a_opt_cult = model2a_opt_cult,
  model2a_opt_oth = model2a_opt_oth,

  # Wild cluster bootstrap results behind the significance stars
  bootstrap_se = list(
    model2a_opt_z = boot_model2a_opt_z,
    model2b_z = boot_model2b_z,
    model2d_z = boot_model2d_z,
    matched_model_z = boot_matched_model_z,
    model2a_opt_pol = boot_model2a_opt_pol,
    model2a_opt_mil = boot_model2a_opt_mil,
    model2a_opt_econ = boot_model2a_opt_econ,
    model2a_opt_cult = boot_model2a_opt_cult,
    model2a_opt_oth = boot_model2a_opt_oth
  )
)

saveRDS(results_h2_drop, file.path(DATA_INTERMEDIATE, "05_h2_results_drop.rds"))
cat("Results saved to:", file.path(DATA_INTERMEDIATE, "05_h2_results_drop.rds"), "\n")
```

# Session Info

```{r session-info-drop}
print_session_info()
```
