---
title: "06 - Heterogeneity Analysis"
author: "Donald Moratz"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

# Overview

This script examines heterogeneous treatment effects by:
- Russian alignment (CSTO vs Neutral)
- Ethnic Russian population
- Country-specific analyses

**Inputs:**
- `data/intermediate/02_cleaned_data.rds`
- `data/intermediate/02_data_non_ukraine.rds`

**Outputs:**
- Heterogeneity analysis results
- Table 3
- Additional visualizations

```{r setup, include=FALSE}
source("00_setup.R")
```

# Load Data

```{r load}
data <- readRDS(file.path(DATA_INTERMEDIATE, "02_cleaned_data.rds"))
data_non_ukraine <- readRDS(file.path(DATA_INTERMEDIATE, "02_data_non_ukraine.rds"))

cat("Full data:", nrow(data), "articles\n")
cat("Non-Ukraine data:", nrow(data_non_ukraine), "articles\n")
```

# Russian Alignment Analysis (CSTO vs Neutral)

## Create Alignment Subsets

```{r alignment-data}
# Filter to non-NATO countries for alignment analysis
data_align <- data %>%
  filter(nato == 0)

# Create alignment indicator
data_align <- data_align %>%
  mutate(align_indicator = factor(case_when(
    indicator == 1 & csto == 1 ~ "Pre. Ind. CSTO",
    indicator == 1 & csto == 0 ~ "Pre. Ind. Neut",
    indicator == 2 & csto == 1 ~ "Pre. State CSTO",
    indicator == 2 & csto == 0 ~ "Pre. State Neut",
    indicator == 3 & csto == 1 ~ "Post Ind. CSTO",
    indicator == 3 & csto == 0 ~ "Post Ind. Neut",
    indicator == 4 & csto == 1 ~ "Post State CSTO",
    indicator == 4 & csto == 0 ~ "Post State Neut"
  ),
  levels = c("Pre. Ind. CSTO", "Pre. Ind. Neut", "Pre. State CSTO",
             "Pre. State Neut", "Post Ind. CSTO", "Post Ind. Neut",
             "Post State CSTO", "Post State Neut")))

cat("Non-NATO countries sample:", nrow(data_align), "articles\n")
cat("CSTO:", sum(data_align$csto), "\n")
cat("Neutral:", sum(data_align$csto == 0), "\n")
```

## Visualization: Independent Media by Alignment

```{r align-ind-plot, fig.width=10, fig.height=7}
agg_data_align_ind <- data_align %>%
  filter(state_owned == 0) %>%
  group_by(running, csto) %>%
  summarize(sentiment_clean = mean(sentiment_clean), num_obs = n(), .groups = "drop")

data_align %>%
  filter(state_owned == 0) %>%
  ggplot(aes(x = running, y = sentiment_clean, group = align_indicator, color = align_indicator)) +
  geom_point(data = agg_data_align_ind,
             aes(x = running, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = COLORS_DISCS, name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on Independent Media Sentiment",
    subtitle = "Neutral vs Russia Aligned, Difference in Discontinuities",
    x = "Days Pre/Post Invasion",
    y = "Sentiment"
  )
```

## Visualization: State Media by Alignment

```{r align-state-plot, fig.width=10, fig.height=7}
agg_data_align_state <- data_align %>%
  filter(state_owned == 1) %>%
  group_by(running, csto) %>%
  summarize(sentiment_clean = mean(sentiment_clean), num_obs = n(), .groups = "drop")

state_align_discs_graph <- data_align %>%
  filter(state_owned == 1) %>%
  ggplot(aes(x = running, y = sentiment_clean, group = align_indicator, color = align_indicator)) +
  geom_point(data = agg_data_align_state,
             aes(x = running, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = COLORS_DISCS, name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on State Media Sentiment",
    subtitle = "Neutral vs Russia Aligned, Difference in Discontinuities",
    x = "Days Pre/Post Invasion",
    y = "Sentiment"
  )

state_align_discs_graph

ggsave(plot = state_align_discs_graph,
       file.path(FIGURES_DIR, "state_align_discs.png"),
       width = 10, height = 7)
```

## State Media Alignment Regressions

### CSTO Countries Only

```{r align-csto}
data_align_state_csto <- data_align %>%
  filter(state_owned == 1, csto == 1)

model5a_state <- felm(sentiment_clean ~ running * treatment | source_domain + topic_clean | 0 | source_domain,
                      data = data_align_state_csto)

summary(model5a_state)
```

### Neutral Countries Only

```{r align-neutral}
data_align_state_neutral <- data_align %>%
  filter(state_owned == 1, csto == 0)

model5a_neutral <- felm(sentiment_clean ~ running * treatment | source_domain + topic_clean | 0 | source_domain,
                        data = data_align_state_neutral)

summary(model5a_neutral)
```

### Diff-in-Disc: CSTO vs Neutral (State Media)

```{r align-diff}
data_align_state <- data_align %>%
  filter(state_owned == 1)

model5a <- felm(sentiment_clean ~ running * treatment * csto | 0 | 0 | source_domain,
                data = data_align_state)

summary(model5a)
```

## Optimal Bandwidth

```{r align-optimal}
bw_align <- rdbwselect(y = data_align_state$sentiment_clean,
                       x = data_align_state$running,
                       kernel = "triangular",
                       cluster = data_align_state$source_domain,
                       p = 1,
                       bwselect = "mserd")

optimal_bw_align <- bw_align$bws[1, 1]
cat("Optimal bandwidth:", round(optimal_bw_align, 1), "days\n")

optimal_bandwidth_data_state <- data_align_state %>%
  filter(running < optimal_bw_align, running > -optimal_bw_align)

model5a_opt <- felm(sentiment_clean ~ running * treatment * csto | 0 | 0 | source_domain,
                    data = optimal_bandwidth_data_state)

summary(model5a_opt)
```

## Effect Size

```{r align-effect}
sd_state_owned <- sd(data_align_state$sentiment_clean)
cat("SD of sentiment (state media):", round(sd_state_owned, 3), "\n")

coef_csto_int <- summary(model5a_opt)$coef["running:treatment:csto", "Estimate"]
cat("CSTO x Treatment interaction effect (in SD):", round(coef_csto_int / sd_state_owned, 3), "\n")
```

## Non-Military Topics

```{r align-non-mil}
data_align_state_non_mil <- data_align_state %>%
  filter(!topic_clean %in% "Military")

model5a_non_mil <- felm(sentiment_clean ~ running * treatment * csto | 0 | 0 | source_domain,
                        data = data_align_state_non_mil)

summary(model5a_non_mil)
```

# Ethnic Russian Population Analysis

## Create Ethnic Subsets

```{r ethnic-data}
data_ethnic <- data %>%
  filter(nato == 0)

data_ethnic <- data_ethnic %>%
  mutate(ethnic_indicator = factor(case_when(
    indicator == 1 & high_russia == 1 ~ "Pre. Ind. High Rus",
    indicator == 1 & high_russia == 0 ~ "Pre. Ind. Low Rus",
    indicator == 2 & high_russia == 1 ~ "Pre. State High Rus",
    indicator == 2 & high_russia == 0 ~ "Pre. State Low Rus",
    indicator == 3 & high_russia == 1 ~ "Post Ind. High Rus",
    indicator == 3 & high_russia == 0 ~ "Post Ind. Low Rus",
    indicator == 4 & high_russia == 1 ~ "Post State High Rus",
    indicator == 4 & high_russia == 0 ~ "Post State Low Rus"
  ),
  levels = c("Pre. Ind. High Rus", "Pre. Ind. Low Rus", "Pre. State High Rus",
             "Pre. State Low Rus", "Post Ind. High Rus", "Post Ind. Low Rus",
             "Post State High Rus", "Post State Low Rus")))

cat("High Russian population:", sum(data_ethnic$high_russia), "\n")
cat("Low Russian population:", sum(data_ethnic$high_russia == 0), "\n")
```

## Visualization: State Media by Ethnic Russian Population

```{r ethnic-plot, fig.width=10, fig.height=7}
agg_data_ethnic <- data_ethnic %>%
  filter(state_owned == 1) %>%
  group_by(running, csto) %>%
  summarize(sentiment_clean = mean(sentiment_clean), num_obs = n(), .groups = "drop")

ethnic_discs_graph <- data_ethnic %>%
  filter(state_owned == 1) %>%
  ggplot(aes(x = running, y = sentiment_clean, group = ethnic_indicator, color = ethnic_indicator)) +
  geom_point(data = agg_data_ethnic,
             aes(x = running, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = COLORS_DISCS, name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on State Media Sentiment",
    subtitle = "High vs Low Ethnic Russian, Difference in Discontinuities",
    x = "Days Pre/Post Invasion",
    y = "Sentiment"
  )

ethnic_discs_graph

ggsave(plot = ethnic_discs_graph,
       file.path(FIGURES_DIR, "ethnic_discs.png"),
       width = 10, height = 7)
```

## Ethnic Russian Population Regression

```{r ethnic-reg}
data_ethnic_state <- data_ethnic %>%
  filter(state_owned == 1)

model6a <- felm(sentiment_clean ~ running * treatment * high_russia | 0 | 0 | 0,
                data = data_ethnic_state)

summary(model6a)
```

# Country-Level Analysis

## State Media by Country and Alliance

```{r country-facet, fig.width=12, fig.height=8}
# Create alliance for faceting
data_long <- data %>%
  pivot_longer(cols = c(nato, csto, neutral),
               names_to = "alliance",
               values_to = "membership") %>%
  filter(membership == 1) %>%
  mutate(
    alliance = factor(alliance, levels = c("nato", "csto", "neutral")),
    state_indicator = factor(paste(country, treatment, sep = ", "))
  )

data_long %>%
  filter(state_owned == 1) %>%
  ggplot(aes(x = running, y = sentiment_clean, group = state_indicator, color = country)) +
  geom_smooth(method = "lm", se = FALSE) +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  facet_wrap(~alliance, nrow = 2) +
  labs(
    title = "Effect of Invasion on State Media Sentiment by Country",
    subtitle = "Faceted by Alliance",
    x = "Days Pre/Post Invasion",
    y = "Sentiment"
  )
```

# Summary Table (Table 3)

```{r table3}
note_text <- "All standard errors are clustered at the source level. Model 2 uses the optimal bandwidth. Model 3 omits military-related articles."
note_wrapped <- str_wrap(note_text, width = 80)

table_3 <- modelsummary(
  list(model5a, model5a_opt, model5a_non_mil),
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors",
  title = "Russian Alignment: Difference in Discontinuity Analysis",
  notes = note_wrapped
)

table_3

# Also save as HTML using stargazer
stargazer(model5a, model5a_opt, model5a_non_mil,
          type = "html",
          out = file.path(FIGURES_DIR, "table_3.html"),
          title = "Russian Alignment: Difference in Discontinuity Analysis",
          covariate.labels = c("Invasion", "CSTO x Treatment"),
          dep.var.labels = "Sentiment",
          notes = gsub("\n", "<br>", note_wrapped),
          notes.align = "l",
          omit.stat = c("aic", "bic", "f", "ll", "ser"))
```

# Save Results

```{r save}
results_het <- list(
  model5a = model5a,
  model5a_opt = model5a_opt,
  model5a_non_mil = model5a_non_mil,
  model5a_csto = model5a_state,
  model5a_neutral = model5a_neutral,
  model6a = model6a,
  optimal_bandwidth_align = optimal_bw_align
)

saveRDS(results_het, file.path(DATA_INTERMEDIATE, "06_heterogeneity_results.rds"))
cat("Results saved to:", file.path(DATA_INTERMEDIATE, "06_heterogeneity_results.rds"), "\n")
```

# Session Info

```{r session-info}
print_session_info()
```
