---
title: "06 - Heterogeneity Analysis"
author: "Donald Moratz"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

# Overview

This script examines heterogeneous treatment effects by:
- Russian alignment (CSTO vs Neutral)
- Ethnic Russian population
- Country-specific analyses

**Inputs:**
- `data/intermediate/02_cleaned_data.rds`
- `data/intermediate/02_data_non_ukraine.rds`

**Outputs:**
- Heterogeneity analysis results
- Table 3
- Additional visualizations

```{r setup, include=FALSE}
source("00_setup.R")
knitr::opts_chunk$set(fig.path = paste0(FIGURES_HETEROGENEITY_DAYS, "/"))
```

# Load Data

```{r load}
data <- readRDS(file.path(DATA_INTERMEDIATE, "02_cleaned_data.rds"))
data_non_ukraine <- readRDS(file.path(DATA_INTERMEDIATE, "02_data_non_ukraine.rds"))

cat("Full data:", nrow(data), "articles\n")
cat("Non-Ukraine data:", nrow(data_non_ukraine), "articles\n")
```

# Russian Alignment Analysis (CSTO vs Neutral)

## Create Alignment Subsets

```{r alignment-data}
# Filter to non-NATO countries for alignment analysis
data_align <- data %>%
  filter(nato == 0)

# Create alignment indicator
data_align <- data_align %>%
  mutate(align_indicator = factor(case_when(
    indicator == 1 & csto == 1 ~ "Pre. Ind. CSTO",
    indicator == 1 & csto == 0 ~ "Pre. Ind. Neut",
    indicator == 2 & csto == 1 ~ "Pre. State CSTO",
    indicator == 2 & csto == 0 ~ "Pre. State Neut",
    indicator == 3 & csto == 1 ~ "Post Ind. CSTO",
    indicator == 3 & csto == 0 ~ "Post Ind. Neut",
    indicator == 4 & csto == 1 ~ "Post State CSTO",
    indicator == 4 & csto == 0 ~ "Post State Neut"
  ),
  levels = c("Pre. Ind. CSTO", "Pre. Ind. Neut", "Pre. State CSTO",
             "Pre. State Neut", "Post Ind. CSTO", "Post Ind. Neut",
             "Post State CSTO", "Post State Neut")))

cat("Non-NATO countries sample:", nrow(data_align), "articles\n")
cat("CSTO:", sum(data_align$csto), "\n")
cat("Neutral:", sum(data_align$csto == 0), "\n")
```

## Visualization: Independent Media by Alignment

```{r align-ind-plot, fig.width=10, fig.height=7}
agg_data_align_ind <- data_align %>%
  filter(state_owned == 0) %>%
  group_by(running, csto) %>%
  summarize(sentiment_clean = mean(sentiment_clean), num_obs = n(), .groups = "drop")

data_align %>%
  filter(state_owned == 0) %>%
  ggplot(aes(x = running, y = sentiment_clean, group = align_indicator, color = align_indicator)) +
  geom_point(data = agg_data_align_ind,
             aes(x = running, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = COLORS_DISCS, name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on Independent Media Sentiment",
    subtitle = "Neutral vs Russia Aligned, Difference in Discontinuities",
    x = "Days Pre/Post Invasion",
    y = "Sentiment"
  )
```

## Visualization: State Media by Alignment

```{r align-state-plot, fig.width=10, fig.height=7}
agg_data_align_state <- data_align %>%
  filter(state_owned == 1) %>%
  group_by(running, csto) %>%
  summarize(sentiment_clean = mean(sentiment_clean), num_obs = n(), .groups = "drop")

state_align_discs_graph <- data_align %>%
  filter(state_owned == 1) %>%
  ggplot(aes(x = running, y = sentiment_clean, group = align_indicator, color = align_indicator)) +
  geom_point(data = agg_data_align_state,
             aes(x = running, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = COLORS_DISCS, name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on State Media Sentiment",
    subtitle = "Neutral vs Russia Aligned, Difference in Discontinuities",
    x = "Days Pre/Post Invasion",
    y = "Sentiment"
  )

state_align_discs_graph

ggsave(plot = state_align_discs_graph,
       file.path(FIGURES_HETEROGENEITY_DAYS, "state_align_discs.png"),
       width = 10, height = 7)
```

## State Media Alignment Regressions

### CSTO Countries Only

```{r align-csto}
data_align_state_csto <- data_align %>%
  filter(state_owned == 1, csto == 1) %>%
  filter(!topic_clean %in% "Military")

covs_matrix <- model.matrix(~ source_domain + topic_clean - 1, data = data_align_state_csto)
  

model5a_csto <- rdrobust(
  y = data_align_state_csto$sentiment_clean, 
  x = data_align_state_csto$running,
  covs = covs_matrix,
  cluster = data_align_state_csto$source_domain
)

summary(model5a_csto)
```

### Neutral Countries Only

```{r align-neutral}
data_align_state_neutral <- data_align %>%
  filter(state_owned == 1, csto == 0)%>%
  filter(!topic_clean %in% "Military")

covs_matrix <- model.matrix(~ source_domain + topic_clean - 1, data = data_align_state_neutral)
  

model5a_neutral <- rdrobust(
  y = data_align_state_neutral$sentiment_clean, 
  x = data_align_state_neutral$running,
  covs = covs_matrix,
  cluster = data_align_state_neutral$source_domain
)

summary(model5a_neutral)
```

### Diff-in-Disc: CSTO vs Neutral (State Media)

```{r align-diff}
data_align_state <- data_align %>%
  filter(state_owned == 1) #%>%
  #filter(!country == "Belarus")

model5a <- felm(sentiment_clean ~ running * treatment * csto | 0 | 0 | source_domain,
                data = data_align_state)

summary(model5a)
```


## Full Data with Topic FEs

```{r align-full}
model5a_full <- felm(sentiment_clean ~ running * treatment * csto | topic_clean | 0 | source_domain,
                     data = data_align_state)

summary(model5a_full)
```

## Optimal Bandwidth

```{r align-optimal}
bw_align <- rdbwselect(y = data_align_state$sentiment_clean,
                       x = data_align_state$running,
                       kernel = "triangular",
                       cluster = data_align_state$source_domain,
                       p = 1,
                       bwselect = "mserd")

optimal_bw_align <- bw_align$bws[1, 1]
cat("Optimal bandwidth:", round(optimal_bw_align, 1), "days\n")

optimal_bandwidth_data_state <- data_align_state %>%
  filter(running < optimal_bw_align, running > -optimal_bw_align)

model5a_opt <- felm(sentiment_clean ~ running * treatment * csto | topic_clean | 0 | source_domain,
                    data = optimal_bandwidth_data_state)

summary(model5a_opt)
```

## Effect Size

```{r align-effect}
sd_state_owned <- sd(data_align_state$sentiment_clean)
cat("SD of sentiment (state media):", round(sd_state_owned, 3), "\n")

coef_csto_int <- summary(model5a_opt)$coef["treatment:csto", "Estimate"]
cat("CSTO x Treatment interaction effect (in SD):", round(coef_csto_int / sd_state_owned, 3), "\n")
```

## Non-Military Topics

```{r align-non-mil}
data_align_state_non_mil <- data_align_state %>%
  filter(!topic_clean %in% "Military")

bw_align <- rdbwselect(y = data_align_state_non_mil$sentiment_clean,
                       x = data_align_state_non_mil$running,
                       kernel = "triangular",
                       cluster = data_align_state_non_mil$source_domain,
                       p = 1,
                       bwselect = "mserd")

optimal_bw_align <- bw_align$bws[1, 1]
cat("Optimal bandwidth:", round(optimal_bw_align, 1), "days\n")

optimal_bandwidth_data_state_non_mil <- data_align_state_non_mil %>%
  filter(running < optimal_bw_align, running > -optimal_bw_align)

model5a_opt_non_mil <- felm(sentiment_clean ~ running * treatment * csto | topic_clean | 0 | source_domain,
                        data = optimal_bandwidth_data_state_non_mil)

summary(model5a_opt_non_mil)
```

## Leave-One-Out Country Robustness

```{r loo-country}
countries <- unique(data_align_state_non_mil$country)
loo_results <- list()

for (cntry in countries) {
  data_loo <- data_align_state_non_mil %>%
    filter(country != cntry)

  # Re-calculate optimal bandwidth for LOO data
  bw_loo <- rdbwselect(y = data_loo$sentiment_clean,
                       x = data_loo$running,
                       kernel = "triangular",
                       cluster = data_loo$source_domain,
                       p = 1,
                       bwselect = "mserd")

  optimal_bw_loo <- bw_loo$bws[1, 1]

  data_loo_bw <- data_loo %>%
    filter(running < optimal_bw_loo, running > -optimal_bw_loo)

  model_loo <- felm(sentiment_clean ~ running * treatment * csto | topic_clean | 0 | source_domain,
                    data = data_loo_bw)

  loo_results[[cntry]] <- list(
    model = model_loo,
    bandwidth = optimal_bw_loo,
    n = nrow(data_loo_bw),
    country_dropped = cntry
  )
}

# Extract key coefficient (treatment:csto interaction)
loo_summary <- map_df(names(loo_results), function(cntry) {
  mod <- loo_results[[cntry]]$model
  coef_row <- summary(mod)$coef["treatment:csto", ]
  tibble(
    country_dropped = cntry,
    estimate = coef_row["Estimate"],
    std_error = coef_row["Cluster s.e."],
    p_value = coef_row["Pr(>|t|)"],
    n_obs = loo_results[[cntry]]$n,
    bandwidth = loo_results[[cntry]]$bandwidth
  )
})

print(loo_summary)
```

## Placebo Test: December 7th Announcement (Non-Military Topics)

```{r placebo-dec-nonmil}
data_dec_align <- data_align_state_non_mil %>%
  filter(date_publish < "2022-02-19") %>%
  mutate(
    running = as.numeric(date_publish - as.Date("2021-12-07")),
    treatment = ifelse(date_publish < as.Date("2021-12-07"), 0, 1)
  )

# Find optimal bandwidth for placebo
bw_placebo_nonmil <- rdbwselect(y = data_dec_align$sentiment_clean,
                                x = data_dec_align$running,
                                kernel = "triangular",
                                cluster = data_dec_align$source_domain,
                                p = 1,
                                bwselect = "mserd")

optimal_bw_placebo_nonmil <- bw_placebo_nonmil$bws[1, 1]
cat("Placebo optimal bandwidth (non-mil):", round(optimal_bw_placebo_nonmil, 1), "days\n")

data_dec_align_bw <- data_dec_align %>%
  filter(running < optimal_bw_placebo_nonmil, running > -optimal_bw_placebo_nonmil)

model_placebo_nonmil <- felm(sentiment_clean ~ running * treatment * csto | topic_clean | 0 | source_domain,
                              data = data_dec_align_bw)

summary(model_placebo_nonmil)
cat("\nNote: Non-significant treatment effect suggests parallel trends assumption holds.\n")
```

## Russian-Related Articles Only

```{r align-russian}
data_align_state_russian <- data_align_state %>%
  filter(!topic_clean %in% "Military") %>%
  filter(!Russian.Involvement == "Not")

bw_align <- rdbwselect(y = data_align_state_russian$sentiment_clean,
                       x = data_align_state_russian$running,
                       kernel = "triangular",
                       cluster = data_align_state_russian$source_domain,
                       p = 1,
                       bwselect = "mserd")

optimal_bw_align <- bw_align$bws[1, 1]
cat("Optimal bandwidth:", round(optimal_bw_align, 1), "days\n")

optimal_bandwidth_data_state_russian <- data_align_state_russian %>%
  filter(running < optimal_bw_align, running > -optimal_bw_align)


model5a_opt_russian <- felm(sentiment_clean ~ running * treatment * csto | topic_clean | 0 | source_domain,
                        data = optimal_bandwidth_data_state_russian)

summary(model5a_opt_russian)
```

## By-Topic Models: Full Data

```{r topic-full-het}
data_align_state_pol <- data_align_state %>% filter(topic_clean == "Political")
data_align_state_mil <- data_align_state %>% filter(topic_clean == "Military")
data_align_state_econ <- data_align_state %>% filter(topic_clean == "Economic")
data_align_state_cult <- data_align_state %>% filter(topic_clean == "Culture")
data_align_state_oth <- data_align_state %>% filter(topic_clean == "Other")

model5a_full_pol <- felm(sentiment_clean ~ running * treatment * csto | 0 | 0 | source_domain,
                         data = data_align_state_pol)
model5a_full_mil <- felm(sentiment_clean ~ running * treatment * csto | 0 | 0 | source_domain,
                         data = data_align_state_mil)
model5a_full_econ <- felm(sentiment_clean ~ running * treatment * csto | 0 | 0 | source_domain,
                          data = data_align_state_econ)
model5a_full_cult <- felm(sentiment_clean ~ running * treatment * csto | 0 | 0 | source_domain,
                          data = data_align_state_cult)
model5a_full_oth <- felm(sentiment_clean ~ running * treatment * csto | 0 | 0 | source_domain,
                         data = data_align_state_oth)
```

## By-Topic Models: Per-Topic Optimal Bandwidth

```{r topic-opt-het}
# Political
bw_align_pol <- rdbwselect(y = data_align_state_pol$sentiment_clean, x = data_align_state_pol$running,
                           kernel = "triangular", cluster = data_align_state_pol$source_domain, p = 1, bwselect = "mserd")
optimal_bw_align_pol <- bw_align_pol$bws[1, 1]
cat("Political optimal bandwidth:", round(optimal_bw_align_pol, 1), "days\n")
opt_align_pol <- data_align_state_pol %>% filter(running < optimal_bw_align_pol, running > -optimal_bw_align_pol)

# Military
bw_align_mil <- rdbwselect(y = data_align_state_mil$sentiment_clean, x = data_align_state_mil$running,
                           kernel = "triangular", cluster = data_align_state_mil$source_domain, p = 1, bwselect = "mserd")
optimal_bw_align_mil <- bw_align_mil$bws[1, 1]
cat("Military optimal bandwidth:", round(optimal_bw_align_mil, 1), "days\n")
opt_align_mil <- data_align_state_mil %>% filter(running < optimal_bw_align_mil, running > -optimal_bw_align_mil)

# Economic
bw_align_econ <- rdbwselect(y = data_align_state_econ$sentiment_clean, x = data_align_state_econ$running,
                            kernel = "triangular", cluster = data_align_state_econ$source_domain, p = 1, bwselect = "mserd")
optimal_bw_align_econ <- bw_align_econ$bws[1, 1]
cat("Economic optimal bandwidth:", round(optimal_bw_align_econ, 1), "days\n")
opt_align_econ <- data_align_state_econ %>% filter(running < optimal_bw_align_econ, running > -optimal_bw_align_econ)

# Culture
bw_align_cult <- rdbwselect(y = data_align_state_cult$sentiment_clean, x = data_align_state_cult$running,
                            kernel = "triangular", cluster = data_align_state_cult$source_domain, p = 1, bwselect = "mserd")
optimal_bw_align_cult <- bw_align_cult$bws[1, 1]
cat("Culture optimal bandwidth:", round(optimal_bw_align_cult, 1), "days\n")
opt_align_cult <- data_align_state_cult %>% filter(running < optimal_bw_align_cult, running > -optimal_bw_align_cult)

# Other
bw_align_oth <- rdbwselect(y = data_align_state_oth$sentiment_clean, x = data_align_state_oth$running,
                           kernel = "triangular", cluster = data_align_state_oth$source_domain, p = 1, bwselect = "mserd")
optimal_bw_align_oth <- bw_align_oth$bws[1, 1]
cat("Other optimal bandwidth:", round(optimal_bw_align_oth, 1), "days\n")
opt_align_oth <- data_align_state_oth %>% filter(running < optimal_bw_align_oth, running > -optimal_bw_align_oth)

model5a_opt_pol <- felm(sentiment_clean ~ running * treatment * csto | 0 | 0 | source_domain,
                        data = opt_align_pol)
model5a_opt_mil <- felm(sentiment_clean ~ running * treatment * csto | 0 | 0 | source_domain,
                        data = opt_align_mil)
model5a_opt_econ <- felm(sentiment_clean ~ running * treatment * csto | 0 | 0 | source_domain,
                         data = opt_align_econ)
model5a_opt_cult <- felm(sentiment_clean ~ running * treatment * csto | 0 | 0 | source_domain,
                         data = opt_align_cult)
model5a_opt_oth <- felm(sentiment_clean ~ running * treatment * csto | 0 | 0 | source_domain,
                        data = opt_align_oth)
```

# Ethnic Russian Population Analysis

## Create Ethnic Subsets

```{r ethnic-data}
data_ethnic <- data %>%
  filter(nato == 0)

data_ethnic <- data_ethnic %>%
  mutate(ethnic_indicator = factor(case_when(
    indicator == 1 & high_russia == 1 ~ "Pre. Ind. High Rus",
    indicator == 1 & high_russia == 0 ~ "Pre. Ind. Low Rus",
    indicator == 2 & high_russia == 1 ~ "Pre. State High Rus",
    indicator == 2 & high_russia == 0 ~ "Pre. State Low Rus",
    indicator == 3 & high_russia == 1 ~ "Post Ind. High Rus",
    indicator == 3 & high_russia == 0 ~ "Post Ind. Low Rus",
    indicator == 4 & high_russia == 1 ~ "Post State High Rus",
    indicator == 4 & high_russia == 0 ~ "Post State Low Rus"
  ),
  levels = c("Pre. Ind. High Rus", "Pre. Ind. Low Rus", "Pre. State High Rus",
             "Pre. State Low Rus", "Post Ind. High Rus", "Post Ind. Low Rus",
             "Post State High Rus", "Post State Low Rus")))

cat("High Russian population:", sum(data_ethnic$high_russia), "\n")
cat("Low Russian population:", sum(data_ethnic$high_russia == 0), "\n")
```

## Visualization: State Media by Ethnic Russian Population

```{r ethnic-plot, fig.width=10, fig.height=7}
agg_data_ethnic <- data_ethnic %>%
  filter(state_owned == 1) %>%
  group_by(running, csto) %>%
  summarize(sentiment_clean = mean(sentiment_clean), num_obs = n(), .groups = "drop")

ethnic_discs_graph <- data_ethnic %>%
  filter(state_owned == 1) %>%
  ggplot(aes(x = running, y = sentiment_clean, group = ethnic_indicator, color = ethnic_indicator)) +
  geom_point(data = agg_data_ethnic,
             aes(x = running, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = COLORS_DISCS, name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on State Media Sentiment",
    subtitle = "High vs Low Ethnic Russian, Difference in Discontinuities",
    x = "Days Pre/Post Invasion",
    y = "Sentiment"
  )

ethnic_discs_graph

ggsave(plot = ethnic_discs_graph,
       file.path(FIGURES_HETEROGENEITY_DAYS, "ethnic_discs.png"),
       width = 10, height = 7)
```

## Ethnic Russian Population Regressions

### Diff-in-Disc: High vs Low Ethnic Russian (State Media)

```{r ethnic-reg}
data_ethnic_state <- data_ethnic %>%
  filter(state_owned == 1)

model6a <- felm(sentiment_clean ~ running * treatment * high_russia | 0 | 0 | source_domain,
                data = data_ethnic_state)

summary(model6a)
```

## Full Data with Topic FEs

```{r ethnic-full}
model6a_full <- felm(sentiment_clean ~ running * treatment * high_russia | topic_clean | 0 | source_domain,
                     data = data_ethnic_state)

summary(model6a_full)
```

## Optimal Bandwidth

```{r ethnic-optimal}
bw_ethnic <- rdbwselect(y = data_ethnic_state$sentiment_clean,
                        x = data_ethnic_state$running,
                        kernel = "triangular",
                        cluster = data_ethnic_state$source_domain,
                        p = 1,
                        bwselect = "mserd")

optimal_bw_ethnic <- bw_ethnic$bws[1, 1]
cat("Optimal bandwidth:", round(optimal_bw_ethnic, 1), "days\n")

optimal_bandwidth_data_ethnic <- data_ethnic_state %>%
  filter(running < optimal_bw_ethnic, running > -optimal_bw_ethnic)

model6a_opt <- felm(sentiment_clean ~ running * treatment * high_russia | topic_clean | 0 | source_domain,
                    data = optimal_bandwidth_data_ethnic)

summary(model6a_opt)
```

## Non-Military Topics

```{r ethnic-non-mil}
data_ethnic_state_non_mil <- data_ethnic_state %>%
  filter(!topic_clean %in% "Military")

bw_ethnic_non_mil <- rdbwselect(y = data_ethnic_state_non_mil$sentiment_clean,
                                x = data_ethnic_state_non_mil$running,
                                kernel = "triangular",
                                cluster = data_ethnic_state_non_mil$source_domain,
                                p = 1,
                                bwselect = "mserd")

optimal_bw_ethnic_non_mil <- bw_ethnic_non_mil$bws[1, 1]
cat("Optimal bandwidth (non-mil):", round(optimal_bw_ethnic_non_mil, 1), "days\n")

optimal_bandwidth_data_ethnic_non_mil <- data_ethnic_state_non_mil %>%
  filter(running < optimal_bw_ethnic_non_mil, running > -optimal_bw_ethnic_non_mil)

model6a_opt_non_mil <- felm(sentiment_clean ~ running * treatment * high_russia | topic_clean | 0 | source_domain,
                            data = optimal_bandwidth_data_ethnic_non_mil)

summary(model6a_opt_non_mil)
```

## Russian-Related Articles Only

```{r ethnic-russian}
data_ethnic_state_russian <- data_ethnic_state %>%
  filter(!topic_clean %in% "Military") %>%
  filter(!Russian.Involvement == "Not")

bw_ethnic_russian <- rdbwselect(y = data_ethnic_state_russian$sentiment_clean,
                                x = data_ethnic_state_russian$running,
                                kernel = "triangular",
                                cluster = data_ethnic_state_russian$source_domain,
                                p = 1,
                                bwselect = "mserd")

optimal_bw_ethnic_russian <- bw_ethnic_russian$bws[1, 1]
cat("Optimal bandwidth (russian):", round(optimal_bw_ethnic_russian, 1), "days\n")

optimal_bandwidth_data_ethnic_russian <- data_ethnic_state_russian %>%
  filter(running < optimal_bw_ethnic_russian, running > -optimal_bw_ethnic_russian)

model6a_opt_russian <- felm(sentiment_clean ~ running * treatment * high_russia | topic_clean | 0 | source_domain,
                            data = optimal_bandwidth_data_ethnic_russian)

summary(model6a_opt_russian)
```

## By-Topic Models: Full Data

```{r ethnic-topic-full}
data_ethnic_state_pol <- data_ethnic_state %>% filter(topic_clean == "Political")
data_ethnic_state_mil <- data_ethnic_state %>% filter(topic_clean == "Military")
data_ethnic_state_econ <- data_ethnic_state %>% filter(topic_clean == "Economic")
data_ethnic_state_cult <- data_ethnic_state %>% filter(topic_clean == "Culture")
data_ethnic_state_oth <- data_ethnic_state %>% filter(topic_clean == "Other")

model6a_full_pol <- felm(sentiment_clean ~ running * treatment * high_russia | 0 | 0 | source_domain,
                         data = data_ethnic_state_pol)
model6a_full_mil <- felm(sentiment_clean ~ running * treatment * high_russia | 0 | 0 | source_domain,
                         data = data_ethnic_state_mil)
model6a_full_econ <- felm(sentiment_clean ~ running * treatment * high_russia | 0 | 0 | source_domain,
                          data = data_ethnic_state_econ)
model6a_full_cult <- felm(sentiment_clean ~ running * treatment * high_russia | 0 | 0 | source_domain,
                          data = data_ethnic_state_cult)
model6a_full_oth <- felm(sentiment_clean ~ running * treatment * high_russia | 0 | 0 | source_domain,
                         data = data_ethnic_state_oth)
```

## By-Topic Models: Per-Topic Optimal Bandwidth

```{r ethnic-topic-opt}
# Political
bw_ethnic_pol <- rdbwselect(y = data_ethnic_state_pol$sentiment_clean, x = data_ethnic_state_pol$running,
                            kernel = "triangular", cluster = data_ethnic_state_pol$source_domain, p = 1, bwselect = "mserd")
optimal_bw_ethnic_pol <- bw_ethnic_pol$bws[1, 1]
cat("Political optimal bandwidth:", round(optimal_bw_ethnic_pol, 1), "days\n")
opt_ethnic_pol <- data_ethnic_state_pol %>% filter(running < optimal_bw_ethnic_pol, running > -optimal_bw_ethnic_pol)

# Military
bw_ethnic_mil <- rdbwselect(y = data_ethnic_state_mil$sentiment_clean, x = data_ethnic_state_mil$running,
                            kernel = "triangular", cluster = data_ethnic_state_mil$source_domain, p = 1, bwselect = "mserd")
optimal_bw_ethnic_mil <- bw_ethnic_mil$bws[1, 1]
cat("Military optimal bandwidth:", round(optimal_bw_ethnic_mil, 1), "days\n")
opt_ethnic_mil <- data_ethnic_state_mil %>% filter(running < optimal_bw_ethnic_mil, running > -optimal_bw_ethnic_mil)

# Economic
bw_ethnic_econ <- rdbwselect(y = data_ethnic_state_econ$sentiment_clean, x = data_ethnic_state_econ$running,
                             kernel = "triangular", cluster = data_ethnic_state_econ$source_domain, p = 1, bwselect = "mserd")
optimal_bw_ethnic_econ <- bw_ethnic_econ$bws[1, 1]
cat("Economic optimal bandwidth:", round(optimal_bw_ethnic_econ, 1), "days\n")
opt_ethnic_econ <- data_ethnic_state_econ %>% filter(running < optimal_bw_ethnic_econ, running > -optimal_bw_ethnic_econ)

# Culture
bw_ethnic_cult <- rdbwselect(y = data_ethnic_state_cult$sentiment_clean, x = data_ethnic_state_cult$running,
                             kernel = "triangular", cluster = data_ethnic_state_cult$source_domain, p = 1, bwselect = "mserd")
optimal_bw_ethnic_cult <- bw_ethnic_cult$bws[1, 1]
cat("Culture optimal bandwidth:", round(optimal_bw_ethnic_cult, 1), "days\n")
opt_ethnic_cult <- data_ethnic_state_cult %>% filter(running < optimal_bw_ethnic_cult, running > -optimal_bw_ethnic_cult)

# Other
bw_ethnic_oth <- rdbwselect(y = data_ethnic_state_oth$sentiment_clean, x = data_ethnic_state_oth$running,
                            kernel = "triangular", cluster = data_ethnic_state_oth$source_domain, p = 1, bwselect = "mserd")
optimal_bw_ethnic_oth <- bw_ethnic_oth$bws[1, 1]
cat("Other optimal bandwidth:", round(optimal_bw_ethnic_oth, 1), "days\n")
opt_ethnic_oth <- data_ethnic_state_oth %>% filter(running < optimal_bw_ethnic_oth, running > -optimal_bw_ethnic_oth)

model6a_opt_pol <- felm(sentiment_clean ~ running * treatment * high_russia | 0 | 0 | source_domain,
                        data = opt_ethnic_pol)
model6a_opt_mil <- felm(sentiment_clean ~ running * treatment * high_russia | 0 | 0 | source_domain,
                        data = opt_ethnic_mil)
model6a_opt_econ <- felm(sentiment_clean ~ running * treatment * high_russia | 0 | 0 | source_domain,
                         data = opt_ethnic_econ)
model6a_opt_cult <- felm(sentiment_clean ~ running * treatment * high_russia | 0 | 0 | source_domain,
                         data = opt_ethnic_cult)
model6a_opt_oth <- felm(sentiment_clean ~ running * treatment * high_russia | 0 | 0 | source_domain,
                        data = opt_ethnic_oth)
```

# Summary Table (Table 4)

```{r table4}
note_t4 <- "All standard errors are clustered at the source level. Model 1 uses no fixed effects. Model 2 uses full data with topic fixed effects. Model 3 uses the optimal bandwidth with topic fixed effects. Model 4 omits military-related articles and uses a re-optimized bandwidth. Model 5 uses only Russian-related (non-military) articles with a re-optimized bandwidth."
note_t4_wrapped <- str_wrap(note_t4, width = 80)

table_4 <- modelsummary(
  list("(1)" = model6a, "(2)" = model6a_full, "(3)" = model6a_opt,
       "(4)" = model6a_opt_non_mil, "(5)" = model6a_opt_russian),
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors",
  title = "Ethnic Russian Population: Difference in Discontinuity Analysis",
  notes = note_t4_wrapped
)

table_4
```

## Summary Table: By Topic (Optimal Bandwidth)

```{r table4b}
note_t4b <- "All standard errors are clustered at the source level. Each model uses a per-topic re-optimized bandwidth. State media in non-NATO countries only."
note_t4b_wrapped <- str_wrap(note_t4b, width = 80)

table_4b <- modelsummary(
  list("Political" = model6a_opt_pol, "Military" = model6a_opt_mil,
       "Economic" = model6a_opt_econ, "Cultural" = model6a_opt_cult, "Other" = model6a_opt_oth),
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors",
  title = "Ethnic Russian Population By Topic (Per-Topic Optimal Bandwidth)",
  notes = note_t4b_wrapped
)

table_4b
```

## Summary Table: By Topic (Full Data)

```{r table4c}
note_t4c <- "All standard errors are clustered at the source level. Each model uses the full dataset (no bandwidth restriction). State media in non-NATO countries only."
note_t4c_wrapped <- str_wrap(note_t4c, width = 80)

table_4c <- modelsummary(
  list("Political" = model6a_full_pol, "Military" = model6a_full_mil,
       "Economic" = model6a_full_econ, "Cultural" = model6a_full_cult, "Other" = model6a_full_oth),
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors",
  title = "Ethnic Russian Population By Topic (Full Data)",
  notes = note_t4c_wrapped
)

table_4c
```

# Country-Level Analysis

## State Media by Country and Alliance

```{r country-facet, fig.width=12, fig.height=8}
# Create alliance for faceting
data_long <- data %>%
  pivot_longer(cols = c(nato, csto, neutral),
               names_to = "alliance",
               values_to = "membership") %>%
  filter(membership == 1) %>%
  mutate(
    alliance = factor(alliance, levels = c("nato", "csto", "neutral")),
    state_indicator = factor(paste(country, treatment, sep = ", "))
  )

data_long %>%
  filter(state_owned == 1) %>%
  ggplot(aes(x = running, y = sentiment_clean, group = state_indicator, color = country)) +
  geom_smooth(method = "lm", se = FALSE) +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  facet_wrap(~alliance, nrow = 2) +
  labs(
    title = "Effect of Invasion on State Media Sentiment by Country",
    subtitle = "Faceted by Alliance",
    x = "Days Pre/Post Invasion",
    y = "Sentiment"
  )
```

# Summary Table (Table 3)

```{r table3}
note_text <- "All standard errors are clustered at the source level. Model 1 uses no fixed effects. Model 2 uses full data with topic fixed effects. Model 3 uses the optimal bandwidth with topic fixed effects. Model 4 omits military-related articles and uses a re-optimized bandwidth. Model 5 uses only Russian-related (non-military) articles with a re-optimized bandwidth."
note_wrapped <- str_wrap(note_text, width = 80)

table_3 <- modelsummary(
  list("(1)" = model5a, "(2)" = model5a_full, "(3)" = model5a_opt,
       "(4)" = model5a_opt_non_mil, "(5)" = model5a_opt_russian),
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors",
  title = "Russian Alignment: Difference in Discontinuity Analysis",
  notes = note_wrapped
)

table_3
```

## Summary Table: By Topic (Optimal Bandwidth)

```{r table3b}
note_topic_opt <- "All standard errors are clustered at the source level. Each model uses a per-topic re-optimized bandwidth. State media in non-NATO countries only."
note_topic_opt_wrapped <- str_wrap(note_topic_opt, width = 80)

table_3b <- modelsummary(
  list("Political" = model5a_opt_pol, "Military" = model5a_opt_mil,
       "Economic" = model5a_opt_econ, "Cultural" = model5a_opt_cult, "Other" = model5a_opt_oth),
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors",
  title = "Russian Alignment By Topic (Per-Topic Optimal Bandwidth)",
  notes = note_topic_opt_wrapped
)

table_3b
```

## Summary Table: By Topic (Full Data)

```{r table3c}
note_topic_full <- "All standard errors are clustered at the source level. Each model uses the full dataset (no bandwidth restriction). State media in non-NATO countries only."
note_topic_full_wrapped <- str_wrap(note_topic_full, width = 80)

table_3c <- modelsummary(
  list("Political" = model5a_full_pol, "Military" = model5a_full_mil,
       "Economic" = model5a_full_econ, "Cultural" = model5a_full_cult, "Other" = model5a_full_oth),
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors",
  title = "Russian Alignment By Topic (Full Data)",
  notes = note_topic_full_wrapped
)

table_3c
```

# Save Results

```{r save}
results_het <- list(
  model5a = model5a,
  model5a_full = model5a_full,
  model5a_opt = model5a_opt,
  model5a_opt_non_mil = model5a_opt_non_mil,
  model5a_opt_russian = model5a_opt_russian,
  model5a_csto = model5a_csto,
  model5a_neutral = model5a_neutral,
  model5a_opt_pol = model5a_opt_pol,
  model5a_opt_mil = model5a_opt_mil,
  model5a_opt_econ = model5a_opt_econ,
  model5a_opt_cult = model5a_opt_cult,
  model5a_opt_oth = model5a_opt_oth,
  model5a_full_pol = model5a_full_pol,
  model5a_full_mil = model5a_full_mil,
  model5a_full_econ = model5a_full_econ,
  model5a_full_cult = model5a_full_cult,
  model5a_full_oth = model5a_full_oth,
  model6a = model6a,
  model6a_full = model6a_full,
  model6a_opt = model6a_opt,
  model6a_opt_non_mil = model6a_opt_non_mil,
  model6a_opt_russian = model6a_opt_russian,
  model6a_opt_pol = model6a_opt_pol,
  model6a_opt_mil = model6a_opt_mil,
  model6a_opt_econ = model6a_opt_econ,
  model6a_opt_cult = model6a_opt_cult,
  model6a_opt_oth = model6a_opt_oth,
  model6a_full_pol = model6a_full_pol,
  model6a_full_mil = model6a_full_mil,
  model6a_full_econ = model6a_full_econ,
  model6a_full_cult = model6a_full_cult,
  model6a_full_oth = model6a_full_oth,
  optimal_bandwidth_ethnic = optimal_bw_ethnic,
  optimal_bw_ethnic_pol = optimal_bw_ethnic_pol,
  optimal_bw_ethnic_mil = optimal_bw_ethnic_mil,
  optimal_bw_ethnic_econ = optimal_bw_ethnic_econ,
  optimal_bw_ethnic_cult = optimal_bw_ethnic_cult,
  optimal_bw_ethnic_oth = optimal_bw_ethnic_oth,
  optimal_bandwidth_align = optimal_bw_align,
  optimal_bw_align_pol = optimal_bw_align_pol,
  optimal_bw_align_mil = optimal_bw_align_mil,
  optimal_bw_align_econ = optimal_bw_align_econ,
  optimal_bw_align_cult = optimal_bw_align_cult,
  optimal_bw_align_oth = optimal_bw_align_oth,
  loo_results = loo_results,
  loo_summary = loo_summary,
  model_placebo_nonmil = model_placebo_nonmil,
  optimal_bw_placebo_nonmil = optimal_bw_placebo_nonmil
)

saveRDS(results_het, file.path(DATA_INTERMEDIATE, "06_heterogeneity_results.rds"))
cat("Results saved to:", file.path(DATA_INTERMEDIATE, "06_heterogeneity_results.rds"), "\n")
```

# Session Info

```{r session-info}
print_session_info()
```
