---
title: "06a - Russian Alignment Analysis (Probabilistic Time Assignment) (CSTO vs Neutral)"
author: "Donald Moratz"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

# Overview

This script examines heterogeneous treatment effects by Russian alignment (CSTO vs Neutral) only, using probabilistic time assignment.

**Inputs:**
- `data/intermediate/02_cleaned_data.rds`
- `data/intermediate/02_data_non_ukraine.rds`

**Outputs:**
- Table 3I (Russian Alignment)

```{r setup-prob, include=FALSE}
source("00_setup.R")
knitr::opts_chunk$set(fig.path = paste0(FIGURES_HETEROGENEITY_PROB, "/"))
options(digits = 10)

set.seed(3184)
```

# Load Data

```{r load-prob}
data <- readRDS(file.path(DATA_INTERMEDIATE, "02_cleaned_data.rds"))
data_non_ukraine <- readRDS(file.path(DATA_INTERMEDIATE, "02_data_non_ukraine.rds"))

cat("Full data:", nrow(data), "articles\n")
cat("Non-Ukraine data:", nrow(data_non_ukraine), "articles\n")

data <- data %>% mutate(across(c(topic_clean, country, source_domain), as.factor))
data_non_ukraine <- data_non_ukraine %>% mutate(across(c(topic_clean, country, source_domain), as.factor))
```

# Russian Alignment Analysis (CSTO vs Neutral)

## Create Alignment Subsets

```{r alignment-data-prob}
# Filter to non-NATO countries for alignment analysis
data_align <- data %>%
  filter(nato == 0)%>%
  drop_na()

# Create alignment indicator
data_align <- data_align %>%
  mutate(align_indicator = factor(case_when(
    indicator == 1 & csto == 1 ~ "Pre. Ind. CSTO",
    indicator == 1 & csto == 0 ~ "Pre. Ind. Neut",
    indicator == 2 & csto == 1 ~ "Pre. State CSTO",
    indicator == 2 & csto == 0 ~ "Pre. State Neut",
    indicator == 3 & csto == 1 ~ "Post Ind. CSTO",
    indicator == 3 & csto == 0 ~ "Post Ind. Neut",
    indicator == 4 & csto == 1 ~ "Post State CSTO",
    indicator == 4 & csto == 0 ~ "Post State Neut"
  ),
  levels = c("Pre. Ind. CSTO", "Pre. Ind. Neut", "Pre. State CSTO",
             "Pre. State Neut", "Post Ind. CSTO", "Post Ind. Neut",
             "Post State CSTO", "Post State Neut")))

cat("Non-NATO countries sample:", nrow(data_align), "articles\n")
cat("CSTO:", sum(data_align$csto), "\n")
cat("Neutral:", sum(data_align$csto == 0), "\n")
```

## Visualization: Independent Media by Alignment

```{r align-ind-plot-prob, fig.width=10, fig.height=7}
agg_data_align_ind <- data_align %>%
  filter(state_owned == 0) %>%
  group_by(running_probabilistic, csto) %>%
  summarize(sentiment_clean = mean(sentiment_clean), num_obs = n(), .groups = "drop")

data_align %>%
  filter(state_owned == 0) %>%
  ggplot(aes(x = running_probabilistic, y = sentiment_clean, group = align_indicator, color = align_indicator)) +
  geom_point(data = agg_data_align_ind,
             aes(x = running_probabilistic, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = COLORS_DISCS, name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on Independent Media Sentiment (Probabilistic)",
    subtitle = "Neutral vs Russia Aligned, Difference in Discontinuities",
    x = "Hours Pre/Post Invasion",
    y = "Sentiment"
  )
```

## Visualization: State Media by Alignment

```{r align-state-plot-prob, fig.width=10, fig.height=7}
agg_data_align_state <- data_align %>%
  filter(state_owned == 1) %>%
  group_by(running_probabilistic, csto) %>%
  summarize(sentiment_clean = mean(sentiment_clean), num_obs = n(), .groups = "drop")

state_align_discs_graph <- data_align %>%
  filter(state_owned == 1) %>%
  ggplot(aes(x = running_probabilistic, y = sentiment_clean, group = align_indicator, color = align_indicator)) +
  geom_point(data = agg_data_align_state,
             aes(x = running_probabilistic, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = COLORS_DISCS, name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on State Media Sentiment (Probabilistic)",
    subtitle = "Neutral vs Russia Aligned, Difference in Discontinuities",
    x = "Hours Pre/Post Invasion",
    y = "Sentiment"
  )

state_align_discs_graph

ggsave(plot = state_align_discs_graph,
       file.path(FIGURES_HETEROGENEITY_PROB, "state_align_discs_prob.png"),
       width = 10, height = 7)
```

## Pre-Trend Diagnostic: State Media in Russia-Aligned Countries

Addresses the concern that sentiment toward Russia may have turned negative *before* the
Feb 24, 2022 invasion (during the troop buildup) in state-owned media of Russia-aligned
countries. We plot the daily mean sentiment for state-owned sources in each aligned country
(Armenia, Azerbaijan, Belarus, Kazakhstan), mark both the Dec 7, 2021 US public-warning
date and the Feb 24, 2022 invasion cutoff, and overlay a linear fit on the pre-invasion
window only so any pre-existing slide is visible.

```{r pretrend-by-country-aligned-prob, fig.width=10, fig.height=7}
# Buildup display window (trim to keep the pre-invasion period readable)
PRETREND_START <- as.Date("2021-06-01")
PRETREND_END   <- as.Date("2022-06-01")
INVASION_DATE  <- as.Date("2022-02-24")
WARNING_DATE   <- as.Date("2021-12-07")

# State-owned media in the Russia-aligned (CSTO) group; Ukraine already excluded (NATO)
data_pretrend <- data %>%
  filter(country %in% CSTO_COUNTRIES, state_owned == 1,
         date_publish >= PRETREND_START, date_publish <= PRETREND_END) %>%
  mutate(country = droplevels(country))

# Daily mean sentiment per country (same outcome + daily aggregation as other figures)
agg_pretrend <- data_pretrend %>%
  group_by(country, date_publish) %>%
  summarize(sentiment_clean = mean(sentiment_clean, na.rm = TRUE),
            num_obs = n(), .groups = "drop")

# Pre-invasion daily means only (the linear fit is restricted to this window)
agg_pretrend_pre <- agg_pretrend %>%
  filter(date_publish < INVASION_DATE)

pretrend_by_country_aligned_graph <- ggplot(agg_pretrend,
                                             aes(x = date_publish, y = sentiment_clean)) +
  geom_point(aes(size = num_obs), alpha = 0.2, inherit.aes = TRUE) +
  geom_smooth(data = agg_pretrend_pre, method = "lm", se = TRUE, color = "red4") +
  geom_vline(xintercept = INVASION_DATE, linetype = "dashed", alpha = 0.7) +
  geom_vline(xintercept = WARNING_DATE, linetype = "dotted", color = "grey30") +
  scale_size(name = "Observations") +
  facet_wrap(~ country, scales = "free_y") +
  theme_classic() +
  labs(
    title = "Pre-Invasion Sentiment Trend in State Media (Probabilistic)",
    subtitle = "Russia-aligned countries; dotted = Dec 7 warning, dashed = Feb 24 invasion",
    x = "Publication date",
    y = "Mean sentiment toward Russia"
  )

pretrend_by_country_aligned_graph

ggsave(plot = pretrend_by_country_aligned_graph,
       file.path(FIGURES_HETEROGENEITY_PROB, "pretrend_by_country_aligned.png"),
       width = 10, height = 7)
```

```{r pretrend-slopes-aligned-prob}
# Per-country pre-invasion linear slope (fit on the plotted daily means).
# Slope is in sentiment units per day; also reported per 30 days for readability.
pretrend_slopes <- agg_pretrend_pre %>%
  group_by(country) %>%
  group_modify(~ {
    fit <- lm(sentiment_clean ~ as.numeric(date_publish), data = .x)
    ct <- summary(fit)$coefficients["as.numeric(date_publish)", ]
    tibble(
      n_days       = nrow(.x),
      slope_day    = ct["Estimate"],
      slope_30day  = ct["Estimate"] * 30,
      std_error    = ct["Std. Error"],
      p_value      = ct["Pr(>|t|)"]
    )
  }) %>%
  ungroup()

cat("=== Pre-invasion sentiment slope in state media, by Russia-aligned country ===\n")
cat("(slope in sentiment units per day; slope_30day = per 30 days)\n\n")
print(as.data.frame(pretrend_slopes), row.names = FALSE, digits = 4)

# Persist alongside the figure the slopes describe, so the numbers are available
# without re-rendering this script.
write_csv(pretrend_slopes,
          file.path(FIGURES_HETEROGENEITY_PROB, "pretrend_slopes_aligned.csv"))
cat("\nSlopes saved to:",
    file.path(FIGURES_HETEROGENEITY_PROB, "pretrend_slopes_aligned.csv"), "\n")
```

Replica of the figure above with a later start date (Dec 1, 2021) to confirm the
pre-invasion trend lines are not an artifact of fitting across a long (nine-month) window.
INVASION_DATE and WARNING_DATE are reused from the chunk above.

```{r pretrend-by-country-aligned-dec-prob, fig.width=10, fig.height=7}
# Shorter buildup display window (later start; same invasion / warning markers)
PRETREND_START_DEC <- as.Date("2021-12-01")

data_pretrend_dec <- data %>%
  filter(country %in% CSTO_COUNTRIES, state_owned == 1,
         date_publish >= PRETREND_START_DEC, date_publish <= PRETREND_END) %>%
  mutate(country = droplevels(country))

agg_pretrend_dec <- data_pretrend_dec %>%
  group_by(country, date_publish) %>%
  summarize(sentiment_clean = mean(sentiment_clean, na.rm = TRUE),
            num_obs = n(), .groups = "drop")

# Pre-invasion daily means only (linear fit restricted to this window)
agg_pretrend_dec_pre <- agg_pretrend_dec %>%
  filter(date_publish < INVASION_DATE)

pretrend_by_country_aligned_dec_graph <- ggplot(agg_pretrend_dec,
                                                 aes(x = date_publish, y = sentiment_clean)) +
  geom_point(aes(size = num_obs), alpha = 0.2, inherit.aes = TRUE) +
  geom_smooth(data = agg_pretrend_dec_pre, method = "lm", se = TRUE, color = "red4") +
  geom_vline(xintercept = INVASION_DATE, linetype = "dashed", alpha = 0.7) +
  geom_vline(xintercept = WARNING_DATE, linetype = "dotted", color = "grey30") +
  scale_size(name = "Observations") +
  facet_wrap(~ country, scales = "free_y") +
  theme_classic() +
  labs(
    title = "Pre-Invasion Sentiment Trend in State Media, Dec 1 Start (Probabilistic)",
    subtitle = "Russia-aligned countries; dotted = Dec 7 warning, dashed = Feb 24 invasion",
    x = "Publication date",
    y = "Mean sentiment toward Russia"
  )

pretrend_by_country_aligned_dec_graph

ggsave(plot = pretrend_by_country_aligned_dec_graph,
       file.path(FIGURES_HETEROGENEITY_PROB, "pretrend_by_country_aligned_dec.png"),
       width = 10, height = 7)
```

## State Media Alignment Regressions

### CSTO Countries Only

```{r align-csto-prob}
# Filter to CSTO data, non military
data_align_state_csto <- data_align %>%
  filter(state_owned == 1, csto == 1) %>%
  filter(!topic_clean %in% "Military") %>%
  mutate(running_probabilistic = running_probabilistic / 86400.0)

covs_matrix <- model.matrix(~ source_domain + topic_clean - 1, data = data_align_state_csto)

model5a_csto <- rdrobust(
  y = data_align_state_csto$sentiment_clean,
  x = data_align_state_csto$running_probabilistic,
  covs = covs_matrix,
  cluster = data_align_state_csto$source_domain
)

summary(model5a_csto)
```

```{r}
# Applying a Z-Score Transformation
data_align_state_csto <- data_align_state_csto %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) / 
                   sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()

covs_matrix <- model.matrix(~ topic_clean - 1, data = data_align_state_csto)

model5a_csto_z <- rdrobust(
  y = data_align_state_csto$sentiment_z,
  x = data_align_state_csto$running_probabilistic,
  covs = covs_matrix,
  cluster = data_align_state_csto$source_domain
)

summary(model5a_csto_z)
```


### Neutral Countries Only

```{r align-neutral-prob}
# Filter data to neutral countries only
data_align_state_neutral <- data_align %>%
  filter(state_owned == 1, csto == 0) %>%
  filter(!topic_clean %in% "Military") %>%
  mutate(running_probabilistic = running_probabilistic / 86400)

covs_matrix <- model.matrix(~ source_domain + topic_clean - 1, data = data_align_state_neutral)

model5a_neutral <- rdrobust(
  y = data_align_state_neutral$sentiment_clean,
  x = data_align_state_neutral$running_probabilistic,
  covs = covs_matrix,
  cluster = data_align_state_neutral$source_domain
)

summary(model5a_neutral)
```

```{r}
# Applying a Z-Score Transformation
data_align_state_neutral <- data_align_state_neutral %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) / 
                   sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()

covs_matrix <- model.matrix(~ topic_clean - 1, data = data_align_state_neutral)

model5a_neutral_z <- rdrobust(
  y = data_align_state_neutral$sentiment_z,
  x = data_align_state_neutral$running_probabilistic,
  covs = covs_matrix,
  cluster = data_align_state_neutral$source_domain
)

summary(model5a_neutral_z)
```

# Diff-in-Disc Analysis

## Full Data

### Full Data, Topic FEs
Diff-in-Disc: CSTO vs Neutral (State Media)

```{r align-diff-prob}
data_align_state <- data_align %>%
  filter(state_owned == 1) %>%
  mutate(source_domain = droplevels(source_domain)) %>%
  mutate(running_probabilistic = running_probabilistic / 86400)

model5a <- feols(sentiment_clean ~ running_probabilistic * treatment * csto | topic_clean,
                 cluster = ~source_domain,
                 data = data_align_state)

summary(model5a)

# Wild cluster bootstrap for model5a
boot_model5a <- run_wild_bootstrap(model5a, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a$se, "\n")
cat("Bootstrap p-value:", boot_model5a$p_val, "\n")
```


### Full Data with FEs

```{r align-full-prob}

model5a_full <- feols(sentiment_clean ~ running_probabilistic * 
                        treatment * csto  
                        | topic_clean + source_domain,
                      cluster = ~source_domain,
                      data = data_align_state)

summary(model5a_full)

# Wild cluster bootstrap for model5a_full
boot_model5a_full <- run_wild_bootstrap(model5a_full, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_full$se, "\n")
cat("Bootstrap p-value:", boot_model5a_full$p_val, "\n")
```

### Sentiment Z

```{r align-diff-prob-z}
data_align_state <- data_align_state %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) / 
                   sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()

model5a_z <- feols(sentiment_z ~ running_probabilistic * treatment * csto | topic_clean,
                 cluster = ~source_domain,
                 data = data_align_state)

summary(model5a_z)

# Wild cluster bootstrap for model5a
boot_model5a_z <- run_wild_bootstrap(model5a_z, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_z$se, "\n")
cat("Bootstrap p-value:", boot_model5a_z$p_val, "\n")
```


## Optimal Bandwidth

### Optimal Bandwidth, Topic FEs

```{r align-optimal-prob}
# Residualize the dependent variable for fixed effects to do bandwidth selection
resid_y <- feols(sentiment_clean ~ 1 | topic_clean + source_domain + csto, 
                 data = data_align_state)$residuals

bw_align <- rdbwselect(y = resid_y,
                       x = data_align_state$running_probabilistic,
                       kernel = "triangular",
                       cluster = data_align_state$source_domain,
                       p = 1,
                       bwselect = "mserd")

optimal_bw_align <- bw_align$bws[1, 1]
cat("Optimal bandwidth:", round(optimal_bw_align, 1), "days\n")

optimal_bandwidth_data_state <- data_align_state %>%
  filter(running_probabilistic < optimal_bw_align, running_probabilistic > -optimal_bw_align)

model5a_opt <- feols(sentiment_clean ~ running_probabilistic * treatment * csto | topic_clean,
                     cluster = ~source_domain,
                     data = optimal_bandwidth_data_state)

summary(model5a_opt)

# Wild cluster bootstrap for model5a_opt
boot_model5a_opt <- run_wild_bootstrap(model5a_opt, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_opt$se, "\n")
cat("Bootstrap p-value:", boot_model5a_opt$p_val, "\n")
```


### Optimal Bandwidth Full FE

```{r align-optimal-prob-full-fe}

model5a_opt_full_fe <- feols(sentiment_clean ~ running_probabilistic
                                     * treatment * csto 
                                       | topic_clean + source_domain,
                                     cluster = ~source_domain,
                                     data = optimal_bandwidth_data_state
                                     )

summary(model5a_opt_full_fe)

# Wild cluster bootstrap for model5a_opt
boot_model5a_opt_full_fe <- run_wild_bootstrap(model5a_opt_full_fe, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_opt_full_fe$se, "\n")
cat("Bootstrap p-value:", boot_model5a_opt_full_fe$p_val, "\n")
```

### Optimal Bandwidth Sentiment Z

```{r align-optimal-prob-z}
# Residualize the dependent variable for fixed effects to do bandwidth selection
resid_y <- feols(sentiment_z ~ 1 | topic_clean + csto, 
                 data = data_align_state)$residuals

bw_align <- rdbwselect(y = resid_y,
                       x = data_align_state$running_probabilistic,
                       kernel = "triangular",
                       cluster = data_align_state$source_domain,
                       p = 1,
                       bwselect = "mserd")

optimal_bw_align <- bw_align$bws[1, 1]
cat("Optimal bandwidth:", round(optimal_bw_align, 1), "days\n")

optimal_bandwidth_data_state <- data_align_state %>%
  filter(running_probabilistic < optimal_bw_align, running_probabilistic > -optimal_bw_align)

model5a_opt_z <- feols(sentiment_z ~ running_probabilistic * treatment * csto | topic_clean,
                     cluster = ~source_domain,
                     data = optimal_bandwidth_data_state)

summary(model5a_opt_z)

# Wild cluster bootstrap for model5a_opt
boot_model5a_opt_z <- run_wild_bootstrap(model5a_opt_z, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_opt_z$se, "\n")
cat("Bootstrap p-value:", boot_model5a_opt_z$p_val, "\n")
```

## Non-Military

### Non-Military Topics

```{r align-non-mil-prob}
data_align_state_non_mil <- data_align_state %>%
  filter(!topic_clean %in% "Military")

# Residualize the dependent variable for fixed effects to do bandwidth selection
resid_y <- feols(sentiment_clean ~ 1 | topic_clean + source_domain + csto, 
                 data = data_align_state_non_mil)$residuals

bw_align_non_mil <- rdbwselect(y = resid_y,
                               x = data_align_state_non_mil$running_probabilistic,
                               kernel = "triangular",
                               cluster = data_align_state_non_mil$source_domain,
                               p = 1,
                               bwselect = "mserd")

optimal_bw_align_non_mil <- bw_align_non_mil$bws[1, 1]
cat("Optimal bandwidth (non-mil):", round(optimal_bw_align_non_mil, 1), "days\n")

optimal_bandwidth_data_state_non_mil <- data_align_state_non_mil %>%
  filter(running_probabilistic < optimal_bw_align_non_mil, running_probabilistic > -optimal_bw_align_non_mil)

model5a_opt_non_mil <- feols(sentiment_clean ~ running_probabilistic 
                             * treatment * csto | topic_clean,
                             cluster = ~source_domain,
                             data = optimal_bandwidth_data_state_non_mil)

summary(model5a_opt_non_mil)

# Wild cluster bootstrap for model5a_opt_non_mil
boot_model5a_opt_non_mil <- run_wild_bootstrap(model5a_opt_non_mil, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_opt_non_mil$se, "\n")
cat("Bootstrap p-value:", boot_model5a_opt_non_mil$p_val, "\n")
```

### Non-Military Topics, Full FE

```{r align-non-mil-prob-full-fe}

model5a_opt_non_mil_full_fe <- feols(sentiment_clean ~ running_probabilistic
                                     * treatment * csto
                                       | topic_clean + source_domain,
                                     cluster = ~source_domain,
                                     data = optimal_bandwidth_data_state_non_mil
                                     )

summary(model5a_opt_non_mil_full_fe)

# Wild cluster bootstrap for model5a_opt_non_mil
boot_model5a_opt_non_mil_full_fe <- run_wild_bootstrap(model5a_opt_non_mil_full_fe, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_opt_non_mil_full_fe$se, "\n")
cat("Bootstrap p-value:", boot_model5a_opt_non_mil_full_fe$p_val, "\n")
```

### Effect Size

```{r align-effect-prob}
sd_state_owned <- sd(data_align_state$sentiment_clean)
cat("SD of sentiment (state media):", round(sd_state_owned, 3), "\n")

coef_csto_int <- model5a_opt_non_mil_full_fe$coeftable["treatment:csto", "Estimate"]
cat("CSTO x Treatment interaction effect (in SD):", round(coef_csto_int / sd_state_owned, 3), "\n")
```



### Non-Military, Z-Score

```{r align-non-mil-prob-z}
# Create New z score
data_align_state_non_mil <- data_align_state_non_mil %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) / 
                   sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()


# Residualize the dependent variable for fixed effects to do bandwidth selection
resid_y <- feols(sentiment_z ~ 1 | topic_clean + csto, 
                 data = data_align_state_non_mil)$residuals

bw_align_non_mil <- rdbwselect(y = resid_y,
                               x = data_align_state_non_mil$running_probabilistic,
                               kernel = "triangular",
                               cluster = data_align_state_non_mil$source_domain,
                               p = 1,
                               bwselect = "mserd")

optimal_bw_align_non_mil <- bw_align_non_mil$bws[1, 1]
cat("Optimal bandwidth (non-mil):", round(optimal_bw_align_non_mil, 1), "days\n")

optimal_bandwidth_data_state_non_mil <- data_align_state_non_mil %>%
  filter(running_probabilistic < optimal_bw_align_non_mil, running_probabilistic > -optimal_bw_align_non_mil)

model5a_opt_non_mil_z <- feols(sentiment_z ~ running_probabilistic 
                             * treatment * csto | topic_clean,
                             cluster = ~source_domain,
                             data = optimal_bandwidth_data_state_non_mil)

summary(model5a_opt_non_mil_z)

# Wild cluster bootstrap for model5a_opt_non_mil
boot_model5a_opt_non_mil_z <- run_wild_bootstrap(model5a_opt_non_mil_z, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_opt_non_mil_z$se, "\n")
cat("Bootstrap p-value:", boot_model5a_opt_non_mil_z$p_val, "\n")
```


```{r}

# Prepare the data for plotting
plot_data <- optimal_bandwidth_data_state_non_mil %>%
  group_by(source_domain) %>%
  mutate(
    # Recalculate Local Z-score
    sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) / 
                   sd(sentiment_clean, na.rm = TRUE)
  ) %>%
  ungroup() %>%
  select(source_domain, sentiment_clean, sentiment_z) %>%
  pivot_longer(cols = c(sentiment_clean, sentiment_z), 
               names_to = "Type", values_to = "Value")

# Plotting the comparison
zscore_comp <- ggplot(plot_data, aes(x = Value, y = source_domain, fill = Type)) +
  geom_density_ridges(alpha = 0.5, scale = 0.9) +
  facet_wrap(~Type, scales = "free_x") +
  theme_minimal() +
  labs(title = "Ternary Sentiment vs. Z-Scored Sentiment by Source",
       subtitle = "Local Z-scoring centers each source and adjusts for their specific volatility",
       x = "Sentiment Value",
       y = "Media Outlet") +
  scale_fill_manual(values = c("sentiment_clean" = "#69b3a2", "sentiment_z" = "#404080"))

zscore_comp

ggsave(plot = zscore_comp,
       file.path(FIGURES_HETEROGENEITY_PROB, "sentiment_zscore_comparison_prob.png"),
       width = 10, height = 7)
```


## Russian Only

### Russian-Related Articles Only

```{r align-russian-prob}
data_align_state_russian <- data_align_state %>%
  filter(!topic_clean %in% "Military") %>%
  filter(!Russian.Involvement == "Not")

# Residualize the dependent variable for fixed effects to do bandwidth selection
resid_y <- feols(sentiment_clean ~ 1 | topic_clean + source_domain + csto, 
                 data = data_align_state_russian)$residuals

bw_align_russian <- rdbwselect(y = resid_y,
                               x = data_align_state_russian$running_probabilistic,
                               kernel = "triangular",
                               cluster = data_align_state_russian$source_domain,
                               p = 1,
                               bwselect = "mserd")

optimal_bw_align_russian <- bw_align_russian$bws[1, 1]
cat("Optimal bandwidth (russian):", round(optimal_bw_align_russian, 1), "days\n")

optimal_bandwidth_data_state_russian <- data_align_state_russian %>%
  filter(running_probabilistic < optimal_bw_align_russian, running_probabilistic > -optimal_bw_align_russian)

model5a_opt_russian <- feols(sentiment_clean ~ running_probabilistic * 
                               treatment * csto | topic_clean,
                             cluster = ~source_domain,
                             data = optimal_bandwidth_data_state_russian)

summary(model5a_opt_russian)

# Wild cluster bootstrap for model5a_opt_russian
boot_model5a_opt_russian <- run_wild_bootstrap(model5a_opt_russian, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_opt_russian$se, "\n")
cat("Bootstrap p-value:", boot_model5a_opt_russian$p_val, "\n")
```

### Russia Only, Full FE

```{r align-russian-prob-full-fe}

model5a_opt_rus_full_fe <- feols(sentiment_clean ~ running_probabilistic
                                    * treatment * csto
                                       | topic_clean + source_domain,
                                     cluster = ~source_domain,
                                     data = optimal_bandwidth_data_state_russian
                                     )

summary(model5a_opt_rus_full_fe)

# Wild cluster bootstrap for model5a_opt_non_mil
boot_model5a_opt_rus_full_fe <- run_wild_bootstrap(model5a_opt_rus_full_fe, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_opt_rus_full_fe$se, "\n")
cat("Bootstrap p-value:", boot_model5a_opt_rus_full_fe$p_val, "\n")
```


### Russia Only, Sentiment Z

```{r align-russian-prob-z}
# Create New z score
data_align_state_russian <- data_align_state_russian %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) / 
                   sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()


# Residualize the dependent variable for fixed effects to do bandwidth selection
resid_y <- feols(sentiment_z ~ 1 | topic_clean + csto, 
                 data = data_align_state_russian)$residuals

bw_align_russian <- rdbwselect(y = resid_y,
                               x = data_align_state_russian$running_probabilistic,
                               kernel = "triangular",
                               cluster = data_align_state_russian$source_domain,
                               p = 1,
                               bwselect = "mserd")

optimal_bw_align_russian <- bw_align_russian$bws[1, 1]
cat("Optimal bandwidth (non-mil):", round(optimal_bw_align_russian, 1), "days\n")

optimal_bandwidth_data_state_russian <- data_align_state_russian %>%
  filter(running_probabilistic < optimal_bw_align_russian, running_probabilistic > -optimal_bw_align_russian)

model5a_opt_russian_z <- feols(sentiment_z ~ running_probabilistic 
                             * treatment * csto | topic_clean,
                             cluster = ~source_domain,
                             data = optimal_bandwidth_data_state_russian)

summary(model5a_opt_russian_z)

# Wild cluster bootstrap for model5a_opt_non_mil
boot_model5a_opt_russian_z <- run_wild_bootstrap(model5a_opt_russian_z, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_opt_russian_z$se, "\n")
cat("Bootstrap p-value:", boot_model5a_opt_russian_z$p_val, "\n")
```

# By Topic

## By-Topic Models: Full Data

```{r topic-full-het-prob}
data_align_state_pol <- data_align_state %>% filter(topic_clean == "Political")
data_align_state_mil <- data_align_state %>% filter(topic_clean == "Military")
data_align_state_econ <- data_align_state %>% filter(topic_clean == "Economic")
data_align_state_cult <- data_align_state %>% filter(topic_clean == "Culture")
data_align_state_oth <- data_align_state %>% filter(topic_clean == "Other")

model5a_full_pol <- feols(sentiment_z ~ running_probabilistic * treatment * csto,
                          cluster = ~source_domain,
                          data = data_align_state_pol)
model5a_full_mil <- feols(sentiment_z ~ running_probabilistic * treatment * csto,
                          cluster = ~source_domain,
                          data = data_align_state_mil)
model5a_full_econ <- feols(sentiment_z ~ running_probabilistic * treatment * csto,
                           cluster = ~source_domain,
                           data = data_align_state_econ)
model5a_full_cult <- feols(sentiment_z ~ running_probabilistic * treatment * csto,
                           cluster = ~source_domain,
                           data = data_align_state_cult)
model5a_full_oth <- feols(sentiment_z ~ running_probabilistic * treatment * csto,
                          cluster = ~source_domain,
                          data = data_align_state_oth)

# Wild cluster bootstrap for topic-specific model5a (full data)
boot_model5a_full_pol <- run_wild_bootstrap(model5a_full_pol, "treatment:csto")
boot_model5a_full_mil <- run_wild_bootstrap(model5a_full_mil, "treatment:csto")
boot_model5a_full_econ <- run_wild_bootstrap(model5a_full_econ, "treatment:csto")
boot_model5a_full_cult <- run_wild_bootstrap(model5a_full_cult, "treatment:csto")
boot_model5a_full_oth <- run_wild_bootstrap(model5a_full_oth, "treatment:csto")
```

## By-Topic Models: Per-Topic Optimal Bandwidth

```{r topic-opt-het-prob}
# Political
bw_align_pol <- rdbwselect(y = data_align_state_pol$sentiment_z, 
                           x = data_align_state_pol$running_probabilistic,
                           kernel = "triangular", 
                           cluster = data_align_state_pol$source_domain, 
                           p = 1, 
                           bwselect = "mserd")

optimal_bw_align_pol <- bw_align_pol$bws[1, 1]

cat("Political optimal bandwidth:", round(optimal_bw_align_pol, 1), "days\n")

opt_align_pol <- data_align_state_pol %>% filter(running_probabilistic < optimal_bw_align_pol, 
                                                 running_probabilistic > -optimal_bw_align_pol)

# Military
bw_align_mil <- rdbwselect(y = data_align_state_mil$sentiment_z, 
                           x = data_align_state_mil$running_probabilistic,
                           kernel = "triangular", 
                           cluster = data_align_state_mil$source_domain, 
                           p = 1, 
                           bwselect = "mserd")

optimal_bw_align_mil <- bw_align_mil$bws[1, 1]

cat("Military optimal bandwidth:", round(optimal_bw_align_mil, 1), "days\n")

opt_align_mil <- data_align_state_mil %>% filter(running_probabilistic < optimal_bw_align_mil, 
                                                 running_probabilistic > -optimal_bw_align_mil)

# Economic
bw_align_econ <- rdbwselect(y = data_align_state_econ$sentiment_z, 
                            x = data_align_state_econ$running_probabilistic,
                            kernel = "triangular", 
                            cluster = data_align_state_econ$source_domain, 
                            p = 1, 
                            bwselect = "mserd")

optimal_bw_align_econ <- bw_align_econ$bws[1, 1]

cat("Economic optimal bandwidth:", round(optimal_bw_align_econ, 1), "days\n")

opt_align_econ <- data_align_state_econ %>% filter(running_probabilistic < optimal_bw_align_econ, 
                                                   running_probabilistic > -optimal_bw_align_econ)

# Culture
bw_align_cult <- rdbwselect(y = data_align_state_cult$sentiment_z, 
                            x = data_align_state_cult$running_probabilistic,
                            kernel = "triangular", 
                            cluster = data_align_state_cult$source_domain, 
                            p = 1, 
                            bwselect = "mserd")

optimal_bw_align_cult <- bw_align_cult$bws[1, 1]

cat("Culture optimal bandwidth:", round(optimal_bw_align_cult, 1), "days\n")

opt_align_cult <- data_align_state_cult %>% filter(running_probabilistic < optimal_bw_align_cult, 
                                                   running_probabilistic > -optimal_bw_align_cult)

# Other
bw_align_oth <- rdbwselect(y = data_align_state_oth$sentiment_z, 
                           x = data_align_state_oth$running_probabilistic,
                           kernel = "triangular", 
                           cluster = data_align_state_oth$source_domain, 
                           p = 1, 
                           bwselect = "mserd")

optimal_bw_align_oth <- bw_align_oth$bws[1, 1]

cat("Other optimal bandwidth:", round(optimal_bw_align_oth, 1), "seconds\n")

opt_align_oth <- data_align_state_oth %>% filter(running_probabilistic < optimal_bw_align_oth, 
                                                 running_probabilistic > -optimal_bw_align_oth)

# Models
model5a_opt_pol <- feols(sentiment_z ~ running_probabilistic * treatment * csto,
                         cluster = ~source_domain,
                         data = opt_align_pol)
summary(model5a_opt_pol)

model5a_opt_mil <- feols(sentiment_z ~ running_probabilistic * treatment * csto,
                         cluster = ~source_domain,
                         data = opt_align_mil)
summary(model5a_opt_mil)

model5a_opt_econ <- feols(sentiment_z ~ running_probabilistic * treatment * csto,
                          cluster = ~source_domain,
                          data = opt_align_econ)
summary(model5a_opt_econ)

model5a_opt_cult <- feols(sentiment_z ~ running_probabilistic * treatment * csto,
                          cluster = ~source_domain,
                          data = opt_align_cult)
summary(model5a_opt_cult)

model5a_opt_oth <- feols(sentiment_z ~ running_probabilistic * treatment * csto,
                         cluster = ~source_domain,
                         data = opt_align_oth)
summary(model5a_opt_oth)


# Wild cluster bootstrap for topic-specific model5a (optimal BW)
boot_model5a_opt_pol <- run_wild_bootstrap(model5a_opt_pol, "treatment:csto")
cat("Bootstrap p-value:", boot_model5a_opt_pol$p_val, "\n")
boot_model5a_opt_mil <- run_wild_bootstrap(model5a_opt_mil, "treatment:csto")
cat("Bootstrap p-value:", boot_model5a_opt_mil$p_val, "\n")
boot_model5a_opt_econ <- run_wild_bootstrap(model5a_opt_econ, "treatment:csto")
cat("Bootstrap p-value:", boot_model5a_opt_econ$p_val, "\n")
boot_model5a_opt_cult <- run_wild_bootstrap(model5a_opt_cult, "treatment:csto")
cat("Bootstrap p-value:", boot_model5a_opt_cult$p_val, "\n")
boot_model5a_opt_oth <- run_wild_bootstrap(model5a_opt_oth, "treatment:csto")
cat("Bootstrap p-value:", boot_model5a_opt_oth$p_val, "\n")
```

# Robustness

## Leave-One-Out Country Robustness

```{r loo-country-prob}
countries <- unique(data_align_state_non_mil$country)
loo_results <- list()

for (cntry in countries) {
  data_loo <- data_align_state_non_mil %>%
    filter(country != cntry)

  # Re-calculate optimal bandwidth for LOO data
  resid_y <- feols(sentiment_z ~ 1 | topic_clean + csto, 
                 data = data_loo)$residuals
  
  bw_loo <- rdbwselect(y = data_loo$sentiment_z,
                       x = data_loo$running_probabilistic,
                       kernel = "triangular",
                       cluster = data_loo$source_domain,
                       p = 1,
                       bwselect = "mserd")

  optimal_bw_loo <- bw_loo$bws[1, 1]

  data_loo_bw <- data_loo %>%
    filter(running_probabilistic < optimal_bw_loo, running_probabilistic > -optimal_bw_loo)

  model_loo <- feols(sentiment_z ~ running_probabilistic * treatment * csto | topic_clean,
                     cluster = ~source_domain,
                     data = data_loo_bw)

  boot_loo <- tryCatch(
    run_wild_bootstrap(model_loo, "treatment:csto", B = 99999),
    error = function(e) list(se = NA, p_val = NA, ci_lower = NA, ci_upper = NA, t_stat = NA)
  )
  loo_results[[cntry]] <- list(
    model = model_loo,
    bandwidth = optimal_bw_loo,
    n = nrow(data_loo_bw),
    country_dropped = cntry,
    boot_p_val = boot_loo$p_val,
    boot_se = boot_loo$se
  )
}

# Extract key coefficient (treatment:csto interaction)
loo_summary <- map_df(names(loo_results), function(cntry) {
  mod <- loo_results[[cntry]]$model
  tibble(
    country_dropped = cntry,
    estimate = coef(mod)["treatment:csto"],
    std_error = se(mod)["treatment:csto"],
    p_value = pvalue(mod)["treatment:csto"],
    n_obs = loo_results[[cntry]]$n,
    bandwidth = loo_results[[cntry]]$bandwidth
  )
})

print(loo_summary)
```

## Placebo Test: December 7th Announcement (Non-Military Topics)

```{r placebo-dec-nonmil-prob}
data_dec_align <- data_align_state_non_mil %>%
  filter(date_publish < "2022-02-19") %>%
  mutate(
    running_probabilistic = as.numeric(difftime(date_publish_probabilistic, as.POSIXct("2021-12-07 00:00:00", tz = "UTC"), units = "secs"))/86400,
    treatment = ifelse(date_publish_probabilistic < as.POSIXct("2021-12-07 00:00:00", tz = "UTC"), 0, 1)
  )

# Find optimal bandwidth for placebo
bw_placebo_nonmil <- rdbwselect(y = data_dec_align$sentiment_z,
                                x = data_dec_align$running_probabilistic,
                                kernel = "triangular",
                                cluster = data_dec_align$source_domain,
                                p = 1,
                                bwselect = "mserd")

optimal_bw_placebo_nonmil <- bw_placebo_nonmil$bws[1, 1]
cat("Placebo optimal bandwidth (non-mil):", round(optimal_bw_placebo_nonmil, 1), "seconds\n")

data_dec_align_bw <- data_dec_align %>%
  filter(running_probabilistic < optimal_bw_placebo_nonmil, running_probabilistic > -optimal_bw_placebo_nonmil)

model_placebo_nonmil <- feols(sentiment_z ~ running_probabilistic * treatment * csto | topic_clean,
                               cluster = ~source_domain,
                               data = data_dec_align_bw)

summary(model_placebo_nonmil)
boot_model_placebo_nonmil <- run_wild_bootstrap(model_placebo_nonmil, "treatment:csto")
cat("Bootstrap SE for treatment:csto (placebo):", boot_model_placebo_nonmil$se, "\n")
cat("Bootstrap p-value (placebo):", boot_model_placebo_nonmil$p_val, "\n")
cat("\nNote: Non-significant treatment effect suggests parallel trends assumption holds.\n")
```

## Placebo Test: December 7th Announcement (Aligned State Media, by Country)

Directly addresses the reviewer concern: a placebo-cutoff RDD restricted to state-owned
media in the Russia-aligned (CSTO) group, estimated **separately for each country**
(Armenia, Azerbaijan, Belarus, Kazakhstan) so cross-country consistency is visible. Each
model uses the z-scored outcome used throughout the CSTO state-media RDDs and rdrobust's
MSE-optimal bandwidth. Because each country has only 2-3 state-owned sources — too few for
cluster-robust inference — standard errors use rdrobust's default (nearest-neighbor
heteroskedasticity-robust) variance rather than clustering by source. A non-significant
discontinuity at the Dec 7, 2021 warning date indicates that sentiment was not already
jumping during the buildup.

```{r placebo-dec-aligned-prob}
# Cutoff constants for the Dec 7, 2021 US public-warning date
DEC7_CUTOFF <- as.POSIXct("2021-12-07 00:00:00", tz = "UTC")

# One placebo RDD per aligned country: state-owned, non-military, pre-invasion.
placebo_aligned_models <- list()

for (cntry in CSTO_COUNTRIES) {
  dat_c <- data_align %>%
    filter(state_owned == 1, country == cntry,
           !topic_clean %in% "Military",
           date_publish < "2022-02-19") %>%
    mutate(
      topic_clean = droplevels(topic_clean),   # drop empty topic levels within this country
      running_probabilistic = as.numeric(difftime(
        date_publish_probabilistic, DEC7_CUTOFF, units = "secs")) / 86400,
      treatment = ifelse(date_publish_probabilistic < DEC7_CUTOFF, 0, 1)
    ) %>%
    # Source-level z-score adjustment (as in the CSTO state-media RDDs)
    group_by(source_domain) %>%
    mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                          sd(sentiment_clean, na.rm = TRUE)) %>%
    ungroup() %>%
    filter(is.finite(sentiment_z))              # drop degenerate single-article sources

  covs_c <- model.matrix(~ topic_clean - 1, data = dat_c)

  # rdrobust default HC (nn) SEs; no clustering (only 2-3 sources per country)
  placebo_aligned_models[[cntry]] <- rdrobust(
    y = dat_c$sentiment_z,
    x = dat_c$running_probabilistic,
    covs = covs_c
  )

  m <- placebo_aligned_models[[cntry]]
  cat("\n--- ", cntry, " ---\n", sep = "")
  cat("Estimate:  ", round(m$coef[1], 3), "\n")
  cat("95% CI:    [", round(m$ci[1, 1], 3), ",", round(m$ci[1, 2], 3), "]\n")
  cat("p-value:   ", round(m$pv[1], 3), "\n")
  cat("Bandwidth: ", round(m$bws[1, 1], 3), "days\n")
  cat("N (within bw):", m$N_h[1] + m$N_h[2], "\n")
  cat("Sources:", paste(sort(unique(dat_c$source_domain)), collapse = ", "), "\n")
}

cat("\nNote: Non-significant discontinuities suggest no pre-invasion jump at the warning date.\n")
```

## Placebo Test: December 7th Announcement (Aligned State Media, Pooled)

The per-country placebos above are estimated on 2-3 sources each, so any single
column is imprecise. This chunk pools all four Russia-aligned countries into one
Dec 7, 2021 placebo RDD, mirroring the per-country estimation exactly (state-owned,
non-military, pre-invasion, source-level z-scored outcome, topic dummies as
covariates, rdrobust's MSE-optimal bandwidth). Pooling gives enough sources to
report a source-clustered variance alongside rdrobust's default nearest-neighbour
HC variance; both are reported so the per-country columns and the pooled column
remain directly comparable.

```{r placebo-dec-aligned-pooled-prob}
# Same sample construction as the per-country loop above, but without the
# country split. DEC7_CUTOFF is defined in the chunk above.
dat_pooled <- data_align %>%
  filter(state_owned == 1, country %in% CSTO_COUNTRIES,
         !topic_clean %in% "Military",
         date_publish < "2022-02-19") %>%
  mutate(
    topic_clean = droplevels(topic_clean),
    country     = droplevels(country),
    running_probabilistic = as.numeric(difftime(
      date_publish_probabilistic, DEC7_CUTOFF, units = "secs")) / 86400,
    treatment = ifelse(date_publish_probabilistic < DEC7_CUTOFF, 0, 1)
  ) %>%
  # Source-level z-score adjustment (as in the per-country placebos)
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                        sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup() %>%
  filter(is.finite(sentiment_z))              # drop degenerate single-article sources

covs_pooled <- model.matrix(~ topic_clean - 1, data = dat_pooled)

# Primary pooled estimate: rdrobust default HC (nn) SEs, matching the per-country columns
placebo_aligned_pooled <- rdrobust(
  y    = dat_pooled$sentiment_z,
  x    = dat_pooled$running_probabilistic,
  covs = covs_pooled
)

# Secondary pooled estimate: source-clustered, viable here because pooling the four
# countries yields enough sources for cluster-robust inference
placebo_aligned_pooled_cl <- rdrobust(
  y       = dat_pooled$sentiment_z,
  x       = dat_pooled$running_probabilistic,
  covs    = covs_pooled,
  cluster = dat_pooled$source_domain
)

cat("\n--- Pooled (all Russia-aligned countries) ---\n")
cat("Countries:", paste(sort(unique(as.character(dat_pooled$country))), collapse = ", "), "\n")
cat("Sources:  ", n_distinct(dat_pooled$source_domain), "\n\n")

for (lab in c("HC (nn), matching per-country columns", "Source-clustered")) {
  m <- if (lab == "Source-clustered") placebo_aligned_pooled_cl else placebo_aligned_pooled
  cat(lab, "\n")
  cat("  Estimate:  ", round(m$coef[1], 3), "\n")
  cat("  Std. Error:", round(m$se[1], 3), "\n")
  cat("  95% CI:    [", round(m$ci[1, 1], 3), ",", round(m$ci[1, 2], 3), "]\n")
  cat("  p-value:   ", round(m$pv[1], 3), "\n")
  cat("  Bandwidth: ", round(m$bws[1, 1], 3), "days\n")
  cat("  N (within bw):", m$N_h[1] + m$N_h[2], "\n")
}
```

### Placebo Estimate Summary (Per-Country and Pooled)

Collects the per-country and pooled placebo estimates into a single tidy table and
writes it beside the appendix table it backs, so the numbers are available without
re-rendering this script.

```{r placebo-dec-aligned-summary-prob}
# One tidy row per rdrobust fit
tidy_placebo_rd <- function(m, label, n_sources) {
  tibble(
    group       = label,
    n_sources   = n_sources,
    estimate    = m$coef[1],
    std_error   = m$se[1],
    ci_lower    = m$ci[1, 1],
    ci_upper    = m$ci[1, 2],
    p_value     = m$pv[1],
    bandwidth   = m$bws[1, 1],
    n_within_bw = m$N_h[1] + m$N_h[2]
  )
}

# Per-country source counts, recomputed on the same filters used in the loop above
placebo_country_sources <- data_align %>%
  filter(state_owned == 1, country %in% CSTO_COUNTRIES,
         !topic_clean %in% "Military",
         date_publish < "2022-02-19") %>%
  group_by(country) %>%
  summarize(n_sources = n_distinct(source_domain), .groups = "drop")

placebo_aligned_estimates <- bind_rows(
  map_df(names(placebo_aligned_models), function(cntry) {
    n_src <- placebo_country_sources$n_sources[placebo_country_sources$country == cntry]
    tidy_placebo_rd(placebo_aligned_models[[cntry]], cntry,
                    if (length(n_src)) n_src else NA_integer_)
  }),
  tidy_placebo_rd(placebo_aligned_pooled, "Pooled (HC)",
                  n_distinct(dat_pooled$source_domain)),
  tidy_placebo_rd(placebo_aligned_pooled_cl, "Pooled (source-clustered)",
                  n_distinct(dat_pooled$source_domain))
)

print(as.data.frame(placebo_aligned_estimates), row.names = FALSE, digits = 4)

dir.create(file.path(FIGURES_TABLES, "prob"), showWarnings = FALSE, recursive = TRUE)
write_csv(placebo_aligned_estimates,
          file.path(FIGURES_TABLES, "prob", "placebo_aligned_estimates.csv"))
cat("\nEstimates saved to:",
    file.path(FIGURES_TABLES, "prob", "placebo_aligned_estimates.csv"), "\n")
```

## Matching

### Initial Match 

```{r}
# Subset to data of interest

matching_data <- optimal_bandwidth_data_state_non_mil %>%
  select(sentiment_z, running, running_probabilistic, treatment, csto, 
         topic_clean, source_domain, country)

# Match on topic and publication day

ps_model <- matchit(
  csto ~ running + topic_clean,
  data = matching_data,
  method = "exact",
  ratio = 1,
)

summary(ps_model)
```

### Assess Balance

```{r}
# Numerical balance check (better)
bal.tab(ps_model, un = TRUE, stats = c("m", "v"), thresholds = c(m = 0.1))
# Want: all standardized mean differences < 0.1 after matching

# Love plot (publication quality)
love <- love.plot(ps_model, binary = "std", thresholds = c(m = 0.1))
love
ggsave(plot = love,
       file.path(FIGURES_HETEROGENEITY_PROB, "love_plot.png"),
       width = 10, height = 7)
```

### Matching analysis

```{r}
# Extract matched data and calculate treatment effects
matched_data <-match.data(ps_model)

matched_model <- feols(sentiment_z ~ running_probabilistic
                                     * treatment * csto |
                                       topic_clean,
                                     cluster = ~source_domain,
                                     data = matched_data
                                     )

summary(matched_model)


# Wild cluster bootstrap for model5a_opt_non_mil
boot_matched_model <- run_wild_bootstrap(matched_model, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_matched_model$se, "\n")
cat("Bootstrap p-value:", boot_matched_model$p_val, "\n")
```



### Total Effect (No Topic Adjustment)

Table 4 Model 3 conditions on topic, so it measures how
Russia-aligned and neutral state media diverged *within* topics. The total effect
also lets the topic mix move. This clone keeps the sample (state-owned, non-NATO,
all articles including military), the source-level z-scored outcome and the source
clustering, and removes topic from both the model and the bandwidth
residualization.

```{r align-optimal-total-prob}
# Following `align-optimal-prob-z`, with topic_clean removed from the
# residualization and from the fixed effects.
resid_y_total <- feols(sentiment_z ~ 1 | csto,
                       data = data_align_state)$residuals

bw_align_total <- rdbwselect(y = resid_y_total,
                             x = data_align_state$running_probabilistic,
                             kernel = "triangular",
                             cluster = data_align_state$source_domain,
                             p = 1,
                             bwselect = "mserd")

optimal_bw_align_total <- bw_align_total$bws[1, 1]
cat("Total-effect optimal bandwidth:", round(optimal_bw_align_total, 1), "days\n")

optimal_bandwidth_data_state_total <- data_align_state %>%
  filter(running_probabilistic < optimal_bw_align_total,
         running_probabilistic > -optimal_bw_align_total)

model5a_opt_z_total <- feols(sentiment_z ~ running_probabilistic * treatment * csto,
                             cluster = ~source_domain,
                             data = optimal_bandwidth_data_state_total)

summary(model5a_opt_z_total)

boot_model5a_opt_z_total <- run_wild_bootstrap(model5a_opt_z_total, "treatment:csto")
cat("Bootstrap SE for treatment:csto (total):", boot_model5a_opt_z_total$se, "\n")
cat("Bootstrap p-value (total):", boot_model5a_opt_z_total$p_val, "\n")

# --- Total effect on the main sample: military omitted, no topic FE ---------
# Completes the 2x2 of {all topics, military omitted} x {topic FE, no topic FE}.
# data_align_state_non_mil is the sample Table 4 Model 4 is fitted on.
resid_y_nonmil_total <- feols(sentiment_z ~ 1 | csto,
                              data = data_align_state_non_mil)$residuals

bw_align_nonmil_total <- rdbwselect(y = resid_y_nonmil_total,
                                    x = data_align_state_non_mil$running_probabilistic,
                                    kernel = "triangular",
                                    cluster = data_align_state_non_mil$source_domain,
                                    p = 1,
                                    bwselect = "mserd")

optimal_bw_align_nonmil_total <- bw_align_nonmil_total$bws[1, 1]
cat("Total-effect optimal bandwidth (military omitted):",
    round(optimal_bw_align_nonmil_total, 1), "days\n")

optimal_bandwidth_data_state_nonmil_total <- data_align_state_non_mil %>%
  filter(running_probabilistic < optimal_bw_align_nonmil_total,
         running_probabilistic > -optimal_bw_align_nonmil_total)

model5a_opt_non_mil_z_total <- feols(sentiment_z ~ running_probabilistic * treatment * csto,
                                     cluster = ~source_domain,
                                     data = optimal_bandwidth_data_state_nonmil_total)

summary(model5a_opt_non_mil_z_total)

boot_model5a_opt_non_mil_z_total <- run_wild_bootstrap(model5a_opt_non_mil_z_total,
                                                       "treatment:csto")
cat("Bootstrap p-value (total, military omitted):",
    boot_model5a_opt_non_mil_z_total$p_val, "\n")
```

### Country-Level Clustering Check

Table 4 Model 3 clusters inference at the source level, but the treatment
contrast here is between country groups and only eight countries contribute
state-owned sources. This chunk re-runs the same WCR bootstrap clustered by
country for the two H3a RDIDs the paper reports (the optimal-bandwidth
interaction and the matched interaction) and reports both levels side by side.
Clustering affects inference only, so the estimates must be unchanged.

```{r country-cluster-check-h3a-prob}
# Drop unused factor levels before bootstrapping: boottest() errors on cluster
# levels with no observations, and this file does not droplevels() after the
# bandwidth filter, so the non-NATO samples still declare the NATO countries.
# Dropping them cannot move the estimate (asserted below).
optimal_bandwidth_data_state_dl <- droplevels(optimal_bandwidth_data_state)
matched_data_dl                 <- droplevels(matched_data)

model5a_opt_z_dl <- feols(sentiment_z ~ running_probabilistic * treatment * csto |
                            topic_clean,
                          cluster = ~source_domain, data = optimal_bandwidth_data_state_dl)
matched_model_dl <- feols(sentiment_z ~ running_probabilistic * treatment * csto |
                            topic_clean,
                          cluster = ~source_domain, data = matched_data_dl)

stopifnot(
  isTRUE(all.equal(coef(model5a_opt_z_dl)[["treatment:csto"]],
                   coef(model5a_opt_z)[["treatment:csto"]], tolerance = 0)),
  isTRUE(all.equal(coef(matched_model_dl)[["treatment:csto"]],
                   coef(matched_model)[["treatment:csto"]], tolerance = 0))
)

country_cluster_check <- bind_rows(
  compare_cluster_levels(model5a_opt_z_dl, "treatment:csto", "H3a_table4_model3"),
  compare_cluster_levels(matched_model_dl, "treatment:csto", "H3a_table4_model5")
)

print(as.data.frame(country_cluster_check), row.names = FALSE, digits = 4)
```

### Sensitivity of OVB

```{r}
# Save the bootstrapped p-val
bootstrapped_se <- boot_matched_model$se

# Respecify the model using lm
lm_model <- lm(sentiment_z ~ running_probabilistic * treatment * csto +
                 factor(topic_clean),
               data = matched_data)


# Sensitivity analysis
sensitivity <- sensemakr(
  model = lm_model,
  treatment = "treatment:csto",
  benchmark_covariates = c("treatment"),
  kd = .25,
  ky = 1,
  reduce = TRUE
)

# Extract coefficient and bootstrapped SE
coef_interest <- coef(lm_model)["treatment:csto"]
boot_se <- boot_matched_model$se
dof <- df.residual(lm_model)

# Corrected t-stat using bootstrapped SE
t_corrected <- coef_interest / boot_se

# Compute robustness values using corrected t-stat
rv_point <- sensemakr::robustness_value(t_statistic = t_corrected, dof = dof, q = 1)
rv_alpha <- sensemakr::robustness_value(t_statistic = t_corrected, dof = dof, q = 1, alpha = 0.05)

cat("RV (q=1):", rv_point, "\n")
cat("RV (q=1, alpha=0.05):", rv_alpha, "\n")
```


```{r}
partial_r2(lm_model, covariates = c("running_probabilistic:treatment",
                                     "running_probabilistic:csto",
                                     "treatment",
                                     "csto"))

all_r2 <- partial_r2(lm_model, covariates = c("running_probabilistic:treatment",
                                     "running_probabilistic:csto",
                                     "treatment",
                                     "csto"))

max_observed <- max(all_r2)

treatment_r2 <- partial_r2(lm_model, covariates = c("treatment"))
```

```{r}
cat("RV:", rv_point, "\n")
cat("Treatment partial R²:", treatment_r2, "\n")
cat("RV is", round(rv_point / treatment_r2, 1), "x the effect of treatment\n")
```


```{r}
# Manually recompute the CI bound using the bootstrapped SE
coef_interest <- coef(lm_model)["treatment:csto"]
rv_ci <- coef_interest / bootstrapped_se

plot(sensitivity,
     xlab = "Partial R² of confounder with CSTO membership",
     ylab = "Partial R² of confounder with sentiment",
     main = "Sensitivity to Unobserved Confounding",
     lim.x = .1,  
     lim.y = .1,
     col.contour = "grey60",
     label.text = FALSE)   # turn off the ugly overlapping label first
text(x = 0.01, y = 0.00005, 
     labels = "treatment", 
     cex = 0.8, pos = 4)
```


```{r}
# Sensitivity Plot

# Extract the data sensemakr uses for the plot
ovb_contour_data <- function(sensitivity, lim = 0.005, custom_se=NULL) {
  
  # Grid of r2dz.x and r2yz.dx values
  r2dz <- seq(0, lim, length.out = 400)
  r2yz <- seq(0, lim, length.out = 400)
  grid <- expand.grid(r2dz.x = r2dz, r2yz.dx = r2yz)
  
  # Extract key stats
  estimate <- sensitivity$sensitivity_stats$estimate
  se <- if (!is.null(custom_se)) custom_se else sensitivity$sensitivity_stats$se
  df <- sensitivity$sensitivity_stats$dof
  
  # Compute adjusted estimate across grid
  grid$adjusted <- mapply(function(r2dz, r2yz) {
    sensemakr::adjusted_estimate(
      estimate = estimate,
      se = se,
      dof = df,
      r2dz.x = r2dz,
      r2yz.dx = r2yz
    )
  }, grid$r2dz.x, grid$r2yz.dx)
  
  return(grid)
}

# Extract benchmark points
benchmark_df <- data.frame(
  r2dz.x = sensitivity$bounds$r2dz.x,
  r2yz.dx = sensitivity$bounds$r2yz.dx,
  label = sensitivity$bounds$bound_label
)

# Extract actual estimate
unadj_est <- round(sensitivity$sensitivity_stats$estimate, 2)

# Build contour data — expand to cover the benchmark point
contour_data <- ovb_contour_data(sensitivity, lim = 0.7, custom_se = boot_se)

sensitivity_plot <- ggplot(contour_data, aes(x = r2dz.x, y = r2yz.dx, z = adjusted)) +
  geom_contour(colour = "grey60",
               breaks = c(-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4)) +
  geom_contour(breaks = 0,
               colour = "red",
               linetype = "dashed",
               linewidth = 0.8) +
  #geom_point(data = benchmark_df,
  #           aes(x = r2dz.x, y = r2yz.dx),
  #           shape = 18, colour = "red", size = 3,
  #           inherit.aes = FALSE) +
  annotate("point", x = 0, y = 0, shape = 17, size = 3) +
  annotate("text", x = 0.005, y = 0.0001,
           label = paste0("Unadjusted (", unadj_est, ")"),
           size = 4, hjust = 0, vjust = 0) +
  #annotate("text",
  #         x = benchmark_df$r2dz.x[1] + 0.01,
  #         y = benchmark_df$r2yz.dx[1] + 0.0005,
  #         label = "Treatment \n(x-axis at 0.25x)",
  #         size = 4, hjust = 0) +
  coord_cartesian(xlim = c(0, 0.7), ylim = c(0, 0.015)) +
  scale_x_continuous(breaks = seq(0, 0.7, by = 0.1),
                     labels = scales::number_format(accuracy = 0.01)) +
  scale_y_continuous(breaks = seq(0, 0.015, by = 0.005),
                     labels = scales::number_format(accuracy = 0.001)) +
  labs(
    x = "Partial R² of Confounder with Treatment * Russia-Aligned",
    y = "Partial R² of Confounder with Sentiment",
    title = "Sensitivity to Unobserved Confounding, Russia Affiliation",
    subtitle = "Red dashed line indicates where estimate = 0"
  ) +
  theme_bw() +
  theme(
    panel.grid.minor = element_blank(),
    plot.title = element_text(face = "bold"),
    legend.position = "none"
  )

treatment_r2yz <- benchmark_df$r2yz.dx[1]

sensitivity_plot <- sensitivity_plot +
  geom_hline(yintercept = treatment_r2yz,
             linetype = "dotted",
             colour = "blue",
             linewidth = 1) +
  annotate("text", x = 0.2, y = treatment_r2yz + 0.0007,
           label = paste0("Treatment partial R² with sentiment (",
                          round(treatment_r2yz, 4), ")"),
           size = 3.5, hjust = 0, colour = "blue")

sensitivity_plot

ggsave(plot = sensitivity_plot,
       file.path(FIGURES_HETEROGENEITY_PROB, "sensitivity_ovb_csto.png"),
       width = 10, height = 7)
```

```{r}
# At treatment's actual partial R² with CSTO, what partial R² with sentiment
# would a confounder need to nullify the estimate?
est <- sensitivity$sensitivity_stats$estimate
se <- boot_se
dof <- sensitivity$sensitivity_stats$dof
bm_r2dz <- benchmark_df$r2dz.x[1]

f <- function(r2yz) {
  sensemakr::adjusted_estimate(
    estimate = est, se = se, dof = dof,
    r2dz.x = bm_r2dz,
    r2yz.dx = r2yz
  )
}

r2yz_needed <- uniroot(f, interval = c(0, 0.9999))$root
bm_r2yz <- benchmark_df$r2yz.dx[1]  # 0.001

cat("Treatment's actual R²yz:", round(bm_r2yz, 5), "\n")
cat("R²yz needed to nullify at treatment's R²dz:", round(r2yz_needed, 5), "\n")
cat("Multiplier:", round(r2yz_needed / bm_r2yz, 1), "x treatment's R²yz\n")
```

The robustness value of 4.38% indicates that an unobserved confounder would need to simultaneously explain 4.38% of residual variance in both CSTO membership and sentiment to explain away our result. To contextualize this threshold, our observed covariates — including treatment assignment (partial R² = 0.0002%) and CSTO membership itself (partial R² = 0.0001%) — explain a fraction of this amount. We additionally benchmark against temporal proximity to the date of the invasion (partial R² = 4.6% for CSTO membership, 0.00001% for sentiment), which represents the strongest observed predictor of group assignment in our model. Despite exceeding the robustness value threshold on the treatment dimension, this benchmark explains essentially no variance in sentiment outcomes — as visible in Figure X, where the benchmark point sits far to the right of the zero contour but hugging the x-axis. An unobserved confounder would therefore need to be approximately 21,900 times more influential than treatment assignment itself, and simultaneously predict sentiment far more strongly than the timing of the invasion, to overturn our finding. This suggests the result is highly robust to potential confounding.

We caution that robustness values should never be interpreted in isolation. The partial R² scale is model and data specific, and a robustness value that appears small in absolute terms may represent an implausibly large confounding requirement relative to the explanatory power of observed covariates. We recommend always reporting benchmark partial R² values alongside the robustness value to allow readers to calibrate the practical significance of the sensitivity result.


## Leave One Out Matching

```{r}
countries <- unique(data_align_state_non_mil$country)
matched_loo_results <- list()

for (cntry in countries) {
  data_loo <- data_align_state_non_mil %>%
    filter(country != cntry)

  # Re-calculate optimal bandwidth for LOO data
  resid_y <- feols(sentiment_z ~ 1 | topic_clean + csto, 
                 data = data_loo)$residuals
  
  bw_loo <- rdbwselect(y = data_loo$sentiment_z,
                       x = data_loo$running_probabilistic,
                       kernel = "triangular",
                       cluster = data_loo$source_domain,
                       p = 1,
                       bwselect = "mserd")

  optimal_bw_loo <- bw_loo$bws[1, 1]

  data_loo_bw <- data_loo %>%
    filter(running_probabilistic < optimal_bw_loo, running_probabilistic > -optimal_bw_loo)
  
  ps_model <- matchit(
    csto ~ running + topic_clean,
    data = data_loo_bw,
    method = "exact",
    ratio = 1,
  )

  matched_data_loo <-match.data(ps_model)

  matched_model_loo <- feols(sentiment_z ~ running_probabilistic
                                     * treatment * csto |
                                       topic_clean,
                                     cluster = ~source_domain,
                                     data = matched_data_loo
                                     )

  matched_boot_loo <- tryCatch(
    run_wild_bootstrap(matched_model_loo, "treatment:csto", B = 99999),
    error = function(e) list(se = NA, p_val = NA, ci_lower = NA, ci_upper = NA, t_stat = NA)
  )
  matched_loo_results[[cntry]] <- list(
    model = matched_model_loo,
    bandwidth = optimal_bw_loo,
    n = nrow(matched_data_loo),
    country_dropped = cntry,
    boot_p_val = matched_boot_loo$p_val,
    boot_se = matched_boot_loo$se
  )
}

# Extract key coefficient (treatment:csto interaction)
matched_loo_summary <- map_df(names(matched_loo_results), function(cntry) {
  mod <- matched_loo_results[[cntry]]$model
  tibble(
    country_dropped = cntry,
    estimate = coef(mod)["treatment:csto"],
    std_error = se(mod)["treatment:csto"],
    p_value = pvalue(mod)["treatment:csto"],
    n_obs = matched_loo_results[[cntry]]$n,
    bandwidth = matched_loo_results[[cntry]]$bandwidth
  )
})

print(matched_loo_summary)
```

## Pooled Fully Saturated Regression

```{r}
library(data.table)

# ---- 0. DATA PREP -----------------------------------------------------------
 
dt <- as.data.table(optimal_bandwidth_data_state_non_mil)
 
# Ensure key variables are the right type
invisible(dt[, treatment_num  := as.numeric(treatment)])
invisible(dt[, running_num    := as.numeric(running_probabilistic)])
invisible(dt[, treat_x_run    := treatment_num * running_num])
 
# Create a clean source×topic cell identifier
invisible(dt[, cell := paste(source_domain, topic_clean, sep = " :: ")])
invisible(dt[, cell := factor(cell)])
 
# Cell-level metadata: N, source, csto flag
cell_info <- dt[, .(
  N             = .N,
  source_domain = source_domain[1],
  csto          = csto[1],
  n_treated     = sum(treatment_num),
  n_control     = sum(1 - treatment_num)
), by = cell]
 
cat("=== Cell structure ===\n")
print(cell_info[order(-N)])
cat("\nTotal cells:", nrow(cell_info), "\n")
cat("CSTO cells:", sum(cell_info$csto == 1),
    "  |  Non-CSTO cells:", sum(cell_info$csto == 0), "\n\n")
 
# Flag cells that can't identify a treatment effect (need obs on both sides)
cell_info[, estimable := (n_treated >= 2 & n_control >= 2)]
cat("Estimable cells:", sum(cell_info$estimable), "/", nrow(cell_info), "\n")
cat("Dropped cells (insufficient variation):\n")
if (any(!cell_info$estimable)) {
  print(cell_info[estimable == FALSE])
} else {
  cat("  (none)\n")
}
 
# Restrict data to estimable cells
estimable_cells <- cell_info[estimable == TRUE, cell]
dt_est <- dt[cell %in% estimable_cells]
invisible(dt_est[, cell := droplevels(cell)])
 
# Update cell_info to estimable only
cell_info_est <- cell_info[estimable == TRUE]
```


```{r}
# ---- 1. FULLY SATURATED MODEL -----------------------------------------------
# Formula: each cell gets its own intercept, running slope, treatment effect,
#          and treatment×running interaction.
#
# sentiment = Σ_c [ α_c + β_c·running + τ_c·treatment + γ_c·treatment·running ]
#
# The τ_c coefficients are the cell-specific RDD treatment effects at the cutoff.
 
model_saturated <- feols(
  sentiment_z ~ cell + cell:running_num + cell:treatment_num + cell:treat_x_run - 1,
  vcov = "hetero",
  data   = dt_est
)
 
cat("\n=== Model summary (first 20 coefficients) ===\n")
print(summary(model_saturated), n = 20)
```


```{r}
# ---- 2. EXTRACT CELL-SPECIFIC TREATMENT EFFECTS (τ_c) -----------------------
 
all_coefs <- coef(model_saturated)
V_full    <- vcov(model_saturated)
 
# Identify the treatment coefficients: named "cell<level>:treatment_num"
treat_names <- grep(":treatment_num$", names(all_coefs), value = TRUE)
 
theta   <- all_coefs[treat_names]
V_theta <- V_full[treat_names, treat_names]
 
# Map coefficient names back to cell labels
coef_cells <- sub(":treatment_num$", "", treat_names)
coef_cells <- sub("^cell", "", coef_cells)
 
# Match to metadata
match_idx      <- match(coef_cells, as.character(cell_info_est$cell))
matched_info   <- cell_info_est[match_idx]
 
# Sanity check: did all coefficients match?
stopifnot(!any(is.na(match_idx)))
 
cat("\n=== Cell-specific treatment effects (τ_c) ===\n")
cell_results <- data.table(
  cell   = coef_cells,
  source = matched_info$source_domain,
  csto   = matched_info$csto,
  N      = matched_info$N,
  theta  = as.numeric(theta),
  se     = sqrt(diag(V_theta))
)
cell_results[, `:=`(t_stat = theta / se, p_val = 2 * pnorm(-abs(theta / se)))]
print(cell_results[order(csto, source, cell)])
```


```{r}
# ---- 3. BUILD WEIGHT VECTORS (R MATRIX) & WALD TESTS ------------------------
# Weight = N_c / Σ N_c within the CSTO group
# The weighted average τ_group = w' θ  is a linear combination of coefficients.
# Var(τ_group) = w' V_θ w   (using clustered VCV)
# Wald stat = τ_group² / Var(τ_group) ~ χ²(1)
 
N_vec <- matched_info$N
csto_flag <- matched_info$csto
 
# --- 3a. CSTO group ---
csto_mask <- (csto_flag == 1)
w_csto    <- ifelse(csto_mask, N_vec / sum(N_vec[csto_mask]), 0)
 
theta_csto <- as.numeric(crossprod(w_csto, theta))
var_csto   <- as.numeric(t(w_csto) %*% V_theta %*% w_csto)
se_csto    <- sqrt(var_csto)
 
# --- 3b. Non-CSTO group ---
non_mask    <- (csto_flag == 0)
w_non       <- ifelse(non_mask, N_vec / sum(N_vec[non_mask]), 0)
 
theta_non <- as.numeric(crossprod(w_non, theta))
var_non   <- as.numeric(t(w_non) %*% V_theta %*% w_non)
se_non    <- sqrt(var_non)
 
# --- 3c. Difference (CSTO minus Non-CSTO) ---
w_diff     <- w_csto - w_non
theta_diff <- as.numeric(crossprod(w_diff, theta))
var_diff   <- as.numeric(t(w_diff) %*% V_theta %*% w_diff)
se_diff    <- sqrt(var_diff)
 
# --- Wald statistics and p-values ---
wald_results <- data.table(
  group     = c("CSTO", "Non-CSTO", "Difference (CSTO - Non)"),
  estimate  = c(theta_csto, theta_non, theta_diff),
  se        = c(se_csto, se_non, se_diff),
  z_stat    = c(theta_csto / se_csto, theta_non / se_non, theta_diff / se_diff),
  p_value   = c(
    2 * pnorm(-abs(theta_csto / se_csto)),
    2 * pnorm(-abs(theta_non / se_non)),
    2 * pnorm(-abs(theta_diff / se_diff))
  ),
  N_total   = c(sum(N_vec[csto_mask]), sum(N_vec[non_mask]),
                sum(N_vec[csto_mask]) + sum(N_vec[non_mask])),
  n_cells   = c(sum(csto_mask), sum(non_mask), sum(csto_mask) + sum(non_mask))
)
 
cat("\n")
cat("=====================================================================\n")
cat("  WALD TEST RESULTS: N-Weighted Treatment Effects by CSTO Group\n")
cat("=====================================================================\n")
print(wald_results, digits = 4)
cat("=====================================================================\n")
cat("Notes:\n")
cat("  - HC-robust SEs (cells nest within clusters, so cell estimates\n")
cat("    are independent and cluster-robust SEs are unnecessary)\n")
cat("  - Weights proportional to N within each CSTO group\n")
cat("  - Treatment effect = RDD estimate at the cutoff (running = 0)\n")
cat("=====================================================================\n\n")
```


```{r}
# ---- 4. DIAGNOSTICS ---------------------------------------------------------
 
# Show the weight each cell contributes
cat("=== Cell weights within CSTO groups ===\n")
weight_table <- data.table(
  cell   = coef_cells,
  source = matched_info$source_domain,
  csto   = matched_info$csto,
  N      = N_vec,
  weight = ifelse(csto_flag == 1, w_csto, w_non)
)
print(weight_table[order(csto, -weight)])
 
# Check: weights sum to 1 within each group
cat("\nWeight sums (should be 1.0 each):\n")
cat("  CSTO:    ", sum(w_csto), "\n")
cat("  Non-CSTO:", sum(w_non), "\n")
```


## Mini-Regressions Approach

```{r}
# ---- 2A. MINI-REGRESSIONS WITHIN EACH SOURCE × TOPIC CELL -------------------
# Estimate: sentiment ~ running + treatment + treatment×running
# within each source_domain × topic_clean cell.
# τ_c = coefficient on `treatment` = RDD effect at cutoff.
 
cat("=== APPROACH 2: Mini-Regressions ===\n\n")
 
cells_to_estimate <- cell_info_est[estimable == TRUE]
 
mini_results <- rbindlist(lapply(seq_len(nrow(cells_to_estimate)), function(i) {
  cc <- cells_to_estimate$cell[i]
  d  <- dt_est[cell == cc]
 
  m <- tryCatch(
    lm(sentiment_z ~ running_num + treatment_num + treat_x_run, data = d),
    error = function(e) NULL
  )
 
  if (is.null(m)) {
    return(data.table(
      cell = as.character(cc), source = cells_to_estimate$source_domain[i],
      topic = NA_character_, csto = cells_to_estimate$csto[i],
      N = nrow(d), theta = NA_real_, se = NA_real_,
      converged = FALSE
    ))
  }
 
  # Extract treatment coefficient
  cf <- summary(m)$coefficients
  if (!"treatment_num" %in% rownames(cf)) {
    return(data.table(
      cell = as.character(cc), source = cells_to_estimate$source_domain[i],
      topic = NA_character_, csto = cells_to_estimate$csto[i],
      N = nrow(d), theta = NA_real_, se = NA_real_,
      converged = FALSE
    ))
  }
 
  data.table(
    cell   = as.character(cc),
    source = cells_to_estimate$source_domain[i],
    topic  = sub("^.* :: ", "", as.character(cc)),
    csto   = cells_to_estimate$csto[i],
    N      = nrow(d),
    theta  = cf["treatment_num", "Estimate"],
    se     = cf["treatment_num", "Std. Error"],
    converged = TRUE
  )
}))
 
mini_results <- mini_results[converged == TRUE & !is.na(theta)]
 
cat("Mini-regression results (cell-level):\n")
print(mini_results[order(csto, source, topic)], digits = 4)
```


```{r}
# ---- 2B. VERIFY: POINT ESTIMATES MATCH APPROACH 1 ---------------------------
 
cat("\n=== VERIFICATION: Approach 1 vs Approach 2 point estimates ===\n")
 
# N-weighted average within CSTO groups
verify <- mini_results[, .(
  theta_mini = weighted.mean(theta, N),
  N_total    = sum(N),
  n_cells    = .N
), by = csto]
 
cat("\nApproach 2 (mini-regressions):\n")
print(verify, digits = 6)
 
cat("\nApproach 1 (pooled saturated):\n")
cat("  CSTO:     ", round(theta_csto, 6), "\n")
cat("  Non-CSTO: ", round(theta_non, 6), "\n")
 
cat("\nDifference (should be ~0 or very small):\n")
cat("  CSTO:     ", round(verify[csto == 1, theta_mini] - theta_csto, 8), "\n")
cat("  Non-CSTO: ", round(verify[csto == 0, theta_mini] - theta_non, 8), "\n\n")
```


```{r}
# ---- 2C. SOURCE-LEVEL PAIRS BOOTSTRAP ---------------------------------------
# For each bootstrap iteration:
#   1. Resample 13 sources with replacement from the full set of 13
#   2. Carry along ALL their topic-level estimates and Ns
#   3. Classify drawn sources by their csto flag
#   4. Compute N-weighted average within CSTO / Non-CSTO groups
#   5. Store CSTO effect, Non-CSTO effect, and difference
 
run_source_pairs_bootstrap <- function(mini_results, B = 9999) {
 
  sources <- unique(mini_results$source)
  n_sources <- length(sources)
 
  source_data <- lapply(sources, function(s) {
    mini_results[source == s, .(topic, csto, N, theta)]
  })
  names(source_data) <- sources
 
  theta_boot_csto <- numeric(B)
  theta_boot_non  <- numeric(B)
  theta_boot_diff <- numeric(B)
  n_valid <- 0
 
  for (b in seq_len(B)) {
    drawn_idx <- sample(n_sources, n_sources, replace = TRUE)
    drawn_sources <- sources[drawn_idx]
    boot_data <- rbindlist(source_data[drawn_sources])
 
    csto_rows <- boot_data[csto == 1]
    non_rows  <- boot_data[csto == 0]
 
    if (nrow(csto_rows) == 0 || nrow(non_rows) == 0) next
 
    n_valid <- n_valid + 1
    theta_boot_csto[n_valid] <- weighted.mean(csto_rows$theta, csto_rows$N)
    theta_boot_non[n_valid]  <- weighted.mean(non_rows$theta, non_rows$N)
    theta_boot_diff[n_valid] <- theta_boot_csto[n_valid] - theta_boot_non[n_valid]
  }
 
  theta_boot_csto <- theta_boot_csto[seq_len(n_valid)]
  theta_boot_non  <- theta_boot_non[seq_len(n_valid)]
  theta_boot_diff <- theta_boot_diff[seq_len(n_valid)]
 
  cat("  Valid bootstrap samples:", n_valid, "/", B, "\n")
 
  orig_csto <- weighted.mean(mini_results[csto == 1, theta], mini_results[csto == 1, N])
  orig_non  <- weighted.mean(mini_results[csto == 0, theta], mini_results[csto == 0, N])
  orig_diff <- orig_csto - orig_non
 
  list(
    results = data.table(
      group     = c("CSTO", "Non-CSTO", "Difference"),
      estimate  = c(orig_csto, orig_non, orig_diff),
      se_boot   = c(sd(theta_boot_csto), sd(theta_boot_non), sd(theta_boot_diff)),
      p_boot    = c(
        2 * min(mean(theta_boot_csto >= 0), mean(theta_boot_csto <= 0)),
        2 * min(mean(theta_boot_non  >= 0), mean(theta_boot_non  <= 0)),
        2 * min(mean(theta_boot_diff >= 0), mean(theta_boot_diff <= 0))
      ),
      ci_lower  = c(quantile(theta_boot_csto, 0.025), quantile(theta_boot_non, 0.025), quantile(theta_boot_diff, 0.025)),
      ci_upper  = c(quantile(theta_boot_csto, 0.975), quantile(theta_boot_non, 0.975), quantile(theta_boot_diff, 0.975))
    ),
    boot_dist = list(csto = theta_boot_csto, non = theta_boot_non, diff = theta_boot_diff)
  )
}
 
 
# ---- 2D. BAYESIAN BOOTSTRAP (Rubin 1981) ------------------------------------
# For each bootstrap iteration:
#   1. Draw Dirichlet(1,1,...,1) weights for all 13 sources
#   2. Every source always contributes — no source is ever dropped
#   3. Effective weight for each topic = dirichlet_weight_source × N_topic
#   4. Compute weighted average within CSTO / Non-CSTO groups
#   5. Store CSTO effect, Non-CSTO effect, and difference
 
run_bayesian_bootstrap <- function(mini_results, B = 9999) {
 
  # Source-level structure
  sources   <- unique(mini_results$source)
  n_sources <- length(sources)
 
  # Map each source to an index, and store its csto flag
  source_idx  <- setNames(seq_along(sources), sources)
  source_csto <- mini_results[, .(csto = csto[1]), by = source]
  csto_flag   <- source_csto$csto  # length n_sources, aligned with sources
 
  # Pre-compute cell-level vectors aligned with mini_results rows
  cell_source_idx <- source_idx[mini_results$source]
  cell_csto       <- mini_results$csto
  cell_N          <- mini_results$N
  cell_theta      <- mini_results$theta
  n_cells         <- nrow(mini_results)
 
  # Masks for CSTO / Non-CSTO cells
  csto_mask <- (cell_csto == 1)
  non_mask  <- (cell_csto == 0)
 
  # Storage
  theta_boot_csto <- numeric(B)
  theta_boot_non  <- numeric(B)
  theta_boot_diff <- numeric(B)
 
  for (b in seq_len(B)) {
 
    # 1. Draw Dirichlet(1,1,...,1) weights for all sources
    #    Dirichlet draw = normalize independent Gamma(1,1) draws
    gam_draws <- rgamma(n_sources, shape = 1, rate = 1)
    dir_weights <- gam_draws / sum(gam_draws)
 
    # 2. Effective weight for each cell = source's Dirichlet weight × cell N
    cell_weights <- dir_weights[cell_source_idx] * cell_N
 
    # 3. Weighted averages within each CSTO group
    w_csto <- cell_weights[csto_mask]
    w_non  <- cell_weights[non_mask]
 
    theta_boot_csto[b] <- sum(w_csto * cell_theta[csto_mask]) / sum(w_csto)
    theta_boot_non[b]  <- sum(w_non  * cell_theta[non_mask])  / sum(w_non)
    theta_boot_diff[b] <- theta_boot_csto[b] - theta_boot_non[b]
  }
 
  cat("  Bayesian bootstrap iterations:", B, "\n")
  cat("  (All iterations valid — no sources are ever dropped)\n")
 
  # Point estimates (from original data, standard N-weighting)
  orig_csto <- weighted.mean(
    mini_results[csto == 1, theta], mini_results[csto == 1, N]
  )
  orig_non <- weighted.mean(
    mini_results[csto == 0, theta], mini_results[csto == 0, N]
  )
  orig_diff <- orig_csto - orig_non
 
  # Posterior SEs (SD of bootstrap distribution)
  se_csto <- sd(theta_boot_csto)
  se_non  <- sd(theta_boot_non)
  se_diff <- sd(theta_boot_diff)
 
  # Percentile CIs (95% credible intervals)
  ci_csto <- quantile(theta_boot_csto, c(0.025, 0.975))
  ci_non  <- quantile(theta_boot_non,  c(0.025, 0.975))
  ci_diff <- quantile(theta_boot_diff, c(0.025, 0.975))
 
  # P-values: posterior probability of sign reversal (two-sided)
  p_csto <- 2 * min(mean(theta_boot_csto >= 0), mean(theta_boot_csto <= 0))
  p_non  <- 2 * min(mean(theta_boot_non  >= 0), mean(theta_boot_non  <= 0))
  p_diff <- 2 * min(mean(theta_boot_diff >= 0), mean(theta_boot_diff <= 0))
 
  list(
    results = data.table(
      group     = c("CSTO", "Non-CSTO", "Difference"),
      estimate  = c(orig_csto, orig_non, orig_diff),
      se_boot   = c(se_csto, se_non, se_diff),
      p_boot    = c(p_csto, p_non, p_diff),
      ci_lower  = c(ci_csto[1], ci_non[1], ci_diff[1]),
      ci_upper  = c(ci_csto[2], ci_non[2], ci_diff[2])
    ),
    boot_dist = list(
      csto = theta_boot_csto,
      non  = theta_boot_non,
      diff = theta_boot_diff
    )
  )
}
 
cat("Running source-level pairs bootstrap for Approach 2...\n")
boot2_pairs <- run_source_pairs_bootstrap(mini_results, B = 9999)
 
cat("\n")
cat("=====================================================================\n")
cat("  APPROACH 2a: Source-Level Pairs Bootstrap Results\n")
cat("=====================================================================\n")
print(boot2_pairs$results, digits = 4)
cat("=====================================================================\n\n")
```


```{r}
cat("Running Bayesian bootstrap for Approach 2...\n")
boot2_bayes <- run_bayesian_bootstrap(mini_results, B = 9999)
 
cat("\n")
cat("=====================================================================\n")
cat("  APPROACH 2b: Bayesian Bootstrap Results (Rubin 1981)\n")
cat("=====================================================================\n")
print(boot2_bayes$results, digits = 4)
cat("=====================================================================\n\n")
```

```{r}
# Write out of data
# Source-level treatment effects (N-weighted average across topics within source)
source_level_effects <- mini_results[, .(
  theta  = weighted.mean(theta, N),
  N      = sum(N),
  csto   = csto[1],
  n_topics = .N
), by = source]
setorder(source_level_effects, csto, source)
 
# Group-level summary (CSTO / Non-CSTO / Difference)
decomposition_results <- list(
  # Cell-level estimates (source x topic)
  cell_effects   = mini_results[order(csto, source, topic)],
  # Source-level estimates (averaged across topics)
  source_effects = source_level_effects,
  # Group-level estimates with both bootstrap methods
  group_effects_pairs = boot2_pairs$results,
  group_effects_bayes = boot2_bayes$results,
  # Bootstrap distributions (for plotting if needed)
  boot_distributions_pairs = boot2_pairs$boot_dist,
  boot_distributions_bayes = boot2_bayes$boot_dist,
  # Metadata
  n_sources_csto     = sum(source_level_effects$csto == 1),
  n_sources_non_csto = sum(source_level_effects$csto == 0),
  n_cells            = nrow(mini_results),
  B                  = length(boot2_pairs$boot_dist$csto)
)
```


## Total Effect, Sentiment-Z (No Fes)

Single-group RDDs on each side of the alignment contrast, with no fixed effects.
The total-effect *difference* in discontinuities is not re-estimated here: it is
`model5a_opt_z_total` in "Total Effect (No Topic Adjustment)" above, which uses
the same `csto` residualization, the same mserd / triangular / source-clustered
bandwidth procedure and the same formula. That section keeps its own
`_total`-suffixed bandwidth names, so `optimal_bw_align` and
`optimal_bandwidth_data_state` stay bound to the headline Table 4 specification.

Note that `model5_full_csto_z` below is fitted on `sentiment_z`, matching the
heading, while `model5_total_neutral` is fitted on `sentiment_clean`.

### Russia-Aligned Only

```{r total-russia-aligned}
# RDD On Total Effect for Russia Aligned Only
model5_full_csto_z <- rdrobust(
  y = data_align_state_csto$sentiment_z,
  x = data_align_state_csto$running_probabilistic,
  cluster = data_align_state_csto$source_domain
)

summary(model5_full_csto_z)
```

### Neutral-Aligned Only

```{r total-neutral-aligned}
# RDD On Total Effect for Neutral Aligned Only
model5_total_neutral <- rdrobust(
  y = data_align_state_neutral$sentiment_clean,
  x = data_align_state_neutral$running_probabilistic,
  covs = covs_matrix,
  cluster = data_align_state_neutral$source_domain
)

summary(model5_total_neutral)
```


# Country-Level Analysis

## State Media by Country and Alliance

```{r country-facet-prob, fig.width=12, fig.height=8}
# Create alliance for faceting
data_long <- data %>%
  pivot_longer(cols = c(nato, csto, neutral),
               names_to = "alliance",
               values_to = "membership") %>%
  filter(membership == 1) %>%
  mutate(
    alliance = factor(alliance, levels = c("nato", "csto", "neutral")),
    state_indicator = factor(paste(country, treatment, sep = ", "))
  )

data_long %>%
  filter(state_owned == 1) %>%
  ggplot(aes(x = running_probabilistic, y = sentiment_clean, group = state_indicator, color = country)) +
  geom_smooth(method = "lm", se = FALSE) +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  facet_wrap(~alliance, nrow = 2) +
  labs(
    title = "Effect of Invasion on State Media Sentiment by Country (Probabilistic)",
    subtitle = "Faceted by Alliance",
    x = "Hours Pre/Post Invasion",
    y = "Sentiment"
  )
```

# Summary Tables

## Summary Table (Table 3I)

```{r table3i-prob}
note_text <- "All standard errors are clustered at the source level. Model 1 uses no fixed effects. Model 2 uses full data with topic fixed effects. Model 3 uses the optimal bandwidth with topic fixed effects. Model 4 omits military-related articles and uses a re-optimized bandwidth. Model 5 uses only Russian-related (non-military) articles with a re-optimized bandwidth. Model 6 uses optimal bandwidth with full FEs (topic + source + country dummies). Model 7 uses non-military subset with full FEs. Model 8 uses full saturation (source-topic and topic-treatment FEs)."
note_wrapped <- str_wrap(note_text, width = 80)

table_3i <- modelsummary(
  list("(1)" = model5a, "(2)" = model5a_full, "(3)" = model5a_opt,
       "(4)" = model5a_opt_non_mil, "(5)" = model5a_opt_russian,
       "(6)" = model5a_opt_full_fe, "(7)" = model5a_opt_non_mil_full_fe),
       #"(8)" = model5a_fully_saturated),
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors",
  title = "Russian Alignment: Difference in Discontinuity Analysis (Probabilistic Time Assignment)",
  notes = note_wrapped
)

table_3i
```

## Summary Table: By Topic (Optimal Bandwidth)

```{r table3i-topic-opt-prob}
note_topic_opt <- "All standard errors are clustered at the source level. Each model uses a per-topic re-optimized bandwidth. State media in non-NATO countries only."
note_topic_opt_wrapped <- str_wrap(note_topic_opt, width = 80)

table_3i_topic_opt <- modelsummary(
  list("Political" = model5a_opt_pol, "Military" = model5a_opt_mil,
       "Economic" = model5a_opt_econ, "Cultural" = model5a_opt_cult, "Other" = model5a_opt_oth),
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors",
  title = "Russian Alignment By Topic (Per-Topic Optimal Bandwidth, Probabilistic Time Assignment)",
  notes = note_topic_opt_wrapped
)

table_3i_topic_opt
```

## Summary Table: By Topic (Full Data)

```{r table3i-topic-full-prob}
note_topic_full <- "All standard errors are clustered at the source level. Each model uses the full dataset (no bandwidth restriction). State media in non-NATO countries only."
note_topic_full_wrapped <- str_wrap(note_topic_full, width = 80)

table_3i_topic_full <- modelsummary(
  list("Political" = model5a_full_pol, "Military" = model5a_full_mil,
       "Economic" = model5a_full_econ, "Cultural" = model5a_full_cult, "Other" = model5a_full_oth),
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors",
  title = "Russian Alignment By Topic (Full Data, Probabilistic Time Assignment)",
  notes = note_topic_full_wrapped
)

table_3i_topic_full
```

# Save Results

```{r save-prob}
results_het_prob <- list(
  # Main models
  model5a = model5a,
  model5a_full = model5a_full,
  model5a_opt = model5a_opt,
  model5a_opt_non_mil = model5a_opt_non_mil,
  model5a_opt_russian = model5a_opt_russian,
  model5a_csto = model5a_csto,
  model5a_neutral = model5a_neutral,
  model5a_opt_full_fe = model5a_opt_full_fe,
  model5a_opt_non_mil_full_fe = model5a_opt_non_mil_full_fe,
  #model5a_fully_saturated = model5a_fully_saturated,
  matched_model = matched_model,

  # Z-score models
  model5a_z = model5a_z,
  model5a_csto_z = model5a_csto_z,
  model5a_neutral_z = model5a_neutral_z,
  model5a_opt_z = model5a_opt_z,
  model5a_opt_non_mil_z = model5a_opt_non_mil_z,
  model5a_opt_russian_z = model5a_opt_russian_z,

  # Russian Full FE
  model5a_opt_rus_full_fe = model5a_opt_rus_full_fe,

  # Topic-specific models
  model5a_opt_pol = model5a_opt_pol,
  model5a_opt_mil = model5a_opt_mil,
  model5a_opt_econ = model5a_opt_econ,
  model5a_opt_cult = model5a_opt_cult,
  model5a_opt_oth = model5a_opt_oth,
  model5a_full_pol = model5a_full_pol,
  model5a_full_mil = model5a_full_mil,
  model5a_full_econ = model5a_full_econ,
  model5a_full_cult = model5a_full_cult,
  model5a_full_oth = model5a_full_oth,

  # Bootstrap standard errors
  bootstrap_se = list(
    # Main model5a variants
    model5a = boot_model5a,
    model5a_full = boot_model5a_full,
    model5a_opt = boot_model5a_opt,
    model5a_opt_non_mil = boot_model5a_opt_non_mil,
    model5a_opt_russian = boot_model5a_opt_russian,
    model5a_opt_full_fe = boot_model5a_opt_full_fe,
    model5a_opt_non_mil_full_fe = boot_model5a_opt_non_mil_full_fe,
    #model5a_fully_saturated = boot_model5a_fully_saturated,
    matched_model = boot_matched_model,

    # Z-score bootstrap SEs
    model5a_z = boot_model5a_z,
    model5a_opt_z = boot_model5a_opt_z,
    model5a_opt_non_mil_z = boot_model5a_opt_non_mil_z,
    model5a_opt_russian_z = boot_model5a_opt_russian_z,

    # Russian Full FE bootstrap
    model5a_opt_rus_full_fe = boot_model5a_opt_rus_full_fe,

    # Topic-specific model5a (optimal BW)
    model5a_opt_pol = boot_model5a_opt_pol,
    model5a_opt_mil = boot_model5a_opt_mil,
    model5a_opt_econ = boot_model5a_opt_econ,
    model5a_opt_cult = boot_model5a_opt_cult,
    model5a_opt_oth = boot_model5a_opt_oth,

    # Topic-specific model5a (full data)
    model5a_full_pol = boot_model5a_full_pol,
    model5a_full_mil = boot_model5a_full_mil,
    model5a_full_econ = boot_model5a_full_econ,
    model5a_full_cult = boot_model5a_full_cult,
    model5a_full_oth = boot_model5a_full_oth,

    # Placebo test
    model_placebo_nonmil = boot_model_placebo_nonmil,
    model5a_opt_z_total = boot_model5a_opt_z_total,
    model5a_opt_non_mil_z_total = boot_model5a_opt_non_mil_z_total
  ),

  optimal_bandwidth_align = optimal_bw_align,
  optimal_bw_align_pol = optimal_bw_align_pol,
  optimal_bw_align_mil = optimal_bw_align_mil,
  optimal_bw_align_econ = optimal_bw_align_econ,
  optimal_bw_align_cult = optimal_bw_align_cult,
  optimal_bw_align_oth = optimal_bw_align_oth,
  loo_results = loo_results,
  loo_summary = loo_summary,
  matched_loo_results = matched_loo_results,
  matched_loo_summary = matched_loo_summary,
  model_placebo_nonmil = model_placebo_nonmil,
  optimal_bw_placebo_nonmil = optimal_bw_placebo_nonmil,

  # Dec-7 placebo restricted to aligned (CSTO) state media, one rdrobust per country
  placebo_aligned_models = placebo_aligned_models,

  # Same placebo pooled across the four aligned countries (HC and source-clustered),
  # plus the tidy per-country + pooled estimate table
  placebo_aligned_pooled = placebo_aligned_pooled,
  placebo_aligned_pooled_cl = placebo_aligned_pooled_cl,
  placebo_aligned_estimates = placebo_aligned_estimates,

  # Source- vs country-level WCR inference for the reported H3a RDIDs
  country_cluster_check = country_cluster_check,

  # Total effect: Table 4 Model 3 without topic adjustment (appendix S14)
  model5a_opt_z_total = model5a_opt_z_total,
  model5a_opt_non_mil_z_total = model5a_opt_non_mil_z_total,
  optimal_bw_align_total = optimal_bw_align_total,
  optimal_bw_align_nonmil_total = optimal_bw_align_nonmil_total,

  # Mini-Regressions: Heterogeneous treatment effect decomposition
  decomposition = decomposition_results
)

saveRDS(results_het_prob, file.path(DATA_INTERMEDIATE, "06_alignment_results_prob.rds"))
cat("Results saved to:", file.path(DATA_INTERMEDIATE, "06_alignment_results_prob.rds"), "\n")
```

# Session Info

```{r session-info-prob}
print_session_info()
```
