---
title: "06b - Russian Alignment Analysis (Day Running Variable) (CSTO vs Neutral)"
author: "Donald Moratz"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

# Overview

This script examines heterogeneous treatment effects by Russian alignment (CSTO vs Neutral) only, using days-based time assignment.

**Inputs:**
- `data/intermediate/02_cleaned_data.rds`
- `data/intermediate/02_data_non_ukraine.rds`

**Outputs:**
- Table 3 (Russian Alignment)

```{r setup, include=FALSE}
source("00_setup.R")
knitr::opts_chunk$set(fig.path = paste0(FIGURES_HETEROGENEITY_DAYS, "/"))
options(digits = 10)

set.seed(3184)
```

# Load Data

```{r load}
data <- readRDS(file.path(DATA_INTERMEDIATE, "02_cleaned_data.rds"))
data_non_ukraine <- readRDS(file.path(DATA_INTERMEDIATE, "02_data_non_ukraine.rds"))

cat("Full data:", nrow(data), "articles\n")
cat("Non-Ukraine data:", nrow(data_non_ukraine), "articles\n")

data <- data %>% mutate(across(c(topic_clean, country, source_domain), as.factor))
data_non_ukraine <- data_non_ukraine %>% mutate(across(c(topic_clean, country, source_domain), as.factor))
```

# Russian Alignment Analysis (CSTO vs Neutral)

## Create Alignment Subsets

```{r alignment-data}
# Filter to non-NATO countries for alignment analysis
data_align <- data %>%
  filter(nato == 0)%>%
  drop_na()

# Create alignment indicator
data_align <- data_align %>%
  mutate(align_indicator = factor(case_when(
    indicator == 1 & csto == 1 ~ "Pre. Ind. CSTO",
    indicator == 1 & csto == 0 ~ "Pre. Ind. Neut",
    indicator == 2 & csto == 1 ~ "Pre. State CSTO",
    indicator == 2 & csto == 0 ~ "Pre. State Neut",
    indicator == 3 & csto == 1 ~ "Post Ind. CSTO",
    indicator == 3 & csto == 0 ~ "Post Ind. Neut",
    indicator == 4 & csto == 1 ~ "Post State CSTO",
    indicator == 4 & csto == 0 ~ "Post State Neut"
  ),
  levels = c("Pre. Ind. CSTO", "Pre. Ind. Neut", "Pre. State CSTO",
             "Pre. State Neut", "Post Ind. CSTO", "Post Ind. Neut",
             "Post State CSTO", "Post State Neut")))

cat("Non-NATO countries sample:", nrow(data_align), "articles\n")
cat("CSTO:", sum(data_align$csto), "\n")
cat("Neutral:", sum(data_align$csto == 0), "\n")
```

## Visualizations

### Independent Media by Alignment

```{r align-ind-plot, fig.width=10, fig.height=7}
agg_data_align_ind <- data_align %>%
  filter(state_owned == 0) %>%
  group_by(running, csto) %>%
  summarize(sentiment_clean = mean(sentiment_clean), num_obs = n(), .groups = "drop")

data_align %>%
  filter(state_owned == 0) %>%
  ggplot(aes(x = running, y = sentiment_clean, group = align_indicator, color = align_indicator)) +
  geom_point(data = agg_data_align_ind,
             aes(x = running, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = COLORS_DISCS, name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on Independent Media Sentiment (Days)",
    subtitle = "Neutral vs Russia Aligned, Difference in Discontinuities",
    x = "Days Pre/Post Invasion",
    y = "Sentiment"
  )
```

### State Media by Alignment

```{r align-state-plot, fig.width=10, fig.height=7}
agg_data_align_state <- data_align %>%
  filter(state_owned == 1) %>%
  group_by(running, csto) %>%
  summarize(sentiment_clean = mean(sentiment_clean), num_obs = n(), .groups = "drop")

state_align_discs_graph <- data_align %>%
  filter(state_owned == 1) %>%
  mutate(align_indicator = as.factor(align_indicator)) %>%
  mutate(align_indicator = fct_recode(align_indicator,
    "Russia-Aligned Pre" = "Pre. State CSTO",
    "Neutral Pre" = "Pre. State Neut",
    "Russia-Aligned Post" = "Post State CSTO",
    "Neutral Post" = "Post State Neut"
  )) %>%
  ggplot(aes(x = running, y = sentiment_clean, group = align_indicator, color = align_indicator)) +
  geom_point(data = agg_data_align_state,
             aes(x = running, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = COLORS_DISCS, name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on State Media Sentiment (Days)",
    subtitle = "Neutral vs Russia Aligned, Difference in Discontinuities",
    x = "Days Pre/Post Invasion",
    y = "Sentiment"
  )

state_align_discs_graph

ggsave(plot = state_align_discs_graph,
       file.path(FIGURES_HETEROGENEITY_DAYS, "state_align_discs.png"),
       width = 10, height = 7)
```

### Direct-Labelled Variant

The same plot with the series named directly on their own fitted lines instead of
in a colour legend, which keeps the reader's eye on the discontinuity rather than
moving between panel and key. Written to a separate `_labeled` file; the canonical
figure above is left untouched.

```{r align-state-plot-labeled, fig.width=10, fig.height=7}
plot_data_labeled <- data_align %>%
  filter(state_owned == 1) %>%
  mutate(align_indicator = as.factor(align_indicator)) %>%
  mutate(align_indicator = fct_recode(align_indicator,
    "Russia-Aligned Pre" = "Pre. State CSTO",
    "Neutral Pre" = "Pre. State Neut",
    "Russia-Aligned Post" = "Post State CSTO",
    "Neutral Post" = "Post State Neut"
  )) %>%
  droplevels()

labels_align_state <- series_label_positions(plot_data_labeled, "align_indicator")

state_align_discs_labeled <- plot_data_labeled %>%
  ggplot(aes(x = running, y = sentiment_clean,
             group = align_indicator, color = align_indicator)) +
  geom_point(data = agg_data_align_state,
             aes(x = running, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  geom_text(data = labels_align_state,
            aes(x = .x, y = .y, label = .series, color = .series, hjust = .hjust),
            vjust = -0.9, inherit.aes = FALSE, fontface = "bold", size = 3.6,
            show.legend = FALSE) +
  scale_color_manual(values = COLORS_DISCS, guide = "none") +
  scale_size(name = "Observations") +
  scale_x_continuous(expand = expansion(mult = 0.04)) +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on State Media Sentiment (Days)",
    subtitle = "Neutral vs Russia Aligned, Difference in Discontinuities",
    x = "Days Pre/Post Invasion",
    y = "Sentiment"
  )

state_align_discs_labeled

ggsave(plot = state_align_discs_labeled,
       file.path(FIGURES_HETEROGENEITY_DAYS, "state_align_discs_labeled.png"),
       width = 10, height = 7)
```


### State Media by Alignment, Presentation

```{r align-state-plot-present, fig.width=10, fig.height=7}
agg_data_align_state <- data_align %>%
  filter(state_owned == 1) %>%
  group_by(running, csto) %>%
  summarize(sentiment_clean = mean(sentiment_clean), num_obs = n(), .groups = "drop")

state_align_discs_graph_present <- data_align %>%
  filter(state_owned == 1) %>%
  mutate(align_indicator = as.factor(align_indicator)) %>%
  mutate(align_indicator = fct_recode(align_indicator,
    "Russia-Aligned Pre" = "Pre. State CSTO",
    "Neutral Pre" = "Pre. State Neut",
    "Russia-Aligned Post" = "Post State CSTO",
    "Neutral Post" = "Post State Neut"
  )) %>%
  ggplot(aes(x = running, y = sentiment_clean, group = align_indicator, color = align_indicator)) +
  geom_point(data = agg_data_align_state,
             aes(x = running, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm", linewidth = 1.2) +
  scale_color_manual(values = COLORS_DISCS, name = NULL) +
  scale_size(guide = "none") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic(base_size = 18) +
  theme(
    legend.position = c(0.85, 0.85),
    legend.text = element_text(size = 16),
    plot.title = element_blank(),
    plot.subtitle = element_blank()
  ) +
  labs(
    x = "Days Pre/Post Invasion",
    y = "Sentiment"
  )

state_align_discs_graph_present

ggsave(plot = state_align_discs_graph_present,
       file.path(FIGURES_HETEROGENEITY_DAYS, "state_align_discs_present.png"),
       width = 10, height = 7)
```


## Pre-Trend Diagnostic: State Media in Russia-Aligned Countries

Addresses the concern that sentiment toward Russia may have turned negative *before* the
Feb 24, 2022 invasion (during the troop buildup) in state-owned media of Russia-aligned
countries. We plot the daily mean sentiment for state-owned sources in each aligned country
(Armenia, Azerbaijan, Belarus, Kazakhstan), mark both the Dec 7, 2021 US public-warning
date and the Feb 24, 2022 invasion cutoff, and overlay a linear fit on the pre-invasion
window only so any pre-existing slide is visible.

```{r pretrend-by-country-aligned-days, fig.width=10, fig.height=7}
# Buildup display window (trim to keep the pre-invasion period readable)
PRETREND_START <- as.Date("2021-06-01")
PRETREND_END   <- as.Date("2022-06-01")
INVASION_DATE  <- as.Date("2022-02-24")
WARNING_DATE   <- as.Date("2021-12-07")

# State-owned media in the Russia-aligned (CSTO) group; Ukraine already excluded (NATO)
data_pretrend <- data %>%
  filter(country %in% CSTO_COUNTRIES, state_owned == 1,
         date_publish >= PRETREND_START, date_publish <= PRETREND_END) %>%
  mutate(country = droplevels(country))

# Daily mean sentiment per country (same outcome + daily aggregation as other figures)
agg_pretrend <- data_pretrend %>%
  group_by(country, date_publish) %>%
  summarize(sentiment_clean = mean(sentiment_clean, na.rm = TRUE),
            num_obs = n(), .groups = "drop")

# Pre-invasion daily means only (the linear fit is restricted to this window)
agg_pretrend_pre <- agg_pretrend %>%
  filter(date_publish < INVASION_DATE)

pretrend_by_country_aligned_graph <- ggplot(agg_pretrend,
                                             aes(x = date_publish, y = sentiment_clean)) +
  geom_point(aes(size = num_obs), alpha = 0.2, inherit.aes = TRUE) +
  geom_smooth(data = agg_pretrend_pre, method = "lm", se = TRUE, color = "red4") +
  geom_vline(xintercept = INVASION_DATE, linetype = "dashed", alpha = 0.7) +
  geom_vline(xintercept = WARNING_DATE, linetype = "dotted", color = "grey30") +
  scale_size(name = "Observations") +
  facet_wrap(~ country, scales = "free_y") +
  theme_classic() +
  labs(
    title = "Pre-Invasion Sentiment Trend in State Media (Day)",
    subtitle = "Russia-aligned countries; dotted = Dec 7 warning, dashed = Feb 24 invasion",
    x = "Publication date",
    y = "Mean sentiment toward Russia"
  )

pretrend_by_country_aligned_graph

ggsave(plot = pretrend_by_country_aligned_graph,
       file.path(FIGURES_HETEROGENEITY_DAYS, "pretrend_by_country_aligned.png"),
       width = 10, height = 7)
```

```{r pretrend-slopes-aligned-days}
# Per-country pre-invasion linear slope (fit on the plotted daily means).
# Slope is in sentiment units per day; also reported per 30 days for readability.
pretrend_slopes <- agg_pretrend_pre %>%
  group_by(country) %>%
  group_modify(~ {
    fit <- lm(sentiment_clean ~ as.numeric(date_publish), data = .x)
    ct <- summary(fit)$coefficients["as.numeric(date_publish)", ]
    tibble(
      n_days       = nrow(.x),
      slope_day    = ct["Estimate"],
      slope_30day  = ct["Estimate"] * 30,
      std_error    = ct["Std. Error"],
      p_value      = ct["Pr(>|t|)"]
    )
  }) %>%
  ungroup()

cat("=== Task A: Pre-invasion sentiment slope in state media, by aligned country ===\n")
cat("(slope in sentiment units per day; slope_30day = per 30 days)\n\n")
print(as.data.frame(pretrend_slopes), row.names = FALSE, digits = 4)
```

Replica of the figure above with a later start date (Dec 1, 2021) to confirm the
pre-invasion trend lines are not an artifact of fitting across a long (nine-month) window.
INVASION_DATE and WARNING_DATE are reused from the chunk above.

```{r pretrend-by-country-aligned-dec-days, fig.width=10, fig.height=7}
# Shorter buildup display window (later start; same invasion / warning markers)
PRETREND_START_DEC <- as.Date("2021-12-01")

data_pretrend_dec <- data %>%
  filter(country %in% CSTO_COUNTRIES, state_owned == 1,
         date_publish >= PRETREND_START_DEC, date_publish <= PRETREND_END) %>%
  mutate(country = droplevels(country))

agg_pretrend_dec <- data_pretrend_dec %>%
  group_by(country, date_publish) %>%
  summarize(sentiment_clean = mean(sentiment_clean, na.rm = TRUE),
            num_obs = n(), .groups = "drop")

# Pre-invasion daily means only (linear fit restricted to this window)
agg_pretrend_dec_pre <- agg_pretrend_dec %>%
  filter(date_publish < INVASION_DATE)

pretrend_by_country_aligned_dec_graph <- ggplot(agg_pretrend_dec,
                                                 aes(x = date_publish, y = sentiment_clean)) +
  geom_point(aes(size = num_obs), alpha = 0.2, inherit.aes = TRUE) +
  geom_smooth(data = agg_pretrend_dec_pre, method = "lm", se = TRUE, color = "red4") +
  geom_vline(xintercept = INVASION_DATE, linetype = "dashed", alpha = 0.7) +
  geom_vline(xintercept = WARNING_DATE, linetype = "dotted", color = "grey30") +
  scale_size(name = "Observations") +
  facet_wrap(~ country, scales = "free_y") +
  theme_classic() +
  labs(
    title = "Pre-Invasion Sentiment Trend in State Media, Dec 1 Start (Day)",
    subtitle = "Russia-aligned countries; dotted = Dec 7 warning, dashed = Feb 24 invasion",
    x = "Publication date",
    y = "Mean sentiment toward Russia"
  )

pretrend_by_country_aligned_dec_graph

ggsave(plot = pretrend_by_country_aligned_dec_graph,
       file.path(FIGURES_HETEROGENEITY_DAYS, "pretrend_by_country_aligned_dec.png"),
       width = 10, height = 7)
```

## State Media Alignment Regressions

### CSTO Countries Only

```{r align-csto}
# Filter to CSTO data, non military
data_align_state_csto <- data_align %>%
  filter(state_owned == 1, csto == 1) %>%
  filter(!topic_clean %in% "Military")

# Applying a Z-Score Transformation
data_align_state_csto <- data_align_state_csto %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                   sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()

covs_matrix <- model.matrix(~ topic_clean - 1, data = data_align_state_csto)

model5a_csto_z <- rdrobust(
  y = data_align_state_csto$sentiment_z,
  x = data_align_state_csto$running,
  covs = covs_matrix,
  cluster = data_align_state_csto$source_domain
)

summary(model5a_csto_z)
```


### Neutral Countries Only

```{r align-neutral}
# Filter data to neutral countries only
data_align_state_neutral <- data_align %>%
  filter(state_owned == 1, csto == 0) %>%
  filter(!topic_clean %in% "Military")

# Applying a Z-Score Transformation
data_align_state_neutral <- data_align_state_neutral %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                   sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()

covs_matrix <- model.matrix(~ topic_clean - 1, data = data_align_state_neutral)

model5a_neutral_z <- rdrobust(
  y = data_align_state_neutral$sentiment_z,
  x = data_align_state_neutral$running,
  covs = covs_matrix,
  cluster = data_align_state_neutral$source_domain
)

summary(model5a_neutral_z)
```

# Diff-in-Disc Analysis

## Full Data

### State Media Sample and Z-Score

The diff-in-disc sample is state-owned media in non-NATO countries, contrasting
Russia-aligned against neutral outlets. Sentiment is z-scored within source, so
outlets with different baseline tone are on a common scale. This chunk builds the
sample every model below is fitted on; no full-data model is fitted, since none
reaches a table 10b or 11 builds.

```{r align-diff}
data_align_state <- data_align %>%
  filter(state_owned == 1) %>%
  mutate(source_domain = droplevels(source_domain))

data_align_state <- data_align_state %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                   sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()

cat("State media, non-NATO sample:", nrow(data_align_state), "articles\n")
```


## Optimal Bandwidth

### Optimal Bandwidth Sentiment Z

```{r align-optimal-z}
# Residualize the dependent variable for fixed effects to do bandwidth selection
resid_y <- feols(sentiment_z ~ 1 | topic_clean + csto,
                 data = data_align_state)$residuals

bw_align <- rdbwselect(y = resid_y,
                       x = data_align_state$running,
                       kernel = "triangular",
                       cluster = data_align_state$source_domain,
                       p = 1,
                       bwselect = "mserd")

optimal_bw_align <- bw_align$bws[1, 1]
cat("Optimal bandwidth:", round(optimal_bw_align, 1), "days\n")

optimal_bandwidth_data_state <- data_align_state %>%
  filter(running < optimal_bw_align, running > -optimal_bw_align)

model5a_opt_z <- feols(sentiment_z ~ running * treatment * csto | topic_clean,
                     cluster = ~source_domain,
                     data = optimal_bandwidth_data_state)

summary(model5a_opt_z)

# Wild cluster bootstrap for model5a_opt_z
boot_model5a_opt_z <- run_wild_bootstrap(model5a_opt_z, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_opt_z$se, "\n")
cat("Bootstrap p-value:", boot_model5a_opt_z$p_val, "\n")
```

## Non-Military

### Non-Military Sample

Military coverage moves for reasons unrelated to the signalling mechanism, so
Table 4 Model 4 and the matched model below are fitted with it omitted. This
chunk builds that sample; the bandwidth is re-selected on it in the next chunk.

```{r align-non-mil}
data_align_state_non_mil <- data_align_state %>%
  filter(!topic_clean %in% "Military")

cat("State media, non-military sample:", nrow(data_align_state_non_mil), "articles\n")
```

### Non-Military, Sentiment Z

```{r align-non-mil-z}
# Create New z score
data_align_state_non_mil <- data_align_state_non_mil %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                   sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()


# Residualize the dependent variable for fixed effects to do bandwidth selection
resid_y <- feols(sentiment_z ~ 1 | topic_clean + csto,
                 data = data_align_state_non_mil)$residuals

bw_align_non_mil <- rdbwselect(y = resid_y,
                               x = data_align_state_non_mil$running,
                               kernel = "triangular",
                               cluster = data_align_state_non_mil$source_domain,
                               p = 1,
                               bwselect = "mserd")

optimal_bw_align_non_mil <- bw_align_non_mil$bws[1, 1]
cat("Optimal bandwidth (non-mil):", round(optimal_bw_align_non_mil, 1), "days\n")

optimal_bandwidth_data_state_non_mil <- data_align_state_non_mil %>%
  filter(running < optimal_bw_align_non_mil, running > -optimal_bw_align_non_mil)

model5a_opt_non_mil_z <- feols(sentiment_z ~ running
                             * treatment * csto | topic_clean,
                             cluster = ~source_domain,
                             data = optimal_bandwidth_data_state_non_mil)

summary(model5a_opt_non_mil_z)

# Wild cluster bootstrap for model5a_opt_non_mil_z
boot_model5a_opt_non_mil_z <- run_wild_bootstrap(model5a_opt_non_mil_z, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_opt_non_mil_z$se, "\n")
cat("Bootstrap p-value:", boot_model5a_opt_non_mil_z$p_val, "\n")
```


```{r}

# Prepare the data for plotting
plot_data <- optimal_bandwidth_data_state_non_mil %>%
  group_by(source_domain) %>%
  mutate(
    # Recalculate Local Z-score
    sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                   sd(sentiment_clean, na.rm = TRUE)
  ) %>%
  ungroup() %>%
  select(source_domain, sentiment_clean, sentiment_z) %>%
  pivot_longer(cols = c(sentiment_clean, sentiment_z),
               names_to = "Type", values_to = "Value")

# Plotting the comparison
zscore_comp <- ggplot(plot_data, aes(x = Value, y = source_domain, fill = Type)) +
  geom_density_ridges(alpha = 0.5, scale = 0.9) +
  facet_wrap(~Type, scales = "free_x") +
  theme_minimal() +
  labs(title = "Ternary Sentiment vs. Z-Scored Sentiment by Source",
       subtitle = "Local Z-scoring centers each source and adjusts for their specific volatility",
       x = "Sentiment Value",
       y = "Media Outlet") +
  scale_fill_manual(values = c("sentiment_clean" = "#69b3a2", "sentiment_z" = "#404080"))

zscore_comp

ggsave(plot = zscore_comp,
       file.path(FIGURES_HETEROGENEITY_DAYS, "sentiment_zscore_comparison.png"),
       width = 10, height = 7)
```


# Robustness

## Matching

### Initial Match

```{r}
# Subset to data of interest

matching_data <- optimal_bandwidth_data_state_non_mil %>%
  select(sentiment_z, running, treatment, csto,
         topic_clean, source_domain, country)

# Match on topic and publication day

ps_model <- matchit(
  csto ~ running + topic_clean,
  data = matching_data,
  method = "exact",
  ratio = 1,
)

summary(ps_model)
```

### Assess Balance

```{r}
# Numerical balance check (better)
bal.tab(ps_model, un = TRUE, stats = c("m", "v"), thresholds = c(m = 0.1))
# Want: all standardized mean differences < 0.1 after matching

# Love plot (publication quality)
love <- love.plot(ps_model, binary = "std", thresholds = c(m = 0.1))
love
ggsave(plot = love,
       file.path(FIGURES_HETEROGENEITY_DAYS, "love_plot.png"),
       width = 10, height = 7)
```

### Matching analysis

```{r}
# Extract matched data and calculate treatment effects
matched_data <-match.data(ps_model)

matched_model <- feols(sentiment_z ~ running
                                     * treatment * csto |
                                       topic_clean,
                                     cluster = ~source_domain,
                                     data = matched_data
                                     )

summary(matched_model)


# Wild cluster bootstrap for matched_model
boot_matched_model <- run_wild_bootstrap(matched_model, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_matched_model$se, "\n")
cat("Bootstrap p-value:", boot_matched_model$p_val, "\n")
```



### Sensitivity of OVB

```{r}
# Save the bootstrapped p-val
bootstrapped_se <- boot_matched_model$p_val

# Respecify the model using lm
lm_model <- lm(sentiment_z ~ running * treatment * csto +
                 factor(topic_clean),
               data = matched_data)


# Sensitivity analysis
sensitivity <- sensemakr(
  model = lm_model,
  treatment = "treatment:csto",
  benchmark_covariates = c("running:treatment"),
  kd = 1,
  ky = 1,
  reduce = TRUE
)

summary(sensitivity)
```


```{r}
partial_r2(lm_model, covariates = c("running:treatment",
                                     "running:csto",
                                     "treatment",
                                     "csto"))

treatment_r2 <- partial_r2(lm_model, covariates = c("treatment"))
```


```{r}
# Manually recompute the CI bound using the bootstrapped SE
coef_interest <- coef(lm_model)["treatment:csto"]
rv_ci <- coef_interest / bootstrapped_se  # your corrected t-stat for reference

plot(sensitivity,
     xlab = "Partial R² of confounder with CSTO membership",
     ylab = "Partial R² of confounder with sentiment",
     main = "Sensitivity to Unobserved Confounding",
     lim.x = .1,
     lim.y = .1,
     col.contour = "grey60",
     label.text = FALSE)   # turn off the ugly overlapping label first
text(x = 0.01, y = 0.00005,
     labels = "running:treatment",
     cex = 0.8, pos = 4)
```


```{r}
# Sensitivity Plot

# Extract the data sensemakr uses for the plot
ovb_contour_data <- function(sensitivity, lim = 0.005) {

  # Grid of r2dz.x and r2yz.dx values
  r2dz <- seq(0, lim, length.out = 400)
  r2yz <- seq(0, lim, length.out = 400)
  grid <- expand.grid(r2dz.x = r2dz, r2yz.dx = r2yz)

  # Extract key stats
  estimate <- sensitivity$sensitivity_stats$estimate
  se <- sensitivity$sensitivity_stats$se
  df <- sensitivity$sensitivity_stats$dof

  # Compute adjusted estimate across grid
  grid$adjusted <- mapply(function(r2dz, r2yz) {
    sensemakr::adjusted_estimate(
      estimate = estimate,
      se = se,
      dof = df,
      r2dz.x = r2dz,
      r2yz.dx = r2yz
    )
  }, grid$r2dz.x, grid$r2yz.dx)

  return(grid)
}

# Extract benchmark points
benchmark_df <- data.frame(
  r2dz.x = sensitivity$bounds$r2dz.x,
  r2yz.dx = sensitivity$bounds$r2yz.dx,
  label = sensitivity$bounds$bound_label
)

# Build contour data
# Rebuild with wider x limit
contour_data <- ovb_contour_data(sensitivity, lim = 0.1)

sensitivity_plot <- ggplot(contour_data, aes(x = r2dz.x, y = r2yz.dx, z = adjusted)) +
  geom_contour(colour = "grey60",
               breaks = c(-0.1, -0.05, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3)) +
  geom_contour(breaks = 0,
               colour = "red",
               linetype = "dashed",
               linewidth = 0.8) +
  geom_point(data = benchmark_df,
             aes(x = r2dz.x, y = r2yz.dx),
             shape = 18, colour = "red", size = 3,
             inherit.aes = FALSE) +
  annotate("point", x = 0, y = 0, shape = 17, size = 3) +
  annotate("text", x = 0.002, y = 0.003,
           label = "Unadjusted\n(-0.146)",
           size = 5, hjust = 0) +
  annotate("text", x = 0.047, y = 0.003,
           label = "running:treatment",
           size = 5, hjust = 0) +
  coord_cartesian(xlim = c(0, 0.1), ylim = c(0, 0.1)) +
  scale_x_continuous(breaks = seq(0, 0.1, by = 0.02),
                     labels = scales::number_format(accuracy = 0.01)) +
  scale_y_continuous(breaks = seq(0, 0.1, by = 0.02),
                     labels = scales::number_format(accuracy = 0.01)) +
  labs(
    x = "Partial R² of confounder with CSTO membership",
    y = "Partial R² of confounder with sentiment",
    title = "Sensitivity to Unobserved Confounding, CSTO Affiliation",
    subtitle = "Red dashed line indicates where estimate = 0"
  ) +
  theme_bw() +
  theme(
    panel.grid.minor = element_blank(),
    plot.title = element_text(face = "bold"),
    legend.position = "none"
  )

sensitivity_plot

ggsave(plot = sensitivity_plot,
       file.path(FIGURES_HETEROGENEITY_DAYS, "sensitivity_ovb_csto.png"),
       width = 10, height = 7)
```

The robustness value of 4.38% indicates that an unobserved confounder would need to simultaneously explain 4.38% of residual variance in both CSTO membership and sentiment to explain away our result. To contextualize this threshold, our observed covariates — including treatment assignment (partial R² = 0.0002%) and CSTO membership itself (partial R² = 0.0001%) — explain a fraction of this amount. We additionally benchmark against temporal proximity to the date of the invasion (partial R² = 4.6% for CSTO membership, 0.00001% for sentiment), which represents the strongest observed predictor of group assignment in our model. Despite exceeding the robustness value threshold on the treatment dimension, this benchmark explains essentially no variance in sentiment outcomes — as visible in Figure X, where the benchmark point sits far to the right of the zero contour but hugging the x-axis. An unobserved confounder would therefore need to be approximately 21,900 times more influential than treatment assignment itself, and simultaneously predict sentiment far more strongly than the timing of the invasion, to overturn our finding. This suggests the result is highly robust to potential confounding.

We caution that robustness values should never be interpreted in isolation. The partial R² scale is model and data specific, and a robustness value that appears small in absolute terms may represent an implausibly large confounding requirement relative to the explanatory power of observed covariates. We recommend always reporting benchmark partial R² values alongside the robustness value to allow readers to calibrate the practical significance of the sensitivity result.


# Save Results

```{r save}
results_het <- list(
  # Table 4 Models 1-2: separate RDDs, Russia-aligned and neutral state media
  model5a_csto_z = model5a_csto_z,
  model5a_neutral_z = model5a_neutral_z,

  # Table 4 Models 3-4: diff-in-disc at the optimal bandwidth, all topics and
  # military omitted
  model5a_opt_z = model5a_opt_z,
  model5a_opt_non_mil_z = model5a_opt_non_mil_z,

  # Table 4 Model 5: matched
  matched_model = matched_model,

  # Wild cluster bootstrap results behind the significance stars
  bootstrap_se = list(
    model5a_opt_z = boot_model5a_opt_z,
    model5a_opt_non_mil_z = boot_model5a_opt_non_mil_z,
    matched_model = boot_matched_model
  )
)

saveRDS(results_het, file.path(DATA_INTERMEDIATE, "06_alignment_results.rds"))
cat("Results saved to:", file.path(DATA_INTERMEDIATE, "06_alignment_results.rds"), "\n")
```

# Session Info

```{r session-info}
print_session_info()
```
