---
title: "06B - Russian Alignment Analysis (Drop No-Time Articles) (CSTO vs Neutral)"
author: "Donald Moratz"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

# Overview

This script examines heterogeneous treatment effects by Russian alignment (CSTO vs Neutral) only, using time as a continuous running variable, after dropping articles without exact publication times.

**Inputs:**
- `data/intermediate/02_cleaned_data.rds`
- `data/intermediate/02_data_non_ukraine.rds`

**Outputs:**
- Table 3F (Russian Alignment)

```{r setup-drop, include=FALSE}
source("00_setup.R")
knitr::opts_chunk$set(fig.path = paste0(FIGURES_HETEROGENEITY_DROP, "/"))
options(digits = 10)

set.seed(3184)
```

# Load Data

```{r load-drop}
data <- readRDS(file.path(DATA_INTERMEDIATE, "02_cleaned_data.rds"))
data_non_ukraine <- readRDS(file.path(DATA_INTERMEDIATE, "02_data_non_ukraine.rds"))

data <- data %>% filter(has_time == TRUE)
data_non_ukraine <- data_non_ukraine %>% filter(has_time == TRUE)

cat("Full data after dropping no-time articles:", nrow(data), "articles\n")
cat("Non-Ukraine data after dropping:", nrow(data_non_ukraine), "articles\n")

data <- data %>% mutate(across(c(topic_clean, country, source_domain), as.factor))
data_non_ukraine <- data_non_ukraine %>% mutate(across(c(topic_clean, country, source_domain), as.factor))
```

# Russian Alignment Analysis (CSTO vs Neutral)

## Create Alignment Subsets

```{r alignment-data-drop}
# Filter to non-NATO countries for alignment analysis
data_align <- data %>%
  filter(nato == 0)%>%
  drop_na()

# Create alignment indicator
data_align <- data_align %>%
  mutate(align_indicator = factor(case_when(
    indicator == 1 & csto == 1 ~ "Pre. Ind. CSTO",
    indicator == 1 & csto == 0 ~ "Pre. Ind. Neut",
    indicator == 2 & csto == 1 ~ "Pre. State CSTO",
    indicator == 2 & csto == 0 ~ "Pre. State Neut",
    indicator == 3 & csto == 1 ~ "Post Ind. CSTO",
    indicator == 3 & csto == 0 ~ "Post Ind. Neut",
    indicator == 4 & csto == 1 ~ "Post State CSTO",
    indicator == 4 & csto == 0 ~ "Post State Neut"
  ),
  levels = c("Pre. Ind. CSTO", "Pre. Ind. Neut", "Pre. State CSTO",
             "Pre. State Neut", "Post Ind. CSTO", "Post Ind. Neut",
             "Post State CSTO", "Post State Neut")))

cat("Non-NATO countries sample:", nrow(data_align), "articles\n")
cat("CSTO:", sum(data_align$csto), "\n")
cat("Neutral:", sum(data_align$csto == 0), "\n")
```

## Visualization: Independent Media by Alignment

```{r align-ind-plot-drop, fig.width=10, fig.height=7}
agg_data_align_ind <- data_align %>%
  filter(state_owned == 0) %>%
  group_by(running_continuous, csto) %>%
  summarize(sentiment_clean = mean(sentiment_clean), num_obs = n(), .groups = "drop")

data_align %>%
  filter(state_owned == 0) %>%
  ggplot(aes(x = running_continuous, y = sentiment_clean, group = align_indicator, color = align_indicator)) +
  geom_point(data = agg_data_align_ind,
             aes(x = running_continuous, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = COLORS_DISCS, name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on Independent Media Sentiment (Drop No-Time)",
    subtitle = "Neutral vs Russia Aligned, Difference in Discontinuities",
    x = "Hours Pre/Post Invasion",
    y = "Sentiment"
  )
```

## Visualization: State Media by Alignment

```{r align-state-plot-drop, fig.width=10, fig.height=7}
agg_data_align_state <- data_align %>%
  filter(state_owned == 1) %>%
  group_by(running_continuous, csto) %>%
  summarize(sentiment_clean = mean(sentiment_clean), num_obs = n(), .groups = "drop")

state_align_discs_graph <- data_align %>%
  filter(state_owned == 1) %>%
  ggplot(aes(x = running_continuous, y = sentiment_clean, group = align_indicator, color = align_indicator)) +
  geom_point(data = agg_data_align_state,
             aes(x = running_continuous, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = COLORS_DISCS, name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on State Media Sentiment (Drop No-Time)",
    subtitle = "Neutral vs Russia Aligned, Difference in Discontinuities",
    x = "Hours Pre/Post Invasion",
    y = "Sentiment"
  )

state_align_discs_graph

ggsave(plot = state_align_discs_graph,
       file.path(FIGURES_HETEROGENEITY_DROP, "state_align_discs_drop.png"),
       width = 10, height = 7)
```

## State Media Alignment Regressions

### CSTO Countries Only

```{r align-csto-drop}
# Filter to CSTO data, non military
data_align_state_csto <- data_align %>%
  filter(state_owned == 1, csto == 1) %>%
  filter(!topic_clean %in% "Military") %>%
  mutate(running_continuous = running_continuous / 86400.0)

covs_matrix <- model.matrix(~ source_domain + topic_clean - 1, data = data_align_state_csto)

model5a_csto <- rdrobust(
  y = data_align_state_csto$sentiment_clean,
  x = data_align_state_csto$running_continuous,
  covs = covs_matrix,
  cluster = data_align_state_csto$source_domain
)

summary(model5a_csto)
```

```{r align-csto-z-drop}
# Applying a Z-Score Transformation
data_align_state_csto <- data_align_state_csto %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                   sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()

covs_matrix <- model.matrix(~ topic_clean - 1, data = data_align_state_csto)

model5a_csto_z <- rdrobust(
  y = data_align_state_csto$sentiment_z,
  x = data_align_state_csto$running_continuous,
  covs = covs_matrix,
  cluster = data_align_state_csto$source_domain
)

summary(model5a_csto_z)
```


### Neutral Countries Only

```{r align-neutral-drop}
# Filter data to neutral countries only
data_align_state_neutral <- data_align %>%
  filter(state_owned == 1, csto == 0) %>%
  filter(!topic_clean %in% "Military") %>%
  mutate(running_continuous = running_continuous / 86400)

covs_matrix <- model.matrix(~ source_domain + topic_clean - 1, data = data_align_state_neutral)

model5a_neutral <- rdrobust(
  y = data_align_state_neutral$sentiment_clean,
  x = data_align_state_neutral$running_continuous,
  covs = covs_matrix,
  cluster = data_align_state_neutral$source_domain
)

summary(model5a_neutral)
```

```{r align-neutral-z-drop}
# Applying a Z-Score Transformation
data_align_state_neutral <- data_align_state_neutral %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                   sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()

covs_matrix <- model.matrix(~ topic_clean - 1, data = data_align_state_neutral)

model5a_neutral_z <- rdrobust(
  y = data_align_state_neutral$sentiment_z,
  x = data_align_state_neutral$running_continuous,
  covs = covs_matrix,
  cluster = data_align_state_neutral$source_domain
)

summary(model5a_neutral_z)
```

# Diff-in-Disc Analysis

## Full Data

### Full Data, Topic FEs
Diff-in-Disc: CSTO vs Neutral (State Media)

```{r align-diff-drop}
data_align_state <- data_align %>%
  filter(state_owned == 1) %>%
  mutate(source_domain = droplevels(source_domain)) %>%
  mutate(running_continuous = running_continuous / 86400)

model5a <- feols(sentiment_clean ~ running_continuous * treatment * csto | topic_clean,
                 cluster = ~source_domain,
                 data = data_align_state)

summary(model5a)

# Wild cluster bootstrap for model5a
boot_model5a <- run_wild_bootstrap(model5a, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a$se, "\n")
cat("Bootstrap p-value:", boot_model5a$p_val, "\n")
```


### Full Data with FEs

```{r align-full-drop}

model5a_full <- feols(sentiment_clean ~ running_continuous *
                        treatment * csto
                        | topic_clean + source_domain,
                      cluster = ~source_domain,
                      data = data_align_state)

summary(model5a_full)

# Wild cluster bootstrap for model5a_full
boot_model5a_full <- run_wild_bootstrap(model5a_full, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_full$se, "\n")
cat("Bootstrap p-value:", boot_model5a_full$p_val, "\n")
```

### Sentiment Z

```{r align-diff-z-drop}
data_align_state <- data_align_state %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                   sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()

model5a_z <- feols(sentiment_z ~ running_continuous * treatment * csto | topic_clean,
                 cluster = ~source_domain,
                 data = data_align_state)

summary(model5a_z)

# Wild cluster bootstrap for model5a
boot_model5a_z <- run_wild_bootstrap(model5a_z, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_z$se, "\n")
cat("Bootstrap p-value:", boot_model5a_z$p_val, "\n")
```


## Optimal Bandwidth

### Optimal Bandwidth, Topic FEs

```{r align-optimal-drop}
# Residualize the dependent variable for fixed effects to do bandwidth selection
resid_y <- feols(sentiment_clean ~ 1 | topic_clean + source_domain + csto,
                 data = data_align_state)$residuals

bw_align <- rdbwselect(y = resid_y,
                       x = data_align_state$running_continuous,
                       kernel = "triangular",
                       cluster = data_align_state$source_domain,
                       p = 1,
                       bwselect = "mserd")

optimal_bw_align <- bw_align$bws[1, 1]
cat("Optimal bandwidth:", round(optimal_bw_align, 1), "days\n")

optimal_bandwidth_data_state <- data_align_state %>%
  filter(running_continuous < optimal_bw_align, running_continuous > -optimal_bw_align)

model5a_opt <- feols(sentiment_clean ~ running_continuous * treatment * csto | topic_clean,
                     cluster = ~source_domain,
                     data = optimal_bandwidth_data_state)

summary(model5a_opt)

# Wild cluster bootstrap for model5a_opt
boot_model5a_opt <- run_wild_bootstrap(model5a_opt, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_opt$se, "\n")
cat("Bootstrap p-value:", boot_model5a_opt$p_val, "\n")
```


### Optimal Bandwidth Full FE

```{r align-optimal-full-fe-drop}

model5a_opt_full_fe <- feols(sentiment_clean ~ running_continuous
                                     * treatment * csto
                                       | topic_clean + source_domain,
                                     cluster = ~source_domain,
                                     data = optimal_bandwidth_data_state
                                     )

summary(model5a_opt_full_fe)

# Wild cluster bootstrap for model5a_opt
boot_model5a_opt_full_fe <- run_wild_bootstrap(model5a_opt_full_fe, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_opt_full_fe$se, "\n")
cat("Bootstrap p-value:", boot_model5a_opt_full_fe$p_val, "\n")
```

### Optimal Bandwidth Sentiment Z

```{r align-optimal-z-drop}
# Residualize the dependent variable for fixed effects to do bandwidth selection
resid_y <- feols(sentiment_z ~ 1 | topic_clean + csto,
                 data = data_align_state)$residuals

bw_align <- rdbwselect(y = resid_y,
                       x = data_align_state$running_continuous,
                       kernel = "triangular",
                       cluster = data_align_state$source_domain,
                       p = 1,
                       bwselect = "mserd")

optimal_bw_align <- bw_align$bws[1, 1]
cat("Optimal bandwidth:", round(optimal_bw_align, 1), "days\n")

optimal_bandwidth_data_state <- data_align_state %>%
  filter(running_continuous < optimal_bw_align, running_continuous > -optimal_bw_align)

model5a_opt_z <- feols(sentiment_z ~ running_continuous * treatment * csto | topic_clean,
                     cluster = ~source_domain,
                     data = optimal_bandwidth_data_state)

summary(model5a_opt_z)

# Wild cluster bootstrap for model5a_opt
boot_model5a_opt_z <- run_wild_bootstrap(model5a_opt_z, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_opt_z$se, "\n")
cat("Bootstrap p-value:", boot_model5a_opt_z$p_val, "\n")
```

## Non-Military

### Non-Military Topics

```{r align-non-mil-drop}
data_align_state_non_mil <- data_align_state %>%
  filter(!topic_clean %in% "Military")

# Residualize the dependent variable for fixed effects to do bandwidth selection
resid_y <- feols(sentiment_clean ~ 1 | topic_clean + source_domain + csto,
                 data = data_align_state_non_mil)$residuals

bw_align_non_mil <- rdbwselect(y = resid_y,
                               x = data_align_state_non_mil$running_continuous,
                               kernel = "triangular",
                               cluster = data_align_state_non_mil$source_domain,
                               p = 1,
                               bwselect = "mserd")

optimal_bw_align_non_mil <- bw_align_non_mil$bws[1, 1]
cat("Optimal bandwidth (non-mil):", round(optimal_bw_align_non_mil, 1), "days\n")

optimal_bandwidth_data_state_non_mil <- data_align_state_non_mil %>%
  filter(running_continuous < optimal_bw_align_non_mil, running_continuous > -optimal_bw_align_non_mil)

model5a_opt_non_mil <- feols(sentiment_clean ~ running_continuous
                             * treatment * csto | topic_clean,
                             cluster = ~source_domain,
                             data = optimal_bandwidth_data_state_non_mil)

summary(model5a_opt_non_mil)

# Wild cluster bootstrap for model5a_opt_non_mil
boot_model5a_opt_non_mil <- run_wild_bootstrap(model5a_opt_non_mil, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_opt_non_mil$se, "\n")
cat("Bootstrap p-value:", boot_model5a_opt_non_mil$p_val, "\n")
```

### Non-Military Topics, Full FE

```{r align-non-mil-full-fe-drop}

model5a_opt_non_mil_full_fe <- feols(sentiment_clean ~ running_continuous
                                     * treatment * csto
                                       | topic_clean + source_domain,
                                     cluster = ~source_domain,
                                     data = optimal_bandwidth_data_state_non_mil
                                     )

summary(model5a_opt_non_mil_full_fe)

# Wild cluster bootstrap for model5a_opt_non_mil
boot_model5a_opt_non_mil_full_fe <- run_wild_bootstrap(model5a_opt_non_mil_full_fe, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_opt_non_mil_full_fe$se, "\n")
cat("Bootstrap p-value:", boot_model5a_opt_non_mil_full_fe$p_val, "\n")
```

### Effect Size

```{r align-effect-drop}
sd_state_owned <- sd(data_align_state$sentiment_clean)
cat("SD of sentiment (state media):", round(sd_state_owned, 3), "\n")

coef_csto_int <- model5a_opt_non_mil_full_fe$coeftable["treatment:csto", "Estimate"]
cat("CSTO x Treatment interaction effect (in SD):", round(coef_csto_int / sd_state_owned, 3), "\n")
```



### Non-Military, Sentiment Z

```{r align-non-mil-z-drop}
# Create New z score
data_align_state_non_mil <- data_align_state_non_mil %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                   sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()


# Residualize the dependent variable for fixed effects to do bandwidth selection
resid_y <- feols(sentiment_z ~ 1 | topic_clean + csto,
                 data = data_align_state_non_mil)$residuals

bw_align_non_mil <- rdbwselect(y = resid_y,
                               x = data_align_state_non_mil$running_continuous,
                               kernel = "triangular",
                               cluster = data_align_state_non_mil$source_domain,
                               p = 1,
                               bwselect = "mserd")

optimal_bw_align_non_mil <- bw_align_non_mil$bws[1, 1]
cat("Optimal bandwidth (non-mil):", round(optimal_bw_align_non_mil, 1), "days\n")

optimal_bandwidth_data_state_non_mil <- data_align_state_non_mil %>%
  filter(running_continuous < optimal_bw_align_non_mil, running_continuous > -optimal_bw_align_non_mil)

model5a_opt_non_mil_z <- feols(sentiment_z ~ running_continuous
                             * treatment * csto | topic_clean,
                             cluster = ~source_domain,
                             data = optimal_bandwidth_data_state_non_mil)

summary(model5a_opt_non_mil_z)

# Wild cluster bootstrap for model5a_opt_non_mil
boot_model5a_opt_non_mil_z <- run_wild_bootstrap(model5a_opt_non_mil_z, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_opt_non_mil_z$se, "\n")
cat("Bootstrap p-value:", boot_model5a_opt_non_mil_z$p_val, "\n")
```


```{r ggridges-viz-drop}

# Prepare the data for plotting
plot_data <- optimal_bandwidth_data_state_non_mil %>%
  group_by(source_domain) %>%
  mutate(
    # Recalculate Local Z-score
    sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                   sd(sentiment_clean, na.rm = TRUE)
  ) %>%
  ungroup() %>%
  select(source_domain, sentiment_clean, sentiment_z) %>%
  pivot_longer(cols = c(sentiment_clean, sentiment_z),
               names_to = "Type", values_to = "Value")

# Plotting the comparison
ggplot(plot_data, aes(x = Value, y = source_domain, fill = Type)) +
  geom_density_ridges(alpha = 0.5, scale = 0.9) +
  facet_wrap(~Type, scales = "free_x") +
  theme_minimal() +
  labs(title = "Ternary Sentiment vs. Z-Scored Sentiment by Source",
       subtitle = "Local Z-scoring centers each source and adjusts for their specific volatility",
       x = "Sentiment Value",
       y = "Media Outlet") +
  scale_fill_manual(values = c("sentiment_clean" = "#69b3a2", "sentiment_z" = "#404080"))

ggsave(plot = last_plot(),
       file.path(FIGURES_HETEROGENEITY_DROP, "sentiment_zscore_comparison_drop.png"),
       width = 10, height = 7)
```


## Russian Only

### Russian-Related Articles Only

```{r align-russian-drop}
data_align_state_russian <- data_align_state %>%
  filter(!topic_clean %in% "Military") %>%
  filter(!Russian.Involvement == "Not")

# Residualize the dependent variable for fixed effects to do bandwidth selection
resid_y <- feols(sentiment_clean ~ 1 | topic_clean + source_domain + csto,
                 data = data_align_state_russian)$residuals

bw_align_russian <- rdbwselect(y = resid_y,
                               x = data_align_state_russian$running_continuous,
                               kernel = "triangular",
                               cluster = data_align_state_russian$source_domain,
                               p = 1,
                               bwselect = "mserd")

optimal_bw_align_russian <- bw_align_russian$bws[1, 1]
cat("Optimal bandwidth (russian):", round(optimal_bw_align_russian, 1), "days\n")

optimal_bandwidth_data_state_russian <- data_align_state_russian %>%
  filter(running_continuous < optimal_bw_align_russian, running_continuous > -optimal_bw_align_russian)

model5a_opt_russian <- feols(sentiment_clean ~ running_continuous *
                               treatment * csto | topic_clean,
                             cluster = ~source_domain,
                             data = optimal_bandwidth_data_state_russian)

summary(model5a_opt_russian)

# Wild cluster bootstrap for model5a_opt_russian
boot_model5a_opt_russian <- run_wild_bootstrap(model5a_opt_russian, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_opt_russian$se, "\n")
cat("Bootstrap p-value:", boot_model5a_opt_russian$p_val, "\n")
```

### Russia Only, Full FE

```{r align-russian-full-fe-drop}

model5a_opt_rus_full_fe <- feols(sentiment_clean ~ running_continuous
                                    * treatment * csto
                                       | topic_clean + source_domain,
                                     cluster = ~source_domain,
                                     data = optimal_bandwidth_data_state_russian
                                     )

summary(model5a_opt_rus_full_fe)

# Wild cluster bootstrap for model5a_opt_non_mil
boot_model5a_opt_rus_full_fe <- run_wild_bootstrap(model5a_opt_rus_full_fe, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_opt_rus_full_fe$se, "\n")
cat("Bootstrap p-value:", boot_model5a_opt_rus_full_fe$p_val, "\n")
```


### Russia Only, Sentiment Z

```{r align-russian-z-drop}
# Create New z score
data_align_state_russian <- data_align_state_russian %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                   sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()


# Residualize the dependent variable for fixed effects to do bandwidth selection
resid_y <- feols(sentiment_z ~ 1 | topic_clean + csto,
                 data = data_align_state_russian)$residuals

bw_align_non_mil <- rdbwselect(y = resid_y,
                               x = data_align_state_russian$running_continuous,
                               kernel = "triangular",
                               cluster = data_align_state_russian$source_domain,
                               p = 1,
                               bwselect = "mserd")

optimal_bw_align_russian <- bw_align_russian$bws[1, 1]
cat("Optimal bandwidth (non-mil):", round(optimal_bw_align_russian, 1), "days\n")

optimal_bandwidth_data_state_russian <- data_align_state_russian %>%
  filter(running_continuous < optimal_bw_align_russian, running_continuous > -optimal_bw_align_russian)

model5a_opt_russian_z <- feols(sentiment_z ~ running_continuous
                             * treatment * csto | topic_clean,
                             cluster = ~source_domain,
                             data = optimal_bandwidth_data_state_russian)

summary(model5a_opt_russian_z)

# Wild cluster bootstrap for model5a_opt_non_mil
boot_model5a_opt_russian_z <- run_wild_bootstrap(model5a_opt_russian_z, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_opt_russian_z$se, "\n")
cat("Bootstrap p-value:", boot_model5a_opt_russian_z$p_val, "\n")
```

# By Topic

## By-Topic Models: Full Data

```{r topic-full-het-drop}
data_align_state_pol <- data_align_state %>% filter(topic_clean == "Political")
data_align_state_mil <- data_align_state %>% filter(topic_clean == "Military")
data_align_state_econ <- data_align_state %>% filter(topic_clean == "Economic")
data_align_state_cult <- data_align_state %>% filter(topic_clean == "Culture")
data_align_state_oth <- data_align_state %>% filter(topic_clean == "Other")

model5a_full_pol <- feols(sentiment_z ~ running_continuous * treatment * csto,
                          cluster = ~source_domain,
                          data = data_align_state_pol)
model5a_full_mil <- feols(sentiment_z ~ running_continuous * treatment * csto,
                          cluster = ~source_domain,
                          data = data_align_state_mil)
model5a_full_econ <- feols(sentiment_z ~ running_continuous * treatment * csto,
                           cluster = ~source_domain,
                           data = data_align_state_econ)
model5a_full_cult <- feols(sentiment_z ~ running_continuous * treatment * csto,
                           cluster = ~source_domain,
                           data = data_align_state_cult)
model5a_full_oth <- feols(sentiment_z ~ running_continuous * treatment * csto,
                          cluster = ~source_domain,
                          data = data_align_state_oth)

# Wild cluster bootstrap for topic-specific model5a (full data)
boot_model5a_full_pol <- run_wild_bootstrap(model5a_full_pol, "treatment:csto")
boot_model5a_full_mil <- run_wild_bootstrap(model5a_full_mil, "treatment:csto")
boot_model5a_full_econ <- run_wild_bootstrap(model5a_full_econ, "treatment:csto")
boot_model5a_full_cult <- run_wild_bootstrap(model5a_full_cult, "treatment:csto")
boot_model5a_full_oth <- run_wild_bootstrap(model5a_full_oth, "treatment:csto")
```

## By-Topic Models: Per-Topic Optimal Bandwidth

```{r topic-opt-het-drop}
# Political
bw_align_pol <- rdbwselect(y = data_align_state_pol$sentiment_z,
                           x = data_align_state_pol$running_continuous,
                           kernel = "triangular",
                           cluster = data_align_state_pol$source_domain,
                           p = 1,
                           bwselect = "mserd")

optimal_bw_align_pol <- bw_align_pol$bws[1, 1]

cat("Political optimal bandwidth:", round(optimal_bw_align_pol, 1), "days\n")

opt_align_pol <- data_align_state_pol %>% filter(running_continuous < optimal_bw_align_pol,
                                                 running_continuous > -optimal_bw_align_pol)

# Military
bw_align_mil <- rdbwselect(y = data_align_state_mil$sentiment_z,
                           x = data_align_state_mil$running_continuous,
                           kernel = "triangular",
                           cluster = data_align_state_mil$source_domain,
                           p = 1,
                           bwselect = "mserd")

optimal_bw_align_mil <- bw_align_mil$bws[1, 1]

cat("Military optimal bandwidth:", round(optimal_bw_align_mil, 1), "days\n")

opt_align_mil <- data_align_state_mil %>% filter(running_continuous < optimal_bw_align_mil,
                                                 running_continuous > -optimal_bw_align_mil)

# Economic
bw_align_econ <- rdbwselect(y = data_align_state_econ$sentiment_z,
                            x = data_align_state_econ$running_continuous,
                            kernel = "triangular",
                            cluster = data_align_state_econ$source_domain,
                            p = 1,
                            bwselect = "mserd")

optimal_bw_align_econ <- bw_align_econ$bws[1, 1]

cat("Economic optimal bandwidth:", round(optimal_bw_align_econ, 1), "days\n")

opt_align_econ <- data_align_state_econ %>% filter(running_continuous < optimal_bw_align_econ,
                                                   running_continuous > -optimal_bw_align_econ)

# Culture
bw_align_cult <- rdbwselect(y = data_align_state_cult$sentiment_z,
                            x = data_align_state_cult$running_continuous,
                            kernel = "triangular",
                            cluster = data_align_state_cult$source_domain,
                            p = 1,
                            bwselect = "mserd")

optimal_bw_align_cult <- bw_align_cult$bws[1, 1]

cat("Culture optimal bandwidth:", round(optimal_bw_align_cult, 1), "days\n")

opt_align_cult <- data_align_state_cult %>% filter(running_continuous < optimal_bw_align_cult,
                                                   running_continuous > -optimal_bw_align_cult)

# Other
bw_align_oth <- rdbwselect(y = data_align_state_oth$sentiment_z,
                           x = data_align_state_oth$running_continuous,
                           kernel = "triangular",
                           cluster = data_align_state_oth$source_domain,
                           p = 1,
                           bwselect = "mserd")

optimal_bw_align_oth <- bw_align_oth$bws[1, 1]

cat("Other optimal bandwidth:", round(optimal_bw_align_oth, 1), "days\n")

opt_align_oth <- data_align_state_oth %>% filter(running_continuous < optimal_bw_align_oth,
                                                 running_continuous > -optimal_bw_align_oth)

# Models
model5a_opt_pol <- feols(sentiment_z ~ running_continuous * treatment * csto,
                         cluster = ~source_domain,
                         data = opt_align_pol)
model5a_opt_mil <- feols(sentiment_z ~ running_continuous * treatment * csto,
                         cluster = ~source_domain,
                         data = opt_align_mil)
model5a_opt_econ <- feols(sentiment_z ~ running_continuous * treatment * csto,
                          cluster = ~source_domain,
                          data = opt_align_econ)
model5a_opt_cult <- feols(sentiment_z ~ running_continuous * treatment * csto,
                          cluster = ~source_domain,
                          data = opt_align_cult)
model5a_opt_oth <- feols(sentiment_z ~ running_continuous * treatment * csto,
                         cluster = ~source_domain,
                         data = opt_align_oth)

# Wild cluster bootstrap for topic-specific model5a (optimal BW)
boot_model5a_opt_pol <- run_wild_bootstrap(model5a_opt_pol, "treatment:csto")
boot_model5a_opt_mil <- run_wild_bootstrap(model5a_opt_mil, "treatment:csto")
boot_model5a_opt_econ <- run_wild_bootstrap(model5a_opt_econ, "treatment:csto")
boot_model5a_opt_cult <- run_wild_bootstrap(model5a_opt_cult, "treatment:csto")
boot_model5a_opt_oth <- run_wild_bootstrap(model5a_opt_oth, "treatment:csto")
```

# Robustness

## Leave-One-Out Country Robustness

```{r loo-country-drop}
countries <- unique(data_align_state_non_mil$country)
loo_results <- list()

for (cntry in countries) {
  data_loo <- data_align_state_non_mil %>%
    filter(country != cntry)

  # Re-calculate optimal bandwidth for LOO data
  resid_y <- feols(sentiment_z ~ 1 | topic_clean + csto,
                 data = data_loo)$residuals

  bw_loo <- rdbwselect(y = data_loo$sentiment_z,
                       x = data_loo$running_continuous,
                       kernel = "triangular",
                       cluster = data_loo$source_domain,
                       p = 1,
                       bwselect = "mserd")

  optimal_bw_loo <- bw_loo$bws[1, 1]

  data_loo_bw <- data_loo %>%
    filter(running_continuous < optimal_bw_loo, running_continuous > -optimal_bw_loo)

  model_loo <- feols(sentiment_z ~ running_continuous * treatment * csto | topic_clean,
                     cluster = ~source_domain,
                     data = data_loo_bw)

  boot_loo <- tryCatch(
    run_wild_bootstrap(model_loo, "treatment:csto", B = 4999),
    error = function(e) list(se = NA, p_val = NA, ci_lower = NA, ci_upper = NA, t_stat = NA)
  )
  loo_results[[cntry]] <- list(
    model = model_loo,
    bandwidth = optimal_bw_loo,
    n = nrow(data_loo_bw),
    country_dropped = cntry,
    boot_p_val = boot_loo$p_val,
    boot_se = boot_loo$se
  )
}

# Extract key coefficient (treatment:csto interaction)
loo_summary <- map_df(names(loo_results), function(cntry) {
  mod <- loo_results[[cntry]]$model
  tibble(
    country_dropped = cntry,
    estimate = coef(mod)["treatment:csto"],
    std_error = se(mod)["treatment:csto"],
    p_value = pvalue(mod)["treatment:csto"],
    n_obs = loo_results[[cntry]]$n,
    bandwidth = loo_results[[cntry]]$bandwidth
  )
})

print(loo_summary)
```

## Placebo Test: December 7th Announcement (Non-Military Topics)

```{r placebo-dec-nonmil-drop}
data_dec_align <- data_align_state_non_mil %>%
  filter(date_publish < "2022-02-19") %>%
  mutate(
    running_continuous = as.numeric(difftime(date_publish_continuous, as.POSIXct("2021-12-07 00:00:00", tz = "UTC"), units = "secs")),
    treatment = ifelse(date_publish_continuous < as.POSIXct("2021-12-07 00:00:00", tz = "UTC"), 0, 1)
  )

# Find optimal bandwidth for placebo
bw_placebo_nonmil <- rdbwselect(y = data_dec_align$sentiment_z,
                                x = data_dec_align$running_continuous,
                                kernel = "triangular",
                                cluster = data_dec_align$source_domain,
                                p = 1,
                                bwselect = "mserd")

optimal_bw_placebo_nonmil <- bw_placebo_nonmil$bws[1, 1]
cat("Placebo optimal bandwidth (non-mil):", round(optimal_bw_placebo_nonmil, 1), "seconds\n")

data_dec_align_bw <- data_dec_align %>%
  filter(running_continuous < optimal_bw_placebo_nonmil, running_continuous > -optimal_bw_placebo_nonmil)

model_placebo_nonmil <- feols(sentiment_z ~ running_continuous * treatment * csto | topic_clean,
                               cluster = ~source_domain,
                               data = data_dec_align_bw)

summary(model_placebo_nonmil)
boot_model_placebo_nonmil <- run_wild_bootstrap(model_placebo_nonmil, "treatment:csto")
cat("Bootstrap SE for treatment:csto (placebo):", boot_model_placebo_nonmil$se, "\n")
cat("Bootstrap p-value (placebo):", boot_model_placebo_nonmil$p_val, "\n")
cat("\nNote: Non-significant treatment effect suggests parallel trends assumption holds.\n")
```

## Matching

### Initial Match

```{r matching-analysis-drop}
# Subset to data of interest

matching_data <- optimal_bandwidth_data_state_non_mil %>%
  select(sentiment_z, running, running_continuous, treatment, csto,
         topic_clean, source_domain, country)

# Match on topic and publication day (using integer day from running_continuous)
matching_data <- matching_data %>%
  mutate(running_day = floor(running_continuous / 86400))

ps_model <- matchit(
  csto ~ running_day + topic_clean,
  data = matching_data,
  method = "exact",
  ratio = 1,
)

summary(ps_model)
```

### Assess Balance

```{r matching-balance-drop}
# Numerical balance check (better)
bal.tab(ps_model, un = TRUE, stats = c("m", "v"), thresholds = c(m = 0.1))
# Want: all standardized mean differences < 0.1 after matching

# Love plot (publication quality)
love <- love.plot(ps_model, binary = "std", thresholds = c(m = 0.1))
love
ggsave(plot = love,
       file.path(FIGURES_HETEROGENEITY_DROP, "love_plot_drop.png"),
       width = 10, height = 7)
```

### Matching analysis

```{r matching-model-drop}
# Extract matched data and calculate treatment effects
matched_data <- match.data(ps_model)

matched_model <- feols(sentiment_z ~ running_continuous
                                     * treatment * csto |
                                       topic_clean,
                                     cluster = ~source_domain,
                                     data = matched_data
                                     )

summary(matched_model)


# Wild cluster bootstrap for matched model
boot_matched_model <- run_wild_bootstrap(matched_model, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_matched_model$se, "\n")
cat("Bootstrap p-value:", boot_matched_model$p_val, "\n")
```



### Sensitivity of OVB

```{r sensitivity-ovb-drop}
# Save the bootstrapped p-val
bootstrapped_se <- boot_matched_model$p_val

# Respecify the model using lm
lm_model <- lm(sentiment_z ~ running_continuous * treatment * csto +
                 factor(topic_clean),
               data = matched_data)


# Sensitivity analysis
sensitivity <- sensemakr(
  model = lm_model,
  treatment = "treatment:csto",
  benchmark_covariates = c("running_continuous:treatment"),
  kd = 1,
  ky = 1,
  reduce = TRUE
)

summary(sensitivity)
```


```{r sensitivity-partialr2-drop}
partial_r2(lm_model, covariates = c("running_continuous:treatment",
                                     "running_continuous:csto",
                                     "treatment",
                                     "csto"))

treatment_r2 <- partial_r2(lm_model, covariates = c("treatment"))
```


```{r sensitivity-plot-drop}
# Manually recompute the CI bound using the bootstrapped SE
coef_interest <- coef(lm_model)["treatment:csto"]
rv_ci <- coef_interest / bootstrapped_se  # your corrected t-stat for reference

plot(sensitivity,
     xlab = "Partial R² of confounder with CSTO membership",
     ylab = "Partial R² of confounder with sentiment",
     main = "Sensitivity to Unobserved Confounding",
     lim.x = .1,
     lim.y = .1,
     col.contour = "grey60",
     label.text = FALSE)   # turn off the ugly overlapping label first
text(x = 0.01, y = 0.00005,
     labels = "running:treatment",
     cex = 0.8, pos = 4)
```


```{r sensitivity-contour-drop}
# Sensitivity Plot

# Extract the data sensemakr uses for the plot
ovb_contour_data <- function(sensitivity, lim = 0.005) {

  # Grid of r2dz.x and r2yz.dx values
  r2dz <- seq(0, lim, length.out = 400)
  r2yz <- seq(0, lim, length.out = 400)
  grid <- expand.grid(r2dz.x = r2dz, r2yz.dx = r2yz)

  # Extract key stats
  estimate <- sensitivity$sensitivity_stats$estimate
  se <- sensitivity$sensitivity_stats$se
  df <- sensitivity$sensitivity_stats$dof

  # Compute adjusted estimate across grid
  grid$adjusted <- mapply(function(r2dz, r2yz) {
    sensemakr::adjusted_estimate(
      estimate = estimate,
      se = se,
      dof = df,
      r2dz.x = r2dz,
      r2yz.dx = r2yz
    )
  }, grid$r2dz.x, grid$r2yz.dx)

  return(grid)
}

# Extract benchmark points
benchmark_df <- data.frame(
  r2dz.x = sensitivity$bounds$r2dz.x,
  r2yz.dx = sensitivity$bounds$r2yz.dx,
  label = sensitivity$bounds$bound_label
)

# Build contour data
# Rebuild with wider x limit
contour_data <- ovb_contour_data(sensitivity, lim = 0.1)

ggplot(contour_data, aes(x = r2dz.x, y = r2yz.dx, z = adjusted)) +
  geom_contour(colour = "grey60",
               breaks = c(-0.1, -0.05, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3)) +
  geom_contour(breaks = 0,
               colour = "red",
               linetype = "dashed",
               linewidth = 0.8) +
  geom_point(data = benchmark_df,
             aes(x = r2dz.x, y = r2yz.dx),
             shape = 18, colour = "red", size = 3,
             inherit.aes = FALSE) +
  annotate("point", x = 0, y = 0, shape = 17, size = 3) +
  annotate("text", x = 0.002, y = 0.003,
           label = "Unadjusted\n(-0.146)",
           size = 5, hjust = 0) +
  annotate("text", x = 0.047, y = 0.003,
           label = "running:treatment",
           size = 5, hjust = 0) +
  coord_cartesian(xlim = c(0, 0.1), ylim = c(0, 0.1)) +
  scale_x_continuous(breaks = seq(0, 0.1, by = 0.02),
                     labels = scales::number_format(accuracy = 0.01)) +
  scale_y_continuous(breaks = seq(0, 0.1, by = 0.02),
                     labels = scales::number_format(accuracy = 0.01)) +
  labs(
    x = "Partial R² of confounder with CSTO membership",
    y = "Partial R² of confounder with sentiment",
    title = "Sensitivity to Unobserved Confounding, CSTO Affiliation",
    subtitle = "Red dashed line indicates where estimate = 0"
  ) +
  theme_bw() +
  theme(
    panel.grid.minor = element_blank(),
    plot.title = element_text(face = "bold"),
    legend.position = "none"
  )

ggsave(plot = last_plot(),
       file.path(FIGURES_HETEROGENEITY_DROP, "sensitivity_ovb_csto_drop.png"),
       width = 10, height = 7)
```


## Leave One Out Matching

```{r loo-matching-drop}
countries <- unique(data_align_state_non_mil$country)
matched_loo_results <- list()

for (cntry in countries) {
  data_loo <- data_align_state_non_mil %>%
    filter(country != cntry)

  # Re-calculate optimal bandwidth for LOO data
  resid_y <- feols(sentiment_z ~ 1 | topic_clean + csto,
                 data = data_loo)$residuals

  bw_loo <- rdbwselect(y = data_loo$sentiment_z,
                       x = data_loo$running_continuous,
                       kernel = "triangular",
                       cluster = data_loo$source_domain,
                       p = 1,
                       bwselect = "mserd")

  optimal_bw_loo <- bw_loo$bws[1, 1]

  data_loo_bw <- data_loo %>%
    filter(running_continuous < optimal_bw_loo, running_continuous > -optimal_bw_loo)

  data_loo_bw <- data_loo_bw %>%
    mutate(running_day = floor(running_continuous / 86400))

  ps_model <- matchit(
    csto ~ running_day + topic_clean,
    data = data_loo_bw,
    method = "exact",
    ratio = 1,
  )

  matched_data_loo <- match.data(ps_model)

  matched_model_loo <- feols(sentiment_z ~ running_continuous
                                     * treatment * csto |
                                       topic_clean,
                                     cluster = ~source_domain,
                                     data = matched_data_loo
                                     )

  matched_boot_loo <- tryCatch(
    run_wild_bootstrap(matched_model_loo, "treatment:csto", B = 4999),
    error = function(e) list(se = NA, p_val = NA, ci_lower = NA, ci_upper = NA, t_stat = NA)
  )
  matched_loo_results[[cntry]] <- list(
    model = matched_model_loo,
    bandwidth = optimal_bw_loo,
    n = nrow(matched_data_loo),
    country_dropped = cntry,
    boot_p_val = matched_boot_loo$p_val,
    boot_se = matched_boot_loo$se
  )
}

# Extract key coefficient (treatment:csto interaction)
matched_loo_summary <- map_df(names(matched_loo_results), function(cntry) {
  mod <- matched_loo_results[[cntry]]$model
  tibble(
    country_dropped = cntry,
    estimate = coef(mod)["treatment:csto"],
    std_error = se(mod)["treatment:csto"],
    p_value = pvalue(mod)["treatment:csto"],
    n_obs = matched_loo_results[[cntry]]$n,
    bandwidth = matched_loo_results[[cntry]]$bandwidth
  )
})

print(matched_loo_summary)
```


## Heavily Saturated Non-Mil Model

```{r saturated-model-drop}
# Change source and topic to factor
optimal_bandwidth_data_state_non_mil <- optimal_bandwidth_data_state_non_mil %>%
  mutate(
    source_domain = as.factor(source_domain),
    topic_clean = as.factor(topic_clean)
  )

# Heavily saturated model
model5a_fully_saturated <- feols(
  sentiment_clean ~ running_continuous * treatment * csto |
    source_domain^topic_clean + topic_clean^treatment,
  cluster = ~source_domain,
  data = optimal_bandwidth_data_state_non_mil
)

summary(model5a_fully_saturated)
```

### Manual Wild Bootstrap Standard Errors

```{r saturated-bootstrap-drop}
# set.seed(3184)
# B <- 99
# 
# # Original model
# model_original <- model5a_fully_saturated
# original_coef <- coef(model_original)["treatment:csto"]
# original_se <- se(model_original)["treatment:csto"]
# original_t <- original_coef / original_se
# 
# cat("Original t-stat:", original_t, "\n")
# 
# # CRITICAL: Estimate RESTRICTED model under the null (treatment:csto = 0)
# # Remove treatment:csto from the formula
# model_restricted <- feols(
#   sentiment_clean ~ running_continuous + treatment + csto + running_continuous:treatment + running_continuous:csto +
#     running_continuous:treatment:csto |  # Keep triple interaction but not treatment:csto
#     source_domain^topic_clean + topic_clean^treatment,
#   cluster = ~source_domain,
#   data = optimal_bandwidth_data_state_non_mil
# )
# 
# # Get residuals and fitted values from RESTRICTED model
# residuals_restricted <- residuals(model_restricted)
# fitted_restricted <- fitted(model_restricted)
# 
# cat("Using restricted model residuals (null imposed)\n")
# 
# # Get clusters
# clusters <- unique(optimal_bandwidth_data_state_non_mil$source_domain)
# n_clusters <- length(clusters)
# 
# # Bootstrap
# boot_t_stats <- numeric(B)
# 
# for(b in 1:B) {
#   # Generate Rademacher weights
#   cluster_weights <- sample(c(-1, 1), n_clusters, replace = TRUE)
# 
#   # Assign to observations
#   data_boot <- optimal_bandwidth_data_state_non_mil
#   data_boot$weight <- sapply(data_boot$source_domain, function(clust) {
#     cluster_weights[which(clusters == clust)]
#   })
# 
#   # Create bootstrap outcome using RESTRICTED fitted values
#   data_boot$sentiment_boot <- fitted_restricted + data_boot$weight * residuals_restricted
# 
#   # Re-estimate FULL model on bootstrap data
#   model_boot <- feols(
#     sentiment_boot ~ running_continuous * treatment * csto |
#       source_domain^topic_clean + topic_clean^treatment,
#     cluster = ~source_domain,
#     data = data_boot
#   )
# 
#   boot_coef <- coef(model_boot)["treatment:csto"]
#   boot_se <- se(model_boot)["treatment:csto"]
#   boot_t_stats[b] <- boot_coef / boot_se
# 
#   if(b %% 100 == 0) cat("Iteration:", b, "\n")
# }
# 
# # Calculate p-value
# p_value <- mean(abs(boot_t_stats) >= abs(original_t))
# 
# cat("\n=== Results ===\n")
# cat("Original t-stat:", original_t, "\n")
# cat("Mean bootstrap t-stat (should be ~0):", mean(boot_t_stats), "\n")
# cat("P-value:", p_value, "\n")
# 
# # Plot
# hist(boot_t_stats, breaks=30, main="Wild Bootstrap t-statistics (Null Imposed)",
#      xlab="t-statistic")
# abline(v=original_t, col="red", lwd=2)
# abline(v=0, col="blue", lwd=2, lty=2)
# legend("topright", c("Original t", "Null (t=0)"), col=c("red","blue"), lty=c(1,2), lwd=2)
# 
# # Extract bootstrap results for saturated model in standard format
# boot_model5a_fully_saturated <- list(
#   se = original_se,
#   p_val = p_value,
#   ci_lower = NA,  # Not computed in manual bootstrap
#   ci_upper = NA,  # Not computed in manual bootstrap
#   t_stat = original_t
# )
# cat("Saturated model bootstrap results extracted\n")
```

# Country-Level Analysis

## State Media by Country and Alliance

```{r country-facet-drop, fig.width=12, fig.height=8}
# Create alliance for faceting
data_long <- data %>%
  pivot_longer(cols = c(nato, csto, neutral),
               names_to = "alliance",
               values_to = "membership") %>%
  filter(membership == 1) %>%
  mutate(
    alliance = factor(alliance, levels = c("nato", "csto", "neutral")),
    state_indicator = factor(paste(country, treatment, sep = ", "))
  )

data_long %>%
  filter(state_owned == 1) %>%
  ggplot(aes(x = running_continuous, y = sentiment_clean, group = state_indicator, color = country)) +
  geom_smooth(method = "lm", se = FALSE) +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  facet_wrap(~alliance, nrow = 2) +
  labs(
    title = "Effect of Invasion on State Media Sentiment by Country (Drop No-Time)",
    subtitle = "Faceted by Alliance",
    x = "Hours Pre/Post Invasion",
    y = "Sentiment"
  )
```

# Summary Tables

## Summary Table (Table 3F)

```{r table3f-drop}
note_text <- "All standard errors are clustered at the source level. Model 1 uses no fixed effects. Model 2 uses full data with topic fixed effects. Model 3 uses the optimal bandwidth with topic fixed effects. Model 4 omits military-related articles and uses a re-optimized bandwidth. Model 5 uses only Russian-related (non-military) articles with a re-optimized bandwidth. Model 6 uses optimal bandwidth with full FEs (topic + source). Model 7 uses non-military subset with full FEs. Model 8 uses full saturation (source-topic and topic-treatment FEs). Articles without publication times are dropped."
note_wrapped <- str_wrap(note_text, width = 80)

table_3f <- modelsummary(
  list("(1)" = model5a, "(2)" = model5a_full, "(3)" = model5a_opt,
       "(4)" = model5a_opt_non_mil, "(5)" = model5a_opt_russian,
       "(6)" = model5a_opt_full_fe, "(7)" = model5a_opt_non_mil_full_fe,
       "(8)" = model5a_fully_saturated),
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors",
  title = "Russian Alignment: Difference in Discontinuity Analysis (Drop No-Time Articles)",
  notes = note_wrapped
)

table_3f
```

## Summary Table: By Topic (Optimal Bandwidth)

```{r table3f-topic-opt-drop}
note_topic_opt <- "All standard errors are clustered at the source level. Each model uses a per-topic re-optimized bandwidth. State media in non-NATO countries only. Articles without publication times are dropped."
note_topic_opt_wrapped <- str_wrap(note_topic_opt, width = 80)

table_3f_topic_opt <- modelsummary(
  list("Political" = model5a_opt_pol, "Military" = model5a_opt_mil,
       "Economic" = model5a_opt_econ, "Cultural" = model5a_opt_cult, "Other" = model5a_opt_oth),
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors",
  title = "Russian Alignment By Topic (Per-Topic Optimal Bandwidth, Drop No-Time Articles)",
  notes = note_topic_opt_wrapped
)

table_3f_topic_opt
```

## Summary Table: By Topic (Full Data)

```{r table3f-topic-full-drop}
note_topic_full <- "All standard errors are clustered at the source level. Each model uses the full dataset (no bandwidth restriction). State media in non-NATO countries only. Articles without publication times are dropped."
note_topic_full_wrapped <- str_wrap(note_topic_full, width = 80)

table_3f_topic_full <- modelsummary(
  list("Political" = model5a_full_pol, "Military" = model5a_full_mil,
       "Economic" = model5a_full_econ, "Cultural" = model5a_full_cult, "Other" = model5a_full_oth),
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors",
  title = "Russian Alignment By Topic (Full Data, Drop No-Time Articles)",
  notes = note_topic_full_wrapped
)

table_3f_topic_full
```

# Save Results

```{r save-drop}
results_het_drop <- list(
  # Main models
  model5a = model5a,
  model5a_full = model5a_full,
  model5a_opt = model5a_opt,
  model5a_opt_non_mil = model5a_opt_non_mil,
  model5a_opt_russian = model5a_opt_russian,
  model5a_csto = model5a_csto,
  model5a_neutral = model5a_neutral,
  model5a_opt_full_fe = model5a_opt_full_fe,
  model5a_opt_non_mil_full_fe = model5a_opt_non_mil_full_fe,
  model5a_fully_saturated = model5a_fully_saturated,
  matched_model = matched_model,

  # Z-score models
  model5a_z = model5a_z,
  model5a_csto_z = model5a_csto_z,
  model5a_neutral_z = model5a_neutral_z,
  model5a_opt_z = model5a_opt_z,
  model5a_opt_non_mil_z = model5a_opt_non_mil_z,
  model5a_opt_russian_z = model5a_opt_russian_z,

  # Russian Full FE
  model5a_opt_rus_full_fe = model5a_opt_rus_full_fe,

  # Topic-specific models
  model5a_opt_pol = model5a_opt_pol,
  model5a_opt_mil = model5a_opt_mil,
  model5a_opt_econ = model5a_opt_econ,
  model5a_opt_cult = model5a_opt_cult,
  model5a_opt_oth = model5a_opt_oth,
  model5a_full_pol = model5a_full_pol,
  model5a_full_mil = model5a_full_mil,
  model5a_full_econ = model5a_full_econ,
  model5a_full_cult = model5a_full_cult,
  model5a_full_oth = model5a_full_oth,

  # Bootstrap standard errors
  bootstrap_se = list(
    # Main model5a variants
    model5a = boot_model5a,
    model5a_full = boot_model5a_full,
    model5a_opt = boot_model5a_opt,
    model5a_opt_non_mil = boot_model5a_opt_non_mil,
    model5a_opt_russian = boot_model5a_opt_russian,
    model5a_opt_full_fe = boot_model5a_opt_full_fe,
    model5a_opt_non_mil_full_fe = boot_model5a_opt_non_mil_full_fe,
    model5a_fully_saturated = boot_model5a_fully_saturated,
    matched_model = boot_matched_model,

    # Z-score bootstrap SEs
    model5a_z = boot_model5a_z,
    model5a_opt_z = boot_model5a_opt_z,
    model5a_opt_non_mil_z = boot_model5a_opt_non_mil_z,
    model5a_opt_russian_z = boot_model5a_opt_russian_z,

    # Russian Full FE bootstrap
    model5a_opt_rus_full_fe = boot_model5a_opt_rus_full_fe,

    # Topic-specific model5a (optimal BW)
    model5a_opt_pol = boot_model5a_opt_pol,
    model5a_opt_mil = boot_model5a_opt_mil,
    model5a_opt_econ = boot_model5a_opt_econ,
    model5a_opt_cult = boot_model5a_opt_cult,
    model5a_opt_oth = boot_model5a_opt_oth,

    # Topic-specific model5a (full data)
    model5a_full_pol = boot_model5a_full_pol,
    model5a_full_mil = boot_model5a_full_mil,
    model5a_full_econ = boot_model5a_full_econ,
    model5a_full_cult = boot_model5a_full_cult,
    model5a_full_oth = boot_model5a_full_oth,

    # Placebo test
    model_placebo_nonmil = boot_model_placebo_nonmil
  ),

  optimal_bandwidth_align = optimal_bw_align,
  optimal_bw_align_pol = optimal_bw_align_pol,
  optimal_bw_align_mil = optimal_bw_align_mil,
  optimal_bw_align_econ = optimal_bw_align_econ,
  optimal_bw_align_cult = optimal_bw_align_cult,
  optimal_bw_align_oth = optimal_bw_align_oth,
  loo_results = loo_results,
  loo_summary = loo_summary,
  matched_loo_results = matched_loo_results,
  matched_loo_summary = matched_loo_summary,
  model_placebo_nonmil = model_placebo_nonmil,
  optimal_bw_placebo_nonmil = optimal_bw_placebo_nonmil
)

saveRDS(results_het_drop, file.path(DATA_INTERMEDIATE, "06_alignment_results_drop.rds"))
cat("Results saved to:", file.path(DATA_INTERMEDIATE, "06_alignment_results_drop.rds"), "\n")
```

# Session Info

```{r session-info-drop}
print_session_info()
```
