---
title: "06C - Russian Alignment Analysis (Probabilistic Time Assignment) (CSTO vs Neutral)"
author: "Donald Moratz"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

# Overview

This script examines heterogeneous treatment effects by Russian alignment (CSTO vs Neutral) only, using probabilistic time assignment.

**Inputs:**
- `data/intermediate/02_cleaned_data.rds`
- `data/intermediate/02_data_non_ukraine.rds`

**Outputs:**
- Table 3I (Russian Alignment)

```{r setup-prob, include=FALSE}
source("00_setup.R")
knitr::opts_chunk$set(fig.path = paste0(FIGURES_HETEROGENEITY_PROB, "/"))

# Load fwildclusterboot for wild cluster bootstrap
library(fwildclusterboot)

# Helper function for wild cluster bootstrap
run_wild_bootstrap <- function(model, param, clustid = "source_domain", B = 4999) {
  boot_result <- boottest(
    object = model,
    param = param,
    clustid = clustid,
    B = B,
    impose_null = TRUE,
    type = "rademacher"
  )

  list(
    se = boot_result$point_estimate / boot_result$t_stat,
    p_val = boot_result$p_val,
    ci_lower = boot_result$conf_int[1],
    ci_upper = boot_result$conf_int[2],
    t_stat = boot_result$teststat
  )
}
```

# Load Data

```{r load-prob}
data <- readRDS(file.path(DATA_INTERMEDIATE, "02_cleaned_data.rds"))
data_non_ukraine <- readRDS(file.path(DATA_INTERMEDIATE, "02_data_non_ukraine.rds"))

cat("Full data:", nrow(data), "articles\n")
cat("Non-Ukraine data:", nrow(data_non_ukraine), "articles\n")

data <- data %>% mutate(across(c(topic_clean, country, source_domain), as.factor))
data_non_ukraine <- data_non_ukraine %>% mutate(across(c(topic_clean, country, source_domain), as.factor))
```

# Russian Alignment Analysis (CSTO vs Neutral)

## Create Alignment Subsets

```{r alignment-data-prob}
# Filter to non-NATO countries for alignment analysis
data_align <- data %>%
  filter(nato == 0)

# Create alignment indicator
data_align <- data_align %>%
  mutate(align_indicator = factor(case_when(
    indicator == 1 & csto == 1 ~ "Pre. Ind. CSTO",
    indicator == 1 & csto == 0 ~ "Pre. Ind. Neut",
    indicator == 2 & csto == 1 ~ "Pre. State CSTO",
    indicator == 2 & csto == 0 ~ "Pre. State Neut",
    indicator == 3 & csto == 1 ~ "Post Ind. CSTO",
    indicator == 3 & csto == 0 ~ "Post Ind. Neut",
    indicator == 4 & csto == 1 ~ "Post State CSTO",
    indicator == 4 & csto == 0 ~ "Post State Neut"
  ),
  levels = c("Pre. Ind. CSTO", "Pre. Ind. Neut", "Pre. State CSTO",
             "Pre. State Neut", "Post Ind. CSTO", "Post Ind. Neut",
             "Post State CSTO", "Post State Neut")))

cat("Non-NATO countries sample:", nrow(data_align), "articles\n")
cat("CSTO:", sum(data_align$csto), "\n")
cat("Neutral:", sum(data_align$csto == 0), "\n")
```

## Visualization: Independent Media by Alignment

```{r align-ind-plot-prob, fig.width=10, fig.height=7}
agg_data_align_ind <- data_align %>%
  filter(state_owned == 0) %>%
  group_by(running_probabilistic, csto) %>%
  summarize(sentiment_clean = mean(sentiment_clean), num_obs = n(), .groups = "drop")

data_align %>%
  filter(state_owned == 0) %>%
  ggplot(aes(x = running_probabilistic, y = sentiment_clean, group = align_indicator, color = align_indicator)) +
  geom_point(data = agg_data_align_ind,
             aes(x = running_probabilistic, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = COLORS_DISCS, name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on Independent Media Sentiment (Probabilistic)",
    subtitle = "Neutral vs Russia Aligned, Difference in Discontinuities",
    x = "Hours Pre/Post Invasion",
    y = "Sentiment"
  )
```

## Visualization: State Media by Alignment

```{r align-state-plot-prob, fig.width=10, fig.height=7}
agg_data_align_state <- data_align %>%
  filter(state_owned == 1) %>%
  group_by(running_probabilistic, csto) %>%
  summarize(sentiment_clean = mean(sentiment_clean), num_obs = n(), .groups = "drop")

state_align_discs_graph <- data_align %>%
  filter(state_owned == 1) %>%
  ggplot(aes(x = running_probabilistic, y = sentiment_clean, group = align_indicator, color = align_indicator)) +
  geom_point(data = agg_data_align_state,
             aes(x = running_probabilistic, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = COLORS_DISCS, name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on State Media Sentiment (Probabilistic)",
    subtitle = "Neutral vs Russia Aligned, Difference in Discontinuities",
    x = "Hours Pre/Post Invasion",
    y = "Sentiment"
  )

state_align_discs_graph

ggsave(plot = state_align_discs_graph,
       file.path(FIGURES_HETEROGENEITY_PROB, "state_align_discs_prob.png"),
       width = 10, height = 7)
```

## State Media Alignment Regressions

### CSTO Countries Only

```{r align-csto-prob}
data_align_state_csto <- data_align %>%
  filter(state_owned == 1, csto == 1) %>%
  filter(!topic_clean %in% "Military") %>%
  mutate(running_probabilistic = running_probabilistic / 86400)

covs_matrix <- model.matrix(~ source_domain + topic_clean - 1, data = data_align_state_csto)

model5a_csto <- rdrobust(
  y = data_align_state_csto$sentiment_clean,
  x = data_align_state_csto$running_probabilistic,
  covs = covs_matrix,
  cluster = data_align_state_csto$source_domain
)

summary(model5a_csto)
```

### Neutral Countries Only

```{r align-neutral-prob}
data_align_state_neutral <- data_align %>%
  filter(state_owned == 1, csto == 0) %>%
  filter(!topic_clean %in% "Military") %>%
  mutate(running_probabilistic = running_probabilistic / 86400)

covs_matrix <- model.matrix(~ source_domain + topic_clean - 1, data = data_align_state_neutral)

model5a_neutral <- rdrobust(
  y = data_align_state_neutral$sentiment_clean,
  x = data_align_state_neutral$running_probabilistic,
  covs = covs_matrix,
  cluster = data_align_state_neutral$source_domain
)

summary(model5a_neutral)
```

### Diff-in-Disc: CSTO vs Neutral (State Media)

```{r align-diff-prob}
data_align_state <- data_align %>%
  filter(state_owned == 1) %>%
  mutate(source_domain = droplevels(source_domain)) %>%
  mutate(running_probabilistic = running_probabilistic / 86400)

model5a <- feols(sentiment_clean ~ running_probabilistic * treatment * csto,
                 cluster = ~source_domain,
                 data = data_align_state)

summary(model5a)

# Wild cluster bootstrap for model5a
boot_model5a <- run_wild_bootstrap(model5a, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a$se, "\n")
cat("Bootstrap p-value:", boot_model5a$p_val, "\n")
```


## Full Data with Topic FEs

```{r align-full-prob}
model5a_full <- feols(sentiment_clean ~ running_probabilistic * treatment * csto | topic_clean,
                      cluster = ~source_domain,
                      data = data_align_state)

summary(model5a_full)

# Wild cluster bootstrap for model5a_full
boot_model5a_full <- run_wild_bootstrap(model5a_full, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_full$se, "\n")
cat("Bootstrap p-value:", boot_model5a_full$p_val, "\n")
```

## Optimal Bandwidth

```{r align-optimal-prob}
bw_align <- rdbwselect(y = data_align_state$sentiment_clean,
                       x = data_align_state$running_probabilistic,
                       kernel = "triangular",
                       cluster = data_align_state$source_domain,
                       p = 1,
                       bwselect = "mserd")

optimal_bw_align <- bw_align$bws[1, 1]
cat("Optimal bandwidth:", round(optimal_bw_align, 1), "seconds\n")

optimal_bandwidth_data_state <- data_align_state %>%
  filter(running_probabilistic < optimal_bw_align, running_probabilistic > -optimal_bw_align)

model5a_opt <- feols(sentiment_clean ~ running_probabilistic * treatment * csto | topic_clean,
                     cluster = ~source_domain,
                     data = optimal_bandwidth_data_state)

summary(model5a_opt)

# Wild cluster bootstrap for model5a_opt
boot_model5a_opt <- run_wild_bootstrap(model5a_opt, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_opt$se, "\n")
cat("Bootstrap p-value:", boot_model5a_opt$p_val, "\n")
```

## Effect Size

```{r align-effect-prob}
sd_state_owned <- sd(data_align_state$sentiment_clean)
cat("SD of sentiment (state media):", round(sd_state_owned, 3), "\n")

coef_csto_int <- model5a_opt$coeftable["treatment:csto", "Estimate"]
cat("CSTO x Treatment interaction effect (in SD):", round(coef_csto_int / sd_state_owned, 3), "\n")
```

## Non-Military Topics

```{r align-non-mil-prob}
data_align_state_non_mil <- data_align_state %>%
  filter(!topic_clean %in% "Military")

bw_align_non_mil <- rdbwselect(y = data_align_state_non_mil$sentiment_clean,
                               x = data_align_state_non_mil$running_probabilistic,
                               kernel = "triangular",
                               cluster = data_align_state_non_mil$source_domain,
                               p = 1,
                               bwselect = "mserd")

optimal_bw_align_non_mil <- bw_align_non_mil$bws[1, 1]
cat("Optimal bandwidth (non-mil):", round(optimal_bw_align_non_mil, 1), "seconds\n")

optimal_bandwidth_data_state_non_mil <- data_align_state_non_mil %>%
  filter(running_probabilistic < optimal_bw_align_non_mil, running_probabilistic > -optimal_bw_align_non_mil)

model5a_opt_non_mil <- feols(sentiment_clean ~ running_probabilistic * treatment * csto | topic_clean,
                             cluster = ~source_domain,
                             data = optimal_bandwidth_data_state_non_mil)

summary(model5a_opt_non_mil)

# Wild cluster bootstrap for model5a_opt_non_mil
boot_model5a_opt_non_mil <- run_wild_bootstrap(model5a_opt_non_mil, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_opt_non_mil$se, "\n")
cat("Bootstrap p-value:", boot_model5a_opt_non_mil$p_val, "\n")
```

## Leave-One-Out Country Robustness

```{r loo-country-prob}
countries <- unique(data_align_state_non_mil$country)
loo_results <- list()

for (cntry in countries) {
  data_loo <- data_align_state_non_mil %>%
    filter(country != cntry)

  # Re-calculate optimal bandwidth for LOO data
  bw_loo <- rdbwselect(y = data_loo$sentiment_clean,
                       x = data_loo$running_probabilistic,
                       kernel = "triangular",
                       cluster = data_loo$source_domain,
                       p = 1,
                       bwselect = "mserd")

  optimal_bw_loo <- bw_loo$bws[1, 1]

  data_loo_bw <- data_loo %>%
    filter(running_probabilistic < optimal_bw_loo, running_probabilistic > -optimal_bw_loo)

  model_loo <- feols(sentiment_clean ~ running_probabilistic * treatment * csto | topic_clean,
                     cluster = ~source_domain,
                     data = data_loo_bw)

  boot_loo <- tryCatch(
    run_wild_bootstrap(model_loo, "treatment:csto", B = 999),
    error = function(e) list(se = NA, p_val = NA, ci_lower = NA, ci_upper = NA, t_stat = NA)
  )
  loo_results[[cntry]] <- list(
    model = model_loo,
    bandwidth = optimal_bw_loo,
    n = nrow(data_loo_bw),
    country_dropped = cntry,
    boot_p_val = boot_loo$p_val,
    boot_se = boot_loo$se
  )
}

# Extract key coefficient (treatment:csto interaction)
loo_summary <- map_df(names(loo_results), function(cntry) {
  mod <- loo_results[[cntry]]$model
  tibble(
    country_dropped = cntry,
    estimate = coef(mod)["treatment:csto"],
    std_error = se(mod)["treatment:csto"],
    p_value = pvalue(mod)["treatment:csto"],
    n_obs = loo_results[[cntry]]$n,
    bandwidth = loo_results[[cntry]]$bandwidth
  )
})

print(loo_summary)
```

## Placebo Test: December 7th Announcement (Non-Military Topics)

```{r placebo-dec-nonmil-prob}
data_dec_align <- data_align_state_non_mil %>%
  filter(date_publish < "2022-02-19") %>%
  mutate(
    running_probabilistic = as.numeric(difftime(date_publish_probabilistic, as.POSIXct("2021-12-07 00:00:00", tz = "UTC"), units = "secs")),
    treatment = ifelse(date_publish_probabilistic < as.POSIXct("2021-12-07 00:00:00", tz = "UTC"), 0, 1)
  )

# Find optimal bandwidth for placebo
bw_placebo_nonmil <- rdbwselect(y = data_dec_align$sentiment_clean,
                                x = data_dec_align$running_probabilistic,
                                kernel = "triangular",
                                cluster = data_dec_align$source_domain,
                                p = 1,
                                bwselect = "mserd")

optimal_bw_placebo_nonmil <- bw_placebo_nonmil$bws[1, 1]
cat("Placebo optimal bandwidth (non-mil):", round(optimal_bw_placebo_nonmil, 1), "seconds\n")

data_dec_align_bw <- data_dec_align %>%
  filter(running_probabilistic < optimal_bw_placebo_nonmil, running_probabilistic > -optimal_bw_placebo_nonmil)

model_placebo_nonmil <- feols(sentiment_clean ~ running_probabilistic * treatment * csto | topic_clean,
                               cluster = ~source_domain,
                               data = data_dec_align_bw)

summary(model_placebo_nonmil)
boot_model_placebo_nonmil <- run_wild_bootstrap(model_placebo_nonmil, "treatment:csto")
cat("Bootstrap SE for treatment:csto (placebo):", boot_model_placebo_nonmil$se, "\n")
cat("Bootstrap p-value (placebo):", boot_model_placebo_nonmil$p_val, "\n")
cat("\nNote: Non-significant treatment effect suggests parallel trends assumption holds.\n")
```

## Russian-Related Articles Only

```{r align-russian-prob}
data_align_state_russian <- data_align_state %>%
  filter(!topic_clean %in% "Military") %>%
  filter(!Russian.Involvement == "Not")

bw_align_russian <- rdbwselect(y = data_align_state_russian$sentiment_clean,
                               x = data_align_state_russian$running_probabilistic,
                               kernel = "triangular",
                               cluster = data_align_state_russian$source_domain,
                               p = 1,
                               bwselect = "mserd")

optimal_bw_align_russian <- bw_align_russian$bws[1, 1]
cat("Optimal bandwidth (russian):", round(optimal_bw_align_russian, 1), "seconds\n")

optimal_bandwidth_data_state_russian <- data_align_state_russian %>%
  filter(running_probabilistic < optimal_bw_align_russian, running_probabilistic > -optimal_bw_align_russian)

model5a_opt_russian <- feols(sentiment_clean ~ running_probabilistic * treatment * csto | topic_clean,
                             cluster = ~source_domain,
                             data = optimal_bandwidth_data_state_russian)

summary(model5a_opt_russian)

# Wild cluster bootstrap for model5a_opt_russian
boot_model5a_opt_russian <- run_wild_bootstrap(model5a_opt_russian, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_opt_russian$se, "\n")
cat("Bootstrap p-value:", boot_model5a_opt_russian$p_val, "\n")
```

## By-Topic Models: Full Data

```{r topic-full-het-prob}
data_align_state_pol <- data_align_state %>% filter(topic_clean == "Political")
data_align_state_mil <- data_align_state %>% filter(topic_clean == "Military")
data_align_state_econ <- data_align_state %>% filter(topic_clean == "Economic")
data_align_state_cult <- data_align_state %>% filter(topic_clean == "Culture")
data_align_state_oth <- data_align_state %>% filter(topic_clean == "Other")

model5a_full_pol <- feols(sentiment_clean ~ running_probabilistic * treatment * csto,
                          cluster = ~source_domain,
                          data = data_align_state_pol)
model5a_full_mil <- feols(sentiment_clean ~ running_probabilistic * treatment * csto,
                          cluster = ~source_domain,
                          data = data_align_state_mil)
model5a_full_econ <- feols(sentiment_clean ~ running_probabilistic * treatment * csto,
                           cluster = ~source_domain,
                           data = data_align_state_econ)
model5a_full_cult <- feols(sentiment_clean ~ running_probabilistic * treatment * csto,
                           cluster = ~source_domain,
                           data = data_align_state_cult)
model5a_full_oth <- feols(sentiment_clean ~ running_probabilistic * treatment * csto,
                          cluster = ~source_domain,
                          data = data_align_state_oth)

# Wild cluster bootstrap for topic-specific model5a (full data)
boot_model5a_full_pol <- run_wild_bootstrap(model5a_full_pol, "treatment:csto")
boot_model5a_full_mil <- run_wild_bootstrap(model5a_full_mil, "treatment:csto")
boot_model5a_full_econ <- run_wild_bootstrap(model5a_full_econ, "treatment:csto")
boot_model5a_full_cult <- run_wild_bootstrap(model5a_full_cult, "treatment:csto")
boot_model5a_full_oth <- run_wild_bootstrap(model5a_full_oth, "treatment:csto")
```

## By-Topic Models: Per-Topic Optimal Bandwidth

```{r topic-opt-het-prob}
# Political
bw_align_pol <- rdbwselect(y = data_align_state_pol$sentiment_clean, x = data_align_state_pol$running_probabilistic,
                           kernel = "triangular", cluster = data_align_state_pol$source_domain, p = 1, bwselect = "mserd")
optimal_bw_align_pol <- bw_align_pol$bws[1, 1]
cat("Political optimal bandwidth:", round(optimal_bw_align_pol, 1), "seconds\n")
opt_align_pol <- data_align_state_pol %>% filter(running_probabilistic < optimal_bw_align_pol, running_probabilistic > -optimal_bw_align_pol)

# Military
bw_align_mil <- rdbwselect(y = data_align_state_mil$sentiment_clean, x = data_align_state_mil$running_probabilistic,
                           kernel = "triangular", cluster = data_align_state_mil$source_domain, p = 1, bwselect = "mserd")
optimal_bw_align_mil <- bw_align_mil$bws[1, 1]
cat("Military optimal bandwidth:", round(optimal_bw_align_mil, 1), "seconds\n")
opt_align_mil <- data_align_state_mil %>% filter(running_probabilistic < optimal_bw_align_mil, running_probabilistic > -optimal_bw_align_mil)

# Economic
bw_align_econ <- rdbwselect(y = data_align_state_econ$sentiment_clean, x = data_align_state_econ$running_probabilistic,
                            kernel = "triangular", cluster = data_align_state_econ$source_domain, p = 1, bwselect = "mserd")
optimal_bw_align_econ <- bw_align_econ$bws[1, 1]
cat("Economic optimal bandwidth:", round(optimal_bw_align_econ, 1), "seconds\n")
opt_align_econ <- data_align_state_econ %>% filter(running_probabilistic < optimal_bw_align_econ, running_probabilistic > -optimal_bw_align_econ)

# Culture
bw_align_cult <- rdbwselect(y = data_align_state_cult$sentiment_clean, x = data_align_state_cult$running_probabilistic,
                            kernel = "triangular", cluster = data_align_state_cult$source_domain, p = 1, bwselect = "mserd")
optimal_bw_align_cult <- bw_align_cult$bws[1, 1]
cat("Culture optimal bandwidth:", round(optimal_bw_align_cult, 1), "seconds\n")
opt_align_cult <- data_align_state_cult %>% filter(running_probabilistic < optimal_bw_align_cult, running_probabilistic > -optimal_bw_align_cult)

# Other
bw_align_oth <- rdbwselect(y = data_align_state_oth$sentiment_clean, x = data_align_state_oth$running_probabilistic,
                           kernel = "triangular", cluster = data_align_state_oth$source_domain, p = 1, bwselect = "mserd")
optimal_bw_align_oth <- bw_align_oth$bws[1, 1]
cat("Other optimal bandwidth:", round(optimal_bw_align_oth, 1), "seconds\n")
opt_align_oth <- data_align_state_oth %>% filter(running_probabilistic < optimal_bw_align_oth, running_probabilistic > -optimal_bw_align_oth)

model5a_opt_pol <- feols(sentiment_clean ~ running_probabilistic * treatment * csto,
                         cluster = ~source_domain,
                         data = opt_align_pol)
model5a_opt_mil <- feols(sentiment_clean ~ running_probabilistic * treatment * csto,
                         cluster = ~source_domain,
                         data = opt_align_mil)
model5a_opt_econ <- feols(sentiment_clean ~ running_probabilistic * treatment * csto,
                          cluster = ~source_domain,
                          data = opt_align_econ)
model5a_opt_cult <- feols(sentiment_clean ~ running_probabilistic * treatment * csto,
                          cluster = ~source_domain,
                          data = opt_align_cult)
model5a_opt_oth <- feols(sentiment_clean ~ running_probabilistic * treatment * csto,
                         cluster = ~source_domain,
                         data = opt_align_oth)

# Wild cluster bootstrap for topic-specific model5a (optimal BW)
boot_model5a_opt_pol <- run_wild_bootstrap(model5a_opt_pol, "treatment:csto")
boot_model5a_opt_mil <- run_wild_bootstrap(model5a_opt_mil, "treatment:csto")
boot_model5a_opt_econ <- run_wild_bootstrap(model5a_opt_econ, "treatment:csto")
boot_model5a_opt_cult <- run_wild_bootstrap(model5a_opt_cult, "treatment:csto")
boot_model5a_opt_oth <- run_wild_bootstrap(model5a_opt_oth, "treatment:csto")
```

# Country-Level Analysis

## State Media by Country and Alliance

```{r country-facet-prob, fig.width=12, fig.height=8}
# Create alliance for faceting
data_long <- data %>%
  pivot_longer(cols = c(nato, csto, neutral),
               names_to = "alliance",
               values_to = "membership") %>%
  filter(membership == 1) %>%
  mutate(
    alliance = factor(alliance, levels = c("nato", "csto", "neutral")),
    state_indicator = factor(paste(country, treatment, sep = ", "))
  )

data_long %>%
  filter(state_owned == 1) %>%
  ggplot(aes(x = running_probabilistic, y = sentiment_clean, group = state_indicator, color = country)) +
  geom_smooth(method = "lm", se = FALSE) +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  facet_wrap(~alliance, nrow = 2) +
  labs(
    title = "Effect of Invasion on State Media Sentiment by Country (Probabilistic)",
    subtitle = "Faceted by Alliance",
    x = "Hours Pre/Post Invasion",
    y = "Sentiment"
  )
```

# Summary Table (Table 3I)

```{r table3i-prob}
note_text <- "All standard errors are clustered at the source level. Model 1 uses no fixed effects. Model 2 uses full data with topic fixed effects. Model 3 uses the optimal bandwidth with topic fixed effects. Model 4 omits military-related articles and uses a re-optimized bandwidth. Model 5 uses only Russian-related (non-military) articles with a re-optimized bandwidth."
note_wrapped <- str_wrap(note_text, width = 80)

table_3i <- modelsummary(
  list("(1)" = model5a, "(2)" = model5a_full, "(3)" = model5a_opt,
       "(4)" = model5a_opt_non_mil, "(5)" = model5a_opt_russian),
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors",
  title = "Russian Alignment: Difference in Discontinuity Analysis (Probabilistic Time Assignment)",
  notes = note_wrapped
)

table_3i
```

## Summary Table: By Topic (Optimal Bandwidth)

```{r table3i-topic-opt-prob}
note_topic_opt <- "All standard errors are clustered at the source level. Each model uses a per-topic re-optimized bandwidth. State media in non-NATO countries only."
note_topic_opt_wrapped <- str_wrap(note_topic_opt, width = 80)

table_3i_topic_opt <- modelsummary(
  list("Political" = model5a_opt_pol, "Military" = model5a_opt_mil,
       "Economic" = model5a_opt_econ, "Cultural" = model5a_opt_cult, "Other" = model5a_opt_oth),
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors",
  title = "Russian Alignment By Topic (Per-Topic Optimal Bandwidth, Probabilistic Time Assignment)",
  notes = note_topic_opt_wrapped
)

table_3i_topic_opt
```

## Summary Table: By Topic (Full Data)

```{r table3i-topic-full-prob}
note_topic_full <- "All standard errors are clustered at the source level. Each model uses the full dataset (no bandwidth restriction). State media in non-NATO countries only."
note_topic_full_wrapped <- str_wrap(note_topic_full, width = 80)

table_3i_topic_full <- modelsummary(
  list("Political" = model5a_full_pol, "Military" = model5a_full_mil,
       "Economic" = model5a_full_econ, "Cultural" = model5a_full_cult, "Other" = model5a_full_oth),
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors",
  title = "Russian Alignment By Topic (Full Data, Probabilistic Time Assignment)",
  notes = note_topic_full_wrapped
)

table_3i_topic_full
```

# Save Results

```{r save-prob}
results_het_prob <- list(
  model5a = model5a,
  model5a_full = model5a_full,
  model5a_opt = model5a_opt,
  model5a_opt_non_mil = model5a_opt_non_mil,
  model5a_opt_russian = model5a_opt_russian,
  model5a_csto = model5a_csto,
  model5a_neutral = model5a_neutral,
  model5a_opt_pol = model5a_opt_pol,
  model5a_opt_mil = model5a_opt_mil,
  model5a_opt_econ = model5a_opt_econ,
  model5a_opt_cult = model5a_opt_cult,
  model5a_opt_oth = model5a_opt_oth,
  model5a_full_pol = model5a_full_pol,
  model5a_full_mil = model5a_full_mil,
  model5a_full_econ = model5a_full_econ,
  model5a_full_cult = model5a_full_cult,
  model5a_full_oth = model5a_full_oth,

  # Bootstrap standard errors
  bootstrap_se = list(
    # Main model5a variants
    model5a = boot_model5a,
    model5a_full = boot_model5a_full,
    model5a_opt = boot_model5a_opt,
    model5a_opt_non_mil = boot_model5a_opt_non_mil,
    model5a_opt_russian = boot_model5a_opt_russian,

    # Topic-specific model5a (optimal BW)
    model5a_opt_pol = boot_model5a_opt_pol,
    model5a_opt_mil = boot_model5a_opt_mil,
    model5a_opt_econ = boot_model5a_opt_econ,
    model5a_opt_cult = boot_model5a_opt_cult,
    model5a_opt_oth = boot_model5a_opt_oth,

    # Topic-specific model5a (full data)
    model5a_full_pol = boot_model5a_full_pol,
    model5a_full_mil = boot_model5a_full_mil,
    model5a_full_econ = boot_model5a_full_econ,
    model5a_full_cult = boot_model5a_full_cult,
    model5a_full_oth = boot_model5a_full_oth,

    # Placebo test
    model_placebo_nonmil = boot_model_placebo_nonmil
  ),

  optimal_bandwidth_align = optimal_bw_align,
  optimal_bw_align_pol = optimal_bw_align_pol,
  optimal_bw_align_mil = optimal_bw_align_mil,
  optimal_bw_align_econ = optimal_bw_align_econ,
  optimal_bw_align_cult = optimal_bw_align_cult,
  optimal_bw_align_oth = optimal_bw_align_oth,
  loo_results = loo_results,
  loo_summary = loo_summary,
  model_placebo_nonmil = model_placebo_nonmil,
  optimal_bw_placebo_nonmil = optimal_bw_placebo_nonmil
)

saveRDS(results_het_prob, file.path(DATA_INTERMEDIATE, "06_alignment_results_prob.rds"))
cat("Results saved to:", file.path(DATA_INTERMEDIATE, "06_alignment_results_prob.rds"), "\n")
```

# Session Info

```{r session-info-prob}
print_session_info()
```
