---
title: "06d - Russian Alignment Analysis (Drop No-Time Articles) (CSTO vs Neutral)"
author: "Donald Moratz"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

# Overview

This script examines heterogeneous treatment effects by Russian alignment (CSTO vs Neutral) only, using time as a continuous running variable, after dropping articles without exact publication times.

**Inputs:**
- `data/intermediate/02_cleaned_data.rds`
- `data/intermediate/02_data_non_ukraine.rds`

**Outputs:**
- Table 3F (Russian Alignment)

```{r setup-drop, include=FALSE}
source("00_setup.R")
knitr::opts_chunk$set(fig.path = paste0(FIGURES_HETEROGENEITY_DROP, "/"))
options(digits = 10)

set.seed(3184)
```

# Load Data

```{r load-drop}
data <- readRDS(file.path(DATA_INTERMEDIATE, "02_cleaned_data.rds"))
data_non_ukraine <- readRDS(file.path(DATA_INTERMEDIATE, "02_data_non_ukraine.rds"))

data <- data %>% filter(has_time == TRUE)
data_non_ukraine <- data_non_ukraine %>% filter(has_time == TRUE)

cat("Full data after dropping no-time articles:", nrow(data), "articles\n")
cat("Non-Ukraine data after dropping:", nrow(data_non_ukraine), "articles\n")

data <- data %>% mutate(across(c(topic_clean, country, source_domain), as.factor))
data_non_ukraine <- data_non_ukraine %>% mutate(across(c(topic_clean, country, source_domain), as.factor))
```

# Russian Alignment Analysis (CSTO vs Neutral)

## Create Alignment Subsets

```{r alignment-data-drop}
# Filter to non-NATO countries for alignment analysis
data_align <- data %>%
  filter(nato == 0)%>%
  drop_na()

# Create alignment indicator
data_align <- data_align %>%
  mutate(align_indicator = factor(case_when(
    indicator == 1 & csto == 1 ~ "Pre. Ind. CSTO",
    indicator == 1 & csto == 0 ~ "Pre. Ind. Neut",
    indicator == 2 & csto == 1 ~ "Pre. State CSTO",
    indicator == 2 & csto == 0 ~ "Pre. State Neut",
    indicator == 3 & csto == 1 ~ "Post Ind. CSTO",
    indicator == 3 & csto == 0 ~ "Post Ind. Neut",
    indicator == 4 & csto == 1 ~ "Post State CSTO",
    indicator == 4 & csto == 0 ~ "Post State Neut"
  ),
  levels = c("Pre. Ind. CSTO", "Pre. Ind. Neut", "Pre. State CSTO",
             "Pre. State Neut", "Post Ind. CSTO", "Post Ind. Neut",
             "Post State CSTO", "Post State Neut")))

cat("Non-NATO countries sample:", nrow(data_align), "articles\n")
cat("CSTO:", sum(data_align$csto), "\n")
cat("Neutral:", sum(data_align$csto == 0), "\n")
```

## Visualization: Independent Media by Alignment

```{r align-ind-plot-drop, fig.width=10, fig.height=7}
agg_data_align_ind <- data_align %>%
  filter(state_owned == 0) %>%
  group_by(running_continuous, csto) %>%
  summarize(sentiment_clean = mean(sentiment_clean), num_obs = n(), .groups = "drop")

data_align %>%
  filter(state_owned == 0) %>%
  ggplot(aes(x = running_continuous, y = sentiment_clean, group = align_indicator, color = align_indicator)) +
  geom_point(data = agg_data_align_ind,
             aes(x = running_continuous, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = COLORS_DISCS, name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on Independent Media Sentiment (Drop No-Time)",
    subtitle = "Neutral vs Russia Aligned, Difference in Discontinuities",
    x = "Hours Pre/Post Invasion",
    y = "Sentiment"
  )
```

## Visualization: State Media by Alignment

```{r align-state-plot-drop, fig.width=10, fig.height=7}
agg_data_align_state <- data_align %>%
  filter(state_owned == 1) %>%
  group_by(running_continuous, csto) %>%
  summarize(sentiment_clean = mean(sentiment_clean), num_obs = n(), .groups = "drop")

state_align_discs_graph <- data_align %>%
  filter(state_owned == 1) %>%
  ggplot(aes(x = running_continuous, y = sentiment_clean, group = align_indicator, color = align_indicator)) +
  geom_point(data = agg_data_align_state,
             aes(x = running_continuous, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = COLORS_DISCS, name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on State Media Sentiment (Drop No-Time)",
    subtitle = "Neutral vs Russia Aligned, Difference in Discontinuities",
    x = "Hours Pre/Post Invasion",
    y = "Sentiment"
  )

state_align_discs_graph

ggsave(plot = state_align_discs_graph,
       file.path(FIGURES_HETEROGENEITY_DROP, "state_align_discs_drop.png"),
       width = 10, height = 7)
```

## Pre-Trend Diagnostic: State Media in Russia-Aligned Countries

Addresses the concern that sentiment toward Russia may have turned negative *before* the
Feb 24, 2022 invasion (during the troop buildup) in state-owned media of Russia-aligned
countries. We plot the daily mean sentiment for state-owned sources in each aligned country
(Armenia, Azerbaijan, Belarus, Kazakhstan), mark both the Dec 7, 2021 US public-warning
date and the Feb 24, 2022 invasion cutoff, and overlay a linear fit on the pre-invasion
window only so any pre-existing slide is visible.

```{r pretrend-by-country-aligned-drop, fig.width=10, fig.height=7}
# Buildup display window (trim to keep the pre-invasion period readable)
PRETREND_START <- as.Date("2021-06-01")
PRETREND_END   <- as.Date("2022-06-01")
INVASION_DATE  <- as.Date("2022-02-24")
WARNING_DATE   <- as.Date("2021-12-07")

# State-owned media in the Russia-aligned (CSTO) group; Ukraine already excluded (NATO)
data_pretrend <- data %>%
  filter(country %in% CSTO_COUNTRIES, state_owned == 1,
         date_publish >= PRETREND_START, date_publish <= PRETREND_END) %>%
  mutate(country = droplevels(country))

# Daily mean sentiment per country (same outcome + daily aggregation as other figures)
agg_pretrend <- data_pretrend %>%
  group_by(country, date_publish) %>%
  summarize(sentiment_clean = mean(sentiment_clean, na.rm = TRUE),
            num_obs = n(), .groups = "drop")

# Pre-invasion daily means only (the linear fit is restricted to this window)
agg_pretrend_pre <- agg_pretrend %>%
  filter(date_publish < INVASION_DATE)

pretrend_by_country_aligned_graph <- ggplot(agg_pretrend,
                                             aes(x = date_publish, y = sentiment_clean)) +
  geom_point(aes(size = num_obs), alpha = 0.2, inherit.aes = TRUE) +
  geom_smooth(data = agg_pretrend_pre, method = "lm", se = TRUE, color = "red4") +
  geom_vline(xintercept = INVASION_DATE, linetype = "dashed", alpha = 0.7) +
  geom_vline(xintercept = WARNING_DATE, linetype = "dotted", color = "grey30") +
  scale_size(name = "Observations") +
  facet_wrap(~ country, scales = "free_y") +
  theme_classic() +
  labs(
    title = "Pre-Invasion Sentiment Trend in State Media (Drop No-Time)",
    subtitle = "Russia-aligned countries; dotted = Dec 7 warning, dashed = Feb 24 invasion",
    x = "Publication date",
    y = "Mean sentiment toward Russia"
  )

pretrend_by_country_aligned_graph

ggsave(plot = pretrend_by_country_aligned_graph,
       file.path(FIGURES_HETEROGENEITY_DROP, "pretrend_by_country_aligned.png"),
       width = 10, height = 7)
```

```{r pretrend-slopes-aligned-drop}
# Per-country pre-invasion linear slope (fit on the plotted daily means).
# Slope is in sentiment units per day; also reported per 30 days for readability.
pretrend_slopes <- agg_pretrend_pre %>%
  group_by(country) %>%
  group_modify(~ {
    fit <- lm(sentiment_clean ~ as.numeric(date_publish), data = .x)
    ct <- summary(fit)$coefficients["as.numeric(date_publish)", ]
    tibble(
      n_days       = nrow(.x),
      slope_day    = ct["Estimate"],
      slope_30day  = ct["Estimate"] * 30,
      std_error    = ct["Std. Error"],
      p_value      = ct["Pr(>|t|)"]
    )
  }) %>%
  ungroup()

cat("=== Task A: Pre-invasion sentiment slope in state media, by aligned country ===\n")
cat("(slope in sentiment units per day; slope_30day = per 30 days)\n\n")
print(as.data.frame(pretrend_slopes), row.names = FALSE, digits = 4)
```

Replica of the figure above with a later start date (Dec 1, 2021) to confirm the
pre-invasion trend lines are not an artifact of fitting across a long (nine-month) window.
INVASION_DATE and WARNING_DATE are reused from the chunk above.

```{r pretrend-by-country-aligned-dec-drop, fig.width=10, fig.height=7}
# Shorter buildup display window (later start; same invasion / warning markers)
PRETREND_START_DEC <- as.Date("2021-12-01")

data_pretrend_dec <- data %>%
  filter(country %in% CSTO_COUNTRIES, state_owned == 1,
         date_publish >= PRETREND_START_DEC, date_publish <= PRETREND_END) %>%
  mutate(country = droplevels(country))

agg_pretrend_dec <- data_pretrend_dec %>%
  group_by(country, date_publish) %>%
  summarize(sentiment_clean = mean(sentiment_clean, na.rm = TRUE),
            num_obs = n(), .groups = "drop")

# Pre-invasion daily means only (linear fit restricted to this window)
agg_pretrend_dec_pre <- agg_pretrend_dec %>%
  filter(date_publish < INVASION_DATE)

pretrend_by_country_aligned_dec_graph <- ggplot(agg_pretrend_dec,
                                                 aes(x = date_publish, y = sentiment_clean)) +
  geom_point(aes(size = num_obs), alpha = 0.2, inherit.aes = TRUE) +
  geom_smooth(data = agg_pretrend_dec_pre, method = "lm", se = TRUE, color = "red4") +
  geom_vline(xintercept = INVASION_DATE, linetype = "dashed", alpha = 0.7) +
  geom_vline(xintercept = WARNING_DATE, linetype = "dotted", color = "grey30") +
  scale_size(name = "Observations") +
  facet_wrap(~ country, scales = "free_y") +
  theme_classic() +
  labs(
    title = "Pre-Invasion Sentiment Trend in State Media, Dec 1 Start (Drop No-Time)",
    subtitle = "Russia-aligned countries; dotted = Dec 7 warning, dashed = Feb 24 invasion",
    x = "Publication date",
    y = "Mean sentiment toward Russia"
  )

pretrend_by_country_aligned_dec_graph

ggsave(plot = pretrend_by_country_aligned_dec_graph,
       file.path(FIGURES_HETEROGENEITY_DROP, "pretrend_by_country_aligned_dec.png"),
       width = 10, height = 7)
```

## State Media Alignment Regressions

### CSTO Countries Only

```{r align-csto-drop}
# Filter to CSTO data, non military
data_align_state_csto <- data_align %>%
  filter(state_owned == 1, csto == 1) %>%
  filter(!topic_clean %in% "Military") %>%
  mutate(running_continuous = running_continuous / 86400.0)

covs_matrix <- model.matrix(~ source_domain + topic_clean - 1, data = data_align_state_csto)

model5a_csto <- rdrobust(
  y = data_align_state_csto$sentiment_clean,
  x = data_align_state_csto$running_continuous,
  covs = covs_matrix,
  cluster = data_align_state_csto$source_domain
)

summary(model5a_csto)
```

```{r align-csto-z-drop}
# Applying a Z-Score Transformation
data_align_state_csto <- data_align_state_csto %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                   sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()

covs_matrix <- model.matrix(~ topic_clean - 1, data = data_align_state_csto)

model5a_csto_z <- rdrobust(
  y = data_align_state_csto$sentiment_z,
  x = data_align_state_csto$running_continuous,
  covs = covs_matrix,
  cluster = data_align_state_csto$source_domain
)

summary(model5a_csto_z)
```


### Neutral Countries Only

```{r align-neutral-drop}
# Filter data to neutral countries only
data_align_state_neutral <- data_align %>%
  filter(state_owned == 1, csto == 0) %>%
  filter(!topic_clean %in% "Military") %>%
  mutate(running_continuous = running_continuous / 86400)

covs_matrix <- model.matrix(~ source_domain + topic_clean - 1, data = data_align_state_neutral)

model5a_neutral <- rdrobust(
  y = data_align_state_neutral$sentiment_clean,
  x = data_align_state_neutral$running_continuous,
  covs = covs_matrix,
  cluster = data_align_state_neutral$source_domain
)

summary(model5a_neutral)
```

```{r align-neutral-z-drop}
# Applying a Z-Score Transformation
data_align_state_neutral <- data_align_state_neutral %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                   sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()

covs_matrix <- model.matrix(~ topic_clean - 1, data = data_align_state_neutral)

model5a_neutral_z <- rdrobust(
  y = data_align_state_neutral$sentiment_z,
  x = data_align_state_neutral$running_continuous,
  covs = covs_matrix,
  cluster = data_align_state_neutral$source_domain
)

summary(model5a_neutral_z)
```

# Diff-in-Disc Analysis

## Full Data

### Full Data, Topic FEs
Diff-in-Disc: CSTO vs Neutral (State Media)

```{r align-diff-drop}
data_align_state <- data_align %>%
  filter(state_owned == 1) %>%
  mutate(source_domain = droplevels(source_domain)) %>%
  mutate(running_continuous = running_continuous / 86400)

model5a <- feols(sentiment_clean ~ running_continuous * treatment * csto | topic_clean,
                 cluster = ~source_domain,
                 data = data_align_state)

summary(model5a)

# Wild cluster bootstrap for model5a
boot_model5a <- run_wild_bootstrap(model5a, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a$se, "\n")
cat("Bootstrap p-value:", boot_model5a$p_val, "\n")
```


### Full Data with FEs

```{r align-full-drop}

model5a_full <- feols(sentiment_clean ~ running_continuous *
                        treatment * csto
                        | topic_clean + source_domain,
                      cluster = ~source_domain,
                      data = data_align_state)

summary(model5a_full)

# Wild cluster bootstrap for model5a_full
boot_model5a_full <- run_wild_bootstrap(model5a_full, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_full$se, "\n")
cat("Bootstrap p-value:", boot_model5a_full$p_val, "\n")
```

### Sentiment Z

```{r align-diff-z-drop}
data_align_state <- data_align_state %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                   sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()

model5a_z <- feols(sentiment_z ~ running_continuous * treatment * csto | topic_clean,
                 cluster = ~source_domain,
                 data = data_align_state)

summary(model5a_z)

# Wild cluster bootstrap for model5a
boot_model5a_z <- run_wild_bootstrap(model5a_z, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_z$se, "\n")
cat("Bootstrap p-value:", boot_model5a_z$p_val, "\n")
```


## Optimal Bandwidth

### Optimal Bandwidth, Topic FEs

```{r align-optimal-drop}
# Residualize the dependent variable for fixed effects to do bandwidth selection
resid_y <- feols(sentiment_clean ~ 1 | topic_clean + source_domain + csto,
                 data = data_align_state)$residuals

bw_align <- rdbwselect(y = resid_y,
                       x = data_align_state$running_continuous,
                       kernel = "triangular",
                       cluster = data_align_state$source_domain,
                       p = 1,
                       bwselect = "mserd")

optimal_bw_align <- bw_align$bws[1, 1]
cat("Optimal bandwidth:", round(optimal_bw_align, 1), "days\n")

optimal_bandwidth_data_state <- data_align_state %>%
  filter(running_continuous < optimal_bw_align, running_continuous > -optimal_bw_align)

model5a_opt <- feols(sentiment_clean ~ running_continuous * treatment * csto | topic_clean,
                     cluster = ~source_domain,
                     data = optimal_bandwidth_data_state)

summary(model5a_opt)

# Wild cluster bootstrap for model5a_opt
boot_model5a_opt <- run_wild_bootstrap(model5a_opt, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_opt$se, "\n")
cat("Bootstrap p-value:", boot_model5a_opt$p_val, "\n")
```


### Optimal Bandwidth Full FE

```{r align-optimal-full-fe-drop}

model5a_opt_full_fe <- feols(sentiment_clean ~ running_continuous
                                     * treatment * csto
                                       | topic_clean + source_domain,
                                     cluster = ~source_domain,
                                     data = optimal_bandwidth_data_state
                                     )

summary(model5a_opt_full_fe)

# Wild cluster bootstrap for model5a_opt
boot_model5a_opt_full_fe <- run_wild_bootstrap(model5a_opt_full_fe, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_opt_full_fe$se, "\n")
cat("Bootstrap p-value:", boot_model5a_opt_full_fe$p_val, "\n")
```

### Optimal Bandwidth Sentiment Z

```{r align-optimal-z-drop}
# Residualize the dependent variable for fixed effects to do bandwidth selection
resid_y <- feols(sentiment_z ~ 1 | topic_clean + csto,
                 data = data_align_state)$residuals

bw_align <- rdbwselect(y = resid_y,
                       x = data_align_state$running_continuous,
                       kernel = "triangular",
                       cluster = data_align_state$source_domain,
                       p = 1,
                       bwselect = "mserd")

optimal_bw_align <- bw_align$bws[1, 1]
cat("Optimal bandwidth:", round(optimal_bw_align, 1), "days\n")

optimal_bandwidth_data_state <- data_align_state %>%
  filter(running_continuous < optimal_bw_align, running_continuous > -optimal_bw_align)

model5a_opt_z <- feols(sentiment_z ~ running_continuous * treatment * csto | topic_clean,
                     cluster = ~source_domain,
                     data = optimal_bandwidth_data_state)

summary(model5a_opt_z)

# Wild cluster bootstrap for model5a_opt
boot_model5a_opt_z <- run_wild_bootstrap(model5a_opt_z, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_opt_z$se, "\n")
cat("Bootstrap p-value:", boot_model5a_opt_z$p_val, "\n")
```

## Non-Military

### Non-Military Topics

```{r align-non-mil-drop}
data_align_state_non_mil <- data_align_state %>%
  filter(!topic_clean %in% "Military")

# Residualize the dependent variable for fixed effects to do bandwidth selection
resid_y <- feols(sentiment_clean ~ 1 | topic_clean + source_domain + csto,
                 data = data_align_state_non_mil)$residuals

bw_align_non_mil <- rdbwselect(y = resid_y,
                               x = data_align_state_non_mil$running_continuous,
                               kernel = "triangular",
                               cluster = data_align_state_non_mil$source_domain,
                               p = 1,
                               bwselect = "mserd")

optimal_bw_align_non_mil <- bw_align_non_mil$bws[1, 1]
cat("Optimal bandwidth (non-mil):", round(optimal_bw_align_non_mil, 1), "days\n")

optimal_bandwidth_data_state_non_mil <- data_align_state_non_mil %>%
  filter(running_continuous < optimal_bw_align_non_mil, running_continuous > -optimal_bw_align_non_mil)

model5a_opt_non_mil <- feols(sentiment_clean ~ running_continuous
                             * treatment * csto | topic_clean,
                             cluster = ~source_domain,
                             data = optimal_bandwidth_data_state_non_mil)

summary(model5a_opt_non_mil)

# Wild cluster bootstrap for model5a_opt_non_mil
boot_model5a_opt_non_mil <- run_wild_bootstrap(model5a_opt_non_mil, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_opt_non_mil$se, "\n")
cat("Bootstrap p-value:", boot_model5a_opt_non_mil$p_val, "\n")
```

### Non-Military Topics, Full FE

```{r align-non-mil-full-fe-drop}

model5a_opt_non_mil_full_fe <- feols(sentiment_clean ~ running_continuous
                                     * treatment * csto
                                       | topic_clean + source_domain,
                                     cluster = ~source_domain,
                                     data = optimal_bandwidth_data_state_non_mil
                                     )

summary(model5a_opt_non_mil_full_fe)

# Wild cluster bootstrap for model5a_opt_non_mil
boot_model5a_opt_non_mil_full_fe <- run_wild_bootstrap(model5a_opt_non_mil_full_fe, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_opt_non_mil_full_fe$se, "\n")
cat("Bootstrap p-value:", boot_model5a_opt_non_mil_full_fe$p_val, "\n")
```

### Effect Size

```{r align-effect-drop}
sd_state_owned <- sd(data_align_state$sentiment_clean)
cat("SD of sentiment (state media):", round(sd_state_owned, 3), "\n")

coef_csto_int <- model5a_opt_non_mil_full_fe$coeftable["treatment:csto", "Estimate"]
cat("CSTO x Treatment interaction effect (in SD):", round(coef_csto_int / sd_state_owned, 3), "\n")
```



### Non-Military, Sentiment Z

```{r align-non-mil-z-drop}
# Create New z score
data_align_state_non_mil <- data_align_state_non_mil %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                   sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()


# Residualize the dependent variable for fixed effects to do bandwidth selection
resid_y <- feols(sentiment_z ~ 1 | topic_clean + csto,
                 data = data_align_state_non_mil)$residuals

bw_align_non_mil <- rdbwselect(y = resid_y,
                               x = data_align_state_non_mil$running_continuous,
                               kernel = "triangular",
                               cluster = data_align_state_non_mil$source_domain,
                               p = 1,
                               bwselect = "mserd")

optimal_bw_align_non_mil <- bw_align_non_mil$bws[1, 1]
cat("Optimal bandwidth (non-mil):", round(optimal_bw_align_non_mil, 1), "days\n")

optimal_bandwidth_data_state_non_mil <- data_align_state_non_mil %>%
  filter(running_continuous < optimal_bw_align_non_mil, running_continuous > -optimal_bw_align_non_mil)

model5a_opt_non_mil_z <- feols(sentiment_z ~ running_continuous
                             * treatment * csto | topic_clean,
                             cluster = ~source_domain,
                             data = optimal_bandwidth_data_state_non_mil)

summary(model5a_opt_non_mil_z)

# Wild cluster bootstrap for model5a_opt_non_mil
boot_model5a_opt_non_mil_z <- run_wild_bootstrap(model5a_opt_non_mil_z, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_opt_non_mil_z$se, "\n")
cat("Bootstrap p-value:", boot_model5a_opt_non_mil_z$p_val, "\n")
```


```{r ggridges-viz-drop}

# Prepare the data for plotting
plot_data <- optimal_bandwidth_data_state_non_mil %>%
  group_by(source_domain) %>%
  mutate(
    # Recalculate Local Z-score
    sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                   sd(sentiment_clean, na.rm = TRUE)
  ) %>%
  ungroup() %>%
  select(source_domain, sentiment_clean, sentiment_z) %>%
  pivot_longer(cols = c(sentiment_clean, sentiment_z),
               names_to = "Type", values_to = "Value")

# Plotting the comparison
ggplot(plot_data, aes(x = Value, y = source_domain, fill = Type)) +
  geom_density_ridges(alpha = 0.5, scale = 0.9) +
  facet_wrap(~Type, scales = "free_x") +
  theme_minimal() +
  labs(title = "Ternary Sentiment vs. Z-Scored Sentiment by Source",
       subtitle = "Local Z-scoring centers each source and adjusts for their specific volatility",
       x = "Sentiment Value",
       y = "Media Outlet") +
  scale_fill_manual(values = c("sentiment_clean" = "#69b3a2", "sentiment_z" = "#404080"))

ggsave(plot = last_plot(),
       file.path(FIGURES_HETEROGENEITY_DROP, "sentiment_zscore_comparison_drop.png"),
       width = 10, height = 7)
```


## Russian Only

### Russian-Related Articles Only

```{r align-russian-drop}
data_align_state_russian <- data_align_state %>%
  filter(!topic_clean %in% "Military") %>%
  filter(!Russian.Involvement == "Not")

# Residualize the dependent variable for fixed effects to do bandwidth selection
resid_y <- feols(sentiment_clean ~ 1 | topic_clean + source_domain + csto,
                 data = data_align_state_russian)$residuals

bw_align_russian <- rdbwselect(y = resid_y,
                               x = data_align_state_russian$running_continuous,
                               kernel = "triangular",
                               cluster = data_align_state_russian$source_domain,
                               p = 1,
                               bwselect = "mserd")

optimal_bw_align_russian <- bw_align_russian$bws[1, 1]
cat("Optimal bandwidth (russian):", round(optimal_bw_align_russian, 1), "days\n")

optimal_bandwidth_data_state_russian <- data_align_state_russian %>%
  filter(running_continuous < optimal_bw_align_russian, running_continuous > -optimal_bw_align_russian)

model5a_opt_russian <- feols(sentiment_clean ~ running_continuous *
                               treatment * csto | topic_clean,
                             cluster = ~source_domain,
                             data = optimal_bandwidth_data_state_russian)

summary(model5a_opt_russian)

# Wild cluster bootstrap for model5a_opt_russian
boot_model5a_opt_russian <- run_wild_bootstrap(model5a_opt_russian, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_opt_russian$se, "\n")
cat("Bootstrap p-value:", boot_model5a_opt_russian$p_val, "\n")
```

### Russia Only, Full FE

```{r align-russian-full-fe-drop}

model5a_opt_rus_full_fe <- feols(sentiment_clean ~ running_continuous
                                    * treatment * csto
                                       | topic_clean + source_domain,
                                     cluster = ~source_domain,
                                     data = optimal_bandwidth_data_state_russian
                                     )

summary(model5a_opt_rus_full_fe)

# Wild cluster bootstrap for model5a_opt_non_mil
boot_model5a_opt_rus_full_fe <- run_wild_bootstrap(model5a_opt_rus_full_fe, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_opt_rus_full_fe$se, "\n")
cat("Bootstrap p-value:", boot_model5a_opt_rus_full_fe$p_val, "\n")
```


### Russia Only, Sentiment Z

```{r align-russian-z-drop}
# Create New z score
data_align_state_russian <- data_align_state_russian %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                   sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()


# Residualize the dependent variable for fixed effects to do bandwidth selection
resid_y <- feols(sentiment_z ~ 1 | topic_clean + csto,
                 data = data_align_state_russian)$residuals

bw_align_russian <- rdbwselect(y = resid_y,
                               x = data_align_state_russian$running_continuous,
                               kernel = "triangular",
                               cluster = data_align_state_russian$source_domain,
                               p = 1,
                               bwselect = "mserd")

optimal_bw_align_russian <- bw_align_russian$bws[1, 1]
cat("Optimal bandwidth (non-mil):", round(optimal_bw_align_russian, 1), "days\n")

optimal_bandwidth_data_state_russian <- data_align_state_russian %>%
  filter(running_continuous < optimal_bw_align_russian, running_continuous > -optimal_bw_align_russian)

model5a_opt_russian_z <- feols(sentiment_z ~ running_continuous
                             * treatment * csto | topic_clean,
                             cluster = ~source_domain,
                             data = optimal_bandwidth_data_state_russian)

summary(model5a_opt_russian_z)

# Wild cluster bootstrap for model5a_opt_non_mil
boot_model5a_opt_russian_z <- run_wild_bootstrap(model5a_opt_russian_z, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_opt_russian_z$se, "\n")
cat("Bootstrap p-value:", boot_model5a_opt_russian_z$p_val, "\n")
```

# By Topic

## By-Topic Models: Full Data

```{r topic-full-het-drop}
data_align_state_pol <- data_align_state %>% filter(topic_clean == "Political")
data_align_state_mil <- data_align_state %>% filter(topic_clean == "Military")
data_align_state_econ <- data_align_state %>% filter(topic_clean == "Economic")
data_align_state_cult <- data_align_state %>% filter(topic_clean == "Culture")
data_align_state_oth <- data_align_state %>% filter(topic_clean == "Other")

model5a_full_pol <- feols(sentiment_z ~ running_continuous * treatment * csto,
                          cluster = ~source_domain,
                          data = data_align_state_pol)
model5a_full_mil <- feols(sentiment_z ~ running_continuous * treatment * csto,
                          cluster = ~source_domain,
                          data = data_align_state_mil)
model5a_full_econ <- feols(sentiment_z ~ running_continuous * treatment * csto,
                           cluster = ~source_domain,
                           data = data_align_state_econ)
model5a_full_cult <- feols(sentiment_z ~ running_continuous * treatment * csto,
                           cluster = ~source_domain,
                           data = data_align_state_cult)
model5a_full_oth <- feols(sentiment_z ~ running_continuous * treatment * csto,
                          cluster = ~source_domain,
                          data = data_align_state_oth)

# Wild cluster bootstrap for topic-specific model5a (full data)
boot_model5a_full_pol <- run_wild_bootstrap(model5a_full_pol, "treatment:csto")
boot_model5a_full_mil <- run_wild_bootstrap(model5a_full_mil, "treatment:csto")
boot_model5a_full_econ <- run_wild_bootstrap(model5a_full_econ, "treatment:csto")
boot_model5a_full_cult <- run_wild_bootstrap(model5a_full_cult, "treatment:csto")
boot_model5a_full_oth <- run_wild_bootstrap(model5a_full_oth, "treatment:csto")
```

## By-Topic Models: Per-Topic Optimal Bandwidth

```{r topic-opt-het-drop}
# Political
bw_align_pol <- rdbwselect(y = data_align_state_pol$sentiment_z,
                           x = data_align_state_pol$running_continuous,
                           kernel = "triangular",
                           cluster = data_align_state_pol$source_domain,
                           p = 1,
                           bwselect = "mserd")

optimal_bw_align_pol <- bw_align_pol$bws[1, 1]

cat("Political optimal bandwidth:", round(optimal_bw_align_pol, 1), "days\n")

opt_align_pol <- data_align_state_pol %>% filter(running_continuous < optimal_bw_align_pol,
                                                 running_continuous > -optimal_bw_align_pol)

# Military
bw_align_mil <- rdbwselect(y = data_align_state_mil$sentiment_z,
                           x = data_align_state_mil$running_continuous,
                           kernel = "triangular",
                           cluster = data_align_state_mil$source_domain,
                           p = 1,
                           bwselect = "mserd")

optimal_bw_align_mil <- bw_align_mil$bws[1, 1]

cat("Military optimal bandwidth:", round(optimal_bw_align_mil, 1), "days\n")

opt_align_mil <- data_align_state_mil %>% filter(running_continuous < optimal_bw_align_mil,
                                                 running_continuous > -optimal_bw_align_mil)

# Economic
bw_align_econ <- rdbwselect(y = data_align_state_econ$sentiment_z,
                            x = data_align_state_econ$running_continuous,
                            kernel = "triangular",
                            cluster = data_align_state_econ$source_domain,
                            p = 1,
                            bwselect = "mserd")

optimal_bw_align_econ <- bw_align_econ$bws[1, 1]

cat("Economic optimal bandwidth:", round(optimal_bw_align_econ, 1), "days\n")

opt_align_econ <- data_align_state_econ %>% filter(running_continuous < optimal_bw_align_econ,
                                                   running_continuous > -optimal_bw_align_econ)

# Culture
bw_align_cult <- rdbwselect(y = data_align_state_cult$sentiment_z,
                            x = data_align_state_cult$running_continuous,
                            kernel = "triangular",
                            cluster = data_align_state_cult$source_domain,
                            p = 1,
                            bwselect = "mserd")

optimal_bw_align_cult <- bw_align_cult$bws[1, 1]

cat("Culture optimal bandwidth:", round(optimal_bw_align_cult, 1), "days\n")

opt_align_cult <- data_align_state_cult %>% filter(running_continuous < optimal_bw_align_cult,
                                                   running_continuous > -optimal_bw_align_cult)

# Other
bw_align_oth <- rdbwselect(y = data_align_state_oth$sentiment_z,
                           x = data_align_state_oth$running_continuous,
                           kernel = "triangular",
                           cluster = data_align_state_oth$source_domain,
                           p = 1,
                           bwselect = "mserd")

optimal_bw_align_oth <- bw_align_oth$bws[1, 1]

cat("Other optimal bandwidth:", round(optimal_bw_align_oth, 1), "days\n")

opt_align_oth <- data_align_state_oth %>% filter(running_continuous < optimal_bw_align_oth,
                                                 running_continuous > -optimal_bw_align_oth)

# Models
model5a_opt_pol <- feols(sentiment_z ~ running_continuous * treatment * csto,
                         cluster = ~source_domain,
                         data = opt_align_pol)
model5a_opt_mil <- feols(sentiment_z ~ running_continuous * treatment * csto,
                         cluster = ~source_domain,
                         data = opt_align_mil)
model5a_opt_econ <- feols(sentiment_z ~ running_continuous * treatment * csto,
                          cluster = ~source_domain,
                          data = opt_align_econ)
model5a_opt_cult <- feols(sentiment_z ~ running_continuous * treatment * csto,
                          cluster = ~source_domain,
                          data = opt_align_cult)
model5a_opt_oth <- feols(sentiment_z ~ running_continuous * treatment * csto,
                         cluster = ~source_domain,
                         data = opt_align_oth)

# Wild cluster bootstrap for topic-specific model5a (optimal BW)
boot_model5a_opt_pol <- run_wild_bootstrap(model5a_opt_pol, "treatment:csto")
boot_model5a_opt_mil <- run_wild_bootstrap(model5a_opt_mil, "treatment:csto")
boot_model5a_opt_econ <- run_wild_bootstrap(model5a_opt_econ, "treatment:csto")
boot_model5a_opt_cult <- run_wild_bootstrap(model5a_opt_cult, "treatment:csto")
boot_model5a_opt_oth <- run_wild_bootstrap(model5a_opt_oth, "treatment:csto")
```

# Robustness

## Leave-One-Out Country Robustness

```{r loo-country-drop}
countries <- unique(data_align_state_non_mil$country)
loo_results <- list()

for (cntry in countries) {
  data_loo <- data_align_state_non_mil %>%
    filter(country != cntry)

  # Re-calculate optimal bandwidth for LOO data
  resid_y <- feols(sentiment_z ~ 1 | topic_clean + csto,
                 data = data_loo)$residuals

  bw_loo <- rdbwselect(y = data_loo$sentiment_z,
                       x = data_loo$running_continuous,
                       kernel = "triangular",
                       cluster = data_loo$source_domain,
                       p = 1,
                       bwselect = "mserd")

  optimal_bw_loo <- bw_loo$bws[1, 1]

  data_loo_bw <- data_loo %>%
    filter(running_continuous < optimal_bw_loo, running_continuous > -optimal_bw_loo)

  model_loo <- feols(sentiment_z ~ running_continuous * treatment * csto | topic_clean,
                     cluster = ~source_domain,
                     data = data_loo_bw)

  boot_loo <- tryCatch(
    run_wild_bootstrap(model_loo, "treatment:csto", B = 4999),
    error = function(e) list(se = NA, p_val = NA, ci_lower = NA, ci_upper = NA, t_stat = NA)
  )
  loo_results[[cntry]] <- list(
    model = model_loo,
    bandwidth = optimal_bw_loo,
    n = nrow(data_loo_bw),
    country_dropped = cntry,
    boot_p_val = boot_loo$p_val,
    boot_se = boot_loo$se
  )
}

# Extract key coefficient (treatment:csto interaction)
loo_summary <- map_df(names(loo_results), function(cntry) {
  mod <- loo_results[[cntry]]$model
  tibble(
    country_dropped = cntry,
    estimate = coef(mod)["treatment:csto"],
    std_error = se(mod)["treatment:csto"],
    p_value = pvalue(mod)["treatment:csto"],
    n_obs = loo_results[[cntry]]$n,
    bandwidth = loo_results[[cntry]]$bandwidth
  )
})

print(loo_summary)
```

## Placebo Test: December 7th Announcement (Non-Military Topics)

```{r placebo-dec-nonmil-drop}
data_dec_align <- data_align_state_non_mil %>%
  filter(date_publish < "2022-02-19") %>%
  mutate(
    running_continuous = as.numeric(difftime(date_publish_continuous, as.POSIXct("2021-12-07 00:00:00", tz = "UTC"), units = "secs")),
    treatment = ifelse(date_publish_continuous < as.POSIXct("2021-12-07 00:00:00", tz = "UTC"), 0, 1)
  )

# Find optimal bandwidth for placebo
bw_placebo_nonmil <- rdbwselect(y = data_dec_align$sentiment_z,
                                x = data_dec_align$running_continuous,
                                kernel = "triangular",
                                cluster = data_dec_align$source_domain,
                                p = 1,
                                bwselect = "mserd")

optimal_bw_placebo_nonmil <- bw_placebo_nonmil$bws[1, 1]
cat("Placebo optimal bandwidth (non-mil):", round(optimal_bw_placebo_nonmil, 1), "seconds\n")

data_dec_align_bw <- data_dec_align %>%
  filter(running_continuous < optimal_bw_placebo_nonmil, running_continuous > -optimal_bw_placebo_nonmil)

model_placebo_nonmil <- feols(sentiment_z ~ running_continuous * treatment * csto | topic_clean,
                               cluster = ~source_domain,
                               data = data_dec_align_bw)

summary(model_placebo_nonmil)
boot_model_placebo_nonmil <- run_wild_bootstrap(model_placebo_nonmil, "treatment:csto")
cat("Bootstrap SE for treatment:csto (placebo):", boot_model_placebo_nonmil$se, "\n")
cat("Bootstrap p-value (placebo):", boot_model_placebo_nonmil$p_val, "\n")
cat("\nNote: Non-significant treatment effect suggests parallel trends assumption holds.\n")
```

## Placebo Test: December 7th Announcement (Aligned State Media, by Country)

Directly addresses the reviewer concern: a placebo-cutoff RDD restricted to state-owned
media in the Russia-aligned (CSTO) group, estimated **separately for each country**
(Armenia, Azerbaijan, Belarus, Kazakhstan) so cross-country consistency is visible. Each
model uses the z-scored outcome used throughout the CSTO state-media RDDs and rdrobust's
MSE-optimal bandwidth. Because each country has only 2-3 state-owned sources — too few for
cluster-robust inference — standard errors use rdrobust's default (nearest-neighbor
heteroskedasticity-robust) variance rather than clustering by source. A non-significant
discontinuity at the Dec 7, 2021 warning date indicates that sentiment was not already
jumping during the buildup.

```{r placebo-dec-aligned-drop}
# Cutoff constant for the Dec 7, 2021 US public-warning date
DEC7_CUTOFF <- as.POSIXct("2021-12-07 00:00:00", tz = "UTC")

# One placebo RDD per aligned country: state-owned, non-military, pre-invasion.
placebo_aligned_models <- list()

for (cntry in CSTO_COUNTRIES) {
  dat_c <- data_align %>%
    filter(state_owned == 1, country == cntry,
           !topic_clean %in% "Military",
           date_publish < "2022-02-19") %>%
    mutate(
      topic_clean = droplevels(topic_clean),   # drop empty topic levels within this country
      running_continuous = as.numeric(difftime(
        date_publish_continuous, DEC7_CUTOFF, units = "secs")) / 86400,
      treatment = ifelse(date_publish_continuous < DEC7_CUTOFF, 0, 1)
    ) %>%
    # Source-level z-score adjustment (as in the CSTO state-media RDDs)
    group_by(source_domain) %>%
    mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                          sd(sentiment_clean, na.rm = TRUE)) %>%
    ungroup() %>%
    filter(is.finite(sentiment_z))              # drop degenerate single-article sources

  covs_c <- model.matrix(~ topic_clean - 1, data = dat_c)

  # rdrobust default HC (nn) SEs; no clustering (only 2-3 sources per country)
  placebo_aligned_models[[cntry]] <- rdrobust(
    y = dat_c$sentiment_z,
    x = dat_c$running_continuous,
    covs = covs_c
  )

  m <- placebo_aligned_models[[cntry]]
  cat("\n--- ", cntry, " ---\n", sep = "")
  cat("Estimate:  ", round(m$coef[1], 3), "\n")
  cat("95% CI:    [", round(m$ci[1, 1], 3), ",", round(m$ci[1, 2], 3), "]\n")
  cat("p-value:   ", round(m$pv[1], 3), "\n")
  cat("Bandwidth: ", round(m$bws[1, 1], 3), "days\n")
  cat("N (within bw):", m$N_h[1] + m$N_h[2], "\n")
  cat("Sources:", paste(sort(unique(dat_c$source_domain)), collapse = ", "), "\n")
}

cat("\nNote: Non-significant discontinuities suggest no pre-invasion jump at the warning date.\n")
```

## Matching

### Initial Match

```{r matching-analysis-drop}
# Subset to data of interest

matching_data <- optimal_bandwidth_data_state_non_mil %>%
  select(sentiment_z, running, running_continuous, treatment, csto,
         topic_clean, source_domain, country)

# Match on topic and publication day (using integer day from running_continuous)
matching_data <- matching_data %>%
  mutate(running_day = floor(running_continuous / 86400))

ps_model <- matchit(
  csto ~ running_day + topic_clean,
  data = matching_data,
  method = "exact",
  ratio = 1,
)

summary(ps_model)
```

### Assess Balance

```{r matching-balance-drop}
# Numerical balance check (better)
bal.tab(ps_model, un = TRUE, stats = c("m", "v"), thresholds = c(m = 0.1))
# Want: all standardized mean differences < 0.1 after matching

# Love plot (publication quality)
love <- love.plot(ps_model, binary = "std", thresholds = c(m = 0.1))
love
ggsave(plot = love,
       file.path(FIGURES_HETEROGENEITY_DROP, "love_plot_drop.png"),
       width = 10, height = 7)
```

### Matching analysis

```{r matching-model-drop}
# Extract matched data and calculate treatment effects
matched_data <- match.data(ps_model)

matched_model <- feols(sentiment_z ~ running_continuous
                                     * treatment * csto |
                                       topic_clean,
                                     cluster = ~source_domain,
                                     data = matched_data
                                     )

summary(matched_model)


# Wild cluster bootstrap for matched model
boot_matched_model <- run_wild_bootstrap(matched_model, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_matched_model$se, "\n")
cat("Bootstrap p-value:", boot_matched_model$p_val, "\n")
```



### Sensitivity of OVB

```{r sensitivity-ovb-drop}
# Save the bootstrapped p-val
bootstrapped_se <- boot_matched_model$p_val

# Respecify the model using lm
lm_model <- lm(sentiment_z ~ running_continuous * treatment * csto +
                 factor(topic_clean),
               data = matched_data)


# Sensitivity analysis
sensitivity <- sensemakr(
  model = lm_model,
  treatment = "treatment:csto",
  benchmark_covariates = c("running_continuous:treatment"),
  kd = 1,
  ky = 1,
  reduce = TRUE
)

summary(sensitivity)
```


```{r sensitivity-partialr2-drop}
partial_r2(lm_model, covariates = c("running_continuous:treatment",
                                     "running_continuous:csto",
                                     "treatment",
                                     "csto"))

treatment_r2 <- partial_r2(lm_model, covariates = c("treatment"))
```


```{r sensitivity-plot-drop}
# Manually recompute the CI bound using the bootstrapped SE
coef_interest <- coef(lm_model)["treatment:csto"]
rv_ci <- coef_interest / bootstrapped_se  # your corrected t-stat for reference

plot(sensitivity,
     xlab = "Partial R² of confounder with CSTO membership",
     ylab = "Partial R² of confounder with sentiment",
     main = "Sensitivity to Unobserved Confounding",
     lim.x = .1,
     lim.y = .1,
     col.contour = "grey60",
     label.text = FALSE)   # turn off the ugly overlapping label first
text(x = 0.01, y = 0.00005,
     labels = "running:treatment",
     cex = 0.8, pos = 4)
```


```{r sensitivity-contour-drop}
# Sensitivity Plot

# Extract the data sensemakr uses for the plot
ovb_contour_data <- function(sensitivity, lim = 0.005) {

  # Grid of r2dz.x and r2yz.dx values
  r2dz <- seq(0, lim, length.out = 400)
  r2yz <- seq(0, lim, length.out = 400)
  grid <- expand.grid(r2dz.x = r2dz, r2yz.dx = r2yz)

  # Extract key stats
  estimate <- sensitivity$sensitivity_stats$estimate
  se <- sensitivity$sensitivity_stats$se
  df <- sensitivity$sensitivity_stats$dof

  # Compute adjusted estimate across grid
  grid$adjusted <- mapply(function(r2dz, r2yz) {
    sensemakr::adjusted_estimate(
      estimate = estimate,
      se = se,
      dof = df,
      r2dz.x = r2dz,
      r2yz.dx = r2yz
    )
  }, grid$r2dz.x, grid$r2yz.dx)

  return(grid)
}

# Extract benchmark points
benchmark_df <- data.frame(
  r2dz.x = sensitivity$bounds$r2dz.x,
  r2yz.dx = sensitivity$bounds$r2yz.dx,
  label = sensitivity$bounds$bound_label
)

# Build contour data
# Rebuild with wider x limit
contour_data <- ovb_contour_data(sensitivity, lim = 0.1)

ggplot(contour_data, aes(x = r2dz.x, y = r2yz.dx, z = adjusted)) +
  geom_contour(colour = "grey60",
               breaks = c(-0.1, -0.05, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3)) +
  geom_contour(breaks = 0,
               colour = "red",
               linetype = "dashed",
               linewidth = 0.8) +
  geom_point(data = benchmark_df,
             aes(x = r2dz.x, y = r2yz.dx),
             shape = 18, colour = "red", size = 3,
             inherit.aes = FALSE) +
  annotate("point", x = 0, y = 0, shape = 17, size = 3) +
  annotate("text", x = 0.002, y = 0.003,
           label = "Unadjusted\n(-0.146)",
           size = 5, hjust = 0) +
  annotate("text", x = 0.047, y = 0.003,
           label = "running:treatment",
           size = 5, hjust = 0) +
  coord_cartesian(xlim = c(0, 0.1), ylim = c(0, 0.1)) +
  scale_x_continuous(breaks = seq(0, 0.1, by = 0.02),
                     labels = scales::number_format(accuracy = 0.01)) +
  scale_y_continuous(breaks = seq(0, 0.1, by = 0.02),
                     labels = scales::number_format(accuracy = 0.01)) +
  labs(
    x = "Partial R² of confounder with CSTO membership",
    y = "Partial R² of confounder with sentiment",
    title = "Sensitivity to Unobserved Confounding, CSTO Affiliation",
    subtitle = "Red dashed line indicates where estimate = 0"
  ) +
  theme_bw() +
  theme(
    panel.grid.minor = element_blank(),
    plot.title = element_text(face = "bold"),
    legend.position = "none"
  )

ggsave(plot = last_plot(),
       file.path(FIGURES_HETEROGENEITY_DROP, "sensitivity_ovb_csto_drop.png"),
       width = 10, height = 7)
```


## Leave One Out Matching

```{r loo-matching-drop}
countries <- unique(data_align_state_non_mil$country)
matched_loo_results <- list()

for (cntry in countries) {
  data_loo <- data_align_state_non_mil %>%
    filter(country != cntry)

  # Re-calculate optimal bandwidth for LOO data
  resid_y <- feols(sentiment_z ~ 1 | topic_clean + csto,
                 data = data_loo)$residuals

  bw_loo <- rdbwselect(y = data_loo$sentiment_z,
                       x = data_loo$running_continuous,
                       kernel = "triangular",
                       cluster = data_loo$source_domain,
                       p = 1,
                       bwselect = "mserd")

  optimal_bw_loo <- bw_loo$bws[1, 1]

  data_loo_bw <- data_loo %>%
    filter(running_continuous < optimal_bw_loo, running_continuous > -optimal_bw_loo)

  data_loo_bw <- data_loo_bw %>%
    mutate(running_day = floor(running_continuous / 86400))

  ps_model <- matchit(
    csto ~ running_day + topic_clean,
    data = data_loo_bw,
    method = "exact",
    ratio = 1,
  )

  matched_data_loo <- match.data(ps_model)

  matched_model_loo <- feols(sentiment_z ~ running_continuous
                                     * treatment * csto |
                                       topic_clean,
                                     cluster = ~source_domain,
                                     data = matched_data_loo
                                     )

  matched_boot_loo <- tryCatch(
    run_wild_bootstrap(matched_model_loo, "treatment:csto", B = 4999),
    error = function(e) list(se = NA, p_val = NA, ci_lower = NA, ci_upper = NA, t_stat = NA)
  )
  matched_loo_results[[cntry]] <- list(
    model = matched_model_loo,
    bandwidth = optimal_bw_loo,
    n = nrow(matched_data_loo),
    country_dropped = cntry,
    boot_p_val = matched_boot_loo$p_val,
    boot_se = matched_boot_loo$se
  )
}

# Extract key coefficient (treatment:csto interaction)
matched_loo_summary <- map_df(names(matched_loo_results), function(cntry) {
  mod <- matched_loo_results[[cntry]]$model
  tibble(
    country_dropped = cntry,
    estimate = coef(mod)["treatment:csto"],
    std_error = se(mod)["treatment:csto"],
    p_value = pvalue(mod)["treatment:csto"],
    n_obs = matched_loo_results[[cntry]]$n,
    bandwidth = matched_loo_results[[cntry]]$bandwidth
  )
})

print(matched_loo_summary)
```


## Pooled Fully Saturated Regression

```{r}
library(data.table)

# ---- 0. DATA PREP -----------------------------------------------------------
 
dt <- as.data.table(optimal_bandwidth_data_state_non_mil)
 
# Ensure key variables are the right type
invisible(dt[, treatment_num  := as.numeric(treatment)])
invisible(dt[, running_num    := as.numeric(running_continuous)])
invisible(dt[, treat_x_run    := treatment_num * running_num])
 
# Create a clean source×topic cell identifier
invisible(dt[, cell := paste(source_domain, topic_clean, sep = " :: ")])
invisible(dt[, cell := factor(cell)])
 
# Cell-level metadata: N, source, csto flag
cell_info <- dt[, .(
  N             = .N,
  source_domain = source_domain[1],
  csto          = csto[1],
  n_treated     = sum(treatment_num),
  n_control     = sum(1 - treatment_num)
), by = cell]
 
cat("=== Cell structure ===\n")
print(cell_info[order(-N)])
cat("\nTotal cells:", nrow(cell_info), "\n")
cat("CSTO cells:", sum(cell_info$csto == 1),
    "  |  Non-CSTO cells:", sum(cell_info$csto == 0), "\n\n")
 
# Flag cells that can't identify a treatment effect (need obs on both sides)
cell_info[, estimable := (n_treated >= 2 & n_control >= 2)]
cat("Estimable cells:", sum(cell_info$estimable), "/", nrow(cell_info), "\n")
cat("Dropped cells (insufficient variation):\n")
if (any(!cell_info$estimable)) {
  print(cell_info[estimable == FALSE])
} else {
  cat("  (none)\n")
}
 
# Restrict data to estimable cells
estimable_cells <- cell_info[estimable == TRUE, cell]
dt_est <- dt[cell %in% estimable_cells]
invisible(dt_est[, cell := droplevels(cell)])
 
# Update cell_info to estimable only
cell_info_est <- cell_info[estimable == TRUE]
```


```{r}
# ---- 1. FULLY SATURATED MODEL -----------------------------------------------
# Formula: each cell gets its own intercept, running slope, treatment effect,
#          and treatment×running interaction.
#
# sentiment = Σ_c [ α_c + β_c·running + τ_c·treatment + γ_c·treatment·running ]
#
# The τ_c coefficients are the cell-specific RDD treatment effects at the cutoff.
 
model_saturated <- feols(
  sentiment_z ~ cell + cell:running_num + cell:treatment_num + cell:treat_x_run - 1,
  vcov = "hetero",
  data   = dt_est
)
 
cat("\n=== Model summary (first 20 coefficients) ===\n")
print(summary(model_saturated), n = 20)
```


```{r}
# ---- 2. EXTRACT CELL-SPECIFIC TREATMENT EFFECTS (τ_c) -----------------------
 
all_coefs <- coef(model_saturated)
V_full    <- vcov(model_saturated)
 
# Identify the treatment coefficients: named "cell<level>:treatment_num"
treat_names <- grep(":treatment_num$", names(all_coefs), value = TRUE)
 
theta   <- all_coefs[treat_names]
V_theta <- V_full[treat_names, treat_names]
 
# Map coefficient names back to cell labels
coef_cells <- sub(":treatment_num$", "", treat_names)
coef_cells <- sub("^cell", "", coef_cells)
 
# Match to metadata
match_idx      <- match(coef_cells, as.character(cell_info_est$cell))
matched_info   <- cell_info_est[match_idx]
 
# Sanity check: did all coefficients match?
stopifnot(!any(is.na(match_idx)))
 
cat("\n=== Cell-specific treatment effects (τ_c) ===\n")
cell_results <- data.table(
  cell   = coef_cells,
  source = matched_info$source_domain,
  csto   = matched_info$csto,
  N      = matched_info$N,
  theta  = as.numeric(theta),
  se     = sqrt(diag(V_theta))
)
cell_results[, `:=`(t_stat = theta / se, p_val = 2 * pnorm(-abs(theta / se)))]
print(cell_results[order(csto, source, cell)])
```


```{r}
# ---- 3. BUILD WEIGHT VECTORS (R MATRIX) & WALD TESTS ------------------------
# Weight = N_c / Σ N_c within the CSTO group
# The weighted average τ_group = w' θ  is a linear combination of coefficients.
# Var(τ_group) = w' V_θ w   (using clustered VCV)
# Wald stat = τ_group² / Var(τ_group) ~ χ²(1)
 
N_vec <- matched_info$N
csto_flag <- matched_info$csto
 
# --- 3a. CSTO group ---
csto_mask <- (csto_flag == 1)
w_csto    <- ifelse(csto_mask, N_vec / sum(N_vec[csto_mask]), 0)
 
theta_csto <- as.numeric(crossprod(w_csto, theta))
var_csto   <- as.numeric(t(w_csto) %*% V_theta %*% w_csto)
se_csto    <- sqrt(var_csto)
 
# --- 3b. Non-CSTO group ---
non_mask    <- (csto_flag == 0)
w_non       <- ifelse(non_mask, N_vec / sum(N_vec[non_mask]), 0)
 
theta_non <- as.numeric(crossprod(w_non, theta))
var_non   <- as.numeric(t(w_non) %*% V_theta %*% w_non)
se_non    <- sqrt(var_non)
 
# --- 3c. Difference (CSTO minus Non-CSTO) ---
w_diff     <- w_csto - w_non
theta_diff <- as.numeric(crossprod(w_diff, theta))
var_diff   <- as.numeric(t(w_diff) %*% V_theta %*% w_diff)
se_diff    <- sqrt(var_diff)
 
# --- Wald statistics and p-values ---
wald_results <- data.table(
  group     = c("CSTO", "Non-CSTO", "Difference (CSTO - Non)"),
  estimate  = c(theta_csto, theta_non, theta_diff),
  se        = c(se_csto, se_non, se_diff),
  z_stat    = c(theta_csto / se_csto, theta_non / se_non, theta_diff / se_diff),
  p_value   = c(
    2 * pnorm(-abs(theta_csto / se_csto)),
    2 * pnorm(-abs(theta_non / se_non)),
    2 * pnorm(-abs(theta_diff / se_diff))
  ),
  N_total   = c(sum(N_vec[csto_mask]), sum(N_vec[non_mask]),
                sum(N_vec[csto_mask]) + sum(N_vec[non_mask])),
  n_cells   = c(sum(csto_mask), sum(non_mask), sum(csto_mask) + sum(non_mask))
)
 
cat("\n")
cat("=====================================================================\n")
cat("  WALD TEST RESULTS: N-Weighted Treatment Effects by CSTO Group\n")
cat("=====================================================================\n")
print(wald_results, digits = 4)
cat("=====================================================================\n")
cat("Notes:\n")
cat("  - HC-robust SEs (cells nest within clusters, so cell estimates\n")
cat("    are independent and cluster-robust SEs are unnecessary)\n")
cat("  - Weights proportional to N within each CSTO group\n")
cat("  - Treatment effect = RDD estimate at the cutoff (running = 0)\n")
cat("=====================================================================\n\n")
```


```{r}
# ---- 4. DIAGNOSTICS ---------------------------------------------------------
 
# Show the weight each cell contributes
cat("=== Cell weights within CSTO groups ===\n")
weight_table <- data.table(
  cell   = coef_cells,
  source = matched_info$source_domain,
  csto   = matched_info$csto,
  N      = N_vec,
  weight = ifelse(csto_flag == 1, w_csto, w_non)
)
print(weight_table[order(csto, -weight)])
 
# Check: weights sum to 1 within each group
cat("\nWeight sums (should be 1.0 each):\n")
cat("  CSTO:    ", sum(w_csto), "\n")
cat("  Non-CSTO:", sum(w_non), "\n")
```


## Mini-Regressions Approach

```{r}
# ---- 2A. MINI-REGRESSIONS WITHIN EACH SOURCE × TOPIC CELL -------------------
# Estimate: sentiment ~ running + treatment + treatment×running
# within each source_domain × topic_clean cell.
# τ_c = coefficient on `treatment` = RDD effect at cutoff.
 
cat("=== APPROACH 2: Mini-Regressions ===\n\n")
 
cells_to_estimate <- cell_info_est[estimable == TRUE]
 
mini_results <- rbindlist(lapply(seq_len(nrow(cells_to_estimate)), function(i) {
  cc <- cells_to_estimate$cell[i]
  d  <- dt_est[cell == cc]
 
  m <- tryCatch(
    lm(sentiment_z ~ running_num + treatment_num + treat_x_run, data = d),
    error = function(e) NULL
  )
 
  if (is.null(m)) {
    return(data.table(
      cell = as.character(cc), source = cells_to_estimate$source_domain[i],
      topic = NA_character_, csto = cells_to_estimate$csto[i],
      N = nrow(d), theta = NA_real_, se = NA_real_,
      converged = FALSE
    ))
  }
 
  # Extract treatment coefficient
  cf <- summary(m)$coefficients
  if (!"treatment_num" %in% rownames(cf)) {
    return(data.table(
      cell = as.character(cc), source = cells_to_estimate$source_domain[i],
      topic = NA_character_, csto = cells_to_estimate$csto[i],
      N = nrow(d), theta = NA_real_, se = NA_real_,
      converged = FALSE
    ))
  }
 
  data.table(
    cell   = as.character(cc),
    source = cells_to_estimate$source_domain[i],
    topic  = sub("^.* :: ", "", as.character(cc)),
    csto   = cells_to_estimate$csto[i],
    N      = nrow(d),
    theta  = cf["treatment_num", "Estimate"],
    se     = cf["treatment_num", "Std. Error"],
    converged = TRUE
  )
}))
 
mini_results <- mini_results[converged == TRUE & !is.na(theta)]
 
cat("Mini-regression results (cell-level):\n")
print(mini_results[order(csto, source, topic)], digits = 4)
```


```{r}
# ---- 2B. VERIFY: POINT ESTIMATES MATCH APPROACH 1 ---------------------------
 
cat("\n=== VERIFICATION: Approach 1 vs Approach 2 point estimates ===\n")
 
# N-weighted average within CSTO groups
verify <- mini_results[, .(
  theta_mini = weighted.mean(theta, N),
  N_total    = sum(N),
  n_cells    = .N
), by = csto]
 
cat("\nApproach 2 (mini-regressions):\n")
print(verify, digits = 6)
 
cat("\nApproach 1 (pooled saturated):\n")
cat("  CSTO:     ", round(theta_csto, 6), "\n")
cat("  Non-CSTO: ", round(theta_non, 6), "\n")
 
cat("\nDifference (should be ~0 or very small):\n")
cat("  CSTO:     ", round(verify[csto == 1, theta_mini] - theta_csto, 8), "\n")
cat("  Non-CSTO: ", round(verify[csto == 0, theta_mini] - theta_non, 8), "\n\n")
```


```{r}
# ---- 2C. SOURCE-LEVEL PAIRS BOOTSTRAP ---------------------------------------
# For each bootstrap iteration:
#   1. Resample 13 sources with replacement from the full set of 13
#   2. Carry along ALL their topic-level estimates and Ns
#   3. Classify drawn sources by their csto flag
#   4. Compute N-weighted average within CSTO / Non-CSTO groups
#   5. Store CSTO effect, Non-CSTO effect, and difference
 
run_source_pairs_bootstrap <- function(mini_results, B = 9999) {
 
  sources <- unique(mini_results$source)
  n_sources <- length(sources)
 
  source_data <- lapply(sources, function(s) {
    mini_results[source == s, .(topic, csto, N, theta)]
  })
  names(source_data) <- sources
 
  theta_boot_csto <- numeric(B)
  theta_boot_non  <- numeric(B)
  theta_boot_diff <- numeric(B)
  n_valid <- 0
 
  for (b in seq_len(B)) {
    drawn_idx <- sample(n_sources, n_sources, replace = TRUE)
    drawn_sources <- sources[drawn_idx]
    boot_data <- rbindlist(source_data[drawn_sources])
 
    csto_rows <- boot_data[csto == 1]
    non_rows  <- boot_data[csto == 0]
 
    if (nrow(csto_rows) == 0 || nrow(non_rows) == 0) next
 
    n_valid <- n_valid + 1
    theta_boot_csto[n_valid] <- weighted.mean(csto_rows$theta, csto_rows$N)
    theta_boot_non[n_valid]  <- weighted.mean(non_rows$theta, non_rows$N)
    theta_boot_diff[n_valid] <- theta_boot_csto[n_valid] - theta_boot_non[n_valid]
  }
 
  theta_boot_csto <- theta_boot_csto[seq_len(n_valid)]
  theta_boot_non  <- theta_boot_non[seq_len(n_valid)]
  theta_boot_diff <- theta_boot_diff[seq_len(n_valid)]
 
  cat("  Valid bootstrap samples:", n_valid, "/", B, "\n")
 
  orig_csto <- weighted.mean(mini_results[csto == 1, theta], mini_results[csto == 1, N])
  orig_non  <- weighted.mean(mini_results[csto == 0, theta], mini_results[csto == 0, N])
  orig_diff <- orig_csto - orig_non
 
  list(
    results = data.table(
      group     = c("CSTO", "Non-CSTO", "Difference"),
      estimate  = c(orig_csto, orig_non, orig_diff),
      se_boot   = c(sd(theta_boot_csto), sd(theta_boot_non), sd(theta_boot_diff)),
      p_boot    = c(
        2 * min(mean(theta_boot_csto >= 0), mean(theta_boot_csto <= 0)),
        2 * min(mean(theta_boot_non  >= 0), mean(theta_boot_non  <= 0)),
        2 * min(mean(theta_boot_diff >= 0), mean(theta_boot_diff <= 0))
      ),
      ci_lower  = c(quantile(theta_boot_csto, 0.025), quantile(theta_boot_non, 0.025), quantile(theta_boot_diff, 0.025)),
      ci_upper  = c(quantile(theta_boot_csto, 0.975), quantile(theta_boot_non, 0.975), quantile(theta_boot_diff, 0.975))
    ),
    boot_dist = list(csto = theta_boot_csto, non = theta_boot_non, diff = theta_boot_diff)
  )
}
 
 
# ---- 2D. BAYESIAN BOOTSTRAP (Rubin 1981) ------------------------------------
# For each bootstrap iteration:
#   1. Draw Dirichlet(1,1,...,1) weights for all 13 sources
#   2. Every source always contributes — no source is ever dropped
#   3. Effective weight for each topic = dirichlet_weight_source × N_topic
#   4. Compute weighted average within CSTO / Non-CSTO groups
#   5. Store CSTO effect, Non-CSTO effect, and difference
 
run_bayesian_bootstrap <- function(mini_results, B = 9999) {
 
  # Source-level structure
  sources   <- unique(mini_results$source)
  n_sources <- length(sources)
 
  # Map each source to an index, and store its csto flag
  source_idx  <- setNames(seq_along(sources), sources)
  source_csto <- mini_results[, .(csto = csto[1]), by = source]
  csto_flag   <- source_csto$csto  # length n_sources, aligned with sources
 
  # Pre-compute cell-level vectors aligned with mini_results rows
  cell_source_idx <- source_idx[mini_results$source]
  cell_csto       <- mini_results$csto
  cell_N          <- mini_results$N
  cell_theta      <- mini_results$theta
  n_cells         <- nrow(mini_results)
 
  # Masks for CSTO / Non-CSTO cells
  csto_mask <- (cell_csto == 1)
  non_mask  <- (cell_csto == 0)
 
  # Storage
  theta_boot_csto <- numeric(B)
  theta_boot_non  <- numeric(B)
  theta_boot_diff <- numeric(B)
 
  for (b in seq_len(B)) {
 
    # 1. Draw Dirichlet(1,1,...,1) weights for all sources
    #    Dirichlet draw = normalize independent Gamma(1,1) draws
    gam_draws <- rgamma(n_sources, shape = 1, rate = 1)
    dir_weights <- gam_draws / sum(gam_draws)
 
    # 2. Effective weight for each cell = source's Dirichlet weight × cell N
    cell_weights <- dir_weights[cell_source_idx] * cell_N
 
    # 3. Weighted averages within each CSTO group
    w_csto <- cell_weights[csto_mask]
    w_non  <- cell_weights[non_mask]
 
    theta_boot_csto[b] <- sum(w_csto * cell_theta[csto_mask]) / sum(w_csto)
    theta_boot_non[b]  <- sum(w_non  * cell_theta[non_mask])  / sum(w_non)
    theta_boot_diff[b] <- theta_boot_csto[b] - theta_boot_non[b]
  }
 
  cat("  Bayesian bootstrap iterations:", B, "\n")
  cat("  (All iterations valid — no sources are ever dropped)\n")
 
  # Point estimates (from original data, standard N-weighting)
  orig_csto <- weighted.mean(
    mini_results[csto == 1, theta], mini_results[csto == 1, N]
  )
  orig_non <- weighted.mean(
    mini_results[csto == 0, theta], mini_results[csto == 0, N]
  )
  orig_diff <- orig_csto - orig_non
 
  # Posterior SEs (SD of bootstrap distribution)
  se_csto <- sd(theta_boot_csto)
  se_non  <- sd(theta_boot_non)
  se_diff <- sd(theta_boot_diff)
 
  # Percentile CIs (95% credible intervals)
  ci_csto <- quantile(theta_boot_csto, c(0.025, 0.975))
  ci_non  <- quantile(theta_boot_non,  c(0.025, 0.975))
  ci_diff <- quantile(theta_boot_diff, c(0.025, 0.975))
 
  # P-values: posterior probability of sign reversal (two-sided)
  p_csto <- 2 * min(mean(theta_boot_csto >= 0), mean(theta_boot_csto <= 0))
  p_non  <- 2 * min(mean(theta_boot_non  >= 0), mean(theta_boot_non  <= 0))
  p_diff <- 2 * min(mean(theta_boot_diff >= 0), mean(theta_boot_diff <= 0))
 
  list(
    results = data.table(
      group     = c("CSTO", "Non-CSTO", "Difference"),
      estimate  = c(orig_csto, orig_non, orig_diff),
      se_boot   = c(se_csto, se_non, se_diff),
      p_boot    = c(p_csto, p_non, p_diff),
      ci_lower  = c(ci_csto[1], ci_non[1], ci_diff[1]),
      ci_upper  = c(ci_csto[2], ci_non[2], ci_diff[2])
    ),
    boot_dist = list(
      csto = theta_boot_csto,
      non  = theta_boot_non,
      diff = theta_boot_diff
    )
  )
}
 
cat("Running source-level pairs bootstrap for Approach 2...\n")
boot2_pairs <- run_source_pairs_bootstrap(mini_results, B = 9999)
 
cat("\n")
cat("=====================================================================\n")
cat("  APPROACH 2a: Source-Level Pairs Bootstrap Results\n")
cat("=====================================================================\n")
print(boot2_pairs$results, digits = 4)
cat("=====================================================================\n\n")
```


```{r}
cat("Running Bayesian bootstrap for Approach 2...\n")
boot2_bayes <- run_bayesian_bootstrap(mini_results, B = 9999)
 
cat("\n")
cat("=====================================================================\n")
cat("  APPROACH 2b: Bayesian Bootstrap Results (Rubin 1981)\n")
cat("=====================================================================\n")
print(boot2_bayes$results, digits = 4)
cat("=====================================================================\n\n")
```

```{r}
# Write out of data
# Source-level treatment effects (N-weighted average across topics within source)
source_level_effects <- mini_results[, .(
  theta  = weighted.mean(theta, N),
  N      = sum(N),
  csto   = csto[1],
  n_topics = .N
), by = source]
setorder(source_level_effects, csto, source)
 
# Group-level summary (CSTO / Non-CSTO / Difference)
decomposition_results <- list(
  # Cell-level estimates (source x topic)
  cell_effects   = mini_results[order(csto, source, topic)],
  # Source-level estimates (averaged across topics)
  source_effects = source_level_effects,
  # Group-level estimates with both bootstrap methods
  group_effects_pairs = boot2_pairs$results,
  group_effects_bayes = boot2_bayes$results,
  # Bootstrap distributions (for plotting if needed)
  boot_distributions_pairs = boot2_pairs$boot_dist,
  boot_distributions_bayes = boot2_bayes$boot_dist,
  # Metadata
  n_sources_csto     = sum(source_level_effects$csto == 1),
  n_sources_non_csto = sum(source_level_effects$csto == 0),
  n_cells            = nrow(mini_results),
  B                  = length(boot2_pairs$boot_dist$csto)
)
```




## Heavily Saturated Non-Mil Model

```{r saturated-model-drop}
# Change source and topic to factor
optimal_bandwidth_data_state_non_mil <- optimal_bandwidth_data_state_non_mil %>%
  mutate(
    source_domain = as.factor(source_domain),
    topic_clean = as.factor(topic_clean)
  )

# Heavily saturated model
model5a_fully_saturated <- feols(
  sentiment_clean ~ running_continuous * treatment * csto |
    source_domain^topic_clean + topic_clean^treatment,
  cluster = ~source_domain,
  data = optimal_bandwidth_data_state_non_mil
)

summary(model5a_fully_saturated)
```

### Manual Wild Bootstrap Standard Errors

```{r saturated-bootstrap-drop}
# set.seed(3184)
# B <- 99
# 
# # Original model
# model_original <- model5a_fully_saturated
# original_coef <- coef(model_original)["treatment:csto"]
# original_se <- se(model_original)["treatment:csto"]
# original_t <- original_coef / original_se
# 
# cat("Original t-stat:", original_t, "\n")
# 
# # CRITICAL: Estimate RESTRICTED model under the null (treatment:csto = 0)
# # Remove treatment:csto from the formula
# model_restricted <- feols(
#   sentiment_clean ~ running_continuous + treatment + csto + running_continuous:treatment + running_continuous:csto +
#     running_continuous:treatment:csto |  # Keep triple interaction but not treatment:csto
#     source_domain^topic_clean + topic_clean^treatment,
#   cluster = ~source_domain,
#   data = optimal_bandwidth_data_state_non_mil
# )
# 
# # Get residuals and fitted values from RESTRICTED model
# residuals_restricted <- residuals(model_restricted)
# fitted_restricted <- fitted(model_restricted)
# 
# cat("Using restricted model residuals (null imposed)\n")
# 
# # Get clusters
# clusters <- unique(optimal_bandwidth_data_state_non_mil$source_domain)
# n_clusters <- length(clusters)
# 
# # Bootstrap
# boot_t_stats <- numeric(B)
# 
# for(b in 1:B) {
#   # Generate Rademacher weights
#   cluster_weights <- sample(c(-1, 1), n_clusters, replace = TRUE)
# 
#   # Assign to observations
#   data_boot <- optimal_bandwidth_data_state_non_mil
#   data_boot$weight <- sapply(data_boot$source_domain, function(clust) {
#     cluster_weights[which(clusters == clust)]
#   })
# 
#   # Create bootstrap outcome using RESTRICTED fitted values
#   data_boot$sentiment_boot <- fitted_restricted + data_boot$weight * residuals_restricted
# 
#   # Re-estimate FULL model on bootstrap data
#   model_boot <- feols(
#     sentiment_boot ~ running_continuous * treatment * csto |
#       source_domain^topic_clean + topic_clean^treatment,
#     cluster = ~source_domain,
#     data = data_boot
#   )
# 
#   boot_coef <- coef(model_boot)["treatment:csto"]
#   boot_se <- se(model_boot)["treatment:csto"]
#   boot_t_stats[b] <- boot_coef / boot_se
# 
#   if(b %% 100 == 0) cat("Iteration:", b, "\n")
# }
# 
# # Calculate p-value
# p_value <- mean(abs(boot_t_stats) >= abs(original_t))
# 
# cat("\n=== Results ===\n")
# cat("Original t-stat:", original_t, "\n")
# cat("Mean bootstrap t-stat (should be ~0):", mean(boot_t_stats), "\n")
# cat("P-value:", p_value, "\n")
# 
# # Plot
# hist(boot_t_stats, breaks=30, main="Wild Bootstrap t-statistics (Null Imposed)",
#      xlab="t-statistic")
# abline(v=original_t, col="red", lwd=2)
# abline(v=0, col="blue", lwd=2, lty=2)
# legend("topright", c("Original t", "Null (t=0)"), col=c("red","blue"), lty=c(1,2), lwd=2)
# 
# # Extract bootstrap results for saturated model in standard format
# boot_model5a_fully_saturated <- list(
#   se = original_se,
#   p_val = p_value,
#   ci_lower = NA,  # Not computed in manual bootstrap
#   ci_upper = NA,  # Not computed in manual bootstrap
#   t_stat = original_t
# )
# cat("Saturated model bootstrap results extracted\n")
```

# Save Results

```{r save-drop}
results_het_drop <- list(
  # Main models
  model5a = model5a,
  model5a_full = model5a_full,
  model5a_opt = model5a_opt,
  model5a_opt_non_mil = model5a_opt_non_mil,
  model5a_opt_russian = model5a_opt_russian,
  model5a_csto = model5a_csto,
  model5a_neutral = model5a_neutral,
  model5a_opt_full_fe = model5a_opt_full_fe,
  model5a_opt_non_mil_full_fe = model5a_opt_non_mil_full_fe,
  model5a_fully_saturated = model5a_fully_saturated,
  matched_model = matched_model,

  # Z-score models
  model5a_z = model5a_z,
  model5a_csto_z = model5a_csto_z,
  model5a_neutral_z = model5a_neutral_z,
  model5a_opt_z = model5a_opt_z,
  model5a_opt_non_mil_z = model5a_opt_non_mil_z,
  model5a_opt_russian_z = model5a_opt_russian_z,

  # Russian Full FE
  model5a_opt_rus_full_fe = model5a_opt_rus_full_fe,

  # Topic-specific models
  model5a_opt_pol = model5a_opt_pol,
  model5a_opt_mil = model5a_opt_mil,
  model5a_opt_econ = model5a_opt_econ,
  model5a_opt_cult = model5a_opt_cult,
  model5a_opt_oth = model5a_opt_oth,
  model5a_full_pol = model5a_full_pol,
  model5a_full_mil = model5a_full_mil,
  model5a_full_econ = model5a_full_econ,
  model5a_full_cult = model5a_full_cult,
  model5a_full_oth = model5a_full_oth,

  # Bootstrap standard errors
  bootstrap_se = list(
    # Main model5a variants
    model5a = boot_model5a,
    model5a_full = boot_model5a_full,
    model5a_opt = boot_model5a_opt,
    model5a_opt_non_mil = boot_model5a_opt_non_mil,
    model5a_opt_russian = boot_model5a_opt_russian,
    model5a_opt_full_fe = boot_model5a_opt_full_fe,
    model5a_opt_non_mil_full_fe = boot_model5a_opt_non_mil_full_fe,
    model5a_fully_saturated = boot_model5a_fully_saturated,
    matched_model = boot_matched_model,

    # Z-score bootstrap SEs
    model5a_z = boot_model5a_z,
    model5a_opt_z = boot_model5a_opt_z,
    model5a_opt_non_mil_z = boot_model5a_opt_non_mil_z,
    model5a_opt_russian_z = boot_model5a_opt_russian_z,

    # Russian Full FE bootstrap
    model5a_opt_rus_full_fe = boot_model5a_opt_rus_full_fe,

    # Topic-specific model5a (optimal BW)
    model5a_opt_pol = boot_model5a_opt_pol,
    model5a_opt_mil = boot_model5a_opt_mil,
    model5a_opt_econ = boot_model5a_opt_econ,
    model5a_opt_cult = boot_model5a_opt_cult,
    model5a_opt_oth = boot_model5a_opt_oth,

    # Topic-specific model5a (full data)
    model5a_full_pol = boot_model5a_full_pol,
    model5a_full_mil = boot_model5a_full_mil,
    model5a_full_econ = boot_model5a_full_econ,
    model5a_full_cult = boot_model5a_full_cult,
    model5a_full_oth = boot_model5a_full_oth,

    # Placebo test
    model_placebo_nonmil = boot_model_placebo_nonmil
  ),

  optimal_bandwidth_align = optimal_bw_align,
  optimal_bw_align_pol = optimal_bw_align_pol,
  optimal_bw_align_mil = optimal_bw_align_mil,
  optimal_bw_align_econ = optimal_bw_align_econ,
  optimal_bw_align_cult = optimal_bw_align_cult,
  optimal_bw_align_oth = optimal_bw_align_oth,
  loo_results = loo_results,
  loo_summary = loo_summary,
  matched_loo_results = matched_loo_results,
  matched_loo_summary = matched_loo_summary,
  model_placebo_nonmil = model_placebo_nonmil,
  optimal_bw_placebo_nonmil = optimal_bw_placebo_nonmil,

  # Dec-7 placebo restricted to aligned (CSTO) state media, one rdrobust per country
  placebo_aligned_models = placebo_aligned_models,

  # Mini-Regressions: Heterogeneous treatment effect decomposition
  decomposition = decomposition_results
)

saveRDS(results_het_drop, file.path(DATA_INTERMEDIATE, "06_alignment_results_drop.rds"))
cat("Results saved to:", file.path(DATA_INTERMEDIATE, "06_alignment_results_drop.rds"), "\n")
```

# Session Info

```{r session-info-drop}
print_session_info()
```
