---
title: "06d - Russian Alignment Analysis (Drop No-Time Articles) (CSTO vs Neutral)"
author: "Donald Moratz"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

# Overview

This script examines heterogeneous treatment effects by Russian alignment (CSTO vs Neutral) only, using time as a continuous running variable, after dropping articles without exact publication times.

**Inputs:**
- `data/intermediate/02_cleaned_data.rds`
- `data/intermediate/02_data_non_ukraine.rds`

**Outputs:**
- Table 3F (Russian Alignment)

```{r setup-drop, include=FALSE}
source("00_setup.R")
knitr::opts_chunk$set(fig.path = paste0(FIGURES_HETEROGENEITY_DROP, "/"))
options(digits = 10)

set.seed(3184)
```

# Load Data

```{r load-drop}
data <- readRDS(file.path(DATA_INTERMEDIATE, "02_cleaned_data.rds"))
data_non_ukraine <- readRDS(file.path(DATA_INTERMEDIATE, "02_data_non_ukraine.rds"))

data <- data %>% filter(has_time == TRUE)
data_non_ukraine <- data_non_ukraine %>% filter(has_time == TRUE)

cat("Full data after dropping no-time articles:", nrow(data), "articles\n")
cat("Non-Ukraine data after dropping:", nrow(data_non_ukraine), "articles\n")

data <- data %>% mutate(across(c(topic_clean, country, source_domain), as.factor))
data_non_ukraine <- data_non_ukraine %>% mutate(across(c(topic_clean, country, source_domain), as.factor))
```

# Russian Alignment Analysis (CSTO vs Neutral)

## Create Alignment Subsets

```{r alignment-data-drop}
# Filter to non-NATO countries for alignment analysis
data_align <- data %>%
  filter(nato == 0)%>%
  drop_na()

# Create alignment indicator
data_align <- data_align %>%
  mutate(align_indicator = factor(case_when(
    indicator == 1 & csto == 1 ~ "Pre. Ind. CSTO",
    indicator == 1 & csto == 0 ~ "Pre. Ind. Neut",
    indicator == 2 & csto == 1 ~ "Pre. State CSTO",
    indicator == 2 & csto == 0 ~ "Pre. State Neut",
    indicator == 3 & csto == 1 ~ "Post Ind. CSTO",
    indicator == 3 & csto == 0 ~ "Post Ind. Neut",
    indicator == 4 & csto == 1 ~ "Post State CSTO",
    indicator == 4 & csto == 0 ~ "Post State Neut"
  ),
  levels = c("Pre. Ind. CSTO", "Pre. Ind. Neut", "Pre. State CSTO",
             "Pre. State Neut", "Post Ind. CSTO", "Post Ind. Neut",
             "Post State CSTO", "Post State Neut")))

cat("Non-NATO countries sample:", nrow(data_align), "articles\n")
cat("CSTO:", sum(data_align$csto), "\n")
cat("Neutral:", sum(data_align$csto == 0), "\n")
```

## Visualization: Independent Media by Alignment

```{r align-ind-plot-drop, fig.width=10, fig.height=7}
agg_data_align_ind <- data_align %>%
  filter(state_owned == 0) %>%
  group_by(running_continuous, csto) %>%
  summarize(sentiment_clean = mean(sentiment_clean), num_obs = n(), .groups = "drop")

data_align %>%
  filter(state_owned == 0) %>%
  ggplot(aes(x = running_continuous, y = sentiment_clean, group = align_indicator, color = align_indicator)) +
  geom_point(data = agg_data_align_ind,
             aes(x = running_continuous, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = COLORS_DISCS, name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on Independent Media Sentiment (Drop No-Time)",
    subtitle = "Neutral vs Russia Aligned, Difference in Discontinuities",
    x = "Hours Pre/Post Invasion",
    y = "Sentiment"
  )
```

## Visualization: State Media by Alignment

```{r align-state-plot-drop, fig.width=10, fig.height=7}
agg_data_align_state <- data_align %>%
  filter(state_owned == 1) %>%
  group_by(running_continuous, csto) %>%
  summarize(sentiment_clean = mean(sentiment_clean), num_obs = n(), .groups = "drop")

state_align_discs_graph <- data_align %>%
  filter(state_owned == 1) %>%
  ggplot(aes(x = running_continuous, y = sentiment_clean, group = align_indicator, color = align_indicator)) +
  geom_point(data = agg_data_align_state,
             aes(x = running_continuous, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = COLORS_DISCS, name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on State Media Sentiment (Drop No-Time)",
    subtitle = "Neutral vs Russia Aligned, Difference in Discontinuities",
    x = "Hours Pre/Post Invasion",
    y = "Sentiment"
  )

state_align_discs_graph

ggsave(plot = state_align_discs_graph,
       file.path(FIGURES_HETEROGENEITY_DROP, "state_align_discs_drop.png"),
       width = 10, height = 7)
```

## Pre-Trend Diagnostic: State Media in Russia-Aligned Countries

Addresses the concern that sentiment toward Russia may have turned negative *before* the
Feb 24, 2022 invasion (during the troop buildup) in state-owned media of Russia-aligned
countries. We plot the daily mean sentiment for state-owned sources in each aligned country
(Armenia, Azerbaijan, Belarus, Kazakhstan), mark both the Dec 7, 2021 US public-warning
date and the Feb 24, 2022 invasion cutoff, and overlay a linear fit on the pre-invasion
window only so any pre-existing slide is visible.

```{r pretrend-by-country-aligned-drop, fig.width=10, fig.height=7}
# Buildup display window (trim to keep the pre-invasion period readable)
PRETREND_START <- as.Date("2021-06-01")
PRETREND_END   <- as.Date("2022-06-01")
INVASION_DATE  <- as.Date("2022-02-24")
WARNING_DATE   <- as.Date("2021-12-07")

# State-owned media in the Russia-aligned (CSTO) group; Ukraine already excluded (NATO)
data_pretrend <- data %>%
  filter(country %in% CSTO_COUNTRIES, state_owned == 1,
         date_publish >= PRETREND_START, date_publish <= PRETREND_END) %>%
  mutate(country = droplevels(country))

# Daily mean sentiment per country (same outcome + daily aggregation as other figures)
agg_pretrend <- data_pretrend %>%
  group_by(country, date_publish) %>%
  summarize(sentiment_clean = mean(sentiment_clean, na.rm = TRUE),
            num_obs = n(), .groups = "drop")

# Pre-invasion daily means only (the linear fit is restricted to this window)
agg_pretrend_pre <- agg_pretrend %>%
  filter(date_publish < INVASION_DATE)

pretrend_by_country_aligned_graph <- ggplot(agg_pretrend,
                                             aes(x = date_publish, y = sentiment_clean)) +
  geom_point(aes(size = num_obs), alpha = 0.2, inherit.aes = TRUE) +
  geom_smooth(data = agg_pretrend_pre, method = "lm", se = TRUE, color = "red4") +
  geom_vline(xintercept = INVASION_DATE, linetype = "dashed", alpha = 0.7) +
  geom_vline(xintercept = WARNING_DATE, linetype = "dotted", color = "grey30") +
  scale_size(name = "Observations") +
  facet_wrap(~ country, scales = "free_y") +
  theme_classic() +
  labs(
    title = "Pre-Invasion Sentiment Trend in State Media (Drop No-Time)",
    subtitle = "Russia-aligned countries; dotted = Dec 7 warning, dashed = Feb 24 invasion",
    x = "Publication date",
    y = "Mean sentiment toward Russia"
  )

pretrend_by_country_aligned_graph

ggsave(plot = pretrend_by_country_aligned_graph,
       file.path(FIGURES_HETEROGENEITY_DROP, "pretrend_by_country_aligned.png"),
       width = 10, height = 7)
```

```{r pretrend-slopes-aligned-drop}
# Per-country pre-invasion linear slope (fit on the plotted daily means).
# Slope is in sentiment units per day; also reported per 30 days for readability.
pretrend_slopes <- agg_pretrend_pre %>%
  group_by(country) %>%
  group_modify(~ {
    fit <- lm(sentiment_clean ~ as.numeric(date_publish), data = .x)
    ct <- summary(fit)$coefficients["as.numeric(date_publish)", ]
    tibble(
      n_days       = nrow(.x),
      slope_day    = ct["Estimate"],
      slope_30day  = ct["Estimate"] * 30,
      std_error    = ct["Std. Error"],
      p_value      = ct["Pr(>|t|)"]
    )
  }) %>%
  ungroup()

cat("=== Task A: Pre-invasion sentiment slope in state media, by aligned country ===\n")
cat("(slope in sentiment units per day; slope_30day = per 30 days)\n\n")
print(as.data.frame(pretrend_slopes), row.names = FALSE, digits = 4)
```

Replica of the figure above with a later start date (Dec 1, 2021) to confirm the
pre-invasion trend lines are not an artifact of fitting across a long (nine-month) window.
INVASION_DATE and WARNING_DATE are reused from the chunk above.

```{r pretrend-by-country-aligned-dec-drop, fig.width=10, fig.height=7}
# Shorter buildup display window (later start; same invasion / warning markers)
PRETREND_START_DEC <- as.Date("2021-12-01")

data_pretrend_dec <- data %>%
  filter(country %in% CSTO_COUNTRIES, state_owned == 1,
         date_publish >= PRETREND_START_DEC, date_publish <= PRETREND_END) %>%
  mutate(country = droplevels(country))

agg_pretrend_dec <- data_pretrend_dec %>%
  group_by(country, date_publish) %>%
  summarize(sentiment_clean = mean(sentiment_clean, na.rm = TRUE),
            num_obs = n(), .groups = "drop")

# Pre-invasion daily means only (linear fit restricted to this window)
agg_pretrend_dec_pre <- agg_pretrend_dec %>%
  filter(date_publish < INVASION_DATE)

pretrend_by_country_aligned_dec_graph <- ggplot(agg_pretrend_dec,
                                                 aes(x = date_publish, y = sentiment_clean)) +
  geom_point(aes(size = num_obs), alpha = 0.2, inherit.aes = TRUE) +
  geom_smooth(data = agg_pretrend_dec_pre, method = "lm", se = TRUE, color = "red4") +
  geom_vline(xintercept = INVASION_DATE, linetype = "dashed", alpha = 0.7) +
  geom_vline(xintercept = WARNING_DATE, linetype = "dotted", color = "grey30") +
  scale_size(name = "Observations") +
  facet_wrap(~ country, scales = "free_y") +
  theme_classic() +
  labs(
    title = "Pre-Invasion Sentiment Trend in State Media, Dec 1 Start (Drop No-Time)",
    subtitle = "Russia-aligned countries; dotted = Dec 7 warning, dashed = Feb 24 invasion",
    x = "Publication date",
    y = "Mean sentiment toward Russia"
  )

pretrend_by_country_aligned_dec_graph

ggsave(plot = pretrend_by_country_aligned_dec_graph,
       file.path(FIGURES_HETEROGENEITY_DROP, "pretrend_by_country_aligned_dec.png"),
       width = 10, height = 7)
```

## State Media Alignment Regressions

### CSTO Countries Only

```{r align-csto-drop}
# Filter to CSTO data, non military
data_align_state_csto <- data_align %>%
  filter(state_owned == 1, csto == 1) %>%
  filter(!topic_clean %in% "Military") %>%
  mutate(running_continuous = running_continuous / 86400.0)

# Applying a Z-Score Transformation
data_align_state_csto <- data_align_state_csto %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                   sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()

covs_matrix <- model.matrix(~ topic_clean - 1, data = data_align_state_csto)

model5a_csto_z <- rdrobust(
  y = data_align_state_csto$sentiment_z,
  x = data_align_state_csto$running_continuous,
  covs = covs_matrix,
  cluster = data_align_state_csto$source_domain
)

summary(model5a_csto_z)
```


### Neutral Countries Only

```{r align-neutral-drop}
# Filter data to neutral countries only
data_align_state_neutral <- data_align %>%
  filter(state_owned == 1, csto == 0) %>%
  filter(!topic_clean %in% "Military") %>%
  mutate(running_continuous = running_continuous / 86400)

# Applying a Z-Score Transformation
data_align_state_neutral <- data_align_state_neutral %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                   sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()

covs_matrix <- model.matrix(~ topic_clean - 1, data = data_align_state_neutral)

model5a_neutral_z <- rdrobust(
  y = data_align_state_neutral$sentiment_z,
  x = data_align_state_neutral$running_continuous,
  covs = covs_matrix,
  cluster = data_align_state_neutral$source_domain
)

summary(model5a_neutral_z)
```

# Diff-in-Disc Analysis

## Full Data

### State Media Sample and Z-Score

The diff-in-disc sample is state-owned media in non-NATO countries, contrasting
Russia-aligned against neutral outlets. Sentiment is z-scored within source, so
outlets with different baseline tone are on a common scale. This chunk builds the
sample every model below is fitted on; no full-data model is fitted, since none
reaches a table 10d or 11 builds.

```{r align-diff-drop}
data_align_state <- data_align %>%
  filter(state_owned == 1) %>%
  mutate(source_domain = droplevels(source_domain)) %>%
  mutate(running_continuous = running_continuous / 86400)

data_align_state <- data_align_state %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                   sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()

cat("State media, non-NATO sample:", nrow(data_align_state), "articles\n")
```


## Optimal Bandwidth

### Optimal Bandwidth Sentiment Z

```{r align-optimal-z-drop}
# Residualize the dependent variable for fixed effects to do bandwidth selection
resid_y <- feols(sentiment_z ~ 1 | topic_clean + csto,
                 data = data_align_state)$residuals

bw_align <- rdbwselect(y = resid_y,
                       x = data_align_state$running_continuous,
                       kernel = "triangular",
                       cluster = data_align_state$source_domain,
                       p = 1,
                       bwselect = "mserd")

optimal_bw_align <- bw_align$bws[1, 1]
cat("Optimal bandwidth:", round(optimal_bw_align, 1), "days\n")

optimal_bandwidth_data_state <- data_align_state %>%
  filter(running_continuous < optimal_bw_align, running_continuous > -optimal_bw_align)

model5a_opt_z <- feols(sentiment_z ~ running_continuous * treatment * csto | topic_clean,
                     cluster = ~source_domain,
                     data = optimal_bandwidth_data_state)

summary(model5a_opt_z)

# Wild cluster bootstrap for model5a_opt_z
boot_model5a_opt_z <- run_wild_bootstrap(model5a_opt_z, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_opt_z$se, "\n")
cat("Bootstrap p-value:", boot_model5a_opt_z$p_val, "\n")
```

## Non-Military

### Non-Military Sample

Military coverage moves for reasons unrelated to the signalling mechanism, so
Table 4 Model 4 and the matched model below are fitted with it omitted. This
chunk builds that sample; the bandwidth is re-selected on it in the next chunk.

```{r align-non-mil-drop}
data_align_state_non_mil <- data_align_state %>%
  filter(!topic_clean %in% "Military")

cat("State media, non-military sample:", nrow(data_align_state_non_mil), "articles\n")
```

### Non-Military, Sentiment Z

```{r align-non-mil-z-drop}
# Create New z score
data_align_state_non_mil <- data_align_state_non_mil %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                   sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()


# Residualize the dependent variable for fixed effects to do bandwidth selection
resid_y <- feols(sentiment_z ~ 1 | topic_clean + csto,
                 data = data_align_state_non_mil)$residuals

bw_align_non_mil <- rdbwselect(y = resid_y,
                               x = data_align_state_non_mil$running_continuous,
                               kernel = "triangular",
                               cluster = data_align_state_non_mil$source_domain,
                               p = 1,
                               bwselect = "mserd")

optimal_bw_align_non_mil <- bw_align_non_mil$bws[1, 1]
cat("Optimal bandwidth (non-mil):", round(optimal_bw_align_non_mil, 1), "days\n")

optimal_bandwidth_data_state_non_mil <- data_align_state_non_mil %>%
  filter(running_continuous < optimal_bw_align_non_mil, running_continuous > -optimal_bw_align_non_mil)

model5a_opt_non_mil_z <- feols(sentiment_z ~ running_continuous
                             * treatment * csto | topic_clean,
                             cluster = ~source_domain,
                             data = optimal_bandwidth_data_state_non_mil)

summary(model5a_opt_non_mil_z)

# Wild cluster bootstrap for model5a_opt_non_mil_z
boot_model5a_opt_non_mil_z <- run_wild_bootstrap(model5a_opt_non_mil_z, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_model5a_opt_non_mil_z$se, "\n")
cat("Bootstrap p-value:", boot_model5a_opt_non_mil_z$p_val, "\n")
```


```{r ggridges-viz-drop}

# Prepare the data for plotting
plot_data <- optimal_bandwidth_data_state_non_mil %>%
  group_by(source_domain) %>%
  mutate(
    # Recalculate Local Z-score
    sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                   sd(sentiment_clean, na.rm = TRUE)
  ) %>%
  ungroup() %>%
  select(source_domain, sentiment_clean, sentiment_z) %>%
  pivot_longer(cols = c(sentiment_clean, sentiment_z),
               names_to = "Type", values_to = "Value")

# Plotting the comparison
ggplot(plot_data, aes(x = Value, y = source_domain, fill = Type)) +
  geom_density_ridges(alpha = 0.5, scale = 0.9) +
  facet_wrap(~Type, scales = "free_x") +
  theme_minimal() +
  labs(title = "Ternary Sentiment vs. Z-Scored Sentiment by Source",
       subtitle = "Local Z-scoring centers each source and adjusts for their specific volatility",
       x = "Sentiment Value",
       y = "Media Outlet") +
  scale_fill_manual(values = c("sentiment_clean" = "#69b3a2", "sentiment_z" = "#404080"))

ggsave(plot = last_plot(),
       file.path(FIGURES_HETEROGENEITY_DROP, "sentiment_zscore_comparison_drop.png"),
       width = 10, height = 7)
```


# Robustness

## Matching

### Initial Match

```{r matching-analysis-drop}
# Subset to data of interest

matching_data <- optimal_bandwidth_data_state_non_mil %>%
  select(sentiment_z, running, running_continuous, treatment, csto,
         topic_clean, source_domain, country)

# Match on topic and publication day (using integer day from running_continuous)
matching_data <- matching_data %>%
  mutate(running_day = floor(running_continuous / 86400))

ps_model <- matchit(
  csto ~ running_day + topic_clean,
  data = matching_data,
  method = "exact",
  ratio = 1,
)

summary(ps_model)
```

### Assess Balance

```{r matching-balance-drop}
# Numerical balance check (better)
bal.tab(ps_model, un = TRUE, stats = c("m", "v"), thresholds = c(m = 0.1))
# Want: all standardized mean differences < 0.1 after matching

# Love plot (publication quality)
love <- love.plot(ps_model, binary = "std", thresholds = c(m = 0.1))
love
ggsave(plot = love,
       file.path(FIGURES_HETEROGENEITY_DROP, "love_plot_drop.png"),
       width = 10, height = 7)
```

### Matching analysis

```{r matching-model-drop}
# Extract matched data and calculate treatment effects
matched_data <- match.data(ps_model)

matched_model <- feols(sentiment_z ~ running_continuous
                                     * treatment * csto |
                                       topic_clean,
                                     cluster = ~source_domain,
                                     data = matched_data
                                     )

summary(matched_model)


# Wild cluster bootstrap for matched model
boot_matched_model <- run_wild_bootstrap(matched_model, "treatment:csto")
cat("Bootstrap SE for treatment:csto:", boot_matched_model$se, "\n")
cat("Bootstrap p-value:", boot_matched_model$p_val, "\n")
```



### Sensitivity of OVB

```{r sensitivity-ovb-drop}
# Save the bootstrapped p-val
bootstrapped_se <- boot_matched_model$p_val

# Respecify the model using lm
lm_model <- lm(sentiment_z ~ running_continuous * treatment * csto +
                 factor(topic_clean),
               data = matched_data)


# Sensitivity analysis
sensitivity <- sensemakr(
  model = lm_model,
  treatment = "treatment:csto",
  benchmark_covariates = c("running_continuous:treatment"),
  kd = 1,
  ky = 1,
  reduce = TRUE
)

summary(sensitivity)
```


```{r sensitivity-partialr2-drop}
partial_r2(lm_model, covariates = c("running_continuous:treatment",
                                     "running_continuous:csto",
                                     "treatment",
                                     "csto"))

treatment_r2 <- partial_r2(lm_model, covariates = c("treatment"))
```


```{r sensitivity-plot-drop}
# Manually recompute the CI bound using the bootstrapped SE
coef_interest <- coef(lm_model)["treatment:csto"]
rv_ci <- coef_interest / bootstrapped_se  # your corrected t-stat for reference

plot(sensitivity,
     xlab = "Partial R² of confounder with CSTO membership",
     ylab = "Partial R² of confounder with sentiment",
     main = "Sensitivity to Unobserved Confounding",
     lim.x = .1,
     lim.y = .1,
     col.contour = "grey60",
     label.text = FALSE)   # turn off the ugly overlapping label first
text(x = 0.01, y = 0.00005,
     labels = "running:treatment",
     cex = 0.8, pos = 4)
```


```{r sensitivity-contour-drop}
# Sensitivity Plot

# Extract the data sensemakr uses for the plot
ovb_contour_data <- function(sensitivity, lim = 0.005) {

  # Grid of r2dz.x and r2yz.dx values
  r2dz <- seq(0, lim, length.out = 400)
  r2yz <- seq(0, lim, length.out = 400)
  grid <- expand.grid(r2dz.x = r2dz, r2yz.dx = r2yz)

  # Extract key stats
  estimate <- sensitivity$sensitivity_stats$estimate
  se <- sensitivity$sensitivity_stats$se
  df <- sensitivity$sensitivity_stats$dof

  # Compute adjusted estimate across grid
  grid$adjusted <- mapply(function(r2dz, r2yz) {
    sensemakr::adjusted_estimate(
      estimate = estimate,
      se = se,
      dof = df,
      r2dz.x = r2dz,
      r2yz.dx = r2yz
    )
  }, grid$r2dz.x, grid$r2yz.dx)

  return(grid)
}

# Extract benchmark points
benchmark_df <- data.frame(
  r2dz.x = sensitivity$bounds$r2dz.x,
  r2yz.dx = sensitivity$bounds$r2yz.dx,
  label = sensitivity$bounds$bound_label
)

# Build contour data
# Rebuild with wider x limit
contour_data <- ovb_contour_data(sensitivity, lim = 0.1)

ggplot(contour_data, aes(x = r2dz.x, y = r2yz.dx, z = adjusted)) +
  geom_contour(colour = "grey60",
               breaks = c(-0.1, -0.05, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3)) +
  geom_contour(breaks = 0,
               colour = "red",
               linetype = "dashed",
               linewidth = 0.8) +
  geom_point(data = benchmark_df,
             aes(x = r2dz.x, y = r2yz.dx),
             shape = 18, colour = "red", size = 3,
             inherit.aes = FALSE) +
  annotate("point", x = 0, y = 0, shape = 17, size = 3) +
  annotate("text", x = 0.002, y = 0.003,
           label = "Unadjusted\n(-0.146)",
           size = 5, hjust = 0) +
  annotate("text", x = 0.047, y = 0.003,
           label = "running:treatment",
           size = 5, hjust = 0) +
  coord_cartesian(xlim = c(0, 0.1), ylim = c(0, 0.1)) +
  scale_x_continuous(breaks = seq(0, 0.1, by = 0.02),
                     labels = scales::number_format(accuracy = 0.01)) +
  scale_y_continuous(breaks = seq(0, 0.1, by = 0.02),
                     labels = scales::number_format(accuracy = 0.01)) +
  labs(
    x = "Partial R² of confounder with CSTO membership",
    y = "Partial R² of confounder with sentiment",
    title = "Sensitivity to Unobserved Confounding, CSTO Affiliation",
    subtitle = "Red dashed line indicates where estimate = 0"
  ) +
  theme_bw() +
  theme(
    panel.grid.minor = element_blank(),
    plot.title = element_text(face = "bold"),
    legend.position = "none"
  )

ggsave(plot = last_plot(),
       file.path(FIGURES_HETEROGENEITY_DROP, "sensitivity_ovb_csto_drop.png"),
       width = 10, height = 7)
```


# Save Results

```{r save-drop}
results_het_drop <- list(
  # Table 4 Models 1-2: separate RDDs, Russia-aligned and neutral state media
  model5a_csto_z = model5a_csto_z,
  model5a_neutral_z = model5a_neutral_z,

  # Table 4 Models 3-4: diff-in-disc at the optimal bandwidth, all topics and
  # military omitted
  model5a_opt_z = model5a_opt_z,
  model5a_opt_non_mil_z = model5a_opt_non_mil_z,

  # Table 4 Model 5: matched
  matched_model = matched_model,

  # Wild cluster bootstrap results behind the significance stars
  bootstrap_se = list(
    model5a_opt_z = boot_model5a_opt_z,
    model5a_opt_non_mil_z = boot_model5a_opt_non_mil_z,
    matched_model = boot_matched_model
  )
)

saveRDS(results_het_drop, file.path(DATA_INTERMEDIATE, "06_alignment_results_drop.rds"))
cat("Results saved to:", file.path(DATA_INTERMEDIATE, "06_alignment_results_drop.rds"), "\n")
```

# Session Info

```{r session-info-drop}
print_session_info()
```
