---
title: "07 - Publication Outputs"
author: "Donald Moratz"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

# Overview

This script generates all publication-quality tables and figures.

**Inputs:**
- `data/intermediate/04_h1_results.rds`
- `data/intermediate/05_h2_results.rds`
- `data/intermediate/06_heterogeneity_results.rds`
- `data/intermediate/02_cleaned_data.rds`

**Outputs:**
- Final publication tables (HTML, TeX, PNG)
- Final publication figures

```{r setup, include=FALSE}
source("00_setup.R")
```

# Load Results

```{r load}
# Load model results from previous scripts
results_h1 <- readRDS(file.path(DATA_INTERMEDIATE, "04_h1_results.rds"))
results_h1_cont <- readRDS(file.path(DATA_INTERMEDIATE, "04_h1_results_continuous.rds"))
results_h2 <- readRDS(file.path(DATA_INTERMEDIATE, "05_h2_results.rds"))
results_h2_cont <- readRDS(file.path(DATA_INTERMEDIATE, "05_h2_results_continuous.rds"))
results_het <- readRDS(file.path(DATA_INTERMEDIATE, "06_heterogeneity_results.rds"))

# Load data for additional tables
data <- readRDS(file.path(DATA_INTERMEDIATE, "02_cleaned_data.rds"))

cat("Results loaded successfully.\n")
```

# Table 1: Main RDD Results

```{r table1}
rows_t1 <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7,
  'State FEs', '-', 'X', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', 'X', 'X', 'X', 'X', 'X',
  'Topic FEs', '-', '-', '-', 'X', 'X', 'X', 'X'
)
attr(rows_t1, 'position') <- c(3, 4, 5)

note_t1 <- "All standard errors are clustered at the source level. Models 1-4 uses the optimal bandwidth. Model 5 uses a linear specification with the full set of articles. Model 6 omits Military Topics. Model 7 omits NATO allies."

table_1 <- modelsummary(
  list(
    "(1)" = results_h1$model1_opt,
    "(2)" = results_h1$model2_opt,
    "(3)" = results_h1$model3_opt,
    "(4)" = results_h1$model4_opt,
    "(5)" = results_h1$model1_full_linear,
    "(6)" = results_h1$model4_non_mil,
    "(7)" = results_h1$model4_non_nato
  ),
  output = "gt",
  fmt = fmt_significant(3),
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c("treatment" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 1: Effect of Russian Invasion on Media Sentiment (RDD) with Day Running Variable",
  add_rows = rows_t1,
  notes = str_wrap(note_t1, 80)
)

table_1

gtsave(table_1, file.path(FIGURES_TABLES, "table_1.html"))
```

## Table 1 A: Continuous Running Variable

```{r table1a}
rows_t1a <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7,
  'State FEs', '-', 'X', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', 'X', 'X', 'X', 'X', 'X',
  'Topic FEs', '-', '-', '-', 'X', 'X', 'X', 'X'
)
attr(rows_t1a, 'position') <- c(3, 4, 5)

note_t1a <- "All standard errors are clustered at the source level. Models 1-4 uses the optimal bandwidth. Model 5 uses a linear specification with the full set of articles. Model 6 omits Military Topics. Model 7 omits NATO allies."

table_1_cont <- modelsummary(
  list(
    "(1)" = results_h1_cont$model1_opt,
    "(2)" = results_h1_cont$model2_opt,
    "(3)" = results_h1_cont$model3_opt,
    "(4)" = results_h1_cont$model4_opt,
    "(5)" = results_h1_cont$model1_full_linear,
    "(6)" = results_h1_cont$model4_non_mil,
    "(7)" = results_h1_cont$model4_non_nato
  ),
  output = "gt",
  fmt = fmt_significant(3),
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c("treatment" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 1A: Effect of Russian Invasion on Media Sentiment (RDD) with Continuous Running Variable",
  add_rows = rows_t1a,
  notes = str_wrap(note_t1a, 80)
)

table_1_cont

gtsave(table_1_cont, file.path(FIGURES_TABLES, "table_1_cont.html"))
```

## Table 1B: RDD By Topic (Day)

```{r table1b}
rows_t1b <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', 'X', 'X', 'X', 'X', 'X',
  'Topic FEs', '-', '-', '-', '-', '-'
)
attr(rows_t1b, 'position') <- c(3, 4, 5)

note_t1b <- "All standard errors are clustered at the source level. All models use the optimal bandwidth with country and source fixed effects."

table_1b <- modelsummary(
  list(
    "Political" = results_h1$model4_opt_pol,
    "Military" = results_h1$model4_opt_mil,
    "Economic" = results_h1$model4_opt_econ,
    "Cultural" = results_h1$model4_opt_cult,
    "Other" = results_h1$model4_opt_oth
  ),
  output = "gt",
  fmt = fmt_significant(3),
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c("treatment" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 1B: RDD By Topic (Day Running Variable)",
  add_rows = rows_t1b,
  notes = str_wrap(note_t1b, 80)
)

table_1b

gtsave(table_1b, file.path(FIGURES_TABLES, "table_1b.html"))
```

## Table 1C: RDD By Topic (Continuous)

```{r table1c}
rows_t1c <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', 'X', 'X', 'X', 'X', 'X',
  'Topic FEs', '-', '-', '-', '-', '-'
)
attr(rows_t1c, 'position') <- c(3, 4, 5)

note_t1c <- "All standard errors are clustered at the source level. All models use the optimal bandwidth with country and source fixed effects."

table_1c <- modelsummary(
  list(
    "Political" = results_h1_cont$model4_opt_pol,
    "Military" = results_h1_cont$model4_opt_mil,
    "Economic" = results_h1_cont$model4_opt_econ,
    "Cultural" = results_h1_cont$model4_opt_cult,
    "Other" = results_h1_cont$model4_opt_oth
  ),
  output = "gt",
  fmt = fmt_significant(3),
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c("treatment" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 1C: RDD By Topic (Continuous Running Variable)",
  add_rows = rows_t1c,
  notes = str_wrap(note_t1c, 80)
)

table_1c

gtsave(table_1c, file.path(FIGURES_TABLES, "table_1c.html"))
```

# Table 2: Diff-in-Disc Results

```{r table2}
rows_t2 <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6,
  'State FEs', 'X', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-', '-',
  'Topic FEs', 'X', 'X', 'X', 'X', 'X', 'X'
)
attr(rows_t2, 'position') <- c(5, 6, 7)

note_t2 <- "All standard errors are clustered at the source level. Model 2 uses the optimal bandwidth. Model 3 omits NATO allies. Model 4 omits military-related articles. Model 5 uses only Russian-related articles. Model 6 combines all robustness filters (non-NATO, non-military, Russian-related) with a re-optimized bandwidth."

table_2 <- modelsummary(
  list(
    "(1)" = results_h2$model2a,
    "(2)" = results_h2$model2a_opt,
    "(3)" = results_h2$model2d,
    "(4)" = results_h2$model2b,
    "(5)" = results_h2$model3a,
    "(6)" = results_h2$model3a_opt
  ),
  output = "gt",
  fmt = fmt_significant(3),
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 2: Difference in Discontinuities Analysis",
  add_rows = rows_t2,
  notes = str_wrap(note_t2, 80)
)

table_2

gtsave(table_2, file.path(FIGURES_TABLES, "table_2.html"))
```

## Table 2A: Diff-in-Disc (Continuous)

```{r table2a}
rows_t2a <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6,
  'State FEs', 'X', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-', '-',
  'Topic FEs', 'X', 'X', 'X', 'X', 'X', 'X'
)
attr(rows_t2a, 'position') <- c(5, 6, 7)

note_t2a <- "All standard errors are clustered at the source level. Model 2 uses the optimal bandwidth. Model 3 omits NATO allies. Model 4 omits military-related articles. Model 5 uses only Russian-related articles. Model 6 combines all robustness filters (non-NATO, non-military, Russian-related) with a re-optimized bandwidth."

table_2a <- modelsummary(
  list(
    "(1)" = results_h2_cont$model2a,
    "(2)" = results_h2_cont$model2a_opt,
    "(3)" = results_h2_cont$model2d,
    "(4)" = results_h2_cont$model2b,
    "(5)" = results_h2_cont$model3a,
    "(6)" = results_h2_cont$model3a_opt
  ),
  output = "gt",
  fmt = fmt_significant(3),
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 2A: Difference in Discontinuities (Continuous Running Variable)",
  add_rows = rows_t2a,
  notes = str_wrap(note_t2a, 80)
)

table_2a

gtsave(table_2a, file.path(FIGURES_TABLES, "table_2a.html"))
```

## Table 2B: Diff-in-Disc By Topic (Day)

```{r table2b}
rows_t2b <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-'
)
attr(rows_t2b, 'position') <- c(5, 6, 7)

note_t2b <- "All standard errors are clustered at the source level. All models use the optimal bandwidth with country fixed effects only."

table_2b <- modelsummary(
  list(
    "Political" = results_h2$model2a_opt_pol,
    "Military" = results_h2$model2a_opt_mil,
    "Economic" = results_h2$model2a_opt_econ,
    "Cultural" = results_h2$model2a_opt_cult,
    "Other" = results_h2$model2a_opt_oth
  ),
  output = "gt",
  fmt = fmt_significant(3),
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 2B: Diff-in-Disc By Topic (Day Running Variable)",
  add_rows = rows_t2b,
  notes = str_wrap(note_t2b, 80)
)

table_2b

gtsave(table_2b, file.path(FIGURES_TABLES, "table_2b.html"))
```

## Table 2C: Diff-in-Disc By Topic (Continuous)

```{r table2c}
rows_t2c <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-'
)
attr(rows_t2c, 'position') <- c(5, 6, 7)

note_t2c <- "All standard errors are clustered at the source level. All models use the optimal bandwidth with country fixed effects only."

table_2c <- modelsummary(
  list(
    "Political" = results_h2_cont$model2a_opt_pol,
    "Military" = results_h2_cont$model2a_opt_mil,
    "Economic" = results_h2_cont$model2a_opt_econ,
    "Cultural" = results_h2_cont$model2a_opt_cult,
    "Other" = results_h2_cont$model2a_opt_oth
  ),
  output = "gt",
  fmt = fmt_significant(3),
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 2C: Diff-in-Disc By Topic (Continuous Running Variable)",
  add_rows = rows_t2c,
  notes = str_wrap(note_t2c, 80)
)

table_2c

gtsave(table_2c, file.path(FIGURES_TABLES, "table_2c.html"))
```

# Table 3: Heterogeneity by Russian Alignment

```{r table3}
note_t3 <- "All standard errors are clustered at the source level. Model 2 uses the optimal bandwidth. Model 3 omits military-related articles. Sample restricted to state-owned media in non-NATO countries."

table_3 <- modelsummary(
  list(
    "(1)" = results_het$model5a,
    "(2)" = results_het$model5a_opt,
    "(3)" = results_het$model5a_non_mil
  ),
  output = "gt",
  fmt = fmt_significant(3),
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 3: Russian Alignment Heterogeneity (State Media)",
  notes = str_wrap(note_t3, 80)
)

table_3

gtsave(table_3, file.path(FIGURES_TABLES, "table_3.html"))
```

# Comparison Table: Countries by Alignment and Ethnic Population

```{r comparison-table}
get_group <- function(russian_group, security_group) {
  paste(intersect(russian_group, security_group), collapse = ", ")
}

table_data <- data.frame(
  `Ethnic Russian Population` = c("Low Ethnic", "High Ethnic"),
  `Low Russia Aligned` = c(
    get_group(LOW_RUSSIAN_POP, NEUTRAL_COUNTRIES),
    get_group(HIGH_RUSSIAN_POP, NEUTRAL_COUNTRIES)
  ),
  `High Russia Aligned` = c(
    get_group(LOW_RUSSIAN_POP, CSTO_COUNTRIES),
    get_group(HIGH_RUSSIAN_POP, CSTO_COUNTRIES)
  )
)

comparison_table <- table_data %>%
  gt() %>%
  tab_header(
    title = "Ethnic Russian Population x Russia Security Alignment",
    subtitle = "Country Classification"
  ) %>%
  cols_label(
    Ethnic.Russian.Population = "",
    Low.Russia.Aligned = "Low Alignment (Neutral)",
    High.Russia.Aligned = "High Alignment (CSTO)"
  ) %>%
  tab_style(
    style = cell_borders(sides = "all", color = "black", weight = px(1)),
    locations = cells_body()
  )

comparison_table

gtsave(comparison_table, file.path(FIGURES_TABLES, "comparison_table.html"))
```

# Alignment Table

```{r alignment-table}
alignment_table <- table_data %>%
  gt() %>%
  tab_header(
    title = "Ethnic Russian Population x Russia Security Alignment",
    subtitle = "Alignment Comparison"
  ) %>%
  cols_label(
    Ethnic.Russian.Population = "",
    Low.Russia.Aligned = "Low Alignment",
    High.Russia.Aligned = "High Alignment"
  ) %>%
  fmt_markdown(everything()) %>%
  tab_style(
    style = cell_borders(sides = c("top", "bottom"), color = "black", weight = px(2)),
    locations = cells_body(rows = 1:2, columns = 2:3)
  ) %>%
  tab_style(
    style = cell_borders(sides = c("left", "right"), color = "black", weight = px(2)),
    locations = cells_body(rows = 1:2, columns = 2:3)
  )

alignment_table

gtsave(alignment_table, file.path(FIGURES_TABLES, "alignment_table.html"))
```

# Ethnic Table

```{r ethnic-table}
ethnic_table <- table_data %>%
  gt() %>%
  tab_header(
    title = "Ethnic Russian Population x Russia Security Alignment",
    subtitle = "Ethnic Comparison"
  ) %>%
  cols_label(
    Ethnic.Russian.Population = "",
    Low.Russia.Aligned = "Low Alignment",
    High.Russia.Aligned = "High Alignment"
  ) %>%
  fmt_markdown(everything()) %>%
  tab_style(
    style = cell_borders(sides = "bottom", color = "black", weight = px(2)),
    locations = cells_body(rows = 1, columns = 2:3)
  ) %>%
  tab_style(
    style = cell_borders(sides = c("top", "bottom", "left", "right"), color = "black", weight = px(2)),
    locations = cells_body(rows = 1:2, columns = 2:3)
  )

ethnic_table

gtsave(ethnic_table, file.path(FIGURES_TABLES, "ethnic_table.html"))
```

# Export Tables to LaTeX

```{r latex-export}
# Function to save modelsummary as tex
save_tex <- function(models, filename, coef_map, title, rows = NULL, note = NULL) {
  modelsummary(
    models,
    output = file.path(FIGURES_TABLES, filename),
    fmt = fmt_significant(3),
    stars = c('*' = .05, '**' = .01, '***' = .001),
    coef_map = coef_map,
    gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
    title = title,
    add_rows = rows,
    notes = note
  )
}

# Note: These will generate .tex files for LaTeX inclusion
cat("LaTeX tables can be generated by changing output format to 'latex'\n")
```

# Summary of All Tables

```{r summary}
cat("\n")
cat("=============================================================\n")
cat("PUBLICATION OUTPUTS SUMMARY\n")
cat("=============================================================\n")
cat("\nTables generated:\n")
cat("  - table_1.html: Main RDD results (H1, day)\n")
cat("  - table_1_cont.html: Main RDD results (H1, continuous)\n")
cat("  - table_1b.html: RDD by topic (day)\n")
cat("  - table_1c.html: RDD by topic (continuous)\n")
cat("  - table_2.html: Diff-in-disc results (H2, day)\n")
cat("  - table_2a.html: Diff-in-disc results (H2, continuous)\n")
cat("  - table_2b.html: Diff-in-disc by topic (day)\n")
cat("  - table_2c.html: Diff-in-disc by topic (continuous)\n")
cat("  - table_3.html: Heterogeneity by alignment\n")
cat("  - comparison_table.html: Country classification\n")
cat("  - alignment_table.html: Alignment comparison\n")
cat("  - ethnic_table.html: Ethnic population comparison\n")
cat("\nFigures generated in previous scripts:\n")
cat("  - invasion_on_sentiment.png\n")
cat("  - invasion_on_sentiment_non_mil.png\n")
cat("  - invasion_discs_graph.png\n")
cat("  - invasion_discs_non_mil.png\n")
cat("  - state_align_discs.png\n")
cat("  - ethnic_discs.png\n")
cat("  - articles_per_day.png\n")
cat("  - topic_distribution.png\n")
cat("  - topic_split.png\n")
cat("=============================================================\n")
```
# Session Info

```{r session-info}
print_session_info()
```
