---
title: "07 - Publication Outputs"
author: "Donald Moratz"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

# Overview

This script generates all publication-quality tables and figures.

**Inputs:**
- `data/intermediate/04_h1_results.rds`
- `data/intermediate/04_h1_results_continuous.rds`
- `data/intermediate/04_h1_results_drop.rds`
- `data/intermediate/04_h1_results_prob.rds`
- `data/intermediate/05_h2_results.rds`
- `data/intermediate/05_h2_results_continuous.rds`
- `data/intermediate/05_h2_results_drop.rds`
- `data/intermediate/05_h2_results_prob.rds`
- `data/intermediate/06_heterogeneity_results.rds`
- `data/intermediate/06_heterogeneity_results_continuous.rds`
- `data/intermediate/06_heterogeneity_results_drop.rds`
- `data/intermediate/06_heterogeneity_results_prob.rds`
- `data/intermediate/02_cleaned_data.rds`

**Outputs:**
- Final publication tables (HTML, TeX, PNG)
- Final publication figures

```{r setup, include=FALSE}
source("00_setup.R")
```

# Load Results

```{r load}
# Load model results from previous scripts
results_h1 <- readRDS(file.path(DATA_INTERMEDIATE, "04_h1_results.rds"))
results_h1_cont <- readRDS(file.path(DATA_INTERMEDIATE, "04_h1_results_continuous.rds"))
results_h2 <- readRDS(file.path(DATA_INTERMEDIATE, "05_h2_results.rds"))
results_h2_cont <- readRDS(file.path(DATA_INTERMEDIATE, "05_h2_results_continuous.rds"))
results_het <- readRDS(file.path(DATA_INTERMEDIATE, "06_heterogeneity_results.rds"))
results_het_cont <- readRDS(file.path(DATA_INTERMEDIATE, "06_heterogeneity_results_continuous.rds"))

# Load drop variant results
results_h1_drop <- readRDS(file.path(DATA_INTERMEDIATE, "04_h1_results_drop.rds"))
results_h2_drop <- readRDS(file.path(DATA_INTERMEDIATE, "05_h2_results_drop.rds"))
results_het_drop <- readRDS(file.path(DATA_INTERMEDIATE, "06_heterogeneity_results_drop.rds"))

# Load probabilistic variant results
results_h1_prob <- readRDS(file.path(DATA_INTERMEDIATE, "04_h1_results_prob.rds"))
results_h2_prob <- readRDS(file.path(DATA_INTERMEDIATE, "05_h2_results_prob.rds"))
results_het_prob <- readRDS(file.path(DATA_INTERMEDIATE, "06_heterogeneity_results_prob.rds"))

# Load data for additional tables
data <- readRDS(file.path(DATA_INTERMEDIATE, "02_cleaned_data.rds"))

cat("Results loaded successfully.\n")
```

# Helper Functions for Bootstrap Standard Errors

```{r bootstrap-helpers}
# Helper function to create a vcov-like function that returns bootstrap SEs
# This allows modelsummary to display bootstrap standard errors
create_bootstrap_vcov <- function(model, boot_result, coef_name) {
  # Get the original vcov matrix
  original_vcov <- vcov(model)

  # Create a modified vcov matrix with bootstrap SE for the key coefficient
  modified_vcov <- original_vcov

  # Find the coefficient index
  coef_idx <- which(names(coef(model)) == coef_name)

  if (length(coef_idx) > 0 && !is.null(boot_result$se)) {
    # Replace the diagonal element with bootstrap variance (SE^2)
    modified_vcov[coef_idx, coef_idx] <- boot_result$se^2
  }

  return(modified_vcov)
}

# Helper to get significance stars from bootstrap p-value
get_boot_stars <- function(p_val) {
  if (is.null(p_val) || is.na(p_val)) return("")
  if (p_val < 0.001) return("***")
  if (p_val < 0.01) return("**")
  if (p_val < 0.05) return("*")
  return("")
}
```

# Table 1: Main RDD Results

```{r table1}
rows_t1 <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7,
  'State FEs', '-', 'X', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', 'X', 'X', 'X', 'X', 'X',
  'Topic FEs', '-', '-', '-', 'X', 'X', 'X', 'X'
)
attr(rows_t1, 'position') <- c(3, 4, 5)

note_t1 <- "All standard errors are clustered at the source level. Models 1-4 uses the optimal bandwidth. Model 5 uses a linear specification with the full set of articles. Model 6 omits Military Topics. Model 7 omits NATO allies."

table_1 <- modelsummary(
  list(
    "(1)" = results_h1$model1_opt,
    "(2)" = results_h1$model2_opt,
    "(3)" = results_h1$model3_opt,
    "(4)" = results_h1$model4_opt,
    "(5)" = results_h1$model1_full_linear,
    "(6)" = results_h1$model4_non_mil,
    "(7)" = results_h1$model4_non_nato
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c("treatment" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 1: Effect of Russian Invasion on Media Sentiment (RDD) with Day Running Variable",
  add_rows = rows_t1,
  notes = str_wrap(note_t1, 80)
)

table_1

gtsave(table_1, file.path(FIGURES_TABLES, "table_1.tex"))
```

## Table 1 A: Continuous Running Variable

```{r table1a}
rows_t1a <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7, ~row8,
  'State FEs', '-', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', 'X', 'X', 'X', 'X', 'X', 'X',
  'Topic FEs', '-', '-', '-', 'X', 'X', 'X', 'X', 'X'
)
attr(rows_t1a, 'position') <- c(3, 4, 5)

note_t1a <- "All standard errors are clustered at the source level. Models 1-4 uses the optimal bandwidth. Model 5 uses a linear specification with the full set of articles. Model 6 omits Military Topics. Model 7 omits NATO allies. Model 8 uses full saturation (country-source-topic FEs)."

table_1_cont <- modelsummary(
  list(
    "(1)" = results_h1_cont$model1_opt,
    "(2)" = results_h1_cont$model2_opt,
    "(3)" = results_h1_cont$model3_opt,
    "(4)" = results_h1_cont$model4_opt,
    "(5)" = results_h1_cont$model1_full_linear,
    "(6)" = results_h1_cont$model4_non_mil,
    "(7)" = results_h1_cont$model4_non_nato,
    "(8)" = results_h1_cont$model4_felm_saturated
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c("treatment" = "Invasion", "post" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 1A: Effect of Russian Invasion on Media Sentiment (RDD) with Continuous Running Variable",
  add_rows = rows_t1a,
  notes = str_wrap(note_t1a, 80)
)

table_1_cont

gtsave(table_1_cont, file.path(FIGURES_TABLES, "table_1_cont.tex"))
```

## Table 1B: RDD By Topic (Day)

```{r table1b}
rows_t1b <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', 'X', 'X', 'X', 'X', 'X',
  'Topic FEs', '-', '-', '-', '-', '-'
)
attr(rows_t1b, 'position') <- c(3, 4, 5)

note_t1b <- "All standard errors are clustered at the source level. All models use the optimal bandwidth with country and source fixed effects."

table_1b <- modelsummary(
  list(
    "Political" = results_h1$model4_opt_pol,
    "Military" = results_h1$model4_opt_mil,
    "Economic" = results_h1$model4_opt_econ,
    "Cultural" = results_h1$model4_opt_cult,
    "Other" = results_h1$model4_opt_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c("treatment" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 1B: RDD By Topic (Day Running Variable)",
  add_rows = rows_t1b,
  notes = str_wrap(note_t1b, 80)
)

table_1b

gtsave(table_1b, file.path(FIGURES_TABLES, "table_1b.tex"))
```

## Table 1C: RDD By Topic (Continuous)

```{r table1c}
rows_t1c <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', 'X', 'X', 'X', 'X', 'X',
  'Topic FEs', '-', '-', '-', '-', '-'
)
attr(rows_t1c, 'position') <- c(3, 4, 5)

note_t1c <- "All standard errors are clustered at the source level. All models use the optimal bandwidth with country and source fixed effects."

table_1c <- modelsummary(
  list(
    "Political" = results_h1_cont$model4_opt_pol,
    "Military" = results_h1_cont$model4_opt_mil,
    "Economic" = results_h1_cont$model4_opt_econ,
    "Cultural" = results_h1_cont$model4_opt_cult,
    "Other" = results_h1_cont$model4_opt_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c("treatment" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 1C: RDD By Topic (Continuous Running Variable)",
  add_rows = rows_t1c,
  notes = str_wrap(note_t1c, 80)
)

table_1c

gtsave(table_1c, file.path(FIGURES_TABLES, "table_1c.tex"))
```

# Table 2: Diff-in-Disc Results

```{r table2}
rows_t2 <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6,
  'State FEs', 'X', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-', '-',
  'Topic FEs', 'X', 'X', 'X', 'X', 'X', 'X'
)
attr(rows_t2, 'position') <- c(5, 6, 7)

note_t2 <- "All standard errors are clustered at the source level. Model 2 uses the optimal bandwidth. Model 3 omits NATO allies. Model 4 omits military-related articles. Model 5 uses only Russian-related articles. Model 6 combines all robustness filters (non-NATO, non-military, Russian-related) with a re-optimized bandwidth."

table_2 <- modelsummary(
  list(
    "(1)" = results_h2$model2a,
    "(2)" = results_h2$model2a_opt,
    "(3)" = results_h2$model2d,
    "(4)" = results_h2$model2b,
    "(5)" = results_h2$model3a,
    "(6)" = results_h2$model3a_opt
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 2: Difference in Discontinuities Analysis",
  add_rows = rows_t2,
  notes = str_wrap(note_t2, 80)
)

table_2

gtsave(table_2, file.path(FIGURES_TABLES, "table_2.tex"))
```

## Table 2A: Diff-in-Disc (Continuous)

```{r table2a}
rows_t2a <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7,
  'State FEs', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-', '-', 'X',
  'Topic FEs', 'X', 'X', 'X', 'X', 'X', 'X', 'X'
)
attr(rows_t2a, 'position') <- c(5, 6, 7)

note_t2a <- "All standard errors are clustered at the source level. Model 2 uses the optimal bandwidth. Model 3 omits NATO allies. Model 4 omits military-related articles. Model 5 uses only Russian-related articles. Model 6 combines all robustness filters (non-NATO, non-military, Russian-related) with a re-optimized bandwidth. Model 7 uses full saturation (source-topic and country-state-topic FEs)."

table_2a <- modelsummary(
  list(
    "(1)" = results_h2_cont$model2a,
    "(2)" = results_h2_cont$model2a_opt,
    "(3)" = results_h2_cont$model2d,
    "(4)" = results_h2_cont$model2b,
    "(5)" = results_h2_cont$model3a,
    "(6)" = results_h2_cont$model3a_opt,
    "(7)" = results_h2_cont$model3a_opt_saturated
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 2A: Difference in Discontinuities (Continuous Running Variable)",
  add_rows = rows_t2a,
  notes = str_wrap(note_t2a, 80)
)

table_2a

gtsave(table_2a, file.path(FIGURES_TABLES, "table_2a.tex"))
```

## Table 2B: Diff-in-Disc By Topic (Day)

```{r table2b}
rows_t2b <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-'
)
attr(rows_t2b, 'position') <- c(5, 6, 7)

note_t2b <- "All standard errors are clustered at the source level. All models use a per-topic re-optimized bandwidth with country fixed effects only."

table_2b <- modelsummary(
  list(
    "Political" = results_h2$model2a_opt_pol,
    "Military" = results_h2$model2a_opt_mil,
    "Economic" = results_h2$model2a_opt_econ,
    "Cultural" = results_h2$model2a_opt_cult,
    "Other" = results_h2$model2a_opt_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 2B: Diff-in-Disc By Topic (Day Running Variable)",
  add_rows = rows_t2b,
  notes = str_wrap(note_t2b, 80)
)

table_2b

gtsave(table_2b, file.path(FIGURES_TABLES, "table_2b.tex"))
```

## Table 2C: Diff-in-Disc By Topic (Continuous)

```{r table2c}
rows_t2c <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-'
)
attr(rows_t2c, 'position') <- c(5, 6, 7)

note_t2c <- "All standard errors are clustered at the source level. All models use a per-topic re-optimized bandwidth with country fixed effects only."

table_2c <- modelsummary(
  list(
    "Political" = results_h2_cont$model2a_opt_pol,
    "Military" = results_h2_cont$model2a_opt_mil,
    "Economic" = results_h2_cont$model2a_opt_econ,
    "Cultural" = results_h2_cont$model2a_opt_cult,
    "Other" = results_h2_cont$model2a_opt_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 2C: Diff-in-Disc By Topic (Continuous Running Variable)",
  add_rows = rows_t2c,
  notes = str_wrap(note_t2c, 80)
)

table_2c

gtsave(table_2c, file.path(FIGURES_TABLES, "table_2c.tex"))
```

## Table 2D: Diff-in-Disc By Topic Full Data (Day)

```{r table2d}
rows_t2d <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-'
)
attr(rows_t2d, 'position') <- c(5, 6, 7)

note_t2d <- "All standard errors are clustered at the source level. All models use the full dataset (no bandwidth restriction) with country fixed effects only."

table_2d <- modelsummary(
  list(
    "Political" = results_h2$model2a_full_pol,
    "Military" = results_h2$model2a_full_mil,
    "Economic" = results_h2$model2a_full_econ,
    "Cultural" = results_h2$model2a_full_cult,
    "Other" = results_h2$model2a_full_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 2D: Diff-in-Disc By Topic Full Data (Day Running Variable)",
  add_rows = rows_t2d,
  notes = str_wrap(note_t2d, 80)
)

table_2d

gtsave(table_2d, file.path(FIGURES_TABLES, "table_2d.tex"))
```

## Table 2E: Diff-in-Disc By Topic Full Data (Continuous)

```{r table2e}
rows_t2e <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-'
)
attr(rows_t2e, 'position') <- c(5, 6, 7)

note_t2e <- "All standard errors are clustered at the source level. All models use the full dataset (no bandwidth restriction) with country fixed effects only."

table_2e <- modelsummary(
  list(
    "Political" = results_h2_cont$model2a_full_pol,
    "Military" = results_h2_cont$model2a_full_mil,
    "Economic" = results_h2_cont$model2a_full_econ,
    "Cultural" = results_h2_cont$model2a_full_cult,
    "Other" = results_h2_cont$model2a_full_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 2E: Diff-in-Disc By Topic Full Data (Continuous Running Variable)",
  add_rows = rows_t2e,
  notes = str_wrap(note_t2e, 80)
)

table_2e

gtsave(table_2e, file.path(FIGURES_TABLES, "table_2e.tex"))
```

# Table 3: Heterogeneity by Russian Alignment

```{r table3}
note_t3 <- "Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights) for Models 3-7, clustered at source level. Models 1-2 use rdrobust standard errors. Model 1 shows RDD results for CSTO countries only. Model 2 shows RDD results for Neutral countries only. Model 3 uses full data with topic fixed effects. Model 4 uses the optimal bandwidth with topic fixed effects. Model 5 omits military-related articles and uses a re-optimized bandwidth. Model 6 uses only Russian-related (non-military) articles with a re-optimized bandwidth. Model 7 uses full saturation (country-source-topic FEs). Sample restricted to state-owned media in non-NATO countries."

# Create vcov list with bootstrap SEs for felm models (columns 3-7)
vcov_t3 <- list(
  "(3)" = create_bootstrap_vcov(results_het$model5a_full, results_het$bootstrap_se$model5a_full, "treatment:csto"),
  "(4)" = create_bootstrap_vcov(results_het$model5a_opt, results_het$bootstrap_se$model5a_opt, "treatment:csto"),
  "(5)" = create_bootstrap_vcov(results_het$model5a_opt_non_mil, results_het$bootstrap_se$model5a_opt_non_mil, "treatment:csto"),
  "(6)" = create_bootstrap_vcov(results_het$model5a_opt_russian, results_het$bootstrap_se$model5a_opt_russian, "treatment:csto"),
  "(7)" = create_bootstrap_vcov(results_het$model5a_fully_saturated, results_het$bootstrap_se$model5a_fully_saturated, "treatment:csto")
)

table_3 <- modelsummary(
  list(
    "(1)" = results_het$model5a_csto,
    "(2)" = results_het$model5a_neutral,
    "(3)" = results_het$model5a_full,
    "(4)" = results_het$model5a_opt,
    "(5)" = results_het$model5a_opt_non_mil,
    "(6)" = results_het$model5a_opt_russian,
    "(7)" = results_het$model5a_fully_saturated
  ),
  vcov = vcov_t3,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 3: Russian Alignment Heterogeneity (State Media)",
  notes = str_wrap(note_t3, 80)
)

table_3

gtsave(table_3, file.path(FIGURES_TABLES, "table_3.tex"))
```

## Table 3A: Heterogeneity (Continuous)

```{r table3a}
note_t3a <- "Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights) for Models 3-6, clustered at source level. Models 1-2 use rdrobust standard errors. Model 1 shows RDD results for CSTO countries only. Model 2 shows RDD results for Neutral countries only. Model 3 uses full data with topic fixed effects. Model 4 uses the optimal bandwidth with topic fixed effects. Model 5 omits military-related articles and uses a re-optimized bandwidth. Model 6 uses only Russian-related (non-military) articles with a re-optimized bandwidth. Sample restricted to state-owned media in non-NATO countries."

# Create vcov list with bootstrap SEs for felm models
vcov_t3a <- list(
  "(3)" = create_bootstrap_vcov(results_het_cont$model5a_full, results_het_cont$bootstrap_se$model5a_full, "treatment:csto"),
  "(4)" = create_bootstrap_vcov(results_het_cont$model5a_opt, results_het_cont$bootstrap_se$model5a_opt, "treatment:csto"),
  "(5)" = create_bootstrap_vcov(results_het_cont$model5a_opt_non_mil, results_het_cont$bootstrap_se$model5a_opt_non_mil, "treatment:csto"),
  "(6)" = create_bootstrap_vcov(results_het_cont$model5a_opt_russian, results_het_cont$bootstrap_se$model5a_opt_russian, "treatment:csto")
)

table_3a <- modelsummary(
  list(
    "(1)" = results_het_cont$model5a_csto,
    "(2)" = results_het_cont$model5a_neutral,
    "(3)" = results_het_cont$model5a_full,
    "(4)" = results_het_cont$model5a_opt,
    "(5)" = results_het_cont$model5a_opt_non_mil,
    "(6)" = results_het_cont$model5a_opt_russian
  ),
  vcov = vcov_t3a,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 3A: Russian Alignment Heterogeneity (Continuous Running Variable)",
  notes = str_wrap(note_t3a, 80)
)

table_3a

gtsave(table_3a, file.path(FIGURES_TABLES, "table_3a.tex"))
```

## Table 3B: Heterogeneity By Topic Optimal BW (Day)

```{r table3b}
note_t3b <- "Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights), clustered at source level. Each model uses a per-topic re-optimized bandwidth. State media in non-NATO countries only."

# Create vcov list with bootstrap SEs for topic models
vcov_t3b <- list(
  "Political" = create_bootstrap_vcov(results_het$model5a_opt_pol, results_het$bootstrap_se$model5a_opt_pol, "treatment:csto"),
  "Military" = create_bootstrap_vcov(results_het$model5a_opt_mil, results_het$bootstrap_se$model5a_opt_mil, "treatment:csto"),
  "Economic" = create_bootstrap_vcov(results_het$model5a_opt_econ, results_het$bootstrap_se$model5a_opt_econ, "treatment:csto"),
  "Cultural" = create_bootstrap_vcov(results_het$model5a_opt_cult, results_het$bootstrap_se$model5a_opt_cult, "treatment:csto"),
  "Other" = create_bootstrap_vcov(results_het$model5a_opt_oth, results_het$bootstrap_se$model5a_opt_oth, "treatment:csto")
)

table_3b <- modelsummary(
  list(
    "Political" = results_het$model5a_opt_pol,
    "Military" = results_het$model5a_opt_mil,
    "Economic" = results_het$model5a_opt_econ,
    "Cultural" = results_het$model5a_opt_cult,
    "Other" = results_het$model5a_opt_oth
  ),
  vcov = vcov_t3b,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 3B: Heterogeneity By Topic (Per-Topic Optimal BW, Day)",
  notes = str_wrap(note_t3b, 80)
)

table_3b

gtsave(table_3b, file.path(FIGURES_TABLES, "table_3b.tex"))
```

## Table 3C: Heterogeneity By Topic Optimal BW (Continuous)

```{r table3c}
note_t3c <- "Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights), clustered at source level. Each model uses a per-topic re-optimized bandwidth. State media in non-NATO countries only."

# Create vcov list with bootstrap SEs for topic models
vcov_t3c <- list(
  "Political" = create_bootstrap_vcov(results_het_cont$model5a_opt_pol, results_het_cont$bootstrap_se$model5a_opt_pol, "treatment:csto"),
  "Military" = create_bootstrap_vcov(results_het_cont$model5a_opt_mil, results_het_cont$bootstrap_se$model5a_opt_mil, "treatment:csto"),
  "Economic" = create_bootstrap_vcov(results_het_cont$model5a_opt_econ, results_het_cont$bootstrap_se$model5a_opt_econ, "treatment:csto"),
  "Cultural" = create_bootstrap_vcov(results_het_cont$model5a_opt_cult, results_het_cont$bootstrap_se$model5a_opt_cult, "treatment:csto"),
  "Other" = create_bootstrap_vcov(results_het_cont$model5a_opt_oth, results_het_cont$bootstrap_se$model5a_opt_oth, "treatment:csto")
)

table_3c <- modelsummary(
  list(
    "Political" = results_het_cont$model5a_opt_pol,
    "Military" = results_het_cont$model5a_opt_mil,
    "Economic" = results_het_cont$model5a_opt_econ,
    "Cultural" = results_het_cont$model5a_opt_cult,
    "Other" = results_het_cont$model5a_opt_oth
  ),
  vcov = vcov_t3c,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 3C: Heterogeneity By Topic (Per-Topic Optimal BW, Continuous)",
  notes = str_wrap(note_t3c, 80)
)

table_3c

gtsave(table_3c, file.path(FIGURES_TABLES, "table_3c.tex"))
```

## Table 3D: Heterogeneity By Topic Full Data (Day)

```{r table3d}
note_t3d <- "Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights), clustered at source level. Each model uses the full dataset (no bandwidth restriction). State media in non-NATO countries only."

# Create vcov list with bootstrap SEs for topic models
vcov_t3d <- list(
  "Political" = create_bootstrap_vcov(results_het$model5a_full_pol, results_het$bootstrap_se$model5a_full_pol, "treatment:csto"),
  "Military" = create_bootstrap_vcov(results_het$model5a_full_mil, results_het$bootstrap_se$model5a_full_mil, "treatment:csto"),
  "Economic" = create_bootstrap_vcov(results_het$model5a_full_econ, results_het$bootstrap_se$model5a_full_econ, "treatment:csto"),
  "Cultural" = create_bootstrap_vcov(results_het$model5a_full_cult, results_het$bootstrap_se$model5a_full_cult, "treatment:csto"),
  "Other" = create_bootstrap_vcov(results_het$model5a_full_oth, results_het$bootstrap_se$model5a_full_oth, "treatment:csto")
)

table_3d <- modelsummary(
  list(
    "Political" = results_het$model5a_full_pol,
    "Military" = results_het$model5a_full_mil,
    "Economic" = results_het$model5a_full_econ,
    "Cultural" = results_het$model5a_full_cult,
    "Other" = results_het$model5a_full_oth
  ),
  vcov = vcov_t3d,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 3D: Heterogeneity By Topic (Full Data, Day)",
  notes = str_wrap(note_t3d, 80)
)

table_3d

gtsave(table_3d, file.path(FIGURES_TABLES, "table_3d.tex"))
```

## Table 3E: Heterogeneity By Topic Full Data (Continuous)

```{r table3e}
note_t3e <- "Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights), clustered at source level. Each model uses the full dataset (no bandwidth restriction). State media in non-NATO countries only."

# Create vcov list with bootstrap SEs for topic models
vcov_t3e <- list(
  "Political" = create_bootstrap_vcov(results_het_cont$model5a_full_pol, results_het_cont$bootstrap_se$model5a_full_pol, "treatment:csto"),
  "Military" = create_bootstrap_vcov(results_het_cont$model5a_full_mil, results_het_cont$bootstrap_se$model5a_full_mil, "treatment:csto"),
  "Economic" = create_bootstrap_vcov(results_het_cont$model5a_full_econ, results_het_cont$bootstrap_se$model5a_full_econ, "treatment:csto"),
  "Cultural" = create_bootstrap_vcov(results_het_cont$model5a_full_cult, results_het_cont$bootstrap_se$model5a_full_cult, "treatment:csto"),
  "Other" = create_bootstrap_vcov(results_het_cont$model5a_full_oth, results_het_cont$bootstrap_se$model5a_full_oth, "treatment:csto")
)

table_3e <- modelsummary(
  list(
    "Political" = results_het_cont$model5a_full_pol,
    "Military" = results_het_cont$model5a_full_mil,
    "Economic" = results_het_cont$model5a_full_econ,
    "Cultural" = results_het_cont$model5a_full_cult,
    "Other" = results_het_cont$model5a_full_oth
  ),
  vcov = vcov_t3e,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 3E: Heterogeneity By Topic (Full Data, Continuous)",
  notes = str_wrap(note_t3e, 80)
)

table_3e

gtsave(table_3e, file.path(FIGURES_TABLES, "table_3e.tex"))
```

# Table 4: Heterogeneity by Ethnic Russian Population

```{r table4}
note_t4 <- "Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights), clustered at source level. Model 1 uses full data with topic fixed effects. Model 2 uses the optimal bandwidth with topic fixed effects. Model 3 omits military-related articles and uses a re-optimized bandwidth. Model 4 uses only Russian-related (non-military) articles with a re-optimized bandwidth. Sample restricted to state-owned media in non-NATO countries."

# Create vcov list with bootstrap SEs for all models
vcov_t4 <- list(
  "(1)" = create_bootstrap_vcov(results_het$model6a_full, results_het$bootstrap_se$model6a_full, "treatment:high_russia"),
  "(2)" = create_bootstrap_vcov(results_het$model6a_opt, results_het$bootstrap_se$model6a_opt, "treatment:high_russia"),
  "(3)" = create_bootstrap_vcov(results_het$model6a_opt_non_mil, results_het$bootstrap_se$model6a_opt_non_mil, "treatment:high_russia"),
  "(4)" = create_bootstrap_vcov(results_het$model6a_opt_russian, results_het$bootstrap_se$model6a_opt_russian, "treatment:high_russia")
)

table_4 <- modelsummary(
  list(
    "(1)" = results_het$model6a_full,
    "(2)" = results_het$model6a_opt,
    "(3)" = results_het$model6a_opt_non_mil,
    "(4)" = results_het$model6a_opt_russian
  ),
  vcov = vcov_t4,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 4: Ethnic Russian Population Heterogeneity (State Media)",
  notes = str_wrap(note_t4, 80)
)

table_4

gtsave(table_4, file.path(FIGURES_TABLES, "table_4.tex"))
```

## Table 4A: Ethnic Heterogeneity (Continuous)

```{r table4a}
note_t4a <- "Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights), clustered at source level. Model 1 uses full data with topic fixed effects. Model 2 uses the optimal bandwidth with topic fixed effects. Model 3 omits military-related articles and uses a re-optimized bandwidth. Model 4 uses only Russian-related (non-military) articles with a re-optimized bandwidth. Sample restricted to state-owned media in non-NATO countries."

# Create vcov list with bootstrap SEs
vcov_t4a <- list(
  "(1)" = create_bootstrap_vcov(results_het_cont$model6a_full, results_het_cont$bootstrap_se$model6a_full, "treatment:high_russia"),
  "(2)" = create_bootstrap_vcov(results_het_cont$model6a_opt, results_het_cont$bootstrap_se$model6a_opt, "treatment:high_russia"),
  "(3)" = create_bootstrap_vcov(results_het_cont$model6a_opt_non_mil, results_het_cont$bootstrap_se$model6a_opt_non_mil, "treatment:high_russia"),
  "(4)" = create_bootstrap_vcov(results_het_cont$model6a_opt_russian, results_het_cont$bootstrap_se$model6a_opt_russian, "treatment:high_russia")
)

table_4a <- modelsummary(
  list(
    "(1)" = results_het_cont$model6a_full,
    "(2)" = results_het_cont$model6a_opt,
    "(3)" = results_het_cont$model6a_opt_non_mil,
    "(4)" = results_het_cont$model6a_opt_russian
  ),
  vcov = vcov_t4a,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 4A: Ethnic Russian Population Heterogeneity (Continuous Running Variable)",
  notes = str_wrap(note_t4a, 80)
)

table_4a

gtsave(table_4a, file.path(FIGURES_TABLES, "table_4a.tex"))
```

## Table 4B: Ethnic By Topic Optimal BW (Day)

```{r table4b}
note_t4b <- "Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights), clustered at source level. Each model uses a per-topic re-optimized bandwidth. State media in non-NATO countries only."

# Create vcov list with bootstrap SEs for topic models
vcov_t4b <- list(
  "Political" = create_bootstrap_vcov(results_het$model6a_opt_pol, results_het$bootstrap_se$model6a_opt_pol, "treatment:high_russia"),
  "Military" = create_bootstrap_vcov(results_het$model6a_opt_mil, results_het$bootstrap_se$model6a_opt_mil, "treatment:high_russia"),
  "Economic" = create_bootstrap_vcov(results_het$model6a_opt_econ, results_het$bootstrap_se$model6a_opt_econ, "treatment:high_russia"),
  "Cultural" = create_bootstrap_vcov(results_het$model6a_opt_cult, results_het$bootstrap_se$model6a_opt_cult, "treatment:high_russia"),
  "Other" = create_bootstrap_vcov(results_het$model6a_opt_oth, results_het$bootstrap_se$model6a_opt_oth, "treatment:high_russia")
)

table_4b <- modelsummary(
  list(
    "Political" = results_het$model6a_opt_pol,
    "Military" = results_het$model6a_opt_mil,
    "Economic" = results_het$model6a_opt_econ,
    "Cultural" = results_het$model6a_opt_cult,
    "Other" = results_het$model6a_opt_oth
  ),
  vcov = vcov_t4b,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 4B: Ethnic Heterogeneity By Topic (Per-Topic Optimal BW, Day)",
  notes = str_wrap(note_t4b, 80)
)

table_4b

gtsave(table_4b, file.path(FIGURES_TABLES, "table_4b.tex"))
```

## Table 4C: Ethnic By Topic Optimal BW (Continuous)

```{r table4c}
note_t4c <- "Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights), clustered at source level. Each model uses a per-topic re-optimized bandwidth. State media in non-NATO countries only."

# Create vcov list with bootstrap SEs for topic models
vcov_t4c <- list(
  "Political" = create_bootstrap_vcov(results_het_cont$model6a_opt_pol, results_het_cont$bootstrap_se$model6a_opt_pol, "treatment:high_russia"),
  "Military" = create_bootstrap_vcov(results_het_cont$model6a_opt_mil, results_het_cont$bootstrap_se$model6a_opt_mil, "treatment:high_russia"),
  "Economic" = create_bootstrap_vcov(results_het_cont$model6a_opt_econ, results_het_cont$bootstrap_se$model6a_opt_econ, "treatment:high_russia"),
  "Cultural" = create_bootstrap_vcov(results_het_cont$model6a_opt_cult, results_het_cont$bootstrap_se$model6a_opt_cult, "treatment:high_russia"),
  "Other" = create_bootstrap_vcov(results_het_cont$model6a_opt_oth, results_het_cont$bootstrap_se$model6a_opt_oth, "treatment:high_russia")
)

table_4c <- modelsummary(
  list(
    "Political" = results_het_cont$model6a_opt_pol,
    "Military" = results_het_cont$model6a_opt_mil,
    "Economic" = results_het_cont$model6a_opt_econ,
    "Cultural" = results_het_cont$model6a_opt_cult,
    "Other" = results_het_cont$model6a_opt_oth
  ),
  vcov = vcov_t4c,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 4C: Ethnic Heterogeneity By Topic (Per-Topic Optimal BW, Continuous)",
  notes = str_wrap(note_t4c, 80)
)

table_4c

gtsave(table_4c, file.path(FIGURES_TABLES, "table_4c.tex"))
```

## Table 4D: Ethnic By Topic Full Data (Day)

```{r table4d}
note_t4d <- "Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights), clustered at source level. Each model uses the full dataset (no bandwidth restriction). State media in non-NATO countries only."

# Create vcov list with bootstrap SEs for topic models
vcov_t4d <- list(
  "Political" = create_bootstrap_vcov(results_het$model6a_full_pol, results_het$bootstrap_se$model6a_full_pol, "treatment:high_russia"),
  "Military" = create_bootstrap_vcov(results_het$model6a_full_mil, results_het$bootstrap_se$model6a_full_mil, "treatment:high_russia"),
  "Economic" = create_bootstrap_vcov(results_het$model6a_full_econ, results_het$bootstrap_se$model6a_full_econ, "treatment:high_russia"),
  "Cultural" = create_bootstrap_vcov(results_het$model6a_full_cult, results_het$bootstrap_se$model6a_full_cult, "treatment:high_russia"),
  "Other" = create_bootstrap_vcov(results_het$model6a_full_oth, results_het$bootstrap_se$model6a_full_oth, "treatment:high_russia")
)

table_4d <- modelsummary(
  list(
    "Political" = results_het$model6a_full_pol,
    "Military" = results_het$model6a_full_mil,
    "Economic" = results_het$model6a_full_econ,
    "Cultural" = results_het$model6a_full_cult,
    "Other" = results_het$model6a_full_oth
  ),
  vcov = vcov_t4d,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 4D: Ethnic Heterogeneity By Topic (Full Data, Day)",
  notes = str_wrap(note_t4d, 80)
)

table_4d

gtsave(table_4d, file.path(FIGURES_TABLES, "table_4d.tex"))
```

## Table 4E: Ethnic By Topic Full Data (Continuous)

```{r table4e}
note_t4e <- "Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights), clustered at source level. Each model uses the full dataset (no bandwidth restriction). State media in non-NATO countries only."

# Create vcov list with bootstrap SEs for topic models
vcov_t4e <- list(
  "Political" = create_bootstrap_vcov(results_het_cont$model6a_full_pol, results_het_cont$bootstrap_se$model6a_full_pol, "treatment:high_russia"),
  "Military" = create_bootstrap_vcov(results_het_cont$model6a_full_mil, results_het_cont$bootstrap_se$model6a_full_mil, "treatment:high_russia"),
  "Economic" = create_bootstrap_vcov(results_het_cont$model6a_full_econ, results_het_cont$bootstrap_se$model6a_full_econ, "treatment:high_russia"),
  "Cultural" = create_bootstrap_vcov(results_het_cont$model6a_full_cult, results_het_cont$bootstrap_se$model6a_full_cult, "treatment:high_russia"),
  "Other" = create_bootstrap_vcov(results_het_cont$model6a_full_oth, results_het_cont$bootstrap_se$model6a_full_oth, "treatment:high_russia")
)

table_4e <- modelsummary(
  list(
    "Political" = results_het_cont$model6a_full_pol,
    "Military" = results_het_cont$model6a_full_mil,
    "Economic" = results_het_cont$model6a_full_econ,
    "Cultural" = results_het_cont$model6a_full_cult,
    "Other" = results_het_cont$model6a_full_oth
  ),
  vcov = vcov_t4e,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 4E: Ethnic Heterogeneity By Topic (Full Data, Continuous)",
  notes = str_wrap(note_t4e, 80)
)

table_4e

gtsave(table_4e, file.path(FIGURES_TABLES, "table_4e.tex"))
```

# Drop No-Time Articles Variant Tables

## Table 1D: RDD Main (Drop No-Time)

```{r table1d}
rows_t1d <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7, ~row8,
  'State FEs', '-', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', 'X', 'X', 'X', 'X', 'X', 'X',
  'Topic FEs', '-', '-', '-', 'X', 'X', 'X', 'X', 'X'
)
attr(rows_t1d, 'position') <- c(3, 4, 5)

note_t1d <- "All standard errors are clustered at the source level. Articles without publication times are dropped. Models 1-4 uses the optimal bandwidth. Model 5 uses a linear specification with the full set of articles. Model 6 omits Military Topics. Model 7 omits NATO allies. Model 8 uses full saturation (country-source-topic FEs)."

table_1d <- modelsummary(
  list(
    "(1)" = results_h1_drop$model1_opt,
    "(2)" = results_h1_drop$model2_opt,
    "(3)" = results_h1_drop$model3_opt,
    "(4)" = results_h1_drop$model4_opt,
    "(5)" = results_h1_drop$model1_full_linear,
    "(6)" = results_h1_drop$model4_non_mil,
    "(7)" = results_h1_drop$model4_non_nato,
    "(8)" = results_h1_drop$model4_felm_saturated
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c("treatment" = "Invasion", "post" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 1D: RDD with Continuous Running Variable (Drop No-Time Articles)",
  add_rows = rows_t1d,
  notes = str_wrap(note_t1d, 80)
)

table_1d

gtsave(table_1d, file.path(FIGURES_TABLES, "table_1d.tex"))
```

## Table 1E: RDD By Topic (Drop No-Time)

```{r table1e}
rows_t1e <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', 'X', 'X', 'X', 'X', 'X',
  'Topic FEs', '-', '-', '-', '-', '-'
)
attr(rows_t1e, 'position') <- c(3, 4, 5)

note_t1e <- "All standard errors are clustered at the source level. Articles without publication times are dropped. All models use the optimal bandwidth with country and source fixed effects."

table_1e <- modelsummary(
  list(
    "Political" = results_h1_drop$model4_opt_pol,
    "Military" = results_h1_drop$model4_opt_mil,
    "Economic" = results_h1_drop$model4_opt_econ,
    "Cultural" = results_h1_drop$model4_opt_cult,
    "Other" = results_h1_drop$model4_opt_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c("treatment" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 1E: RDD By Topic (Drop No-Time Articles)",
  add_rows = rows_t1e,
  notes = str_wrap(note_t1e, 80)
)

table_1e

gtsave(table_1e, file.path(FIGURES_TABLES, "table_1e.tex"))
```

## Table 2F: Diff-in-Disc Main (Drop No-Time)

```{r table2f}
rows_t2f <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7,
  'State FEs', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-', '-', 'X',
  'Topic FEs', 'X', 'X', 'X', 'X', 'X', 'X', 'X'
)
attr(rows_t2f, 'position') <- c(5, 6, 7)

note_t2f <- "All standard errors are clustered at the source level. Articles without publication times are dropped. Model 2 uses the optimal bandwidth. Model 3 omits NATO allies. Model 4 omits military-related articles. Model 5 uses only Russian-related articles. Model 6 combines all robustness filters with a re-optimized bandwidth. Model 7 uses full saturation (source-topic and country-state-topic FEs)."

table_2f <- modelsummary(
  list(
    "(1)" = results_h2_drop$model2a,
    "(2)" = results_h2_drop$model2a_opt,
    "(3)" = results_h2_drop$model2d,
    "(4)" = results_h2_drop$model2b,
    "(5)" = results_h2_drop$model3a,
    "(6)" = results_h2_drop$model3a_opt,
    "(7)" = results_h2_drop$model3a_opt_saturated
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 2F: Diff-in-Disc (Drop No-Time Articles)",
  add_rows = rows_t2f,
  notes = str_wrap(note_t2f, 80)
)

table_2f

gtsave(table_2f, file.path(FIGURES_TABLES, "table_2f.tex"))
```

## Table 2G: Diff-in-Disc By Topic Optimal BW (Drop No-Time)

```{r table2g}
rows_t2g <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-'
)
attr(rows_t2g, 'position') <- c(5, 6, 7)

note_t2g <- "All standard errors are clustered at the source level. Articles without publication times are dropped. All models use a per-topic re-optimized bandwidth with country fixed effects only."

table_2g <- modelsummary(
  list(
    "Political" = results_h2_drop$model2a_opt_pol,
    "Military" = results_h2_drop$model2a_opt_mil,
    "Economic" = results_h2_drop$model2a_opt_econ,
    "Cultural" = results_h2_drop$model2a_opt_cult,
    "Other" = results_h2_drop$model2a_opt_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 2G: Diff-in-Disc By Topic, Optimal BW (Drop No-Time Articles)",
  add_rows = rows_t2g,
  notes = str_wrap(note_t2g, 80)
)

table_2g

gtsave(table_2g, file.path(FIGURES_TABLES, "table_2g.tex"))
```

## Table 2H: Diff-in-Disc By Topic Full Data (Drop No-Time)

```{r table2h}
rows_t2h <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-'
)
attr(rows_t2h, 'position') <- c(5, 6, 7)

note_t2h <- "All standard errors are clustered at the source level. Articles without publication times are dropped. All models use the full dataset (no bandwidth restriction) with country fixed effects only."

table_2h <- modelsummary(
  list(
    "Political" = results_h2_drop$model2a_full_pol,
    "Military" = results_h2_drop$model2a_full_mil,
    "Economic" = results_h2_drop$model2a_full_econ,
    "Cultural" = results_h2_drop$model2a_full_cult,
    "Other" = results_h2_drop$model2a_full_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 2H: Diff-in-Disc By Topic, Full Data (Drop No-Time Articles)",
  add_rows = rows_t2h,
  notes = str_wrap(note_t2h, 80)
)

table_2h

gtsave(table_2h, file.path(FIGURES_TABLES, "table_2h.tex"))
```

## Table 3F: Alignment Main (Drop No-Time)

```{r table3f}
note_t3f <- "Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights) for Models 3-6, clustered at source level. Models 1-2 use rdrobust standard errors. Articles without publication times are dropped. Model 1 shows RDD results for CSTO countries only. Model 2 shows RDD results for Neutral countries only. Model 3 uses full data with topic fixed effects. Model 4 uses the optimal bandwidth with topic fixed effects. Model 5 omits military-related articles and uses a re-optimized bandwidth. Model 6 uses only Russian-related (non-military) articles with a re-optimized bandwidth. Sample restricted to state-owned media in non-NATO countries."

# Create vcov list with bootstrap SEs for felm models
vcov_t3f <- list(
  "(3)" = create_bootstrap_vcov(results_het_drop$model5a_full, results_het_drop$bootstrap_se$model5a_full, "treatment:csto"),
  "(4)" = create_bootstrap_vcov(results_het_drop$model5a_opt, results_het_drop$bootstrap_se$model5a_opt, "treatment:csto"),
  "(5)" = create_bootstrap_vcov(results_het_drop$model5a_opt_non_mil, results_het_drop$bootstrap_se$model5a_opt_non_mil, "treatment:csto"),
  "(6)" = create_bootstrap_vcov(results_het_drop$model5a_opt_russian, results_het_drop$bootstrap_se$model5a_opt_russian, "treatment:csto")
)

table_3f <- modelsummary(
  list(
    "(1)" = results_het_drop$model5a_csto,
    "(2)" = results_het_drop$model5a_neutral,
    "(3)" = results_het_drop$model5a_full,
    "(4)" = results_het_drop$model5a_opt,
    "(5)" = results_het_drop$model5a_opt_non_mil,
    "(6)" = results_het_drop$model5a_opt_russian
  ),
  vcov = vcov_t3f,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 3F: Russian Alignment Heterogeneity (Drop No-Time Articles)",
  notes = str_wrap(note_t3f, 80)
)

table_3f

gtsave(table_3f, file.path(FIGURES_TABLES, "table_3f.tex"))
```

## Table 3G: Alignment By Topic Optimal BW (Drop No-Time)

```{r table3g}
note_t3g <- "All standard errors are clustered at the source level. Articles without publication times are dropped. Each model uses a per-topic re-optimized bandwidth. State media in non-NATO countries only."

table_3g <- modelsummary(
  list(
    "Political" = results_het_drop$model5a_opt_pol,
    "Military" = results_het_drop$model5a_opt_mil,
    "Economic" = results_het_drop$model5a_opt_econ,
    "Cultural" = results_het_drop$model5a_opt_cult,
    "Other" = results_het_drop$model5a_opt_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 3G: Alignment By Topic, Optimal BW (Drop No-Time Articles)",
  notes = str_wrap(note_t3g, 80)
)

table_3g

gtsave(table_3g, file.path(FIGURES_TABLES, "table_3g.tex"))
```

## Table 3H: Alignment By Topic Full Data (Drop No-Time)

```{r table3h}
note_t3h <- "All standard errors are clustered at the source level. Articles without publication times are dropped. Each model uses the full dataset (no bandwidth restriction). State media in non-NATO countries only."

table_3h <- modelsummary(
  list(
    "Political" = results_het_drop$model5a_full_pol,
    "Military" = results_het_drop$model5a_full_mil,
    "Economic" = results_het_drop$model5a_full_econ,
    "Cultural" = results_het_drop$model5a_full_cult,
    "Other" = results_het_drop$model5a_full_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 3H: Alignment By Topic, Full Data (Drop No-Time Articles)",
  notes = str_wrap(note_t3h, 80)
)

table_3h

gtsave(table_3h, file.path(FIGURES_TABLES, "table_3h.tex"))
```

## Table 4F: Ethnic Main (Drop No-Time)

```{r table4f}
note_t4f <- "Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights), clustered at source level. Articles without publication times are dropped. Model 1 uses full data with topic fixed effects. Model 2 uses the optimal bandwidth with topic fixed effects. Model 3 omits military-related articles and uses a re-optimized bandwidth. Model 4 uses only Russian-related (non-military) articles with a re-optimized bandwidth. Sample restricted to state-owned media in non-NATO countries."

# Create vcov list with bootstrap SEs
vcov_t4f <- list(
  "(1)" = create_bootstrap_vcov(results_het_drop$model6a_full, results_het_drop$bootstrap_se$model6a_full, "treatment:high_russia"),
  "(2)" = create_bootstrap_vcov(results_het_drop$model6a_opt, results_het_drop$bootstrap_se$model6a_opt, "treatment:high_russia"),
  "(3)" = create_bootstrap_vcov(results_het_drop$model6a_opt_non_mil, results_het_drop$bootstrap_se$model6a_opt_non_mil, "treatment:high_russia"),
  "(4)" = create_bootstrap_vcov(results_het_drop$model6a_opt_russian, results_het_drop$bootstrap_se$model6a_opt_russian, "treatment:high_russia")
)

table_4f <- modelsummary(
  list(
    "(1)" = results_het_drop$model6a_full,
    "(2)" = results_het_drop$model6a_opt,
    "(3)" = results_het_drop$model6a_opt_non_mil,
    "(4)" = results_het_drop$model6a_opt_russian
  ),
  vcov = vcov_t4f,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 4F: Ethnic Heterogeneity (Drop No-Time Articles)",
  notes = str_wrap(note_t4f, 80)
)

table_4f

gtsave(table_4f, file.path(FIGURES_TABLES, "table_4f.tex"))
```

## Table 4G: Ethnic By Topic Optimal BW (Drop No-Time)

```{r table4g}
note_t4g <- "All standard errors are clustered at the source level. Articles without publication times are dropped. Each model uses a per-topic re-optimized bandwidth. State media in non-NATO countries only."

table_4g <- modelsummary(
  list(
    "Political" = results_het_drop$model6a_opt_pol,
    "Military" = results_het_drop$model6a_opt_mil,
    "Economic" = results_het_drop$model6a_opt_econ,
    "Cultural" = results_het_drop$model6a_opt_cult,
    "Other" = results_het_drop$model6a_opt_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 4G: Ethnic By Topic, Optimal BW (Drop No-Time Articles)",
  notes = str_wrap(note_t4g, 80)
)

table_4g

gtsave(table_4g, file.path(FIGURES_TABLES, "table_4g.tex"))
```

## Table 4H: Ethnic By Topic Full Data (Drop No-Time)

```{r table4h}
note_t4h <- "All standard errors are clustered at the source level. Articles without publication times are dropped. Each model uses the full dataset (no bandwidth restriction). State media in non-NATO countries only."

table_4h <- modelsummary(
  list(
    "Political" = results_het_drop$model6a_full_pol,
    "Military" = results_het_drop$model6a_full_mil,
    "Economic" = results_het_drop$model6a_full_econ,
    "Cultural" = results_het_drop$model6a_full_cult,
    "Other" = results_het_drop$model6a_full_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 4H: Ethnic By Topic, Full Data (Drop No-Time Articles)",
  notes = str_wrap(note_t4h, 80)
)

table_4h

gtsave(table_4h, file.path(FIGURES_TABLES, "table_4h.tex"))
```

# Probabilistic Time Assignment Variant Tables

## Table 1F: RDD Main (Probabilistic Time)

```{r table1f}
rows_t1f <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7, ~row8,
  'State FEs', '-', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', 'X', 'X', 'X', 'X', 'X', 'X',
  'Topic FEs', '-', '-', '-', 'X', 'X', 'X', 'X', 'X'
)
attr(rows_t1f, 'position') <- c(3, 4, 5)

note_t1f <- "All standard errors are clustered at the source level. Articles without publication times are assigned times via KDE sampling from same-source distributions. Models 1-4 uses the optimal bandwidth. Model 5 uses a linear specification with the full set of articles. Model 6 omits Military Topics. Model 7 omits NATO allies. Model 8 uses full saturation (country-source-topic FEs)."

table_1f <- modelsummary(
  list(
    "(1)" = results_h1_prob$model1_opt,
    "(2)" = results_h1_prob$model2_opt,
    "(3)" = results_h1_prob$model3_opt,
    "(4)" = results_h1_prob$model4_opt,
    "(5)" = results_h1_prob$model1_full_linear,
    "(6)" = results_h1_prob$model4_non_mil,
    "(7)" = results_h1_prob$model4_non_nato,
    "(8)" = results_h1_prob$model4_felm_saturated
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c("treatment" = "Invasion", "post" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 1F: RDD with Probabilistic Time Assignment",
  add_rows = rows_t1f,
  notes = str_wrap(note_t1f, 80)
)

table_1f

gtsave(table_1f, file.path(FIGURES_TABLES, "table_1f.tex"))
```

## Table 1G: RDD By Topic (Probabilistic Time)

```{r table1g}
rows_t1g <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', 'X', 'X', 'X', 'X', 'X',
  'Topic FEs', '-', '-', '-', '-', '-'
)
attr(rows_t1g, 'position') <- c(3, 4, 5)

note_t1g <- "All standard errors are clustered at the source level. Articles without publication times are assigned times via KDE sampling. All models use the optimal bandwidth with country and source fixed effects."

table_1g <- modelsummary(
  list(
    "Political" = results_h1_prob$model4_opt_pol,
    "Military" = results_h1_prob$model4_opt_mil,
    "Economic" = results_h1_prob$model4_opt_econ,
    "Cultural" = results_h1_prob$model4_opt_cult,
    "Other" = results_h1_prob$model4_opt_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c("treatment" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 1G: RDD By Topic (Probabilistic Time Assignment)",
  add_rows = rows_t1g,
  notes = str_wrap(note_t1g, 80)
)

table_1g

gtsave(table_1g, file.path(FIGURES_TABLES, "table_1g.tex"))
```

## Table 2I: Diff-in-Disc Main (Probabilistic Time)

```{r table2i}
rows_t2i <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7,
  'State FEs', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-', '-', 'X',
  'Topic FEs', 'X', 'X', 'X', 'X', 'X', 'X', 'X'
)
attr(rows_t2i, 'position') <- c(5, 6, 7)

note_t2i <- "All standard errors are clustered at the source level. Articles without publication times are assigned times via KDE sampling. Model 2 uses the optimal bandwidth. Model 3 omits NATO allies. Model 4 omits military-related articles. Model 5 uses only Russian-related articles. Model 6 combines all robustness filters with a re-optimized bandwidth. Model 7 uses full saturation (source-topic and country-state-topic FEs)."

table_2i <- modelsummary(
  list(
    "(1)" = results_h2_prob$model2a,
    "(2)" = results_h2_prob$model2a_opt,
    "(3)" = results_h2_prob$model2d,
    "(4)" = results_h2_prob$model2b,
    "(5)" = results_h2_prob$model3a,
    "(6)" = results_h2_prob$model3a_opt,
    "(7)" = results_h2_prob$model3a_opt_saturated
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 2I: Diff-in-Disc (Probabilistic Time Assignment)",
  add_rows = rows_t2i,
  notes = str_wrap(note_t2i, 80)
)

table_2i

gtsave(table_2i, file.path(FIGURES_TABLES, "table_2i.tex"))
```

## Table 2J: Diff-in-Disc By Topic Optimal BW (Probabilistic Time)

```{r table2j}
rows_t2j <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-'
)
attr(rows_t2j, 'position') <- c(5, 6, 7)

note_t2j <- "All standard errors are clustered at the source level. Articles without publication times are assigned times via KDE sampling. All models use a per-topic re-optimized bandwidth with country fixed effects only."

table_2j <- modelsummary(
  list(
    "Political" = results_h2_prob$model2a_opt_pol,
    "Military" = results_h2_prob$model2a_opt_mil,
    "Economic" = results_h2_prob$model2a_opt_econ,
    "Cultural" = results_h2_prob$model2a_opt_cult,
    "Other" = results_h2_prob$model2a_opt_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 2J: Diff-in-Disc By Topic, Optimal BW (Probabilistic Time)",
  add_rows = rows_t2j,
  notes = str_wrap(note_t2j, 80)
)

table_2j

gtsave(table_2j, file.path(FIGURES_TABLES, "table_2j.tex"))
```

## Table 2K: Diff-in-Disc By Topic Full Data (Probabilistic Time)

```{r table2k}
rows_t2k <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-'
)
attr(rows_t2k, 'position') <- c(5, 6, 7)

note_t2k <- "All standard errors are clustered at the source level. Articles without publication times are assigned times via KDE sampling. All models use the full dataset (no bandwidth restriction) with country fixed effects only."

table_2k <- modelsummary(
  list(
    "Political" = results_h2_prob$model2a_full_pol,
    "Military" = results_h2_prob$model2a_full_mil,
    "Economic" = results_h2_prob$model2a_full_econ,
    "Cultural" = results_h2_prob$model2a_full_cult,
    "Other" = results_h2_prob$model2a_full_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 2K: Diff-in-Disc By Topic, Full Data (Probabilistic Time)",
  add_rows = rows_t2k,
  notes = str_wrap(note_t2k, 80)
)

table_2k

gtsave(table_2k, file.path(FIGURES_TABLES, "table_2k.tex"))
```

## Table 3I: Alignment Main (Probabilistic Time)

```{r table3i}
note_t3i <- "Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights) for Models 3-6, clustered at source level. Models 1-2 use rdrobust standard errors. Articles without publication times are assigned times via KDE sampling. Model 1 shows RDD results for CSTO countries only. Model 2 shows RDD results for Neutral countries only. Model 3 uses full data with topic fixed effects. Model 4 uses the optimal bandwidth with topic fixed effects. Model 5 omits military-related articles and uses a re-optimized bandwidth. Model 6 uses only Russian-related (non-military) articles with a re-optimized bandwidth. Sample restricted to state-owned media in non-NATO countries."

# Create vcov list with bootstrap SEs for felm models
vcov_t3i <- list(
  "(3)" = create_bootstrap_vcov(results_het_prob$model5a_full, results_het_prob$bootstrap_se$model5a_full, "treatment:csto"),
  "(4)" = create_bootstrap_vcov(results_het_prob$model5a_opt, results_het_prob$bootstrap_se$model5a_opt, "treatment:csto"),
  "(5)" = create_bootstrap_vcov(results_het_prob$model5a_opt_non_mil, results_het_prob$bootstrap_se$model5a_opt_non_mil, "treatment:csto"),
  "(6)" = create_bootstrap_vcov(results_het_prob$model5a_opt_russian, results_het_prob$bootstrap_se$model5a_opt_russian, "treatment:csto")
)

table_3i <- modelsummary(
  list(
    "(1)" = results_het_prob$model5a_csto,
    "(2)" = results_het_prob$model5a_neutral,
    "(3)" = results_het_prob$model5a_full,
    "(4)" = results_het_prob$model5a_opt,
    "(5)" = results_het_prob$model5a_opt_non_mil,
    "(6)" = results_het_prob$model5a_opt_russian
  ),
  vcov = vcov_t3i,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 3I: Russian Alignment Heterogeneity (Probabilistic Time)",
  notes = str_wrap(note_t3i, 80)
)

table_3i

gtsave(table_3i, file.path(FIGURES_TABLES, "table_3i.tex"))
```

## Table 3J: Alignment By Topic Optimal BW (Probabilistic Time)

```{r table3j}
note_t3j <- "All standard errors are clustered at the source level. Articles without publication times are assigned times via KDE sampling. Each model uses a per-topic re-optimized bandwidth. State media in non-NATO countries only."

table_3j <- modelsummary(
  list(
    "Political" = results_het_prob$model5a_opt_pol,
    "Military" = results_het_prob$model5a_opt_mil,
    "Economic" = results_het_prob$model5a_opt_econ,
    "Cultural" = results_het_prob$model5a_opt_cult,
    "Other" = results_het_prob$model5a_opt_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 3J: Alignment By Topic, Optimal BW (Probabilistic Time)",
  notes = str_wrap(note_t3j, 80)
)

table_3j

gtsave(table_3j, file.path(FIGURES_TABLES, "table_3j.tex"))
```

## Table 3K: Alignment By Topic Full Data (Probabilistic Time)

```{r table3k}
note_t3k <- "All standard errors are clustered at the source level. Articles without publication times are assigned times via KDE sampling. Each model uses the full dataset (no bandwidth restriction). State media in non-NATO countries only."

table_3k <- modelsummary(
  list(
    "Political" = results_het_prob$model5a_full_pol,
    "Military" = results_het_prob$model5a_full_mil,
    "Economic" = results_het_prob$model5a_full_econ,
    "Cultural" = results_het_prob$model5a_full_cult,
    "Other" = results_het_prob$model5a_full_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 3K: Alignment By Topic, Full Data (Probabilistic Time)",
  notes = str_wrap(note_t3k, 80)
)

table_3k

gtsave(table_3k, file.path(FIGURES_TABLES, "table_3k.tex"))
```

## Table 4I: Ethnic Main (Probabilistic Time)

```{r table4i}
note_t4i <- "Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights), clustered at source level. Articles without publication times are assigned times via KDE sampling. Model 1 uses full data with topic fixed effects. Model 2 uses the optimal bandwidth with topic fixed effects. Model 3 omits military-related articles and uses a re-optimized bandwidth. Model 4 uses only Russian-related (non-military) articles with a re-optimized bandwidth. Sample restricted to state-owned media in non-NATO countries."

# Create vcov list with bootstrap SEs
vcov_t4i <- list(
  "(1)" = create_bootstrap_vcov(results_het_prob$model6a_full, results_het_prob$bootstrap_se$model6a_full, "treatment:high_russia"),
  "(2)" = create_bootstrap_vcov(results_het_prob$model6a_opt, results_het_prob$bootstrap_se$model6a_opt, "treatment:high_russia"),
  "(3)" = create_bootstrap_vcov(results_het_prob$model6a_opt_non_mil, results_het_prob$bootstrap_se$model6a_opt_non_mil, "treatment:high_russia"),
  "(4)" = create_bootstrap_vcov(results_het_prob$model6a_opt_russian, results_het_prob$bootstrap_se$model6a_opt_russian, "treatment:high_russia")
)

table_4i <- modelsummary(
  list(
    "(1)" = results_het_prob$model6a_full,
    "(2)" = results_het_prob$model6a_opt,
    "(3)" = results_het_prob$model6a_opt_non_mil,
    "(4)" = results_het_prob$model6a_opt_russian
  ),
  vcov = vcov_t4i,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 4I: Ethnic Heterogeneity (Probabilistic Time)",
  notes = str_wrap(note_t4i, 80)
)

table_4i

gtsave(table_4i, file.path(FIGURES_TABLES, "table_4i.tex"))
```

## Table 4J: Ethnic By Topic Optimal BW (Probabilistic Time)

```{r table4j}
note_t4j <- "All standard errors are clustered at the source level. Articles without publication times are assigned times via KDE sampling. Each model uses a per-topic re-optimized bandwidth. State media in non-NATO countries only."

table_4j <- modelsummary(
  list(
    "Political" = results_het_prob$model6a_opt_pol,
    "Military" = results_het_prob$model6a_opt_mil,
    "Economic" = results_het_prob$model6a_opt_econ,
    "Cultural" = results_het_prob$model6a_opt_cult,
    "Other" = results_het_prob$model6a_opt_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 4J: Ethnic By Topic, Optimal BW (Probabilistic Time)",
  notes = str_wrap(note_t4j, 80)
)

table_4j

gtsave(table_4j, file.path(FIGURES_TABLES, "table_4j.tex"))
```

## Table 4K: Ethnic By Topic Full Data (Probabilistic Time)

```{r table4k}
note_t4k <- "All standard errors are clustered at the source level. Articles without publication times are assigned times via KDE sampling. Each model uses the full dataset (no bandwidth restriction). State media in non-NATO countries only."

table_4k <- modelsummary(
  list(
    "Political" = results_het_prob$model6a_full_pol,
    "Military" = results_het_prob$model6a_full_mil,
    "Economic" = results_het_prob$model6a_full_econ,
    "Cultural" = results_het_prob$model6a_full_cult,
    "Other" = results_het_prob$model6a_full_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 4K: Ethnic By Topic, Full Data (Probabilistic Time)",
  notes = str_wrap(note_t4k, 80)
)

table_4k

gtsave(table_4k, file.path(FIGURES_TABLES, "table_4k.tex"))
```

# Comparison Table: Countries by Alignment and Ethnic Population

```{r comparison-table}
get_group <- function(russian_group, security_group) {
  paste(intersect(russian_group, security_group), collapse = ", ")
}

table_data <- data.frame(
  `Ethnic Russian Population` = c("Low Ethnic", "High Ethnic"),
  `Low Russia Aligned` = c(
    get_group(LOW_RUSSIAN_POP, NEUTRAL_COUNTRIES),
    get_group(HIGH_RUSSIAN_POP, NEUTRAL_COUNTRIES)
  ),
  `High Russia Aligned` = c(
    get_group(LOW_RUSSIAN_POP, CSTO_COUNTRIES),
    get_group(HIGH_RUSSIAN_POP, CSTO_COUNTRIES)
  )
)

comparison_table <- table_data %>%
  gt() %>%
  tab_header(
    title = "Ethnic Russian Population x Russia Security Alignment",
    subtitle = "Country Classification"
  ) %>%
  cols_label(
    Ethnic.Russian.Population = "",
    Low.Russia.Aligned = "Low Alignment (Neutral)",
    High.Russia.Aligned = "High Alignment (CSTO)"
  ) %>%
  tab_style(
    style = cell_borders(sides = "all", color = "black", weight = px(1)),
    locations = cells_body()
  )

comparison_table

gtsave(comparison_table, file.path(FIGURES_TABLES, "comparison_table.tex"))
```

# Alignment Table

```{r alignment-table}
alignment_table <- table_data %>%
  gt() %>%
  tab_header(
    title = "Ethnic Russian Population x Russia Security Alignment",
    subtitle = "Alignment Comparison"
  ) %>%
  cols_label(
    Ethnic.Russian.Population = "",
    Low.Russia.Aligned = "Low Alignment",
    High.Russia.Aligned = "High Alignment"
  ) %>%
  fmt_markdown(everything()) %>%
  tab_style(
    style = cell_borders(sides = c("top", "bottom"), color = "black", weight = px(2)),
    locations = cells_body(rows = 1:2, columns = 2:3)
  ) %>%
  tab_style(
    style = cell_borders(sides = c("left", "right"), color = "black", weight = px(2)),
    locations = cells_body(rows = 1:2, columns = 2:3)
  )

alignment_table

gtsave(alignment_table, file.path(FIGURES_TABLES, "alignment_table.tex"))
```

# Ethnic Table

```{r ethnic-table}
ethnic_table <- table_data %>%
  gt() %>%
  tab_header(
    title = "Ethnic Russian Population x Russia Security Alignment",
    subtitle = "Ethnic Comparison"
  ) %>%
  cols_label(
    Ethnic.Russian.Population = "",
    Low.Russia.Aligned = "Low Alignment",
    High.Russia.Aligned = "High Alignment"
  ) %>%
  fmt_markdown(everything()) %>%
  tab_style(
    style = cell_borders(sides = "bottom", color = "black", weight = px(2)),
    locations = cells_body(rows = 1, columns = 2:3)
  ) %>%
  tab_style(
    style = cell_borders(sides = c("top", "bottom", "left", "right"), color = "black", weight = px(2)),
    locations = cells_body(rows = 1:2, columns = 2:3)
  )

ethnic_table

gtsave(ethnic_table, file.path(FIGURES_TABLES, "ethnic_table.tex"))
```

# Export Tables to LaTeX

```{r latex-export}
# Function to save modelsummary as tex
save_tex <- function(models, filename, coef_map, title, rows = NULL, note = NULL) {
  modelsummary(
    models,
    output = file.path(FIGURES_TABLES, filename),
    fmt = 3,
    stars = c('*' = .05, '**' = .01, '***' = .001),
    coef_map = coef_map,
    gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
    title = title,
    add_rows = rows,
    notes = note
  )
}

# Note: These will generate .tex files for LaTeX inclusion
cat("LaTeX tables can be generated by changing output format to 'latex'\n")
```

# Summary of All Tables

```{r summary}
cat("\n")
cat("=============================================================\n")
cat("PUBLICATION OUTPUTS SUMMARY\n")
cat("=============================================================\n")
cat("\nTables generated:\n")
cat("  - table_1.tex: Main RDD results (H1, day)\n")
cat("  - table_1_cont.tex: Main RDD results (H1, continuous)\n")
cat("  - table_1b.tex: RDD by topic (day)\n")
cat("  - table_1c.tex: RDD by topic (continuous)\n")
cat("  - table_2.tex: Diff-in-disc results (H2, day)\n")
cat("  - table_2a.tex: Diff-in-disc results (H2, continuous)\n")
cat("  - table_2b.tex: Diff-in-disc by topic, optimal BW (day)\n")
cat("  - table_2c.tex: Diff-in-disc by topic, optimal BW (continuous)\n")
cat("  - table_2d.tex: Diff-in-disc by topic, full data (day)\n")
cat("  - table_2e.tex: Diff-in-disc by topic, full data (continuous)\n")
cat("  - table_3.tex: Heterogeneity by alignment (day)\n")
cat("  - table_3a.tex: Heterogeneity by alignment (continuous)\n")
cat("  - table_3b.tex: Heterogeneity by topic, optimal BW (day)\n")
cat("  - table_3c.tex: Heterogeneity by topic, optimal BW (continuous)\n")
cat("  - table_3d.tex: Heterogeneity by topic, full data (day)\n")
cat("  - table_3e.tex: Heterogeneity by topic, full data (continuous)\n")
cat("  - table_4.tex: Ethnic heterogeneity (day)\n")
cat("  - table_4a.tex: Ethnic heterogeneity (continuous)\n")
cat("  - table_4b.tex: Ethnic by topic, optimal BW (day)\n")
cat("  - table_4c.tex: Ethnic by topic, optimal BW (continuous)\n")
cat("  - table_4d.tex: Ethnic by topic, full data (day)\n")
cat("  - table_4e.tex: Ethnic by topic, full data (continuous)\n")
cat("  - table_1d.tex: RDD main (drop no-time)\n")
cat("  - table_1e.tex: RDD by topic (drop no-time)\n")
cat("  - table_2f.tex: Diff-in-disc main (drop no-time)\n")
cat("  - table_2g.tex: Diff-in-disc by topic, opt BW (drop no-time)\n")
cat("  - table_2h.tex: Diff-in-disc by topic, full data (drop no-time)\n")
cat("  - table_3f.tex: Alignment main (drop no-time)\n")
cat("  - table_3g.tex: Alignment by topic, opt BW (drop no-time)\n")
cat("  - table_3h.tex: Alignment by topic, full data (drop no-time)\n")
cat("  - table_4f.tex: Ethnic main (drop no-time)\n")
cat("  - table_4g.tex: Ethnic by topic, opt BW (drop no-time)\n")
cat("  - table_4h.tex: Ethnic by topic, full data (drop no-time)\n")
cat("  - table_1f.tex: RDD main (probabilistic time)\n")
cat("  - table_1g.tex: RDD by topic (probabilistic time)\n")
cat("  - table_2i.tex: Diff-in-disc main (probabilistic time)\n")
cat("  - table_2j.tex: Diff-in-disc by topic, opt BW (probabilistic time)\n")
cat("  - table_2k.tex: Diff-in-disc by topic, full data (probabilistic time)\n")
cat("  - table_3i.tex: Alignment main (probabilistic time)\n")
cat("  - table_3j.tex: Alignment by topic, opt BW (probabilistic time)\n")
cat("  - table_3k.tex: Alignment by topic, full data (probabilistic time)\n")
cat("  - table_4i.tex: Ethnic main (probabilistic time)\n")
cat("  - table_4j.tex: Ethnic by topic, opt BW (probabilistic time)\n")
cat("  - table_4k.tex: Ethnic by topic, full data (probabilistic time)\n")
cat("  - comparison_table.tex: Country classification\n")
cat("  - alignment_table.tex: Alignment comparison\n")
cat("  - ethnic_table.tex: Ethnic population comparison\n")
cat("\nFigures generated in previous scripts:\n")
cat("  - invasion_on_sentiment.png\n")
cat("  - invasion_on_sentiment_non_mil.png\n")
cat("  - invasion_discs_graph.png\n")
cat("  - invasion_discs_non_mil.png\n")
cat("  - state_align_discs.png\n")
cat("  - ethnic_discs.png\n")
cat("  - articles_per_day.png\n")
cat("  - topic_distribution.png\n")
cat("  - topic_split.png\n")
cat("=============================================================\n")
```

# Leave-One-Out Country Robustness Table

```{r loo-table}
loo_data <- results_het$loo_summary

note_loo <- "Leave-one-out robustness analysis for the non-military topics model. Each row shows results when excluding the specified country from the sample. Bandwidth is recalculated for each subset. Coefficient shown is for the treatment:csto interaction term. Standard errors clustered at source domain level."
note_loo_wrapped <- str_wrap(note_loo, width = 80)

loo_table <- loo_data %>%
  mutate(
    estimate_fmt = sprintf("%.3f%s", estimate,
                     case_when(p_value < 0.001 ~ "***",
                               p_value < 0.01 ~ "**",
                               p_value < 0.05 ~ "*",
                               TRUE ~ "")),
    std_error_fmt = sprintf("(%.3f)", std_error),
    p_value_fmt = sprintf("%.3f", p_value),
    n_obs_fmt = format(n_obs, big.mark = ","),
    bandwidth_fmt = sprintf("%.1f", bandwidth)
  ) %>%
  select(country_dropped, estimate_fmt, std_error_fmt, p_value_fmt, n_obs_fmt, bandwidth_fmt) %>%
  gt() %>%
  cols_label(
    country_dropped = "Country Dropped",
    estimate_fmt = "Coefficient",
    std_error_fmt = "Std. Error",
    p_value_fmt = "p-value",
    n_obs_fmt = "N",
    bandwidth_fmt = "Bandwidth"
  ) %>%
  tab_header(title = "Table A: Leave-One-Out Country Robustness Analysis",
             subtitle = "Non-Military Topics Model") %>%
  tab_footnote(footnote = note_loo_wrapped)

loo_table

gtsave(loo_table, file.path(FIGURES_TABLES, "table_loo_robustness.tex"))
```

# Placebo Test Summary Table

```{r placebo-summary}
# Extract placebo results from all hypothesis results
# Note: H1 uses rdrobust, H2 and H3 use felm

# Extract rdrobust result for H1
placebo_h1 <- results_h1$model_placebo
h1_estimate <- placebo_h1$coef[1]  # Conventional RD estimate
h1_se <- placebo_h1$se[1]
h1_pval <- placebo_h1$pv[1]
h1_bw <- placebo_h1$bws[1, 1]
h1_n <- placebo_h1$N_h[1] + placebo_h1$N_h[2]

# Extract felm results for H2 and H3
placebo_h2 <- results_h2$model_placebo
placebo_h3 <- results_het$model_placebo_nonmil

h2_coef <- summary(placebo_h2)$coef["treatment", ]
h3_coef <- summary(placebo_h3)$coef["treatment", ]

# Create summary data frame
placebo_summary <- tibble(
  Model = c("(1) H1: Full Model (RDD)", "(2) H2: Diff-in-Disc", "(3) H3: Non-Military"),
  Estimate = c(h1_estimate, h2_coef["Estimate"], h3_coef["Estimate"]),
  Std_Error = c(h1_se, h2_coef["Cluster s.e."], h3_coef["Cluster s.e."]),
  p_value = c(h1_pval, h2_coef["Pr(>|t|)"], h3_coef["Pr(>|t|)"]),
  Bandwidth = c(h1_bw, results_h2$optimal_bw_placebo, results_het$optimal_bw_placebo_nonmil),
  N = c(h1_n, nobs(placebo_h2), nobs(placebo_h3))
)

note_placebo <- "Placebo tests using December 7, 2021 (Putin's announcement) as a false treatment date. Data restricted to pre-invasion period (before Feb 19, 2022). Model 1 uses rdrobust; Models 2-3 use felm with optimal bandwidth. Non-significant treatment effects suggest parallel trends assumption holds."
note_placebo_wrapped <- str_wrap(note_placebo, width = 80)

table_placebo <- placebo_summary %>%
  mutate(
    Estimate_fmt = sprintf("%.3f%s", Estimate,
                     case_when(p_value < 0.001 ~ "***",
                               p_value < 0.01 ~ "**",
                               p_value < 0.05 ~ "*",
                               TRUE ~ "")),
    Std_Error_fmt = sprintf("(%.3f)", Std_Error),
    p_value_fmt = sprintf("%.3f", p_value),
    Bandwidth_fmt = sprintf("%.1f", Bandwidth),
    N_fmt = format(N, big.mark = ",")
  ) %>%
  select(Model, Estimate_fmt, Std_Error_fmt, p_value_fmt, Bandwidth_fmt, N_fmt) %>%
  gt() %>%
  cols_label(
    Model = "Model",
    Estimate_fmt = "Estimate",
    Std_Error_fmt = "Std. Error",
    p_value_fmt = "p-value",
    Bandwidth_fmt = "Bandwidth",
    N_fmt = "N"
  ) %>%
  tab_header(title = "Table B: Placebo Test Summary (December 7, 2021)") %>%
  tab_footnote(footnote = note_placebo_wrapped)

table_placebo

gtsave(table_placebo, file.path(FIGURES_TABLES, "table_placebo_summary.tex"))
```

# Session Info

```{r session-info}
print_session_info()
```
