---
title: "07B - Ethnic Russian Population Analysis (Drop No-Time Articles)"
author: "Donald Moratz"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

# Overview

This script examines heterogeneous treatment effects by Ethnic Russian Population. Specifically, it analyzes whether state-owned media in non-NATO countries with high ethnic Russian populations showed differential sentiment changes following the Russian invasion of Ukraine, compared to those with low ethnic Russian populations. Articles without publication times are dropped.

**Analysis:**
- Diff-in-disc regressions: High vs Low Ethnic Russian population (state media, non-NATO countries)
- Optimal bandwidth selection
- Non-military topic subsetting
- Russian-related article subsetting
- By-topic models (full data and per-topic optimal bandwidth)
- Placebo test using December 7th 2021 announcement date
- Leave-one-out country robustness checks

**Inputs:**
- `data/intermediate/02_cleaned_data.rds`
- `data/intermediate/02_data_non_ukraine.rds`

**Outputs:**
- `data/intermediate/07_ethnic_results_drop.rds`
- Table 4F (Ethnic Russian Population heterogeneity, Drop No-Time Articles)

```{r setup, include=FALSE}
source("00_setup.R")
knitr::opts_chunk$set(fig.path = paste0(FIGURES_HETEROGENEITY_DROP, "/"))
```

# Load Data

```{r load}
library(fwildclusterboot)

data <- readRDS(file.path(DATA_INTERMEDIATE, "02_cleaned_data.rds"))
data_non_ukraine <- readRDS(file.path(DATA_INTERMEDIATE, "02_data_non_ukraine.rds"))

# Drop articles without publication times
data <- data %>% filter(has_time == TRUE)
data_non_ukraine <- data_non_ukraine %>% filter(has_time == TRUE)

cat("Full data:", nrow(data), "articles\n")
cat("Non-Ukraine data:", nrow(data_non_ukraine), "articles\n")

data <- data %>% mutate(across(c(topic_clean, country, source_domain), as.factor))
data_non_ukraine <- data_non_ukraine %>% mutate(across(c(topic_clean, country, source_domain), as.factor))

# Helper function for wild cluster bootstrap
run_wild_bootstrap <- function(model, param, clustid = "source_domain", B = 4999) {
  boot_result <- boottest(
    object = model,
    param = param,
    clustid = clustid,
    B = B,
    impose_null = TRUE,
    type = "rademacher"
  )
  list(
    se = boot_result$point_estimate / boot_result$t_stat,
    p_val = boot_result$p_val,
    ci_lower = boot_result$conf_int[1],
    ci_upper = boot_result$conf_int[2],
    t_stat = boot_result$teststat
  )
}
```

# Ethnic Russian Population Analysis

## Create Ethnic Subsets

```{r ethnic-data}
data_ethnic <- data %>%
  filter(nato == 0)

data_ethnic <- data_ethnic %>%
  mutate(ethnic_indicator = factor(case_when(
    indicator == 1 & high_russia == 1 ~ "Pre. Ind. High Rus",
    indicator == 1 & high_russia == 0 ~ "Pre. Ind. Low Rus",
    indicator == 2 & high_russia == 1 ~ "Pre. State High Rus",
    indicator == 2 & high_russia == 0 ~ "Pre. State Low Rus",
    indicator == 3 & high_russia == 1 ~ "Post Ind. High Rus",
    indicator == 3 & high_russia == 0 ~ "Post Ind. Low Rus",
    indicator == 4 & high_russia == 1 ~ "Post State High Rus",
    indicator == 4 & high_russia == 0 ~ "Post State Low Rus"
  ),
  levels = c("Pre. Ind. High Rus", "Pre. Ind. Low Rus", "Pre. State High Rus",
             "Pre. State Low Rus", "Post Ind. High Rus", "Post Ind. Low Rus",
             "Post State High Rus", "Post State Low Rus")))

cat("High Russian population:", sum(data_ethnic$high_russia), "\n")
cat("Low Russian population:", sum(data_ethnic$high_russia == 0), "\n")
```

## Visualization: State Media by Ethnic Russian Population

```{r ethnic-plot, fig.width=10, fig.height=7}
agg_data_ethnic <- data_ethnic %>%
  filter(state_owned == 1) %>%
  group_by(running_continuous, csto) %>%
  summarize(sentiment_clean = mean(sentiment_clean), num_obs = n(), .groups = "drop")

ethnic_discs_graph <- data_ethnic %>%
  filter(state_owned == 1) %>%
  ggplot(aes(x = running_continuous, y = sentiment_clean, group = ethnic_indicator, color = ethnic_indicator)) +
  geom_point(data = agg_data_ethnic,
             aes(x = running_continuous, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = COLORS_DISCS, name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on State Media Sentiment",
    subtitle = "High vs Low Ethnic Russian, Difference in Discontinuities",
    x = "Days Pre/Post Invasion (Continuous)",
    y = "Sentiment"
  )

ethnic_discs_graph

ggsave(plot = ethnic_discs_graph,
       file.path(FIGURES_HETEROGENEITY_DROP, "ethnic_discs.png"),
       width = 10, height = 7)
```

## Ethnic Russian Population Regressions

### Diff-in-Disc: High vs Low Ethnic Russian (State Media)

```{r ethnic-reg}
data_ethnic_state <- data_ethnic %>%
  filter(state_owned == 1) %>%
  mutate(source_domain = droplevels(source_domain)) %>%
  mutate(running_continuous = running_continuous / 86400)

model6a <- feols(sentiment_clean ~ running_continuous * treatment * high_russia,
                 cluster = ~source_domain,
                 data = data_ethnic_state)

summary(model6a)

# Wild cluster bootstrap for model6a
boot_model6a <- run_wild_bootstrap(model6a, "treatment:high_russia")
cat("Bootstrap SE for treatment:high_russia:", boot_model6a$se, "\n")
cat("Bootstrap p-value:", boot_model6a$p_val, "\n")
```

## Full Data with Topic FEs

```{r ethnic-full}
model6a_full <- feols(sentiment_clean ~ running_continuous * treatment * high_russia | topic_clean,
                      cluster = ~source_domain,
                      data = data_ethnic_state)

summary(model6a_full)

# Wild cluster bootstrap for model6a_full
boot_model6a_full <- run_wild_bootstrap(model6a_full, "treatment:high_russia")
cat("Bootstrap SE for treatment:high_russia:", boot_model6a_full$se, "\n")
cat("Bootstrap p-value:", boot_model6a_full$p_val, "\n")
```

## Optimal Bandwidth

```{r ethnic-optimal}
bw_ethnic <- rdbwselect(y = data_ethnic_state$sentiment_clean,
                        x = data_ethnic_state$running_continuous,
                        kernel = "triangular",
                        cluster = data_ethnic_state$source_domain,
                        p = 1,
                        bwselect = "mserd")

optimal_bw_ethnic <- bw_ethnic$bws[1, 1]
cat("Optimal bandwidth:", round(optimal_bw_ethnic, 1), "units\n")

optimal_bandwidth_data_ethnic <- data_ethnic_state %>%
  filter(running_continuous < optimal_bw_ethnic, running_continuous > -optimal_bw_ethnic)

model6a_opt <- feols(sentiment_clean ~ running_continuous * treatment * high_russia | topic_clean,
                     cluster = ~source_domain,
                     data = optimal_bandwidth_data_ethnic)

summary(model6a_opt)

# Wild cluster bootstrap for model6a_opt
boot_model6a_opt <- run_wild_bootstrap(model6a_opt, "treatment:high_russia")
cat("Bootstrap SE for treatment:high_russia:", boot_model6a_opt$se, "\n")
cat("Bootstrap p-value:", boot_model6a_opt$p_val, "\n")
```

## Non-Military Topics

```{r ethnic-non-mil}
data_ethnic_state_non_mil <- data_ethnic_state %>%
  filter(!topic_clean %in% "Military")

bw_ethnic_non_mil <- rdbwselect(y = data_ethnic_state_non_mil$sentiment_clean,
                                x = data_ethnic_state_non_mil$running_continuous,
                                kernel = "triangular",
                                cluster = data_ethnic_state_non_mil$source_domain,
                                p = 1,
                                bwselect = "mserd")

optimal_bw_ethnic_non_mil <- bw_ethnic_non_mil$bws[1, 1]
cat("Optimal bandwidth (non-mil):", round(optimal_bw_ethnic_non_mil, 1), "units\n")

optimal_bandwidth_data_ethnic_non_mil <- data_ethnic_state_non_mil %>%
  filter(running_continuous < optimal_bw_ethnic_non_mil, running_continuous > -optimal_bw_ethnic_non_mil)

model6a_opt_non_mil <- feols(sentiment_clean ~ running_continuous * treatment * high_russia | topic_clean,
                             cluster = ~source_domain,
                             data = optimal_bandwidth_data_ethnic_non_mil)

summary(model6a_opt_non_mil)

# Wild cluster bootstrap for model6a_opt_non_mil
boot_model6a_opt_non_mil <- run_wild_bootstrap(model6a_opt_non_mil, "treatment:high_russia")
cat("Bootstrap SE for treatment:high_russia:", boot_model6a_opt_non_mil$se, "\n")
cat("Bootstrap p-value:", boot_model6a_opt_non_mil$p_val, "\n")
```

## Russian-Related Articles Only

```{r ethnic-russian}
data_ethnic_state_russian <- data_ethnic_state %>%
  filter(!topic_clean %in% "Military") %>%
  filter(!Russian.Involvement == "Not")

bw_ethnic_russian <- rdbwselect(y = data_ethnic_state_russian$sentiment_clean,
                                x = data_ethnic_state_russian$running_continuous,
                                kernel = "triangular",
                                cluster = data_ethnic_state_russian$source_domain,
                                p = 1,
                                bwselect = "mserd")

optimal_bw_ethnic_russian <- bw_ethnic_russian$bws[1, 1]
cat("Optimal bandwidth (russian):", round(optimal_bw_ethnic_russian, 1), "units\n")

optimal_bandwidth_data_ethnic_russian <- data_ethnic_state_russian %>%
  filter(running_continuous < optimal_bw_ethnic_russian, running_continuous > -optimal_bw_ethnic_russian)

model6a_opt_russian <- feols(sentiment_clean ~ running_continuous * treatment * high_russia | topic_clean,
                             cluster = ~source_domain,
                             data = optimal_bandwidth_data_ethnic_russian)

summary(model6a_opt_russian)

# Wild cluster bootstrap for model6a_opt_russian
boot_model6a_opt_russian <- run_wild_bootstrap(model6a_opt_russian, "treatment:high_russia")
cat("Bootstrap SE for treatment:high_russia:", boot_model6a_opt_russian$se, "\n")
cat("Bootstrap p-value:", boot_model6a_opt_russian$p_val, "\n")
```

## Fully Saturated Model

```{r ethnic-fully-saturated}
# Change source and topic to factor for interaction FEs
optimal_bandwidth_data_ethnic_non_mil <- optimal_bandwidth_data_ethnic_non_mil %>%
  mutate(
    source_domain = as.factor(source_domain),
    topic_clean = as.factor(topic_clean)
  )

# Heavily saturated model (source:topic + topic:treatment FEs)
model6a_fully_saturated <- feols(
  sentiment_clean ~ running_continuous * treatment * high_russia |
    source_domain^topic_clean + topic_clean^treatment,
  cluster = ~source_domain,
  data = optimal_bandwidth_data_ethnic_non_mil
)

summary(model6a_fully_saturated)
```

### Manual Wild Bootstrap Standard Errors

```{r ethnic-fully-saturated-bootstrap}
set.seed(3184)
B <- 99

# Original model
model_original <- model6a_fully_saturated
original_coef <- coef(model_original)["treatment:high_russia"]
original_se <- se(model_original)["treatment:high_russia"]
original_t <- original_coef / original_se

cat("Original t-stat:", original_t, "\n")

# CRITICAL: Estimate RESTRICTED model under the null (treatment:high_russia = 0)
model_restricted <- feols(
  sentiment_clean ~ running_continuous + treatment + high_russia + running_continuous:treatment +
    running_continuous:high_russia + running_continuous:treatment:high_russia |
    source_domain^topic_clean + topic_clean^treatment,
  cluster = ~source_domain,
  data = optimal_bandwidth_data_ethnic_non_mil
)

# Get residuals and fitted values from RESTRICTED model
residuals_restricted <- residuals(model_restricted)
fitted_restricted <- fitted(model_restricted)

cat("Using restricted model residuals (null imposed)\n")

# Get clusters
clusters <- unique(optimal_bandwidth_data_ethnic_non_mil$source_domain)
n_clusters <- length(clusters)

# Bootstrap
boot_t_stats <- numeric(B)

for(b in 1:B) {
  # Generate Rademacher weights
  cluster_weights <- sample(c(-1, 1), n_clusters, replace = TRUE)

  # Assign to observations
  data_boot <- optimal_bandwidth_data_ethnic_non_mil
  data_boot$weight <- sapply(data_boot$source_domain, function(clust) {
    cluster_weights[which(clusters == clust)]
  })

  # Create bootstrap outcome using RESTRICTED fitted values
  data_boot$sentiment_boot <- fitted_restricted + data_boot$weight * residuals_restricted

  # Re-estimate FULL model on bootstrap data
  model_boot <- feols(
    sentiment_boot ~ running_continuous * treatment * high_russia |
      source_domain^topic_clean + topic_clean^treatment,
    cluster = ~source_domain,
    data = data_boot
  )

  boot_coef <- coef(model_boot)["treatment:high_russia"]
  boot_se <- se(model_boot)["treatment:high_russia"]
  boot_t_stats[b] <- boot_coef / boot_se

  if(b %% 100 == 0) cat("Iteration:", b, "\n")
}

# Calculate p-value
p_value <- mean(abs(boot_t_stats) >= abs(original_t))

cat("\n=== Results ===\n")
cat("Original t-stat:", original_t, "\n")
cat("Mean bootstrap t-stat (should be ~0):", mean(boot_t_stats), "\n")
cat("P-value:", p_value, "\n")

# Plot
hist(boot_t_stats, breaks = 30, main = "Wild Bootstrap t-statistics (Null Imposed)",
     xlab = "t-statistic")
abline(v = original_t, col = "red", lwd = 2)
abline(v = 0, col = "blue", lwd = 2, lty = 2)
legend("topright", c("Original t", "Null (t=0)"), col = c("red", "blue"), lty = c(1, 2), lwd = 2)

# Extract bootstrap results in standard format
boot_model6a_fully_saturated <- list(
  se = original_se,
  p_val = p_value,
  ci_lower = NA,
  ci_upper = NA,
  t_stat = original_t
)
cat("Saturated model bootstrap results extracted\n")
```

## By-Topic Models: Full Data

```{r ethnic-topic-full}
data_ethnic_state_pol <- data_ethnic_state %>% filter(topic_clean == "Political")
data_ethnic_state_mil <- data_ethnic_state %>% filter(topic_clean == "Military")
data_ethnic_state_econ <- data_ethnic_state %>% filter(topic_clean == "Economic")
data_ethnic_state_cult <- data_ethnic_state %>% filter(topic_clean == "Culture")
data_ethnic_state_oth <- data_ethnic_state %>% filter(topic_clean == "Other")

model6a_full_pol <- feols(sentiment_clean ~ running_continuous * treatment * high_russia,
                          cluster = ~source_domain,
                          data = data_ethnic_state_pol)
model6a_full_mil <- feols(sentiment_clean ~ running_continuous * treatment * high_russia,
                          cluster = ~source_domain,
                          data = data_ethnic_state_mil)
model6a_full_econ <- feols(sentiment_clean ~ running_continuous * treatment * high_russia,
                           cluster = ~source_domain,
                           data = data_ethnic_state_econ)
model6a_full_cult <- feols(sentiment_clean ~ running_continuous * treatment * high_russia,
                           cluster = ~source_domain,
                           data = data_ethnic_state_cult)
model6a_full_oth <- feols(sentiment_clean ~ running_continuous * treatment * high_russia,
                          cluster = ~source_domain,
                          data = data_ethnic_state_oth)
```

## By-Topic Models: Per-Topic Optimal Bandwidth

```{r ethnic-topic-opt}
# Political
bw_ethnic_pol <- rdbwselect(y = data_ethnic_state_pol$sentiment_clean, x = data_ethnic_state_pol$running_continuous,
                            kernel = "triangular", cluster = data_ethnic_state_pol$source_domain, p = 1, bwselect = "mserd")
optimal_bw_ethnic_pol <- bw_ethnic_pol$bws[1, 1]
cat("Political optimal bandwidth:", round(optimal_bw_ethnic_pol, 1), "units\n")
opt_ethnic_pol <- data_ethnic_state_pol %>% filter(running_continuous < optimal_bw_ethnic_pol, running_continuous > -optimal_bw_ethnic_pol)

# Military
bw_ethnic_mil <- rdbwselect(y = data_ethnic_state_mil$sentiment_clean, x = data_ethnic_state_mil$running_continuous,
                            kernel = "triangular", cluster = data_ethnic_state_mil$source_domain, p = 1, bwselect = "mserd")
optimal_bw_ethnic_mil <- bw_ethnic_mil$bws[1, 1]
cat("Military optimal bandwidth:", round(optimal_bw_ethnic_mil, 1), "units\n")
opt_ethnic_mil <- data_ethnic_state_mil %>% filter(running_continuous < optimal_bw_ethnic_mil, running_continuous > -optimal_bw_ethnic_mil)

# Economic
bw_ethnic_econ <- rdbwselect(y = data_ethnic_state_econ$sentiment_clean, x = data_ethnic_state_econ$running_continuous,
                             kernel = "triangular", cluster = data_ethnic_state_econ$source_domain, p = 1, bwselect = "mserd")
optimal_bw_ethnic_econ <- bw_ethnic_econ$bws[1, 1]
cat("Economic optimal bandwidth:", round(optimal_bw_ethnic_econ, 1), "units\n")
opt_ethnic_econ <- data_ethnic_state_econ %>% filter(running_continuous < optimal_bw_ethnic_econ, running_continuous > -optimal_bw_ethnic_econ)

# Culture
bw_ethnic_cult <- rdbwselect(y = data_ethnic_state_cult$sentiment_clean, x = data_ethnic_state_cult$running_continuous,
                             kernel = "triangular", cluster = data_ethnic_state_cult$source_domain, p = 1, bwselect = "mserd")
optimal_bw_ethnic_cult <- bw_ethnic_cult$bws[1, 1]
cat("Culture optimal bandwidth:", round(optimal_bw_ethnic_cult, 1), "units\n")
opt_ethnic_cult <- data_ethnic_state_cult %>% filter(running_continuous < optimal_bw_ethnic_cult, running_continuous > -optimal_bw_ethnic_cult)

# Other
bw_ethnic_oth <- rdbwselect(y = data_ethnic_state_oth$sentiment_clean, x = data_ethnic_state_oth$running_continuous,
                            kernel = "triangular", cluster = data_ethnic_state_oth$source_domain, p = 1, bwselect = "mserd")
optimal_bw_ethnic_oth <- bw_ethnic_oth$bws[1, 1]
cat("Other optimal bandwidth:", round(optimal_bw_ethnic_oth, 1), "units\n")
opt_ethnic_oth <- data_ethnic_state_oth %>% filter(running_continuous < optimal_bw_ethnic_oth, running_continuous > -optimal_bw_ethnic_oth)

model6a_opt_pol <- feols(sentiment_clean ~ running_continuous * treatment * high_russia,
                         cluster = ~source_domain,
                         data = opt_ethnic_pol)
model6a_opt_mil <- feols(sentiment_clean ~ running_continuous * treatment * high_russia,
                         cluster = ~source_domain,
                         data = opt_ethnic_mil)
model6a_opt_econ <- feols(sentiment_clean ~ running_continuous * treatment * high_russia,
                          cluster = ~source_domain,
                          data = opt_ethnic_econ)
model6a_opt_cult <- feols(sentiment_clean ~ running_continuous * treatment * high_russia,
                          cluster = ~source_domain,
                          data = opt_ethnic_cult)
model6a_opt_oth <- feols(sentiment_clean ~ running_continuous * treatment * high_russia,
                         cluster = ~source_domain,
                         data = opt_ethnic_oth)

# Wild cluster bootstrap for topic-specific model6a models (optimal BW)
boot_model6a_opt_pol <- run_wild_bootstrap(model6a_opt_pol, "treatment:high_russia")
boot_model6a_opt_mil <- run_wild_bootstrap(model6a_opt_mil, "treatment:high_russia")
boot_model6a_opt_econ <- run_wild_bootstrap(model6a_opt_econ, "treatment:high_russia")
boot_model6a_opt_cult <- run_wild_bootstrap(model6a_opt_cult, "treatment:high_russia")
boot_model6a_opt_oth <- run_wild_bootstrap(model6a_opt_oth, "treatment:high_russia")

# Wild cluster bootstrap for topic-specific model6a models (full data)
boot_model6a_full_pol <- run_wild_bootstrap(model6a_full_pol, "treatment:high_russia")
boot_model6a_full_mil <- run_wild_bootstrap(model6a_full_mil, "treatment:high_russia")
boot_model6a_full_econ <- run_wild_bootstrap(model6a_full_econ, "treatment:high_russia")
boot_model6a_full_cult <- run_wild_bootstrap(model6a_full_cult, "treatment:high_russia")
boot_model6a_full_oth <- run_wild_bootstrap(model6a_full_oth, "treatment:high_russia")

cat("Bootstrap completed for all model6a topic-specific variants\n")
```

# Placebo Test: December 7th Announcement (Non-Military Topics, Ethnic Russian)

```{r placebo-dec-ethnic}
# Filter to state media non-NATO countries
data_ethnic_state_non_mil_full <- data %>%
  filter(nato == 0) %>%
  filter(state_owned == 1) %>%
  filter(!topic_clean %in% "Military") %>%
  mutate(source_domain = droplevels(source_domain)) %>%
  mutate(running_continuous = running_continuous / 86400)

data_dec_ethnic <- data_ethnic_state_non_mil_full %>%
  filter(date_publish < "2022-02-19") %>%
  mutate(
    running_continuous = as.numeric(date_publish - as.Date("2021-12-07")),
    treatment = ifelse(date_publish < as.Date("2021-12-07"), 0, 1)
  )

bw_placebo_ethnic <- rdbwselect(y = data_dec_ethnic$sentiment_clean,
                                x = data_dec_ethnic$running_continuous,
                                kernel = "triangular",
                                cluster = data_dec_ethnic$source_domain,
                                p = 1,
                                bwselect = "mserd")

optimal_bw_placebo_ethnic <- bw_placebo_ethnic$bws[1, 1]
cat("Placebo optimal bandwidth (ethnic, non-mil):", round(optimal_bw_placebo_ethnic, 1), "units\n")

data_dec_ethnic_bw <- data_dec_ethnic %>%
  filter(running_continuous < optimal_bw_placebo_ethnic, running_continuous > -optimal_bw_placebo_ethnic)

model_placebo_ethnic <- feols(sentiment_clean ~ running_continuous * treatment * high_russia | topic_clean,
                               cluster = ~source_domain,
                               data = data_dec_ethnic_bw)

summary(model_placebo_ethnic)

boot_model_placebo_ethnic <- run_wild_bootstrap(model_placebo_ethnic, "treatment:high_russia")
cat("Bootstrap SE for treatment:high_russia (placebo):", boot_model_placebo_ethnic$se, "\n")
cat("Bootstrap p-value (placebo):", boot_model_placebo_ethnic$p_val, "\n")
cat("\nNote: Non-significant treatment effect suggests parallel trends assumption holds.\n")
```

# Leave-One-Out Country Robustness (Ethnic Russian)

```{r loo-country-ethnic}
data_ethnic_state_non_mil <- data %>%
  filter(nato == 0, state_owned == 1, !topic_clean %in% "Military") %>%
  filter(running_continuous < optimal_bw_ethnic_non_mil, running_continuous > -optimal_bw_ethnic_non_mil)

countries_ethnic <- unique(data_ethnic_state_non_mil$country)
loo_results_ethnic <- list()

for (cntry in countries_ethnic) {
  data_loo <- data_ethnic_state_non_mil %>%
    filter(country != cntry)

  bw_loo <- tryCatch(
    rdbwselect(y = data_loo$sentiment_clean, x = data_loo$running_continuous,
               kernel = "triangular", cluster = data_loo$source_domain,
               p = 1, bwselect = "mserd"),
    error = function(e) NULL
  )

  if (is.null(bw_loo)) next

  optimal_bw_loo <- bw_loo$bws[1, 1]
  data_loo_bw <- data_loo %>%
    filter(running_continuous < optimal_bw_loo, running_continuous > -optimal_bw_loo)

  model_loo <- feols(sentiment_clean ~ running_continuous * treatment * high_russia | topic_clean,
                     cluster = ~source_domain,
                     data = data_loo_bw)

  boot_loo <- tryCatch(
    run_wild_bootstrap(model_loo, "treatment:high_russia", B = 999),
    error = function(e) list(se = NA, p_val = NA, ci_lower = NA, ci_upper = NA, t_stat = NA)
  )

  loo_results_ethnic[[cntry]] <- list(
    model = model_loo,
    bandwidth = optimal_bw_loo,
    n = nrow(data_loo_bw),
    country_dropped = cntry,
    boot_p_val = boot_loo$p_val,
    boot_se = boot_loo$se
  )
}

loo_summary_ethnic <- map_df(names(loo_results_ethnic), function(cntry) {
  mod <- loo_results_ethnic[[cntry]]$model
  tibble(
    country_dropped = cntry,
    estimate = coef(mod)["treatment:high_russia"],
    std_error = se(mod)["treatment:high_russia"],
    p_value = pvalue(mod)["treatment:high_russia"],
    boot_p_val = loo_results_ethnic[[cntry]]$boot_p_val,
    boot_se = loo_results_ethnic[[cntry]]$boot_se,
    n_obs = loo_results_ethnic[[cntry]]$n,
    bandwidth = loo_results_ethnic[[cntry]]$bandwidth
  )
})

print(loo_summary_ethnic)
```

# Summary Table (Table 4F)

```{r table4}
note_t4 <- "All standard errors are clustered at the source level. Articles without publication times are dropped. Model 1 uses no fixed effects. Model 2 uses full data with topic fixed effects. Model 3 uses the optimal bandwidth with topic fixed effects. Model 4 omits military-related articles and uses a re-optimized bandwidth. Model 5 uses only Russian-related (non-military) articles with a re-optimized bandwidth."
note_t4_wrapped <- str_wrap(note_t4, width = 80)

table_4 <- modelsummary(
  list("(1)" = model6a, "(2)" = model6a_full, "(3)" = model6a_opt,
       "(4)" = model6a_opt_non_mil, "(5)" = model6a_opt_russian),
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors",
  title = "Ethnic Russian Population: Difference in Discontinuity Analysis (Drop No-Time Articles)",
  notes = note_t4_wrapped
)

table_4
```

## Summary Table: By Topic (Optimal Bandwidth)

```{r table4b}
note_t4b <- "All standard errors are clustered at the source level. Articles without publication times are dropped. Each model uses a per-topic re-optimized bandwidth. State media in non-NATO countries only."
note_t4b_wrapped <- str_wrap(note_t4b, width = 80)

table_4b <- modelsummary(
  list("Political" = model6a_opt_pol, "Military" = model6a_opt_mil,
       "Economic" = model6a_opt_econ, "Cultural" = model6a_opt_cult, "Other" = model6a_opt_oth),
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors",
  title = "Ethnic Russian Population By Topic (Per-Topic Optimal Bandwidth, Drop No-Time Articles)",
  notes = note_t4b_wrapped
)

table_4b
```

## Summary Table: By Topic (Full Data)

```{r table4c}
note_t4c <- "All standard errors are clustered at the source level. Articles without publication times are dropped. Each model uses the full dataset (no bandwidth restriction). State media in non-NATO countries only."
note_t4c_wrapped <- str_wrap(note_t4c, width = 80)

table_4c <- modelsummary(
  list("Political" = model6a_full_pol, "Military" = model6a_full_mil,
       "Economic" = model6a_full_econ, "Cultural" = model6a_full_cult, "Other" = model6a_full_oth),
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors",
  title = "Ethnic Russian Population By Topic (Full Data, Drop No-Time Articles)",
  notes = note_t4c_wrapped
)

table_4c
```

# Save Results

```{r save}
results_ethnic_drop <- list(
  # Model6a variants
  model6a = model6a,
  model6a_full = model6a_full,
  model6a_opt = model6a_opt,
  model6a_opt_non_mil = model6a_opt_non_mil,
  model6a_opt_russian = model6a_opt_russian,
  model6a_fully_saturated = model6a_fully_saturated,
  model6a_opt_pol = model6a_opt_pol,
  model6a_opt_mil = model6a_opt_mil,
  model6a_opt_econ = model6a_opt_econ,
  model6a_opt_cult = model6a_opt_cult,
  model6a_opt_oth = model6a_opt_oth,
  model6a_full_pol = model6a_full_pol,
  model6a_full_mil = model6a_full_mil,
  model6a_full_econ = model6a_full_econ,
  model6a_full_cult = model6a_full_cult,
  model6a_full_oth = model6a_full_oth,

  # Bootstrap standard errors
  bootstrap_se = list(
    model6a = boot_model6a,
    model6a_full = boot_model6a_full,
    model6a_opt = boot_model6a_opt,
    model6a_opt_non_mil = boot_model6a_opt_non_mil,
    model6a_opt_russian = boot_model6a_opt_russian,
    model6a_fully_saturated = boot_model6a_fully_saturated,
    model6a_opt_pol = boot_model6a_opt_pol,
    model6a_opt_mil = boot_model6a_opt_mil,
    model6a_opt_econ = boot_model6a_opt_econ,
    model6a_opt_cult = boot_model6a_opt_cult,
    model6a_opt_oth = boot_model6a_opt_oth,
    model6a_full_pol = boot_model6a_full_pol,
    model6a_full_mil = boot_model6a_full_mil,
    model6a_full_econ = boot_model6a_full_econ,
    model6a_full_cult = boot_model6a_full_cult,
    model6a_full_oth = boot_model6a_full_oth,
    model_placebo_ethnic = boot_model_placebo_ethnic
  ),

  # Bandwidths
  optimal_bandwidth_ethnic = optimal_bw_ethnic,
  optimal_bw_ethnic_non_mil = optimal_bw_ethnic_non_mil,
  optimal_bw_ethnic_pol = optimal_bw_ethnic_pol,
  optimal_bw_ethnic_mil = optimal_bw_ethnic_mil,
  optimal_bw_ethnic_econ = optimal_bw_ethnic_econ,
  optimal_bw_ethnic_cult = optimal_bw_ethnic_cult,
  optimal_bw_ethnic_oth = optimal_bw_ethnic_oth,

  # Other results
  loo_results_ethnic = loo_results_ethnic,
  loo_summary_ethnic = loo_summary_ethnic,
  model_placebo_ethnic = model_placebo_ethnic,
  optimal_bw_placebo_ethnic = optimal_bw_placebo_ethnic
)

saveRDS(results_ethnic_drop, file.path(DATA_INTERMEDIATE, "07_ethnic_results_drop.rds"))
cat("Results saved to:", file.path(DATA_INTERMEDIATE, "07_ethnic_results_drop.rds"), "\n")
```

# Session Info

```{r session-info}
print_session_info()
```
