---
title: "07B - Ethnic Russian Population Analysis (Drop No-Time Articles)"
author: "Donald Moratz"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

# Overview

This script examines heterogeneous treatment effects by Ethnic Russian Population. It tests whether state-owned media in non-NATO countries with high ethnic Russian populations showed differential sentiment changes following the Russian invasion of Ukraine (H3b). Articles without publication times are dropped. This is an alternative specification to the CSTO analysis (H3) — the null expectation is that ethnic Russian population share does not explain the pattern.

**Analysis:**
- Separate RDDs: High vs Low Ethnic Russian population (rdrobust, Z-score, non-military)
- Diff-in-disc interaction models: Optimal bandwidth and non-military subset (Z-score, topic FEs)
- Matched model (Z-score, topic FEs)
- Placebo test using December 7th 2021 announcement date

**Inputs:**
- `data/intermediate/02_cleaned_data.rds`
- `data/intermediate/02_data_non_ukraine.rds`

**Outputs:**
- `data/intermediate/07_ethnic_results_drop.rds`
- Table 6B (Ethnic Russian Population heterogeneity, Drop No-Time Articles)

```{r setup, include=FALSE}
source("00_setup.R")
knitr::opts_chunk$set(fig.path = paste0(FIGURES_HETEROGENEITY_DROP, "/"))
options(digits = 10)

set.seed(3184)
```

# Load Data

```{r load}
library(fwildclusterboot)

data <- readRDS(file.path(DATA_INTERMEDIATE, "02_cleaned_data.rds"))
data_non_ukraine <- readRDS(file.path(DATA_INTERMEDIATE, "02_data_non_ukraine.rds"))

# Drop articles without publication times
data <- data %>% filter(has_time == TRUE)
data_non_ukraine <- data_non_ukraine %>% filter(has_time == TRUE)

cat("Full data:", nrow(data), "articles\n")
cat("Non-Ukraine data:", nrow(data_non_ukraine), "articles\n")

data <- data %>% mutate(across(c(topic_clean, country, source_domain), as.factor))
data_non_ukraine <- data_non_ukraine %>% mutate(across(c(topic_clean, country, source_domain), as.factor))
```

# Ethnic Russian Population Analysis

## Create Ethnic Subsets

```{r ethnic-data}
data_ethnic <- data %>%
  filter(nato == 0)

data_ethnic <- data_ethnic %>%
  mutate(ethnic_indicator = factor(case_when(
    indicator == 1 & high_russia == 1 ~ "Pre. Ind. High Rus",
    indicator == 1 & high_russia == 0 ~ "Pre. Ind. Low Rus",
    indicator == 2 & high_russia == 1 ~ "Pre. State High Rus",
    indicator == 2 & high_russia == 0 ~ "Pre. State Low Rus",
    indicator == 3 & high_russia == 1 ~ "Post Ind. High Rus",
    indicator == 3 & high_russia == 0 ~ "Post Ind. Low Rus",
    indicator == 4 & high_russia == 1 ~ "Post State High Rus",
    indicator == 4 & high_russia == 0 ~ "Post State Low Rus"
  ),
  levels = c("Pre. Ind. High Rus", "Pre. Ind. Low Rus", "Pre. State High Rus",
             "Pre. State Low Rus", "Post Ind. High Rus", "Post Ind. Low Rus",
             "Post State High Rus", "Post State Low Rus")))

cat("High Russian population:", sum(data_ethnic$high_russia), "\n")
cat("Low Russian population:", sum(data_ethnic$high_russia == 0), "\n")
```

## State Media Subset and Z-Score

```{r ethnic-state-data}
# Convert running_continuous from seconds to days
data_ethnic_state <- data_ethnic %>%
  filter(state_owned == 1) %>%
  mutate(source_domain = droplevels(source_domain)) %>%
  mutate(running_continuous = running_continuous / 86400)

# Compute Z-score on full state media data
data_ethnic_state <- data_ethnic_state %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                   sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()
```

## Visualization: State Media by Ethnic Russian Population

```{r ethnic-plot, fig.width=10, fig.height=7}
agg_data_ethnic <- data_ethnic %>%
  filter(state_owned == 1) %>%
  group_by(running_continuous, csto) %>%
  summarize(sentiment_clean = mean(sentiment_clean), num_obs = n(), .groups = "drop")

ethnic_discs_graph <- data_ethnic %>%
  filter(state_owned == 1) %>%
  ggplot(aes(x = running_continuous, y = sentiment_clean, group = ethnic_indicator, color = ethnic_indicator)) +
  geom_point(data = agg_data_ethnic,
             aes(x = running_continuous, y = sentiment_clean, size = num_obs),
             alpha = 0.2, inherit.aes = FALSE) +
  geom_smooth(method = "lm") +
  scale_color_manual(values = COLORS_DISCS, name = "Source Type") +
  scale_size(name = "Observations") +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.7) +
  theme_classic() +
  labs(
    title = "Effect of Invasion on State Media Sentiment",
    subtitle = "High vs Low Ethnic Russian, Difference in Discontinuities (Drop No-Time)",
    x = "Days Pre/Post Invasion (Continuous)",
    y = "Sentiment"
  )

ethnic_discs_graph

ggsave(plot = ethnic_discs_graph,
       file.path(FIGURES_HETEROGENEITY_DROP, "ethnic_discs.png"),
       width = 10, height = 7)
```

# Separate RDD Models (Z-Score)

## High Ethnic Russian Population

```{r ethnic-high-rdd}
data_high <- data_ethnic_state %>%
  filter(high_russia == 1) %>%
  filter(!topic_clean %in% "Military")

# Recompute Z-score within this subset
data_high <- data_high %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                   sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()

covs_matrix <- model.matrix(~ topic_clean - 1, data = data_high)

model6a_high_z <- rdrobust(
  y = data_high$sentiment_z,
  x = data_high$running_continuous,
  covs = covs_matrix,
  cluster = data_high$source_domain
)

summary(model6a_high_z)
```

## Low Ethnic Russian Population

```{r ethnic-low-rdd}
data_low <- data_ethnic_state %>%
  filter(high_russia == 0) %>%
  filter(!topic_clean %in% "Military")

# Recompute Z-score within this subset
data_low <- data_low %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                   sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()

covs_matrix <- model.matrix(~ topic_clean - 1, data = data_low)

model6a_low_z <- rdrobust(
  y = data_low$sentiment_z,
  x = data_low$running_continuous,
  covs = covs_matrix,
  cluster = data_low$source_domain
)

summary(model6a_low_z)
```

# Interaction Model — Optimal Bandwidth, Z-Score

```{r ethnic-optimal-z}
# Residualize for bandwidth selection
resid_y <- feols(sentiment_z ~ 1 | topic_clean + high_russia,
                 data = data_ethnic_state)$residuals

bw_ethnic_z <- rdbwselect(y = resid_y,
                          x = data_ethnic_state$running_continuous,
                          kernel = "triangular",
                          cluster = data_ethnic_state$source_domain,
                          p = 1,
                          bwselect = "mserd")

optimal_bw_ethnic_z <- bw_ethnic_z$bws[1, 1]
cat("Optimal bandwidth (Z-score):", round(optimal_bw_ethnic_z, 1), "days\n")

optimal_bandwidth_data_z <- data_ethnic_state %>%
  filter(running_continuous < optimal_bw_ethnic_z,
         running_continuous > -optimal_bw_ethnic_z)

model6a_opt_z <- feols(
  sentiment_z ~ running_continuous * treatment * high_russia | topic_clean,
  cluster = ~source_domain,
  data = optimal_bandwidth_data_z
)

summary(model6a_opt_z)

boot_model6a_opt_z <- run_wild_bootstrap(model6a_opt_z, "treatment:high_russia")
cat("Bootstrap SE:", boot_model6a_opt_z$se, "\n")
cat("Bootstrap p-value:", boot_model6a_opt_z$p_val, "\n")
```

# Non-Military Topics, Z-Score

```{r ethnic-non-mil-z}
data_ethnic_state_non_mil <- data_ethnic_state %>%
  filter(!topic_clean %in% "Military")

# Recompute Z-score on non-mil subset
data_ethnic_state_non_mil <- data_ethnic_state_non_mil %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                   sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()

# Residualize for bandwidth selection
resid_y <- feols(sentiment_z ~ 1 | topic_clean + high_russia,
                 data = data_ethnic_state_non_mil)$residuals

bw_ethnic_non_mil_z <- rdbwselect(y = resid_y,
                                  x = data_ethnic_state_non_mil$running_continuous,
                                  kernel = "triangular",
                                  cluster = data_ethnic_state_non_mil$source_domain,
                                  p = 1,
                                  bwselect = "mserd")

optimal_bw_ethnic_non_mil_z <- bw_ethnic_non_mil_z$bws[1, 1]
cat("Optimal bandwidth (non-mil, Z-score):", round(optimal_bw_ethnic_non_mil_z, 1), "days\n")

optimal_bandwidth_data_non_mil_z <- data_ethnic_state_non_mil %>%
  filter(running_continuous < optimal_bw_ethnic_non_mil_z,
         running_continuous > -optimal_bw_ethnic_non_mil_z)

model6a_opt_non_mil_z <- feols(
  sentiment_z ~ running_continuous * treatment * high_russia | topic_clean,
  cluster = ~source_domain,
  data = optimal_bandwidth_data_non_mil_z
)

summary(model6a_opt_non_mil_z)

boot_model6a_opt_non_mil_z <- run_wild_bootstrap(model6a_opt_non_mil_z, "treatment:high_russia")
cat("Bootstrap SE:", boot_model6a_opt_non_mil_z$se, "\n")
cat("Bootstrap p-value:", boot_model6a_opt_non_mil_z$p_val, "\n")
```

# Matched Model, Z-Score

```{r ethnic-matching}
library(MatchIt)
library(cobalt)

# Use running (day variable) for exact matching, not running_continuous
matching_data <- optimal_bandwidth_data_non_mil_z %>%
  select(sentiment_z, running, running_continuous, treatment, high_russia,
         topic_clean, source_domain, country)

ps_model <- matchit(
  high_russia ~ running + topic_clean,
  data = matching_data,
  method = "exact",
  ratio = 1
)

summary(ps_model)
```

## Assess Balance

```{r ethnic-balance}
bal.tab(ps_model, un = TRUE, stats = c("m", "v"), thresholds = c(m = 0.1))
```

## Matching Analysis

```{r ethnic-matched-model}
matched_data <- match.data(ps_model)
cat("Matched observations:", nrow(matched_data), "\n")

matched_model_z <- feols(
  sentiment_z ~ running_continuous * treatment * high_russia | topic_clean,
  cluster = ~source_domain,
  data = matched_data
)

summary(matched_model_z)

boot_matched_model_z <- run_wild_bootstrap(matched_model_z, "treatment:high_russia")
cat("Bootstrap SE:", boot_matched_model_z$se, "\n")
cat("Bootstrap p-value:", boot_matched_model_z$p_val, "\n")
```

# Placebo Test: December 7th Announcement (Non-Military Topics, Ethnic Russian)

```{r placebo-dec-ethnic}
data_dec_ethnic <- data_ethnic_state_non_mil %>%
  filter(date_publish < "2022-02-19") %>%
  mutate(
    running_continuous = as.numeric(date_publish - as.Date("2021-12-07")),
    treatment = ifelse(date_publish < as.Date("2021-12-07"), 0, 1)
  )

# Recompute Z-score for placebo subset
data_dec_ethnic <- data_dec_ethnic %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                   sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()

bw_placebo_ethnic <- rdbwselect(y = data_dec_ethnic$sentiment_z,
                                x = data_dec_ethnic$running_continuous,
                                kernel = "triangular",
                                cluster = data_dec_ethnic$source_domain,
                                p = 1,
                                bwselect = "mserd")

optimal_bw_placebo_ethnic <- bw_placebo_ethnic$bws[1, 1]
cat("Placebo optimal bandwidth (ethnic, non-mil):", round(optimal_bw_placebo_ethnic, 1), "days\n")

data_dec_ethnic_bw <- data_dec_ethnic %>%
  filter(running_continuous < optimal_bw_placebo_ethnic, running_continuous > -optimal_bw_placebo_ethnic)

model_placebo_ethnic <- feols(sentiment_z ~ running_continuous * treatment * high_russia | topic_clean,
                               cluster = ~source_domain,
                               data = data_dec_ethnic_bw)

summary(model_placebo_ethnic)

boot_model_placebo_ethnic <- run_wild_bootstrap(model_placebo_ethnic, "treatment:high_russia")
cat("Bootstrap SE for treatment:high_russia (placebo):", boot_model_placebo_ethnic$se, "\n")
cat("Bootstrap p-value (placebo):", boot_model_placebo_ethnic$p_val, "\n")
cat("\nNote: Non-significant treatment effect suggests parallel trends assumption holds.\n")
```

# Save Results

```{r save}
results_ethnic_drop <- list(
  # Z-score models for Table 6B
  model6a_high_z = model6a_high_z,
  model6a_low_z = model6a_low_z,
  model6a_opt_z = model6a_opt_z,
  model6a_opt_non_mil_z = model6a_opt_non_mil_z,
  matched_model_z = matched_model_z,

  # Bootstrap SEs (only for feols interaction models)
  bootstrap_se = list(
    model6a_opt_z = boot_model6a_opt_z,
    model6a_opt_non_mil_z = boot_model6a_opt_non_mil_z,
    matched_model_z = boot_matched_model_z
  ),

  # Placebo
  model_placebo_ethnic = model_placebo_ethnic,
  optimal_bw_placebo_ethnic = optimal_bw_placebo_ethnic,
  bootstrap_se_placebo = list(
    model_placebo_ethnic = boot_model_placebo_ethnic
  ),

  # Bandwidths
  optimal_bw_ethnic_z = optimal_bw_ethnic_z,
  optimal_bw_ethnic_non_mil_z = optimal_bw_ethnic_non_mil_z
)

saveRDS(results_ethnic_drop, file.path(DATA_INTERMEDIATE, "07_ethnic_results_drop.rds"))
cat("Results saved to:", file.path(DATA_INTERMEDIATE, "07_ethnic_results_drop.rds"), "\n")
```

# Session Info

```{r session-info}
print_session_info()
```
