---
title: "08 - Publication Outputs"
author: "Donald Moratz"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

# Overview

This script generates all publication-quality tables and figures.

**Inputs:**
- `data/intermediate/04_h1_results.rds`
- `data/intermediate/04_h1_results_continuous.rds`
- `data/intermediate/04_h1_results_drop.rds`
- `data/intermediate/04_h1_results_prob.rds`
- `data/intermediate/05_h2_results.rds`
- `data/intermediate/05_h2_results_continuous.rds`
- `data/intermediate/05_h2_results_drop.rds`
- `data/intermediate/05_h2_results_prob.rds`
- `data/intermediate/06_alignment_results.rds`
- `data/intermediate/06_alignment_results_continuous.rds`
- `data/intermediate/06_alignment_results_drop.rds`
- `data/intermediate/06_alignment_results_prob.rds`
- `data/intermediate/07_ethnic_results.rds`
- `data/intermediate/07_ethnic_results_continuous.rds`
- `data/intermediate/07_ethnic_results_drop.rds`
- `data/intermediate/07_ethnic_results_prob.rds`
- `data/intermediate/02_cleaned_data.rds`

**Outputs:**
- Final publication tables (HTML, TeX, PNG)
- Final publication figures

```{r setup, include=FALSE}
source("00_setup.R")
```

# Load Results

```{r load}
# H1: Main RDD results (04 scripts)
results_h1      <- readRDS(file.path(DATA_INTERMEDIATE, "04_h1_results.rds"))
results_h1_cont <- readRDS(file.path(DATA_INTERMEDIATE, "04_h1_results_continuous.rds"))
results_h1_drop <- readRDS(file.path(DATA_INTERMEDIATE, "04_h1_results_drop.rds"))
results_h1_prob <- readRDS(file.path(DATA_INTERMEDIATE, "04_h1_results_prob.rds"))

# H2: Diff-in-disc results (05 scripts)
results_h2      <- readRDS(file.path(DATA_INTERMEDIATE, "05_h2_results.rds"))
results_h2_cont <- readRDS(file.path(DATA_INTERMEDIATE, "05_h2_results_continuous.rds"))
results_h2_drop <- readRDS(file.path(DATA_INTERMEDIATE, "05_h2_results_drop.rds"))
results_h2_prob <- readRDS(file.path(DATA_INTERMEDIATE, "05_h2_results_prob.rds"))

# Russian alignment results (06 scripts – model5a variants)
results_align      <- readRDS(file.path(DATA_INTERMEDIATE, "06_alignment_results.rds"))
results_align_cont <- readRDS(file.path(DATA_INTERMEDIATE, "06_alignment_results_continuous.rds"))
results_align_drop <- readRDS(file.path(DATA_INTERMEDIATE, "06_alignment_results_drop.rds"))
results_align_prob <- readRDS(file.path(DATA_INTERMEDIATE, "06_alignment_results_prob.rds"))

# Ethnic Russian population results (07 scripts – model6a variants)
results_ethnic      <- readRDS(file.path(DATA_INTERMEDIATE, "07_ethnic_results.rds"))
results_ethnic_cont <- readRDS(file.path(DATA_INTERMEDIATE, "07_ethnic_results_continuous.rds"))
results_ethnic_drop <- readRDS(file.path(DATA_INTERMEDIATE, "07_ethnic_results_drop.rds"))
results_ethnic_prob <- readRDS(file.path(DATA_INTERMEDIATE, "07_ethnic_results_prob.rds"))

# Raw data for country classification tables
data <- readRDS(file.path(DATA_INTERMEDIATE, "02_cleaned_data.rds"))

cat("Results loaded successfully.\n")
```

# Helper Functions for Bootstrap Standard Errors

```{r bootstrap-helpers}
# Helper function to create a vcov-like function that returns bootstrap SEs
# This allows modelsummary to display bootstrap standard errors
create_bootstrap_vcov <- function(model, boot_result, coef_name) {
  # Get the original vcov matrix
  original_vcov <- vcov(model)

  # Create a modified vcov matrix with bootstrap SE for the key coefficient
  modified_vcov <- original_vcov

  # Find the coefficient index
  coef_idx <- which(names(coef(model)) == coef_name)

  if (length(coef_idx) > 0 && !is.null(boot_result$se)) {
    # Replace the diagonal element with bootstrap variance (SE^2)
    modified_vcov[coef_idx, coef_idx] <- boot_result$se^2
  }

  return(modified_vcov)
}

# Helper to get significance stars from bootstrap p-value
get_boot_stars <- function(p_val) {
  if (is.null(p_val) || is.na(p_val)) return("")
  if (p_val < 0.001) return("***")
  if (p_val < 0.01) return("**")
  if (p_val < 0.05) return("*")
  return("")
}

# Helper to count unique clusters from a felm model
get_n_clusters <- function(model) {
  tryCatch({
    if ("fixest" %in% class(model)) {
      n_cl <- attr(model$cov.scaled, "G")
      if (!is.null(n_cl)) return(as.character(n_cl))
    }
    return("—")
  }, error = function(e) "—")
}
```

# Table Output Helper

```{r save-table-helper}
# Save a gt table as both .tex and .html
save_table <- function(tbl, name) {
  gtsave(tbl, file.path(FIGURES_TABLES, paste0(name, ".tex")))
  gtsave(tbl, file.path(FIGURES_TABLES, paste0(name, ".html")))
  invisible(tbl)
}

# Standard SE notation footnote appended to all table notes
SE_NOTE <- "† Wild cluster bootstrap SEs (B=9999, Rademacher, null imposed), clustered by source domain. ‡ Cluster-robust SEs from rdrobust."
```

# Table 1: Main RDD Results

```{r table1}
n_cl_t1 <- sapply(list(results_h1$model1_opt, results_h1$model2_opt, results_h1$model3_opt,
                        results_h1$model4_opt, results_h1$model1_full_linear,
                        results_h1$model4_non_mil, results_h1$model4_non_nato), get_n_clusters)
rows_t1 <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7,
  'State FEs', '-', 'X', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', 'X', 'X', 'X', 'X', 'X',
  'Topic FEs', '-', '-', '-', 'X', 'X', 'X', 'X',
  'Clusters', n_cl_t1[1], n_cl_t1[2], n_cl_t1[3], n_cl_t1[4], n_cl_t1[5], n_cl_t1[6], n_cl_t1[7]
)
attr(rows_t1, 'position') <- c(3, 4, 5, 6)

note_t1 <- paste("All standard errors are clustered at the source level. Models 1-4 uses the optimal bandwidth. Model 5 uses a linear specification with the full set of articles. Model 6 omits Military Topics. Model 7 omits NATO allies.", SE_NOTE)

table_1 <- modelsummary(
  list(
    "(1)" = results_h1$model1_opt,
    "(2)" = results_h1$model2_opt,
    "(3)" = results_h1$model3_opt,
    "(4)" = results_h1$model4_opt,
    "(5)" = results_h1$model1_full_linear,
    "(6)" = results_h1$model4_non_mil,
    "(7)" = results_h1$model4_non_nato
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c("treatment" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 1: Effect of Russian Invasion on Media Sentiment (RDD) with Day Running Variable",
  add_rows = rows_t1,
  notes = str_wrap(note_t1, 80)
)

table_1

save_table(table_1, "table_01_rdd_main")
```

## Table 1 A: Continuous Running Variable

```{r table1a}
n_cl_t1a <- sapply(list(results_h1_cont$model1_opt, results_h1_cont$model2_opt,
                         results_h1_cont$model3_opt, results_h1_cont$model4_opt,
                         results_h1_cont$model1_full_linear, results_h1_cont$model4_non_mil,
                         results_h1_cont$model4_non_nato, results_h1_cont$model4_felm_saturated),
                   get_n_clusters)
rows_t1a <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7, ~row8,
  'State FEs', '-', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', 'X', 'X', 'X', 'X', 'X', 'X',
  'Topic FEs', '-', '-', '-', 'X', 'X', 'X', 'X', 'X',
  'Clusters', n_cl_t1a[1], n_cl_t1a[2], n_cl_t1a[3], n_cl_t1a[4], n_cl_t1a[5], n_cl_t1a[6], n_cl_t1a[7], n_cl_t1a[8]
)
attr(rows_t1a, 'position') <- c(3, 4, 5, 6)

note_t1a <- paste("All standard errors are clustered at the source level. Models 1-4 uses the optimal bandwidth. Model 5 uses a linear specification with the full set of articles. Model 6 omits Military Topics. Model 7 omits NATO allies. Model 8 uses full saturation (country-source-topic FEs).", SE_NOTE)

table_1_cont <- modelsummary(
  list(
    "(1)" = results_h1_cont$model1_opt,
    "(2)" = results_h1_cont$model2_opt,
    "(3)" = results_h1_cont$model3_opt,
    "(4)" = results_h1_cont$model4_opt,
    "(5)" = results_h1_cont$model1_full_linear,
    "(6)" = results_h1_cont$model4_non_mil,
    "(7)" = results_h1_cont$model4_non_nato,
    "(8)" = results_h1_cont$model4_felm_saturated
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c("treatment" = "Invasion", "post" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 1A: Effect of Russian Invasion on Media Sentiment (RDD) with Continuous Running Variable",
  add_rows = rows_t1a,
  notes = str_wrap(note_t1a, 80)
)

table_1_cont

save_table(table_1_cont, "table_01a_rdd_continuous")
```

## Table 1B: RDD By Topic (Day)

```{r table1b}
n_cl_t1b <- sapply(list(results_h1$model4_opt_pol, results_h1$model4_opt_mil,
                         results_h1$model4_opt_econ, results_h1$model4_opt_cult,
                         results_h1$model4_opt_oth), get_n_clusters)
rows_t1b <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', 'X', 'X', 'X', 'X', 'X',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t1b[1], n_cl_t1b[2], n_cl_t1b[3], n_cl_t1b[4], n_cl_t1b[5]
)
attr(rows_t1b, 'position') <- c(3, 4, 5, 6)

note_t1b <- paste("All standard errors are clustered at the source level. All models use the optimal bandwidth with country and source fixed effects.", SE_NOTE)

table_1b <- modelsummary(
  list(
    "Political" = results_h1$model4_opt_pol,
    "Military" = results_h1$model4_opt_mil,
    "Economic" = results_h1$model4_opt_econ,
    "Cultural" = results_h1$model4_opt_cult,
    "Other" = results_h1$model4_opt_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c("treatment" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 1B: RDD By Topic (Day Running Variable)",
  add_rows = rows_t1b,
  notes = str_wrap(note_t1b, 80)
)

table_1b

save_table(table_1b, "table_01b_rdd_by_topic_day")
```

## Table 1C: RDD By Topic (Continuous)

```{r table1c}
n_cl_t1c <- sapply(list(results_h1_cont$model4_opt_pol, results_h1_cont$model4_opt_mil,
                         results_h1_cont$model4_opt_econ, results_h1_cont$model4_opt_cult,
                         results_h1_cont$model4_opt_oth), get_n_clusters)
rows_t1c <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', 'X', 'X', 'X', 'X', 'X',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t1c[1], n_cl_t1c[2], n_cl_t1c[3], n_cl_t1c[4], n_cl_t1c[5]
)
attr(rows_t1c, 'position') <- c(3, 4, 5, 6)

note_t1c <- paste("All standard errors are clustered at the source level. All models use the optimal bandwidth with country and source fixed effects.", SE_NOTE)

table_1c <- modelsummary(
  list(
    "Political" = results_h1_cont$model4_opt_pol,
    "Military" = results_h1_cont$model4_opt_mil,
    "Economic" = results_h1_cont$model4_opt_econ,
    "Cultural" = results_h1_cont$model4_opt_cult,
    "Other" = results_h1_cont$model4_opt_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c("treatment" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 1C: RDD By Topic (Continuous Running Variable)",
  add_rows = rows_t1c,
  notes = str_wrap(note_t1c, 80)
)

table_1c

save_table(table_1c, "table_01c_rdd_by_topic_continuous")
```

# Table 2: Diff-in-Disc Results

```{r table2}
n_cl_t2 <- sapply(list(results_h2$model2a, results_h2$model2a_opt, results_h2$model2d,
                        results_h2$model2b, results_h2$model3a, results_h2$model3a_opt),
                  get_n_clusters)
rows_t2 <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6,
  'State FEs', 'X', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-', '-',
  'Topic FEs', 'X', 'X', 'X', 'X', 'X', 'X',
  'Clusters', n_cl_t2[1], n_cl_t2[2], n_cl_t2[3], n_cl_t2[4], n_cl_t2[5], n_cl_t2[6]
)
attr(rows_t2, 'position') <- c(5, 6, 7, 8)

note_t2 <- paste("All standard errors are clustered at the source level. Model 2 uses the optimal bandwidth. Model 3 omits NATO allies. Model 4 omits military-related articles. Model 5 uses only Russian-related articles. Model 6 combines all robustness filters (non-NATO, non-military, Russian-related) with a re-optimized bandwidth.", SE_NOTE)

table_2 <- modelsummary(
  list(
    "(1)" = results_h2$model2a,
    "(2)" = results_h2$model2a_opt,
    "(3)" = results_h2$model2d,
    "(4)" = results_h2$model2b,
    "(5)" = results_h2$model3a,
    "(6)" = results_h2$model3a_opt
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 2: Difference in Discontinuities Analysis",
  add_rows = rows_t2,
  notes = str_wrap(note_t2, 80)
)

table_2

save_table(table_2, "table_02_diff_disc_main")
```

## Table 2A: Diff-in-Disc (Continuous)

```{r table2a}
n_cl_t2a <- sapply(list(results_h2_cont$model2a, results_h2_cont$model2a_opt,
                         results_h2_cont$model2d, results_h2_cont$model2b,
                         results_h2_cont$model3a, results_h2_cont$model3a_opt,
                         results_h2_cont$model3a_opt_saturated), get_n_clusters)
rows_t2a <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7,
  'State FEs', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-', '-', 'X',
  'Topic FEs', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Clusters', n_cl_t2a[1], n_cl_t2a[2], n_cl_t2a[3], n_cl_t2a[4], n_cl_t2a[5], n_cl_t2a[6], n_cl_t2a[7]
)
attr(rows_t2a, 'position') <- c(5, 6, 7, 8)

note_t2a <- paste("All standard errors are clustered at the source level. Model 2 uses the optimal bandwidth. Model 3 omits NATO allies. Model 4 omits military-related articles. Model 5 uses only Russian-related articles. Model 6 combines all robustness filters (non-NATO, non-military, Russian-related) with a re-optimized bandwidth. Model 7 uses full saturation (source-topic and country-state-topic FEs).", SE_NOTE)

table_2a <- modelsummary(
  list(
    "(1)" = results_h2_cont$model2a,
    "(2)" = results_h2_cont$model2a_opt,
    "(3)" = results_h2_cont$model2d,
    "(4)" = results_h2_cont$model2b,
    "(5)" = results_h2_cont$model3a,
    "(6)" = results_h2_cont$model3a_opt,
    "(7)" = results_h2_cont$model3a_opt_saturated
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 2A: Difference in Discontinuities (Continuous Running Variable)",
  add_rows = rows_t2a,
  notes = str_wrap(note_t2a, 80)
)

table_2a

save_table(table_2a, "table_02a_diff_disc_continuous")
```

## Table 2B: Diff-in-Disc By Topic (Day)

```{r table2b}
n_cl_t2b <- sapply(list(results_h2$model2a_opt_pol, results_h2$model2a_opt_mil,
                         results_h2$model2a_opt_econ, results_h2$model2a_opt_cult,
                         results_h2$model2a_opt_oth), get_n_clusters)
rows_t2b <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t2b[1], n_cl_t2b[2], n_cl_t2b[3], n_cl_t2b[4], n_cl_t2b[5]
)
attr(rows_t2b, 'position') <- c(5, 6, 7, 8)

note_t2b <- paste("All standard errors are clustered at the source level. All models use a per-topic re-optimized bandwidth with country fixed effects only.", SE_NOTE)

table_2b <- modelsummary(
  list(
    "Political" = results_h2$model2a_opt_pol,
    "Military" = results_h2$model2a_opt_mil,
    "Economic" = results_h2$model2a_opt_econ,
    "Cultural" = results_h2$model2a_opt_cult,
    "Other" = results_h2$model2a_opt_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 2B: Diff-in-Disc By Topic (Day Running Variable)",
  add_rows = rows_t2b,
  notes = str_wrap(note_t2b, 80)
)

table_2b

save_table(table_2b, "table_02b_diff_disc_by_topic_day")
```

## Table 2C: Diff-in-Disc By Topic (Continuous)

```{r table2c}
n_cl_t2c <- sapply(list(results_h2_cont$model2a_opt_pol, results_h2_cont$model2a_opt_mil,
                         results_h2_cont$model2a_opt_econ, results_h2_cont$model2a_opt_cult,
                         results_h2_cont$model2a_opt_oth), get_n_clusters)
rows_t2c <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t2c[1], n_cl_t2c[2], n_cl_t2c[3], n_cl_t2c[4], n_cl_t2c[5]
)
attr(rows_t2c, 'position') <- c(5, 6, 7, 8)

note_t2c <- paste("All standard errors are clustered at the source level. All models use a per-topic re-optimized bandwidth with country fixed effects only.", SE_NOTE)

table_2c <- modelsummary(
  list(
    "Political" = results_h2_cont$model2a_opt_pol,
    "Military" = results_h2_cont$model2a_opt_mil,
    "Economic" = results_h2_cont$model2a_opt_econ,
    "Cultural" = results_h2_cont$model2a_opt_cult,
    "Other" = results_h2_cont$model2a_opt_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 2C: Diff-in-Disc By Topic (Continuous Running Variable)",
  add_rows = rows_t2c,
  notes = str_wrap(note_t2c, 80)
)

table_2c

save_table(table_2c, "table_02c_diff_disc_by_topic_continuous")
```

## Table 2D: Diff-in-Disc By Topic Full Data (Day)

```{r table2d}
n_cl_t2d <- sapply(list(results_h2$model2a_full_pol, results_h2$model2a_full_mil,
                         results_h2$model2a_full_econ, results_h2$model2a_full_cult,
                         results_h2$model2a_full_oth), get_n_clusters)
rows_t2d <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t2d[1], n_cl_t2d[2], n_cl_t2d[3], n_cl_t2d[4], n_cl_t2d[5]
)
attr(rows_t2d, 'position') <- c(5, 6, 7, 8)

note_t2d <- paste("All standard errors are clustered at the source level. All models use the full dataset (no bandwidth restriction) with country fixed effects only.", SE_NOTE)

table_2d <- modelsummary(
  list(
    "Political" = results_h2$model2a_full_pol,
    "Military" = results_h2$model2a_full_mil,
    "Economic" = results_h2$model2a_full_econ,
    "Cultural" = results_h2$model2a_full_cult,
    "Other" = results_h2$model2a_full_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 2D: Diff-in-Disc By Topic Full Data (Day Running Variable)",
  add_rows = rows_t2d,
  notes = str_wrap(note_t2d, 80)
)

table_2d

save_table(table_2d, "table_02d_diff_disc_by_topic_full_day")
```

## Table 2E: Diff-in-Disc By Topic Full Data (Continuous)

```{r table2e}
n_cl_t2e <- sapply(list(results_h2_cont$model2a_full_pol, results_h2_cont$model2a_full_mil,
                         results_h2_cont$model2a_full_econ, results_h2_cont$model2a_full_cult,
                         results_h2_cont$model2a_full_oth), get_n_clusters)
rows_t2e <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t2e[1], n_cl_t2e[2], n_cl_t2e[3], n_cl_t2e[4], n_cl_t2e[5]
)
attr(rows_t2e, 'position') <- c(5, 6, 7, 8)

note_t2e <- paste("All standard errors are clustered at the source level. All models use the full dataset (no bandwidth restriction) with country fixed effects only.", SE_NOTE)

table_2e <- modelsummary(
  list(
    "Political" = results_h2_cont$model2a_full_pol,
    "Military" = results_h2_cont$model2a_full_mil,
    "Economic" = results_h2_cont$model2a_full_econ,
    "Cultural" = results_h2_cont$model2a_full_cult,
    "Other" = results_h2_cont$model2a_full_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 2E: Diff-in-Disc By Topic Full Data (Continuous Running Variable)",
  add_rows = rows_t2e,
  notes = str_wrap(note_t2e, 80)
)

table_2e

save_table(table_2e, "table_02e_diff_disc_by_topic_full_continuous")
```

# Table 3: Heterogeneity by Russian Alignment

```{r table3}
n_cl_t3 <- sapply(list(results_align$model5a_csto, results_align$model5a_neutral,
                       results_align$model5a_full, results_align$model5a_opt,
                       results_align$model5a_opt_non_mil, results_align$model5a_opt_russian,
                       results_align$model5a_opt_full_fe, results_align$model5a_opt_non_mil_full_fe,
                       results_align$model5a_fully_saturated), get_n_clusters)
rows_t3 <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7, ~row8, ~row9,
  'State FEs', '-', '-', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-', '-', 'X', 'X', 'X',
  'Topic FEs', '-', '-', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Country Dummies', '-', '-', '-', '-', '-', '-', 'X', 'X', '-',
  'Clusters', n_cl_t3[1], n_cl_t3[2], n_cl_t3[3], n_cl_t3[4], n_cl_t3[5], n_cl_t3[6], n_cl_t3[7], n_cl_t3[8], n_cl_t3[9]
)
attr(rows_t3, 'position') <- c(5, 6, 7, 8, 9)

note_t3 <- paste("Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights) for Models 3-9, clustered at source level. Models 1-2 use rdrobust standard errors. Model 1 shows RDD results for CSTO countries only. Model 2 shows RDD results for Neutral countries only. Model 3 uses full data with topic fixed effects. Model 4 uses the optimal bandwidth with topic fixed effects. Model 5 omits military-related articles and uses a re-optimized bandwidth. Model 6 uses only Russian-related (non-military) articles with a re-optimized bandwidth. Model 7 uses optimal bandwidth with full FEs (topic + source + country dummies). Model 8 uses non-military subset with full FEs. Model 9 uses full saturation (source-topic and topic-treatment FEs). Sample restricted to state-owned media in non-NATO countries.", SE_NOTE)

# Create vcov list with bootstrap SEs for felm models (columns 3-9)
vcov_t3 <- list(
  NULL,
  NULL,
  "(3)" = create_bootstrap_vcov(results_align$model5a_full, results_align$bootstrap_se$model5a_full, "treatment:csto"),
  "(4)" = create_bootstrap_vcov(results_align$model5a_opt, results_align$bootstrap_se$model5a_opt, "treatment:csto"),
  "(5)" = create_bootstrap_vcov(results_align$model5a_opt_non_mil, results_align$bootstrap_se$model5a_opt_non_mil, "treatment:csto"),
  "(6)" = create_bootstrap_vcov(results_align$model5a_opt_russian, results_align$bootstrap_se$model5a_opt_russian, "treatment:csto"),
  "(7)" = create_bootstrap_vcov(results_align$model5a_opt_full_fe, results_align$bootstrap_se$model5a_opt_full_fe, "treatment:csto"),
  "(8)" = create_bootstrap_vcov(results_align$model5a_opt_non_mil_full_fe, results_align$bootstrap_se$model5a_opt_non_mil_full_fe, "treatment:csto"),
  "(9)" = create_bootstrap_vcov(results_align$model5a_fully_saturated, results_align$bootstrap_se$model5a_fully_saturated, "treatment:csto")
)

table_3 <- modelsummary(
  list(
    "(1)" = results_align$model5a_csto,
    "(2)" = results_align$model5a_neutral,
    "(3)" = results_align$model5a_full,
    "(4)" = results_align$model5a_opt,
    "(5)" = results_align$model5a_opt_non_mil,
    "(6)" = results_align$model5a_opt_russian,
    "(7)" = results_align$model5a_opt_full_fe,
    "(8)" = results_align$model5a_opt_non_mil_full_fe,
    "(9)" = results_align$model5a_fully_saturated
  ),
  vcov = vcov_t3,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 3: Russian Alignment Heterogeneity (State Media)",
  add_rows = rows_t3,
  notes = str_wrap(note_t3, 80)
)

table_3

save_table(table_3, "table_03_alignment_main")
```


## Table 3A: Heterogeneity (Continuous)

```{r table3a}
n_cl_t3a <- sapply(list(results_align_cont$model5a_csto, results_align_cont$model5a_neutral,
                        results_align_cont$model5a_full, results_align_cont$model5a_opt,
                        results_align_cont$model5a_opt_non_mil, results_align_cont$model5a_opt_russian,
                        results_align_cont$model5a_opt_full_fe, results_align_cont$model5a_opt_non_mil_full_fe,
                        results_align_cont$model5a_fully_saturated),
                   get_n_clusters)
rows_t3a <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7, ~row8, ~row9,
  'State FEs', '-', '-', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-', '-', 'X', 'X', 'X',
  'Topic FEs', '-', '-', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Country Dummies', '-', '-', '-', '-', '-', '-', 'X', 'X', '-',
  'Clusters', n_cl_t3a[1], n_cl_t3a[2], n_cl_t3a[3], n_cl_t3a[4], n_cl_t3a[5], n_cl_t3a[6], n_cl_t3a[7], n_cl_t3a[8], n_cl_t3a[9]
)
attr(rows_t3a, 'position') <- c(5, 6, 7, 8, 9)

note_t3a <- paste("Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights) for Models 3-9, clustered at source level. Models 1-2 use rdrobust standard errors. Model 1 shows RDD results for CSTO countries only. Model 2 shows RDD results for Neutral countries only. Model 3 uses full data with topic fixed effects. Model 4 uses the optimal bandwidth with topic fixed effects. Model 5 omits military-related articles and uses a re-optimized bandwidth. Model 6 uses only Russian-related (non-military) articles with a re-optimized bandwidth. Model 7 uses optimal bandwidth with full FEs (topic + source + country dummies). Model 8 uses non-military subset with full FEs. Model 9 uses full saturation (source-topic and topic-treatment FEs). Sample restricted to state-owned media in non-NATO countries.", SE_NOTE)

# Create vcov list with bootstrap SEs for felm models
vcov_t3a <- list(
  NULL,
  NULL,
  "(3)" = create_bootstrap_vcov(results_align_cont$model5a_full, results_align_cont$bootstrap_se$model5a_full, "treatment:csto"),
  "(4)" = create_bootstrap_vcov(results_align_cont$model5a_opt, results_align_cont$bootstrap_se$model5a_opt, "treatment:csto"),
  "(5)" = create_bootstrap_vcov(results_align_cont$model5a_opt_non_mil, results_align_cont$bootstrap_se$model5a_opt_non_mil, "treatment:csto"),
  "(6)" = create_bootstrap_vcov(results_align_cont$model5a_opt_russian, results_align_cont$bootstrap_se$model5a_opt_russian, "treatment:csto"),
  "(7)" = create_bootstrap_vcov(results_align_cont$model5a_opt_full_fe, results_align_cont$bootstrap_se$model5a_opt_full_fe, "treatment:csto"),
  "(8)" = create_bootstrap_vcov(results_align_cont$model5a_opt_non_mil_full_fe, results_align_cont$bootstrap_se$model5a_opt_non_mil_full_fe, "treatment:csto"),
  "(9)" = create_bootstrap_vcov(results_align_cont$model5a_fully_saturated, results_align_cont$bootstrap_se$model5a_fully_saturated, "treatment:csto")
)

table_3a <- modelsummary(
  list(
    "(1)" = results_align_cont$model5a_csto,
    "(2)" = results_align_cont$model5a_neutral,
    "(3)" = results_align_cont$model5a_full,
    "(4)" = results_align_cont$model5a_opt,
    "(5)" = results_align_cont$model5a_opt_non_mil,
    "(6)" = results_align_cont$model5a_opt_russian,
    "(7)" = results_align_cont$model5a_opt_full_fe,
    "(8)" = results_align_cont$model5a_opt_non_mil_full_fe,
    "(9)" = results_align_cont$model5a_fully_saturated
  ),
  vcov = vcov_t3a,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 3A: Russian Alignment Heterogeneity (Continuous Running Variable)",
  add_rows = rows_t3a,
  notes = str_wrap(note_t3a, 80)
)

table_3a

save_table(table_3a, "table_03a_alignment_continuous")
```

## Table 3B: Heterogeneity By Topic Optimal BW (Day)

```{r table3b}
n_cl_t3b <- sapply(list(results_align$model5a_opt_pol, results_align$model5a_opt_mil,
                        results_align$model5a_opt_econ, results_align$model5a_opt_cult,
                        results_align$model5a_opt_oth), get_n_clusters)
rows_t3b <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t3b[1], n_cl_t3b[2], n_cl_t3b[3], n_cl_t3b[4], n_cl_t3b[5]
)
attr(rows_t3b, 'position') <- c(5, 6, 7, 8)

note_t3b <- paste("Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights), clustered at source level. Each model uses a per-topic re-optimized bandwidth. State media in non-NATO countries only.", SE_NOTE)

# Create vcov list with bootstrap SEs for topic models
vcov_t3b <- list(
  "Political" = create_bootstrap_vcov(results_align$model5a_opt_pol, results_align$bootstrap_se$model5a_opt_pol, "treatment:csto"),
  "Military" = create_bootstrap_vcov(results_align$model5a_opt_mil, results_align$bootstrap_se$model5a_opt_mil, "treatment:csto"),
  "Economic" = create_bootstrap_vcov(results_align$model5a_opt_econ, results_align$bootstrap_se$model5a_opt_econ, "treatment:csto"),
  "Cultural" = create_bootstrap_vcov(results_align$model5a_opt_cult, results_align$bootstrap_se$model5a_opt_cult, "treatment:csto"),
  "Other" = create_bootstrap_vcov(results_align$model5a_opt_oth, results_align$bootstrap_se$model5a_opt_oth, "treatment:csto")
)

table_3b <- modelsummary(
  list(
    "Political" = results_align$model5a_opt_pol,
    "Military" = results_align$model5a_opt_mil,
    "Economic" = results_align$model5a_opt_econ,
    "Cultural" = results_align$model5a_opt_cult,
    "Other" = results_align$model5a_opt_oth
  ),
  vcov = vcov_t3b,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 3B: Heterogeneity By Topic (Per-Topic Optimal BW, Day)",
  add_rows = rows_t3b,
  notes = str_wrap(note_t3b, 80)
)

table_3b

save_table(table_3b, "table_03b_alignment_by_topic_day")
```

## Table 3C: Heterogeneity By Topic Optimal BW (Continuous)

```{r table3c}
n_cl_t3c <- sapply(list(results_align_cont$model5a_opt_pol, results_align_cont$model5a_opt_mil,
                        results_align_cont$model5a_opt_econ, results_align_cont$model5a_opt_cult,
                        results_align_cont$model5a_opt_oth), get_n_clusters)
rows_t3c <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t3c[1], n_cl_t3c[2], n_cl_t3c[3], n_cl_t3c[4], n_cl_t3c[5]
)
attr(rows_t3c, 'position') <- c(5, 6, 7, 8)

note_t3c <- paste("Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights), clustered at source level. Each model uses a per-topic re-optimized bandwidth. State media in non-NATO countries only.", SE_NOTE)

# Create vcov list with bootstrap SEs for topic models
vcov_t3c <- list(
  "Political" = create_bootstrap_vcov(results_align_cont$model5a_opt_pol, results_align_cont$bootstrap_se$model5a_opt_pol, "treatment:csto"),
  "Military" = create_bootstrap_vcov(results_align_cont$model5a_opt_mil, results_align_cont$bootstrap_se$model5a_opt_mil, "treatment:csto"),
  "Economic" = create_bootstrap_vcov(results_align_cont$model5a_opt_econ, results_align_cont$bootstrap_se$model5a_opt_econ, "treatment:csto"),
  "Cultural" = create_bootstrap_vcov(results_align_cont$model5a_opt_cult, results_align_cont$bootstrap_se$model5a_opt_cult, "treatment:csto"),
  "Other" = create_bootstrap_vcov(results_align_cont$model5a_opt_oth, results_align_cont$bootstrap_se$model5a_opt_oth, "treatment:csto")
)

table_3c <- modelsummary(
  list(
    "Political" = results_align_cont$model5a_opt_pol,
    "Military" = results_align_cont$model5a_opt_mil,
    "Economic" = results_align_cont$model5a_opt_econ,
    "Cultural" = results_align_cont$model5a_opt_cult,
    "Other" = results_align_cont$model5a_opt_oth
  ),
  vcov = vcov_t3c,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 3C: Heterogeneity By Topic (Per-Topic Optimal BW, Continuous)",
  add_rows = rows_t3c,
  notes = str_wrap(note_t3c, 80)
)

table_3c

save_table(table_3c, "table_03c_alignment_by_topic_continuous")
```

## Table 3D: Heterogeneity By Topic Full Data (Day)

```{r table3d}
n_cl_t3d <- sapply(list(results_align$model5a_full_pol, results_align$model5a_full_mil,
                        results_align$model5a_full_econ, results_align$model5a_full_cult,
                        results_align$model5a_full_oth), get_n_clusters)
rows_t3d <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t3d[1], n_cl_t3d[2], n_cl_t3d[3], n_cl_t3d[4], n_cl_t3d[5]
)
attr(rows_t3d, 'position') <- c(5, 6, 7, 8)

note_t3d <- paste("Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights), clustered at source level. Each model uses the full dataset (no bandwidth restriction). State media in non-NATO countries only.", SE_NOTE)

# Create vcov list with bootstrap SEs for topic models
vcov_t3d <- list(
  "Political" = create_bootstrap_vcov(results_align$model5a_full_pol, results_align$bootstrap_se$model5a_full_pol, "treatment:csto"),
  "Military" = create_bootstrap_vcov(results_align$model5a_full_mil, results_align$bootstrap_se$model5a_full_mil, "treatment:csto"),
  "Economic" = create_bootstrap_vcov(results_align$model5a_full_econ, results_align$bootstrap_se$model5a_full_econ, "treatment:csto"),
  "Cultural" = create_bootstrap_vcov(results_align$model5a_full_cult, results_align$bootstrap_se$model5a_full_cult, "treatment:csto"),
  "Other" = create_bootstrap_vcov(results_align$model5a_full_oth, results_align$bootstrap_se$model5a_full_oth, "treatment:csto")
)

table_3d <- modelsummary(
  list(
    "Political" = results_align$model5a_full_pol,
    "Military" = results_align$model5a_full_mil,
    "Economic" = results_align$model5a_full_econ,
    "Cultural" = results_align$model5a_full_cult,
    "Other" = results_align$model5a_full_oth
  ),
  vcov = vcov_t3d,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 3D: Heterogeneity By Topic (Full Data, Day)",
  add_rows = rows_t3d,
  notes = str_wrap(note_t3d, 80)
)

table_3d

save_table(table_3d, "table_03d_alignment_by_topic_full_day")
```

## Table 3E: Heterogeneity By Topic Full Data (Continuous)

```{r table3e}
n_cl_t3e <- sapply(list(results_align_cont$model5a_full_pol, results_align_cont$model5a_full_mil,
                        results_align_cont$model5a_full_econ, results_align_cont$model5a_full_cult,
                        results_align_cont$model5a_full_oth), get_n_clusters)
rows_t3e <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t3e[1], n_cl_t3e[2], n_cl_t3e[3], n_cl_t3e[4], n_cl_t3e[5]
)
attr(rows_t3e, 'position') <- c(5, 6, 7, 8)

note_t3e <- paste("Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights), clustered at source level. Each model uses the full dataset (no bandwidth restriction). State media in non-NATO countries only.", SE_NOTE)

# Create vcov list with bootstrap SEs for topic models
vcov_t3e <- list(
  "Political" = create_bootstrap_vcov(results_align_cont$model5a_full_pol, results_align_cont$bootstrap_se$model5a_full_pol, "treatment:csto"),
  "Military" = create_bootstrap_vcov(results_align_cont$model5a_full_mil, results_align_cont$bootstrap_se$model5a_full_mil, "treatment:csto"),
  "Economic" = create_bootstrap_vcov(results_align_cont$model5a_full_econ, results_align_cont$bootstrap_se$model5a_full_econ, "treatment:csto"),
  "Cultural" = create_bootstrap_vcov(results_align_cont$model5a_full_cult, results_align_cont$bootstrap_se$model5a_full_cult, "treatment:csto"),
  "Other" = create_bootstrap_vcov(results_align_cont$model5a_full_oth, results_align_cont$bootstrap_se$model5a_full_oth, "treatment:csto")
)

table_3e <- modelsummary(
  list(
    "Political" = results_align_cont$model5a_full_pol,
    "Military" = results_align_cont$model5a_full_mil,
    "Economic" = results_align_cont$model5a_full_econ,
    "Cultural" = results_align_cont$model5a_full_cult,
    "Other" = results_align_cont$model5a_full_oth
  ),
  vcov = vcov_t3e,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 3E: Heterogeneity By Topic (Full Data, Continuous)",
  add_rows = rows_t3e,
  notes = str_wrap(note_t3e, 80)
)

table_3e

save_table(table_3e, "table_03e_alignment_by_topic_full_continuous")
```

# Table 4: Heterogeneity by Ethnic Russian Population

```{r table4}
n_cl_t4 <- sapply(list(results_ethnic$model6a_full, results_ethnic$model6a_opt,
                       results_ethnic$model6a_opt_non_mil, results_ethnic$model6a_opt_russian),
                  get_n_clusters)
rows_t4 <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4,
  'State FEs', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-',
  'Topic FEs', 'X', 'X', 'X', 'X',
  'Clusters', n_cl_t4[1], n_cl_t4[2], n_cl_t4[3], n_cl_t4[4]
)
attr(rows_t4, 'position') <- c(5, 6, 7, 8)

note_t4 <- paste("Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights), clustered at source level. Model 1 uses full data with topic fixed effects. Model 2 uses the optimal bandwidth with topic fixed effects. Model 3 omits military-related articles and uses a re-optimized bandwidth. Model 4 uses only Russian-related (non-military) articles with a re-optimized bandwidth. Sample restricted to state-owned media in non-NATO countries.", SE_NOTE)

# Create vcov list with bootstrap SEs for all models
vcov_t4 <- list(
  "(1)" = create_bootstrap_vcov(results_ethnic$model6a_full, results_ethnic$bootstrap_se$model6a_full, "treatment:high_russia"),
  "(2)" = create_bootstrap_vcov(results_ethnic$model6a_opt, results_ethnic$bootstrap_se$model6a_opt, "treatment:high_russia"),
  "(3)" = create_bootstrap_vcov(results_ethnic$model6a_opt_non_mil, results_ethnic$bootstrap_se$model6a_opt_non_mil, "treatment:high_russia"),
  "(4)" = create_bootstrap_vcov(results_ethnic$model6a_opt_russian, results_ethnic$bootstrap_se$model6a_opt_russian, "treatment:high_russia")
)

table_4 <- modelsummary(
  list(
    "(1)" = results_ethnic$model6a_full,
    "(2)" = results_ethnic$model6a_opt,
    "(3)" = results_ethnic$model6a_opt_non_mil,
    "(4)" = results_ethnic$model6a_opt_russian
  ),
  vcov = vcov_t4,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 4: Ethnic Russian Population Heterogeneity (State Media)",
  add_rows = rows_t4,
  notes = str_wrap(note_t4, 80)
)

table_4

save_table(table_4, "table_04_ethnic_main")
```

## Table 4A: Ethnic Heterogeneity (Continuous)

```{r table4a}
n_cl_t4a <- sapply(list(results_ethnic_cont$model6a_full, results_ethnic_cont$model6a_opt,
                        results_ethnic_cont$model6a_opt_non_mil, results_ethnic_cont$model6a_opt_russian),
                   get_n_clusters)
rows_t4a <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4,
  'State FEs', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-',
  'Topic FEs', 'X', 'X', 'X', 'X',
  'Clusters', n_cl_t4a[1], n_cl_t4a[2], n_cl_t4a[3], n_cl_t4a[4]
)
attr(rows_t4a, 'position') <- c(5, 6, 7, 8)

note_t4a <- paste("Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights), clustered at source level. Model 1 uses full data with topic fixed effects. Model 2 uses the optimal bandwidth with topic fixed effects. Model 3 omits military-related articles and uses a re-optimized bandwidth. Model 4 uses only Russian-related (non-military) articles with a re-optimized bandwidth. Sample restricted to state-owned media in non-NATO countries.", SE_NOTE)

# Create vcov list with bootstrap SEs
vcov_t4a <- list(
  "(1)" = create_bootstrap_vcov(results_ethnic_cont$model6a_full, results_ethnic_cont$bootstrap_se$model6a_full, "treatment:high_russia"),
  "(2)" = create_bootstrap_vcov(results_ethnic_cont$model6a_opt, results_ethnic_cont$bootstrap_se$model6a_opt, "treatment:high_russia"),
  "(3)" = create_bootstrap_vcov(results_ethnic_cont$model6a_opt_non_mil, results_ethnic_cont$bootstrap_se$model6a_opt_non_mil, "treatment:high_russia"),
  "(4)" = create_bootstrap_vcov(results_ethnic_cont$model6a_opt_russian, results_ethnic_cont$bootstrap_se$model6a_opt_russian, "treatment:high_russia")
)

table_4a <- modelsummary(
  list(
    "(1)" = results_ethnic_cont$model6a_full,
    "(2)" = results_ethnic_cont$model6a_opt,
    "(3)" = results_ethnic_cont$model6a_opt_non_mil,
    "(4)" = results_ethnic_cont$model6a_opt_russian
  ),
  vcov = vcov_t4a,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 4A: Ethnic Russian Population Heterogeneity (Continuous Running Variable)",
  add_rows = rows_t4a,
  notes = str_wrap(note_t4a, 80)
)

table_4a

save_table(table_4a, "table_04a_ethnic_continuous")
```

## Table 4B: Ethnic By Topic Optimal BW (Day)

```{r table4b}
n_cl_t4b <- sapply(list(results_ethnic$model6a_opt_pol, results_ethnic$model6a_opt_mil,
                        results_ethnic$model6a_opt_econ, results_ethnic$model6a_opt_cult,
                        results_ethnic$model6a_opt_oth), get_n_clusters)
rows_t4b <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t4b[1], n_cl_t4b[2], n_cl_t4b[3], n_cl_t4b[4], n_cl_t4b[5]
)
attr(rows_t4b, 'position') <- c(5, 6, 7, 8)

note_t4b <- paste("Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights), clustered at source level. Each model uses a per-topic re-optimized bandwidth. State media in non-NATO countries only.", SE_NOTE)

# Create vcov list with bootstrap SEs for topic models
vcov_t4b <- list(
  "Political" = create_bootstrap_vcov(results_ethnic$model6a_opt_pol, results_ethnic$bootstrap_se$model6a_opt_pol, "treatment:high_russia"),
  "Military" = create_bootstrap_vcov(results_ethnic$model6a_opt_mil, results_ethnic$bootstrap_se$model6a_opt_mil, "treatment:high_russia"),
  "Economic" = create_bootstrap_vcov(results_ethnic$model6a_opt_econ, results_ethnic$bootstrap_se$model6a_opt_econ, "treatment:high_russia"),
  "Cultural" = create_bootstrap_vcov(results_ethnic$model6a_opt_cult, results_ethnic$bootstrap_se$model6a_opt_cult, "treatment:high_russia"),
  "Other" = create_bootstrap_vcov(results_ethnic$model6a_opt_oth, results_ethnic$bootstrap_se$model6a_opt_oth, "treatment:high_russia")
)

table_4b <- modelsummary(
  list(
    "Political" = results_ethnic$model6a_opt_pol,
    "Military" = results_ethnic$model6a_opt_mil,
    "Economic" = results_ethnic$model6a_opt_econ,
    "Cultural" = results_ethnic$model6a_opt_cult,
    "Other" = results_ethnic$model6a_opt_oth
  ),
  vcov = vcov_t4b,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 4B: Ethnic Heterogeneity By Topic (Per-Topic Optimal BW, Day)",
  add_rows = rows_t4b,
  notes = str_wrap(note_t4b, 80)
)

table_4b

save_table(table_4b, "table_04b_ethnic_by_topic_day")
```

## Table 4C: Ethnic By Topic Optimal BW (Continuous)

```{r table4c}
n_cl_t4c <- sapply(list(results_ethnic_cont$model6a_opt_pol, results_ethnic_cont$model6a_opt_mil,
                        results_ethnic_cont$model6a_opt_econ, results_ethnic_cont$model6a_opt_cult,
                        results_ethnic_cont$model6a_opt_oth), get_n_clusters)
rows_t4c <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t4c[1], n_cl_t4c[2], n_cl_t4c[3], n_cl_t4c[4], n_cl_t4c[5]
)
attr(rows_t4c, 'position') <- c(5, 6, 7, 8)

note_t4c <- paste("Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights), clustered at source level. Each model uses a per-topic re-optimized bandwidth. State media in non-NATO countries only.", SE_NOTE)

# Create vcov list with bootstrap SEs for topic models
vcov_t4c <- list(
  "Political" = create_bootstrap_vcov(results_ethnic_cont$model6a_opt_pol, results_ethnic_cont$bootstrap_se$model6a_opt_pol, "treatment:high_russia"),
  "Military" = create_bootstrap_vcov(results_ethnic_cont$model6a_opt_mil, results_ethnic_cont$bootstrap_se$model6a_opt_mil, "treatment:high_russia"),
  "Economic" = create_bootstrap_vcov(results_ethnic_cont$model6a_opt_econ, results_ethnic_cont$bootstrap_se$model6a_opt_econ, "treatment:high_russia"),
  "Cultural" = create_bootstrap_vcov(results_ethnic_cont$model6a_opt_cult, results_ethnic_cont$bootstrap_se$model6a_opt_cult, "treatment:high_russia"),
  "Other" = create_bootstrap_vcov(results_ethnic_cont$model6a_opt_oth, results_ethnic_cont$bootstrap_se$model6a_opt_oth, "treatment:high_russia")
)

table_4c <- modelsummary(
  list(
    "Political" = results_ethnic_cont$model6a_opt_pol,
    "Military" = results_ethnic_cont$model6a_opt_mil,
    "Economic" = results_ethnic_cont$model6a_opt_econ,
    "Cultural" = results_ethnic_cont$model6a_opt_cult,
    "Other" = results_ethnic_cont$model6a_opt_oth
  ),
  vcov = vcov_t4c,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 4C: Ethnic Heterogeneity By Topic (Per-Topic Optimal BW, Continuous)",
  add_rows = rows_t4c,
  notes = str_wrap(note_t4c, 80)
)

table_4c

save_table(table_4c, "table_04c_ethnic_by_topic_continuous")
```

## Table 4D: Ethnic By Topic Full Data (Day)

```{r table4d}
n_cl_t4d <- sapply(list(results_ethnic$model6a_full_pol, results_ethnic$model6a_full_mil,
                        results_ethnic$model6a_full_econ, results_ethnic$model6a_full_cult,
                        results_ethnic$model6a_full_oth), get_n_clusters)
rows_t4d <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t4d[1], n_cl_t4d[2], n_cl_t4d[3], n_cl_t4d[4], n_cl_t4d[5]
)
attr(rows_t4d, 'position') <- c(5, 6, 7, 8)

note_t4d <- paste("Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights), clustered at source level. Each model uses the full dataset (no bandwidth restriction). State media in non-NATO countries only.", SE_NOTE)

# Create vcov list with bootstrap SEs for topic models
vcov_t4d <- list(
  "Political" = create_bootstrap_vcov(results_ethnic$model6a_full_pol, results_ethnic$bootstrap_se$model6a_full_pol, "treatment:high_russia"),
  "Military" = create_bootstrap_vcov(results_ethnic$model6a_full_mil, results_ethnic$bootstrap_se$model6a_full_mil, "treatment:high_russia"),
  "Economic" = create_bootstrap_vcov(results_ethnic$model6a_full_econ, results_ethnic$bootstrap_se$model6a_full_econ, "treatment:high_russia"),
  "Cultural" = create_bootstrap_vcov(results_ethnic$model6a_full_cult, results_ethnic$bootstrap_se$model6a_full_cult, "treatment:high_russia"),
  "Other" = create_bootstrap_vcov(results_ethnic$model6a_full_oth, results_ethnic$bootstrap_se$model6a_full_oth, "treatment:high_russia")
)

table_4d <- modelsummary(
  list(
    "Political" = results_ethnic$model6a_full_pol,
    "Military" = results_ethnic$model6a_full_mil,
    "Economic" = results_ethnic$model6a_full_econ,
    "Cultural" = results_ethnic$model6a_full_cult,
    "Other" = results_ethnic$model6a_full_oth
  ),
  vcov = vcov_t4d,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 4D: Ethnic Heterogeneity By Topic (Full Data, Day)",
  add_rows = rows_t4d,
  notes = str_wrap(note_t4d, 80)
)

table_4d

save_table(table_4d, "table_04d_ethnic_by_topic_full_day")
```

## Table 4E: Ethnic By Topic Full Data (Continuous)

```{r table4e}
n_cl_t4e <- sapply(list(results_ethnic_cont$model6a_full_pol, results_ethnic_cont$model6a_full_mil,
                        results_ethnic_cont$model6a_full_econ, results_ethnic_cont$model6a_full_cult,
                        results_ethnic_cont$model6a_full_oth), get_n_clusters)
rows_t4e <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t4e[1], n_cl_t4e[2], n_cl_t4e[3], n_cl_t4e[4], n_cl_t4e[5]
)
attr(rows_t4e, 'position') <- c(5, 6, 7, 8)

note_t4e <- paste("Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights), clustered at source level. Each model uses the full dataset (no bandwidth restriction). State media in non-NATO countries only.", SE_NOTE)

# Create vcov list with bootstrap SEs for topic models
vcov_t4e <- list(
  "Political" = create_bootstrap_vcov(results_ethnic_cont$model6a_full_pol, results_ethnic_cont$bootstrap_se$model6a_full_pol, "treatment:high_russia"),
  "Military" = create_bootstrap_vcov(results_ethnic_cont$model6a_full_mil, results_ethnic_cont$bootstrap_se$model6a_full_mil, "treatment:high_russia"),
  "Economic" = create_bootstrap_vcov(results_ethnic_cont$model6a_full_econ, results_ethnic_cont$bootstrap_se$model6a_full_econ, "treatment:high_russia"),
  "Cultural" = create_bootstrap_vcov(results_ethnic_cont$model6a_full_cult, results_ethnic_cont$bootstrap_se$model6a_full_cult, "treatment:high_russia"),
  "Other" = create_bootstrap_vcov(results_ethnic_cont$model6a_full_oth, results_ethnic_cont$bootstrap_se$model6a_full_oth, "treatment:high_russia")
)

table_4e <- modelsummary(
  list(
    "Political" = results_ethnic_cont$model6a_full_pol,
    "Military" = results_ethnic_cont$model6a_full_mil,
    "Economic" = results_ethnic_cont$model6a_full_econ,
    "Cultural" = results_ethnic_cont$model6a_full_cult,
    "Other" = results_ethnic_cont$model6a_full_oth
  ),
  vcov = vcov_t4e,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 4E: Ethnic Heterogeneity By Topic (Full Data, Continuous)",
  add_rows = rows_t4e,
  notes = str_wrap(note_t4e, 80)
)

table_4e

save_table(table_4e, "table_04e_ethnic_by_topic_full_continuous")
```

# Drop No-Time Articles Variant Tables

## Table 1D: RDD Main (Drop No-Time)

```{r table1d}
n_cl_t1d <- sapply(list(results_h1_drop$model1_opt, results_h1_drop$model2_opt,
                        results_h1_drop$model3_opt, results_h1_drop$model4_opt,
                        results_h1_drop$model1_full_linear, results_h1_drop$model4_non_mil,
                        results_h1_drop$model4_non_nato, results_h1_drop$model4_felm_saturated),
                   get_n_clusters)
rows_t1d <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7, ~row8,
  'State FEs', '-', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', 'X', 'X', 'X', 'X', 'X', 'X',
  'Topic FEs', '-', '-', '-', 'X', 'X', 'X', 'X', 'X',
  'Clusters', n_cl_t1d[1], n_cl_t1d[2], n_cl_t1d[3], n_cl_t1d[4], n_cl_t1d[5], n_cl_t1d[6], n_cl_t1d[7], n_cl_t1d[8]
)
attr(rows_t1d, 'position') <- c(3, 4, 5, 6)

note_t1d <- paste("All standard errors are clustered at the source level. Articles without publication times are dropped. Models 1-4 uses the optimal bandwidth. Model 5 uses a linear specification with the full set of articles. Model 6 omits Military Topics. Model 7 omits NATO allies. Model 8 uses full saturation (country-source-topic FEs).", SE_NOTE)

table_1d <- modelsummary(
  list(
    "(1)" = results_h1_drop$model1_opt,
    "(2)" = results_h1_drop$model2_opt,
    "(3)" = results_h1_drop$model3_opt,
    "(4)" = results_h1_drop$model4_opt,
    "(5)" = results_h1_drop$model1_full_linear,
    "(6)" = results_h1_drop$model4_non_mil,
    "(7)" = results_h1_drop$model4_non_nato,
    "(8)" = results_h1_drop$model4_felm_saturated
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c("treatment" = "Invasion", "post" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 1D: RDD with Continuous Running Variable (Drop No-Time Articles)",
  add_rows = rows_t1d,
  notes = str_wrap(note_t1d, 80)
)

table_1d

save_table(table_1d, "table_01d_rdd_drop_notime")
```

## Table 1E: RDD By Topic (Drop No-Time)

```{r table1e}
n_cl_t1e <- sapply(list(results_h1_drop$model4_opt_pol, results_h1_drop$model4_opt_mil,
                        results_h1_drop$model4_opt_econ, results_h1_drop$model4_opt_cult,
                        results_h1_drop$model4_opt_oth), get_n_clusters)
rows_t1e <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', 'X', 'X', 'X', 'X', 'X',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t1e[1], n_cl_t1e[2], n_cl_t1e[3], n_cl_t1e[4], n_cl_t1e[5]
)
attr(rows_t1e, 'position') <- c(3, 4, 5, 6)

note_t1e <- paste("All standard errors are clustered at the source level. Articles without publication times are dropped. All models use the optimal bandwidth with country and source fixed effects.", SE_NOTE)

table_1e <- modelsummary(
  list(
    "Political" = results_h1_drop$model4_opt_pol,
    "Military" = results_h1_drop$model4_opt_mil,
    "Economic" = results_h1_drop$model4_opt_econ,
    "Cultural" = results_h1_drop$model4_opt_cult,
    "Other" = results_h1_drop$model4_opt_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c("treatment" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 1E: RDD By Topic (Drop No-Time Articles)",
  add_rows = rows_t1e,
  notes = str_wrap(note_t1e, 80)
)

table_1e

save_table(table_1e, "table_01e_rdd_by_topic_drop_notime")
```

## Table 2F: Diff-in-Disc Main (Drop No-Time)

```{r table2f}
n_cl_t2f <- sapply(list(results_h2_drop$model2a, results_h2_drop$model2a_opt,
                        results_h2_drop$model2d, results_h2_drop$model2b,
                        results_h2_drop$model3a, results_h2_drop$model3a_opt,
                        results_h2_drop$model3a_opt_saturated), get_n_clusters)
rows_t2f <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7,
  'State FEs', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-', '-', 'X',
  'Topic FEs', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Clusters', n_cl_t2f[1], n_cl_t2f[2], n_cl_t2f[3], n_cl_t2f[4], n_cl_t2f[5], n_cl_t2f[6], n_cl_t2f[7]
)
attr(rows_t2f, 'position') <- c(5, 6, 7, 8)

note_t2f <- paste("All standard errors are clustered at the source level. Articles without publication times are dropped. Model 2 uses the optimal bandwidth. Model 3 omits NATO allies. Model 4 omits military-related articles. Model 5 uses only Russian-related articles. Model 6 combines all robustness filters with a re-optimized bandwidth. Model 7 uses full saturation (source-topic and country-state-topic FEs).", SE_NOTE)

table_2f <- modelsummary(
  list(
    "(1)" = results_h2_drop$model2a,
    "(2)" = results_h2_drop$model2a_opt,
    "(3)" = results_h2_drop$model2d,
    "(4)" = results_h2_drop$model2b,
    "(5)" = results_h2_drop$model3a,
    "(6)" = results_h2_drop$model3a_opt,
    "(7)" = results_h2_drop$model3a_opt_saturated
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 2F: Diff-in-Disc (Drop No-Time Articles)",
  add_rows = rows_t2f,
  notes = str_wrap(note_t2f, 80)
)

table_2f

save_table(table_2f, "table_02f_diff_disc_drop_notime")
```

## Table 2G: Diff-in-Disc By Topic Optimal BW (Drop No-Time)

```{r table2g}
n_cl_t2g <- sapply(list(results_h2_drop$model2a_opt_pol, results_h2_drop$model2a_opt_mil,
                        results_h2_drop$model2a_opt_econ, results_h2_drop$model2a_opt_cult,
                        results_h2_drop$model2a_opt_oth), get_n_clusters)
rows_t2g <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t2g[1], n_cl_t2g[2], n_cl_t2g[3], n_cl_t2g[4], n_cl_t2g[5]
)
attr(rows_t2g, 'position') <- c(5, 6, 7, 8)

note_t2g <- paste("All standard errors are clustered at the source level. Articles without publication times are dropped. All models use a per-topic re-optimized bandwidth with country fixed effects only.", SE_NOTE)

table_2g <- modelsummary(
  list(
    "Political" = results_h2_drop$model2a_opt_pol,
    "Military" = results_h2_drop$model2a_opt_mil,
    "Economic" = results_h2_drop$model2a_opt_econ,
    "Cultural" = results_h2_drop$model2a_opt_cult,
    "Other" = results_h2_drop$model2a_opt_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 2G: Diff-in-Disc By Topic, Optimal BW (Drop No-Time Articles)",
  add_rows = rows_t2g,
  notes = str_wrap(note_t2g, 80)
)

table_2g

save_table(table_2g, "table_02g_diff_disc_by_topic_opt_drop_notime")
```

## Table 2H: Diff-in-Disc By Topic Full Data (Drop No-Time)

```{r table2h}
n_cl_t2h <- sapply(list(results_h2_drop$model2a_full_pol, results_h2_drop$model2a_full_mil,
                        results_h2_drop$model2a_full_econ, results_h2_drop$model2a_full_cult,
                        results_h2_drop$model2a_full_oth), get_n_clusters)
rows_t2h <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t2h[1], n_cl_t2h[2], n_cl_t2h[3], n_cl_t2h[4], n_cl_t2h[5]
)
attr(rows_t2h, 'position') <- c(5, 6, 7, 8)

note_t2h <- paste("All standard errors are clustered at the source level. Articles without publication times are dropped. All models use the full dataset (no bandwidth restriction) with country fixed effects only.", SE_NOTE)

table_2h <- modelsummary(
  list(
    "Political" = results_h2_drop$model2a_full_pol,
    "Military" = results_h2_drop$model2a_full_mil,
    "Economic" = results_h2_drop$model2a_full_econ,
    "Cultural" = results_h2_drop$model2a_full_cult,
    "Other" = results_h2_drop$model2a_full_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 2H: Diff-in-Disc By Topic, Full Data (Drop No-Time Articles)",
  add_rows = rows_t2h,
  notes = str_wrap(note_t2h, 80)
)

table_2h

save_table(table_2h, "table_02h_diff_disc_by_topic_full_drop_notime")
```

## Table 3F: Alignment Main (Drop No-Time)

```{r table3f}
n_cl_t3f <- sapply(list(results_align_drop$model5a_csto, results_align_drop$model5a_neutral,
                        results_align_drop$model5a_full, results_align_drop$model5a_opt,
                        results_align_drop$model5a_opt_non_mil, results_align_drop$model5a_opt_russian,
                        results_align_drop$model5a_opt_full_fe, results_align_drop$model5a_opt_non_mil_full_fe,
                        results_align_drop$model5a_fully_saturated),
                   get_n_clusters)
rows_t3f <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7, ~row8, ~row9,
  'State FEs', '-', '-', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-', '-', 'X', 'X', 'X',
  'Topic FEs', '-', '-', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Country Dummies', '-', '-', '-', '-', '-', '-', 'X', 'X', '-',
  'Clusters', n_cl_t3f[1], n_cl_t3f[2], n_cl_t3f[3], n_cl_t3f[4], n_cl_t3f[5], n_cl_t3f[6], n_cl_t3f[7], n_cl_t3f[8], n_cl_t3f[9]
)
attr(rows_t3f, 'position') <- c(5, 6, 7, 8, 9)

note_t3f <- paste("Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights) for Models 3-9, clustered at source level. Models 1-2 use rdrobust standard errors. Articles without publication times are dropped. Model 1 shows RDD results for CSTO countries only. Model 2 shows RDD results for Neutral countries only. Model 3 uses full data with topic fixed effects. Model 4 uses the optimal bandwidth with topic fixed effects. Model 5 omits military-related articles and uses a re-optimized bandwidth. Model 6 uses only Russian-related (non-military) articles with a re-optimized bandwidth. Model 7 uses optimal bandwidth with full FEs (topic + source + country dummies). Model 8 uses non-military subset with full FEs. Model 9 uses full saturation (source-topic and topic-treatment FEs). Sample restricted to state-owned media in non-NATO countries.", SE_NOTE)

# Create vcov list with bootstrap SEs for felm models
vcov_t3f <- list(
  NULL,
  NULL,
  "(3)" = create_bootstrap_vcov(results_align_drop$model5a_full, results_align_drop$bootstrap_se$model5a_full, "treatment:csto"),
  "(4)" = create_bootstrap_vcov(results_align_drop$model5a_opt, results_align_drop$bootstrap_se$model5a_opt, "treatment:csto"),
  "(5)" = create_bootstrap_vcov(results_align_drop$model5a_opt_non_mil, results_align_drop$bootstrap_se$model5a_opt_non_mil, "treatment:csto"),
  "(6)" = create_bootstrap_vcov(results_align_drop$model5a_opt_russian, results_align_drop$bootstrap_se$model5a_opt_russian, "treatment:csto"),
  "(7)" = create_bootstrap_vcov(results_align_drop$model5a_opt_full_fe, results_align_drop$bootstrap_se$model5a_opt_full_fe, "treatment:csto"),
  "(8)" = create_bootstrap_vcov(results_align_drop$model5a_opt_non_mil_full_fe, results_align_drop$bootstrap_se$model5a_opt_non_mil_full_fe, "treatment:csto"),
  "(9)" = create_bootstrap_vcov(results_align_drop$model5a_fully_saturated, results_align_drop$bootstrap_se$model5a_fully_saturated, "treatment:csto")
)

table_3f <- modelsummary(
  list(
    "(1)" = results_align_drop$model5a_csto,
    "(2)" = results_align_drop$model5a_neutral,
    "(3)" = results_align_drop$model5a_full,
    "(4)" = results_align_drop$model5a_opt,
    "(5)" = results_align_drop$model5a_opt_non_mil,
    "(6)" = results_align_drop$model5a_opt_russian,
    "(7)" = results_align_drop$model5a_opt_full_fe,
    "(8)" = results_align_drop$model5a_opt_non_mil_full_fe,
    "(9)" = results_align_drop$model5a_fully_saturated
  ),
  vcov = vcov_t3f,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 3F: Russian Alignment Heterogeneity (Drop No-Time Articles)",
  add_rows = rows_t3f,
  notes = str_wrap(note_t3f, 80)
)

table_3f

save_table(table_3f, "table_03f_alignment_drop_notime")
```

## Table 3G: Alignment By Topic Optimal BW (Drop No-Time)

```{r table3g}
n_cl_t3g <- sapply(list(results_align_drop$model5a_opt_pol, results_align_drop$model5a_opt_mil,
                        results_align_drop$model5a_opt_econ, results_align_drop$model5a_opt_cult,
                        results_align_drop$model5a_opt_oth), get_n_clusters)
rows_t3g <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t3g[1], n_cl_t3g[2], n_cl_t3g[3], n_cl_t3g[4], n_cl_t3g[5]
)
attr(rows_t3g, 'position') <- c(5, 6, 7, 8)

note_t3g <- paste("All standard errors are clustered at the source level. Articles without publication times are dropped. Each model uses a per-topic re-optimized bandwidth. State media in non-NATO countries only.", SE_NOTE)

table_3g <- modelsummary(
  list(
    "Political" = results_align_drop$model5a_opt_pol,
    "Military" = results_align_drop$model5a_opt_mil,
    "Economic" = results_align_drop$model5a_opt_econ,
    "Cultural" = results_align_drop$model5a_opt_cult,
    "Other" = results_align_drop$model5a_opt_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 3G: Alignment By Topic, Optimal BW (Drop No-Time Articles)",
  add_rows = rows_t3g,
  notes = str_wrap(note_t3g, 80)
)

table_3g

save_table(table_3g, "table_03g_alignment_by_topic_opt_drop_notime")
```

## Table 3H: Alignment By Topic Full Data (Drop No-Time)

```{r table3h}
n_cl_t3h <- sapply(list(results_align_drop$model5a_full_pol, results_align_drop$model5a_full_mil,
                        results_align_drop$model5a_full_econ, results_align_drop$model5a_full_cult,
                        results_align_drop$model5a_full_oth), get_n_clusters)
rows_t3h <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t3h[1], n_cl_t3h[2], n_cl_t3h[3], n_cl_t3h[4], n_cl_t3h[5]
)
attr(rows_t3h, 'position') <- c(5, 6, 7, 8)

note_t3h <- paste("All standard errors are clustered at the source level. Articles without publication times are dropped. Each model uses the full dataset (no bandwidth restriction). State media in non-NATO countries only.", SE_NOTE)

table_3h <- modelsummary(
  list(
    "Political" = results_align_drop$model5a_full_pol,
    "Military" = results_align_drop$model5a_full_mil,
    "Economic" = results_align_drop$model5a_full_econ,
    "Cultural" = results_align_drop$model5a_full_cult,
    "Other" = results_align_drop$model5a_full_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 3H: Alignment By Topic, Full Data (Drop No-Time Articles)",
  add_rows = rows_t3h,
  notes = str_wrap(note_t3h, 80)
)

table_3h

save_table(table_3h, "table_03h_alignment_by_topic_full_drop_notime")
```

## Table 4F: Ethnic Main (Drop No-Time)

```{r table4f}
n_cl_t4f <- sapply(list(results_ethnic_drop$model6a_full, results_ethnic_drop$model6a_opt,
                        results_ethnic_drop$model6a_opt_non_mil, results_ethnic_drop$model6a_opt_russian),
                   get_n_clusters)
rows_t4f <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4,
  'State FEs', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-',
  'Topic FEs', 'X', 'X', 'X', 'X',
  'Clusters', n_cl_t4f[1], n_cl_t4f[2], n_cl_t4f[3], n_cl_t4f[4]
)
attr(rows_t4f, 'position') <- c(5, 6, 7, 8)

note_t4f <- paste("Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights), clustered at source level. Articles without publication times are dropped. Model 1 uses full data with topic fixed effects. Model 2 uses the optimal bandwidth with topic fixed effects. Model 3 omits military-related articles and uses a re-optimized bandwidth. Model 4 uses only Russian-related (non-military) articles with a re-optimized bandwidth. Sample restricted to state-owned media in non-NATO countries.", SE_NOTE)

# Create vcov list with bootstrap SEs
vcov_t4f <- list(
  "(1)" = create_bootstrap_vcov(results_ethnic_drop$model6a_full, results_ethnic_drop$bootstrap_se$model6a_full, "treatment:high_russia"),
  "(2)" = create_bootstrap_vcov(results_ethnic_drop$model6a_opt, results_ethnic_drop$bootstrap_se$model6a_opt, "treatment:high_russia"),
  "(3)" = create_bootstrap_vcov(results_ethnic_drop$model6a_opt_non_mil, results_ethnic_drop$bootstrap_se$model6a_opt_non_mil, "treatment:high_russia"),
  "(4)" = create_bootstrap_vcov(results_ethnic_drop$model6a_opt_russian, results_ethnic_drop$bootstrap_se$model6a_opt_russian, "treatment:high_russia")
)

table_4f <- modelsummary(
  list(
    "(1)" = results_ethnic_drop$model6a_full,
    "(2)" = results_ethnic_drop$model6a_opt,
    "(3)" = results_ethnic_drop$model6a_opt_non_mil,
    "(4)" = results_ethnic_drop$model6a_opt_russian
  ),
  vcov = vcov_t4f,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 4F: Ethnic Heterogeneity (Drop No-Time Articles)",
  add_rows = rows_t4f,
  notes = str_wrap(note_t4f, 80)
)

table_4f

save_table(table_4f, "table_04f_ethnic_drop_notime")
```

## Table 4G: Ethnic By Topic Optimal BW (Drop No-Time)

```{r table4g}
n_cl_t4g <- sapply(list(results_ethnic_drop$model6a_opt_pol, results_ethnic_drop$model6a_opt_mil,
                        results_ethnic_drop$model6a_opt_econ, results_ethnic_drop$model6a_opt_cult,
                        results_ethnic_drop$model6a_opt_oth), get_n_clusters)
rows_t4g <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t4g[1], n_cl_t4g[2], n_cl_t4g[3], n_cl_t4g[4], n_cl_t4g[5]
)
attr(rows_t4g, 'position') <- c(5, 6, 7, 8)

note_t4g <- paste("All standard errors are clustered at the source level. Articles without publication times are dropped. Each model uses a per-topic re-optimized bandwidth. State media in non-NATO countries only.", SE_NOTE)

table_4g <- modelsummary(
  list(
    "Political" = results_ethnic_drop$model6a_opt_pol,
    "Military" = results_ethnic_drop$model6a_opt_mil,
    "Economic" = results_ethnic_drop$model6a_opt_econ,
    "Cultural" = results_ethnic_drop$model6a_opt_cult,
    "Other" = results_ethnic_drop$model6a_opt_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 4G: Ethnic By Topic, Optimal BW (Drop No-Time Articles)",
  add_rows = rows_t4g,
  notes = str_wrap(note_t4g, 80)
)

table_4g

save_table(table_4g, "table_04g_ethnic_by_topic_opt_drop_notime")
```

## Table 4H: Ethnic By Topic Full Data (Drop No-Time)

```{r table4h}
n_cl_t4h <- sapply(list(results_ethnic_drop$model6a_full_pol, results_ethnic_drop$model6a_full_mil,
                        results_ethnic_drop$model6a_full_econ, results_ethnic_drop$model6a_full_cult,
                        results_ethnic_drop$model6a_full_oth), get_n_clusters)
rows_t4h <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t4h[1], n_cl_t4h[2], n_cl_t4h[3], n_cl_t4h[4], n_cl_t4h[5]
)
attr(rows_t4h, 'position') <- c(5, 6, 7, 8)

note_t4h <- paste("All standard errors are clustered at the source level. Articles without publication times are dropped. Each model uses the full dataset (no bandwidth restriction). State media in non-NATO countries only.", SE_NOTE)

table_4h <- modelsummary(
  list(
    "Political" = results_ethnic_drop$model6a_full_pol,
    "Military" = results_ethnic_drop$model6a_full_mil,
    "Economic" = results_ethnic_drop$model6a_full_econ,
    "Cultural" = results_ethnic_drop$model6a_full_cult,
    "Other" = results_ethnic_drop$model6a_full_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 4H: Ethnic By Topic, Full Data (Drop No-Time Articles)",
  add_rows = rows_t4h,
  notes = str_wrap(note_t4h, 80)
)

table_4h

save_table(table_4h, "table_04h_ethnic_by_topic_full_drop_notime")
```

# Probabilistic Time Assignment Variant Tables

## Table 1F: RDD Main (Probabilistic Time)

```{r table1f}
n_cl_t1f <- sapply(list(results_h1_prob$model1_opt, results_h1_prob$model2_opt,
                        results_h1_prob$model3_opt, results_h1_prob$model4_opt,
                        results_h1_prob$model1_full_linear, results_h1_prob$model4_non_mil,
                        results_h1_prob$model4_non_nato, results_h1_prob$model4_felm_saturated),
                   get_n_clusters)
rows_t1f <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7, ~row8,
  'State FEs', '-', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', 'X', 'X', 'X', 'X', 'X', 'X',
  'Topic FEs', '-', '-', '-', 'X', 'X', 'X', 'X', 'X',
  'Clusters', n_cl_t1f[1], n_cl_t1f[2], n_cl_t1f[3], n_cl_t1f[4], n_cl_t1f[5], n_cl_t1f[6], n_cl_t1f[7], n_cl_t1f[8]
)
attr(rows_t1f, 'position') <- c(3, 4, 5, 6)

note_t1f <- paste("All standard errors are clustered at the source level. Articles without publication times are assigned times via KDE sampling from same-source distributions. Models 1-4 uses the optimal bandwidth. Model 5 uses a linear specification with the full set of articles. Model 6 omits Military Topics. Model 7 omits NATO allies. Model 8 uses full saturation (country-source-topic FEs).", SE_NOTE)

table_1f <- modelsummary(
  list(
    "(1)" = results_h1_prob$model1_opt,
    "(2)" = results_h1_prob$model2_opt,
    "(3)" = results_h1_prob$model3_opt,
    "(4)" = results_h1_prob$model4_opt,
    "(5)" = results_h1_prob$model1_full_linear,
    "(6)" = results_h1_prob$model4_non_mil,
    "(7)" = results_h1_prob$model4_non_nato,
    "(8)" = results_h1_prob$model4_felm_saturated
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c("treatment" = "Invasion", "post" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 1F: RDD with Probabilistic Time Assignment",
  add_rows = rows_t1f,
  notes = str_wrap(note_t1f, 80)
)

table_1f

save_table(table_1f, "table_01f_rdd_probabilistic")
```

## Table 1G: RDD By Topic (Probabilistic Time)

```{r table1g}
n_cl_t1g <- sapply(list(results_h1_prob$model4_opt_pol, results_h1_prob$model4_opt_mil,
                        results_h1_prob$model4_opt_econ, results_h1_prob$model4_opt_cult,
                        results_h1_prob$model4_opt_oth), get_n_clusters)
rows_t1g <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', 'X', 'X', 'X', 'X', 'X',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t1g[1], n_cl_t1g[2], n_cl_t1g[3], n_cl_t1g[4], n_cl_t1g[5]
)
attr(rows_t1g, 'position') <- c(3, 4, 5, 6)

note_t1g <- paste("All standard errors are clustered at the source level. Articles without publication times are assigned times via KDE sampling. All models use the optimal bandwidth with country and source fixed effects.", SE_NOTE)

table_1g <- modelsummary(
  list(
    "Political" = results_h1_prob$model4_opt_pol,
    "Military" = results_h1_prob$model4_opt_mil,
    "Economic" = results_h1_prob$model4_opt_econ,
    "Cultural" = results_h1_prob$model4_opt_cult,
    "Other" = results_h1_prob$model4_opt_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c("treatment" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 1G: RDD By Topic (Probabilistic Time Assignment)",
  add_rows = rows_t1g,
  notes = str_wrap(note_t1g, 80)
)

table_1g

save_table(table_1g, "table_01g_rdd_by_topic_probabilistic")
```

## Table 2I: Diff-in-Disc Main (Probabilistic Time)

```{r table2i}
n_cl_t2i <- sapply(list(results_h2_prob$model2a, results_h2_prob$model2a_opt,
                        results_h2_prob$model2d, results_h2_prob$model2b,
                        results_h2_prob$model3a, results_h2_prob$model3a_opt,
                        results_h2_prob$model3a_opt_saturated), get_n_clusters)
rows_t2i <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7,
  'State FEs', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-', '-', 'X',
  'Topic FEs', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Clusters', n_cl_t2i[1], n_cl_t2i[2], n_cl_t2i[3], n_cl_t2i[4], n_cl_t2i[5], n_cl_t2i[6], n_cl_t2i[7]
)
attr(rows_t2i, 'position') <- c(5, 6, 7, 8)

note_t2i <- paste("All standard errors are clustered at the source level. Articles without publication times are assigned times via KDE sampling. Model 2 uses the optimal bandwidth. Model 3 omits NATO allies. Model 4 omits military-related articles. Model 5 uses only Russian-related articles. Model 6 combines all robustness filters with a re-optimized bandwidth. Model 7 uses full saturation (source-topic and country-state-topic FEs).", SE_NOTE)

table_2i <- modelsummary(
  list(
    "(1)" = results_h2_prob$model2a,
    "(2)" = results_h2_prob$model2a_opt,
    "(3)" = results_h2_prob$model2d,
    "(4)" = results_h2_prob$model2b,
    "(5)" = results_h2_prob$model3a,
    "(6)" = results_h2_prob$model3a_opt,
    "(7)" = results_h2_prob$model3a_opt_saturated
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 2I: Diff-in-Disc (Probabilistic Time Assignment)",
  add_rows = rows_t2i,
  notes = str_wrap(note_t2i, 80)
)

table_2i

save_table(table_2i, "table_02i_diff_disc_probabilistic")
```

## Table 2J: Diff-in-Disc By Topic Optimal BW (Probabilistic Time)

```{r table2j}
n_cl_t2j <- sapply(list(results_h2_prob$model2a_opt_pol, results_h2_prob$model2a_opt_mil,
                        results_h2_prob$model2a_opt_econ, results_h2_prob$model2a_opt_cult,
                        results_h2_prob$model2a_opt_oth), get_n_clusters)
rows_t2j <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t2j[1], n_cl_t2j[2], n_cl_t2j[3], n_cl_t2j[4], n_cl_t2j[5]
)
attr(rows_t2j, 'position') <- c(5, 6, 7, 8)

note_t2j <- paste("All standard errors are clustered at the source level. Articles without publication times are assigned times via KDE sampling. All models use a per-topic re-optimized bandwidth with country fixed effects only.", SE_NOTE)

table_2j <- modelsummary(
  list(
    "Political" = results_h2_prob$model2a_opt_pol,
    "Military" = results_h2_prob$model2a_opt_mil,
    "Economic" = results_h2_prob$model2a_opt_econ,
    "Cultural" = results_h2_prob$model2a_opt_cult,
    "Other" = results_h2_prob$model2a_opt_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 2J: Diff-in-Disc By Topic, Optimal BW (Probabilistic Time)",
  add_rows = rows_t2j,
  notes = str_wrap(note_t2j, 80)
)

table_2j

save_table(table_2j, "table_02j_diff_disc_by_topic_opt_probabilistic")
```

## Table 2K: Diff-in-Disc By Topic Full Data (Probabilistic Time)

```{r table2k}
n_cl_t2k <- sapply(list(results_h2_prob$model2a_full_pol, results_h2_prob$model2a_full_mil,
                        results_h2_prob$model2a_full_econ, results_h2_prob$model2a_full_cult,
                        results_h2_prob$model2a_full_oth), get_n_clusters)
rows_t2k <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t2k[1], n_cl_t2k[2], n_cl_t2k[3], n_cl_t2k[4], n_cl_t2k[5]
)
attr(rows_t2k, 'position') <- c(5, 6, 7, 8)

note_t2k <- paste("All standard errors are clustered at the source level. Articles without publication times are assigned times via KDE sampling. All models use the full dataset (no bandwidth restriction) with country fixed effects only.", SE_NOTE)

table_2k <- modelsummary(
  list(
    "Political" = results_h2_prob$model2a_full_pol,
    "Military" = results_h2_prob$model2a_full_mil,
    "Economic" = results_h2_prob$model2a_full_econ,
    "Cultural" = results_h2_prob$model2a_full_cult,
    "Other" = results_h2_prob$model2a_full_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 2K: Diff-in-Disc By Topic, Full Data (Probabilistic Time)",
  add_rows = rows_t2k,
  notes = str_wrap(note_t2k, 80)
)

table_2k

save_table(table_2k, "table_02k_diff_disc_by_topic_full_probabilistic")
```

## Table 2L: State-Owned and Independent Media RDD (Day)

```{r table2l}
note_t2l <- paste("Separate RDD estimates for state-owned and independent media using the day running variable. Bandwidths selected by MSE-optimal bandwidth selector. Standard errors are cluster-robust (rdrobust).", SE_NOTE)

table_2l <- modelsummary(
  list(
    "State Media" = results_h2$model2_state_rdd,
    "Independent Media" = results_h2$model2_ind_rdd
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c("treatment" = "Invasion (RDD)"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 2L: RDD for State-Owned and Independent Media Separately (Day)",
  notes = str_wrap(note_t2l, 80)
)

table_2l

save_table(table_2l, "table_02l_state_ind_rdd")
```

## Table 3I: Alignment Main (Probabilistic Time)

```{r table3i}
n_cl_t3i <- sapply(list(results_align_prob$model5a_csto, results_align_prob$model5a_neutral,
                        results_align_prob$model5a_full, results_align_prob$model5a_opt,
                        results_align_prob$model5a_opt_non_mil, results_align_prob$model5a_opt_russian,
                        results_align_prob$model5a_opt_full_fe, results_align_prob$model5a_opt_non_mil_full_fe,
                        results_align_prob$model5a_fully_saturated),
                   get_n_clusters)
rows_t3i <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7, ~row8, ~row9,
  'State FEs', '-', '-', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-', '-', 'X', 'X', 'X',
  'Topic FEs', '-', '-', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Country Dummies', '-', '-', '-', '-', '-', '-', 'X', 'X', '-',
  'Clusters', n_cl_t3i[1], n_cl_t3i[2], n_cl_t3i[3], n_cl_t3i[4], n_cl_t3i[5], n_cl_t3i[6], n_cl_t3i[7], n_cl_t3i[8], n_cl_t3i[9]
)
attr(rows_t3i, 'position') <- c(5, 6, 7, 8, 9)

note_t3i <- paste("Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights) for Models 3-9, clustered at source level. Models 1-2 use rdrobust standard errors. Articles without publication times are assigned times via KDE sampling. Model 1 shows RDD results for CSTO countries only. Model 2 shows RDD results for Neutral countries only. Model 3 uses full data with topic fixed effects. Model 4 uses the optimal bandwidth with topic fixed effects. Model 5 omits military-related articles and uses a re-optimized bandwidth. Model 6 uses only Russian-related (non-military) articles with a re-optimized bandwidth. Model 7 uses optimal bandwidth with full FEs (topic + source + country dummies). Model 8 uses non-military subset with full FEs. Model 9 uses full saturation (source-topic and topic-treatment FEs). Sample restricted to state-owned media in non-NATO countries.", SE_NOTE)

# Create vcov list with bootstrap SEs for felm models
vcov_t3i <- list(
  NULL,
  NULL,
  "(3)" = create_bootstrap_vcov(results_align_prob$model5a_full, results_align_prob$bootstrap_se$model5a_full, "treatment:csto"),
  "(4)" = create_bootstrap_vcov(results_align_prob$model5a_opt, results_align_prob$bootstrap_se$model5a_opt, "treatment:csto"),
  "(5)" = create_bootstrap_vcov(results_align_prob$model5a_opt_non_mil, results_align_prob$bootstrap_se$model5a_opt_non_mil, "treatment:csto"),
  "(6)" = create_bootstrap_vcov(results_align_prob$model5a_opt_russian, results_align_prob$bootstrap_se$model5a_opt_russian, "treatment:csto"),
  "(7)" = create_bootstrap_vcov(results_align_prob$model5a_opt_full_fe, results_align_prob$bootstrap_se$model5a_opt_full_fe, "treatment:csto"),
  "(8)" = create_bootstrap_vcov(results_align_prob$model5a_opt_non_mil_full_fe, results_align_prob$bootstrap_se$model5a_opt_non_mil_full_fe, "treatment:csto"),
  "(9)" = create_bootstrap_vcov(results_align_prob$model5a_fully_saturated, results_align_prob$bootstrap_se$model5a_fully_saturated, "treatment:csto")
)

table_3i <- modelsummary(
  list(
    "(1)" = results_align_prob$model5a_csto,
    "(2)" = results_align_prob$model5a_neutral,
    "(3)" = results_align_prob$model5a_full,
    "(4)" = results_align_prob$model5a_opt,
    "(5)" = results_align_prob$model5a_opt_non_mil,
    "(6)" = results_align_prob$model5a_opt_russian,
    "(7)" = results_align_prob$model5a_opt_full_fe,
    "(8)" = results_align_prob$model5a_opt_non_mil_full_fe,
    "(9)" = results_align_prob$model5a_fully_saturated
  ),
  vcov = vcov_t3i,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 3I: Russian Alignment Heterogeneity (Probabilistic Time)",
  add_rows = rows_t3i,
  notes = str_wrap(note_t3i, 80)
)

table_3i

save_table(table_3i, "table_03i_alignment_probabilistic")
```

## Table 3J: Alignment By Topic Optimal BW (Probabilistic Time)

```{r table3j}
n_cl_t3j <- sapply(list(results_align_prob$model5a_opt_pol, results_align_prob$model5a_opt_mil,
                        results_align_prob$model5a_opt_econ, results_align_prob$model5a_opt_cult,
                        results_align_prob$model5a_opt_oth), get_n_clusters)
rows_t3j <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t3j[1], n_cl_t3j[2], n_cl_t3j[3], n_cl_t3j[4], n_cl_t3j[5]
)
attr(rows_t3j, 'position') <- c(5, 6, 7, 8)

note_t3j <- paste("All standard errors are clustered at the source level. Articles without publication times are assigned times via KDE sampling. Each model uses a per-topic re-optimized bandwidth. State media in non-NATO countries only.", SE_NOTE)

table_3j <- modelsummary(
  list(
    "Political" = results_align_prob$model5a_opt_pol,
    "Military" = results_align_prob$model5a_opt_mil,
    "Economic" = results_align_prob$model5a_opt_econ,
    "Cultural" = results_align_prob$model5a_opt_cult,
    "Other" = results_align_prob$model5a_opt_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 3J: Alignment By Topic, Optimal BW (Probabilistic Time)",
  add_rows = rows_t3j,
  notes = str_wrap(note_t3j, 80)
)

table_3j

save_table(table_3j, "table_03j_alignment_by_topic_opt_probabilistic")
```

## Table 3K: Alignment By Topic Full Data (Probabilistic Time)

```{r table3k}
n_cl_t3k <- sapply(list(results_align_prob$model5a_full_pol, results_align_prob$model5a_full_mil,
                        results_align_prob$model5a_full_econ, results_align_prob$model5a_full_cult,
                        results_align_prob$model5a_full_oth), get_n_clusters)
rows_t3k <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t3k[1], n_cl_t3k[2], n_cl_t3k[3], n_cl_t3k[4], n_cl_t3k[5]
)
attr(rows_t3k, 'position') <- c(5, 6, 7, 8)

note_t3k <- paste("All standard errors are clustered at the source level. Articles without publication times are assigned times via KDE sampling. Each model uses the full dataset (no bandwidth restriction). State media in non-NATO countries only.", SE_NOTE)

table_3k <- modelsummary(
  list(
    "Political" = results_align_prob$model5a_full_pol,
    "Military" = results_align_prob$model5a_full_mil,
    "Economic" = results_align_prob$model5a_full_econ,
    "Cultural" = results_align_prob$model5a_full_cult,
    "Other" = results_align_prob$model5a_full_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 3K: Alignment By Topic, Full Data (Probabilistic Time)",
  add_rows = rows_t3k,
  notes = str_wrap(note_t3k, 80)
)

table_3k

save_table(table_3k, "table_03k_alignment_by_topic_full_probabilistic")
```

## Table 4I: Ethnic Main (Probabilistic Time)

```{r table4i}
n_cl_t4i <- sapply(list(results_ethnic_prob$model6a_full, results_ethnic_prob$model6a_opt,
                        results_ethnic_prob$model6a_opt_non_mil, results_ethnic_prob$model6a_opt_russian),
                   get_n_clusters)
rows_t4i <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4,
  'State FEs', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-',
  'Topic FEs', 'X', 'X', 'X', 'X',
  'Clusters', n_cl_t4i[1], n_cl_t4i[2], n_cl_t4i[3], n_cl_t4i[4]
)
attr(rows_t4i, 'position') <- c(5, 6, 7, 8)

note_t4i <- paste("Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights), clustered at source level. Articles without publication times are assigned times via KDE sampling. Model 1 uses full data with topic fixed effects. Model 2 uses the optimal bandwidth with topic fixed effects. Model 3 omits military-related articles and uses a re-optimized bandwidth. Model 4 uses only Russian-related (non-military) articles with a re-optimized bandwidth. Sample restricted to state-owned media in non-NATO countries.", SE_NOTE)

# Create vcov list with bootstrap SEs
vcov_t4i <- list(
  "(1)" = create_bootstrap_vcov(results_ethnic_prob$model6a_full, results_ethnic_prob$bootstrap_se$model6a_full, "treatment:high_russia"),
  "(2)" = create_bootstrap_vcov(results_ethnic_prob$model6a_opt, results_ethnic_prob$bootstrap_se$model6a_opt, "treatment:high_russia"),
  "(3)" = create_bootstrap_vcov(results_ethnic_prob$model6a_opt_non_mil, results_ethnic_prob$bootstrap_se$model6a_opt_non_mil, "treatment:high_russia"),
  "(4)" = create_bootstrap_vcov(results_ethnic_prob$model6a_opt_russian, results_ethnic_prob$bootstrap_se$model6a_opt_russian, "treatment:high_russia")
)

table_4i <- modelsummary(
  list(
    "(1)" = results_ethnic_prob$model6a_full,
    "(2)" = results_ethnic_prob$model6a_opt,
    "(3)" = results_ethnic_prob$model6a_opt_non_mil,
    "(4)" = results_ethnic_prob$model6a_opt_russian
  ),
  vcov = vcov_t4i,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 4I: Ethnic Heterogeneity (Probabilistic Time)",
  add_rows = rows_t4i,
  notes = str_wrap(note_t4i, 80)
)

table_4i

save_table(table_4i, "table_04i_ethnic_probabilistic")
```

## Table 4J: Ethnic By Topic Optimal BW (Probabilistic Time)

```{r table4j}
n_cl_t4j <- sapply(list(results_ethnic_prob$model6a_opt_pol, results_ethnic_prob$model6a_opt_mil,
                        results_ethnic_prob$model6a_opt_econ, results_ethnic_prob$model6a_opt_cult,
                        results_ethnic_prob$model6a_opt_oth), get_n_clusters)
rows_t4j <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t4j[1], n_cl_t4j[2], n_cl_t4j[3], n_cl_t4j[4], n_cl_t4j[5]
)
attr(rows_t4j, 'position') <- c(5, 6, 7, 8)

note_t4j <- paste("All standard errors are clustered at the source level. Articles without publication times are assigned times via KDE sampling. Each model uses a per-topic re-optimized bandwidth. State media in non-NATO countries only.", SE_NOTE)

table_4j <- modelsummary(
  list(
    "Political" = results_ethnic_prob$model6a_opt_pol,
    "Military" = results_ethnic_prob$model6a_opt_mil,
    "Economic" = results_ethnic_prob$model6a_opt_econ,
    "Cultural" = results_ethnic_prob$model6a_opt_cult,
    "Other" = results_ethnic_prob$model6a_opt_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 4J: Ethnic By Topic, Optimal BW (Probabilistic Time)",
  add_rows = rows_t4j,
  notes = str_wrap(note_t4j, 80)
)

table_4j

save_table(table_4j, "table_04j_ethnic_by_topic_opt_probabilistic")
```

## Table 4K: Ethnic By Topic Full Data (Probabilistic Time)

```{r table4k}
n_cl_t4k <- sapply(list(results_ethnic_prob$model6a_full_pol, results_ethnic_prob$model6a_full_mil,
                        results_ethnic_prob$model6a_full_econ, results_ethnic_prob$model6a_full_cult,
                        results_ethnic_prob$model6a_full_oth), get_n_clusters)
rows_t4k <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t4k[1], n_cl_t4k[2], n_cl_t4k[3], n_cl_t4k[4], n_cl_t4k[5]
)
attr(rows_t4k, 'position') <- c(5, 6, 7, 8)

note_t4k <- paste("All standard errors are clustered at the source level. Articles without publication times are assigned times via KDE sampling. Each model uses the full dataset (no bandwidth restriction). State media in non-NATO countries only.", SE_NOTE)

table_4k <- modelsummary(
  list(
    "Political" = results_ethnic_prob$model6a_full_pol,
    "Military" = results_ethnic_prob$model6a_full_mil,
    "Economic" = results_ethnic_prob$model6a_full_econ,
    "Cultural" = results_ethnic_prob$model6a_full_cult,
    "Other" = results_ethnic_prob$model6a_full_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 4K: Ethnic By Topic, Full Data (Probabilistic Time)",
  add_rows = rows_t4k,
  notes = str_wrap(note_t4k, 80)
)

table_4k

save_table(table_4k, "table_04k_ethnic_by_topic_full_probabilistic")
```

# Comparison Table: Countries by Alignment and Ethnic Population

```{r comparison-table}
get_group <- function(russian_group, security_group) {
  paste(intersect(russian_group, security_group), collapse = ", ")
}

table_data <- data.frame(
  `Ethnic Russian Population` = c("Low Ethnic", "High Ethnic"),
  `Low Russia Aligned` = c(
    get_group(LOW_RUSSIAN_POP, NEUTRAL_COUNTRIES),
    get_group(HIGH_RUSSIAN_POP, NEUTRAL_COUNTRIES)
  ),
  `High Russia Aligned` = c(
    get_group(LOW_RUSSIAN_POP, CSTO_COUNTRIES),
    get_group(HIGH_RUSSIAN_POP, CSTO_COUNTRIES)
  )
)

comparison_table <- table_data %>%
  gt() %>%
  tab_header(
    title = "Ethnic Russian Population x Russia Security Alignment",
    subtitle = "Country Classification"
  ) %>%
  cols_label(
    Ethnic.Russian.Population = "",
    Low.Russia.Aligned = "Low Alignment (Neutral)",
    High.Russia.Aligned = "High Alignment (CSTO)"
  ) %>%
  tab_style(
    style = cell_borders(sides = "all", color = "black", weight = px(1)),
    locations = cells_body()
  )

comparison_table

save_table(comparison_table, "table_05_country_classification")
```

# Alignment Table

```{r alignment-table}
alignment_table <- table_data %>%
  gt() %>%
  tab_header(
    title = "Ethnic Russian Population x Russia Security Alignment",
    subtitle = "Alignment Comparison"
  ) %>%
  cols_label(
    Ethnic.Russian.Population = "",
    Low.Russia.Aligned = "Low Alignment",
    High.Russia.Aligned = "High Alignment"
  ) %>%
  fmt_markdown(everything()) %>%
  tab_style(
    style = cell_borders(sides = c("top", "bottom"), color = "black", weight = px(2)),
    locations = cells_body(rows = 1:2, columns = 2:3)
  ) %>%
  tab_style(
    style = cell_borders(sides = c("left", "right"), color = "black", weight = px(2)),
    locations = cells_body(rows = 1:2, columns = 2:3)
  )

alignment_table

save_table(alignment_table, "table_06_alignment_classification")
```

# Ethnic Table

```{r ethnic-table}
ethnic_table <- table_data %>%
  gt() %>%
  tab_header(
    title = "Ethnic Russian Population x Russia Security Alignment",
    subtitle = "Ethnic Comparison"
  ) %>%
  cols_label(
    Ethnic.Russian.Population = "",
    Low.Russia.Aligned = "Low Alignment",
    High.Russia.Aligned = "High Alignment"
  ) %>%
  fmt_markdown(everything()) %>%
  tab_style(
    style = cell_borders(sides = "bottom", color = "black", weight = px(2)),
    locations = cells_body(rows = 1, columns = 2:3)
  ) %>%
  tab_style(
    style = cell_borders(sides = c("top", "bottom", "left", "right"), color = "black", weight = px(2)),
    locations = cells_body(rows = 1:2, columns = 2:3)
  )

ethnic_table

save_table(ethnic_table, "table_07_ethnic_classification")
```

# Export Tables to LaTeX

```{r latex-export}
# Function to save modelsummary as tex
save_tex <- function(models, filename, coef_map, title, rows = NULL, note = NULL) {
  modelsummary(
    models,
    output = file.path(FIGURES_TABLES, filename),
    fmt = 3,
    stars = c('*' = .05, '**' = .01, '***' = .001),
    coef_map = coef_map,
    gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
    title = title,
    add_rows = rows,
    notes = note
  )
}

# Note: These will generate .tex files for LaTeX inclusion
cat("LaTeX tables can be generated by changing output format to 'latex'\n")
```

# Summary of All Tables

```{r summary}
cat("\n")
cat("=============================================================\n")
cat("PUBLICATION OUTPUTS SUMMARY\n")
cat("=============================================================\n")
cat("\nRDS inputs loaded:\n")
cat("  - 04_h1_results*.rds      (H1: Main RDD, 4 variants)\n")
cat("  - 05_h2_results*.rds      (H2: Diff-in-Disc, 4 variants)\n")
cat("  - 06_alignment_results*.rds (Alignment heterogeneity, 4 variants)\n")
cat("  - 07_ethnic_results*.rds   (Ethnic heterogeneity, 4 variants)\n")
cat("\nTables generated (each saved as .tex AND .html):\n")
cat("\n  ## Main Day-Running-Variable Tables ##\n")
cat("  - table_01_rdd_main:                  RDD main results (H1, day)\n")
cat("  - table_01a_rdd_continuous:           RDD main results (H1, continuous)\n")
cat("  - table_01b_rdd_by_topic_day:         RDD by topic, opt BW (day)\n")
cat("  - table_01c_rdd_by_topic_continuous:  RDD by topic, opt BW (continuous)\n")
cat("  - table_02_diff_disc_main:            Diff-in-Disc main (H2, day)\n")
cat("  - table_02a_diff_disc_continuous:     Diff-in-Disc main (H2, continuous)\n")
cat("  - table_02b_diff_disc_by_topic_day:   Diff-in-Disc by topic, opt BW (day)\n")
cat("  - table_02c_diff_disc_by_topic_continuous: Diff-in-Disc by topic, opt BW (cont)\n")
cat("  - table_02d_diff_disc_by_topic_full_day:   Diff-in-Disc by topic, full (day)\n")
cat("  - table_02e_diff_disc_by_topic_full_continuous: Diff-in-Disc by topic, full (cont)\n")
cat("  - table_02l_state_ind_rdd:            RDD for state vs independent media\n")
cat("  - table_03_alignment_main:            Alignment heterogeneity (day)\n")
cat("  - table_03a_alignment_continuous:     Alignment heterogeneity (continuous)\n")
cat("  - table_03b_alignment_by_topic_day:   Alignment by topic, opt BW (day)\n")
cat("  - table_03c_alignment_by_topic_continuous: Alignment by topic, opt BW (cont)\n")
cat("  - table_03d_alignment_by_topic_full_day:   Alignment by topic, full (day)\n")
cat("  - table_03e_alignment_by_topic_full_continuous: Alignment by topic, full (cont)\n")
cat("  - table_04_ethnic_main:               Ethnic heterogeneity (day)\n")
cat("  - table_04a_ethnic_continuous:        Ethnic heterogeneity (continuous)\n")
cat("  - table_04b_ethnic_by_topic_day:      Ethnic by topic, opt BW (day)\n")
cat("  - table_04c_ethnic_by_topic_continuous: Ethnic by topic, opt BW (cont)\n")
cat("  - table_04d_ethnic_by_topic_full_day:   Ethnic by topic, full (day)\n")
cat("  - table_04e_ethnic_by_topic_full_continuous: Ethnic by topic, full (cont)\n")
cat("\n  ## Drop No-Time Articles Robustness ##\n")
cat("  - table_01d_rdd_drop_notime:          RDD main (drop no-time)\n")
cat("  - table_01e_rdd_by_topic_drop_notime: RDD by topic (drop no-time)\n")
cat("  - table_02f_diff_disc_drop_notime:    Diff-in-Disc main (drop no-time)\n")
cat("  - table_02g_diff_disc_by_topic_opt_drop_notime: DiD by topic, opt (drop)\n")
cat("  - table_02h_diff_disc_by_topic_full_drop_notime: DiD by topic, full (drop)\n")
cat("  - table_03f_alignment_drop_notime:    Alignment main (drop no-time)\n")
cat("  - table_03g_alignment_by_topic_opt_drop_notime: Alignment by topic (drop)\n")
cat("  - table_03h_alignment_by_topic_full_drop_notime: Alignment full (drop)\n")
cat("  - table_04f_ethnic_drop_notime:       Ethnic main (drop no-time)\n")
cat("  - table_04g_ethnic_by_topic_opt_drop_notime: Ethnic by topic, opt (drop)\n")
cat("  - table_04h_ethnic_by_topic_full_drop_notime: Ethnic by topic, full (drop)\n")
cat("\n  ## Probabilistic Time Assignment Robustness ##\n")
cat("  - table_01f_rdd_probabilistic:        RDD main (probabilistic time)\n")
cat("  - table_01g_rdd_by_topic_probabilistic: RDD by topic (probabilistic time)\n")
cat("  - table_02i_diff_disc_probabilistic:  Diff-in-Disc main (probabilistic)\n")
cat("  - table_02j_diff_disc_by_topic_opt_probabilistic: DiD by topic, opt (prob)\n")
cat("  - table_02k_diff_disc_by_topic_full_probabilistic: DiD by topic, full (prob)\n")
cat("  - table_03i_alignment_probabilistic:  Alignment main (probabilistic)\n")
cat("  - table_03j_alignment_by_topic_opt_probabilistic: Alignment by topic (prob)\n")
cat("  - table_03k_alignment_by_topic_full_probabilistic: Alignment full (prob)\n")
cat("  - table_04i_ethnic_probabilistic:     Ethnic main (probabilistic)\n")
cat("  - table_04j_ethnic_by_topic_opt_probabilistic: Ethnic by topic, opt (prob)\n")
cat("  - table_04k_ethnic_by_topic_full_probabilistic: Ethnic by topic, full (prob)\n")
cat("\n  ## Classification / Descriptive Tables ##\n")
cat("  - table_05_country_classification:    Country × alignment × ethnic\n")
cat("  - table_06_alignment_classification:  Alignment comparison\n")
cat("  - table_07_ethnic_classification:     Ethnic population comparison\n")
cat("  - table_loo_alignment_robustness:     LOO country robustness (alignment)\n")
cat("  - table_placebo_summary:              Placebo test summary\n")
cat("\nFigures generated in previous scripts:\n")
cat("  - invasion_on_sentiment.png\n")
cat("  - invasion_on_sentiment_non_mil.png\n")
cat("  - invasion_discs_graph.png\n")
cat("  - invasion_discs_non_mil.png\n")
cat("  - state_align_discs.png\n")
cat("  - ethnic_discs.png\n")
cat("  - articles_per_day.png\n")
cat("  - topic_distribution.png\n")
cat("  - topic_split.png\n")
cat("=============================================================\n")
```

# Leave-One-Out Country Robustness Table

```{r loo-table}
loo_data <- results_align$loo_summary

note_loo <- "Leave-one-out robustness analysis for the non-military topics model. Each row shows results when excluding the specified country from the sample. Bandwidth is recalculated for each subset. Coefficient shown is for the treatment:csto interaction term. Standard errors clustered at source domain level."
note_loo_wrapped <- str_wrap(note_loo, width = 80)

loo_table <- loo_data %>%
  mutate(
    estimate_fmt = sprintf("%.3f%s", estimate,
                     case_when(p_value < 0.001 ~ "***",
                               p_value < 0.01 ~ "**",
                               p_value < 0.05 ~ "*",
                               TRUE ~ "")),
    std_error_fmt = sprintf("(%.3f)", std_error),
    p_value_fmt = sprintf("%.3f", p_value),
    n_obs_fmt = format(n_obs, big.mark = ","),
    bandwidth_fmt = sprintf("%.1f", bandwidth)
  ) %>%
  select(country_dropped, estimate_fmt, std_error_fmt, p_value_fmt, n_obs_fmt, bandwidth_fmt) %>%
  gt() %>%
  cols_label(
    country_dropped = "Country Dropped",
    estimate_fmt = "Coefficient",
    std_error_fmt = "Std. Error",
    p_value_fmt = "p-value",
    n_obs_fmt = "N",
    bandwidth_fmt = "Bandwidth"
  ) %>%
  tab_header(title = "Table A: Leave-One-Out Country Robustness Analysis",
             subtitle = "Non-Military Topics Model") %>%
  tab_footnote(footnote = note_loo_wrapped)

loo_table

save_table(loo_table, "table_loo_alignment_robustness")
```

# Placebo Test Summary Table

```{r placebo-summary}
# Extract placebo results from all hypothesis results
# Note: H1 uses rdrobust, H2 and H3 use felm

# Extract rdrobust result for H1
placebo_h1 <- results_h1$model_placebo
h1_estimate <- placebo_h1$coef[1]  # Conventional RD estimate
h1_se <- placebo_h1$se[1]
h1_pval <- placebo_h1$pv[1]
h1_bw <- placebo_h1$bws[1, 1]
h1_n <- placebo_h1$N_h[1] + placebo_h1$N_h[2]

# Extract felm results for H2 and H3
placebo_h2 <- results_h2$model_placebo
placebo_h3 <- results_align$model_placebo_nonmil

h2_coef <- summary(placebo_h2)$coef["treatment", ]
h3_coef <- summary(placebo_h3)$coef["treatment", ]

# Create summary data frame
placebo_summary <- tibble(
  Model = c("(1) H1: Full Model (RDD)", "(2) H2: Diff-in-Disc", "(3) H3: Non-Military"),
  Estimate = c(h1_estimate, h2_coef["Estimate"], h3_coef["Estimate"]),
  Std_Error = c(h1_se, h2_coef["Cluster s.e."], h3_coef["Cluster s.e."]),
  p_value = c(h1_pval, h2_coef["Pr(>|t|)"], h3_coef["Pr(>|t|)"]),
  Bandwidth = c(h1_bw, results_h2$optimal_bw_placebo, results_align$optimal_bw_placebo_nonmil),
  N = c(h1_n, nobs(placebo_h2), nobs(placebo_h3))
)

note_placebo <- "Placebo tests using December 7, 2021 (Putin's announcement) as a false treatment date. Data restricted to pre-invasion period (before Feb 19, 2022). Model 1 uses rdrobust; Models 2-3 use felm with optimal bandwidth. Non-significant treatment effects suggest parallel trends assumption holds."
note_placebo_wrapped <- str_wrap(note_placebo, width = 80)

table_placebo <- placebo_summary %>%
  mutate(
    Estimate_fmt = sprintf("%.3f%s", Estimate,
                     case_when(p_value < 0.001 ~ "***",
                               p_value < 0.01 ~ "**",
                               p_value < 0.05 ~ "*",
                               TRUE ~ "")),
    Std_Error_fmt = sprintf("(%.3f)", Std_Error),
    p_value_fmt = sprintf("%.3f", p_value),
    Bandwidth_fmt = sprintf("%.1f", Bandwidth),
    N_fmt = format(N, big.mark = ",")
  ) %>%
  select(Model, Estimate_fmt, Std_Error_fmt, p_value_fmt, Bandwidth_fmt, N_fmt) %>%
  gt() %>%
  cols_label(
    Model = "Model",
    Estimate_fmt = "Estimate",
    Std_Error_fmt = "Std. Error",
    p_value_fmt = "p-value",
    Bandwidth_fmt = "Bandwidth",
    N_fmt = "N"
  ) %>%
  tab_header(title = "Table B: Placebo Test Summary (December 7, 2021)") %>%
  tab_footnote(footnote = note_placebo_wrapped)

table_placebo

save_table(table_placebo, "table_placebo_summary")
```

# Session Info

```{r session-info}
print_session_info()
```
