---
title: "08 - Publication Outputs"
author: "Donald Moratz"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

# Overview

This script generates all publication-quality tables following a standardized
numbering system.

## Table Numbering System

**Main Paper Tables (Tables 1–4):** One per hypothesis. Each exists in four data variants:

| Suffix | Data variant | Source objects |
|--------|-------------|---------------|
| *(no suffix)* | Day running variable | `results_h1`, `results_h2`, `results_align`, `results_ethnic` |
| *(Prob)* | Probabilistic time assignment | `results_h1_prob`, `results_h2_prob`, `results_align_prob`, `results_ethnic_prob` |
| *(Cont)* | Continuous (seconds) running variable | `results_h1_cont`, `results_h2_cont`, `results_align_cont`, `results_ethnic_cont` |
| *(Drop)* | Drop no-time articles | `results_h1_drop`, `results_h2_drop`, `results_align_drop`, `results_ethnic_drop` |

**Supplementary Tables (Tables S1–S22):**

| Range | Content |
|-------|---------|
| S1–S4 | FE-based main results (all 4 data variants each) |
| S5–S8 | By-topic Z-Score (all 4 data variants each) |
| S9–S12 | By-topic FE, optimal BW (all 4 data variants each) |
| S13–S15 | By-topic FE, full data (all 4 data variants each) |
| S16–S17 | Additional robustness (all 4 data variants each) |
| S18–S22 | Descriptive & diagnostic (standalone, no variants) |

**Inputs:**
- `data/intermediate/04_h1_results.rds`
- `data/intermediate/04_h1_results_continuous.rds`
- `data/intermediate/04_h1_results_drop.rds`
- `data/intermediate/04_h1_results_prob.rds`
- `data/intermediate/05_h2_results.rds`
- `data/intermediate/05_h2_results_continuous.rds`
- `data/intermediate/05_h2_results_drop.rds`
- `data/intermediate/05_h2_results_prob.rds`
- `data/intermediate/06_alignment_results.rds`
- `data/intermediate/06_alignment_results_continuous.rds`
- `data/intermediate/06_alignment_results_drop.rds`
- `data/intermediate/06_alignment_results_prob.rds`
- `data/intermediate/07_ethnic_results.rds`
- `data/intermediate/07_ethnic_results_continuous.rds`
- `data/intermediate/07_ethnic_results_drop.rds`
- `data/intermediate/07_ethnic_results_prob.rds`
- `data/intermediate/02_cleaned_data.rds`

**Outputs:**
- Main paper tables: Tables 1–4, all four data variants each (saved as .tex and .html)
- Supplementary tables: Tables S1–S22 (saved as .tex and .html)

```{r setup, include=FALSE}
source("00_setup.R")
```

# Load Results

```{r load}
# H1: Main RDD results (04 scripts)
results_h1      <- readRDS(file.path(DATA_INTERMEDIATE, "04_h1_results.rds"))
results_h1_cont <- readRDS(file.path(DATA_INTERMEDIATE, "04_h1_results_continuous.rds"))
results_h1_drop <- readRDS(file.path(DATA_INTERMEDIATE, "04_h1_results_drop.rds"))
results_h1_prob <- readRDS(file.path(DATA_INTERMEDIATE, "04_h1_results_prob.rds"))

# H2: Diff-in-disc results (05 scripts)
results_h2      <- readRDS(file.path(DATA_INTERMEDIATE, "05_h2_results.rds"))
results_h2_cont <- readRDS(file.path(DATA_INTERMEDIATE, "05_h2_results_continuous.rds"))
results_h2_drop <- readRDS(file.path(DATA_INTERMEDIATE, "05_h2_results_drop.rds"))
results_h2_prob <- readRDS(file.path(DATA_INTERMEDIATE, "05_h2_results_prob.rds"))

# Russian alignment results (06 scripts – model5a variants)
results_align      <- readRDS(file.path(DATA_INTERMEDIATE, "06_alignment_results.rds"))
results_align_cont <- readRDS(file.path(DATA_INTERMEDIATE, "06_alignment_results_continuous.rds"))
results_align_drop <- readRDS(file.path(DATA_INTERMEDIATE, "06_alignment_results_drop.rds"))
results_align_prob <- readRDS(file.path(DATA_INTERMEDIATE, "06_alignment_results_prob.rds"))

# Ethnic Russian population results (07 scripts – model6a variants)
results_ethnic      <- readRDS(file.path(DATA_INTERMEDIATE, "07_ethnic_results.rds"))
results_ethnic_cont <- readRDS(file.path(DATA_INTERMEDIATE, "07_ethnic_results_continuous.rds"))
results_ethnic_drop <- readRDS(file.path(DATA_INTERMEDIATE, "07_ethnic_results_drop.rds"))
results_ethnic_prob <- readRDS(file.path(DATA_INTERMEDIATE, "07_ethnic_results_prob.rds"))

# Raw data for country classification tables
data <- readRDS(file.path(DATA_INTERMEDIATE, "02_cleaned_data.rds"))

cat("Results loaded successfully.\n")
```


# Model Verification

```{r verify-models}
check_model <- function(obj, name, label) {
  if (is.null(obj[[name]])) {
    cat(sprintf("WARNING: %s$%s not found — table will be skipped\n", label, name))
  } else {
    cat(sprintf("OK: %s$%s\n", label, name))
  }
}

# H2 Z-score separate RDD models (needed for main Table 2)
check_model(results_h2, "model2_state_rdd_z", "results_h2")
check_model(results_h2, "model2_ind_rdd_z",   "results_h2")

# H1 Z-score by-topic models (needed for Table S5)
check_model(results_h1, "model5_opt_pol",  "results_h1")
check_model(results_h1, "model5_opt_mil",  "results_h1")
check_model(results_h1, "model5_opt_econ", "results_h1")
check_model(results_h1, "model5_opt_cult", "results_h1")
check_model(results_h1, "model5_opt_oth",  "results_h1")

# H2 Z-score by-topic models (needed for Table S6)
check_model(results_h2, "model2a_opt_pol",  "results_h2")
check_model(results_h2, "model2a_opt_mil",  "results_h2")
check_model(results_h2, "model2a_opt_econ", "results_h2")
check_model(results_h2, "model2a_opt_cult", "results_h2")
check_model(results_h2, "model2a_opt_oth",  "results_h2")

# H3a Z-score by-topic models (needed for Table S7)
check_model(results_align, "model5a_opt_pol",  "results_align")
check_model(results_align, "model5a_opt_mil",  "results_align")
check_model(results_align, "model5a_opt_econ", "results_align")
check_model(results_align, "model5a_opt_cult", "results_align")
check_model(results_align, "model5a_opt_oth",  "results_align")

# H3b Z-score models (needed for main Table 4 and Table S8)
check_model(results_ethnic, "model6a_high_z",          "results_ethnic")
check_model(results_ethnic, "model6a_low_z",           "results_ethnic")
check_model(results_ethnic, "model6a_z",               "results_ethnic")
check_model(results_ethnic, "model6a_opt_z",           "results_ethnic")
check_model(results_ethnic, "model6a_opt_non_mil_z",   "results_ethnic")
check_model(results_ethnic, "model6a_opt_russian_z",   "results_ethnic")
```

# Helper Functions for Bootstrap Standard Errors

```{r bootstrap-helpers}
# Helper function to create a vcov-like function that returns bootstrap SEs
# This allows modelsummary to display bootstrap standard errors
create_bootstrap_vcov <- function(model, boot_result, coef_name) {
  # Get the original vcov matrix
  original_vcov <- vcov(model)

  # Create a modified vcov matrix with bootstrap SE for the key coefficient
  modified_vcov <- original_vcov

  # Find the coefficient index
  coef_idx <- which(names(coef(model)) == coef_name)

  if (length(coef_idx) > 0 && !is.null(boot_result$se)) {
    # Replace the diagonal element with bootstrap variance (SE^2)
    modified_vcov[coef_idx, coef_idx] <- boot_result$se^2
  }

  return(modified_vcov)
}

# Helper to get significance stars from bootstrap p-value
get_boot_stars <- function(p_val) {
  if (is.null(p_val) || is.na(p_val)) return("")
  if (p_val < 0.001) return("***")
  if (p_val < 0.01) return("**")
  if (p_val < 0.05) return("*")
  if (p_val < 0.1) return("+")
  return("")
}

# Helper to count unique clusters from a felm model
get_n_clusters <- function(model) {
  tryCatch({
    if ("fixest" %in% class(model)) {
      n_cl <- attr(model$cov.scaled, "G")
      if (!is.null(n_cl)) return(as.character(n_cl))
    }
    return("—")
  }, error = function(e) "—")
}
```

# Table Output Helper

```{r save-table-helper}
# Save a gt table as both .tex and .html
save_table <- function(tbl, name) {
  gtsave(tbl, file.path(FIGURES_TABLES, paste0(name, ".tex")))
  gtsave(tbl, file.path(FIGURES_TABLES, paste0(name, ".html")))
  invisible(tbl)
}

# Get Clusters
get_n_clusters <- function(mod) {
  if (inherits(mod, "fixest")) {
    as.character(attr(mod$cov.scaled, "G"))
  } else if (inherits(mod, "rdrobust")) {
    NA
  } else {
    "—"
  }
}


# Standard SE notation footnotes
SE_NOTE_BOOT    <- "† Standard errors computed via wild cluster restricted (WCR) bootstrap (Cameron, Gelbach & Miller 2008) with Webb six-point weights (B=4999, null imposed), clustered by source domain."
SE_NOTE_RDROBUST <- "‡ Cluster-robust SEs from rdrobust."
SE_NOTE_CLUSTER  <- "All standard errors are clustered at the source level."
# Legacy alias kept for existing table code that references SE_NOTE directly
SE_NOTE <- paste(SE_NOTE_BOOT, SE_NOTE_RDROBUST)
```

# =============================================
# MAIN PAPER TABLES
# =============================================

## Table 1: H1 RDD (Day)

```{r table1}

rows <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7,
  'Topic FEs',      '-', '-', '-', 'X', 'X', 'X', 'X',
  'State FEs',      '-', 'X', 'X', 'X', '-', '-', '-',
  'Source FEs',     '-', '-', 'X', 'X', '-', '-', '-',
  'Source Z-Score', '-', '-', '-', '-', 'X', 'X', 'X',
  'Clusters', '61', '61', '61', '61', '61', '61', '61'
)
attr(rows, 'position') <- c(3, 4, 5, 6,7)

note_text <- paste(SE_NOTE_CLUSTER,
                   "Models 1-4 use the optimal bandwidth.",
                   "Models 5-7 use a Z-Score adjustment instead of fixed effects.",
                   "Model 6 omits Military Topics. Model 7 omits NATO allies.")

table_1 <- modelsummary(
  list(
    "(1)" = results_h1$model1_opt,
    "(2)" = results_h1$model2_opt,
    "(3)" = results_h1$model3_opt,
    "(4)" = results_h1$model4_opt,
    "(5)" = results_h1$model5_opt,
    "(6)" = results_h1$model6a_nonmil,
    "(7)" = results_h1$model7a_nonnato
  ),
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c("treatment" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|nobs.left|nobs.right|bandwidth.left|bandwidth.right",
  title = "Table 1: Effect of Russian Invasion on Media Sentiment (RDD, Day Running Variable)",
  add_rows = rows,
  notes = str_wrap(note_text, 80)
)

table_1
save_table(table_1, "table_01_main")
```

## Table 2: H2 Diff-in-Disc (Day)

```{r table2}
models <- list(
  results_h2$model2_state_rdd_z,
  results_h2$model2_ind_rdd_z,
  results_h2$model2a_z,
  results_h2$model2a_opt_z,
  results_h2$model2b_z,
  results_h2$model2d_z,
  results_h2$model3a_z,
  results_h2$matched_model_z
)

cluster_counts <- map_chr(models, get_n_clusters)
cluster_counts[1] <- 17
cluster_counts[2] <- 44

rows <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7, ~row8,
  'Source Z-Score', 'X', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Clusters', cluster_counts[1], cluster_counts[2], cluster_counts[3],
  cluster_counts[4], cluster_counts[5], cluster_counts[6],
  cluster_counts[7], cluster_counts[8]
)
attr(rows, 'position') <- c(5, 6)

note_text <- paste(
  "All models use a source-level Z-Score normalization.",
  SE_NOTE,
  "Models 1-2 show separate RDD estimates for state-owned and independent media, filtered to omit military topics.",
  "Models 3-8 estimate the state-owned × treatment interaction.",
  "Model 3 uses the full dataset. Model 4 uses the optimal bandwidth.",
  "Model 5 omits military topics. Model 6 omits NATO allies.",
  "Model 7 restricts to Russian-related articles with a re-optimized bandwidth.",
  "Model 8 omits military topics and uses matched data across independent and state-owned outlet. Matching done on topic and date of publication."
)

# Bootstrap SE objects for felm models (columns 3-8)
boot_keys <- c("model2a_z", "model2a_opt_z", "model2b_z", "model2d_z", "model3a_z", "matched_model_z")
boot_results <- lapply(boot_keys, function(k) results_h2$bootstrap_se[[k]])

# Create vcov list with bootstrap SEs
vcov_t2 <- list(
  NULL,
  NULL,
  "(3)†" = create_bootstrap_vcov(results_h2$model2a_z, boot_results[[1]], "treatment:state_owned"),
  "(4)†" = create_bootstrap_vcov(results_h2$model2a_opt_z, boot_results[[2]], "treatment:state_owned"),
  "(5)†" = create_bootstrap_vcov(results_h2$model2b_z, boot_results[[3]], "treatment:state_owned"),
  "(6)†" = create_bootstrap_vcov(results_h2$model2d_z, boot_results[[4]], "treatment:state_owned"),
  "(7)†" = create_bootstrap_vcov(results_h2$model3a_z, boot_results[[5]], "treatment:state_owned"),
  "(8)†" = create_bootstrap_vcov(results_h2$matched_model_z, boot_results[[6]], "treatment:state_owned")
)

# Build table with default stars (correct for rdrobust + main effects)
table_2 <- modelsummary(
  list(
    "(1)‡" = results_h2$model2_state_rdd_z,
    "(2)‡" = results_h2$model2_ind_rdd_z,
    "(3)†" = results_h2$model2a_z,
    "(4)†" = results_h2$model2a_opt_z,
    "(5)†" = results_h2$model2b_z,
    "(6)†" = results_h2$model2d_z,
    "(7)†" = results_h2$model3a_z,
    "(8)†" = results_h2$matched_model_z
  ),
  vcov = vcov_t2,
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE|nobs.left|nobs.right|bandwidth.left|bandwidth.right|R2 Within|R2 Within Adj.",
  title = "Table 2: Difference in Discontinuities — State vs. Independent Media (Day Running Variable)",
  add_rows = rows,
  notes = str_wrap(note_text, 80)
)

# Post-process: overwrite interaction row stars with bootstrap p-values
# The interaction row ("State Owned x Treatment") is row 3 in the gt body
# (row 1 = Invasion estimate, row 2 = Invasion SE, row 3 = interaction estimate, row 4 = interaction SE)
interaction_row <- 3
boot_col_names <- paste0("(", 3:8, ")†")

for (i in seq_along(boot_results)) {
  boot_p <- boot_results[[i]]$p_val
  boot_stars <- get_boot_stars(boot_p)
  
  # Extract the current cell value, strip any existing stars, and add bootstrap stars
  table_2 <- table_2 %>%
    text_transform(
      locations = cells_body(columns = boot_col_names[i], rows = interaction_row),
      fn = function(x) {
        # Remove any stars modelsummary may have added
        val <- gsub("[*]+$", "", x)
        paste0(val, boot_stars)
      }
    )
}

table_2
save_table(table_2, "table_02_main")
```


## Table 3: H3a Alignment (Day)

```{r table3}
models <- list(
  results_align$model5a_csto_z,
  results_align$model5a_neutral_z,
  results_align$model5a_z,
  results_align$model5a_opt_z,
  results_align$model5a_opt_non_mil_z,
  results_align$model5a_opt_russian_z,
  results_align$matched_model
)

cluster_counts <- map_chr(models, get_n_clusters)
cluster_counts[1] <- 9
cluster_counts[2] <- 4

rows <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7,
  'Source Z-Score', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Clusters', cluster_counts[1], cluster_counts[2], cluster_counts[3],
  cluster_counts[4], cluster_counts[5], cluster_counts[6], cluster_counts[7]
)
attr(rows, 'position') <- c(5, 6)

note_text <- paste(
  "All models use a source-level Z-Score normalization.",
  SE_NOTE,
  "Sample restricted to state-owned media in non-NATO countries.",
  "Models 1-2 show separate RDD estimates for CSTO-aligned and neutral countries, filtered to omit military topics.",
  "Models 3-7 estimate the CSTO × treatment interaction.",
  "Model 3 uses the full dataset. Model 4 uses the optimal bandwidth.",
  "Model 5 omits military topics.",
  "Model 6 restricts to Russian-related articles with a re-optimized bandwidth.",
  "Model 7 omits military topics and uses matched data across CSTO and neutral countries. Matching done on topic and date of publication."
)

# Bootstrap SE objects for felm models (columns 3-7)
boot_keys <- c("model5a_z", "model5a_opt_z", "model5a_opt_non_mil_z", "model5a_opt_russian_z", "matched_model")
boot_results <- lapply(boot_keys, function(k) results_align$bootstrap_se[[k]])

# Create vcov list with bootstrap SEs for felm models (columns 3-7)
vcov_t3 <- list(
  NULL,
  NULL,
  "(3)†" = create_bootstrap_vcov(results_align$model5a_z, boot_results[[1]], "treatment:csto"),
  "(4)†" = create_bootstrap_vcov(results_align$model5a_opt_z, boot_results[[2]], "treatment:csto"),
  "(5)†" = create_bootstrap_vcov(results_align$model5a_opt_non_mil_z, boot_results[[3]], "treatment:csto"),
  "(6)†" = create_bootstrap_vcov(results_align$model5a_opt_russian_z, boot_results[[4]], "treatment:csto"),
  "(7)†" = create_bootstrap_vcov(results_align$matched_model, boot_results[[5]], "treatment:csto")
)

# Build table with default stars
table_3 <- modelsummary(
  list(
    "(1)‡" = results_align$model5a_csto_z,
    "(2)‡" = results_align$model5a_neutral_z,
    "(3)†" = results_align$model5a_z,
    "(4)†" = results_align$model5a_opt_z,
    "(5)†" = results_align$model5a_opt_non_mil_z,
    "(6)†" = results_align$model5a_opt_russian_z,
    "(7)†" = results_align$matched_model
  ),
  vcov = vcov_t3,
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE|nobs.left|nobs.right|bandwidth.left|bandwidth.right|R2 Within|R2 Within Adj.",
  title = "Table 3: Russian Alignment Heterogeneity — State Media (Day Running Variable)",
  add_rows = rows,
  notes = str_wrap(note_text, 80)
)

# Post-process: overwrite interaction row stars with bootstrap p-values
interaction_row <- 3
boot_col_names <- paste0("(", 3:7, ")†")

for (i in seq_along(boot_results)) {
  boot_p <- boot_results[[i]]$p_val
  boot_stars <- get_boot_stars(boot_p)

  table_3 <- table_3 %>%
    text_transform(
      locations = cells_body(columns = boot_col_names[i], rows = interaction_row),
      fn = function(x) {
        val <- gsub("[*]+$", "", x)
        paste0(val, boot_stars)
      }
    )
}

table_3
save_table(table_3, "table_03_main")
```

## Table 4: H3b Ethnic (Day)

```{r table4}
if (is.null(results_ethnic$model6a_high_z) || is.null(results_ethnic$model6a_low_z) ||
    is.null(results_ethnic$model6a_z) || is.null(results_ethnic$model6a_opt_z) ||
    is.null(results_ethnic$model6a_opt_non_mil_z) || is.null(results_ethnic$model6a_opt_russian_z)) {
  # TODO: Table 4 requires Z-score models to be created in 07_ethnic scripts.
  # Expected model names: model6a_high_z, model6a_low_z, model6a_z, model6a_opt_z,
  # model6a_opt_non_mil_z, model6a_opt_russian_z
  # These should mirror the Z-score model structure in 06_alignment scripts.
  # Once created, uncomment the code below.
  cat("WARNING: Ethnic Z-score models not found for Table 4 — table skipped (TODO).\n")
} else {
  rows <- tibble::tribble(
    ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6,
    'Source Z-Score', 'X', 'X', 'X', 'X', 'X', 'X'
  )
  attr(rows, 'position') <- c(5)

  note_text <- paste(
    "All models use a source-level Z-Score normalization.",
    "Models 1-2 show separate RDD estimates for high and low ethnic Russian population countries.",
    "Models 3-6 estimate the high ethnic Russian pop × treatment interaction.",
    "Model 3 uses the full dataset. Model 4 uses the optimal bandwidth.",
    "Model 5 omits military topics.",
    "Model 6 restricts to Russian-related articles with a re-optimized bandwidth.",
    "Sample restricted to state-owned media in non-NATO countries.",
    SE_NOTE_CLUSTER
  )

  table_4 <- modelsummary(
    list(
      "(1)" = results_ethnic$model6a_high_z,
      "(2)" = results_ethnic$model6a_low_z,
      "(3)" = results_ethnic$model6a_z,
      "(4)" = results_ethnic$model6a_opt_z,
      "(5)" = results_ethnic$model6a_opt_non_mil_z,
      "(6)" = results_ethnic$model6a_opt_russian_z
    ),
    output = "gt",
    fmt = fmt_significant(2),
    stars = TRUE,
    coef_map = c(
      "treatment" = "Invasion",
      "treatment:high_russia" = "High Russian Pop x Treatment"
    ),
    gof_omit = "BIC|AIC|RMSE|Std.Errors|FE|nobs.left|nobs.right|bandwidth.left|bandwidth.right",
    title = "Table 4: Ethnic Russian Population Heterogeneity — State Media (Day Running Variable)",
    add_rows = rows,
    notes = str_wrap(note_text, 80)
  )

  table_4
  save_table(table_4, "table_04_main")
}
```

## Table 1 (Prob): H1 RDD (Probabilistic Time)

```{r table1-prob}
rows <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7,
  'Topic FEs',      '-', '-', '-', 'X', 'X', 'X', 'X',
  'State FEs',      '-', 'X', 'X', 'X', '-', '-', '-',
  'Source FEs',     '-', '-', 'X', 'X', '-', '-', '-',
  'Source Z-Score', '-', '-', '-', '-', 'X', 'X', 'X'
)
attr(rows, 'position') <- c(3, 4, 5, 6)

note_text <- paste(SE_NOTE_CLUSTER,
                   "Articles without publication times are assigned times via KDE sampling.",
                   "Models 1-4 use the optimal bandwidth.",
                   "Models 5-7 use a Z-Score adjustment instead of fixed effects.",
                   "Model 6 omits Military Topics. Model 7 omits NATO allies.")

table_1_prob <- modelsummary(
  list(
    "(1)" = results_h1_prob$model1_opt,
    "(2)" = results_h1_prob$model2_opt,
    "(3)" = results_h1_prob$model3_opt,
    "(4)" = results_h1_prob$model4_opt,
    "(5)" = results_h1_prob$model5_opt,
    "(6)" = results_h1_prob$model6a_nonmil,
    "(7)" = results_h1_prob$model7a_nonnato
  ),
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c("treatment" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|nobs.left|nobs.right|bandwidth.left|bandwidth.right",
  title = "Table 1 (Prob): Effect of Russian Invasion on Media Sentiment (RDD, Probabilistic Time)",
  add_rows = rows,
  notes = str_wrap(note_text, 80)
)

table_1_prob
save_table(table_1_prob, "table_01_main_prob")
```

## Table 2 (Prob): H2 Diff-in-Disc (Probabilistic Time)

```{r table2-prob}
rows <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7,
  'Source Z-Score', 'X', 'X', 'X', 'X', 'X', 'X', 'X'
)
attr(rows, 'position') <- c(5)

note_text <- paste(
  "All models use a source-level Z-Score normalization.",
  "Articles without publication times are assigned times via KDE sampling.",
  "Models 1-2 show separate RDD estimates for state-owned and independent media.",
  "Models 3-7 estimate the state-owned × treatment interaction.",
  "Model 3 uses the full dataset. Model 4 uses the optimal bandwidth.",
  "Model 5 omits military topics. Model 6 omits NATO allies.",
  "Model 7 restricts to Russian-related articles with a re-optimized bandwidth.",
  SE_NOTE_CLUSTER
)


table_2_prob <- modelsummary(
  list(
    "(1)" = results_h2_prob$model2_state_rdd_z,
    "(2)" = results_h2_prob$model2_ind_rdd_z,
    "(3)" = results_h2_prob$model2a_z,
    "(4)" = results_h2_prob$model2a_opt_z,
    "(5)" = results_h2_prob$model2b_z,
    "(6)" = results_h2_prob$model2d_z,
    "(7)" = results_h2_prob$model3a_z
  ),
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE|nobs.left|nobs.right|bandwidth.left|bandwidth.right|R2 Within|R2 Within Adj.",
  title = "Table 2 (Prob): Difference in Discontinuities — State vs. Independent Media (Probabilistic Time)",
  add_rows = rows,
  notes = str_wrap(note_text, 80)
)
table_2_prob
save_table(table_2_prob, "table_02_main_prob")

```

## Table 3 (Prob): H3a Alignment (Probabilistic Time)

```{r table3-prob}
rows <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6,
  'Source Z-Score', 'X', 'X', 'X', 'X', 'X', 'X'
)
attr(rows, 'position') <- c(5)

note_text <- paste(
  "All models use a source-level Z-Score normalization.",
  "Articles without publication times are assigned times via KDE sampling.",
  "Models 1-2 show separate RDD estimates for CSTO-aligned and neutral countries.",
  "Models 3-6 estimate the CSTO × treatment interaction.",
  "Model 3 uses the full dataset. Model 4 uses the optimal bandwidth.",
  "Model 5 omits military topics.",
  "Model 6 restricts to Russian-related articles with a re-optimized bandwidth.",
  "Sample restricted to state-owned media in non-NATO countries.",
  SE_NOTE_CLUSTER
)

table_3_prob <- modelsummary(
  list(
    "(1)" = results_align_prob$model5a_csto_z,
    "(2)" = results_align_prob$model5a_neutral_z,
    "(3)" = results_align_prob$model5a_z,
    "(4)" = results_align_prob$model5a_opt_z,
    "(5)" = results_align_prob$model5a_opt_non_mil_z,
    "(6)" = results_align_prob$model5a_opt_russian_z
  ),
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE|nobs.left|nobs.right|bandwidth.left|bandwidth.right",
  title = "Table 3 (Prob): Russian Alignment Heterogeneity — State Media (Probabilistic Time)",
  add_rows = rows,
  notes = str_wrap(note_text, 80)
)

table_3_prob
save_table(table_3_prob, "table_03_main_prob")
```

## Table 4 (Prob): H3b Ethnic (Probabilistic Time)

```{r table4-prob}
if (is.null(results_ethnic_prob$model6a_high_z) || is.null(results_ethnic_prob$model6a_opt_z)) {
  # TODO: Table 4 (Prob) requires Z-score ethnic models in results_ethnic_prob.
  # Create model6a_high_z, model6a_low_z, model6a_z, model6a_opt_z,
  # model6a_opt_non_mil_z, model6a_opt_russian_z in 07_ethnic_prob scripts.
  cat("WARNING: Ethnic Z-score models not found for Table 4 (Prob) — table skipped (TODO).\n")
} else {
  rows <- tibble::tribble(
    ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6,
    'Source Z-Score', 'X', 'X', 'X', 'X', 'X', 'X'
  )
  attr(rows, 'position') <- c(5)

  note_text <- paste(
    "All models use a source-level Z-Score normalization.",
    "Articles without publication times are assigned times via KDE sampling.",
    "Models 1-2 show separate RDD estimates for high and low ethnic Russian population countries.",
    "Models 3-6 estimate the high ethnic Russian pop × treatment interaction.",
    "Model 3 uses the full dataset. Model 4 uses the optimal bandwidth.",
    "Model 5 omits military topics.",
    "Model 6 restricts to Russian-related articles with a re-optimized bandwidth.",
    "Sample restricted to state-owned media in non-NATO countries.",
    SE_NOTE_CLUSTER
  )

  table_4_prob <- modelsummary(
    list(
      "(1)" = results_ethnic_prob$model6a_high_z,
      "(2)" = results_ethnic_prob$model6a_low_z,
      "(3)" = results_ethnic_prob$model6a_z,
      "(4)" = results_ethnic_prob$model6a_opt_z,
      "(5)" = results_ethnic_prob$model6a_opt_non_mil_z,
      "(6)" = results_ethnic_prob$model6a_opt_russian_z
    ),
    output = "gt",
    fmt = fmt_significant(2),
    stars = TRUE,
    coef_map = c(
      "treatment" = "Invasion",
      "treatment:high_russia" = "High Russian Pop x Treatment"
    ),
    gof_omit = "BIC|AIC|RMSE|Std.Errors|FE|nobs.left|nobs.right|bandwidth.left|bandwidth.right",
    title = "Table 4 (Prob): Ethnic Russian Population Heterogeneity — State Media (Probabilistic Time)",
    add_rows = rows,
    notes = str_wrap(note_text, 80)
  )

  table_4_prob
  save_table(table_4_prob, "table_04_main_prob")
}
```

## Table 1 (Cont): H1 RDD (Continuous Running Variable)

```{r table1-cont}
rows <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7,
  'Topic FEs',      '-', '-', '-', 'X', 'X', 'X', 'X',
  'State FEs',      '-', 'X', 'X', 'X', '-', '-', '-',
  'Source FEs',     '-', '-', 'X', 'X', '-', '-', '-',
  'Source Z-Score', '-', '-', '-', '-', 'X', 'X', 'X'
)
attr(rows, 'position') <- c(3, 4, 5, 6)

note_text <- paste(SE_NOTE_CLUSTER,
                   "Continuous (seconds) running variable.",
                   "Models 1-4 use the optimal bandwidth.",
                   "Models 5-7 use a Z-Score adjustment instead of fixed effects.",
                   "Model 6 omits Military Topics. Model 7 omits NATO allies.")

table_1_cont_new <- modelsummary(
  list(
    "(1)" = results_h1_cont$model1_opt,
    "(2)" = results_h1_cont$model2_opt,
    "(3)" = results_h1_cont$model3_opt,
    "(4)" = results_h1_cont$model4_opt,
    "(5)" = results_h1_cont$model5_opt,
    "(6)" = results_h1_cont$model6a_nonmil,
    "(7)" = results_h1_cont$model7a_nonnato
  ),
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c("treatment" = "Invasion", "post" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors",
  title = "Table 1 (Cont): Effect of Russian Invasion on Media Sentiment (RDD, Continuous Running Variable)",
  add_rows = rows,
  notes = str_wrap(note_text, 80)
)

table_1_cont_new
save_table(table_1_cont_new, "table_01_main_cont")
```

## Table 2 (Cont): H2 Diff-in-Disc (Continuous Running Variable)

```{r table2-cont}
rows <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7,
  'Source Z-Score', 'X', 'X', 'X', 'X', 'X', 'X', 'X'
)
attr(rows, 'position') <- c(5)

note_text <- paste(
  "All models use a source-level Z-Score normalization.",
  "Continuous (seconds) running variable.",
  "Models 1-2 show separate RDD estimates for state-owned and independent media.",
  "Models 3-7 estimate the state-owned × treatment interaction.",
  SE_NOTE_CLUSTER
)

if (is.null(results_h2_cont$model2_state_rdd_z) || is.null(results_h2_cont$model2_ind_rdd_z)) {
  cat("WARNING: Z-score separate RDD models not found for Table 2 (Cont) — skipping.\n")
} else {
  table_2_cont_new <- modelsummary(
    list(
      "(1)" = results_h2_cont$model2_state_rdd_z,
      "(2)" = results_h2_cont$model2_ind_rdd_z,
      "(3)" = results_h2_cont$model2a_z,
      "(4)" = results_h2_cont$model2a_opt_z,
      "(5)" = results_h2_cont$model2b_z,
      "(6)" = results_h2_cont$model2d_z,
      "(7)" = results_h2_cont$model3a_opt_z
    ),
    output = "gt",
    fmt = fmt_significant(2),
    stars = TRUE,
    coef_map = c(
      "treatment" = "Invasion",
      "treatment:state_owned" = "State Owned x Treatment"
    ),
    gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
    title = "Table 2 (Cont): Difference in Discontinuities — State vs. Independent Media (Continuous Running Variable)",
    add_rows = rows,
    notes = str_wrap(note_text, 80)
  )
  table_2_cont_new
  save_table(table_2_cont_new, "table_02_main_cont")
}
```

## Table 3 (Cont): H3a Alignment (Continuous Running Variable)

```{r table3-cont}
rows <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6,
  'Source Z-Score', 'X', 'X', 'X', 'X', 'X', 'X'
)
attr(rows, 'position') <- c(5)

note_text <- paste(
  "All models use a source-level Z-Score normalization.",
  "Continuous (seconds) running variable.",
  "Models 1-2 show separate RDD estimates for CSTO-aligned and neutral countries.",
  "Models 3-6 estimate the CSTO × treatment interaction.",
  "Sample restricted to state-owned media in non-NATO countries.",
  SE_NOTE_CLUSTER
)

table_3_cont_new <- modelsummary(
  list(
    "(1)" = results_align_cont$model5a_csto_z,
    "(2)" = results_align_cont$model5a_neutral_z,
    "(3)" = results_align_cont$model5a_z,
    "(4)" = results_align_cont$model5a_opt_z,
    "(5)" = results_align_cont$model5a_opt_non_mil_z,
    "(6)" = results_align_cont$model5a_opt_russian_z
  ),
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 3 (Cont): Russian Alignment Heterogeneity — State Media (Continuous Running Variable)",
  add_rows = rows,
  notes = str_wrap(note_text, 80)
)

table_3_cont_new
save_table(table_3_cont_new, "table_03_main_cont")
```

## Table 4 (Cont): H3b Ethnic (Continuous Running Variable)

```{r table4-cont}
if (is.null(results_ethnic_cont$model6a_high_z) || is.null(results_ethnic_cont$model6a_opt_z)) {
  # TODO: Table 4 (Cont) requires Z-score ethnic models in results_ethnic_cont.
  cat("WARNING: Ethnic Z-score models not found for Table 4 (Cont) — table skipped (TODO).\n")
} else {
  rows <- tibble::tribble(
    ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6,
    'Source Z-Score', 'X', 'X', 'X', 'X', 'X', 'X'
  )
  attr(rows, 'position') <- c(5)

  note_text <- paste(
    "All models use a source-level Z-Score normalization.",
    "Continuous (seconds) running variable.",
    "Sample restricted to state-owned media in non-NATO countries.",
    SE_NOTE_CLUSTER
  )

  table_4_cont_new <- modelsummary(
    list(
      "(1)" = results_ethnic_cont$model6a_high_z,
      "(2)" = results_ethnic_cont$model6a_low_z,
      "(3)" = results_ethnic_cont$model6a_z,
      "(4)" = results_ethnic_cont$model6a_opt_z,
      "(5)" = results_ethnic_cont$model6a_opt_non_mil_z,
      "(6)" = results_ethnic_cont$model6a_opt_russian_z
    ),
    output = "gt",
    fmt = fmt_significant(2),
    stars = TRUE,
    coef_map = c(
      "treatment" = "Invasion",
      "treatment:high_russia" = "High Russian Pop x Treatment"
    ),
    gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
    title = "Table 4 (Cont): Ethnic Russian Population Heterogeneity — State Media (Continuous Running Variable)",
    add_rows = rows,
    notes = str_wrap(note_text, 80)
  )

  table_4_cont_new
  save_table(table_4_cont_new, "table_04_main_cont")
}
```

## Table 1 (Drop): H1 RDD (Drop No-Time Articles)

```{r table1-drop}
rows <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7,
  'Topic FEs',      '-', '-', '-', 'X', 'X', 'X', 'X',
  'State FEs',      '-', 'X', 'X', 'X', '-', '-', '-',
  'Source FEs',     '-', '-', 'X', 'X', '-', '-', '-',
  'Source Z-Score', '-', '-', '-', '-', 'X', 'X', 'X'
)
attr(rows, 'position') <- c(3, 4, 5, 6)

note_text <- paste(SE_NOTE_CLUSTER,
                   "Articles without publication times are dropped.",
                   "Models 1-4 use the optimal bandwidth.",
                   "Models 5-7 use a Z-Score adjustment instead of fixed effects.",
                   "Model 6 omits Military Topics. Model 7 omits NATO allies.")

table_1_drop_new <- modelsummary(
  list(
    "(1)" = results_h1_drop$model1_opt,
    "(2)" = results_h1_drop$model2_opt,
    "(3)" = results_h1_drop$model3_opt,
    "(4)" = results_h1_drop$model4_opt,
    "(5)" = results_h1_drop$model5_opt,
    "(6)" = results_h1_drop$model6a_nonmil,
    "(7)" = results_h1_drop$model7a_nonnato
  ),
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c("treatment" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors",
  title = "Table 1 (Drop): Effect of Russian Invasion on Media Sentiment (RDD, Drop No-Time Articles)",
  add_rows = rows,
  notes = str_wrap(note_text, 80)
)

table_1_drop_new
save_table(table_1_drop_new, "table_01_main_drop")
```

## Table 2 (Drop): H2 Diff-in-Disc (Drop No-Time Articles)

```{r table2-drop}
rows <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7,
  'Source Z-Score', 'X', 'X', 'X', 'X', 'X', 'X', 'X'
)
attr(rows, 'position') <- c(5)

note_text <- paste(
  "All models use a source-level Z-Score normalization.",
  "Articles without publication times are dropped.",
  "Models 1-2 show separate RDD estimates for state-owned and independent media.",
  "Models 3-7 estimate the state-owned × treatment interaction.",
  SE_NOTE_CLUSTER
)

if (is.null(results_h2_drop$model2_state_rdd_z) || is.null(results_h2_drop$model2_ind_rdd_z)) {
  cat("WARNING: Z-score separate RDD models not found for Table 2 (Drop) — skipping.\n")
} else {
  table_2_drop_new <- modelsummary(
    list(
      "(1)" = results_h2_drop$model2_state_rdd_z,
      "(2)" = results_h2_drop$model2_ind_rdd_z,
      "(3)" = results_h2_drop$model2a_z,
      "(4)" = results_h2_drop$model2a_opt_z,
      "(5)" = results_h2_drop$model2b_z,
      "(6)" = results_h2_drop$model2d_z,
      "(7)" = results_h2_drop$model3a_opt_z
    ),
    output = "gt",
    fmt = fmt_significant(2),
    stars = TRUE,
    coef_map = c(
      "treatment" = "Invasion",
      "treatment:state_owned" = "State Owned x Treatment"
    ),
    gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
    title = "Table 2 (Drop): Difference in Discontinuities — State vs. Independent Media (Drop No-Time Articles)",
    add_rows = rows,
    notes = str_wrap(note_text, 80)
  )
  table_2_drop_new
  save_table(table_2_drop_new, "table_02_main_drop")
}
```

## Table 3 (Drop): H3a Alignment (Drop No-Time Articles)

```{r table3-drop}
rows <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6,
  'Source Z-Score', 'X', 'X', 'X', 'X', 'X', 'X'
)
attr(rows, 'position') <- c(5)

note_text <- paste(
  "All models use a source-level Z-Score normalization.",
  "Articles without publication times are dropped.",
  "Models 1-2 show separate RDD estimates for CSTO-aligned and neutral countries.",
  "Models 3-6 estimate the CSTO × treatment interaction.",
  "Sample restricted to state-owned media in non-NATO countries.",
  SE_NOTE_CLUSTER
)

table_3_drop_new <- modelsummary(
  list(
    "(1)" = results_align_drop$model5a_csto_z,
    "(2)" = results_align_drop$model5a_neutral_z,
    "(3)" = results_align_drop$model5a_z,
    "(4)" = results_align_drop$model5a_opt_z,
    "(5)" = results_align_drop$model5a_opt_non_mil_z,
    "(6)" = results_align_drop$model5a_opt_russian_z
  ),
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table 3 (Drop): Russian Alignment Heterogeneity — State Media (Drop No-Time Articles)",
  add_rows = rows,
  notes = str_wrap(note_text, 80)
)

table_3_drop_new
save_table(table_3_drop_new, "table_03_main_drop")
```

## Table 4 (Drop): H3b Ethnic (Drop No-Time Articles)

```{r table4-drop}
if (is.null(results_ethnic_drop$model6a_high_z) || is.null(results_ethnic_drop$model6a_opt_z)) {
  # TODO: Table 4 (Drop) requires Z-score ethnic models in results_ethnic_drop.
  cat("WARNING: Ethnic Z-score models not found for Table 4 (Drop) — table skipped (TODO).\n")
} else {
  rows <- tibble::tribble(
    ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6,
    'Source Z-Score', 'X', 'X', 'X', 'X', 'X', 'X'
  )
  attr(rows, 'position') <- c(5)

  note_text <- paste(
    "All models use a source-level Z-Score normalization.",
    "Articles without publication times are dropped.",
    "Sample restricted to state-owned media in non-NATO countries.",
    SE_NOTE_CLUSTER
  )

  table_4_drop_new <- modelsummary(
    list(
      "(1)" = results_ethnic_drop$model6a_high_z,
      "(2)" = results_ethnic_drop$model6a_low_z,
      "(3)" = results_ethnic_drop$model6a_z,
      "(4)" = results_ethnic_drop$model6a_opt_z,
      "(5)" = results_ethnic_drop$model6a_opt_non_mil_z,
      "(6)" = results_ethnic_drop$model6a_opt_russian_z
    ),
    output = "gt",
    fmt = fmt_significant(2),
    stars = TRUE,
    coef_map = c(
      "treatment" = "Invasion",
      "treatment:high_russia" = "High Russian Pop x Treatment"
    ),
    gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
    title = "Table 4 (Drop): Ethnic Russian Population Heterogeneity — State Media (Drop No-Time Articles)",
    add_rows = rows,
    notes = str_wrap(note_text, 80)
  )

  table_4_drop_new
  save_table(table_4_drop_new, "table_04_main_drop")
}
```

# =============================================
# SUPPLEMENTARY TABLES
# =============================================

## --- S1–S4: FE-Based Main Results ---

### Table S1 (Days): H1 FE Main Results

```{r table-s01-fe-days}
n_cl_s1 <- sapply(list(results_h1$model1_opt, results_h1$model2_opt, results_h1$model3_opt,
                       results_h1$model4_opt, results_h1$model1_full_linear,
                       results_h1$model4_non_mil, results_h1$model4_non_nato), get_n_clusters)
rows_s1 <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7,
  'State FEs',  '-', 'X', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', 'X', 'X', 'X', 'X', 'X',
  'Topic FEs',  '-', '-', '-', 'X', 'X', 'X', 'X',
  'Clusters', n_cl_s1[1], n_cl_s1[2], n_cl_s1[3], n_cl_s1[4], n_cl_s1[5], n_cl_s1[6], n_cl_s1[7]
)
attr(rows_s1, 'position') <- c(3, 4, 5, 6)

note_s1 <- paste("All standard errors are clustered at the source level.",
                 "Models 1-4 use the optimal bandwidth.",
                 "Model 5 uses a linear specification with the full set of articles.",
                 "Model 6 omits Military Topics. Model 7 omits NATO allies.",
                 SE_NOTE_BOOT)

table_s01_days <- modelsummary(
  list(
    "(1)" = results_h1$model1_opt,
    "(2)" = results_h1$model2_opt,
    "(3)" = results_h1$model3_opt,
    "(4)" = results_h1$model4_opt,
    "(5)" = results_h1$model1_full_linear,
    "(6)" = results_h1$model4_non_mil,
    "(7)" = results_h1$model4_non_nato
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c("treatment" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S1: H1 RDD — Fixed Effects (Day Running Variable)",
  add_rows = rows_s1,
  notes = str_wrap(note_s1, 80)
)

table_s01_days
save_table(table_s01_days, "table_s01_fe_days")
```

### Table S1 (Cont): H1 FE Main Results — Continuous Running Variable

```{r table-s01-fe-cont}
n_cl_t1a <- sapply(list(results_h1_cont$model1_opt, results_h1_cont$model2_opt,
                         results_h1_cont$model3_opt, results_h1_cont$model4_opt,
                         results_h1_cont$model1_full_linear, results_h1_cont$model4_non_mil,
                         results_h1_cont$model4_non_nato, results_h1_cont$model4_felm_saturated),
                   get_n_clusters)
rows_t1a <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7, ~row8,
  'State FEs', '-', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', 'X', 'X', 'X', 'X', 'X', 'X',
  'Topic FEs', '-', '-', '-', 'X', 'X', 'X', 'X', 'X',
  'Clusters', n_cl_t1a[1], n_cl_t1a[2], n_cl_t1a[3], n_cl_t1a[4], n_cl_t1a[5], n_cl_t1a[6], n_cl_t1a[7], n_cl_t1a[8]
)
attr(rows_t1a, 'position') <- c(3, 4, 5, 6)

note_t1a <- paste("All standard errors are clustered at the source level. Models 1-4 uses the optimal bandwidth. Model 5 uses a linear specification with the full set of articles. Model 6 omits Military Topics. Model 7 omits NATO allies. Model 8 uses full saturation (country-source-topic FEs).", SE_NOTE)

table_1_cont <- modelsummary(
  list(
    "(1)" = results_h1_cont$model1_opt,
    "(2)" = results_h1_cont$model2_opt,
    "(3)" = results_h1_cont$model3_opt,
    "(4)" = results_h1_cont$model4_opt,
    "(5)" = results_h1_cont$model1_full_linear,
    "(6)" = results_h1_cont$model4_non_mil,
    "(7)" = results_h1_cont$model4_non_nato,
    "(8)" = results_h1_cont$model4_felm_saturated
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c("treatment" = "Invasion", "post" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S1 (Cont): H1 RDD — Fixed Effects (Continuous Running Variable)",
  add_rows = rows_t1a,
  notes = str_wrap(note_t1a, 80)
)

table_1_cont

save_table(table_1_cont, "table_s01_fe_cont")
```

## Table 1B: RDD By Topic (Day)

```{r table1b}
n_cl_t1b <- sapply(list(results_h1$model4_opt_pol, results_h1$model4_opt_mil,
                         results_h1$model4_opt_econ, results_h1$model4_opt_cult,
                         results_h1$model4_opt_oth), get_n_clusters)
rows_t1b <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', 'X', 'X', 'X', 'X', 'X',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t1b[1], n_cl_t1b[2], n_cl_t1b[3], n_cl_t1b[4], n_cl_t1b[5]
)
attr(rows_t1b, 'position') <- c(3, 4, 5, 6)

note_t1b <- paste("All standard errors are clustered at the source level. All models use the optimal bandwidth with country and source fixed effects.", SE_NOTE)

table_1b <- modelsummary(
  list(
    "Political" = results_h1$model4_opt_pol,
    "Military" = results_h1$model4_opt_mil,
    "Economic" = results_h1$model4_opt_econ,
    "Cultural" = results_h1$model4_opt_cult,
    "Other" = results_h1$model4_opt_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c("treatment" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S9: H1 RDD by Topic — FE, Optimal BW (Day Running Variable)",
  add_rows = rows_t1b,
  notes = str_wrap(note_t1b, 80)
)

table_1b

save_table(table_1b, "table_s09_fe_topic_opt_days")
```

## --- S5–S8: By-Topic Z-Score ---

### Table S5 (Days): H1 By-Topic Z-Score

```{r table-s05-z-topic-days}
models_1bz <- list(
  "Political" = results_h1$model5_opt_pol,
  "Military" = results_h1$model5_opt_mil,
  "Economic" = results_h1$model5_opt_econ,
  "Cultural" = results_h1$model5_opt_cult,
  "Other" = results_h1$model5_opt_oth
)
tbl_1bz <- modelsummary(
  models_1bz,
  output = "gt",
  coef_map = c("treatment" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  stars = c('*' = .05, '**' = .01, '***' = .001),
  fmt = 3,
  title = "Table S5: H1 RDD by Topic — Z-Score (Day Running Variable)"
)
tbl_1bz
save_table(tbl_1bz, "table_s05_z_topic_days")
```

## Table 1C: RDD By Topic (Continuous)

```{r table1c}
n_cl_t1c <- sapply(list(results_h1_cont$model4_opt_pol, results_h1_cont$model4_opt_mil,
                         results_h1_cont$model4_opt_econ, results_h1_cont$model4_opt_cult,
                         results_h1_cont$model4_opt_oth), get_n_clusters)
rows_t1c <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', 'X', 'X', 'X', 'X', 'X',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t1c[1], n_cl_t1c[2], n_cl_t1c[3], n_cl_t1c[4], n_cl_t1c[5]
)
attr(rows_t1c, 'position') <- c(3, 4, 5, 6)

note_t1c <- paste("All standard errors are clustered at the source level. All models use the optimal bandwidth with country and source fixed effects.", SE_NOTE)

table_1c <- modelsummary(
  list(
    "Political" = results_h1_cont$model4_opt_pol,
    "Military" = results_h1_cont$model4_opt_mil,
    "Economic" = results_h1_cont$model4_opt_econ,
    "Cultural" = results_h1_cont$model4_opt_cult,
    "Other" = results_h1_cont$model4_opt_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c("treatment" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S9 (Cont): H1 RDD by Topic — FE, Optimal BW (Continuous Running Variable)",
  add_rows = rows_t1c,
  notes = str_wrap(note_t1c, 80)
)

table_1c

save_table(table_1c, "table_s09_fe_topic_opt_cont")
```

### Table S5 (Cont): H1 By-Topic Z-Score — Continuous

```{r table-s05-z-topic-cont}
models_1cz <- list(
  "Political" = results_h1_cont$model5_opt_pol,
  "Military" = results_h1_cont$model5_opt_mil,
  "Economic" = results_h1_cont$model5_opt_econ,
  "Cultural" = results_h1_cont$model5_opt_cult,
  "Other" = results_h1_cont$model5_opt_oth
)
tbl_1cz <- modelsummary(
  models_1cz,
  output = "gt",
  coef_map = c("treatment" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  stars = c('*' = .05, '**' = .01, '***' = .001),
  fmt = 3,
  title = "Table S5 (Cont): H1 RDD by Topic — Z-Score (Continuous Running Variable)"
)
tbl_1cz
save_table(tbl_1cz, "table_s05_z_topic_cont")
```

# Table 2: Diff-in-Disc Results

```{r table-s02-fe-days}
n_cl_t2 <- sapply(list(results_h2$model2a, results_h2$model2a_full,
                        results_h2$model2a_opt, results_h2$model2a_opt_full_fe,
                        results_h2$model2b, results_h2$model2d,
                        results_h2$model3a_opt, results_h2$model3a_opt_saturated),
                  get_n_clusters)
rows_t2 <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7, ~row8,
  'State FEs', 'X', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', 'X', '-', 'X', '-', '-', '-', 'X',
  'Topic FEs', 'X', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Clusters', n_cl_t2[1], n_cl_t2[2], n_cl_t2[3], n_cl_t2[4], n_cl_t2[5], n_cl_t2[6], n_cl_t2[7], n_cl_t2[8]
)
attr(rows_t2, 'position') <- c(5, 6, 7, 8)

note_t2 <- paste("All standard errors are clustered at the source level. Model 1 uses full data with topic FEs. Model 2 adds source FEs. Model 3 uses optimal bandwidth with topic FEs. Model 4 uses optimal bandwidth with full FEs. Model 5 omits military-related articles. Model 6 omits NATO allies. Model 7 combines Russian-related + combined bandwidth filters. Model 8 uses saturated FEs.", SE_NOTE)

table_2 <- modelsummary(
  list(
    "(1)" = results_h2$model2a,
    "(2)" = results_h2$model2a_full,
    "(3)" = results_h2$model2a_opt,
    "(4)" = results_h2$model2a_opt_full_fe,
    "(5)" = results_h2$model2b,
    "(6)" = results_h2$model2d,
    "(7)" = results_h2$model3a_opt,
    "(8)" = results_h2$model3a_opt_saturated
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S2: H2 Diff-in-Disc — Fixed Effects (Day Running Variable)",
  add_rows = rows_t2,
  notes = str_wrap(note_t2, 80)
)

table_2

save_table(table_2, "table_s02_fe_days")
```

## Table 2-S: H2 Diff-in-Disc (Days) — Full FE Robustness

```{r table2s}
n_cl_t2s <- sapply(list(results_h2$model2b_full_fe, results_h2$model3a_opt_full_fe),
                   get_n_clusters)
rows_t2s <- tibble::tribble(
  ~term, ~row1, ~row2,
  'State FEs', 'X', 'X',
  'Source FEs', 'X', 'X',
  'Topic FEs', 'X', 'X',
  'Clusters', n_cl_t2s[1], n_cl_t2s[2]
)
attr(rows_t2s, 'position') <- c(5, 6, 7, 8)

note_t2s <- paste("All standard errors are clustered at the source level. Both models include full FEs (topic + source). Model 1 uses non-military subset. Model 2 uses Russian-related + combined bandwidth filters.", SE_NOTE)

table_2s <- modelsummary(
  list(
    "(1) Non-Mil, Full FEs" = results_h2$model2b_full_fe,
    "(2) Russian Opt, Full FEs" = results_h2$model3a_opt_full_fe
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S16: H2 Diff-in-Disc — Full FE Robustness (Day Running Variable)",
  add_rows = rows_t2s,
  notes = str_wrap(note_t2s, 80)
)

table_2s

save_table(table_2s, "table_s16_full_fe_robustness_days")
```

## Table 2A: Diff-in-Disc (Continuous)

```{r table2a}
n_cl_t2a <- sapply(list(results_h2_cont$model2a, results_h2_cont$model2a_full,
                         results_h2_cont$model2a_opt, results_h2_cont$model2a_opt_full_fe,
                         results_h2_cont$model2b, results_h2_cont$model2d,
                         results_h2_cont$model3a_opt, results_h2_cont$model3a_opt_saturated),
                   get_n_clusters)
rows_t2a <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7, ~row8,
  'State FEs', 'X', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', 'X', '-', 'X', '-', '-', '-', 'X',
  'Topic FEs', 'X', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Clusters', n_cl_t2a[1], n_cl_t2a[2], n_cl_t2a[3], n_cl_t2a[4], n_cl_t2a[5], n_cl_t2a[6], n_cl_t2a[7], n_cl_t2a[8]
)
attr(rows_t2a, 'position') <- c(5, 6, 7, 8)

note_t2a <- paste("All standard errors are clustered at the source level. Model 1 uses full data with topic FEs. Model 2 adds source FEs. Model 3 uses optimal bandwidth with topic FEs. Model 4 uses optimal bandwidth with full FEs. Model 5 omits military-related articles. Model 6 omits NATO allies. Model 7 combines Russian-related + combined bandwidth filters. Model 8 uses saturated FEs.", SE_NOTE)

table_2a <- modelsummary(
  list(
    "(1)" = results_h2_cont$model2a,
    "(2)" = results_h2_cont$model2a_full,
    "(3)" = results_h2_cont$model2a_opt,
    "(4)" = results_h2_cont$model2a_opt_full_fe,
    "(5)" = results_h2_cont$model2b,
    "(6)" = results_h2_cont$model2d,
    "(7)" = results_h2_cont$model3a_opt,
    "(8)" = results_h2_cont$model3a_opt_saturated
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S2 (Cont): H2 Diff-in-Disc — Fixed Effects (Continuous Running Variable)",
  add_rows = rows_t2a,
  notes = str_wrap(note_t2a, 80)
)

table_2a

save_table(table_2a, "table_s02_fe_cont")
```

## Table 2A-S: H2 Diff-in-Disc (Continuous) — Full FE Robustness

```{r table2as}
n_cl_t2as <- sapply(list(results_h2_cont$model2b_full_fe, results_h2_cont$model3a_opt_full_fe),
                    get_n_clusters)
rows_t2as <- tibble::tribble(
  ~term, ~row1, ~row2,
  'State FEs', 'X', 'X',
  'Source FEs', 'X', 'X',
  'Topic FEs', 'X', 'X',
  'Clusters', n_cl_t2as[1], n_cl_t2as[2]
)
attr(rows_t2as, 'position') <- c(5, 6, 7, 8)

note_t2as <- paste("All standard errors are clustered at the source level. Both models include full FEs (topic + source). Model 1 uses non-military subset. Model 2 uses Russian-related + combined bandwidth filters.", SE_NOTE)

table_2as <- modelsummary(
  list(
    "(1) Non-Mil, Full FEs" = results_h2_cont$model2b_full_fe,
    "(2) Russian Opt, Full FEs" = results_h2_cont$model3a_opt_full_fe
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S16 (Cont): H2 Diff-in-Disc — Full FE Robustness (Continuous Running Variable)",
  add_rows = rows_t2as,
  notes = str_wrap(note_t2as, 80)
)

table_2as

save_table(table_2as, "table_s16_full_fe_robustness_cont")
```

## Table 2B: Diff-in-Disc By Topic (Day)

```{r table2b}
n_cl_t2b <- sapply(list(results_h2$model2a_opt_pol, results_h2$model2a_opt_mil,
                         results_h2$model2a_opt_econ, results_h2$model2a_opt_cult,
                         results_h2$model2a_opt_oth), get_n_clusters)
rows_t2b <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t2b[1], n_cl_t2b[2], n_cl_t2b[3], n_cl_t2b[4], n_cl_t2b[5]
)
attr(rows_t2b, 'position') <- c(5, 6, 7, 8)

note_t2b <- paste("All standard errors are clustered at the source level. All models use a per-topic re-optimized bandwidth with country fixed effects only.", SE_NOTE)

table_2b <- modelsummary(
  list(
    "Political" = results_h2$model2a_opt_pol,
    "Military" = results_h2$model2a_opt_mil,
    "Economic" = results_h2$model2a_opt_econ,
    "Cultural" = results_h2$model2a_opt_cult,
    "Other" = results_h2$model2a_opt_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S10: H2 Diff-in-Disc by Topic — FE, Optimal BW (Day Running Variable)",
  add_rows = rows_t2b,
  notes = str_wrap(note_t2b, 80)
)

table_2b

save_table(table_2b, "table_s10_fe_topic_opt_days")
```

## Table 2C: Diff-in-Disc By Topic (Continuous)

```{r table2c}
n_cl_t2c <- sapply(list(results_h2_cont$model2a_opt_pol, results_h2_cont$model2a_opt_mil,
                         results_h2_cont$model2a_opt_econ, results_h2_cont$model2a_opt_cult,
                         results_h2_cont$model2a_opt_oth), get_n_clusters)
rows_t2c <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t2c[1], n_cl_t2c[2], n_cl_t2c[3], n_cl_t2c[4], n_cl_t2c[5]
)
attr(rows_t2c, 'position') <- c(5, 6, 7, 8)

note_t2c <- paste("All standard errors are clustered at the source level. All models use a per-topic re-optimized bandwidth with country fixed effects only.", SE_NOTE)

table_2c <- modelsummary(
  list(
    "Political" = results_h2_cont$model2a_opt_pol,
    "Military" = results_h2_cont$model2a_opt_mil,
    "Economic" = results_h2_cont$model2a_opt_econ,
    "Cultural" = results_h2_cont$model2a_opt_cult,
    "Other" = results_h2_cont$model2a_opt_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S10 (Cont): H2 Diff-in-Disc by Topic — FE, Optimal BW (Continuous Running Variable)",
  add_rows = rows_t2c,
  notes = str_wrap(note_t2c, 80)
)

table_2c

save_table(table_2c, "table_s10_fe_topic_opt_cont")
```

## Table 2D: Diff-in-Disc By Topic Full Data (Day)

```{r table2d}
n_cl_t2d <- sapply(list(results_h2$model2a_full_pol, results_h2$model2a_full_mil,
                         results_h2$model2a_full_econ, results_h2$model2a_full_cult,
                         results_h2$model2a_full_oth), get_n_clusters)
rows_t2d <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t2d[1], n_cl_t2d[2], n_cl_t2d[3], n_cl_t2d[4], n_cl_t2d[5]
)
attr(rows_t2d, 'position') <- c(5, 6, 7, 8)

note_t2d <- paste("All standard errors are clustered at the source level. All models use the full dataset (no bandwidth restriction) with country fixed effects only.", SE_NOTE)

table_2d <- modelsummary(
  list(
    "Political" = results_h2$model2a_full_pol,
    "Military" = results_h2$model2a_full_mil,
    "Economic" = results_h2$model2a_full_econ,
    "Cultural" = results_h2$model2a_full_cult,
    "Other" = results_h2$model2a_full_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S13: H2 Diff-in-Disc by Topic — FE, Full Data (Day Running Variable)",
  add_rows = rows_t2d,
  notes = str_wrap(note_t2d, 80)
)

table_2d

save_table(table_2d, "table_s13_fe_topic_full_days")
```

## Table 2E: Diff-in-Disc By Topic Full Data (Continuous)

```{r table2e}
n_cl_t2e <- sapply(list(results_h2_cont$model2a_full_pol, results_h2_cont$model2a_full_mil,
                         results_h2_cont$model2a_full_econ, results_h2_cont$model2a_full_cult,
                         results_h2_cont$model2a_full_oth), get_n_clusters)
rows_t2e <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t2e[1], n_cl_t2e[2], n_cl_t2e[3], n_cl_t2e[4], n_cl_t2e[5]
)
attr(rows_t2e, 'position') <- c(5, 6, 7, 8)

note_t2e <- paste("All standard errors are clustered at the source level. All models use the full dataset (no bandwidth restriction) with country fixed effects only.", SE_NOTE)

table_2e <- modelsummary(
  list(
    "Political" = results_h2_cont$model2a_full_pol,
    "Military" = results_h2_cont$model2a_full_mil,
    "Economic" = results_h2_cont$model2a_full_econ,
    "Cultural" = results_h2_cont$model2a_full_cult,
    "Other" = results_h2_cont$model2a_full_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S13 (Cont): H2 Diff-in-Disc by Topic — FE, Full Data (Continuous Running Variable)",
  add_rows = rows_t2e,
  notes = str_wrap(note_t2e, 80)
)

table_2e

save_table(table_2e, "table_s13_fe_topic_full_cont")
```

# Table 3: Heterogeneity by Russian Alignment

```{r table-s03-fe-days}
n_cl_t3 <- sapply(list(results_align$model5a_csto, results_align$model5a_neutral,
                       results_align$model5a_full, results_align$model5a_opt,
                       results_align$model5a_opt_non_mil, results_align$model5a_opt_russian,
                       results_align$model5a_opt_full_fe, results_align$model5a_opt_non_mil_full_fe,
                       results_align$model5a_fully_saturated, results_align$matched_model), get_n_clusters)
rows_t3 <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7, ~row8, ~row9, ~row10,
  'State FEs', '-', '-', 'X', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-', '-', 'X', 'X', 'X', 'X',
  'Topic FEs', '-', '-', 'X', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Matched', '-', '-', '-', '-', '-', '-', '-', '-', '-', 'X',
  'Clusters', n_cl_t3[1], n_cl_t3[2], n_cl_t3[3], n_cl_t3[4], n_cl_t3[5], n_cl_t3[6], n_cl_t3[7], n_cl_t3[8], n_cl_t3[9], n_cl_t3[10]
)
attr(rows_t3, 'position') <- c(5, 6, 7, 8, 9)

note_t3 <- paste("Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights) for Models 3-10, clustered at source level. Models 1-2 use rdrobust standard errors. Model 1 shows RDD results for CSTO countries only. Model 2 shows RDD results for Neutral countries only. Model 3 uses full data with topic fixed effects. Model 4 uses the optimal bandwidth with topic fixed effects. Model 5 omits military-related articles and uses a re-optimized bandwidth. Model 6 uses only Russian-related (non-military) articles with a re-optimized bandwidth. Model 7 uses optimal bandwidth with full FEs (topic + source + state FEs). Model 8 uses non-military subset with full FEs. Model 9 uses full saturation (source-topic and topic-treatment FEs). Model 10 uses exact matching on publication day and topic. Sample restricted to state-owned media in non-NATO countries.", SE_NOTE)

# Create vcov list with bootstrap SEs for felm models (columns 3-10)
vcov_t3 <- list(
  NULL,
  NULL,
  "(3)" = create_bootstrap_vcov(results_align$model5a_full, results_align$bootstrap_se$model5a_full, "treatment:csto"),
  "(4)" = create_bootstrap_vcov(results_align$model5a_opt, results_align$bootstrap_se$model5a_opt, "treatment:csto"),
  "(5)" = create_bootstrap_vcov(results_align$model5a_opt_non_mil, results_align$bootstrap_se$model5a_opt_non_mil, "treatment:csto"),
  "(6)" = create_bootstrap_vcov(results_align$model5a_opt_russian, results_align$bootstrap_se$model5a_opt_russian, "treatment:csto"),
  "(7)" = create_bootstrap_vcov(results_align$model5a_opt_full_fe, results_align$bootstrap_se$model5a_opt_full_fe, "treatment:csto"),
  "(8)" = create_bootstrap_vcov(results_align$model5a_opt_non_mil_full_fe, results_align$bootstrap_se$model5a_opt_non_mil_full_fe, "treatment:csto"),
  "(9)" = create_bootstrap_vcov(results_align$model5a_fully_saturated, results_align$bootstrap_se$model5a_fully_saturated, "treatment:csto"),
  "(10)" = create_bootstrap_vcov(results_align$matched_model, results_align$bootstrap_se$matched_model, "treatment:csto")
)

table_3 <- modelsummary(
  list(
    "(1)" = results_align$model5a_csto,
    "(2)" = results_align$model5a_neutral,
    "(3)" = results_align$model5a_full,
    "(4)" = results_align$model5a_opt,
    "(5)" = results_align$model5a_opt_non_mil,
    "(6)" = results_align$model5a_opt_russian,
    "(7)" = results_align$model5a_opt_full_fe,
    "(8)" = results_align$model5a_opt_non_mil_full_fe,
    "(9)" = results_align$model5a_fully_saturated,
    "(10)" = results_align$matched_model
  ),
  vcov = vcov_t3,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S3: H3a Alignment — Fixed Effects (Day Running Variable)",
  add_rows = rows_t3,
  notes = str_wrap(note_t3, 80)
)

table_3

save_table(table_3, "table_s03_fe_days")
```

## Table 3A: Heterogeneity (Continuous)

```{r table3a}
n_cl_t3a <- sapply(list(results_align_cont$model5a_csto, results_align_cont$model5a_neutral,
                        results_align_cont$model5a_full, results_align_cont$model5a_opt,
                        results_align_cont$model5a_opt_non_mil, results_align_cont$model5a_opt_russian,
                        results_align_cont$model5a_opt_full_fe, results_align_cont$model5a_opt_non_mil_full_fe,
                        results_align_cont$model5a_fully_saturated, results_align_cont$matched_model),
                   get_n_clusters)
rows_t3a <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7, ~row8, ~row9, ~row10,
  'State FEs', '-', '-', 'X', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-', '-', 'X', 'X', 'X', 'X',
  'Topic FEs', '-', '-', 'X', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Matched', '-', '-', '-', '-', '-', '-', '-', '-', '-', 'X',
  'Clusters', n_cl_t3a[1], n_cl_t3a[2], n_cl_t3a[3], n_cl_t3a[4], n_cl_t3a[5], n_cl_t3a[6], n_cl_t3a[7], n_cl_t3a[8], n_cl_t3a[9], n_cl_t3a[10]
)
attr(rows_t3a, 'position') <- c(5, 6, 7, 8, 9)

note_t3a <- paste("Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights) for Models 3-10, clustered at source level. Models 1-2 use rdrobust standard errors. Model 1 shows RDD results for CSTO countries only. Model 2 shows RDD results for Neutral countries only. Model 3 uses full data with topic fixed effects. Model 4 uses the optimal bandwidth with topic fixed effects. Model 5 omits military-related articles and uses a re-optimized bandwidth. Model 6 uses only Russian-related (non-military) articles with a re-optimized bandwidth. Model 7 uses optimal bandwidth with full FEs (topic + source + state FEs). Model 8 uses non-military subset with full FEs. Model 9 uses full saturation (source-topic and topic-treatment FEs). Model 10 uses exact matching on publication day and topic. Sample restricted to state-owned media in non-NATO countries.", SE_NOTE)

# Create vcov list with bootstrap SEs for felm models
vcov_t3a <- list(
  NULL,
  NULL,
  "(3)" = create_bootstrap_vcov(results_align_cont$model5a_full, results_align_cont$bootstrap_se$model5a_full, "treatment:csto"),
  "(4)" = create_bootstrap_vcov(results_align_cont$model5a_opt, results_align_cont$bootstrap_se$model5a_opt, "treatment:csto"),
  "(5)" = create_bootstrap_vcov(results_align_cont$model5a_opt_non_mil, results_align_cont$bootstrap_se$model5a_opt_non_mil, "treatment:csto"),
  "(6)" = create_bootstrap_vcov(results_align_cont$model5a_opt_russian, results_align_cont$bootstrap_se$model5a_opt_russian, "treatment:csto"),
  "(7)" = create_bootstrap_vcov(results_align_cont$model5a_opt_full_fe, results_align_cont$bootstrap_se$model5a_opt_full_fe, "treatment:csto"),
  "(8)" = create_bootstrap_vcov(results_align_cont$model5a_opt_non_mil_full_fe, results_align_cont$bootstrap_se$model5a_opt_non_mil_full_fe, "treatment:csto"),
  "(9)" = create_bootstrap_vcov(results_align_cont$model5a_fully_saturated, results_align_cont$bootstrap_se$model5a_fully_saturated, "treatment:csto"),
  "(10)" = create_bootstrap_vcov(results_align_cont$matched_model, results_align_cont$bootstrap_se$matched_model, "treatment:csto")
)

table_3a <- modelsummary(
  list(
    "(1)" = results_align_cont$model5a_csto,
    "(2)" = results_align_cont$model5a_neutral,
    "(3)" = results_align_cont$model5a_full,
    "(4)" = results_align_cont$model5a_opt,
    "(5)" = results_align_cont$model5a_opt_non_mil,
    "(6)" = results_align_cont$model5a_opt_russian,
    "(7)" = results_align_cont$model5a_opt_full_fe,
    "(8)" = results_align_cont$model5a_opt_non_mil_full_fe,
    "(9)" = results_align_cont$model5a_fully_saturated,
    "(10)" = results_align_cont$matched_model
  ),
  vcov = vcov_t3a,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S3 (Cont): H3a Alignment — Fixed Effects (Continuous Running Variable)",
  add_rows = rows_t3a,
  notes = str_wrap(note_t3a, 80)
)

table_3a

save_table(table_3a, "table_s03_fe_cont")
```

## Table 3B: Heterogeneity By Topic Optimal BW (Day)

```{r table3b}
n_cl_t3b <- sapply(list(results_align$model5a_opt_pol, results_align$model5a_opt_mil,
                        results_align$model5a_opt_econ, results_align$model5a_opt_cult,
                        results_align$model5a_opt_oth), get_n_clusters)
rows_t3b <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t3b[1], n_cl_t3b[2], n_cl_t3b[3], n_cl_t3b[4], n_cl_t3b[5]
)
attr(rows_t3b, 'position') <- c(5, 6, 7, 8)

note_t3b <- paste("Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights), clustered at source level. Each model uses a per-topic re-optimized bandwidth. State media in non-NATO countries only.", SE_NOTE)

# Create vcov list with bootstrap SEs for topic models
vcov_t3b <- list(
  "Political" = create_bootstrap_vcov(results_align$model5a_opt_pol, results_align$bootstrap_se$model5a_opt_pol, "treatment:csto"),
  "Military" = create_bootstrap_vcov(results_align$model5a_opt_mil, results_align$bootstrap_se$model5a_opt_mil, "treatment:csto"),
  "Economic" = create_bootstrap_vcov(results_align$model5a_opt_econ, results_align$bootstrap_se$model5a_opt_econ, "treatment:csto"),
  "Cultural" = create_bootstrap_vcov(results_align$model5a_opt_cult, results_align$bootstrap_se$model5a_opt_cult, "treatment:csto"),
  "Other" = create_bootstrap_vcov(results_align$model5a_opt_oth, results_align$bootstrap_se$model5a_opt_oth, "treatment:csto")
)

table_3b <- modelsummary(
  list(
    "Political" = results_align$model5a_opt_pol,
    "Military" = results_align$model5a_opt_mil,
    "Economic" = results_align$model5a_opt_econ,
    "Cultural" = results_align$model5a_opt_cult,
    "Other" = results_align$model5a_opt_oth
  ),
  vcov = vcov_t3b,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S11: H3a Alignment by Topic — FE, Optimal BW (Day Running Variable)",
  add_rows = rows_t3b,
  notes = str_wrap(note_t3b, 80)
)

table_3b

save_table(table_3b, "table_s11_fe_topic_opt_days")
```

## Table 3C: Heterogeneity By Topic Optimal BW (Continuous)

```{r table3c}
n_cl_t3c <- sapply(list(results_align_cont$model5a_opt_pol, results_align_cont$model5a_opt_mil,
                        results_align_cont$model5a_opt_econ, results_align_cont$model5a_opt_cult,
                        results_align_cont$model5a_opt_oth), get_n_clusters)
rows_t3c <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t3c[1], n_cl_t3c[2], n_cl_t3c[3], n_cl_t3c[4], n_cl_t3c[5]
)
attr(rows_t3c, 'position') <- c(5, 6, 7, 8)

note_t3c <- paste("Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights), clustered at source level. Each model uses a per-topic re-optimized bandwidth. State media in non-NATO countries only.", SE_NOTE)

# Create vcov list with bootstrap SEs for topic models
vcov_t3c <- list(
  "Political" = create_bootstrap_vcov(results_align_cont$model5a_opt_pol, results_align_cont$bootstrap_se$model5a_opt_pol, "treatment:csto"),
  "Military" = create_bootstrap_vcov(results_align_cont$model5a_opt_mil, results_align_cont$bootstrap_se$model5a_opt_mil, "treatment:csto"),
  "Economic" = create_bootstrap_vcov(results_align_cont$model5a_opt_econ, results_align_cont$bootstrap_se$model5a_opt_econ, "treatment:csto"),
  "Cultural" = create_bootstrap_vcov(results_align_cont$model5a_opt_cult, results_align_cont$bootstrap_se$model5a_opt_cult, "treatment:csto"),
  "Other" = create_bootstrap_vcov(results_align_cont$model5a_opt_oth, results_align_cont$bootstrap_se$model5a_opt_oth, "treatment:csto")
)

table_3c <- modelsummary(
  list(
    "Political" = results_align_cont$model5a_opt_pol,
    "Military" = results_align_cont$model5a_opt_mil,
    "Economic" = results_align_cont$model5a_opt_econ,
    "Cultural" = results_align_cont$model5a_opt_cult,
    "Other" = results_align_cont$model5a_opt_oth
  ),
  vcov = vcov_t3c,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S11 (Cont): H3a Alignment by Topic — FE, Optimal BW (Continuous Running Variable)",
  add_rows = rows_t3c,
  notes = str_wrap(note_t3c, 80)
)

table_3c

save_table(table_3c, "table_s11_fe_topic_opt_cont")
```

## Table 3D: Heterogeneity By Topic Full Data (Day)

```{r table3d}
n_cl_t3d <- sapply(list(results_align$model5a_full_pol, results_align$model5a_full_mil,
                        results_align$model5a_full_econ, results_align$model5a_full_cult,
                        results_align$model5a_full_oth), get_n_clusters)
rows_t3d <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t3d[1], n_cl_t3d[2], n_cl_t3d[3], n_cl_t3d[4], n_cl_t3d[5]
)
attr(rows_t3d, 'position') <- c(5, 6, 7, 8)

note_t3d <- paste("Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights), clustered at source level. Each model uses the full dataset (no bandwidth restriction). State media in non-NATO countries only.", SE_NOTE)

# Create vcov list with bootstrap SEs for topic models
vcov_t3d <- list(
  "Political" = create_bootstrap_vcov(results_align$model5a_full_pol, results_align$bootstrap_se$model5a_full_pol, "treatment:csto"),
  "Military" = create_bootstrap_vcov(results_align$model5a_full_mil, results_align$bootstrap_se$model5a_full_mil, "treatment:csto"),
  "Economic" = create_bootstrap_vcov(results_align$model5a_full_econ, results_align$bootstrap_se$model5a_full_econ, "treatment:csto"),
  "Cultural" = create_bootstrap_vcov(results_align$model5a_full_cult, results_align$bootstrap_se$model5a_full_cult, "treatment:csto"),
  "Other" = create_bootstrap_vcov(results_align$model5a_full_oth, results_align$bootstrap_se$model5a_full_oth, "treatment:csto")
)

table_3d <- modelsummary(
  list(
    "Political" = results_align$model5a_full_pol,
    "Military" = results_align$model5a_full_mil,
    "Economic" = results_align$model5a_full_econ,
    "Cultural" = results_align$model5a_full_cult,
    "Other" = results_align$model5a_full_oth
  ),
  vcov = vcov_t3d,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S14: H3a Alignment by Topic — FE, Full Data (Day Running Variable)",
  add_rows = rows_t3d,
  notes = str_wrap(note_t3d, 80)
)

table_3d

save_table(table_3d, "table_s14_fe_topic_full_days")
```

## Table 3E: Heterogeneity By Topic Full Data (Continuous)

```{r table3e}
n_cl_t3e <- sapply(list(results_align_cont$model5a_full_pol, results_align_cont$model5a_full_mil,
                        results_align_cont$model5a_full_econ, results_align_cont$model5a_full_cult,
                        results_align_cont$model5a_full_oth), get_n_clusters)
rows_t3e <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t3e[1], n_cl_t3e[2], n_cl_t3e[3], n_cl_t3e[4], n_cl_t3e[5]
)
attr(rows_t3e, 'position') <- c(5, 6, 7, 8)

note_t3e <- paste("Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights), clustered at source level. Each model uses the full dataset (no bandwidth restriction). State media in non-NATO countries only.", SE_NOTE)

# Create vcov list with bootstrap SEs for topic models
vcov_t3e <- list(
  "Political" = create_bootstrap_vcov(results_align_cont$model5a_full_pol, results_align_cont$bootstrap_se$model5a_full_pol, "treatment:csto"),
  "Military" = create_bootstrap_vcov(results_align_cont$model5a_full_mil, results_align_cont$bootstrap_se$model5a_full_mil, "treatment:csto"),
  "Economic" = create_bootstrap_vcov(results_align_cont$model5a_full_econ, results_align_cont$bootstrap_se$model5a_full_econ, "treatment:csto"),
  "Cultural" = create_bootstrap_vcov(results_align_cont$model5a_full_cult, results_align_cont$bootstrap_se$model5a_full_cult, "treatment:csto"),
  "Other" = create_bootstrap_vcov(results_align_cont$model5a_full_oth, results_align_cont$bootstrap_se$model5a_full_oth, "treatment:csto")
)

table_3e <- modelsummary(
  list(
    "Political" = results_align_cont$model5a_full_pol,
    "Military" = results_align_cont$model5a_full_mil,
    "Economic" = results_align_cont$model5a_full_econ,
    "Cultural" = results_align_cont$model5a_full_cult,
    "Other" = results_align_cont$model5a_full_oth
  ),
  vcov = vcov_t3e,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S14 (Cont): H3a Alignment by Topic — FE, Full Data (Continuous Running Variable)",
  add_rows = rows_t3e,
  notes = str_wrap(note_t3e, 80)
)

table_3e

save_table(table_3e, "table_s14_fe_topic_full_cont")
```

# Table 4: Heterogeneity by Ethnic Russian Population

```{r table-s04-fe-days}
n_cl_t4 <- sapply(list(results_ethnic$model6a_full, results_ethnic$model6a_opt,
                       results_ethnic$model6a_opt_non_mil, results_ethnic$model6a_opt_russian),
                  get_n_clusters)
rows_t4 <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4,
  'State FEs', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-',
  'Topic FEs', 'X', 'X', 'X', 'X',
  'Clusters', n_cl_t4[1], n_cl_t4[2], n_cl_t4[3], n_cl_t4[4]
)
attr(rows_t4, 'position') <- c(5, 6, 7, 8)

note_t4 <- paste("Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights), clustered at source level. Model 1 uses full data with topic fixed effects. Model 2 uses the optimal bandwidth with topic fixed effects. Model 3 omits military-related articles and uses a re-optimized bandwidth. Model 4 uses only Russian-related (non-military) articles with a re-optimized bandwidth. Sample restricted to state-owned media in non-NATO countries.", SE_NOTE)

# Create vcov list with bootstrap SEs for all models
vcov_t4 <- list(
  "(1)" = create_bootstrap_vcov(results_ethnic$model6a_full, results_ethnic$bootstrap_se$model6a_full, "treatment:high_russia"),
  "(2)" = create_bootstrap_vcov(results_ethnic$model6a_opt, results_ethnic$bootstrap_se$model6a_opt, "treatment:high_russia"),
  "(3)" = create_bootstrap_vcov(results_ethnic$model6a_opt_non_mil, results_ethnic$bootstrap_se$model6a_opt_non_mil, "treatment:high_russia"),
  "(4)" = create_bootstrap_vcov(results_ethnic$model6a_opt_russian, results_ethnic$bootstrap_se$model6a_opt_russian, "treatment:high_russia")
)

table_4 <- modelsummary(
  list(
    "(1)" = results_ethnic$model6a_full,
    "(2)" = results_ethnic$model6a_opt,
    "(3)" = results_ethnic$model6a_opt_non_mil,
    "(4)" = results_ethnic$model6a_opt_russian
  ),
  vcov = vcov_t4,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S4: H3b Ethnic — Fixed Effects (Day Running Variable)",
  add_rows = rows_t4,
  notes = str_wrap(note_t4, 80)
)

table_4

save_table(table_4, "table_s04_fe_days")
```

## Table 4A: Ethnic Heterogeneity (Continuous)

```{r table4a}
n_cl_t4a <- sapply(list(results_ethnic_cont$model6a_full, results_ethnic_cont$model6a_opt,
                        results_ethnic_cont$model6a_opt_non_mil, results_ethnic_cont$model6a_opt_russian),
                   get_n_clusters)
rows_t4a <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4,
  'State FEs', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-',
  'Topic FEs', 'X', 'X', 'X', 'X',
  'Clusters', n_cl_t4a[1], n_cl_t4a[2], n_cl_t4a[3], n_cl_t4a[4]
)
attr(rows_t4a, 'position') <- c(5, 6, 7, 8)

note_t4a <- paste("Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights), clustered at source level. Model 1 uses full data with topic fixed effects. Model 2 uses the optimal bandwidth with topic fixed effects. Model 3 omits military-related articles and uses a re-optimized bandwidth. Model 4 uses only Russian-related (non-military) articles with a re-optimized bandwidth. Sample restricted to state-owned media in non-NATO countries.", SE_NOTE)

# Create vcov list with bootstrap SEs
vcov_t4a <- list(
  "(1)" = create_bootstrap_vcov(results_ethnic_cont$model6a_full, results_ethnic_cont$bootstrap_se$model6a_full, "treatment:high_russia"),
  "(2)" = create_bootstrap_vcov(results_ethnic_cont$model6a_opt, results_ethnic_cont$bootstrap_se$model6a_opt, "treatment:high_russia"),
  "(3)" = create_bootstrap_vcov(results_ethnic_cont$model6a_opt_non_mil, results_ethnic_cont$bootstrap_se$model6a_opt_non_mil, "treatment:high_russia"),
  "(4)" = create_bootstrap_vcov(results_ethnic_cont$model6a_opt_russian, results_ethnic_cont$bootstrap_se$model6a_opt_russian, "treatment:high_russia")
)

table_4a <- modelsummary(
  list(
    "(1)" = results_ethnic_cont$model6a_full,
    "(2)" = results_ethnic_cont$model6a_opt,
    "(3)" = results_ethnic_cont$model6a_opt_non_mil,
    "(4)" = results_ethnic_cont$model6a_opt_russian
  ),
  vcov = vcov_t4a,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S4 (Cont): H3b Ethnic — Fixed Effects (Continuous Running Variable)",
  add_rows = rows_t4a,
  notes = str_wrap(note_t4a, 80)
)

table_4a

save_table(table_4a, "table_s04_fe_cont")
```

## Table 4B: Ethnic By Topic Optimal BW (Day)

```{r table4b}
n_cl_t4b <- sapply(list(results_ethnic$model6a_opt_pol, results_ethnic$model6a_opt_mil,
                        results_ethnic$model6a_opt_econ, results_ethnic$model6a_opt_cult,
                        results_ethnic$model6a_opt_oth), get_n_clusters)
rows_t4b <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t4b[1], n_cl_t4b[2], n_cl_t4b[3], n_cl_t4b[4], n_cl_t4b[5]
)
attr(rows_t4b, 'position') <- c(5, 6, 7, 8)

note_t4b <- paste("Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights), clustered at source level. Each model uses a per-topic re-optimized bandwidth. State media in non-NATO countries only.", SE_NOTE)

# Create vcov list with bootstrap SEs for topic models
vcov_t4b <- list(
  "Political" = create_bootstrap_vcov(results_ethnic$model6a_opt_pol, results_ethnic$bootstrap_se$model6a_opt_pol, "treatment:high_russia"),
  "Military" = create_bootstrap_vcov(results_ethnic$model6a_opt_mil, results_ethnic$bootstrap_se$model6a_opt_mil, "treatment:high_russia"),
  "Economic" = create_bootstrap_vcov(results_ethnic$model6a_opt_econ, results_ethnic$bootstrap_se$model6a_opt_econ, "treatment:high_russia"),
  "Cultural" = create_bootstrap_vcov(results_ethnic$model6a_opt_cult, results_ethnic$bootstrap_se$model6a_opt_cult, "treatment:high_russia"),
  "Other" = create_bootstrap_vcov(results_ethnic$model6a_opt_oth, results_ethnic$bootstrap_se$model6a_opt_oth, "treatment:high_russia")
)

table_4b <- modelsummary(
  list(
    "Political" = results_ethnic$model6a_opt_pol,
    "Military" = results_ethnic$model6a_opt_mil,
    "Economic" = results_ethnic$model6a_opt_econ,
    "Cultural" = results_ethnic$model6a_opt_cult,
    "Other" = results_ethnic$model6a_opt_oth
  ),
  vcov = vcov_t4b,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S12: H3b Ethnic by Topic — FE, Optimal BW (Day Running Variable)",
  add_rows = rows_t4b,
  notes = str_wrap(note_t4b, 80)
)

table_4b

save_table(table_4b, "table_s12_fe_topic_opt_days")
```

## Table 4C: Ethnic By Topic Optimal BW (Continuous)

```{r table4c}
n_cl_t4c <- sapply(list(results_ethnic_cont$model6a_opt_pol, results_ethnic_cont$model6a_opt_mil,
                        results_ethnic_cont$model6a_opt_econ, results_ethnic_cont$model6a_opt_cult,
                        results_ethnic_cont$model6a_opt_oth), get_n_clusters)
rows_t4c <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t4c[1], n_cl_t4c[2], n_cl_t4c[3], n_cl_t4c[4], n_cl_t4c[5]
)
attr(rows_t4c, 'position') <- c(5, 6, 7, 8)

note_t4c <- paste("Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights), clustered at source level. Each model uses a per-topic re-optimized bandwidth. State media in non-NATO countries only.", SE_NOTE)

# Create vcov list with bootstrap SEs for topic models
vcov_t4c <- list(
  "Political" = create_bootstrap_vcov(results_ethnic_cont$model6a_opt_pol, results_ethnic_cont$bootstrap_se$model6a_opt_pol, "treatment:high_russia"),
  "Military" = create_bootstrap_vcov(results_ethnic_cont$model6a_opt_mil, results_ethnic_cont$bootstrap_se$model6a_opt_mil, "treatment:high_russia"),
  "Economic" = create_bootstrap_vcov(results_ethnic_cont$model6a_opt_econ, results_ethnic_cont$bootstrap_se$model6a_opt_econ, "treatment:high_russia"),
  "Cultural" = create_bootstrap_vcov(results_ethnic_cont$model6a_opt_cult, results_ethnic_cont$bootstrap_se$model6a_opt_cult, "treatment:high_russia"),
  "Other" = create_bootstrap_vcov(results_ethnic_cont$model6a_opt_oth, results_ethnic_cont$bootstrap_se$model6a_opt_oth, "treatment:high_russia")
)

table_4c <- modelsummary(
  list(
    "Political" = results_ethnic_cont$model6a_opt_pol,
    "Military" = results_ethnic_cont$model6a_opt_mil,
    "Economic" = results_ethnic_cont$model6a_opt_econ,
    "Cultural" = results_ethnic_cont$model6a_opt_cult,
    "Other" = results_ethnic_cont$model6a_opt_oth
  ),
  vcov = vcov_t4c,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S12 (Cont): H3b Ethnic by Topic — FE, Optimal BW (Continuous Running Variable)",
  add_rows = rows_t4c,
  notes = str_wrap(note_t4c, 80)
)

table_4c

save_table(table_4c, "table_s12_fe_topic_opt_cont")
```

## Table 4D: Ethnic By Topic Full Data (Day)

```{r table4d}
n_cl_t4d <- sapply(list(results_ethnic$model6a_full_pol, results_ethnic$model6a_full_mil,
                        results_ethnic$model6a_full_econ, results_ethnic$model6a_full_cult,
                        results_ethnic$model6a_full_oth), get_n_clusters)
rows_t4d <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t4d[1], n_cl_t4d[2], n_cl_t4d[3], n_cl_t4d[4], n_cl_t4d[5]
)
attr(rows_t4d, 'position') <- c(5, 6, 7, 8)

note_t4d <- paste("Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights), clustered at source level. Each model uses the full dataset (no bandwidth restriction). State media in non-NATO countries only.", SE_NOTE)

# Create vcov list with bootstrap SEs for topic models
vcov_t4d <- list(
  "Political" = create_bootstrap_vcov(results_ethnic$model6a_full_pol, results_ethnic$bootstrap_se$model6a_full_pol, "treatment:high_russia"),
  "Military" = create_bootstrap_vcov(results_ethnic$model6a_full_mil, results_ethnic$bootstrap_se$model6a_full_mil, "treatment:high_russia"),
  "Economic" = create_bootstrap_vcov(results_ethnic$model6a_full_econ, results_ethnic$bootstrap_se$model6a_full_econ, "treatment:high_russia"),
  "Cultural" = create_bootstrap_vcov(results_ethnic$model6a_full_cult, results_ethnic$bootstrap_se$model6a_full_cult, "treatment:high_russia"),
  "Other" = create_bootstrap_vcov(results_ethnic$model6a_full_oth, results_ethnic$bootstrap_se$model6a_full_oth, "treatment:high_russia")
)

table_4d <- modelsummary(
  list(
    "Political" = results_ethnic$model6a_full_pol,
    "Military" = results_ethnic$model6a_full_mil,
    "Economic" = results_ethnic$model6a_full_econ,
    "Cultural" = results_ethnic$model6a_full_cult,
    "Other" = results_ethnic$model6a_full_oth
  ),
  vcov = vcov_t4d,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S15: H3b Ethnic by Topic — FE, Full Data (Day Running Variable)",
  add_rows = rows_t4d,
  notes = str_wrap(note_t4d, 80)
)

table_4d

save_table(table_4d, "table_s15_fe_topic_full_days")
```

## Table 4E: Ethnic By Topic Full Data (Continuous)

```{r table4e}
n_cl_t4e <- sapply(list(results_ethnic_cont$model6a_full_pol, results_ethnic_cont$model6a_full_mil,
                        results_ethnic_cont$model6a_full_econ, results_ethnic_cont$model6a_full_cult,
                        results_ethnic_cont$model6a_full_oth), get_n_clusters)
rows_t4e <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t4e[1], n_cl_t4e[2], n_cl_t4e[3], n_cl_t4e[4], n_cl_t4e[5]
)
attr(rows_t4e, 'position') <- c(5, 6, 7, 8)

note_t4e <- paste("Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights), clustered at source level. Each model uses the full dataset (no bandwidth restriction). State media in non-NATO countries only.", SE_NOTE)

# Create vcov list with bootstrap SEs for topic models
vcov_t4e <- list(
  "Political" = create_bootstrap_vcov(results_ethnic_cont$model6a_full_pol, results_ethnic_cont$bootstrap_se$model6a_full_pol, "treatment:high_russia"),
  "Military" = create_bootstrap_vcov(results_ethnic_cont$model6a_full_mil, results_ethnic_cont$bootstrap_se$model6a_full_mil, "treatment:high_russia"),
  "Economic" = create_bootstrap_vcov(results_ethnic_cont$model6a_full_econ, results_ethnic_cont$bootstrap_se$model6a_full_econ, "treatment:high_russia"),
  "Cultural" = create_bootstrap_vcov(results_ethnic_cont$model6a_full_cult, results_ethnic_cont$bootstrap_se$model6a_full_cult, "treatment:high_russia"),
  "Other" = create_bootstrap_vcov(results_ethnic_cont$model6a_full_oth, results_ethnic_cont$bootstrap_se$model6a_full_oth, "treatment:high_russia")
)

table_4e <- modelsummary(
  list(
    "Political" = results_ethnic_cont$model6a_full_pol,
    "Military" = results_ethnic_cont$model6a_full_mil,
    "Economic" = results_ethnic_cont$model6a_full_econ,
    "Cultural" = results_ethnic_cont$model6a_full_cult,
    "Other" = results_ethnic_cont$model6a_full_oth
  ),
  vcov = vcov_t4e,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S15 (Cont): H3b Ethnic by Topic — FE, Full Data (Continuous Running Variable)",
  add_rows = rows_t4e,
  notes = str_wrap(note_t4e, 80)
)

table_4e

save_table(table_4e, "table_s15_fe_topic_full_cont")
```

### Table S1 (Drop): H1 FE Main Results — Drop No-Time Articles

```{r table-s01-fe-drop}
n_cl_t1d <- sapply(list(results_h1_drop$model1_opt, results_h1_drop$model2_opt,
                        results_h1_drop$model3_opt, results_h1_drop$model4_opt,
                        results_h1_drop$model1_full_linear, results_h1_drop$model4_non_mil,
                        results_h1_drop$model4_non_nato, results_h1_drop$model4_felm_saturated),
                   get_n_clusters)
rows_t1d <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7, ~row8,
  'State FEs', '-', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', 'X', 'X', 'X', 'X', 'X', 'X',
  'Topic FEs', '-', '-', '-', 'X', 'X', 'X', 'X', 'X',
  'Clusters', n_cl_t1d[1], n_cl_t1d[2], n_cl_t1d[3], n_cl_t1d[4], n_cl_t1d[5], n_cl_t1d[6], n_cl_t1d[7], n_cl_t1d[8]
)
attr(rows_t1d, 'position') <- c(3, 4, 5, 6)

note_t1d <- paste("All standard errors are clustered at the source level. Articles without publication times are dropped. Models 1-4 uses the optimal bandwidth. Model 5 uses a linear specification with the full set of articles. Model 6 omits Military Topics. Model 7 omits NATO allies. Model 8 uses full saturation (country-source-topic FEs).", SE_NOTE)

table_1d <- modelsummary(
  list(
    "(1)" = results_h1_drop$model1_opt,
    "(2)" = results_h1_drop$model2_opt,
    "(3)" = results_h1_drop$model3_opt,
    "(4)" = results_h1_drop$model4_opt,
    "(5)" = results_h1_drop$model1_full_linear,
    "(6)" = results_h1_drop$model4_non_mil,
    "(7)" = results_h1_drop$model4_non_nato,
    "(8)" = results_h1_drop$model4_felm_saturated
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c("treatment" = "Invasion", "post" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S1 (Drop): H1 RDD — Fixed Effects (Drop No-Time Articles)",
  add_rows = rows_t1d,
  notes = str_wrap(note_t1d, 80)
)

table_1d

save_table(table_1d, "table_s01_fe_drop")
```

## Table 1E: RDD By Topic (Drop No-Time)

```{r table1e}
n_cl_t1e <- sapply(list(results_h1_drop$model4_opt_pol, results_h1_drop$model4_opt_mil,
                        results_h1_drop$model4_opt_econ, results_h1_drop$model4_opt_cult,
                        results_h1_drop$model4_opt_oth), get_n_clusters)
rows_t1e <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', 'X', 'X', 'X', 'X', 'X',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t1e[1], n_cl_t1e[2], n_cl_t1e[3], n_cl_t1e[4], n_cl_t1e[5]
)
attr(rows_t1e, 'position') <- c(3, 4, 5, 6)

note_t1e <- paste("All standard errors are clustered at the source level. Articles without publication times are dropped. All models use the optimal bandwidth with country and source fixed effects.", SE_NOTE)

table_1e <- modelsummary(
  list(
    "Political" = results_h1_drop$model4_opt_pol,
    "Military" = results_h1_drop$model4_opt_mil,
    "Economic" = results_h1_drop$model4_opt_econ,
    "Cultural" = results_h1_drop$model4_opt_cult,
    "Other" = results_h1_drop$model4_opt_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c("treatment" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S9 (Drop): H1 RDD by Topic — FE, Optimal BW (Drop No-Time Articles)",
  add_rows = rows_t1e,
  notes = str_wrap(note_t1e, 80)
)

table_1e

save_table(table_1e, "table_s09_fe_topic_opt_drop")
```

### Table S5 (Drop): H1 By-Topic Z-Score — Drop No-Time Articles

```{r table-s05-z-topic-drop}
models_1ez <- list(
  "Political" = results_h1_drop$model5_opt_pol,
  "Military" = results_h1_drop$model5_opt_mil,
  "Economic" = results_h1_drop$model5_opt_econ,
  "Cultural" = results_h1_drop$model5_opt_cult,
  "Other" = results_h1_drop$model5_opt_oth
)
tbl_1ez <- modelsummary(
  models_1ez,
  output = "gt",
  coef_map = c("treatment" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  stars = c('*' = .05, '**' = .01, '***' = .001),
  fmt = 3,
  title = "Table S5 (Drop): H1 RDD by Topic — Z-Score (Drop No-Time Articles)"
)
tbl_1ez
save_table(tbl_1ez, "table_s05_z_topic_drop")
```

## Table 2F: Diff-in-Disc Main (Drop No-Time)

```{r table2f}
n_cl_t2f <- sapply(list(results_h2_drop$model2a, results_h2_drop$model2a_full,
                        results_h2_drop$model2a_opt, results_h2_drop$model2a_opt_full_fe,
                        results_h2_drop$model2b, results_h2_drop$model2d,
                        results_h2_drop$model3a_opt, results_h2_drop$model3a_opt_saturated),
                   get_n_clusters)
rows_t2f <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7, ~row8,
  'State FEs', 'X', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', 'X', '-', 'X', '-', '-', '-', 'X',
  'Topic FEs', 'X', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Clusters', n_cl_t2f[1], n_cl_t2f[2], n_cl_t2f[3], n_cl_t2f[4], n_cl_t2f[5], n_cl_t2f[6], n_cl_t2f[7], n_cl_t2f[8]
)
attr(rows_t2f, 'position') <- c(5, 6, 7, 8)

note_t2f <- paste("All standard errors are clustered at the source level. Articles without publication times are dropped. Model 1 uses full data with topic FEs. Model 2 adds source FEs. Model 3 uses optimal bandwidth with topic FEs. Model 4 uses optimal bandwidth with full FEs. Model 5 omits military-related articles. Model 6 omits NATO allies. Model 7 combines Russian-related + combined bandwidth filters. Model 8 uses saturated FEs.", SE_NOTE)

table_2f <- modelsummary(
  list(
    "(1)" = results_h2_drop$model2a,
    "(2)" = results_h2_drop$model2a_full,
    "(3)" = results_h2_drop$model2a_opt,
    "(4)" = results_h2_drop$model2a_opt_full_fe,
    "(5)" = results_h2_drop$model2b,
    "(6)" = results_h2_drop$model2d,
    "(7)" = results_h2_drop$model3a_opt,
    "(8)" = results_h2_drop$model3a_opt_saturated
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S2 (Drop): H2 Diff-in-Disc — Fixed Effects (Drop No-Time Articles)",
  add_rows = rows_t2f,
  notes = str_wrap(note_t2f, 80)
)

table_2f

save_table(table_2f, "table_s02_fe_drop")
```

## Table 2F-S: H2 Diff-in-Disc (Drop No-Time) — Full FE Robustness

```{r table2fs}
n_cl_t2fs <- sapply(list(results_h2_drop$model2b_full_fe, results_h2_drop$model3a_opt_full_fe),
                    get_n_clusters)
rows_t2fs <- tibble::tribble(
  ~term, ~row1, ~row2,
  'State FEs', 'X', 'X',
  'Source FEs', 'X', 'X',
  'Topic FEs', 'X', 'X',
  'Clusters', n_cl_t2fs[1], n_cl_t2fs[2]
)
attr(rows_t2fs, 'position') <- c(5, 6, 7, 8)

note_t2fs <- paste("All standard errors are clustered at the source level. Articles without publication times are dropped. Both models include full FEs (topic + source). Model 1 uses non-military subset. Model 2 uses Russian-related + combined bandwidth filters.", SE_NOTE)

table_2fs <- modelsummary(
  list(
    "(1) Non-Mil, Full FEs" = results_h2_drop$model2b_full_fe,
    "(2) Russian Opt, Full FEs" = results_h2_drop$model3a_opt_full_fe
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S16 (Drop): H2 Diff-in-Disc — Full FE Robustness (Drop No-Time Articles)",
  add_rows = rows_t2fs,
  notes = str_wrap(note_t2fs, 80)
)

table_2fs

save_table(table_2fs, "table_s16_full_fe_robustness_drop")
```

## Table 2G: Diff-in-Disc By Topic Optimal BW (Drop No-Time)

```{r table2g}
n_cl_t2g <- sapply(list(results_h2_drop$model2a_opt_pol, results_h2_drop$model2a_opt_mil,
                        results_h2_drop$model2a_opt_econ, results_h2_drop$model2a_opt_cult,
                        results_h2_drop$model2a_opt_oth), get_n_clusters)
rows_t2g <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t2g[1], n_cl_t2g[2], n_cl_t2g[3], n_cl_t2g[4], n_cl_t2g[5]
)
attr(rows_t2g, 'position') <- c(5, 6, 7, 8)

note_t2g <- paste("All standard errors are clustered at the source level. Articles without publication times are dropped. All models use a per-topic re-optimized bandwidth with country fixed effects only.", SE_NOTE)

table_2g <- modelsummary(
  list(
    "Political" = results_h2_drop$model2a_opt_pol,
    "Military" = results_h2_drop$model2a_opt_mil,
    "Economic" = results_h2_drop$model2a_opt_econ,
    "Cultural" = results_h2_drop$model2a_opt_cult,
    "Other" = results_h2_drop$model2a_opt_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S10 (Drop): H2 Diff-in-Disc by Topic — FE, Optimal BW (Drop No-Time Articles)",
  add_rows = rows_t2g,
  notes = str_wrap(note_t2g, 80)
)

table_2g

save_table(table_2g, "table_s10_fe_topic_opt_drop")
```

## Table 2H: Diff-in-Disc By Topic Full Data (Drop No-Time)

```{r table2h}
n_cl_t2h <- sapply(list(results_h2_drop$model2a_full_pol, results_h2_drop$model2a_full_mil,
                        results_h2_drop$model2a_full_econ, results_h2_drop$model2a_full_cult,
                        results_h2_drop$model2a_full_oth), get_n_clusters)
rows_t2h <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t2h[1], n_cl_t2h[2], n_cl_t2h[3], n_cl_t2h[4], n_cl_t2h[5]
)
attr(rows_t2h, 'position') <- c(5, 6, 7, 8)

note_t2h <- paste("All standard errors are clustered at the source level. Articles without publication times are dropped. All models use the full dataset (no bandwidth restriction) with country fixed effects only.", SE_NOTE)

table_2h <- modelsummary(
  list(
    "Political" = results_h2_drop$model2a_full_pol,
    "Military" = results_h2_drop$model2a_full_mil,
    "Economic" = results_h2_drop$model2a_full_econ,
    "Cultural" = results_h2_drop$model2a_full_cult,
    "Other" = results_h2_drop$model2a_full_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S13 (Drop): H2 Diff-in-Disc by Topic — FE, Full Data (Drop No-Time Articles)",
  add_rows = rows_t2h,
  notes = str_wrap(note_t2h, 80)
)

table_2h

save_table(table_2h, "table_s13_fe_topic_full_drop")
```

## Table 3F: Alignment Main (Drop No-Time)

```{r table3f}
n_cl_t3f <- sapply(list(results_align_drop$model5a_csto, results_align_drop$model5a_neutral,
                        results_align_drop$model5a_full, results_align_drop$model5a_opt,
                        results_align_drop$model5a_opt_non_mil, results_align_drop$model5a_opt_russian,
                        results_align_drop$model5a_opt_full_fe, results_align_drop$model5a_opt_non_mil_full_fe,
                        results_align_drop$model5a_fully_saturated, results_align_drop$matched_model),
                   get_n_clusters)
rows_t3f <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7, ~row8, ~row9, ~row10,
  'State FEs', '-', '-', 'X', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-', '-', 'X', 'X', 'X', 'X',
  'Topic FEs', '-', '-', 'X', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Matched', '-', '-', '-', '-', '-', '-', '-', '-', '-', 'X',
  'Clusters', n_cl_t3f[1], n_cl_t3f[2], n_cl_t3f[3], n_cl_t3f[4], n_cl_t3f[5], n_cl_t3f[6], n_cl_t3f[7], n_cl_t3f[8], n_cl_t3f[9], n_cl_t3f[10]
)
attr(rows_t3f, 'position') <- c(5, 6, 7, 8, 9)

note_t3f <- paste("Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights) for Models 3-10, clustered at source level. Models 1-2 use rdrobust standard errors. Articles without publication times are dropped. Model 1 shows RDD results for CSTO countries only. Model 2 shows RDD results for Neutral countries only. Model 3 uses full data with topic fixed effects. Model 4 uses the optimal bandwidth with topic fixed effects. Model 5 omits military-related articles and uses a re-optimized bandwidth. Model 6 uses only Russian-related (non-military) articles with a re-optimized bandwidth. Model 7 uses optimal bandwidth with full FEs (topic + source + state FEs). Model 8 uses non-military subset with full FEs. Model 9 uses full saturation (source-topic and topic-treatment FEs). Model 10 uses exact matching on publication day and topic. Sample restricted to state-owned media in non-NATO countries.", SE_NOTE)

# Create vcov list with bootstrap SEs for felm models
vcov_t3f <- list(
  NULL,
  NULL,
  "(3)" = create_bootstrap_vcov(results_align_drop$model5a_full, results_align_drop$bootstrap_se$model5a_full, "treatment:csto"),
  "(4)" = create_bootstrap_vcov(results_align_drop$model5a_opt, results_align_drop$bootstrap_se$model5a_opt, "treatment:csto"),
  "(5)" = create_bootstrap_vcov(results_align_drop$model5a_opt_non_mil, results_align_drop$bootstrap_se$model5a_opt_non_mil, "treatment:csto"),
  "(6)" = create_bootstrap_vcov(results_align_drop$model5a_opt_russian, results_align_drop$bootstrap_se$model5a_opt_russian, "treatment:csto"),
  "(7)" = create_bootstrap_vcov(results_align_drop$model5a_opt_full_fe, results_align_drop$bootstrap_se$model5a_opt_full_fe, "treatment:csto"),
  "(8)" = create_bootstrap_vcov(results_align_drop$model5a_opt_non_mil_full_fe, results_align_drop$bootstrap_se$model5a_opt_non_mil_full_fe, "treatment:csto"),
  "(9)" = create_bootstrap_vcov(results_align_drop$model5a_fully_saturated, results_align_drop$bootstrap_se$model5a_fully_saturated, "treatment:csto"),
  "(10)" = create_bootstrap_vcov(results_align_drop$matched_model, results_align_drop$bootstrap_se$matched_model, "treatment:csto")
)

table_3f <- modelsummary(
  list(
    "(1)" = results_align_drop$model5a_csto,
    "(2)" = results_align_drop$model5a_neutral,
    "(3)" = results_align_drop$model5a_full,
    "(4)" = results_align_drop$model5a_opt,
    "(5)" = results_align_drop$model5a_opt_non_mil,
    "(6)" = results_align_drop$model5a_opt_russian,
    "(7)" = results_align_drop$model5a_opt_full_fe,
    "(8)" = results_align_drop$model5a_opt_non_mil_full_fe,
    "(9)" = results_align_drop$model5a_fully_saturated,
    "(10)" = results_align_drop$matched_model
  ),
  vcov = vcov_t3f,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S3 (Drop): H3a Alignment — Fixed Effects (Drop No-Time Articles)",
  add_rows = rows_t3f,
  notes = str_wrap(note_t3f, 80)
)

table_3f

save_table(table_3f, "table_s03_fe_drop")
```

## Table 3G: Alignment By Topic Optimal BW (Drop No-Time)

```{r table3g}
n_cl_t3g <- sapply(list(results_align_drop$model5a_opt_pol, results_align_drop$model5a_opt_mil,
                        results_align_drop$model5a_opt_econ, results_align_drop$model5a_opt_cult,
                        results_align_drop$model5a_opt_oth), get_n_clusters)
rows_t3g <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t3g[1], n_cl_t3g[2], n_cl_t3g[3], n_cl_t3g[4], n_cl_t3g[5]
)
attr(rows_t3g, 'position') <- c(5, 6, 7, 8)

note_t3g <- paste("All standard errors are clustered at the source level. Articles without publication times are dropped. Each model uses a per-topic re-optimized bandwidth. State media in non-NATO countries only.", SE_NOTE)

table_3g <- modelsummary(
  list(
    "Political" = results_align_drop$model5a_opt_pol,
    "Military" = results_align_drop$model5a_opt_mil,
    "Economic" = results_align_drop$model5a_opt_econ,
    "Cultural" = results_align_drop$model5a_opt_cult,
    "Other" = results_align_drop$model5a_opt_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S11 (Drop): H3a Alignment by Topic — FE, Optimal BW (Drop No-Time Articles)",
  add_rows = rows_t3g,
  notes = str_wrap(note_t3g, 80)
)

table_3g

save_table(table_3g, "table_s11_fe_topic_opt_drop")
```

## Table 3H: Alignment By Topic Full Data (Drop No-Time)

```{r table3h}
n_cl_t3h <- sapply(list(results_align_drop$model5a_full_pol, results_align_drop$model5a_full_mil,
                        results_align_drop$model5a_full_econ, results_align_drop$model5a_full_cult,
                        results_align_drop$model5a_full_oth), get_n_clusters)
rows_t3h <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t3h[1], n_cl_t3h[2], n_cl_t3h[3], n_cl_t3h[4], n_cl_t3h[5]
)
attr(rows_t3h, 'position') <- c(5, 6, 7, 8)

note_t3h <- paste("All standard errors are clustered at the source level. Articles without publication times are dropped. Each model uses the full dataset (no bandwidth restriction). State media in non-NATO countries only.", SE_NOTE)

table_3h <- modelsummary(
  list(
    "Political" = results_align_drop$model5a_full_pol,
    "Military" = results_align_drop$model5a_full_mil,
    "Economic" = results_align_drop$model5a_full_econ,
    "Cultural" = results_align_drop$model5a_full_cult,
    "Other" = results_align_drop$model5a_full_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S14 (Drop): H3a Alignment by Topic — FE, Full Data (Drop No-Time Articles)",
  add_rows = rows_t3h,
  notes = str_wrap(note_t3h, 80)
)

table_3h

save_table(table_3h, "table_s14_fe_topic_full_drop")
```

## Table 4F: Ethnic Main (Drop No-Time)

```{r table4f}
n_cl_t4f <- sapply(list(results_ethnic_drop$model6a_full, results_ethnic_drop$model6a_opt,
                        results_ethnic_drop$model6a_opt_non_mil, results_ethnic_drop$model6a_opt_russian),
                   get_n_clusters)
rows_t4f <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4,
  'State FEs', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-',
  'Topic FEs', 'X', 'X', 'X', 'X',
  'Clusters', n_cl_t4f[1], n_cl_t4f[2], n_cl_t4f[3], n_cl_t4f[4]
)
attr(rows_t4f, 'position') <- c(5, 6, 7, 8)

note_t4f <- paste("Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights), clustered at source level. Articles without publication times are dropped. Model 1 uses full data with topic fixed effects. Model 2 uses the optimal bandwidth with topic fixed effects. Model 3 omits military-related articles and uses a re-optimized bandwidth. Model 4 uses only Russian-related (non-military) articles with a re-optimized bandwidth. Sample restricted to state-owned media in non-NATO countries.", SE_NOTE)

# Create vcov list with bootstrap SEs
vcov_t4f <- list(
  "(1)" = create_bootstrap_vcov(results_ethnic_drop$model6a_full, results_ethnic_drop$bootstrap_se$model6a_full, "treatment:high_russia"),
  "(2)" = create_bootstrap_vcov(results_ethnic_drop$model6a_opt, results_ethnic_drop$bootstrap_se$model6a_opt, "treatment:high_russia"),
  "(3)" = create_bootstrap_vcov(results_ethnic_drop$model6a_opt_non_mil, results_ethnic_drop$bootstrap_se$model6a_opt_non_mil, "treatment:high_russia"),
  "(4)" = create_bootstrap_vcov(results_ethnic_drop$model6a_opt_russian, results_ethnic_drop$bootstrap_se$model6a_opt_russian, "treatment:high_russia")
)

table_4f <- modelsummary(
  list(
    "(1)" = results_ethnic_drop$model6a_full,
    "(2)" = results_ethnic_drop$model6a_opt,
    "(3)" = results_ethnic_drop$model6a_opt_non_mil,
    "(4)" = results_ethnic_drop$model6a_opt_russian
  ),
  vcov = vcov_t4f,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S4 (Drop): H3b Ethnic — Fixed Effects (Drop No-Time Articles)",
  add_rows = rows_t4f,
  notes = str_wrap(note_t4f, 80)
)

table_4f

save_table(table_4f, "table_s04_fe_drop")
```

## Table 4G: Ethnic By Topic Optimal BW (Drop No-Time)

```{r table4g}
n_cl_t4g <- sapply(list(results_ethnic_drop$model6a_opt_pol, results_ethnic_drop$model6a_opt_mil,
                        results_ethnic_drop$model6a_opt_econ, results_ethnic_drop$model6a_opt_cult,
                        results_ethnic_drop$model6a_opt_oth), get_n_clusters)
rows_t4g <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t4g[1], n_cl_t4g[2], n_cl_t4g[3], n_cl_t4g[4], n_cl_t4g[5]
)
attr(rows_t4g, 'position') <- c(5, 6, 7, 8)

note_t4g <- paste("All standard errors are clustered at the source level. Articles without publication times are dropped. Each model uses a per-topic re-optimized bandwidth. State media in non-NATO countries only.", SE_NOTE)

table_4g <- modelsummary(
  list(
    "Political" = results_ethnic_drop$model6a_opt_pol,
    "Military" = results_ethnic_drop$model6a_opt_mil,
    "Economic" = results_ethnic_drop$model6a_opt_econ,
    "Cultural" = results_ethnic_drop$model6a_opt_cult,
    "Other" = results_ethnic_drop$model6a_opt_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S12 (Drop): H3b Ethnic by Topic — FE, Optimal BW (Drop No-Time Articles)",
  add_rows = rows_t4g,
  notes = str_wrap(note_t4g, 80)
)

table_4g

save_table(table_4g, "table_s12_fe_topic_opt_drop")
```

## Table 4H: Ethnic By Topic Full Data (Drop No-Time)

```{r table4h}
n_cl_t4h <- sapply(list(results_ethnic_drop$model6a_full_pol, results_ethnic_drop$model6a_full_mil,
                        results_ethnic_drop$model6a_full_econ, results_ethnic_drop$model6a_full_cult,
                        results_ethnic_drop$model6a_full_oth), get_n_clusters)
rows_t4h <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t4h[1], n_cl_t4h[2], n_cl_t4h[3], n_cl_t4h[4], n_cl_t4h[5]
)
attr(rows_t4h, 'position') <- c(5, 6, 7, 8)

note_t4h <- paste("All standard errors are clustered at the source level. Articles without publication times are dropped. Each model uses the full dataset (no bandwidth restriction). State media in non-NATO countries only.", SE_NOTE)

table_4h <- modelsummary(
  list(
    "Political" = results_ethnic_drop$model6a_full_pol,
    "Military" = results_ethnic_drop$model6a_full_mil,
    "Economic" = results_ethnic_drop$model6a_full_econ,
    "Cultural" = results_ethnic_drop$model6a_full_cult,
    "Other" = results_ethnic_drop$model6a_full_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S15 (Drop): H3b Ethnic by Topic — FE, Full Data (Drop No-Time Articles)",
  add_rows = rows_t4h,
  notes = str_wrap(note_t4h, 80)
)

table_4h

save_table(table_4h, "table_s15_fe_topic_full_drop")
```

### Table S1 (Prob): H1 FE Main Results — Probabilistic Time Assignment

```{r table-s01-fe-prob}
n_cl_t1f <- sapply(list(results_h1_prob$model1_opt, results_h1_prob$model2_opt,
                        results_h1_prob$model3_opt, results_h1_prob$model4_opt,
                        results_h1_prob$model1_full_linear, results_h1_prob$model4_non_mil,
                        results_h1_prob$model4_non_nato, results_h1_prob$model4_felm_saturated),
                   get_n_clusters)
rows_t1f <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7, ~row8,
  'State FEs', '-', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', 'X', 'X', 'X', 'X', 'X', 'X',
  'Topic FEs', '-', '-', '-', 'X', 'X', 'X', 'X', 'X',
  'Clusters', n_cl_t1f[1], n_cl_t1f[2], n_cl_t1f[3], n_cl_t1f[4], n_cl_t1f[5], n_cl_t1f[6], n_cl_t1f[7], n_cl_t1f[8]
)
attr(rows_t1f, 'position') <- c(3, 4, 5, 6)

note_t1f <- paste("All standard errors are clustered at the source level. Articles without publication times are assigned times via KDE sampling from same-source distributions. Models 1-4 uses the optimal bandwidth. Model 5 uses a linear specification with the full set of articles. Model 6 omits Military Topics. Model 7 omits NATO allies. Model 8 uses full saturation (country-source-topic FEs).", SE_NOTE)

table_1f <- modelsummary(
  list(
    "(1)" = results_h1_prob$model1_opt,
    "(2)" = results_h1_prob$model2_opt,
    "(3)" = results_h1_prob$model3_opt,
    "(4)" = results_h1_prob$model4_opt,
    "(5)" = results_h1_prob$model1_full_linear,
    "(6)" = results_h1_prob$model4_non_mil,
    "(7)" = results_h1_prob$model4_non_nato,
    "(8)" = results_h1_prob$model4_felm_saturated
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c("treatment" = "Invasion", "post" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S1 (Prob): H1 RDD — Fixed Effects (Probabilistic Time Assignment)",
  add_rows = rows_t1f,
  notes = str_wrap(note_t1f, 80)
)

table_1f

save_table(table_1f, "table_s01_fe_prob")
```

## Table 1G: RDD By Topic (Probabilistic Time)

```{r table1g}
n_cl_t1g <- sapply(list(results_h1_prob$model4_opt_pol, results_h1_prob$model4_opt_mil,
                        results_h1_prob$model4_opt_econ, results_h1_prob$model4_opt_cult,
                        results_h1_prob$model4_opt_oth), get_n_clusters)
rows_t1g <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', 'X', 'X', 'X', 'X', 'X',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t1g[1], n_cl_t1g[2], n_cl_t1g[3], n_cl_t1g[4], n_cl_t1g[5]
)
attr(rows_t1g, 'position') <- c(3, 4, 5, 6)

note_t1g <- paste("All standard errors are clustered at the source level. Articles without publication times are assigned times via KDE sampling. All models use the optimal bandwidth with country and source fixed effects.", SE_NOTE)

table_1g <- modelsummary(
  list(
    "Political" = results_h1_prob$model4_opt_pol,
    "Military" = results_h1_prob$model4_opt_mil,
    "Economic" = results_h1_prob$model4_opt_econ,
    "Cultural" = results_h1_prob$model4_opt_cult,
    "Other" = results_h1_prob$model4_opt_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c("treatment" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S9 (Prob): H1 RDD by Topic — FE, Optimal BW (Probabilistic Time Assignment)",
  add_rows = rows_t1g,
  notes = str_wrap(note_t1g, 80)
)

table_1g

save_table(table_1g, "table_s09_fe_topic_opt_prob")
```

### Table S5 (Prob): H1 By-Topic Z-Score — Probabilistic Time

```{r table-s05-z-topic-prob}
models_1gz <- list(
  "Political" = results_h1_prob$model5_opt_pol,
  "Military" = results_h1_prob$model5_opt_mil,
  "Economic" = results_h1_prob$model5_opt_econ,
  "Cultural" = results_h1_prob$model5_opt_cult,
  "Other" = results_h1_prob$model5_opt_oth
)
tbl_1gz <- modelsummary(
  models_1gz,
  output = "gt",
  coef_map = c("treatment" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  stars = c('*' = .05, '**' = .01, '***' = .001),
  fmt = 3,
  title = "Table S5 (Prob): H1 RDD by Topic — Z-Score (Probabilistic Time Assignment)"
)
tbl_1gz
save_table(tbl_1gz, "table_s05_z_topic_prob")
```

### Table S6 (All Variants): H2 By-Topic Z-Score

```{r table-s06-z-topic-todo}
# TODO: Table S6 requires Z-score by-topic models for H2 (state_owned interaction).
# Expected model names in results_h2 (and _prob, _cont, _drop variants):
#   model2a_opt_z_pol, model2a_opt_z_mil, model2a_opt_z_econ,
#   model2a_opt_z_cult, model2a_opt_z_oth
# Create these in 05 scripts. Once available, build table with:
#   coef_map = c("treatment" = "Invasion", "treatment:state_owned" = "State Owned x Treatment")
# Save files: table_s06_z_topic_days, table_s06_z_topic_prob,
#             table_s06_z_topic_cont, table_s06_z_topic_drop
cat("NOTE: Table S6 (H2 by-topic Z-score) skipped — models not yet created.\n")
```

### Table S7 (All Variants): H3a By-Topic Z-Score

```{r table-s07-z-topic-todo}
# TODO: Table S7 requires Z-score by-topic models for H3a (CSTO interaction).
# Expected model names in results_align (and _prob, _cont, _drop variants):
#   model5a_opt_z_pol, model5a_opt_z_mil, model5a_opt_z_econ,
#   model5a_opt_z_cult, model5a_opt_z_oth
# Create these in 06 scripts. Once available, build table with:
#   coef_map = c("treatment" = "Invasion", "treatment:csto" = "CSTO x Treatment")
# Save files: table_s07_z_topic_days, table_s07_z_topic_prob,
#             table_s07_z_topic_cont, table_s07_z_topic_drop
cat("NOTE: Table S7 (H3a by-topic Z-score) skipped — models not yet created.\n")
```

### Table S8 (All Variants): H3b By-Topic Z-Score

```{r table-s08-z-topic-todo}
# TODO: Table S8 requires Z-score by-topic models for H3b (high_russia interaction).
# Expected model names in results_ethnic (and _prob, _cont, _drop variants):
#   model6a_opt_z_pol, model6a_opt_z_mil, model6a_opt_z_econ,
#   model6a_opt_z_cult, model6a_opt_z_oth
# Create these in 07 scripts. Once available, build table with:
#   coef_map = c("treatment" = "Invasion", "treatment:high_russia" = "High Russian Pop x Treatment")
# Save files: table_s08_z_topic_days, table_s08_z_topic_prob,
#             table_s08_z_topic_cont, table_s08_z_topic_drop
cat("NOTE: Table S8 (H3b by-topic Z-score) skipped — models not yet created.\n")
```

## --- S9–S12: By-Topic FE Optimal BW ---

## Table 2I: Diff-in-Disc Main (Probabilistic Time)

```{r table2i}
n_cl_t2i <- sapply(list(results_h2_prob$model2a, results_h2_prob$model2a_full,
                        results_h2_prob$model2a_opt, results_h2_prob$model2a_opt_full_fe,
                        results_h2_prob$model2b, results_h2_prob$model2d,
                        results_h2_prob$model3a_opt, results_h2_prob$model3a_opt_saturated),
                   get_n_clusters)
rows_t2i <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7, ~row8,
  'State FEs', 'X', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', 'X', '-', 'X', '-', '-', '-', 'X',
  'Topic FEs', 'X', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Clusters', n_cl_t2i[1], n_cl_t2i[2], n_cl_t2i[3], n_cl_t2i[4], n_cl_t2i[5], n_cl_t2i[6], n_cl_t2i[7], n_cl_t2i[8]
)
attr(rows_t2i, 'position') <- c(5, 6, 7, 8)

note_t2i <- paste("All standard errors are clustered at the source level. Articles without publication times are assigned times via KDE sampling. Model 1 uses full data with topic FEs. Model 2 adds source FEs. Model 3 uses optimal bandwidth with topic FEs. Model 4 uses optimal bandwidth with full FEs. Model 5 omits military-related articles. Model 6 omits NATO allies. Model 7 combines Russian-related + combined bandwidth filters. Model 8 uses saturated FEs.", SE_NOTE)

table_2i <- modelsummary(
  list(
    "(1)" = results_h2_prob$model2a,
    "(2)" = results_h2_prob$model2a_full,
    "(3)" = results_h2_prob$model2a_opt,
    "(4)" = results_h2_prob$model2a_opt_full_fe,
    "(5)" = results_h2_prob$model2b,
    "(6)" = results_h2_prob$model2d,
    "(7)" = results_h2_prob$model3a_opt,
    "(8)" = results_h2_prob$model3a_opt_saturated
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S2 (Prob): H2 Diff-in-Disc — Fixed Effects (Probabilistic Time Assignment)",
  add_rows = rows_t2i,
  notes = str_wrap(note_t2i, 80)
)

table_2i

save_table(table_2i, "table_s02_fe_prob")
```

## Table 2I-S: H2 Diff-in-Disc (Probabilistic) — Full FE Robustness

```{r table2is}
n_cl_t2is <- sapply(list(results_h2_prob$model2b_full_fe, results_h2_prob$model3a_opt_full_fe),
                    get_n_clusters)
rows_t2is <- tibble::tribble(
  ~term, ~row1, ~row2,
  'State FEs', 'X', 'X',
  'Source FEs', 'X', 'X',
  'Topic FEs', 'X', 'X',
  'Clusters', n_cl_t2is[1], n_cl_t2is[2]
)
attr(rows_t2is, 'position') <- c(5, 6, 7, 8)

note_t2is <- paste("All standard errors are clustered at the source level. Articles without publication times are assigned times via KDE sampling. Both models include full FEs (topic + source). Model 1 uses non-military subset. Model 2 uses Russian-related + combined bandwidth filters.", SE_NOTE)

table_2is <- modelsummary(
  list(
    "(1) Non-Mil, Full FEs" = results_h2_prob$model2b_full_fe,
    "(2) Russian Opt, Full FEs" = results_h2_prob$model3a_opt_full_fe
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S16 (Prob): H2 Diff-in-Disc — Full FE Robustness (Probabilistic Time)",
  add_rows = rows_t2is,
  notes = str_wrap(note_t2is, 80)
)

table_2is

save_table(table_2is, "table_s16_full_fe_robustness_prob")
```

## Table 2J: Diff-in-Disc By Topic Optimal BW (Probabilistic Time)

```{r table2j}
n_cl_t2j <- sapply(list(results_h2_prob$model2a_opt_pol, results_h2_prob$model2a_opt_mil,
                        results_h2_prob$model2a_opt_econ, results_h2_prob$model2a_opt_cult,
                        results_h2_prob$model2a_opt_oth), get_n_clusters)
rows_t2j <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t2j[1], n_cl_t2j[2], n_cl_t2j[3], n_cl_t2j[4], n_cl_t2j[5]
)
attr(rows_t2j, 'position') <- c(5, 6, 7, 8)

note_t2j <- paste("All standard errors are clustered at the source level. Articles without publication times are assigned times via KDE sampling. All models use a per-topic re-optimized bandwidth with country fixed effects only.", SE_NOTE)

table_2j <- modelsummary(
  list(
    "Political" = results_h2_prob$model2a_opt_pol,
    "Military" = results_h2_prob$model2a_opt_mil,
    "Economic" = results_h2_prob$model2a_opt_econ,
    "Cultural" = results_h2_prob$model2a_opt_cult,
    "Other" = results_h2_prob$model2a_opt_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S10 (Prob): H2 Diff-in-Disc by Topic — FE, Optimal BW (Probabilistic Time Assignment)",
  add_rows = rows_t2j,
  notes = str_wrap(note_t2j, 80)
)

table_2j

save_table(table_2j, "table_s10_fe_topic_opt_prob")
```

## Table 2K: Diff-in-Disc By Topic Full Data (Probabilistic Time)

```{r table2k}
n_cl_t2k <- sapply(list(results_h2_prob$model2a_full_pol, results_h2_prob$model2a_full_mil,
                        results_h2_prob$model2a_full_econ, results_h2_prob$model2a_full_cult,
                        results_h2_prob$model2a_full_oth), get_n_clusters)
rows_t2k <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t2k[1], n_cl_t2k[2], n_cl_t2k[3], n_cl_t2k[4], n_cl_t2k[5]
)
attr(rows_t2k, 'position') <- c(5, 6, 7, 8)

note_t2k <- paste("All standard errors are clustered at the source level. Articles without publication times are assigned times via KDE sampling. All models use the full dataset (no bandwidth restriction) with country fixed effects only.", SE_NOTE)

table_2k <- modelsummary(
  list(
    "Political" = results_h2_prob$model2a_full_pol,
    "Military" = results_h2_prob$model2a_full_mil,
    "Economic" = results_h2_prob$model2a_full_econ,
    "Cultural" = results_h2_prob$model2a_full_cult,
    "Other" = results_h2_prob$model2a_full_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S13 (Prob): H2 Diff-in-Disc by Topic — FE, Full Data (Probabilistic Time)",
  add_rows = rows_t2k,
  notes = str_wrap(note_t2k, 80)
)

table_2k

save_table(table_2k, "table_s13_fe_topic_full_prob")
```

## Table 2L: State-Owned and Independent Media RDD (Day)

```{r table2l}
note_t2l <- paste("Separate RDD estimates for state-owned and independent media using the day running variable. Bandwidths selected by MSE-optimal bandwidth selector. Standard errors are cluster-robust (rdrobust).", SE_NOTE)

table_2l <- modelsummary(
  list(
    "State Media" = results_h2$model2_state_rdd,
    "Independent Media" = results_h2$model2_ind_rdd
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c("treatment" = "Invasion (RDD)"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S17: H2 State vs. Independent Media RDDs — FE (Day Running Variable)",
  notes = str_wrap(note_t2l, 80)
)

table_2l

save_table(table_2l, "table_s17_h2_state_ind_rdd_days")
```

```{r table-s17-state-ind-rdd-cont}
# TODO: Verify model2_state_rdd and model2_ind_rdd exist in results_h2_cont.
# If yes, create Table S17 (Cont): H2 State vs. Independent Media RDDs — FE (Continuous Running Variable)
# and save as table_s17_h2_state_ind_rdd_cont.
cat("TODO: Table S17 (Cont) — model2_state_rdd / model2_ind_rdd in results_h2_cont not yet verified.\n")
```

```{r table-s17-state-ind-rdd-drop}
# TODO: Verify model2_state_rdd and model2_ind_rdd exist in results_h2_drop.
# If yes, create Table S17 (Drop): H2 State vs. Independent Media RDDs — FE (Drop No-Time Articles)
# and save as table_s17_h2_state_ind_rdd_drop.
cat("TODO: Table S17 (Drop) — model2_state_rdd / model2_ind_rdd in results_h2_drop not yet verified.\n")
```

```{r table-s17-state-ind-rdd-prob}
# TODO: Verify model2_state_rdd and model2_ind_rdd exist in results_h2_prob.
# If yes, create Table S17 (Prob): H2 State vs. Independent Media RDDs — FE (Probabilistic Time)
# and save as table_s17_h2_state_ind_rdd_prob.
cat("TODO: Table S17 (Prob) — model2_state_rdd / model2_ind_rdd in results_h2_prob not yet verified.\n")
```

## Table 3I: Alignment Main (Probabilistic Time)

```{r table3i}
n_cl_t3i <- sapply(list(results_align_prob$model5a_csto, results_align_prob$model5a_neutral,
                        results_align_prob$model5a_full, results_align_prob$model5a_opt,
                        results_align_prob$model5a_opt_non_mil, results_align_prob$model5a_opt_russian,
                        results_align_prob$model5a_opt_full_fe, results_align_prob$model5a_opt_non_mil_full_fe,
                        results_align_prob$model5a_fully_saturated, results_align_prob$matched_model),
                   get_n_clusters)
rows_t3i <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7, ~row8, ~row9, ~row10,
  'State FEs', '-', '-', 'X', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-', '-', 'X', 'X', 'X', 'X',
  'Topic FEs', '-', '-', 'X', 'X', 'X', 'X', 'X', 'X', 'X', 'X',
  'Matched', '-', '-', '-', '-', '-', '-', '-', '-', '-', 'X',
  'Clusters', n_cl_t3i[1], n_cl_t3i[2], n_cl_t3i[3], n_cl_t3i[4], n_cl_t3i[5], n_cl_t3i[6], n_cl_t3i[7], n_cl_t3i[8], n_cl_t3i[9], n_cl_t3i[10]
)
attr(rows_t3i, 'position') <- c(5, 6, 7, 8, 9)

note_t3i <- paste("Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights) for Models 3-10, clustered at source level. Models 1-2 use rdrobust standard errors. Articles without publication times are assigned times via KDE sampling. Model 1 shows RDD results for CSTO countries only. Model 2 shows RDD results for Neutral countries only. Model 3 uses full data with topic fixed effects. Model 4 uses the optimal bandwidth with topic fixed effects. Model 5 omits military-related articles and uses a re-optimized bandwidth. Model 6 uses only Russian-related (non-military) articles with a re-optimized bandwidth. Model 7 uses optimal bandwidth with full FEs (topic + source + state FEs). Model 8 uses non-military subset with full FEs. Model 9 uses full saturation (source-topic and topic-treatment FEs). Model 10 uses exact matching on publication day and topic. Sample restricted to state-owned media in non-NATO countries.", SE_NOTE)

# Create vcov list with bootstrap SEs for felm models
vcov_t3i <- list(
  NULL,
  NULL,
  "(3)" = create_bootstrap_vcov(results_align_prob$model5a_full, results_align_prob$bootstrap_se$model5a_full, "treatment:csto"),
  "(4)" = create_bootstrap_vcov(results_align_prob$model5a_opt, results_align_prob$bootstrap_se$model5a_opt, "treatment:csto"),
  "(5)" = create_bootstrap_vcov(results_align_prob$model5a_opt_non_mil, results_align_prob$bootstrap_se$model5a_opt_non_mil, "treatment:csto"),
  "(6)" = create_bootstrap_vcov(results_align_prob$model5a_opt_russian, results_align_prob$bootstrap_se$model5a_opt_russian, "treatment:csto"),
  "(7)" = create_bootstrap_vcov(results_align_prob$model5a_opt_full_fe, results_align_prob$bootstrap_se$model5a_opt_full_fe, "treatment:csto"),
  "(8)" = create_bootstrap_vcov(results_align_prob$model5a_opt_non_mil_full_fe, results_align_prob$bootstrap_se$model5a_opt_non_mil_full_fe, "treatment:csto"),
  "(9)" = create_bootstrap_vcov(results_align_prob$model5a_fully_saturated, results_align_prob$bootstrap_se$model5a_fully_saturated, "treatment:csto"),
  "(10)" = create_bootstrap_vcov(results_align_prob$matched_model, results_align_prob$bootstrap_se$matched_model, "treatment:csto")
)

table_3i <- modelsummary(
  list(
    "(1)" = results_align_prob$model5a_csto,
    "(2)" = results_align_prob$model5a_neutral,
    "(3)" = results_align_prob$model5a_full,
    "(4)" = results_align_prob$model5a_opt,
    "(5)" = results_align_prob$model5a_opt_non_mil,
    "(6)" = results_align_prob$model5a_opt_russian,
    "(7)" = results_align_prob$model5a_opt_full_fe,
    "(8)" = results_align_prob$model5a_opt_non_mil_full_fe,
    "(9)" = results_align_prob$model5a_fully_saturated,
    "(10)" = results_align_prob$matched_model
  ),
  vcov = vcov_t3i,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S3 (Prob): H3a Alignment — Fixed Effects (Probabilistic Time Assignment)",
  add_rows = rows_t3i,
  notes = str_wrap(note_t3i, 80)
)

table_3i

save_table(table_3i, "table_s03_fe_prob")
```

## Table 3J: Alignment By Topic Optimal BW (Probabilistic Time)

```{r table3j}
n_cl_t3j <- sapply(list(results_align_prob$model5a_opt_pol, results_align_prob$model5a_opt_mil,
                        results_align_prob$model5a_opt_econ, results_align_prob$model5a_opt_cult,
                        results_align_prob$model5a_opt_oth), get_n_clusters)
rows_t3j <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t3j[1], n_cl_t3j[2], n_cl_t3j[3], n_cl_t3j[4], n_cl_t3j[5]
)
attr(rows_t3j, 'position') <- c(5, 6, 7, 8)

note_t3j <- paste("All standard errors are clustered at the source level. Articles without publication times are assigned times via KDE sampling. Each model uses a per-topic re-optimized bandwidth. State media in non-NATO countries only.", SE_NOTE)

table_3j <- modelsummary(
  list(
    "Political" = results_align_prob$model5a_opt_pol,
    "Military" = results_align_prob$model5a_opt_mil,
    "Economic" = results_align_prob$model5a_opt_econ,
    "Cultural" = results_align_prob$model5a_opt_cult,
    "Other" = results_align_prob$model5a_opt_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S11 (Prob): H3a Alignment by Topic — FE, Optimal BW (Probabilistic Time Assignment)",
  add_rows = rows_t3j,
  notes = str_wrap(note_t3j, 80)
)

table_3j

save_table(table_3j, "table_s11_fe_topic_opt_prob")
```

## Table 3K: Alignment By Topic Full Data (Probabilistic Time)

```{r table3k}
n_cl_t3k <- sapply(list(results_align_prob$model5a_full_pol, results_align_prob$model5a_full_mil,
                        results_align_prob$model5a_full_econ, results_align_prob$model5a_full_cult,
                        results_align_prob$model5a_full_oth), get_n_clusters)
rows_t3k <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t3k[1], n_cl_t3k[2], n_cl_t3k[3], n_cl_t3k[4], n_cl_t3k[5]
)
attr(rows_t3k, 'position') <- c(5, 6, 7, 8)

note_t3k <- paste("All standard errors are clustered at the source level. Articles without publication times are assigned times via KDE sampling. Each model uses the full dataset (no bandwidth restriction). State media in non-NATO countries only.", SE_NOTE)

table_3k <- modelsummary(
  list(
    "Political" = results_align_prob$model5a_full_pol,
    "Military" = results_align_prob$model5a_full_mil,
    "Economic" = results_align_prob$model5a_full_econ,
    "Cultural" = results_align_prob$model5a_full_cult,
    "Other" = results_align_prob$model5a_full_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S14 (Prob): H3a Alignment by Topic — FE, Full Data (Probabilistic Time)",
  add_rows = rows_t3k,
  notes = str_wrap(note_t3k, 80)
)

table_3k

save_table(table_3k, "table_s14_fe_topic_full_prob")
```

## Table 4I: Ethnic Main (Probabilistic Time)

```{r table4i}
n_cl_t4i <- sapply(list(results_ethnic_prob$model6a_full, results_ethnic_prob$model6a_opt,
                        results_ethnic_prob$model6a_opt_non_mil, results_ethnic_prob$model6a_opt_russian),
                   get_n_clusters)
rows_t4i <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4,
  'State FEs', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-',
  'Topic FEs', 'X', 'X', 'X', 'X',
  'Clusters', n_cl_t4i[1], n_cl_t4i[2], n_cl_t4i[3], n_cl_t4i[4]
)
attr(rows_t4i, 'position') <- c(5, 6, 7, 8)

note_t4i <- paste("Standard errors computed via wild cluster bootstrap (9999 iterations, Rademacher weights), clustered at source level. Articles without publication times are assigned times via KDE sampling. Model 1 uses full data with topic fixed effects. Model 2 uses the optimal bandwidth with topic fixed effects. Model 3 omits military-related articles and uses a re-optimized bandwidth. Model 4 uses only Russian-related (non-military) articles with a re-optimized bandwidth. Sample restricted to state-owned media in non-NATO countries.", SE_NOTE)

# Create vcov list with bootstrap SEs
vcov_t4i <- list(
  "(1)" = create_bootstrap_vcov(results_ethnic_prob$model6a_full, results_ethnic_prob$bootstrap_se$model6a_full, "treatment:high_russia"),
  "(2)" = create_bootstrap_vcov(results_ethnic_prob$model6a_opt, results_ethnic_prob$bootstrap_se$model6a_opt, "treatment:high_russia"),
  "(3)" = create_bootstrap_vcov(results_ethnic_prob$model6a_opt_non_mil, results_ethnic_prob$bootstrap_se$model6a_opt_non_mil, "treatment:high_russia"),
  "(4)" = create_bootstrap_vcov(results_ethnic_prob$model6a_opt_russian, results_ethnic_prob$bootstrap_se$model6a_opt_russian, "treatment:high_russia")
)

table_4i <- modelsummary(
  list(
    "(1)" = results_ethnic_prob$model6a_full,
    "(2)" = results_ethnic_prob$model6a_opt,
    "(3)" = results_ethnic_prob$model6a_opt_non_mil,
    "(4)" = results_ethnic_prob$model6a_opt_russian
  ),
  vcov = vcov_t4i,
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S4 (Prob): H3b Ethnic — Fixed Effects (Probabilistic Time Assignment)",
  add_rows = rows_t4i,
  notes = str_wrap(note_t4i, 80)
)

table_4i

save_table(table_4i, "table_s04_fe_prob")
```

## Table 4J: Ethnic By Topic Optimal BW (Probabilistic Time)

```{r table4j}
n_cl_t4j <- sapply(list(results_ethnic_prob$model6a_opt_pol, results_ethnic_prob$model6a_opt_mil,
                        results_ethnic_prob$model6a_opt_econ, results_ethnic_prob$model6a_opt_cult,
                        results_ethnic_prob$model6a_opt_oth), get_n_clusters)
rows_t4j <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t4j[1], n_cl_t4j[2], n_cl_t4j[3], n_cl_t4j[4], n_cl_t4j[5]
)
attr(rows_t4j, 'position') <- c(5, 6, 7, 8)

note_t4j <- paste("All standard errors are clustered at the source level. Articles without publication times are assigned times via KDE sampling. Each model uses a per-topic re-optimized bandwidth. State media in non-NATO countries only.", SE_NOTE)

table_4j <- modelsummary(
  list(
    "Political" = results_ethnic_prob$model6a_opt_pol,
    "Military" = results_ethnic_prob$model6a_opt_mil,
    "Economic" = results_ethnic_prob$model6a_opt_econ,
    "Cultural" = results_ethnic_prob$model6a_opt_cult,
    "Other" = results_ethnic_prob$model6a_opt_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S12 (Prob): H3b Ethnic by Topic — FE, Optimal BW (Probabilistic Time Assignment)",
  add_rows = rows_t4j,
  notes = str_wrap(note_t4j, 80)
)

table_4j

save_table(table_4j, "table_s12_fe_topic_opt_prob")
```

## Table 4K: Ethnic By Topic Full Data (Probabilistic Time)

```{r table4k}
n_cl_t4k <- sapply(list(results_ethnic_prob$model6a_full_pol, results_ethnic_prob$model6a_full_mil,
                        results_ethnic_prob$model6a_full_econ, results_ethnic_prob$model6a_full_cult,
                        results_ethnic_prob$model6a_full_oth), get_n_clusters)
rows_t4k <- tibble::tribble(
  ~term, ~row1, ~row2, ~row3, ~row4, ~row5,
  'State FEs', 'X', 'X', 'X', 'X', 'X',
  'Source FEs', '-', '-', '-', '-', '-',
  'Topic FEs', '-', '-', '-', '-', '-',
  'Clusters', n_cl_t4k[1], n_cl_t4k[2], n_cl_t4k[3], n_cl_t4k[4], n_cl_t4k[5]
)
attr(rows_t4k, 'position') <- c(5, 6, 7, 8)

note_t4k <- paste("All standard errors are clustered at the source level. Articles without publication times are assigned times via KDE sampling. Each model uses the full dataset (no bandwidth restriction). State media in non-NATO countries only.", SE_NOTE)

table_4k <- modelsummary(
  list(
    "Political" = results_ethnic_prob$model6a_full_pol,
    "Military" = results_ethnic_prob$model6a_full_mil,
    "Economic" = results_ethnic_prob$model6a_full_econ,
    "Cultural" = results_ethnic_prob$model6a_full_cult,
    "Other" = results_ethnic_prob$model6a_full_oth
  ),
  output = "gt",
  fmt = 3,
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
  title = "Table S15 (Prob): H3b Ethnic by Topic — FE, Full Data (Probabilistic Time)",
  add_rows = rows_t4k,
  notes = str_wrap(note_t4k, 80)
)

table_4k

save_table(table_4k, "table_s15_fe_topic_full_prob")
```

# Comparison Table: Countries by Alignment and Ethnic Population

```{r comparison-table}
get_group <- function(russian_group, security_group) {
  paste(intersect(russian_group, security_group), collapse = ", ")
}

table_data <- data.frame(
  `Ethnic Russian Population` = c("Low Ethnic", "High Ethnic"),
  `Low Russia Aligned` = c(
    get_group(LOW_RUSSIAN_POP, NEUTRAL_COUNTRIES),
    get_group(HIGH_RUSSIAN_POP, NEUTRAL_COUNTRIES)
  ),
  `High Russia Aligned` = c(
    get_group(LOW_RUSSIAN_POP, CSTO_COUNTRIES),
    get_group(HIGH_RUSSIAN_POP, CSTO_COUNTRIES)
  )
)

comparison_table <- table_data %>%
  gt() %>%
  tab_header(
    title = "Ethnic Russian Population x Russia Security Alignment",
    subtitle = "Country Classification"
  ) %>%
  cols_label(
    Ethnic.Russian.Population = "",
    Low.Russia.Aligned = "Low Alignment (Neutral)",
    High.Russia.Aligned = "High Alignment (CSTO)"
  ) %>%
  tab_style(
    style = cell_borders(sides = "all", color = "black", weight = px(1)),
    locations = cells_body()
  )

comparison_table

save_table(comparison_table, "table_s18_country_classification")
```

# Alignment Table

```{r alignment-table}
alignment_table <- table_data %>%
  gt() %>%
  tab_header(
    title = "Ethnic Russian Population x Russia Security Alignment",
    subtitle = "Alignment Comparison"
  ) %>%
  cols_label(
    Ethnic.Russian.Population = "",
    Low.Russia.Aligned = "Low Alignment",
    High.Russia.Aligned = "High Alignment"
  ) %>%
  fmt_markdown(everything()) %>%
  tab_style(
    style = cell_borders(sides = c("top", "bottom"), color = "black", weight = px(2)),
    locations = cells_body(rows = 1:2, columns = 2:3)
  ) %>%
  tab_style(
    style = cell_borders(sides = c("left", "right"), color = "black", weight = px(2)),
    locations = cells_body(rows = 1:2, columns = 2:3)
  )

alignment_table

save_table(alignment_table, "table_s19_alignment_classification")
```

# Ethnic Table

```{r ethnic-table}
ethnic_table <- table_data %>%
  gt() %>%
  tab_header(
    title = "Ethnic Russian Population x Russia Security Alignment",
    subtitle = "Ethnic Comparison"
  ) %>%
  cols_label(
    Ethnic.Russian.Population = "",
    Low.Russia.Aligned = "Low Alignment",
    High.Russia.Aligned = "High Alignment"
  ) %>%
  fmt_markdown(everything()) %>%
  tab_style(
    style = cell_borders(sides = "bottom", color = "black", weight = px(2)),
    locations = cells_body(rows = 1, columns = 2:3)
  ) %>%
  tab_style(
    style = cell_borders(sides = c("top", "bottom", "left", "right"), color = "black", weight = px(2)),
    locations = cells_body(rows = 1:2, columns = 2:3)
  )

ethnic_table

save_table(ethnic_table, "table_s20_ethnic_classification")
```

# Export Tables to LaTeX

```{r latex-export}
# Function to save modelsummary as tex
save_tex <- function(models, filename, coef_map, title, rows = NULL, note = NULL) {
  modelsummary(
    models,
    output = file.path(FIGURES_TABLES, filename),
    fmt = 3,
    stars = c('*' = .05, '**' = .01, '***' = .001),
    coef_map = coef_map,
    gof_omit = "BIC|AIC|RMSE|Std.Errors|FE",
    title = title,
    add_rows = rows,
    notes = note
  )
}

# Note: These will generate .tex files for LaTeX inclusion
cat("LaTeX tables can be generated by changing output format to 'latex'\n")
```

# Summary of All Tables

```{r summary}
cat("\n")
cat("=============================================================\n")
cat("PUBLICATION OUTPUTS SUMMARY\n")
cat("=============================================================\n")
cat("\nRDS inputs loaded:\n")
cat("  - 04_h1_results*.rds      (H1: Main RDD, 4 variants)\n")
cat("  - 05_h2_results*.rds      (H2: Diff-in-Disc, 4 variants)\n")
cat("  - 06_alignment_results*.rds (Alignment heterogeneity, 4 variants)\n")
cat("  - 07_ethnic_results*.rds   (Ethnic heterogeneity, 4 variants)\n")
cat("\nTables generated (each saved as .tex AND .html):\n")
cat("\n  ## MAIN PAPER TABLES (Tables 1–4, each × 4 data variants) ##\n")
cat("  - table_01_main / _prob / _cont / _drop   Table 1: H1 RDD (hybrid FE + Z-score)\n")
cat("  - table_02_main / _prob / _cont / _drop   Table 2: H2 Diff-in-Disc (Z-score)\n")
cat("  - table_03_main / _prob / _cont / _drop   Table 3: H3a Alignment (Z-score)\n")
cat("  - table_04_main / _prob / _cont / _drop   Table 4: H3b Ethnic (Z-score)\n")
cat("\n  ## SUPPLEMENTARY TABLES ##\n")
cat("  S1  table_s01_fe_days/cont/drop/prob    H1 FE-based main results\n")
cat("  S2  table_s02_fe_days/cont/drop/prob    H2 FE-based main results\n")
cat("  S3  table_s03_fe_days/cont/drop/prob    H3a Alignment FE-based main results\n")
cat("  S4  table_s04_fe_days/cont/drop/prob    H3b Ethnic FE-based main results\n")
cat("  S5  table_s05_z_topic_days/cont/drop/prob  H1 by-topic Z-score, opt BW\n")
cat("  S6  table_s06_z_topic_*                 H2 by-topic Z-score (TODO: models missing)\n")
cat("  S7  table_s07_z_topic_*                 H3a by-topic Z-score (TODO: models missing)\n")
cat("  S8  table_s08_z_topic_*                 H3b by-topic Z-score (TODO: models missing)\n")
cat("  S9  table_s09_fe_topic_opt_days/cont/drop/prob  H1 by-topic FE opt BW\n")
cat("  S10 table_s10_fe_topic_opt_days/cont/drop/prob  H2 by-topic FE opt BW\n")
cat("  S11 table_s11_fe_topic_opt_days/cont/drop/prob  H3a by-topic FE opt BW\n")
cat("  S12 table_s12_fe_topic_opt_days/cont/drop/prob  H3b by-topic FE opt BW\n")
cat("  S13 table_s13_fe_topic_full_days/cont/drop/prob H2 by-topic FE full data\n")
cat("  S14 table_s14_fe_topic_full_days/cont/drop/prob H3a by-topic FE full data\n")
cat("  S15 table_s15_fe_topic_full_days/cont/drop/prob H3b by-topic FE full data\n")
cat("  S16 table_s16_full_fe_robustness_days/cont/drop/prob  H2 Full FE robustness\n")
cat("  S17 table_s17_h2_state_ind_rdd_days (+TODO: cont/drop/prob)  H2 State vs Ind RDDs\n")
cat("  S18 table_s18_country_classification    Country classification\n")
cat("  S19 table_s19_alignment_classification  Alignment classification\n")
cat("  S20 table_s20_ethnic_classification     Ethnic population classification\n")
cat("  S21 table_s21_loo_alignment_robustness  Leave-one-out robustness\n")
cat("  S22 table_s22_placebo_summary           Placebo test summary\n")
cat("\nFigures generated in previous scripts:\n")
cat("  - invasion_on_sentiment.png\n")
cat("  - invasion_on_sentiment_non_mil.png\n")
cat("  - invasion_discs_graph.png\n")
cat("  - invasion_discs_non_mil.png\n")
cat("  - state_align_discs.png\n")
cat("  - ethnic_discs.png\n")
cat("  - articles_per_day.png\n")
cat("  - topic_distribution.png\n")
cat("  - topic_split.png\n")
cat("=============================================================\n")
```

# Leave-One-Out Country Robustness Table

```{r loo-table}
loo_data <- results_align$loo_summary

note_loo <- "Leave-one-out robustness analysis for the non-military topics model. Each row shows results when excluding the specified country from the sample. Bandwidth is recalculated for each subset. Coefficient shown is for the treatment:csto interaction term. Standard errors clustered at source domain level."
note_loo_wrapped <- str_wrap(note_loo, width = 80)

loo_table <- loo_data %>%
  mutate(
    estimate_fmt = sprintf("%.3f%s", estimate,
                     case_when(p_value < 0.001 ~ "***",
                               p_value < 0.01 ~ "**",
                               p_value < 0.05 ~ "*",
                               TRUE ~ "")),
    std_error_fmt = sprintf("(%.3f)", std_error),
    p_value_fmt = sprintf("%.3f", p_value),
    n_obs_fmt = format(n_obs, big.mark = ","),
    bandwidth_fmt = sprintf("%.1f", bandwidth)
  ) %>%
  select(country_dropped, estimate_fmt, std_error_fmt, p_value_fmt, n_obs_fmt, bandwidth_fmt) %>%
  gt() %>%
  cols_label(
    country_dropped = "Country Dropped",
    estimate_fmt = "Coefficient",
    std_error_fmt = "Std. Error",
    p_value_fmt = "p-value",
    n_obs_fmt = "N",
    bandwidth_fmt = "Bandwidth"
  ) %>%
  tab_header(title = "Table S21: Leave-One-Out Country Robustness Analysis",
             subtitle = "Non-Military Topics Model") %>%
  tab_footnote(footnote = note_loo_wrapped)

loo_table

save_table(loo_table, "table_s21_loo_alignment_robustness")
```

# Placebo Test Summary Table

```{r placebo-summary}
# Extract placebo results from all hypothesis results
# Note: H1 uses rdrobust, H2 and H3 use felm

# Extract rdrobust result for H1
placebo_h1 <- results_h1$model_placebo
h1_estimate <- placebo_h1$coef[1]  # Conventional RD estimate
h1_se <- placebo_h1$se[1]
h1_pval <- placebo_h1$pv[1]
h1_bw <- placebo_h1$bws[1, 1]
h1_n <- placebo_h1$N_h[1] + placebo_h1$N_h[2]

# Extract felm results for H2 and H3
placebo_h2 <- results_h2$model_placebo
placebo_h3 <- results_align$model_placebo_nonmil

h2_coef <- summary(placebo_h2)$coef["treatment", ]
h3_coef <- summary(placebo_h3)$coef["treatment", ]

# Create summary data frame
placebo_summary <- tibble(
  Model = c("(1) H1: Full Model (RDD)", "(2) H2: Diff-in-Disc", "(3) H3: Non-Military"),
  Estimate = c(h1_estimate, h2_coef["Estimate"], h3_coef["Estimate"]),
  Std_Error = c(h1_se, h2_coef["Cluster s.e."], h3_coef["Cluster s.e."]),
  p_value = c(h1_pval, h2_coef["Pr(>|t|)"], h3_coef["Pr(>|t|)"]),
  Bandwidth = c(h1_bw, results_h2$optimal_bw_placebo, results_align$optimal_bw_placebo_nonmil),
  N = c(h1_n, nobs(placebo_h2), nobs(placebo_h3))
)

note_placebo <- "Placebo tests using December 7, 2021 (Putin's announcement) as a false treatment date. Data restricted to pre-invasion period (before Feb 19, 2022). Model 1 uses rdrobust; Models 2-3 use felm with optimal bandwidth. Non-significant treatment effects suggest parallel trends assumption holds."
note_placebo_wrapped <- str_wrap(note_placebo, width = 80)

table_placebo <- placebo_summary %>%
  mutate(
    Estimate_fmt = sprintf("%.3f%s", Estimate,
                     case_when(p_value < 0.001 ~ "***",
                               p_value < 0.01 ~ "**",
                               p_value < 0.05 ~ "*",
                               TRUE ~ "")),
    Std_Error_fmt = sprintf("(%.3f)", Std_Error),
    p_value_fmt = sprintf("%.3f", p_value),
    Bandwidth_fmt = sprintf("%.1f", Bandwidth),
    N_fmt = format(N, big.mark = ",")
  ) %>%
  select(Model, Estimate_fmt, Std_Error_fmt, p_value_fmt, Bandwidth_fmt, N_fmt) %>%
  gt() %>%
  cols_label(
    Model = "Model",
    Estimate_fmt = "Estimate",
    Std_Error_fmt = "Std. Error",
    p_value_fmt = "p-value",
    Bandwidth_fmt = "Bandwidth",
    N_fmt = "N"
  ) %>%
  tab_header(title = "Table S22: Placebo Test Summary (December 7, 2021)") %>%
  tab_footnote(footnote = note_placebo_wrapped)

table_placebo

save_table(table_placebo, "table_s22_placebo_summary")
```

# Session Info

```{r session-info}
print_session_info()
```
