---
title: "09 - Bandwidth Sensitivity Analysis"
author: "Donald Moratz"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

# Overview

This script produces bandwidth sensitivity figures for each of the 4 hypotheses. For each hypothesis, the main model is re-estimated at 10 bandwidth values from 50% to 200% of the optimal bandwidth. The resulting coefficient estimates and 95% confidence intervals (analytic, cluster-robust) are plotted across bandwidths, with a vertical dashed line at the optimal.

**Hypotheses:**

- H1: Effect of invasion on sentiment (all topics, Z-score, rdrobust)
- H2: State vs independent media (non-mil, Z-score, feols interaction)
- H3a: CSTO vs neutral alignment (non-mil, Z-score, state media, feols interaction)
- H3b: Ethnic Russian population (non-mil, Z-score, state media, feols interaction)

**Outputs:**

- 4 figures saved to `FIGURES_TABLES/prob/` (probabilistic variant, primary)
- 4 figures saved to `FIGURES_TABLES/days/` (day running variable, robustness)
- Combined 2x2 figures for each variant

```{r setup, include=FALSE}
source("00_setup.R")
knitr::opts_chunk$set(fig.path = paste0(FIGURES_TABLES, "/"))
options(digits = 10)

set.seed(3184)
```

# Load Data

```{r load-data}
data <- readRDS(file.path(DATA_INTERMEDIATE, "02_cleaned_data.rds"))
data_non_ukraine <- readRDS(file.path(DATA_INTERMEDIATE, "02_data_non_ukraine.rds"))

data <- data %>% mutate(across(c(topic_clean, country, source_domain), as.factor))
data_non_ukraine <- data_non_ukraine %>% mutate(across(c(topic_clean, country, source_domain), as.factor))

cat("Full data:", nrow(data), "articles\n")
cat("Non-Ukraine data:", nrow(data_non_ukraine), "articles\n")

# Ensure output directories exist
dir.create(file.path(FIGURES_TABLES, "prob"), showWarnings = FALSE, recursive = TRUE)
dir.create(file.path(FIGURES_TABLES, "days"), showWarnings = FALSE, recursive = TRUE)
```

# Helper Functions

```{r helpers}
# Run feols at a given bandwidth and extract coefficient + CI
bw_sensitivity_feols <- function(data, running_var, bw, formula, coef_name) {
  d <- data %>% filter(abs(.data[[running_var]]) < bw)

  n_clusters <- length(unique(d$source_domain))
  if (nrow(d) < 50 || n_clusters < 3) {
    return(tibble(bandwidth = bw, estimate = NA_real_, se = NA_real_,
                  ci_lower = NA_real_, ci_upper = NA_real_,
                  n_obs = nrow(d), n_clusters = n_clusters))
  }

  m <- tryCatch(
    feols(as.formula(formula), cluster = ~source_domain, data = d),
    error = function(e) NULL
  )

  if (is.null(m) || !(coef_name %in% names(coef(m)))) {
    return(tibble(bandwidth = bw, estimate = NA_real_, se = NA_real_,
                  ci_lower = NA_real_, ci_upper = NA_real_,
                  n_obs = nrow(d), n_clusters = n_clusters))
  }

  coef_val <- coef(m)[coef_name]
  se_val <- se(m)[coef_name]

  tibble(
    bandwidth = bw,
    estimate = coef_val,
    se = se_val,
    ci_lower = coef_val - 1.96 * se_val,
    ci_upper = coef_val + 1.96 * se_val,
    n_obs = nrow(d),
    n_clusters = n_clusters
  )
}

# Run rdrobust at a given bandwidth and extract coefficient + CI
bw_sensitivity_rdrobust <- function(y, x, cluster, bw, covs = NULL) {
  m <- tryCatch(
    rdrobust(y = y, x = x, h = bw, cluster = cluster, covs = covs),
    error = function(e) NULL
  )

  if (is.null(m)) {
    return(tibble(bandwidth = bw, estimate = NA_real_, se = NA_real_,
                  ci_lower = NA_real_, ci_upper = NA_real_))
  }

  tibble(
    bandwidth = bw,
    estimate = m$coef[1],
    se = m$se[1],
    ci_lower = m$ci[1, 1],
    ci_upper = m$ci[1, 2]
  )
}

# Plotting function
plot_bw_sensitivity <- function(results, optimal_bw, title, subtitle = NULL) {
  results %>%
    filter(!is.na(estimate)) %>%
    ggplot(aes(x = bandwidth, y = estimate)) +
    geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.2, fill = "steelblue") +
    geom_line(color = "steelblue", linewidth = 0.8) +
    geom_point(color = "steelblue", size = 2) +
    geom_vline(xintercept = optimal_bw, linetype = "dashed", color = "red", alpha = 0.7) +
    geom_hline(yintercept = 0, linetype = "solid", color = "grey50", alpha = 0.5) +
    annotate("text", x = optimal_bw, y = Inf, label = "Optimal BW",
             vjust = 2, hjust = -0.1, color = "red", size = 3) +
    theme_classic() +
    labs(
      title = title,
      subtitle = subtitle,
      x = "Bandwidth (days)",
      y = "Coefficient Estimate"
    )
}
```

# ============================================================================
# PROBABILISTIC VARIANT (Primary)
# ============================================================================

# H1: Effect of Invasion on Sentiment (Probabilistic)

```{r h1-prob-data}
# H1 uses data_non_ukraine, all topics, Z-score DV, rdrobust
# Following 04C_main_rdd_analysis_prob.Rmd

h1_data_prob <- data_non_ukraine %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                   sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()

# Convert running variable to days for consistent units
h1_data_prob <- h1_data_prob %>%
  mutate(running_prob_days = running_probabilistic / 86400)

# Covariates: topic FEs (matching model5_opt in 04C)
covs_h1_prob <- model.matrix(~ topic_clean - 1, data = h1_data_prob)

# Get optimal bandwidth: run rdrobust once to get its selected bandwidth
rd_h1_prob <- rdrobust(
  y = h1_data_prob$sentiment_z,
  x = h1_data_prob$running_prob_days,
  covs = covs_h1_prob,
  cluster = h1_data_prob$source_domain
)

optimal_bw_h1_prob <- rd_h1_prob$bws[1, 1]
cat("H1 optimal bandwidth (prob, days):", round(optimal_bw_h1_prob, 2), "\n")
```

```{r h1-prob-sensitivity}
bw_grid_h1_prob <- seq(0.5 * optimal_bw_h1_prob, 2 * optimal_bw_h1_prob, length.out = 10)

results_bw_h1_prob <- map_df(bw_grid_h1_prob, function(h) {
  bw_sensitivity_rdrobust(
    y = h1_data_prob$sentiment_z,
    x = h1_data_prob$running_prob_days,
    cluster = h1_data_prob$source_domain,
    bw = h,
    covs = covs_h1_prob
  )
})

cat("H1 sensitivity results:\n")
print(results_bw_h1_prob)
```

```{r h1-prob-plot, fig.width=8, fig.height=5}
p_h1_prob <- plot_bw_sensitivity(
  results_bw_h1_prob, optimal_bw_h1_prob,
  title = "H1: Bandwidth Sensitivity — Effect of Invasion on Sentiment",
  subtitle = "Probabilistic Time Assignment"
)

p_h1_prob
ggsave(file.path(FIGURES_TABLES, "prob", "bw_sensitivity_h1.png"),
       p_h1_prob, width = 8, height = 5)
```

# H2: State vs Independent Media (Probabilistic)

```{r h2-prob-data}
# H2 uses data_non_ukraine, non-mil, Z-score, feols interaction
# Following 05C_diff_in_disc_analysis_prob.Rmd

h2_data_prob <- data_non_ukraine %>%
  drop_na() %>%
  droplevels()

# Convert running variable to days
h2_data_prob <- h2_data_prob %>%
  mutate(running_probabilistic = running_probabilistic / 86400)

# Filter to non-military topics
h2_data_non_mil_prob <- h2_data_prob %>%
  filter(!topic_clean %in% c("Military"))

# Recompute Z-score on non-mil subset (matching 05C pattern)
h2_data_non_mil_prob <- h2_data_non_mil_prob %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                   sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()

# Compute optimal bandwidth via rdbwselect (residualized, matching 05C)
resid_y_h2 <- feols(sentiment_z ~ 1 | topic_clean + state_owned,
                     data = h2_data_non_mil_prob)$residuals

bw_h2_prob <- rdbwselect(y = resid_y_h2,
                          x = h2_data_non_mil_prob$running_probabilistic,
                          kernel = "triangular",
                          cluster = h2_data_non_mil_prob$source_domain,
                          p = 1,
                          bwselect = "mserd")

optimal_bw_h2_prob <- bw_h2_prob$bws[1, 1]
cat("H2 optimal bandwidth (prob, non-mil Z-score, days):", round(optimal_bw_h2_prob, 2), "\n")
```

```{r h2-prob-sensitivity}
bw_grid_h2_prob <- seq(0.5 * optimal_bw_h2_prob, 2 * optimal_bw_h2_prob, length.out = 10)

results_bw_h2_prob <- map_df(bw_grid_h2_prob, function(h) {
  bw_sensitivity_feols(
    data = h2_data_non_mil_prob,
    running_var = "running_probabilistic",
    bw = h,
    formula = "sentiment_z ~ running_probabilistic * treatment * state_owned | topic_clean",
    coef_name = "treatment:state_owned"
  )
})

cat("H2 sensitivity results:\n")
print(results_bw_h2_prob)
```

```{r h2-prob-plot, fig.width=8, fig.height=5}
p_h2_prob <- plot_bw_sensitivity(
  results_bw_h2_prob, optimal_bw_h2_prob,
  title = "H2: Bandwidth Sensitivity — State vs. Independent Media",
  subtitle = "Non-Military Topics, Probabilistic Time"
)

p_h2_prob
ggsave(file.path(FIGURES_TABLES, "prob", "bw_sensitivity_h2.png"),
       p_h2_prob, width = 8, height = 5)
```

# H3a: CSTO vs Neutral Alignment (Probabilistic)

```{r h3a-prob-data}
# H3a uses full data filtered to non-NATO, state-owned, non-mil, Z-score
# Following 06C_russian_alignment_analysis_prob.Rmd

# Filter to non-NATO countries
data_align_prob <- data %>%
  filter(nato == 0) %>%
  drop_na()

# Filter to state-owned media and convert running variable to days
data_align_state_prob <- data_align_prob %>%
  filter(state_owned == 1) %>%
  mutate(source_domain = droplevels(source_domain)) %>%
  mutate(running_probabilistic = running_probabilistic / 86400)

# Filter to non-military topics
data_align_state_non_mil_prob <- data_align_state_prob %>%
  filter(!topic_clean %in% "Military")

# Recompute Z-score on non-mil subset (matching 06C)
data_align_state_non_mil_prob <- data_align_state_non_mil_prob %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                   sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()

# Compute optimal bandwidth (residualized, matching 06C non-mil Z-score section)
resid_y_h3a <- feols(sentiment_z ~ 1 | topic_clean + csto,
                      data = data_align_state_non_mil_prob)$residuals

bw_h3a_prob <- rdbwselect(y = resid_y_h3a,
                           x = data_align_state_non_mil_prob$running_probabilistic,
                           kernel = "triangular",
                           cluster = data_align_state_non_mil_prob$source_domain,
                           p = 1,
                           bwselect = "mserd")

optimal_bw_h3a_prob <- bw_h3a_prob$bws[1, 1]
cat("H3a optimal bandwidth (prob, non-mil Z-score, days):", round(optimal_bw_h3a_prob, 2), "\n")
```

```{r h3a-prob-sensitivity}
bw_grid_h3a_prob <- seq(0.5 * optimal_bw_h3a_prob, 2 * optimal_bw_h3a_prob, length.out = 10)

results_bw_h3a_prob <- map_df(bw_grid_h3a_prob, function(h) {
  bw_sensitivity_feols(
    data = data_align_state_non_mil_prob,
    running_var = "running_probabilistic",
    bw = h,
    formula = "sentiment_z ~ running_probabilistic * treatment * csto | topic_clean",
    coef_name = "treatment:csto"
  )
})

cat("H3a sensitivity results:\n")
print(results_bw_h3a_prob)
```

```{r h3a-prob-plot, fig.width=8, fig.height=5}
p_h3a_prob <- plot_bw_sensitivity(
  results_bw_h3a_prob, optimal_bw_h3a_prob,
  title = "H3a: Bandwidth Sensitivity — CSTO vs. Neutral Alignment",
  subtitle = "Non-Military Topics, State Media, Probabilistic Time"
)

p_h3a_prob
ggsave(file.path(FIGURES_TABLES, "prob", "bw_sensitivity_h3a.png"),
       p_h3a_prob, width = 8, height = 5)
```

# H3b: Ethnic Russian Population (Probabilistic)

```{r h3b-prob-data}
# H3b uses full data filtered to non-NATO, state-owned, non-mil, Z-score
# Following 07C_ethnic_russian_analysis_prob.Rmd

# Filter to non-NATO countries
data_ethnic_prob <- data %>%
  filter(nato == 0)

# Filter to state-owned media and convert running variable to days
data_ethnic_state_prob <- data_ethnic_prob %>%
  filter(state_owned == 1) %>%
  mutate(source_domain = droplevels(source_domain)) %>%
  mutate(running_probabilistic = running_probabilistic / 86400)

# Filter to non-military topics
data_ethnic_state_non_mil_prob <- data_ethnic_state_prob %>%
  filter(!topic_clean %in% "Military")

# Recompute Z-score on non-mil subset (matching 07C)
data_ethnic_state_non_mil_prob <- data_ethnic_state_non_mil_prob %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                   sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()

# Compute optimal bandwidth (residualized, matching 07C non-mil Z-score section)
resid_y_h3b <- feols(sentiment_z ~ 1 | topic_clean + high_russia,
                      data = data_ethnic_state_non_mil_prob)$residuals

bw_h3b_prob <- rdbwselect(y = resid_y_h3b,
                           x = data_ethnic_state_non_mil_prob$running_probabilistic,
                           kernel = "triangular",
                           cluster = data_ethnic_state_non_mil_prob$source_domain,
                           p = 1,
                           bwselect = "mserd")

optimal_bw_h3b_prob <- bw_h3b_prob$bws[1, 1]
cat("H3b optimal bandwidth (prob, non-mil Z-score, days):", round(optimal_bw_h3b_prob, 2), "\n")
```

```{r h3b-prob-sensitivity}
bw_grid_h3b_prob <- seq(0.5 * optimal_bw_h3b_prob, 2 * optimal_bw_h3b_prob, length.out = 10)

results_bw_h3b_prob <- map_df(bw_grid_h3b_prob, function(h) {
  bw_sensitivity_feols(
    data = data_ethnic_state_non_mil_prob,
    running_var = "running_probabilistic",
    bw = h,
    formula = "sentiment_z ~ running_probabilistic * treatment * high_russia | topic_clean",
    coef_name = "treatment:high_russia"
  )
})

cat("H3b sensitivity results:\n")
print(results_bw_h3b_prob)
```

```{r h3b-prob-plot, fig.width=8, fig.height=5}
p_h3b_prob <- plot_bw_sensitivity(
  results_bw_h3b_prob, optimal_bw_h3b_prob,
  title = "H3b: Bandwidth Sensitivity — Ethnic Russian Population",
  subtitle = "Non-Military Topics, State Media, Probabilistic Time"
)

p_h3b_prob
ggsave(file.path(FIGURES_TABLES, "prob", "bw_sensitivity_h3b.png"),
       p_h3b_prob, width = 8, height = 5)
```

# Combined Figure (Probabilistic)

```{r combined-prob, fig.width=14, fig.height=10}
combined_prob <- (p_h1_prob + p_h2_prob) / (p_h3a_prob + p_h3b_prob) +
  plot_annotation(title = "Bandwidth Sensitivity Analysis (Probabilistic Time Assignment)")

combined_prob
ggsave(file.path(FIGURES_TABLES, "prob", "bw_sensitivity_combined.png"),
       combined_prob, width = 14, height = 10)
```

# ============================================================================
# DAYS VARIANT (Robustness)
# ============================================================================

# H1: Effect of Invasion on Sentiment (Days)

```{r h1-days-data}
# H1 days: uses data_non_ukraine with `running` variable (already in days)
# Following 04_main_rdd_analysis.Rmd

h1_data_days <- data_non_ukraine %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                   sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()

covs_h1_days <- model.matrix(~ topic_clean - 1, data = h1_data_days)

rd_h1_days <- rdrobust(
  y = h1_data_days$sentiment_z,
  x = h1_data_days$running,
  covs = covs_h1_days,
  cluster = h1_data_days$source_domain
)

optimal_bw_h1_days <- rd_h1_days$bws[1, 1]
cat("H1 optimal bandwidth (days):", round(optimal_bw_h1_days, 2), "\n")
```

```{r h1-days-sensitivity}
bw_grid_h1_days <- seq(0.5 * optimal_bw_h1_days, 2 * optimal_bw_h1_days, length.out = 10)

results_bw_h1_days <- map_df(bw_grid_h1_days, function(h) {
  bw_sensitivity_rdrobust(
    y = h1_data_days$sentiment_z,
    x = h1_data_days$running,
    cluster = h1_data_days$source_domain,
    bw = h,
    covs = covs_h1_days
  )
})

cat("H1 days sensitivity results:\n")
print(results_bw_h1_days)
```

```{r h1-days-plot, fig.width=8, fig.height=5}
p_h1_days <- plot_bw_sensitivity(
  results_bw_h1_days, optimal_bw_h1_days,
  title = "H1: Bandwidth Sensitivity — Effect of Invasion on Sentiment",
  subtitle = "Day Running Variable"
)

p_h1_days
ggsave(file.path(FIGURES_TABLES, "days", "bw_sensitivity_h1.png"),
       p_h1_days, width = 8, height = 5)
```

# H2: State vs Independent Media (Days)

```{r h2-days-data}
# Following 05_diff_in_disc_analysis.Rmd (days variant)

h2_data_days <- data_non_ukraine %>%
  drop_na() %>%
  droplevels()

# Z-score on full data first, then filter
h2_data_days <- h2_data_days %>%
  group_by(source_domain) %>%
  filter(sd(sentiment_clean, na.rm = TRUE) > 0) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                       sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup() %>%
  droplevels()

# Filter to non-military
h2_data_non_mil_days <- h2_data_days %>%
  filter(!topic_clean %in% c("Military"))

# Recompute Z-score on non-mil subset
h2_data_non_mil_days <- h2_data_non_mil_days %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                   sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()

# Compute optimal bandwidth
resid_y_h2_days <- feols(sentiment_z ~ 1 | topic_clean + state_owned,
                          data = h2_data_non_mil_days)$residuals

bw_h2_days <- rdbwselect(y = resid_y_h2_days,
                          x = h2_data_non_mil_days$running,
                          kernel = "triangular",
                          cluster = h2_data_non_mil_days$source_domain,
                          p = 1,
                          bwselect = "mserd")

optimal_bw_h2_days <- bw_h2_days$bws[1, 1]
cat("H2 optimal bandwidth (days, non-mil Z-score):", round(optimal_bw_h2_days, 2), "\n")
```

```{r h2-days-sensitivity}
bw_grid_h2_days <- seq(0.5 * optimal_bw_h2_days, 2 * optimal_bw_h2_days, length.out = 10)

results_bw_h2_days <- map_df(bw_grid_h2_days, function(h) {
  bw_sensitivity_feols(
    data = h2_data_non_mil_days,
    running_var = "running",
    bw = h,
    formula = "sentiment_z ~ running * treatment * state_owned | topic_clean",
    coef_name = "treatment:state_owned"
  )
})

cat("H2 days sensitivity results:\n")
print(results_bw_h2_days)
```

```{r h2-days-plot, fig.width=8, fig.height=5}
p_h2_days <- plot_bw_sensitivity(
  results_bw_h2_days, optimal_bw_h2_days,
  title = "H2: Bandwidth Sensitivity — State vs. Independent Media",
  subtitle = "Non-Military Topics, Day Running Variable"
)

p_h2_days
ggsave(file.path(FIGURES_TABLES, "days", "bw_sensitivity_h2.png"),
       p_h2_days, width = 8, height = 5)
```

# H3a: CSTO vs Neutral Alignment (Days)

```{r h3a-days-data}
# Following 06_russian_alignment_analysis.Rmd (days variant)

data_align_days <- data %>%
  filter(nato == 0) %>%
  drop_na()

data_align_state_days <- data_align_days %>%
  filter(state_owned == 1) %>%
  mutate(source_domain = droplevels(source_domain))

# Filter to non-military
data_align_state_non_mil_days <- data_align_state_days %>%
  filter(!topic_clean %in% "Military")

# Recompute Z-score on non-mil subset
data_align_state_non_mil_days <- data_align_state_non_mil_days %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                   sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()

# Compute optimal bandwidth
resid_y_h3a_days <- feols(sentiment_z ~ 1 | topic_clean + csto,
                           data = data_align_state_non_mil_days)$residuals

bw_h3a_days <- rdbwselect(y = resid_y_h3a_days,
                           x = data_align_state_non_mil_days$running,
                           kernel = "triangular",
                           cluster = data_align_state_non_mil_days$source_domain,
                           p = 1,
                           bwselect = "mserd")

optimal_bw_h3a_days <- bw_h3a_days$bws[1, 1]
cat("H3a optimal bandwidth (days, non-mil Z-score):", round(optimal_bw_h3a_days, 2), "\n")
```

```{r h3a-days-sensitivity}
bw_grid_h3a_days <- seq(0.5 * optimal_bw_h3a_days, 2 * optimal_bw_h3a_days, length.out = 10)

results_bw_h3a_days <- map_df(bw_grid_h3a_days, function(h) {
  bw_sensitivity_feols(
    data = data_align_state_non_mil_days,
    running_var = "running",
    bw = h,
    formula = "sentiment_z ~ running * treatment * csto | topic_clean",
    coef_name = "treatment:csto"
  )
})

cat("H3a days sensitivity results:\n")
print(results_bw_h3a_days)
```

```{r h3a-days-plot, fig.width=8, fig.height=5}
p_h3a_days <- plot_bw_sensitivity(
  results_bw_h3a_days, optimal_bw_h3a_days,
  title = "H3a: Bandwidth Sensitivity — CSTO vs. Neutral Alignment",
  subtitle = "Non-Military Topics, State Media, Day Running Variable"
)

p_h3a_days
ggsave(file.path(FIGURES_TABLES, "days", "bw_sensitivity_h3a.png"),
       p_h3a_days, width = 8, height = 5)
```

# H3b: Ethnic Russian Population (Days)

```{r h3b-days-data}
# Following 07_ethnic_russian_analysis.Rmd (days variant)

data_ethnic_days <- data %>%
  filter(nato == 0)

data_ethnic_state_days <- data_ethnic_days %>%
  filter(state_owned == 1) %>%
  mutate(source_domain = droplevels(source_domain))

# Filter to non-military
data_ethnic_state_non_mil_days <- data_ethnic_state_days %>%
  filter(!topic_clean %in% "Military")

# Recompute Z-score on non-mil subset
data_ethnic_state_non_mil_days <- data_ethnic_state_non_mil_days %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
                   sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()

# Compute optimal bandwidth
resid_y_h3b_days <- feols(sentiment_z ~ 1 | topic_clean + high_russia,
                           data = data_ethnic_state_non_mil_days)$residuals

bw_h3b_days <- rdbwselect(y = resid_y_h3b_days,
                           x = data_ethnic_state_non_mil_days$running,
                           kernel = "triangular",
                           cluster = data_ethnic_state_non_mil_days$source_domain,
                           p = 1,
                           bwselect = "mserd")

optimal_bw_h3b_days <- bw_h3b_days$bws[1, 1]
cat("H3b optimal bandwidth (days, non-mil Z-score):", round(optimal_bw_h3b_days, 2), "\n")
```

```{r h3b-days-sensitivity}
bw_grid_h3b_days <- seq(0.5 * optimal_bw_h3b_days, 2 * optimal_bw_h3b_days, length.out = 10)

results_bw_h3b_days <- map_df(bw_grid_h3b_days, function(h) {
  bw_sensitivity_feols(
    data = data_ethnic_state_non_mil_days,
    running_var = "running",
    bw = h,
    formula = "sentiment_z ~ running * treatment * high_russia | topic_clean",
    coef_name = "treatment:high_russia"
  )
})

cat("H3b days sensitivity results:\n")
print(results_bw_h3b_days)
```

```{r h3b-days-plot, fig.width=8, fig.height=5}
p_h3b_days <- plot_bw_sensitivity(
  results_bw_h3b_days, optimal_bw_h3b_days,
  title = "H3b: Bandwidth Sensitivity — Ethnic Russian Population",
  subtitle = "Non-Military Topics, State Media, Day Running Variable"
)

p_h3b_days
ggsave(file.path(FIGURES_TABLES, "days", "bw_sensitivity_h3b.png"),
       p_h3b_days, width = 8, height = 5)
```

# Combined Figure (Days)

```{r combined-days, fig.width=14, fig.height=10}
combined_days <- (p_h1_days + p_h2_days) / (p_h3a_days + p_h3b_days) +
  plot_annotation(title = "Bandwidth Sensitivity Analysis (Day Running Variable)")

combined_days
ggsave(file.path(FIGURES_TABLES, "days", "bw_sensitivity_combined.png"),
       combined_days, width = 14, height = 10)
```

# Session Info

```{r session-info}
print_session_info()
```
