---
title: "09 - Pre-Period Adjustment Diagnostics (Probabilistic Time Assignment)"
author: "Donald Moratz"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

# Overview

This script asks whether the two normalizations the baseline models rely on --
the pooled topic fixed effects and the full-window source-level z-score -- are
doing work that a pre-invasion-only version of the same adjustment would not do.
Both normalizations are estimated using data from *both* sides of the cutoff. If
the invasion changed what a given topic label means, or changed a source's
sentiment distribution, then an adjustment fitted across the cutoff partly
absorbs the treatment effect itself. Freezing each adjustment at its pre-invasion
value and re-running the baseline specifications is the cleanest way to see how
much that matters.

All estimation machinery here is **copied** from the three hypothesis scripts --
`04a_main_rdd_analysis_prob.Rmd`, `05a_diff_in_disc_analysis_prob.Rmd`, and
`06a_russian_alignment_analysis_prob.Rmd`. Nothing is re-derived. Every copied
block names its source file and chunk in a comment. Only the outcome variable and
the fixed-effect structure change, and only where a diagnostic requires it.

**What in here is a paper output, and what is not.** This script is a registered
pipeline step, running after `08_bandwidth_sensitivity.Rmd` and before the
`10{a,b,d}` publication scripts. Its role is split:

- **Sections 1-3 are author diagnostics.** They exist so the effect of each
  normalization can be inspected; nothing in them is destined for the manuscript.
  Their output goes to `output/diagnostics/` as CSV and text.
- **Section 4 produces paper output.** It runs the pre-period variants against the
  two matched preferred models (Table 2 Model 6 and Table 4 Model 5) and serializes
  the fitted models to `09_preperiod_results_prob.rds`, which
  `10a_publication_outputs_prob.Rmd` reads to build appendix **table S15**.

**Baseline specifications under test** (read from code, not assumed). Note that
these are the full-sample, optimal-bandwidth columns, **not** the paper's main
H2 and H3a results: Table 2's main result is Model 5 and Table 4's is Model 4,
both of which omit military coverage. Section 4 covers the matched preferred
models separately.

| Hypothesis | Object | Reported as | Raw-scale sibling |
|---|---|---|---|
| H1 | `model5_opt` | Table 1, Model 5 | `model2_opt` (Table 1, Model 2) |
| H2 | `model2a_opt_z` | Table 2, Model 3 | `model2a_opt` (Table S3, Model 4) |
| H3a | `model5a_opt_z` | Table 4, Model 3 | `model5a_opt` (Table S7, Model 3) |

- **H1** -- `04a`, chunk `model5-optimal-prob`, heading "Model 5: Z-Score Model
  (Topic FE)". `rdrobust` of `sentiment_z` on `running_probabilistic`, topic
  dummies passed as `covs`, clustered on `source_domain`, fitted on
  `optimal_bandwidth_data`, which `04a` sets equal to `data_non_ukraine` (all
  topics, military included) because `rdrobust` selects its own bandwidth.
- **H2** -- `05a`, chunk `model2a-opt-prob-z`. Residualize `sentiment_z` on
  `topic_clean + state_owned`, select a bandwidth with `rdbwselect`
  (triangular, `p = 1`, `mserd`, clustered on `source_domain`), filter to that
  bandwidth, then `feols(sentiment_z ~ running_probabilistic * treatment *
  state_owned | topic_clean)`. Coefficient of interest: `treatment:state_owned`.
- **H3a** -- `06a`, chunk `align-optimal-prob-z`. Same procedure on
  `data_align_state` (non-NATO, state-owned), residualizing on
  `topic_clean + csto` and interacting with `csto`. Coefficient of interest:
  `treatment:csto`.

**Sections:**

1. Topic adjustment fixed at pre-invasion values.
2. Pre-period-only z-scoring.
3. Topic-mapping diagnostic (pre-period topic means vs. pooled topic FE).

**Inputs:**

- `data/intermediate/02_data_non_ukraine.rds`
- `data/intermediate/02_cleaned_data.rds`

**Outputs** (all under `output/diagnostics/`):

- `preperiod_topic_demeaned_comparison.csv`
- `preperiod_zscore_comparison.csv`
- `preperiod_zscore_dropped_sources.csv`
- `topic_mapping_diagnostic.csv`
- `preperiod_diagnostics_summary.txt`

The wild cluster bootstrap runs at the repository default of `B = 4999`; it was
**not** reduced for these diagnostics.

```{r setup-diag, include=FALSE}
source("00_setup.R")
options(digits = 10)

set.seed(3184)
```

# Setup

## Output Directory

These are author diagnostics rather than paper outputs, so they land in
`output/diagnostics/` rather than under `figures/`. The directory is created the
same way `08_bandwidth_sensitivity.Rmd` creates its output subdirectories.

```{r diag-outdir}
# Following 08_bandwidth_sensitivity.Rmd, chunk `load-data`
OUTPUT_DIAGNOSTICS <- file.path(PROJECT_ROOT, "output", "diagnostics")
dir.create(OUTPUT_DIAGNOSTICS, showWarnings = FALSE, recursive = TRUE)

# Wild cluster bootstrap replications. This is the repository default from
# 00_setup.R (`run_wild_bootstrap`); it is NOT reduced for these diagnostics.
BOOT_B <- 4999


# Both RNG streams (base R and dqrng) are seeded in 00_setup.R; see the note
# there on why fwildclusterboot needs dqrng seeded separately.
cat("Diagnostics directory:", OUTPUT_DIAGNOSTICS, "\n")
cat("Wild cluster bootstrap B:", BOOT_B, "\n")
```

# Load Data and Rebuild the Three Baseline Samples

Each hypothesis is fitted on a differently constructed sample, and the
constructions are not interchangeable: `04a` leaves the running variable in
seconds and does not drop incomplete rows, `05a` drops them and rescales to days,
and `06a` starts from the full cleaned data rather than the non-Ukraine file. The
three chunks below reproduce each pipeline exactly as its host script builds it,
so that every diagnostic is compared against a baseline estimate computed on the
identical sample.

## H1 Sample (from 04a)

`04a` loads `02_data_non_ukraine.rds` and adds a source-level z-score over the
full window. It leaves `running_probabilistic` in its raw units (seconds) and
does not convert columns to factors or drop incomplete rows, so bandwidths
reported for H1 below are in seconds.

```{r diag-sample-h1}
# Following 04a_main_rdd_analysis_prob.Rmd, chunks `load-prob`, `model1-Z-prob`
# and `optimal-bandwidth-prob` (which sets optimal_bandwidth_data <- data_non_ukraine)
h1_data <- readRDS(file.path(DATA_INTERMEDIATE, "02_data_non_ukraine.rds")) %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
           sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()

cat("H1 sample:", nrow(h1_data), "articles,",
    length(unique(h1_data$source_domain)), "sources\n")
cat("Running variable units: seconds (04a does not rescale)\n")
```

## H2 Sample (from 05a)

`05a` converts the grouping columns to factors, drops incomplete rows, keeps only
sources with non-degenerate sentiment variance, z-scores within source over the
full window, and rescales the running variable from seconds to days.

```{r diag-sample-h2}
# Following 05a_diff_in_disc_analysis_prob.Rmd, chunk `load-prob`
h2_data <- readRDS(file.path(DATA_INTERMEDIATE, "02_data_non_ukraine.rds")) %>%
  mutate(across(c("country", "source_domain", "topic_clean"), as.factor)) %>%
  drop_na() %>%
  droplevels() %>%
  group_by(source_domain) %>%
  filter(sd(sentiment_clean, na.rm = TRUE) > 0) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
           sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup() %>%
  droplevels() %>%
  mutate(running_probabilistic = running_probabilistic / 86400)

cat("H2 sample:", nrow(h2_data), "articles,",
    nlevels(h2_data$source_domain), "sources\n")
cat("State-owned:", sum(h2_data$state_owned),
    "| Independent:", sum(h2_data$state_owned == 0), "\n")
```

## H3a Sample (from 06a)

`06a` starts from the full cleaned data, restricts to non-NATO countries, drops
incomplete rows, keeps state-owned outlets only, rescales the running variable to
days, and z-scores within source over the full window. Ukraine is excluded
implicitly because it is a NATO country.

```{r diag-sample-h3}
# Following 06a_russian_alignment_analysis_prob.Rmd, chunks `load-prob`,
# `alignment-data-prob`, `align-diff-prob` and `align-diff-prob-z`
h3_data <- readRDS(file.path(DATA_INTERMEDIATE, "02_cleaned_data.rds")) %>%
  mutate(across(c(topic_clean, country, source_domain), as.factor)) %>%
  filter(nato == 0) %>%
  drop_na() %>%
  filter(state_owned == 1) %>%
  mutate(source_domain = droplevels(source_domain)) %>%
  mutate(running_probabilistic = running_probabilistic / 86400) %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
           sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()

cat("H3a sample:", nrow(h3_data), "articles,",
    nlevels(h3_data$source_domain), "sources\n")
cat("Russia-aligned:", sum(h3_data$csto),
    "| Neutral:", sum(h3_data$csto == 0), "\n")
```

## Definition of the Pre-Invasion Period

Every diagnostic below is built on a pre-invasion subsample, so it matters which
side of the cutoff each article is assigned to. The running variable
`running_probabilistic` is what the RD models actually use, so the pre-invasion
period here is defined as `running_probabilistic < 0` rather than by the
`treatment` dummy. The two can disagree for articles published near midnight on
24 February 2022, because `treatment` is keyed to the publication *date* while
the probabilistic running variable is keyed to an imputed publication *time*.
This chunk reports how many articles disagree so the choice is auditable.

```{r diag-preperiod-def}
check_pre_definition <- function(d, label) {
  pre_by_running <- d$running_probabilistic < 0
  mismatch <- sum(pre_by_running != (d$treatment == 0), na.rm = TRUE)
  cat(sprintf("%-4s  pre-invasion articles: %6d | post: %6d | disagreements with `treatment`: %d\n",
              label, sum(pre_by_running), sum(!pre_by_running), mismatch))
  invisible(mismatch)
}

mismatch_h1 <- check_pre_definition(h1_data, "H1")
mismatch_h2 <- check_pre_definition(h2_data, "H2")
mismatch_h3 <- check_pre_definition(h3_data, "H3a")
```

# Estimation Machinery Copied from the Baseline Scripts

The three functions below are the baseline estimation routines, lifted verbatim
in structure from their source chunks and parameterised only over the outcome
variable and the fixed-effect terms. Parameterising rather than copy-pasting six
near-identical blocks is what keeps every diagnostic provably identical to its
baseline counterpart apart from the one thing the diagnostic changes.

## H1: rdrobust with Topic Dummies as Covariates

`04a` fits H1 with `rdrobust`, which performs its own MSE-optimal bandwidth
selection internally, so there is no separate `rdbwselect` step. Topic adjustment
enters through `covs`; setting `use_topic_covs = FALSE` removes it, which is what
Section 1 requires.

```{r diag-fit-h1}
# Following 04a_main_rdd_analysis_prob.Rmd, chunk `model5-optimal-prob`
fit_h1 <- function(d, yvar, use_topic_covs = TRUE) {
  covs_matrix <- if (use_topic_covs) {
    model.matrix(~ topic_clean - 1, data = d)
  } else {
    NULL
  }

  rdrobust(
    y = d[[yvar]],
    x = d$running_probabilistic,
    covs = covs_matrix,
    cluster = d$source_domain
  )
}
```

## H2: Residualize, Select Bandwidth, Filter, Estimate

`05a` residualizes the outcome on the model's fixed effects, hands those
residuals to `rdbwselect`, filters the sample to the selected bandwidth, and then
fits the triple-interaction `feols` model with a wild cluster bootstrap on the
interaction of interest. `resid_fe` and `model_fe` are separated so that Section 1
can drop `topic_clean` from *both* -- dropping it from the model but leaving it in
the bandwidth selection would produce a bandwidth chosen for a specification that
is no longer being fitted.

```{r diag-fit-h2}
# Following 05a_diff_in_disc_analysis_prob.Rmd, chunk `model2a-opt-prob-z`
fit_h2 <- function(d, yvar,
                   resid_fe = c("topic_clean", "state_owned"),
                   model_fe = "topic_clean") {

  # Residualize the dependent variable for fixed effects to do bandwidth selection
  resid_formula <- as.formula(paste0(yvar, " ~ 1 | ", paste(resid_fe, collapse = " + ")))
  resid_y <- feols(resid_formula, data = d)$residuals

  bw_select <- rdbwselect(y = resid_y,
                          x = d$running_probabilistic,
                          kernel = "triangular",
                          cluster = d$source_domain,
                          p = 1,
                          bwselect = "mserd")

  optimal_bw <- bw_select$bws[1, 1]

  optimal_bandwidth_data <- d %>%
    filter(running_probabilistic < optimal_bw, running_probabilistic > -optimal_bw) %>%
    droplevels()

  model_formula <- as.formula(paste0(
    yvar, " ~ running_probabilistic * treatment * state_owned",
    if (length(model_fe) > 0) paste0(" | ", paste(model_fe, collapse = " + ")) else ""
  ))

  model <- feols(model_formula,
                 cluster = ~source_domain,
                 data = optimal_bandwidth_data)

  boot <- safe_wild_bootstrap(model, "treatment:state_owned")

  list(model = model, boot = boot, bw = optimal_bw,
       data = optimal_bandwidth_data, coef_name = "treatment:state_owned")
}
```

## H3a: Same Procedure on the Russia-Aligned State-Media Sample

Structurally identical to H2, but residualizing on `csto` rather than
`state_owned` and interacting with `csto`. Note that `06a` does **not** call
`droplevels()` after the bandwidth filter; that is preserved here so the fixed
effect sets match the baseline exactly.

```{r diag-fit-h3}
# Following 06a_russian_alignment_analysis_prob.Rmd, chunk `align-optimal-prob-z`
fit_h3 <- function(d, yvar,
                   resid_fe = c("topic_clean", "csto"),
                   model_fe = "topic_clean") {

  # Residualize the dependent variable for fixed effects to do bandwidth selection
  resid_formula <- as.formula(paste0(yvar, " ~ 1 | ", paste(resid_fe, collapse = " + ")))
  resid_y <- feols(resid_formula, data = d)$residuals

  bw_align <- rdbwselect(y = resid_y,
                         x = d$running_probabilistic,
                         kernel = "triangular",
                         cluster = d$source_domain,
                         p = 1,
                         bwselect = "mserd")

  optimal_bw_align <- bw_align$bws[1, 1]

  optimal_bandwidth_data_state <- d %>%
    filter(running_probabilistic < optimal_bw_align,
           running_probabilistic > -optimal_bw_align)

  model_formula <- as.formula(paste0(
    yvar, " ~ running_probabilistic * treatment * csto",
    if (length(model_fe) > 0) paste0(" | ", paste(model_fe, collapse = " + ")) else ""
  ))

  model <- feols(model_formula,
                 cluster = ~source_domain,
                 data = optimal_bandwidth_data_state)

  boot <- safe_wild_bootstrap(model, "treatment:csto")

  list(model = model, boot = boot, bw = optimal_bw_align,
       data = optimal_bandwidth_data_state, coef_name = "treatment:csto")
}
```

## Bootstrap Wrapper and Result Tabulation

`run_wild_bootstrap()` comes from `00_setup.R` and is the same routine the
baseline chunks call. It is wrapped here only so that a bootstrap failure on one
diagnostic returns `NA` and is reported, rather than aborting the whole script and
losing the strands that did work. The two `row_*()` helpers put `rdrobust` and
`feols` results into one common shape so the comparison tables can be stacked.

```{r diag-tabulate}
# `run_wild_bootstrap` is defined in 00_setup.R and is called unchanged by the
# baseline chunks in 05a (`model2a-opt-prob-z`) and 06a (`align-optimal-prob-z`).
safe_wild_bootstrap <- function(model, param) {
  tryCatch(
    run_wild_bootstrap(model, param, B = BOOT_B),
    error = function(e) {
      message("  WILD BOOTSTRAP FAILED for '", param, "': ", conditionMessage(e))
      list(se = NA_real_, p_val = NA_real_,
           ci_lower = NA_real_, ci_upper = NA_real_)
    }
  )
}

# One tidy row from an rdrobust fit (H1 family)
row_rd <- function(m, d, section, spec, scale, outcome, fe_note) {
  bw <- m$bws[1, 1]
  in_bw <- abs(d$running_probabilistic) < bw
  tibble(
    section     = section,
    spec        = spec,
    scale       = scale,
    outcome     = outcome,
    estimator   = "rdrobust",
    term        = "RD treatment effect",
    fixed_effects = fe_note,
    estimate    = m$coef[1],
    std_error   = m$se[1],
    p_value     = m$pv[1],
    ci_lower    = m$ci[1, 1],
    ci_upper    = m$ci[1, 2],
    n_obs       = sum(m$N_h),
    bandwidth   = bw,
    n_clusters  = length(unique(as.character(d$source_domain[in_bw]))),
    boot_se     = NA_real_,
    boot_p      = NA_real_,
    boot_ci_lower = NA_real_,
    boot_ci_upper = NA_real_
  )
}

# One tidy row from a feols fit (H2 / H3a families)
row_fe <- function(fit, section, spec, scale, outcome, fe_note) {
  ct <- coeftable(fit$model)[fit$coef_name, ]
  tibble(
    section     = section,
    spec        = spec,
    scale       = scale,
    outcome     = outcome,
    estimator   = "feols",
    term        = fit$coef_name,
    fixed_effects = fe_note,
    estimate    = ct[["Estimate"]],
    std_error   = ct[["Std. Error"]],
    p_value     = ct[["Pr(>|t|)"]],
    ci_lower    = ct[["Estimate"]] - 1.96 * ct[["Std. Error"]],
    ci_upper    = ct[["Estimate"]] + 1.96 * ct[["Std. Error"]],
    n_obs       = fit$model$nobs,
    bandwidth   = fit$bw,
    n_clusters  = length(unique(as.character(fit$data$source_domain))),
    boot_se     = fit$boot$se,
    boot_p      = fit$boot$p_val,
    boot_ci_lower = fit$boot$ci_lower,
    boot_ci_upper = fit$boot$ci_upper
  )
}

# Compact printer used for every comparison table below
print_comparison <- function(tbl) {
  tbl %>%
    transmute(section, spec, scale, outcome,
              estimate = round(estimate, 4),
              se       = round(std_error, 4),
              p        = signif(p_value, 3),
              boot_p   = signif(boot_p, 3),
              n_obs,
              bandwidth = round(bandwidth, 2),
              n_clusters) %>%
    as.data.frame() %>%
    print(row.names = FALSE)
}
```

# Baseline Estimates (Baselines)

Nothing below can be interpreted without the baseline numbers recomputed on the
same samples, so they are estimated first. Two families are computed for each
hypothesis:

- the **z-score baseline** -- H1 `model5_opt` (Table 1, Model 5), H2
  `model2a_opt_z` (Table 2, Model 3), H3a `model5a_opt_z` (Table 4, Model 3); and
- the **raw-scale sibling** -- H1 `model2_opt` (Table 1, Model 2), H2
  `model2a_opt` (Table S3, Model 4), H3a `model5a_opt` (Table S7, Model 3),
  which is the same specification on `sentiment_clean`.

These are called *baselines* rather than main specifications on purpose. For H2
and H3a they are the full-sample optimal-bandwidth columns, whereas the paper's
main results are Table 2 Model 5 and Table 4 Model 4, which restrict the sample.
Sections 1-3 diagnose the normalizations on the full sample; Section 4 handles
the matched preferred models.

The raw-scale siblings exist here for one reason. Section 1 demeans
`sentiment_clean` by pre-invasion topic means, which produces an outcome in raw
sentiment units, while the named baseline outcomes are z-scores. Reporting the
raw-scale sibling alongside makes that comparison like-for-like instead of
comparing a raw-unit estimate to a z-unit one.

## Z-Score Baselines

```{r diag-baseline-z}
# H1: 04a chunk `model5-optimal-prob` -- Table 1, Model 5
h1_baseline_z <- fit_h1(h1_data, "sentiment_z", use_topic_covs = TRUE)
summary(h1_baseline_z)

# H2: 05a chunk `model2a-opt-prob-z` -- Table 2, Model 3
h2_baseline_z <- fit_h2(h2_data, "sentiment_z")
summary(h2_baseline_z$model)
cat("H2 bootstrap p-value for treatment:state_owned:", h2_baseline_z$boot$p_val, "\n")

# H3a: 06a chunk `align-optimal-prob-z` -- Table 4, Model 3
h3_baseline_z <- fit_h3(h3_data, "sentiment_z")
summary(h3_baseline_z$model)
cat("H3a bootstrap p-value for treatment:csto:", h3_baseline_z$boot$p_val, "\n")

baseline_z <- bind_rows(
  row_rd(h1_baseline_z, h1_data, "baseline", "H1",  "z-score", "sentiment_z",
         "topic dummies as rdrobust covs"),
  row_fe(h2_baseline_z, "baseline", "H2",  "z-score", "sentiment_z", "topic_clean FE"),
  row_fe(h3_baseline_z, "baseline", "H3a", "z-score", "sentiment_z", "topic_clean FE")
)

print_comparison(baseline_z)
```

## Raw-Scale Baseline Siblings

The raw-scale siblings use each host script's own raw-scale bandwidth
residualization, which includes `source_domain` where the z-score version does
not -- this is a genuine difference between the two baseline families in `05a`
and `06a`, not an edit.

```{r diag-baseline-raw}
# H1 raw sibling: 04a chunk `model2-optimal-prob` -- Table 1, Model 2
h1_baseline_raw <- fit_h1(h1_data, "sentiment_clean", use_topic_covs = TRUE)
summary(h1_baseline_raw)

# H2 raw sibling: 05a chunks `optimal-bw-prob` + `model2a-opt-prob` -- Table S3, Model 4
h2_baseline_raw <- fit_h2(h2_data, "sentiment_clean",
                          resid_fe = c("topic_clean", "source_domain", "state_owned"))
cat("H2 raw-scale bandwidth:", round(h2_baseline_raw$bw, 2), "days\n")

# H3a raw sibling: 06a chunk `align-optimal-prob` -- Table S7, Model 3
h3_baseline_raw <- fit_h3(h3_data, "sentiment_clean",
                          resid_fe = c("topic_clean", "source_domain", "csto"))
cat("H3a raw-scale bandwidth:", round(h3_baseline_raw$bw, 2), "days\n")

baseline_raw <- bind_rows(
  row_rd(h1_baseline_raw, h1_data, "baseline", "H1", "raw", "sentiment_clean",
         "topic dummies as rdrobust covs"),
  row_fe(h2_baseline_raw, "baseline", "H2",  "raw", "sentiment_clean", "topic_clean FE"),
  row_fe(h3_baseline_raw, "baseline", "H3a", "raw", "sentiment_clean", "topic_clean FE")
)

print_comparison(baseline_raw)
```

# Section 1: Topic Adjustment Fixed at Pre-Invasion Values

The baseline models adjust for topic with a pooled fixed effect (or, for H1, a
pooled dummy coefficient) estimated on articles from both sides of the cutoff. If
the invasion changed what a topic label *means* -- if, say, "Economic" coverage
after 24 February is a different kind of story than "Economic" coverage before --
then that pooled adjustment is partly absorbing the treatment effect rather than
netting out a fixed compositional difference.

The test freezes the adjustment. Each topic's mean is computed over the
pre-invasion period only and subtracted from every article carrying that topic,
post-invasion articles included. The topic fixed effect is then **removed** from
the specification, because the outcome already carries the adjustment. If the
pooled fixed effects were only netting out a stable compositional difference, the
estimate should barely move. If it moves, the topic adjustment is shifting across
the cutoff.

## Constructing the Pre-Invasion-Demeaned Outcomes

Both scales are constructed. `sentiment_tdm` is the literal instruction --
`sentiment_clean` minus its pre-invasion topic mean. `sentiment_z_tdm` applies the
same pre-invasion topic demeaning on the z-score scale, so that it can be compared
directly against the named z-score baseline without a unit change confounding the
comparison. Topic means are computed within each hypothesis's own estimation
sample, over the full window's pre-invasion articles.

```{r diag-s1-construct}
add_pre_topic_demean <- function(d, label) {
  pre_topic_means <- d %>%
    filter(running_probabilistic < 0) %>%
    group_by(topic_clean) %>%
    summarise(pre_topic_mean_raw = mean(sentiment_clean, na.rm = TRUE),
              pre_topic_mean_z   = mean(sentiment_z, na.rm = TRUE),
              n_pre              = n(),
              .groups = "drop")

  cat("\nPre-invasion topic means -", label, "\n")
  print(as.data.frame(pre_topic_means), row.names = FALSE)

  d %>%
    left_join(pre_topic_means, by = "topic_clean") %>%
    mutate(sentiment_tdm   = sentiment_clean - pre_topic_mean_raw,
           sentiment_z_tdm = sentiment_z - pre_topic_mean_z)
}

h1_s1 <- add_pre_topic_demean(h1_data,  "H1")
h2_s1 <- add_pre_topic_demean(h2_data,  "H2")
h3_s1 <- add_pre_topic_demean(h3_data,  "H3a")
```

## Re-Estimating H1/H2/H3a Without Topic Fixed Effects

Topic is dropped from the model and, for H2 and H3a, from the bandwidth-selection
residualization as well, so the bandwidth is chosen for the specification actually
being fitted. Everything else -- kernel, polynomial order, bandwidth selector,
clustering, bootstrap -- is unchanged from the baseline.

```{r diag-s1-estimate}
# H1: same rdrobust call as `model5-optimal-prob`, with `covs` dropped
h1_s1_z   <- fit_h1(h1_s1, "sentiment_z_tdm", use_topic_covs = FALSE)
h1_s1_raw <- fit_h1(h1_s1, "sentiment_tdm",   use_topic_covs = FALSE)

# H2: same procedure as `model2a-opt-prob-z`, with topic_clean removed throughout
h2_s1_z   <- fit_h2(h2_s1, "sentiment_z_tdm",
                    resid_fe = "state_owned", model_fe = character(0))
h2_s1_raw <- fit_h2(h2_s1, "sentiment_tdm",
                    resid_fe = c("source_domain", "state_owned"), model_fe = character(0))

# H3a: same procedure as `align-optimal-prob-z`, with topic_clean removed throughout
h3_s1_z   <- fit_h3(h3_s1, "sentiment_z_tdm",
                    resid_fe = "csto", model_fe = character(0))
h3_s1_raw <- fit_h3(h3_s1, "sentiment_tdm",
                    resid_fe = c("source_domain", "csto"), model_fe = character(0))

section1_estimates <- bind_rows(
  row_rd(h1_s1_z,  h1_s1, "s1_pre_topic_demeaned", "H1",  "z-score",
         "sentiment_z_tdm", "none (topic covs removed)"),
  row_fe(h2_s1_z,  "s1_pre_topic_demeaned", "H2",  "z-score",
         "sentiment_z_tdm", "none (topic FE removed)"),
  row_fe(h3_s1_z,  "s1_pre_topic_demeaned", "H3a", "z-score",
         "sentiment_z_tdm", "none (topic FE removed)"),
  row_rd(h1_s1_raw, h1_s1, "s1_pre_topic_demeaned", "H1",  "raw",
         "sentiment_tdm", "none (topic covs removed)"),
  row_fe(h2_s1_raw, "s1_pre_topic_demeaned", "H2",  "raw",
         "sentiment_tdm", "none (topic FE removed)"),
  row_fe(h3_s1_raw, "s1_pre_topic_demeaned", "H3a", "raw",
         "sentiment_tdm", "none (topic FE removed)")
)

print_comparison(section1_estimates)
```

## Comparison Against the Baseline, and Write to Disk

Each diagnostic row is paired with the baseline row on the same scale, and the
absolute and relative shifts in the point estimate are reported. `pct_change` is
the shift expressed as a share of the baseline estimate; for H2, whose baseline
estimate is small and statistically indistinguishable from zero, that percentage
is volatile and the absolute shift is the more informative column.

```{r diag-s1-compare}
build_comparison <- function(diagnostic, baseline) {
  baseline_keys <- baseline %>%
    select(spec, scale,
           baseline_estimate = estimate,
           baseline_se       = std_error,
           baseline_p        = p_value,
           baseline_boot_p   = boot_p,
           baseline_n_obs    = n_obs,
           baseline_bandwidth = bandwidth)

  diagnostic %>%
    left_join(baseline_keys, by = c("spec", "scale")) %>%
    mutate(
      abs_change = estimate - baseline_estimate,
      pct_change = 100 * (estimate - baseline_estimate) / baseline_estimate,
      se_ratio   = std_error / baseline_se,
      # how far the diagnostic estimate sits from the baseline in baseline SEs
      shift_in_baseline_ses = (estimate - baseline_estimate) / baseline_se
    )
}

section1_comparison <- build_comparison(
  section1_estimates,
  bind_rows(baseline_z, baseline_raw)
)

section1_comparison %>%
  transmute(spec, scale,
            baseline = round(baseline_estimate, 4),
            diagnostic = round(estimate, 4),
            abs_change = round(abs_change, 4),
            pct_change = round(pct_change, 1),
            shift_in_baseline_ses = round(shift_in_baseline_ses, 3),
            baseline_p = signif(baseline_p, 3),
            diagnostic_p = signif(p_value, 3)) %>%
  as.data.frame() %>%
  print(row.names = FALSE)

write_csv(section1_comparison,
          file.path(OUTPUT_DIAGNOSTICS, "preperiod_topic_demeaned_comparison.csv"))
cat("\nWrote:", file.path(OUTPUT_DIAGNOSTICS, "preperiod_topic_demeaned_comparison.csv"), "\n")
```

# Section 2: Pre-Period-Only Z-Scoring

The baseline outcome is a source-level z-score computed over the full window. Its
mean and standard deviation are therefore themselves functions of the invasion:
a source whose sentiment collapsed after 24 February has a lower full-window mean
and a larger full-window standard deviation than it had before, so the z-score
shrinks the very movement being measured.

This section re-standardizes using **pre-invasion** source means and standard
deviations only, applied to the whole window, and re-runs the baseline
specifications with the topic fixed effects kept exactly as in the baseline. The
mechanical expectation is that the pre-period standard deviation is smaller than
the full-window one, so estimates should grow in magnitude somewhat; what matters
is whether they grow modestly or dramatically.

## Re-Standardizing on Pre-Invasion Moments

Sources with no pre-invasion articles, or with zero or undefined pre-invasion
sentiment variance, cannot be standardized this way and are dropped. The dropped
sources are counted, listed, and written to their own CSV so the sample change is
visible rather than silent.

```{r diag-s2-construct}
add_pre_period_z <- function(d, label) {
  all_sources <- unique(as.character(d$source_domain))

  pre_moments <- d %>%
    filter(running_probabilistic < 0) %>%
    group_by(source_domain) %>%
    summarise(pre_mean = mean(sentiment_clean, na.rm = TRUE),
              pre_sd   = sd(sentiment_clean, na.rm = TRUE),
              n_pre    = n(),
              .groups  = "drop")

  keep <- pre_moments %>% filter(!is.na(pre_sd), pre_sd > 0)

  dropped <- tibble(
    spec          = label,
    source_domain = setdiff(all_sources, as.character(keep$source_domain))
  ) %>%
    left_join(pre_moments %>% mutate(source_domain = as.character(source_domain)),
              by = "source_domain") %>%
    mutate(reason = case_when(
      is.na(n_pre)            ~ "no pre-invasion articles",
      is.na(pre_sd)           ~ "pre-invasion SD undefined (single article)",
      pre_sd <= 0             ~ "pre-invasion SD is zero",
      TRUE                    ~ "unknown"
    ))

  cat(sprintf("%-4s  sources: %d total | %d with pre-invasion articles | %d retained | %d dropped\n",
              label, length(all_sources), nrow(pre_moments), nrow(keep), nrow(dropped)))
  if (nrow(dropped) > 0) {
    print(as.data.frame(dropped %>% select(source_domain, n_pre, pre_sd, reason)),
          row.names = FALSE)
  }

  out <- d %>%
    inner_join(keep, by = "source_domain") %>%
    mutate(sentiment_z_pre = (sentiment_clean - pre_mean) / pre_sd) %>%
    droplevels()

  list(data = out, dropped = dropped)
}

h1_s2 <- add_pre_period_z(h1_data, "H1")
h2_s2 <- add_pre_period_z(h2_data, "H2")
h3_s2 <- add_pre_period_z(h3_data, "H3a")

dropped_sources <- bind_rows(h1_s2$dropped, h2_s2$dropped, h3_s2$dropped)

write_csv(dropped_sources,
          file.path(OUTPUT_DIAGNOSTICS, "preperiod_zscore_dropped_sources.csv"))
cat("\nWrote:", file.path(OUTPUT_DIAGNOSTICS, "preperiod_zscore_dropped_sources.csv"), "\n")
```

## Re-Estimating H1/H2/H3a on the Pre-Period Z-Score

The specification is otherwise untouched: topic dummies stay in the H1 `covs`
matrix and topic fixed effects stay in the H2 and H3a models, exactly as in the
baseline.

```{r diag-s2-estimate}
# H1: 04a chunk `model5-optimal-prob`, outcome swapped for the pre-period z-score
h1_s2_fit <- fit_h1(h1_s2$data, "sentiment_z_pre", use_topic_covs = TRUE)
summary(h1_s2_fit)

# H2: 05a chunk `model2a-opt-prob-z`, outcome swapped
h2_s2_fit <- fit_h2(h2_s2$data, "sentiment_z_pre")
summary(h2_s2_fit$model)
cat("H2 bootstrap p-value for treatment:state_owned:", h2_s2_fit$boot$p_val, "\n")

# H3a: 06a chunk `align-optimal-prob-z`, outcome swapped
h3_s2_fit <- fit_h3(h3_s2$data, "sentiment_z_pre")
summary(h3_s2_fit$model)
cat("H3a bootstrap p-value for treatment:csto:", h3_s2_fit$boot$p_val, "\n")

section2_estimates <- bind_rows(
  row_rd(h1_s2_fit, h1_s2$data, "s2_pre_period_zscore", "H1",  "z-score",
         "sentiment_z_pre", "topic dummies as rdrobust covs"),
  row_fe(h2_s2_fit, "s2_pre_period_zscore", "H2",  "z-score",
         "sentiment_z_pre", "topic_clean FE"),
  row_fe(h3_s2_fit, "s2_pre_period_zscore", "H3a", "z-score",
         "sentiment_z_pre", "topic_clean FE")
)

print_comparison(section2_estimates)
```

## Comparison Against the Baseline, and Write to Disk

```{r diag-s2-compare}
section2_comparison <- build_comparison(section2_estimates, baseline_z) %>%
  left_join(
    dropped_sources %>% count(spec, name = "n_sources_dropped"),
    by = "spec"
  ) %>%
  mutate(n_sources_dropped = coalesce(n_sources_dropped, 0L))

section2_comparison %>%
  transmute(spec,
            baseline = round(baseline_estimate, 4),
            diagnostic = round(estimate, 4),
            abs_change = round(abs_change, 4),
            pct_change = round(pct_change, 1),
            se_ratio = round(se_ratio, 3),
            baseline_p = signif(baseline_p, 3),
            diagnostic_p = signif(p_value, 3),
            n_sources_dropped) %>%
  as.data.frame() %>%
  print(row.names = FALSE)

write_csv(section2_comparison,
          file.path(OUTPUT_DIAGNOSTICS, "preperiod_zscore_comparison.csv"))
cat("\nWrote:", file.path(OUTPUT_DIAGNOSTICS, "preperiod_zscore_comparison.csv"), "\n")
```

# Section 3: Topic-Mapping Diagnostic

Sections 1 and 2 report what happens to the estimates. This section reports
*why*: it puts each topic's pre-invasion mean next to the pooled topic fixed
effect the baseline model actually estimates, and next to that topic's
post-invasion mean, so it is visible which topics' mappings move across the
cutoff. A topic whose mean is stable across the cutoff is well described by a
single pooled fixed effect; a topic whose mean shifts is not, and it is those
topics that drive whatever movement Section 1 found.

## Extracting the Pooled Topic Fixed Effects

`fixest::fixef()` recovers the topic fixed effects from the H2 and H3a baseline
models. They are reported both raw and centred on their own mean, because the
level of a fixed effect is only identified up to the model intercept and only the
spread across topics is interpretable.

H1's baseline is an `rdrobust` fit, whose topic adjustment enters as `covs`
coefficients rather than fixed effects. `rdrobust` drops one dummy for
collinearity **without reporting which one**, so its `beta_covs` vector cannot be
reliably mapped back to topic names; it is printed below as an unlabelled
diagnostic only, and the topic-FE column of the output table is left `NA` for H1.

```{r diag-s3-fixef}
fe_h2 <- fixef(h2_baseline_z$model)$topic_clean
fe_h3 <- fixef(h3_baseline_z$model)$topic_clean

cat("H2 baseline topic fixed effects (model2a_opt_z):\n")
print(fe_h2)
cat("\nH3a baseline topic fixed effects (model5a_opt_z):\n")
print(fe_h3)

cat("\nH1 baseline rdrobust covariate coefficients (model5_opt), UNLABELLED:\n")
cat("rdrobust dropped", ncol(model.matrix(~ topic_clean - 1, data = h1_data)) -
      length(h1_baseline_z$beta_covs),
    "redundant topic dummy/dummies and does not report which, so these\n",
    "coefficients cannot be mapped to topic names. Reported for reference only.\n")
print(as.vector(h1_baseline_z$beta_covs))

topic_fe_table <- bind_rows(
  tibble(spec = "H2",  topic_clean = names(fe_h2), topic_fe = as.numeric(fe_h2)),
  tibble(spec = "H3a", topic_clean = names(fe_h3), topic_fe = as.numeric(fe_h3))
) %>%
  group_by(spec) %>%
  mutate(topic_fe_centered = topic_fe - mean(topic_fe)) %>%
  ungroup()
```

## Pre- Versus Post-Invasion Topic Means

Topic means are computed twice for each hypothesis: over the full estimation
window, which is the window Section 1's demeaning uses, and over the baseline
bandwidth window, which is the window the pooled fixed effects are actually
estimated on. Article counts and topic shares on each side of the cutoff are
included, because a topic whose share of coverage jumps at the cutoff shifts the
composition of the sample even when its own mean is stable.

```{r diag-s3-means}
topic_period_means <- function(d, label, window, bw = NULL) {
  if (!is.null(bw)) {
    d <- d %>% filter(abs(running_probabilistic) < bw)
  }

  d %>%
    mutate(topic_clean = as.character(topic_clean),
           period = if_else(running_probabilistic < 0, "pre", "post")) %>%
    group_by(topic_clean, period) %>%
    summarise(mean_z   = mean(sentiment_z, na.rm = TRUE),
              mean_raw = mean(sentiment_clean, na.rm = TRUE),
              n        = n(),
              .groups  = "drop") %>%
    pivot_wider(names_from = period,
                values_from = c(mean_z, mean_raw, n)) %>%
    mutate(spec   = label,
           window = window,
           share_pre  = n_pre  / sum(n_pre,  na.rm = TRUE),
           share_post = n_post / sum(n_post, na.rm = TRUE),
           change_z   = mean_z_post   - mean_z_pre,
           change_raw = mean_raw_post - mean_raw_pre,
           share_change = share_post - share_pre) %>%
    select(spec, window, topic_clean,
           mean_z_pre, mean_z_post, change_z,
           mean_raw_pre, mean_raw_post, change_raw,
           n_pre, n_post, share_pre, share_post, share_change)
}

topic_means_full <- bind_rows(
  topic_period_means(h1_data, "H1",  "full window"),
  topic_period_means(h2_data, "H2",  "full window"),
  topic_period_means(h3_data, "H3a", "full window")
)

topic_means_bw <- bind_rows(
  topic_period_means(h1_data, "H1",  "baseline bandwidth", h1_baseline_z$bws[1, 1]),
  topic_period_means(h2_data, "H2",  "baseline bandwidth", h2_baseline_z$bw),
  topic_period_means(h3_data, "H3a", "baseline bandwidth", h3_baseline_z$bw)
)

cat("Pre- vs post-invasion topic means, full estimation window:\n")
topic_means_full %>%
  transmute(spec, topic_clean,
            mean_z_pre = round(mean_z_pre, 4),
            mean_z_post = round(mean_z_post, 4),
            change_z = round(change_z, 4),
            change_raw = round(change_raw, 4),
            share_pre = round(share_pre, 3),
            share_post = round(share_post, 3),
            share_change = round(share_change, 3)) %>%
  as.data.frame() %>%
  print(row.names = FALSE)
```

## Assembling and Writing the Mapping Table

The `fe_vs_pre_mean_gap` column is the diagnostic of interest: the distance
between the pooled fixed effect a topic receives in the baseline model and the
pre-invasion mean that topic would receive under a frozen adjustment, both
centred so the comparison is scale-free. A topic with a large gap is one whose
mapping the pooled fixed effect is relocating relative to the pre-invasion
baseline, and those topics are what Section 1 responds to.

```{r diag-s3-assemble}
topic_mapping_diagnostic <- bind_rows(topic_means_bw, topic_means_full) %>%
  left_join(topic_fe_table, by = c("spec", "topic_clean")) %>%
  group_by(spec, window) %>%
  mutate(
    mean_z_pre_centered = mean_z_pre - mean(mean_z_pre, na.rm = TRUE),
    fe_vs_pre_mean_gap  = topic_fe_centered - mean_z_pre_centered
  ) %>%
  ungroup() %>%
  arrange(spec, window, desc(abs(change_z))) %>%
  select(spec, window, topic_clean,
         mean_z_pre, mean_z_post, change_z,
         mean_raw_pre, mean_raw_post, change_raw,
         topic_fe, topic_fe_centered, mean_z_pre_centered, fe_vs_pre_mean_gap,
         n_pre, n_post, share_pre, share_post, share_change)

cat("Topic-FE vs pre-invasion mapping, baseline bandwidth window:\n")
topic_mapping_diagnostic %>%
  filter(window == "baseline bandwidth") %>%
  transmute(spec, topic_clean,
            mean_z_pre = round(mean_z_pre, 4),
            mean_z_post = round(mean_z_post, 4),
            change_z = round(change_z, 4),
            topic_fe_centered = round(topic_fe_centered, 4),
            mean_z_pre_centered = round(mean_z_pre_centered, 4),
            fe_vs_pre_mean_gap = round(fe_vs_pre_mean_gap, 4)) %>%
  as.data.frame() %>%
  print(row.names = FALSE)

write_csv(topic_mapping_diagnostic,
          file.path(OUTPUT_DIAGNOSTICS, "topic_mapping_diagnostic.csv"))
cat("\nWrote:", file.path(OUTPUT_DIAGNOSTICS, "topic_mapping_diagnostic.csv"), "\n")
```

# Section 4: Pre-Period Variants on the Matched Preferred Models

Sections 1 and 2 ran the pre-period variants against the *unmatched* main
specifications. The preferred columns in the paper are the matched ones -- Table 2
Model 6 (`matched_model_z`, from `05a`) and Table 4 Model 5 (`matched_model`, from
`06a`) -- so this section repeats both variants against those.

The matched samples differ from the unmatched ones in ways that matter here. They
are exact-matched on topic and publication day, which means the topic composition
is balanced across the comparison groups by construction; that is precisely the
channel Section 1 probes, so the two sections are not expected to give the same
answer. They are also smaller, and H3a's matched sample is drawn from state-owned
outlets in non-NATO countries only.

Both variants below hold the matched sample fixed. Matching is never re-run: the
matched rows are constructed once, the main estimate is reproduced on them, and only the
outcome and the fixed-effect structure change afterwards.

## Rebuilding the Matched Samples

Reproduces each host script's matching pipeline. Both use `MatchIt` with
`method = "exact"`, which is deterministic, so the matched rows are reproducible
without any RNG concern. Note that both match on `running` -- the day-scale running
variable -- not on `running_probabilistic`.

One deliberate departure: `06a` selects only
`sentiment_z, running, running_probabilistic, treatment, csto, topic_clean,
source_domain, country` into its matching frame, dropping `sentiment_clean`.
Variant (ii) has to rebuild the z-score from pre-invasion `sentiment_clean`
moments, so `sentiment_clean` is carried through here. Matching is on
`csto ~ running + topic_clean` only, so an extra passenger column cannot change
which rows are matched -- and the reproduction check in the next chunk confirms it did
not, at `|diff| = 0`.

```{r diag-s4-matched-samples}
# Following 05a_diff_in_disc_analysis_prob.Rmd, chunks `non-mil-prob`,
# `non-nato-prob` (z-score variant), `matching-h2-prob` and `matched-model-h2-prob`
h2_non_mil <- h2_data %>%
  filter(!topic_clean %in% c("Military")) %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
           sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()

h2_non_nato <- h2_non_mil %>%
  filter(!country %in% NATO_COUNTRIES)

resid_y_h2m <- feols(sentiment_z ~ 1 | topic_clean + state_owned,
                     data = h2_non_nato)$residuals
bw_h2m <- rdbwselect(y = resid_y_h2m,
                     x = h2_non_nato$running_probabilistic,
                     kernel = "triangular",
                     cluster = h2_non_nato$source_domain,
                     p = 1,
                     bwselect = "mserd")$bws[1, 1]

h2_matching_frame <- h2_non_nato %>%
  filter(running_probabilistic < bw_h2m, running_probabilistic > -bw_h2m) %>%
  droplevels() %>%
  select(sentiment_clean, sentiment_z, running, running_probabilistic, treatment,
         state_owned, topic_clean, source_domain, country)

h2_ps <- matchit(state_owned ~ running + topic_clean,
                 data = h2_matching_frame, method = "exact", ratio = 1)
h2_matched <- match.data(h2_ps)

# Following 06a_russian_alignment_analysis_prob.Rmd, chunks `align-non-mil-prob-z`
# and the matching chunks that follow it
h3_non_mil <- h3_data %>%
  filter(!topic_clean %in% "Military") %>%
  group_by(source_domain) %>%
  mutate(sentiment_z = (sentiment_clean - mean(sentiment_clean, na.rm = TRUE)) /
           sd(sentiment_clean, na.rm = TRUE)) %>%
  ungroup()

resid_y_h3m <- feols(sentiment_z ~ 1 | topic_clean + csto,
                     data = h3_non_mil)$residuals
bw_h3m <- rdbwselect(y = resid_y_h3m,
                     x = h3_non_mil$running_probabilistic,
                     kernel = "triangular",
                     cluster = h3_non_mil$source_domain,
                     p = 1,
                     bwselect = "mserd")$bws[1, 1]

h3_matching_frame <- h3_non_mil %>%
  filter(running_probabilistic < bw_h3m, running_probabilistic > -bw_h3m) %>%
  # sentiment_clean added relative to 06a; see the note above this chunk
  select(sentiment_clean, sentiment_z, running, running_probabilistic, treatment,
         csto, topic_clean, source_domain, country)

h3_ps <- matchit(csto ~ running + topic_clean,
                 data = h3_matching_frame, method = "exact", ratio = 1)
h3_matched <- match.data(h3_ps)

cat(sprintf("H2  matched sample: %6d articles, %3d sources (bandwidth %.2f days)\n",
            nrow(h2_matched), length(unique(as.character(h2_matched$source_domain))),
            bw_h2m))
cat(sprintf("H3a matched sample: %6d articles, %3d sources (bandwidth %.2f days)\n",
            nrow(h3_matched), length(unique(as.character(h3_matched$source_domain))),
            bw_h3m))
```

## Reproducing the Matched Main Estimates

Nothing downstream is trustworthy unless the matched samples rebuilt above are the
same ones the paper uses. This chunk refits each matched main specification and compares it
to the serialized object, requiring exact equality. A nonzero difference would mean
the matching pipeline drifted and the diagnostics below would be measuring the
wrong thing, so it is a hard `stopifnot()` rather than a warning.

```{r diag-s4-main-check}
results_h2_ser    <- readRDS(file.path(DATA_INTERMEDIATE, "05_h2_results_prob.rds"))
results_align_ser <- readRDS(file.path(DATA_INTERMEDIATE, "06_alignment_results_prob.rds"))

# Table 2 Model 6 and Table 4 Model 5, refit on the rebuilt matched samples
h2_matched_main <- feols(sentiment_z ~ running_probabilistic * treatment * state_owned |
                               topic_clean,
                             cluster = ~source_domain, data = h2_matched)
h3_matched_main <- feols(sentiment_z ~ running_probabilistic * treatment * csto |
                               topic_clean,
                             cluster = ~source_domain, data = h3_matched)

matched_reproduction <- tibble(
  spec       = c("H2 matched (Table 2 Model 6)", "H3a matched (Table 4 Model 5)"),
  object     = c("matched_model_z", "matched_model"),
  term       = c("treatment:state_owned", "treatment:csto"),
  serialized = c(unname(coef(results_h2_ser$matched_model_z)[["treatment:state_owned"]]),
                 unname(coef(results_align_ser$matched_model)[["treatment:csto"]])),
  recomputed = c(unname(coef(h2_matched_main)[["treatment:state_owned"]]),
                 unname(coef(h3_matched_main)[["treatment:csto"]]))
) %>%
  mutate(abs_diff = abs(recomputed - serialized),
         exact    = abs_diff == 0)

print(as.data.frame(matched_reproduction), row.names = FALSE, digits = 10)

stopifnot(all(matched_reproduction$exact))
cat("\nBoth matched main specifications reproduce at |diff| = 0.\n")
```

## The Four Specifications

Table S15 reports four specifications per matched model. Each isolates one of the
two normalizations, or both together, against the same matched rows:

1. **Main** -- the model as published: `sentiment_z` (source z-scored over the
   full window), topic fixed effects, source clustering.
2. **Pre-period topic adjustment only** -- topic fixed effects removed and the
   outcome demeaned by its pre-invasion topic means, so the topic adjustment is
   frozen at its pre-invasion values instead of being fitted across the cutoff.
3. **Pre-period z-scoring only** -- the outcome re-standardized using each source's
   pre-invasion mean and standard deviation; topic fixed effects retained, so this
   is the main specification with only the source normalization changed.
4. **Both** -- the outcome first re-standardized on pre-invasion source moments,
   then demeaned by pre-invasion topic means computed *on that same pre-period
   z-scale*, with topic fixed effects removed.

Everything else is held constant across the four: the same matched rows, the same
bandwidth machinery inherited from the matched-sample construction, source
clustering, and the wild cluster bootstrap at `B = 4999` under the fixed seed from
`00_setup.R`.

```{r diag-s4-construct}
# Spec 2 inputs: pre-invasion topic means on the main specification's outcome
h2_m_s2in <- add_pre_topic_demean(h2_matched, "H2 matched")
h3_m_s2in <- add_pre_topic_demean(h3_matched, "H3a matched")

# Spec 3 inputs: source z-score rebuilt from pre-invasion moments
h2_m_s3in <- add_pre_period_z(h2_matched, "H2 matched")
h3_m_s3in <- add_pre_period_z(h3_matched, "H3a matched")

# Spec 4 inputs: topic demeaning applied ON the pre-period z-scale, so the two
# adjustments compose rather than being computed on different scales. Column
# names are kept distinct from add_pre_topic_demean()'s so the joins cannot clash.
add_pre_topic_demean_on <- function(d, source_col, target_col, label) {
  pre_means <- d %>%
    filter(running_probabilistic < 0) %>%
    group_by(topic_clean) %>%
    summarise(pre_topic_mean_on = mean(.data[[source_col]], na.rm = TRUE),
              n_pre_topic_on    = n(),
              .groups = "drop")

  cat("\nPre-invasion topic means on", source_col, "-", label, "\n")
  print(as.data.frame(pre_means), row.names = FALSE)

  out <- d %>% left_join(pre_means, by = "topic_clean")
  out[[target_col]] <- out[[source_col]] - out$pre_topic_mean_on
  out
}

h2_m_s4in <- add_pre_topic_demean_on(h2_m_s3in$data, "sentiment_z_pre",
                                     "sentiment_z_pre_tdm", "H2 matched")
h3_m_s4in <- add_pre_topic_demean_on(h3_m_s3in$data, "sentiment_z_pre",
                                     "sentiment_z_pre_tdm", "H3a matched")

dropped_sources_matched <- bind_rows(h2_m_s3in$dropped, h3_m_s3in$dropped)
write_csv(dropped_sources_matched,
          file.path(OUTPUT_DIAGNOSTICS, "preperiod_matched_dropped_sources.csv"))
cat("\nWrote:", file.path(OUTPUT_DIAGNOSTICS, "preperiod_matched_dropped_sources.csv"), "\n")
```

## Estimating the Four Specifications

Specs 2 and 4 drop the topic fixed effects, because the topic adjustment they
apply is already carried in the outcome. Specs 1 and 3 keep them. The interaction
of interest is unchanged throughout.

```{r diag-s4-fits}
# H2 matched -- Table 2 Model 6
h2_s15 <- list(
  spec1 = h2_matched_main,
  spec2 = feols(sentiment_z_tdm ~ running_probabilistic * treatment * state_owned,
                cluster = ~source_domain, data = h2_m_s2in),
  spec3 = feols(sentiment_z_pre ~ running_probabilistic * treatment * state_owned |
                  topic_clean,
                cluster = ~source_domain, data = h2_m_s3in$data),
  spec4 = feols(sentiment_z_pre_tdm ~ running_probabilistic * treatment * state_owned,
                cluster = ~source_domain, data = h2_m_s4in)
)

# H3a matched -- Table 4 Model 5
h3_s15 <- list(
  spec1 = h3_matched_main,
  spec2 = feols(sentiment_z_tdm ~ running_probabilistic * treatment * csto,
                cluster = ~source_domain, data = h3_m_s2in),
  spec3 = feols(sentiment_z_pre ~ running_probabilistic * treatment * csto |
                  topic_clean,
                cluster = ~source_domain, data = h3_m_s3in$data),
  spec4 = feols(sentiment_z_pre_tdm ~ running_probabilistic * treatment * csto,
                cluster = ~source_domain, data = h3_m_s4in)
)

for (nm in names(h2_s15)) { cat("\n--- H2 matched,", nm, "---\n"); print(summary(h2_s15[[nm]])) }
for (nm in names(h3_s15)) { cat("\n--- H3a matched,", nm, "---\n"); print(summary(h3_s15[[nm]])) }
```

## Side-by-Side Comparison and Serialization

Each row carries the analytic cluster-robust p-value and the wild cluster bootstrap
p-value, since the paper reports the bootstrap one for these models. The fitted
models and their bootstraps are serialized so `10a_publication_outputs_prob.Rmd` can
build table S15 without refitting.

```{r diag-s4-comparison}
# Assemble in the shape row_fe() expects, so these rows stack with sections 1-3
as_fit <- function(model, coef_name, data, bw) {
  list(model = model, coef_name = coef_name, data = data, bw = bw,
       boot = safe_wild_bootstrap(model, coef_name))
}

SPEC_LABELS <- c(spec1 = "(1) main",
                 spec2 = "(2) pre-period topic adj.",
                 spec3 = "(3) pre-period z-score",
                 spec4 = "(4) both")

h2_fits <- list(
  spec1 = as_fit(h2_s15$spec1, "treatment:state_owned", h2_matched,      bw_h2m),
  spec2 = as_fit(h2_s15$spec2, "treatment:state_owned", h2_m_s2in,       bw_h2m),
  spec3 = as_fit(h2_s15$spec3, "treatment:state_owned", h2_m_s3in$data,  bw_h2m),
  spec4 = as_fit(h2_s15$spec4, "treatment:state_owned", h2_m_s4in,       bw_h2m)
)
h3_fits <- list(
  spec1 = as_fit(h3_s15$spec1, "treatment:csto", h3_matched,     bw_h3m),
  spec2 = as_fit(h3_s15$spec2, "treatment:csto", h3_m_s2in,      bw_h3m),
  spec3 = as_fit(h3_s15$spec3, "treatment:csto", h3_m_s3in$data, bw_h3m),
  spec4 = as_fit(h3_s15$spec4, "treatment:csto", h3_m_s4in,      bw_h3m)
)

OUTCOME_BY_SPEC <- c(spec1 = "sentiment_z", spec2 = "sentiment_z_tdm",
                     spec3 = "sentiment_z_pre", spec4 = "sentiment_z_pre_tdm")
FE_BY_SPEC      <- c(spec1 = "topic", spec2 = "none", spec3 = "topic", spec4 = "none")

section4_estimates <- bind_rows(
  map_df(names(h2_fits), function(k)
    row_fe(h2_fits[[k]], "s4_matched", "H2 matched", "z-score",
           OUTCOME_BY_SPEC[[k]], FE_BY_SPEC[[k]]) %>% mutate(spec_id = k)),
  map_df(names(h3_fits), function(k)
    row_fe(h3_fits[[k]], "s4_matched", "H3a matched", "z-score",
           OUTCOME_BY_SPEC[[k]], FE_BY_SPEC[[k]]) %>% mutate(spec_id = k))
) %>%
  mutate(variant = unname(SPEC_LABELS[spec_id]), .after = spec)

print_comparison(section4_estimates)

# Shift of each variant against its own matched main specification
section4_comparison <- section4_estimates %>%
  group_by(spec) %>%
  mutate(main_estimate = estimate[spec_id == "spec1"],
         main_se       = std_error[spec_id == "spec1"],
         main_p        = p_value[spec_id == "spec1"],
         main_boot_p   = boot_p[spec_id == "spec1"]) %>%
  ungroup() %>%
  filter(spec_id != "spec1") %>%
  transmute(spec, variant,
            main_estimate, estimate,
            abs_change = estimate - main_estimate,
            pct_change = 100 * (estimate - main_estimate) / abs(main_estimate),
            shift_in_main_ses = (estimate - main_estimate) / main_se,
            main_se, std_error,
            main_p, p_value,
            main_boot_p, boot_p,
            n_obs, n_clusters)

cat("\nShift relative to the matched main specification:\n")
print(as.data.frame(section4_comparison %>%
  transmute(spec, variant,
            main = round(main_estimate, 4),
            diagnostic = round(estimate, 4),
            abs_change = round(abs_change, 4),
            pct_change = round(pct_change, 1),
            shift_in_main_ses = round(shift_in_main_ses, 3),
            main_p = signif(main_p, 3),
            diagnostic_p = signif(p_value, 3),
            main_boot_p = signif(main_boot_p, 3),
            diagnostic_boot_p = signif(boot_p, 3))), row.names = FALSE)

write_csv(section4_estimates,
          file.path(OUTPUT_DIAGNOSTICS, "preperiod_matched_comparison.csv"))
write_csv(section4_comparison,
          file.path(OUTPUT_DIAGNOSTICS, "preperiod_matched_shifts.csv"))
cat("\nWrote:", file.path(OUTPUT_DIAGNOSTICS, "preperiod_matched_comparison.csv"), "\n")
cat("Wrote:", file.path(OUTPUT_DIAGNOSTICS, "preperiod_matched_shifts.csv"), "\n")
```

## Serialized Results

Written to `data/intermediate/` following the same convention as the 04-07 result
files, and read by `10a_publication_outputs_prob.Rmd` to build table S15.

```{r diag-serialize}
results_preperiod_prob <- list(
  # Table 2 Model 6 and Table 4 Model 5, each under the four S15 specifications
  h2_matched_models  = h2_s15,
  h3a_matched_models = h3_s15,

  # WCR bootstrap results, keyed to match the model lists above
  bootstrap_se = list(
    h2_matched  = map(h2_fits, "boot"),
    h3a_matched = map(h3_fits, "boot")
  ),

  spec_labels          = SPEC_LABELS,
  matched_bandwidths   = list(h2 = bw_h2m, h3a = bw_h3m),
  matched_reproduction = matched_reproduction,
  section4_estimates   = section4_estimates,
  section4_comparison  = section4_comparison
)

saveRDS(results_preperiod_prob,
        file.path(DATA_INTERMEDIATE, "09_preperiod_results_prob.rds"))
cat("Results saved to:",
    file.path(DATA_INTERMEDIATE, "09_preperiod_results_prob.rds"), "\n")
```

# Combined Summary File

Everything printed above is also written to a single plain-text file, so the three
diagnostics can be read in one place without opening three CSVs. The file records
the bootstrap setting, the sample sizes, and any bootstrap failures alongside the
numbers, so a later reader can tell what was and was not computed.

```{r diag-summary-txt}
summary_path <- file.path(OUTPUT_DIAGNOSTICS, "preperiod_diagnostics_summary.txt")

summary_lines <- capture.output({
  cat("=============================================================\n")
  cat("PRE-PERIOD ADJUSTMENT DIAGNOSTICS (PROBABILISTIC VARIANT)\n")
  cat("Produced by scripts/09_preperiod_diagnostics.Rmd\n")
  cat("Generated:", as.character(Sys.time()), "\n")
  cat("=============================================================\n\n")

  cat("Sections 1-3 are author diagnostics, not paper outputs.\n")
  cat("Section 4 produces the models behind appendix table S15, serialized to\n")
  cat("  data/intermediate/09_preperiod_results_prob.rds and read by 10a.\n\n")

  cat("Wild cluster bootstrap: B =", BOOT_B,
      "(repository default from 00_setup.R; not reduced)\n")
  cat("Pre-invasion period defined as running_probabilistic < 0.\n")
  cat("Running variable units: H1 seconds (04a convention); H2/H3a days.\n\n")

  cat("SAMPLES\n")
  cat("-------------------------------------------------------------\n")
  cat(sprintf("H1  (04a data_non_ukraine)   : %6d articles, %3d sources\n",
              nrow(h1_data), length(unique(h1_data$source_domain))))
  cat(sprintf("H2  (05a data_non_ukraine)   : %6d articles, %3d sources\n",
              nrow(h2_data), nlevels(h2_data$source_domain)))
  cat(sprintf("H3a (06a data_align_state)   : %6d articles, %3d sources\n",
              nrow(h3_data), nlevels(h3_data$source_domain)))
  cat(sprintf("Articles where `treatment` disagrees with running < 0: H1 %d, H2 %d, H3a %d\n\n",
              mismatch_h1, mismatch_h2, mismatch_h3))

  cat("BASELINE ESTIMATES (recomputed on the samples above)\n")
  cat("-------------------------------------------------------------\n")
  cat("Baselines are the full-sample optimal-bandwidth columns, not the paper's\n")
  cat("main H2/H3a results (Table 2 Model 5 and Table 4 Model 4, which restrict\n")
  cat("the sample; those are covered in Section 4).\n")
  cat("  z-score : H1 Table 1 Model 5 | H2 Table 2 Model 3 | H3a Table 4 Model 3\n")
  cat("  raw     : H1 Table 1 Model 2 | H2 Table S3 Model 4 | H3a Table S7 Model 3\n\n")
  print_comparison(bind_rows(baseline_z, baseline_raw))

  cat("\n\nSECTION 1: TOPIC ADJUSTMENT FIXED AT PRE-INVASION VALUES\n")
  cat("-------------------------------------------------------------\n")
  cat("Outcome demeaned by pre-invasion topic means; topic FE / covs removed.\n")
  cat("'z-score' rows are comparable to the named z-score baselines;\n")
  cat("'raw' rows are the literal sentiment_clean demeaning, compared against\n")
  cat("the raw-scale baseline siblings.\n\n")
  print_comparison(section1_estimates)
  cat("\nShift relative to baseline:\n")
  print(as.data.frame(section1_comparison %>%
    transmute(spec, scale,
              main = round(main_estimate, 4),
              diagnostic = round(estimate, 4),
              abs_change = round(abs_change, 4),
              pct_change = round(pct_change, 1),
              shift_in_main_ses = round(shift_in_main_ses, 3),
              main_p = signif(main_p, 3),
              diagnostic_p = signif(p_value, 3))), row.names = FALSE)

  cat("\n\nSECTION 4: PRE-PERIOD VARIANTS ON THE MATCHED PREFERRED MODELS\n")
  cat("-------------------------------------------------------------\n")
  cat("Table 2 Model 6 (matched_model_z) and Table 4 Model 5 (matched_model).\n")
  cat("Matched samples rebuilt and each main estimate reproduced at |diff| = 0 before\n")
  cat("any variant was estimated. Four specifications per model; see table S15.\n\n")
  print(as.data.frame(matched_reproduction), row.names = FALSE, digits = 10)
  cat("\n")
  print_comparison(section4_estimates)
  cat("\nShift relative to the matched main specification:\n")
  print(as.data.frame(section4_comparison %>%
    transmute(spec, variant,
              main = round(main_estimate, 4),
              diagnostic = round(estimate, 4),
              abs_change = round(abs_change, 4),
              pct_change = round(pct_change, 1),
              shift_in_main_ses = round(shift_in_main_ses, 3),
              main_p = signif(main_p, 3),
              diagnostic_p = signif(p_value, 3),
              main_boot_p = signif(main_boot_p, 3),
              diagnostic_boot_p = signif(boot_p, 3))), row.names = FALSE)

  cat("\n\nSECTION 2: PRE-PERIOD-ONLY Z-SCORING\n")
  cat("-------------------------------------------------------------\n")
  cat("Outcome re-standardized on pre-invasion source means/SDs; topic FE kept.\n")
  cat("Sources dropped for zero/undefined pre-invasion SD:\n")
  if (nrow(dropped_sources) > 0) {
    print(as.data.frame(dropped_sources %>%
      select(spec, source_domain, n_pre, pre_sd, reason)), row.names = FALSE)
  } else {
    cat("  none\n")
  }
  cat("\n")
  print_comparison(section2_estimates)
  cat("\nShift relative to baseline:\n")
  print(as.data.frame(section2_comparison %>%
    transmute(spec,
              main = round(main_estimate, 4),
              diagnostic = round(estimate, 4),
              abs_change = round(abs_change, 4),
              pct_change = round(pct_change, 1),
              se_ratio = round(se_ratio, 3),
              main_p = signif(main_p, 3),
              diagnostic_p = signif(p_value, 3),
              n_sources_dropped)), row.names = FALSE)

  cat("\n\nSECTION 3: TOPIC-MAPPING DIAGNOSTIC\n")
  cat("-------------------------------------------------------------\n")
  cat("Pre- vs post-invasion topic means against the pooled topic FE from the\n")
  cat("baseline models. H1 topic FE are NA: its baseline is rdrobust, whose\n")
  cat("covariate coefficients cannot be mapped to topic names (one dummy is\n")
  cat("dropped for collinearity without being identified).\n\n")
  cat("Baseline bandwidth window:\n")
  print(as.data.frame(topic_mapping_diagnostic %>%
    filter(window == "baseline bandwidth") %>%
    transmute(spec, topic_clean,
              mean_z_pre = round(mean_z_pre, 4),
              mean_z_post = round(mean_z_post, 4),
              change_z = round(change_z, 4),
              topic_fe_centered = round(topic_fe_centered, 4),
              fe_vs_pre_mean_gap = round(fe_vs_pre_mean_gap, 4),
              share_pre = round(share_pre, 3),
              share_post = round(share_post, 3))), row.names = FALSE)
  cat("\nFull estimation window:\n")
  print(as.data.frame(topic_mapping_diagnostic %>%
    filter(window == "full window") %>%
    transmute(spec, topic_clean,
              mean_z_pre = round(mean_z_pre, 4),
              mean_z_post = round(mean_z_post, 4),
              change_z = round(change_z, 4),
              mean_raw_pre = round(mean_raw_pre, 4),
              mean_raw_post = round(mean_raw_post, 4),
              change_raw = round(change_raw, 4),
              share_pre = round(share_pre, 3),
              share_post = round(share_post, 3))), row.names = FALSE)

  cat("\n\nBOOTSTRAP STATUS\n")
  cat("-------------------------------------------------------------\n")
  boot_status <- bind_rows(baseline_z, baseline_raw,
                           section1_estimates, section2_estimates) %>%
    filter(estimator == "feols") %>%
    transmute(section, spec, scale,
              boot_p = signif(boot_p, 3),
              status = if_else(is.na(boot_p), "FAILED", "ok"))
  print(as.data.frame(boot_status), row.names = FALSE)

  cat("\n=============================================================\n")
})

writeLines(summary_lines, summary_path)
cat("Wrote:", summary_path, "\n\n")
cat(paste(summary_lines, collapse = "\n"), "\n")
```

# Session Info

```{r diag-session-info}
print_session_info()
```
