---
title: "10a - Publication Outputs (Probabilistic Time)"
author: "Donald Moratz"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

# Overview

This file generates publication-quality tables for the **probabilistic (KDE) time assignment** data variant. All tables are saved to `FIGURES_TABLES/prob/`.

# To Do
Add Russia models (results_h2$model3a_z, results_align$model5a_opt_russian_z) back into appendix, currently removed

```{r setup}
source("00_setup.R")

TABLE_SUBDIR <- "prob"
```

# Data Loading

```{r load-data}
results_h1    <- readRDS(file.path(DATA_INTERMEDIATE, "04_h1_results_prob.rds"))
results_h2    <- readRDS(file.path(DATA_INTERMEDIATE, "05_h2_results_prob.rds"))
results_align <- readRDS(file.path(DATA_INTERMEDIATE, "06_alignment_results_prob.rds"))
results_prepd <- readRDS(file.path(DATA_INTERMEDIATE, "09_preperiod_results_prob.rds"))
results_ethnic <- readRDS(file.path(DATA_INTERMEDIATE, "07_ethnic_results_prob.rds"))
data <- readRDS(file.path(DATA_INTERMEDIATE, "02_cleaned_data.rds"))
```

# Model Verification

```{r model-check}
check_model <- function(obj, name, obj_name) {
  exists <- !is.null(obj[[name]])
  status <- if (exists) "OK" else "WARNING: NOT FOUND"
  cat(sprintf("  %-45s %s\n", paste0(obj_name, "$", name), status))
  invisible(exists)
}

check_boot <- function(obj, name, obj_name) {
  exists <- !is.null(obj$bootstrap_se[[name]])
  status <- if (exists) "OK" else "WARNING: NOT FOUND"
  cat(sprintf("  %-45s %s\n", paste0(obj_name, "$bootstrap_se$", name), status))
  invisible(exists)
}

cat("=== H1 Models ===\n")
for (m in c("model1_opt", "model2_opt", "model3_opt", "model4_opt",
            "model5_opt", "model6a_nonmil", "model7a_nonnato",
            "model5_opt_pol", "model5_opt_mil", "model5_opt_econ",
            "model5_opt_cult", "model5_opt_oth",
            "model1_basic", "model1_country_fe", "model1_country_source_fe",
            "model1_full_linear", "model1_z", "model6_non_mil", "model7_non_nato",
            "model_placebo", "model_placebo_z")) {
  check_model(results_h1, m, "results_h1")
}

cat("\n=== H2 Models ===\n")
for (m in c("model2_state_rdd_z", "model2_ind_rdd_z",
            "model2a_z", "model2a_opt_z", "model2b_z", "model2d_z",
            "model3a_z", "matched_model_z",
            "model2a_opt_pol", "model2a_opt_mil", "model2a_opt_econ",
            "model2a_opt_cult", "model2a_opt_oth",
            "model2a", "model2a_full", "model2a_opt", "model2a_opt_full_fe",
            "model2b", "model2d", "model3a_opt", "matched_model",
            "model2b_full_fe", "model3a_opt_full_fe", "model_did",
            "model2a_full_pol", "model2a_full_mil", "model2a_full_econ",
            "model2a_full_cult", "model2a_full_oth",
            "model_placebo")) {
  check_model(results_h2, m, "results_h2")
}

cat("\n=== H2 Bootstrap Keys ===\n")
for (m in c("model2a_z", "model2a_opt_z", "model2b_z", "model2d_z",
            "model3a_z", "matched_model_z",
            "model2a_opt_pol", "model2a_opt_mil", "model2a_opt_econ",
            "model2a_opt_cult", "model2a_opt_oth",
            "model2a", "model2a_full", "model2a_opt", "model2a_opt_full_fe",
            "model2b", "model2d", "model3a_opt", "matched_model",
            "model2b_full_fe", "model3a_opt_full_fe", "model_did",
            "model2a_full_pol", "model2a_full_mil", "model2a_full_econ",
            "model2a_full_cult", "model2a_full_oth")) {
  check_boot(results_h2, m, "results_h2")
}

cat("\n=== H3a (Alignment) Models ===\n")
for (m in c("model5a_csto_z", "model5a_neutral_z",
            "model5a_z", "model5a_opt_z", "model5a_opt_non_mil_z",
            "model5a_opt_russian_z", "matched_model",
            "model5a_opt_pol", "model5a_opt_mil", "model5a_opt_econ",
            "model5a_opt_cult", "model5a_opt_oth",
            "model5a_full", "model5a_opt", "model5a_opt_non_mil",
            "model5a_opt_russian", "model5a_opt_full_fe",
            "model5a_opt_non_mil_full_fe", "model5a_opt_rus_full_fe",
            "model5a_fully_saturated",
            "model5a_full_pol", "model5a_full_mil", "model5a_full_econ",
            "model5a_full_cult", "model5a_full_oth",
            "model_placebo_nonmil")) {
  check_model(results_align, m, "results_align")
}

# Per-country Dec-7 aligned placebos (stored as a named list of rdrobust models)
cat(sprintf("  %-45s %s\n", "results_align$placebo_aligned_models",
            if (length(results_align$placebo_aligned_models) > 0) "OK" else "WARNING: NOT FOUND"))

cat("\n=== H3a Bootstrap Keys ===\n")
for (m in c("model5a_z", "model5a_opt_z", "model5a_opt_non_mil_z",
            "model5a_opt_russian_z", "matched_model",
            "model5a_opt_pol", "model5a_opt_mil", "model5a_opt_econ",
            "model5a_opt_cult", "model5a_opt_oth",
            "model5a_full", "model5a_opt", "model5a_opt_non_mil",
            "model5a_opt_russian", "model5a_opt_full_fe",
            "model5a_opt_non_mil_full_fe", "model5a_opt_rus_full_fe",
            "model5a_fully_saturated",
            "model5a_full_pol", "model5a_full_mil", "model5a_full_econ",
            "model5a_full_cult", "model5a_full_oth")) {
  check_boot(results_align, m, "results_align")
}

cat("\n=== H3b (Ethnic) Models ===\n")
for (m in c("model6a_high_z", "model6a_low_z",
            "model6a_opt_z", "model6a_opt_non_mil_z", "matched_model_z")) {
  check_model(results_ethnic, m, "results_ethnic")
}

cat("\n=== H3b Bootstrap Keys ===\n")
for (m in c("model6a_opt_z", "model6a_opt_non_mil_z", "matched_model_z")) {
  check_boot(results_ethnic, m, "results_ethnic")
}

cat("\n=== LOO & Placebo ===\n")
cat(sprintf("  %-45s %s\n", "results_h2$loo_summary",
            if (!is.null(results_h2$loo_summary)) "OK" else "WARNING: NOT FOUND"))
cat(sprintf("  %-45s %s\n", "results_h2$matched_loo_summary",
            if (!is.null(results_h2$matched_loo_summary)) "OK" else "WARNING: NOT FOUND"))
cat(sprintf("  %-45s %s\n", "results_align$loo_summary",
            if (!is.null(results_align$loo_summary)) "OK" else "WARNING: NOT FOUND"))
cat(sprintf("  %-45s %s\n", "results_align$matched_loo_summary",
            if (!is.null(results_align$matched_loo_summary)) "OK" else "WARNING: NOT FOUND"))
```

# Main Paper Tables

## Table 1: H1 RDD — Hybrid FE + Z-Score (Pattern A)

```{r table-01}
h1_models <- list(
  "(1)" = results_h1$model1_opt,
  "(2)" = results_h1$model2_opt,
  "(3)" = results_h1$model3_opt,
  "(4)" = results_h1$model4_opt,
  "(5)" = results_h1$model5_opt,
  "(6)" = results_h1$model6a_nonmil,
  "(7)" = results_h1$model7a_nonnato
)

n_cl_t1 <- sapply(h1_models, get_n_clusters)

rows_t1 <- tibble::tribble(
  ~term,            ~`(1)`, ~`(2)`, ~`(3)`, ~`(4)`, ~`(5)`, ~`(6)`, ~`(7)`,
  "Topic FEs",      "-",    "X",    "X",    "X",    "X",    "X",    "X",
  "State FEs",      "-",    "-",    "-",    "X",    "-",    "-",    "-",
  "Source FEs",     "-",    "-",    "X",    "X",    "-",    "-",    "-",
  "Source Z-Score", "-",    "-",    "-",    "-",    "X",    "X",    "X",
  "Clusters",       "61", "61", "61", "61", "61", "61", "45"
)
attr(rows_t1, "position") <- NULL

note_t1 <- str_wrap(paste(
  SE_NOTE_CLUSTER,
  "Models 1-4 use the optimal bandwidth.",
  "Models 5-7 use a Z-Score adjustment instead of fixed effects.",
  "Model 6 omits Military Topics. Model 7 omits NATO allies."
), 80)

table_1 <- modelsummary(
  h1_models,
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  statistic = "({std.error})",
  coef_map = c("treatment" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE|R2 Within|R2 Within Adj.|Num.Obs.|nobs.left|nobs.right|bandwidth.left|bandwidth.right",
  title = "H1 RDD — Effect of Russian Invasion on Media Sentiment (Probabilistic Time)",
  add_rows = rows_t1,
  notes = note_t1
)

table_1
save_table(table_1, "table_01_main", TABLE_SUBDIR)
```

## Table 2: H2 Interaction Z-Score — State Ownership (Pattern B)

```{r table-02}
# Define model list and bootstrap keys
h2_z_models <- list(
  "(1) State-Owned\u2021" = results_h2$model2_state_rdd_z,
  "(2) Ind.\u2021" = results_h2$model2_ind_rdd_z,
  "(3)\u2020" = results_h2$model2a_opt_z,
  "(4)\u2020" = results_h2$model2b_z,
  "(5)\u2020" = results_h2$model2d_z,
#  "(6)\u2020" = results_h2$model3a_z,
  "(6)\u2020" = results_h2$matched_model_z
)

boot_keys_t2 <- c("model2a_opt_z", "model2b_z", "model2d_z",
                  # "model3a_z", 
                  "matched_model_z")
boot_results_t2 <- lapply(boot_keys_t2, function(k) results_h2$bootstrap_se[[k]])

# Build vcov list: NULL for rdrobust, create_bootstrap_vcov for felm
vcov_t2 <- list(
  "(1) State-Owned\u2021" = NULL,
  "(2) Ind.\u2021" = NULL,
  "(3)\u2020" = create_bootstrap_vcov(results_h2$model2a_opt_z, boot_results_t2[[1]], "treatment:state_owned"),
  "(4)\u2020" = create_bootstrap_vcov(results_h2$model2b_z, boot_results_t2[[2]], "treatment:state_owned"),
  "(5)\u2020" = create_bootstrap_vcov(results_h2$model2d_z, boot_results_t2[[3]], "treatment:state_owned"),
#  "(6)\u2020" = create_bootstrap_vcov(results_h2$model3a_z, boot_results_t2[[4]], "treatment:state_owned"),
  "(6)\u2020" = create_bootstrap_vcov(results_h2$matched_model_z, boot_results_t2[[4]], "treatment:state_owned")
)

n_cl_t2 <- map_chr(h2_z_models, get_n_clusters)

rows_t2 <- tibble::tribble(
  ~term,~row1, ~row2, ~row3, ~row4, ~row5, ~row6,# ~row7,
  "Source Z-Score", "X",    "X",    "X",    "X",    "X",    "X",#    "X",
  "Clusters",       "17", "44", n_cl_t2[3], n_cl_t2[4], n_cl_t2[5], n_cl_t2[6],# n_cl_t2[7]
)
attr(rows_t2, "position") <- c(5, 6)

note_t2 <- str_wrap(paste(
  "All models use a source-level Z-Score normalization.",
  "Models 1-2 show separate RDD estimates for state-owned and independent media, filtered to omit military topics.",
  "Models 3-6 estimate the state-owned x treatment interaction.",
  "Model 3 uses the optimal bandwidth on the full sample.",
  "Model 4 omits military topics.",
  "Model 5 omits military topics and NATO allies.",
  "Model 6 applies exact matching on topic and publication date to Model 5's sample.",
  SE_NOTE
), 80)

table_2 <- modelsummary(
  h2_z_models,
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  vcov = vcov_t2,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State-Owned x Treat"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE|R2 Within|R2 Within Adj.|bandwidth.left|bandwidth.right|nobs.left|nobs.right",
  title = "H2 Diff-in-Disc — State Ownership Interaction, Z-Score (Probabilistic Time)",
  add_rows = rows_t2,
  notes = note_t2
)

boot_col_names_t2 <- c("(3)\u2020", "(4)\u2020", "(5)\u2020", "(6)\u2020")#, "(7)\u2020")
table_2 <- override_interaction_stars(table_2, boot_results_t2, boot_col_names_t2)

table_2
save_table(table_2, "table_02_main", TABLE_SUBDIR)
```

## Table 3: H2 By-Topic Z-Score — State Ownership (Pattern C-z)

```{r table-03}
h2_topic_z_models <- list(
  "Political" = results_h2$model2a_opt_pol,
  "Military"  = results_h2$model2a_opt_mil,
  "Economic"  = results_h2$model2a_opt_econ,
  "Cultural"  = results_h2$model2a_opt_cult,
  "Other"     = results_h2$model2a_opt_oth
)

boot_keys_t3 <- c("model2a_opt_pol", "model2a_opt_mil", "model2a_opt_econ",
                   "model2a_opt_cult", "model2a_opt_oth")
boot_results_t3 <- lapply(boot_keys_t3, function(k) results_h2$bootstrap_se[[k]])

vcov_t3 <- list(
  "Political" = create_bootstrap_vcov(h2_topic_z_models[["Political"]], boot_results_t3[[1]], "treatment:state_owned"),
  "Military"  = create_bootstrap_vcov(h2_topic_z_models[["Military"]],  boot_results_t3[[2]], "treatment:state_owned"),
  "Economic"  = create_bootstrap_vcov(h2_topic_z_models[["Economic"]],  boot_results_t3[[3]], "treatment:state_owned"),
  "Cultural"  = create_bootstrap_vcov(h2_topic_z_models[["Cultural"]],  boot_results_t3[[4]], "treatment:state_owned"),
  "Other"     = create_bootstrap_vcov(h2_topic_z_models[["Other"]],     boot_results_t3[[5]], "treatment:state_owned")
)

n_cl_t3 <- sapply(h2_topic_z_models, get_n_clusters)

rows_t3 <- tibble::tribble(
  ~term,            ~Political, ~Military, ~Economic, ~Cultural, ~Other,
  "Source Z-Score", "X",        "X",       "X",       "X",       "X",
  "Clusters",       n_cl_t3[1], n_cl_t3[2], n_cl_t3[3], n_cl_t3[4], n_cl_t3[5]
)
attr(rows_t3, "position") <- c(5, 6)

note_t3 <- str_wrap(paste(
  "All models use a source-level Z-Score normalization with the optimal bandwidth.",
  "Each column restricts to the indicated topic category.", SE_NOTE
), 80)

table_3 <- modelsummary(
  h2_topic_z_models,
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  vcov = vcov_t3,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE|R2 Within|R2 Within Adj.|bandwidth.left|bandwidth.right|nobs.left|nobs.right",
  title = "H2 Diff-in-Disc by Topic — Z-Score (Probabilistic Time)",
  add_rows = rows_t3,
  notes = note_t3
)

topic_col_names <- c("Political", "Military", "Economic", "Cultural", "Other")
table_3 <- override_interaction_stars(table_3, boot_results_t3, topic_col_names)

table_3
save_table(table_3, "table_03_main", TABLE_SUBDIR)

```

## Table 4: H3a Interaction Z-Score — CSTO Alignment (Pattern B)

```{r table-04}
h3a_z_models <- list(
  "(1) CSTO\u2021" = results_align$model5a_csto_z,
  "(2) Neutral\u2021" = results_align$model5a_neutral_z,
  "(3)\u2020" = results_align$model5a_opt_z,
  "(4)\u2020" = results_align$model5a_opt_non_mil_z,
#  "(5)\u2020" = results_align$model5a_opt_russian_z,
  "(5)\u2020" = results_align$matched_model
)

boot_keys_t4 <- c("model5a_opt_z", "model5a_opt_non_mil_z",
                  # "model5a_opt_russian_z", 
                  "matched_model")
boot_results_t4 <- lapply(boot_keys_t4, function(k) results_align$bootstrap_se[[k]])

vcov_t4 <- list(
  "(1) CSTO\u2021" = NULL,
  "(2) Neutral\u2021" = NULL,
  "(3)\u2020" = create_bootstrap_vcov(results_align$model5a_opt_z, boot_results_t4[[1]], "treatment:csto"),
  "(4)\u2020" = create_bootstrap_vcov(results_align$model5a_opt_non_mil_z, boot_results_t4[[2]], "treatment:csto"),
#  "(5)\u2020" = create_bootstrap_vcov(results_align$model5a_opt_russian_z, boot_results_t4[[3]], "treatment:csto"),
  "(5)\u2020" = create_bootstrap_vcov(results_align$matched_model, boot_results_t4[[3]], "treatment:csto")
)

n_cl_t4 <- sapply(h3a_z_models, get_n_clusters)

rows_t4 <- tibble::tribble(
  ~term,~row1, ~row2, ~row3, ~row4, ~row5,# ~row6,
  "Source Z-Score", "X",    "X",    "X",    "X",    "X",#    "X",
  "Clusters",       "9", "4", n_cl_t4[3], n_cl_t4[4], n_cl_t4[5],# n_cl_t4[6]
)
attr(rows_t4, "position") <- c(5, 6)

note_t4 <- str_wrap(paste(
  "All models use a source-level Z-Score normalization.",
  "Sample restricted to state-owned media in non-NATO countries.",
  "Models 1-2 show separate RDD estimates for CSTO-aligned and neutral countries, filtered to omit military topics.",
  "Models 3-5 estimate the CSTO x treatment interaction.",
  "Model 3 uses the optimal bandwidth.",
  "Model 4 omits military topics.", 
  #"Model 5 restricts to Russian-related articles.",
  "Model 5 uses exact matching on topic and date of publication for the non-military data.", SE_NOTE
), 80)

table_4 <- modelsummary(
  h3a_z_models,
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  vcov = vcov_t4,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE|R2 Within|R2 Within Adj.|bandwidth.left|bandwidth.right|nobs.left|nobs.right",
  title = "H3a Alignment Interaction — Z-Score (Probabilistic Time)",
  add_rows = rows_t4,
  notes = note_t4
)

boot_col_names_t4 <- c("(3)\u2020", "(4)\u2020", "(5)\u2020")#, "(6)\u2020")
table_4 <- override_interaction_stars(table_4, boot_results_t4, boot_col_names_t4)

table_4
save_table(table_4, "table_04_main", TABLE_SUBDIR)
```

## Table 5: H3b Null Result Z-Score — Ethnic Russian Population (Pattern B)

```{r table-05b}
h3b_z_models_exist <- !is.null(results_ethnic$model6a_high_z) &&
                      !is.null(results_ethnic$model6a_low_z) &&
                      !is.null(results_ethnic$model6a_opt_z)


h3b_z_models <- list(
  "(1) High\u2021" = results_ethnic$model6a_high_z,
  "(2) Low\u2021" = results_ethnic$model6a_low_z,
  "(3)\u2020" = results_ethnic$model6a_opt_z,
  "(4)\u2020" = results_ethnic$model6a_opt_non_mil_z,
  "(5)\u2020" = results_ethnic$matched_model_z
)

boot_keys_t6 <- c("model6a_opt_z", "model6a_opt_non_mil_z", "matched_model_z")
boot_results_t6 <- lapply(boot_keys_t6, function(k) results_ethnic$bootstrap_se[[k]])

vcov_t6 <- list(
  "(1)\u2021" = NULL,
  "(2)\u2021" = NULL,
  "(3)\u2020" = create_bootstrap_vcov(results_ethnic$model6a_opt_z, boot_results_t6[[1]], "treatment:high_russia"),
  "(4)\u2020" = create_bootstrap_vcov(results_ethnic$model6a_opt_non_mil_z, boot_results_t6[[2]], "treatment:high_russia"),
  "(5)\u2020" = create_bootstrap_vcov(results_ethnic$matched_model_z, boot_results_t6[[3]], "treatment:high_russia")
)

n_cl_t6 <- sapply(h3b_z_models, get_n_clusters)

rows_t6 <- tibble::tribble(
  ~term,~row1, ~row2, ~row3, ~row4, ~row5,
  "Source Z-Score", "X",    "X",    "X",    "X",    "X",
  "Clusters",       "9", "4", n_cl_t6[3], n_cl_t6[4], n_cl_t6[5]
)
attr(rows_t6, "position") <- c(5, 6)

note_t6 <- str_wrap(paste(
  "All models use a source-level Z-Score normalization.",
  "Models 1-2 show separate RDD estimates for high and low ethnic Russian population countries.",
  "Models 3-5 estimate the high Russian population x treatment interaction.",
  "Model 3 uses the optimal bandwidth. Model 4 omits military topics.",
  "Model 5 uses matched data.", SE_NOTE
), 80)

table_6 <- modelsummary(
  h3b_z_models,
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  vcov = vcov_t6,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:high_russia" = "High Russian Pop x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE|R2 Within|R2 Within Adj.|bandwidth.left|bandwidth.right|nobs.left|nobs.right",
  title = "H3b Ethnic Russian Population — Null Result, Z-Score (Probabilistic Time)",
  add_rows = rows_t6,
  notes = note_t6
)

boot_col_names_t6 <- c("(3)\u2020", "(4)\u2020", "(5)\u2020")
table_6 <- override_interaction_stars(table_6, boot_results_t6, boot_col_names_t6)

table_6
save_table(table_6, "table_05_main", TABLE_SUBDIR)

```

## Table 7: Country Classification (Pattern E)

```{r table-07}
get_group <- function(russian_group, security_group) {
  paste(intersect(russian_group, security_group), collapse = ", ")
}

table_data_7 <- data.frame(
  `Ethnic Russian Population` = c("Low Ethnic", "High Ethnic"),
  `Low Russia Aligned` = c(
    get_group(LOW_RUSSIAN_POP, NEUTRAL_COUNTRIES),
    get_group(HIGH_RUSSIAN_POP, NEUTRAL_COUNTRIES)
  ),
  `High Russia Aligned` = c(
    get_group(LOW_RUSSIAN_POP, CSTO_COUNTRIES),
    get_group(HIGH_RUSSIAN_POP, CSTO_COUNTRIES)
  )
)

table_7 <- table_data_7 %>%
  gt() %>%
  tab_header(
    title = "Ethnic Russian Population x Russia Security Alignment",
    subtitle = "Country Classification"
  ) %>%
  cols_label(
    Ethnic.Russian.Population = "",
    Low.Russia.Aligned = "Low Alignment (Neutral)",
    High.Russia.Aligned = "High Alignment (CSTO)"
  ) %>%
  tab_style(
    style = cell_borders(sides = "all", color = "black", weight = px(1)),
    locations = cells_body()
  )

table_7
save_table(table_7, "table_07_classification", TABLE_SUBDIR)
```

# Supplementary Tables

## Table S1: H1 FE Robustness (Pattern A)

```{r table-s01}
s1_models <- list(
  "(1)" = results_h1$model1_basic,
  "(2)" = results_h1$model1_country_fe,
  "(3)" = results_h1$model1_country_source_fe,
  "(4)" = results_h1$model1_full_linear,
  "(5)" = results_h1$model1_z,
  "(6)" = results_h1$model6_non_mil,
  "(7)" = results_h1$model7_non_nato
)

n_cl_s1 <- sapply(s1_models, get_n_clusters)

rows_s1 <- tibble::tribble(
  ~term,~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7,
  "Topic FEs",      "-",    "-",    "-",    "X",    "X",    "X",    "X",
  "State FEs",      "-",    "X",    "X",    "X",    "-",    "X",    "X",
  "Source FEs",     "-",    "-",    "X",    "X",    "-",    "X",    "X",
  "Source Z-Score", "-",    "-",    "-",    "-",    "X",    "-",    "-",
  "Clusters",       n_cl_s1[1], n_cl_s1[2], n_cl_s1[3], n_cl_s1[4], n_cl_s1[5], n_cl_s1[6], n_cl_s1[7]
)
attr(rows_s1, "position") <- c(3, 4, 5, 6, 7)

note_s1 <- str_wrap(paste(
  SE_NOTE_CLUSTER,
  "Models 1-4 use the full dataset with progressively added fixed effects.",
  "Model 5 uses a Z-Score normalization with the full dataset.",
  "Models 6-7 use full fixed effects, restricting to non-military topics and non-NATO countries respectively."
), 80)

table_s1 <- modelsummary(
  s1_models,
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c("treatment" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE|R2 Within|R2 Within Adj.|nobs.left|nobs.right|bandwidth.left|bandwidth.right",
  title = "H1 RDD — Fixed Effects Robustness (Probabilistic Time)",
  add_rows = rows_s1,
  notes = note_s1
)

table_s1
save_table(table_s1, "table_s01_fe_robustness", TABLE_SUBDIR)
```

## Table S2: H1 By-Topic Z-Score (Pattern C-z, no interaction)

```{r table-s02}
s2_models <- list(
  "Political" = results_h1$model5_opt_pol,
  "Military"  = results_h1$model5_opt_mil,
  "Economic"  = results_h1$model5_opt_econ,
  "Cultural"  = results_h1$model5_opt_cult,
  "Other"     = results_h1$model5_opt_oth
)

n_cl_s2 <- sapply(s2_models, get_n_clusters)

rows_s2 <- tibble::tribble(
  ~term,            ~Political, ~Military, ~Economic, ~Cultural, ~Other,
  "Source Z-Score", "X",        "X",       "X",       "X",       "X",
  "Clusters",       n_cl_s2[1], n_cl_s2[2], n_cl_s2[3], n_cl_s2[4], n_cl_s2[5]
)
attr(rows_s2, "position") <- c(3, 4)

note_s2 <- str_wrap(paste(
  SE_NOTE_CLUSTER,
  "All models use a source-level Z-Score normalization with the optimal bandwidth.",
  "Each column restricts to the indicated topic category."
), 80)

table_s2 <- modelsummary(
  s2_models,
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c("treatment" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE|R2 Within|R2 Within Adj.|nobs.left|nobs.right|bandwidth.left|bandwidth.right",
  title = "H1 RDD by Topic — Z-Score (Probabilistic Time)",
  add_rows = rows_s2,
  notes = note_s2
)

table_s2
save_table(table_s2, "table_s02_h1_z_topic", TABLE_SUBDIR)
```

## Table S3: H2 FE Interaction Core (Pattern B-fe)

```{r table-s03}
s3_models <- list(
  "(1)\u2020" = results_h2$model2a_z,
  "(2)\u2020" = results_h2$model2a,
  "(3)\u2020" = results_h2$model2a_full,
  "(4)\u2020" = results_h2$model2a_opt,
  "(5)\u2020" = results_h2$model2a_opt_full_fe,
  "(6)\u2020" = results_h2$model2b,
  "(7)\u2020" = results_h2$model2d,
  "(8)\u2020" = results_h2$model3a_opt,
  "(9)\u2020" = results_h2$matched_model
)

boot_keys_s3 <- c("model2a_z", "model2a", "model2a_full", "model2a_opt", "model2a_opt_full_fe",
                   "model2b", "model2d", "model3a_opt", "matched_model")
boot_results_s3 <- lapply(boot_keys_s3, function(k) results_h2$bootstrap_se[[k]])

vcov_s3 <- setNames(
  lapply(seq_along(s3_models), function(i) {
    create_bootstrap_vcov(s3_models[[i]], boot_results_s3[[i]], "treatment:state_owned")
  }),
  names(s3_models)
)

n_cl_s3 <- sapply(s3_models, get_n_clusters)

rows_s3 <- tibble::tribble(
  ~term,~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7, ~row8, ~row9,
  "Source Z-Score", "X",    "-",    "-",    "-",    "-",    "-",    "-",    "-",    "-",
  "State FEs",  "-",    "X",    "X",    "X",    "X",    "X",    "X",    "X",    "X",
  "Source FEs", "-",    "-",    "X",    "-",    "X",    "-",    "-",    "-",    "-",
  "Topic FEs",  "-",    "X",    "X",    "X",    "X",    "X",    "X",    "X",    "X",
  "Clusters",   n_cl_s3[1], n_cl_s3[2], n_cl_s3[3], n_cl_s3[4], n_cl_s3[5], n_cl_s3[6], n_cl_s3[7], n_cl_s3[8], n_cl_s3[9]
)
attr(rows_s3, "position") <- c(5, 6, 7, 8, 9)

note_s3 <- str_wrap(paste(
  SE_NOTE_CLUSTER,
  "Model 1 uses a source-level Z-Score normalization with the full dataset.",
  "Model 2 uses the full dataset with state + topic FEs.",
  "Model 3 adds source FEs. Model 4 uses the optimal bandwidth.",
  "Model 5 uses optimal bandwidth with full FEs.",
  "Model 6 omits military topics. Model 7 omits NATO allies.",
  "Model 8 restricts to Russian-related articles. Model 9 uses matched data.",
  SE_NOTE_BOOT
), 80)

table_s3 <- modelsummary(
  s3_models,
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  vcov = vcov_s3,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE|R2 Within|R2 Within Adj.",
  title = "H2 Diff-in-Disc — FE Interaction Core (Probabilistic Time)",
  add_rows = rows_s3,
  notes = note_s3
)

s3_col_names <- names(s3_models)
table_s3 <- override_interaction_stars(table_s3, boot_results_s3, s3_col_names)

table_s3
save_table(table_s3, "table_s03_h2_fe_core", TABLE_SUBDIR)
```

## Table S4: H2 FE Robustness — Full FE + DID (Pattern B-fe)

```{r table-s04}
s4_models <- list(
  "(1)\u2020" = results_h2$model2b_full_fe,
  "(2)\u2020" = results_h2$model3a_opt_full_fe,
  "(3)\u2020" = results_h2$model_did
)

boot_keys_s4 <- c("model2b_full_fe", "model3a_opt_full_fe", "model_did")
boot_results_s4 <- lapply(boot_keys_s4, function(k) results_h2$bootstrap_se[[k]])

vcov_s4 <- setNames(
  lapply(seq_along(s4_models), function(i) {
    create_bootstrap_vcov(s4_models[[i]], boot_results_s4[[i]], "treatment:state_owned")
  }),
  names(s4_models)
)

n_cl_s4 <- sapply(s4_models, get_n_clusters)

rows_s4 <- tibble::tribble(
  ~term,~row1, ~row2, ~row3,
  "State FEs",  "X",    "X",    "X",
  "Source FEs", "X",    "X",    "X",
  "Topic FEs",  "X",    "X",    "X",
  "Clusters",   n_cl_s4[1], n_cl_s4[2], n_cl_s4[3]
)
attr(rows_s4, "position") <- c(5, 6, 7, 8)

note_s4 <- str_wrap(paste(
  SE_NOTE_CLUSTER,
  "Model 1 uses non-military subset with full FEs.",
  "Model 2 uses Russian-related articles with full FEs.",
  "Model 3 is a DID specification within the optimal bandwidth.",
  SE_NOTE_BOOT
), 80)

table_s4 <- modelsummary(
  s4_models,
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  vcov = vcov_s4,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE|R2 Within|R2 Within Adj.",
  title = "H2 Diff-in-Disc — Full FE + DID Robustness (Probabilistic Time)",
  add_rows = rows_s4,
  notes = note_s4
)

s4_col_names <- names(s4_models)
table_s4 <- override_interaction_stars(table_s4, boot_results_s4, s4_col_names)

table_s4
save_table(table_s4, "table_s04_h2_fe_robustness", TABLE_SUBDIR)
```

## Table S5: H2 By-Topic Full Data (Pattern C-fe)

```{r table-s05}
s5_models <- list(
  "Political" = results_h2$model2a_full_pol,
  "Military"  = results_h2$model2a_full_mil,
  "Economic"  = results_h2$model2a_full_econ,
  "Cultural"  = results_h2$model2a_full_cult,
  "Other"     = results_h2$model2a_full_oth
)

boot_keys_s5 <- c("model2a_full_pol", "model2a_full_mil", "model2a_full_econ",
                   "model2a_full_cult", "model2a_full_oth")
boot_results_s5 <- lapply(boot_keys_s5, function(k) results_h2$bootstrap_se[[k]])

vcov_s5 <- setNames(
  lapply(seq_along(s5_models), function(i) {
    create_bootstrap_vcov(s5_models[[i]], boot_results_s5[[i]], "treatment:state_owned")
  }),
  names(s5_models)
)

n_cl_s5 <- sapply(s5_models, get_n_clusters)

rows_s5 <- tibble::tribble(
  ~term,        ~Political, ~Military, ~Economic, ~Cultural, ~Other,
  "State FEs",  "X",        "X",       "X",       "X",       "X",
  "Source FEs", "-",        "-",       "-",       "-",       "-",
  "Topic FEs",  "-",        "-",       "-",       "-",       "-",
  "Clusters",   n_cl_s5[1], n_cl_s5[2], n_cl_s5[3], n_cl_s5[4], n_cl_s5[5]
)
attr(rows_s5, "position") <- c(5, 6, 7, 8)

note_s5 <- str_wrap(paste(
  SE_NOTE_CLUSTER,
  "All models use the optimal bandwidth with state fixed effects.",
  "Each column restricts to the indicated topic category.",
  SE_NOTE_BOOT
), 80)

table_s5 <- modelsummary(
  s5_models,
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  vcov = vcov_s5,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State Owned x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE|R2 Within|R2 Within Adj.",
  title = "H2 Diff-in-Disc by Topic — Full Data (Probabilistic Time)",
  add_rows = rows_s5,
  notes = note_s5
)

s5_col_names <- names(s5_models)
table_s5 <- override_interaction_stars(table_s5, boot_results_s5, s5_col_names)

table_s5
save_table(table_s5, "table_s05_h2_fe_topic", TABLE_SUBDIR)
```

## Table S6: H2 LOO Robustness (Pattern E)

```{r table-s06}
build_loo_table <- function(loo_data, title, subtitle, note) {
  loo_data %>%
    mutate(
      estimate_fmt = sprintf("%.3f%s", estimate,
                       case_when(p_value < 0.001 ~ "***",
                                 p_value < 0.01 ~ "**",
                                 p_value < 0.05 ~ "*",
                                 TRUE ~ "")),
      std_error_fmt = sprintf("(%.3f)", std_error),
      p_value_fmt = sprintf("%.3f", p_value),
      n_obs_fmt = format(n_obs, big.mark = ","),
      bandwidth_fmt = sprintf("%.1f", bandwidth)
    ) %>%
    select(country_dropped, estimate_fmt, std_error_fmt, p_value_fmt, n_obs_fmt, bandwidth_fmt) %>%
    gt() %>%
    cols_label(
      country_dropped = "Country Dropped",
      estimate_fmt = "Coefficient",
      std_error_fmt = "Std. Error",
      p_value_fmt = "p-value",
      n_obs_fmt = "N",
      bandwidth_fmt = "Bandwidth"
    ) %>%
    tab_header(title = title, subtitle = subtitle) %>%
    tab_footnote(footnote = str_wrap(note, 80))
}


note_loo_h2 <- "Leave-one-out robustness analysis. Each row shows results when excluding the specified country. Bandwidth is recalculated for each subset. Coefficient shown is for the treatment:state_owned interaction term. Standard errors clustered at source domain level."


# Combine standard and matched LOO summaries
loo_standard <- results_h2$loo_summary %>% mutate(section = "Standard Model")
loo_matched <- results_h2$matched_loo_summary %>% mutate(section = "Matched Model")
loo_combined <- bind_rows(loo_standard, loo_matched)

table_s6 <- loo_combined %>%
  mutate(
    estimate_fmt = sprintf("%.3f%s", estimate,
                     case_when(p_value < 0.001 ~ "***",
                               p_value < 0.01 ~ "**",
                               p_value < 0.05 ~ "*",
                               TRUE ~ "")),
    std_error_fmt = sprintf("(%.3f)", std_error),
    p_value_fmt = sprintf("%.3f", p_value),
    n_obs_fmt = format(n_obs, big.mark = ","),
    bandwidth_fmt = sprintf("%.1f", bandwidth)
  ) %>%
  select(section, country_dropped, estimate_fmt, std_error_fmt, p_value_fmt, n_obs_fmt, bandwidth_fmt) %>%
  gt(groupname_col = "section") %>%
  cols_label(
    country_dropped = "Country Dropped",
    estimate_fmt = "Coefficient",
    std_error_fmt = "Std. Error",
    p_value_fmt = "p-value",
    n_obs_fmt = "N",
    bandwidth_fmt = "Bandwidth"
  ) %>%
  tab_header(title = "H2 Leave-One-Out Country Robustness (Probabilistic Time)") %>%
  tab_footnote(footnote = str_wrap(note_loo_h2, 80))

table_s6
save_table(table_s6, "table_s06_h2_loo", TABLE_SUBDIR)

```

## Table S7: H3a FE Interaction + Full FE Robustness (Pattern B-fe)

```{r table-s07}
s7_models <- list(
  "(1)\u2020" = results_align$model5a_z,
  "(2)\u2020" = results_align$model5a_full,
  "(3)\u2020" = results_align$model5a_opt,
  "(4)\u2020" = results_align$model5a_opt_non_mil,
  "(5)\u2020" = results_align$model5a_opt_russian,
  "(6)\u2020" = results_align$model5a_opt_full_fe,
  "(7)\u2020" = results_align$matched_model,
  "(8)\u2020" = results_align$model5a_opt_non_mil_full_fe,
  "(9)\u2020" = results_align$model5a_opt_rus_full_fe
)

boot_keys_s7 <- c("model5a_z", "model5a_full", "model5a_opt", "model5a_opt_non_mil",
                   "model5a_opt_russian", "model5a_opt_full_fe", "matched_model",
                   "model5a_opt_non_mil_full_fe", "model5a_opt_rus_full_fe")
boot_results_s7 <- lapply(boot_keys_s7, function(k) results_align$bootstrap_se[[k]])

vcov_s7 <- setNames(
  lapply(seq_along(s7_models), function(i) {
    create_bootstrap_vcov(s7_models[[i]], boot_results_s7[[i]], "treatment:csto")
  }),
  names(s7_models)
)

n_cl_s7 <- sapply(s7_models, get_n_clusters)

rows_s7 <- tibble::tribble(
  ~term,~row1, ~row2, ~row3, ~row4, ~row5, ~row6, ~row7, ~row8, ~row9,
  "Source Z-Score", "X",    "-",    "-",    "-",    "-",    "-",    "-",    "-",    "-",
  "State FEs",  "-",    "X",    "X",    "X",    "X",    "X",    "X",    "X",    "X", 
  "Source FEs", "-",    "-",    "-",    "-",    "-",    "X",    "-",    "X",    "X", 
  "Topic FEs",  "-",    "X",    "X",    "X",    "X",    "X",    "X",    "X",    "X", 
  "Matched",    "-",    "-",    "-",    "-",    "-",    "-",    "X",    "-",    "-",
  "Clusters",   n_cl_s7[1], n_cl_s7[2], n_cl_s7[3], n_cl_s7[4], n_cl_s7[5], n_cl_s7[6], n_cl_s7[7], n_cl_s7[8], n_cl_s7[9]
)
attr(rows_s7, "position") <- c(5, 6, 7, 8, 9, 10)

note_s7 <- str_wrap(paste(
  SE_NOTE_CLUSTER,
  "Sample restricted to state-owned media in non-NATO countries.",
  "Model 1 uses a source-level Z-Score normalization with the full dataset.",
  "Model 2 uses the full dataset with FEs. Model 3 uses the optimal bandwidth.",
  "Model 4 omits military topics. Model 5 restricts to Russian-related articles.",
  "Model 6 uses optimal bandwidth with full FEs. Model 7 uses matched data.",
  "Models 8-9 add full FEs to non-military and Russian subsets.",
  SE_NOTE_BOOT
), 80)

table_s7 <- modelsummary(
  s7_models,
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  vcov = vcov_s7,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE|R2 Within|R2 Within Adj.",
  title = "H3a Alignment — FE Interaction + Robustness (Probabilistic Time)",
  add_rows = rows_s7,
  notes = note_s7
)

s7_col_names <- names(s7_models)
table_s7 <- override_interaction_stars(table_s7, boot_results_s7, s7_col_names)

table_s7
save_table(table_s7, "table_s07_h3a_fe_core", TABLE_SUBDIR)
```

## Table S8: H3a By-Topic Z-Score — CSTO Alignment (Pattern C-z)

```{r table-s08}
# NOTE: These Z-score by-topic alignment models may not exist yet
h3a_topic_z_models <- list(
  "Political" = results_align$model5a_opt_pol,
  "Military"  = results_align$model5a_opt_mil,
  "Economic"  = results_align$model5a_opt_econ,
  "Cultural"  = results_align$model5a_opt_cult,
  "Other"     = results_align$model5a_opt_oth
)

boot_keys_s8z <- c("model5a_opt_z_pol", "model5a_opt_z_mil", "model5a_opt_z_econ",
                   "model5a_opt_z_cult", "model5a_opt_z_oth")
boot_results_s8z <- lapply(boot_keys_s8z, function(k) results_align$bootstrap_se[[k]])

vcov_s8z <- list(
  "Political" = create_bootstrap_vcov(h3a_topic_z_models[["Political"]], boot_results_s8z[[1]], "treatment:csto"),
  "Military"  = create_bootstrap_vcov(h3a_topic_z_models[["Military"]],  boot_results_s8z[[2]], "treatment:csto"),
  "Economic"  = create_bootstrap_vcov(h3a_topic_z_models[["Economic"]],  boot_results_s8z[[3]], "treatment:csto"),
  "Cultural"  = create_bootstrap_vcov(h3a_topic_z_models[["Cultural"]],  boot_results_s8z[[4]], "treatment:csto"),
  "Other"     = create_bootstrap_vcov(h3a_topic_z_models[["Other"]],     boot_results_s8z[[5]], "treatment:csto")
)

n_cl_s8z <- sapply(h3a_topic_z_models, get_n_clusters)

rows_s8z <- tibble::tribble(
  ~term,            ~Political, ~Military, ~Economic, ~Cultural, ~Other,
  "Source Z-Score", "X",        "X",       "X",       "X",       "X",
  "Clusters",       n_cl_s8z[1], n_cl_s8z[2], n_cl_s8z[3], n_cl_s8z[4], n_cl_s8z[5]
)
attr(rows_s8z, "position") <- c(5, 6)

note_s8z <- str_wrap(paste(
  "All models use a source-level Z-Score normalization with the optimal bandwidth.",
  "Sample restricted to state-owned media in non-NATO countries.",
  "Each column restricts to the indicated topic category.", SE_NOTE
), 80)

table_s8z <- modelsummary(
  h3a_topic_z_models,
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  vcov = vcov_s8z,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE|R2 Within|R2 Within Adj.",
  title = "H3a Alignment by Topic — Z-Score (Probabilistic Time)",
  add_rows = rows_s8z,
  notes = note_s8z
)

s8z_col_names <- c("Political", "Military", "Economic", "Cultural", "Other")
table_s8z <- override_interaction_stars(table_s8z, boot_results_s8z, s8z_col_names)

table_s8z
save_table(table_s8z, "table_s08_h3a_z_topic", TABLE_SUBDIR)

```

## Table S9: H3a By-Topic Full Data (Pattern C-fe)

```{r table-s09-fe-topic}
s9_models <- list(
  "Political" = results_align$model5a_full_pol,
  "Military"  = results_align$model5a_full_mil,
  "Economic"  = results_align$model5a_full_econ,
  "Cultural"  = results_align$model5a_full_cult,
  "Other"     = results_align$model5a_full_oth
)

boot_keys_s9 <- c("model5a_full_pol", "model5a_full_mil", "model5a_full_econ",
                   "model5a_full_cult", "model5a_full_oth")
boot_results_s9 <- lapply(boot_keys_s9, function(k) results_align$bootstrap_se[[k]])

vcov_s9 <- setNames(
  lapply(seq_along(s9_models), function(i) {
    create_bootstrap_vcov(s9_models[[i]], boot_results_s9[[i]], "treatment:csto")
  }),
  names(s9_models)
)

n_cl_s9 <- sapply(s9_models, get_n_clusters)

rows_s9 <- tibble::tribble(
  ~term,        ~Political, ~Military, ~Economic, ~Cultural, ~Other,
  "State FEs",  "X",        "X",       "X",       "X",       "X",
  "Source FEs", "-",        "-",       "-",       "-",       "-",
  "Topic FEs",  "-",        "-",       "-",       "-",       "-",
  "Clusters",   n_cl_s9[1], n_cl_s9[2], n_cl_s9[3], n_cl_s9[4], n_cl_s9[5]
)
attr(rows_s9, "position") <- c(5, 6, 7, 8)

note_s9 <- str_wrap(paste(
  SE_NOTE_CLUSTER,
  "Sample restricted to state-owned media in non-NATO countries.",
  "All models use the optimal bandwidth with state fixed effects.",
  "Each column restricts to the indicated topic category.",
  SE_NOTE_BOOT
), 80)

table_s9 <- modelsummary(
  s9_models,
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  vcov = vcov_s9,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE|R2 Within|R2 Within Adj.",
  title = "H3a Alignment by Topic — Full Data (Probabilistic Time)",
  add_rows = rows_s9,
  notes = note_s9
)

s9_col_names <- names(s9_models)
table_s9 <- override_interaction_stars(table_s9, boot_results_s9, s9_col_names)

table_s9
save_table(table_s9, "table_s09_h3a_fe_topic", TABLE_SUBDIR)
```

## Table S10: H3a LOO Robustness (Pattern E)

```{r table-s10-loo}

note_loo_h3a <- "Leave-one-out robustness analysis. Each row shows results when excluding the specified country. Bandwidth is recalculated for each subset. Coefficient shown is for the treatment:csto interaction term. Standard errors clustered at source domain level."


loo_standard_h3a <- results_align$loo_summary %>% mutate(section = "Standard Model")
loo_matched_h3a <- results_align$matched_loo_summary %>% mutate(section = "Matched Model")
loo_combined_h3a <- bind_rows(loo_standard_h3a, loo_matched_h3a)

table_s10 <- loo_combined_h3a %>%
  mutate(
    estimate_fmt = sprintf("%.3f%s", estimate,
                     case_when(p_value < 0.001 ~ "***",
                               p_value < 0.01 ~ "**",
                               p_value < 0.05 ~ "*",
                               TRUE ~ "")),
    std_error_fmt = sprintf("(%.3f)", std_error),
    p_value_fmt = sprintf("%.3f", p_value),
    n_obs_fmt = format(n_obs, big.mark = ","),
    bandwidth_fmt = sprintf("%.1f", bandwidth)
  ) %>%
  select(section, country_dropped, estimate_fmt, std_error_fmt, p_value_fmt, n_obs_fmt, bandwidth_fmt) %>%
  gt(groupname_col = "section") %>%
  cols_label(
    country_dropped = "Country Dropped",
    estimate_fmt = "Coefficient",
    std_error_fmt = "Std. Error",
    p_value_fmt = "p-value",
    n_obs_fmt = "N",
    bandwidth_fmt = "Bandwidth"
  ) %>%
  tab_header(title = "H3a Leave-One-Out Country Robustness (Probabilistic Time)") %>%
  tab_footnote(footnote = str_wrap(note_loo_h3a, 80))

table_s10
save_table(table_s10, "table_s10_h3a_loo", TABLE_SUBDIR)
```

## Table S11: H3a Heterogenous Treatment Effects

```{r table-s11-decomposition}
decomp <- results_align$decomposition
pairs  <- decomp$group_effects_pairs
bayes  <- decomp$group_effects_bayes

# --- Panel A: Group-level effects with both bootstrap methods side-by-side ---
panel_a <- pairs %>%
  rename(se_pairs = se_boot, p_pairs = p_boot, 
         ci_lower_pairs = ci_lower, ci_upper_pairs = ci_upper) %>%
  mutate(
    se_bayes = bayes$se_boot,
    p_bayes  = bayes$p_boot,
    section  = "Panel A: Group-Level Effects",
    estimate_fmt = sprintf("%.3f", estimate),
    se_pairs_fmt = sprintf("(%.3f)", se_pairs),
    p_pairs_fmt  = sprintf("%.3f%s", p_pairs,
                     case_when(p_pairs < 0.001 ~ "***",
                               p_pairs < 0.01 ~ "**",
                               p_pairs < 0.05 ~ "*",
                               p_pairs < 0.1 ~ "+",
                               TRUE ~ "")),
    se_bayes_fmt = sprintf("(%.3f)", se_bayes),
    p_bayes_fmt  = sprintf("%.3f%s", p_bayes,
                     case_when(p_bayes < 0.001 ~ "***",
                               p_bayes < 0.01 ~ "**",
                               p_bayes < 0.05 ~ "*",
                               p_bayes < 0.1 ~ "+",
                               TRUE ~ "")),
    n_col = c(decomp$n_sources_csto, 
              decomp$n_sources_non_csto,
              decomp$n_sources_csto + decomp$n_sources_non_csto)
  ) %>%
  select(section, group, estimate_fmt, se_pairs_fmt, p_pairs_fmt,
         se_bayes_fmt, p_bayes_fmt, n_col)

# --- Panel B: Source-level effects ---
panel_b <- decomp$source_effects %>%
  mutate(
    section = "Panel B: Source-Level Effects",
    group = ifelse(csto == 1, paste0(source, " (CSTO)"), paste0(source, " (Neutral)")),
    estimate_fmt = sprintf("%.3f", theta),
    se_pairs_fmt = "",
    p_pairs_fmt  = "",
    se_bayes_fmt = "",
    p_bayes_fmt  = "",
    n_col = N
  ) %>%
  arrange(desc(csto), source) %>%
  select(section, group, estimate_fmt, se_pairs_fmt, p_pairs_fmt,
         se_bayes_fmt, p_bayes_fmt, n_col)

# Combine panels
decomp_combined <- bind_rows(panel_a, panel_b)

note_decomp <- str_wrap(paste(
  "Panel A reports N-weighted average treatment effects by CSTO group,",
  "estimated from separate RDD regressions within each source-topic cell.",
  "Pairs bootstrap resamples sources with replacement (B =",
  sprintf("%s).", format(decomp$B, big.mark = ",")),
  "Bayesian bootstrap draws Dirichlet(1,...,1) source weights",
  sprintf("(Rubin 1981; B = %s).", format(decomp$B, big.mark = ",")),
  "Panel B reports source-level treatment effects (N-weighted average",
  "across topics within each source). N in Panel A is number of sources;",
  "N in Panel B is articles per source.",
  "Sample restricted to state-owned, non-NATO, non-military articles",
  "within the optimal bandwidth. Source-level Z-score normalization applied."
), 80)

table_s11 <- decomp_combined %>%
  gt(groupname_col = "section") %>%
  cols_label(
    group = "",
    estimate_fmt = "Estimate",
    se_pairs_fmt = "SE (Pairs)",
    p_pairs_fmt  = "p (Pairs)",
    se_bayes_fmt = "SE (Bayes)",
    p_bayes_fmt  = "p (Bayes)",
    n_col = "N"
  ) %>%
  tab_header(
    title = "Treatment Effect Decomposition by Source"
  ) %>%
  tab_footnote(footnote = note_decomp) %>%
  sub_values(values = "", replacement = "\u2014")

table_s11
save_table(table_s11, "table_s11_decomposition", TABLE_SUBDIR)

```

## Table S12: Placebo Test Summary (Pattern E)

```{r table-s12}
# H1 placebo (rdrobust)
placebo_h1 <- results_h1$model_placebo
h1_estimate <- placebo_h1$coef[1]
h1_se <- placebo_h1$se[1]
h1_pval <- placebo_h1$pv[1]
h1_bw <- placebo_h1$bws[1, 1]
h1_n <- placebo_h1$N_h[1] + placebo_h1$N_h[2]

# H1 placebo Z-score (rdrobust)
has_h1_z_placebo <- !is.null(results_h1$model_placebo_z)
if (has_h1_z_placebo) {
  placebo_h1z <- results_h1$model_placebo_z
  h1z_estimate <- placebo_h1z$coef[1]
  h1z_se <- placebo_h1z$se[1]
  h1z_pval <- placebo_h1z$pv[1]
  h1z_bw <- placebo_h1z$bws[1, 1]
  h1z_n <- placebo_h1z$N_h[1] + placebo_h1z$N_h[2]
}

# H2 placebo (felm)
placebo_h2 <- results_h2$model_placebo
placebo_h2_boot <- results_h2$bootstrap_se$model_placebo
h2_coef <- summary(placebo_h2)$coeftable["treatment:state_owned",]

# H3a placebo (felm)
placebo_h3 <- results_align$model_placebo_nonmil
placebo_h3_boot <- results_align$bootstrap_se$model_placebo_nonmil
h3_coef <- summary(placebo_h3)$coeftable["treatment:csto",]

# Build summary
if (has_h1_z_placebo) {
  placebo_summary <- tibble(
    Model = c("(1) H1: Full Model (RDD)",
              "(2) H1: Z-Score (RDD)",
              "(3) H2: Diff-in-Disc",
              "(4) H3: Non-Military"),
    Estimate = c(h1_estimate, h1z_estimate, h2_coef["Estimate"], h3_coef["Estimate"]),
    Std_Error = c(h1_se, h1z_se, placebo_h2_boot$se, placebo_h3_boot$se),
    p_value = c(h1_pval, h1z_pval, placebo_h2_boot$p_val, placebo_h3_boot$p_val),
    Bandwidth = c(h1_bw, h1z_bw, results_h2$optimal_bw_placebo, results_align$optimal_bw_placebo_nonmil),
    N = c(h1_n, h1z_n, nobs(placebo_h2), nobs(placebo_h3))
  )
} else {
  placebo_summary <- tibble(
    Model = c("(1) H1: Full Model (RDD)",
              "(2) H2: Diff-in-Disc",
              "(3) H3: Non-Military"),
    Estimate = c(h1_estimate, h2_coef["Estimate"], h3_coef["Estimate"]),
    Std_Error = c(h1_se, placebo_h2_boot$se, placebo_h3_boot$se),
    p_value = c(h1_pval, placebo_h2_boot$p_val, placebo_h3_boot$p_val),
    Bandwidth = c(h1_bw, results_h2$optimal_bw_placebo, results_align$optimal_bw_placebo_nonmil),
    N = c(h1_n, nobs(placebo_h2), nobs(placebo_h3))
  )
}

note_placebo <- str_wrap(paste(
  "Placebo tests using December 7, 2021 (Biden's announcement) as a false treatment date.",
  "Data restricted to pre-invasion period (before Feb 19, 2022).",
  "Model 1 uses rdrobust; remaining models use felm with optimal bandwidth.",
  "Non-significant treatment effects suggest parallel trends assumption holds."
), 80)

table_s12 <- placebo_summary %>%
  mutate(
    Estimate_fmt = sprintf("%.3f%s", Estimate,
                     case_when(p_value < 0.001 ~ "***",
                               p_value < 0.01 ~ "**",
                               p_value < 0.05 ~ "*",
                               TRUE ~ "")),
    Std_Error_fmt = sprintf("(%.3f)", Std_Error),
    p_value_fmt = sprintf("%.3f", p_value),
    Bandwidth_fmt = sprintf("%.1f", Bandwidth),
    N_fmt = format(N, big.mark = ",")
  ) %>%
  select(Model, Estimate_fmt, Std_Error_fmt, p_value_fmt, Bandwidth_fmt, N_fmt) %>%
  gt() %>%
  cols_label(
    Model = "Model",
    Estimate_fmt = "Estimate",
    Std_Error_fmt = "Std. Error",
    p_value_fmt = "p-value",
    Bandwidth_fmt = "Bandwidth",
    N_fmt = "N"
  ) %>%
  tab_header(title = "Placebo Test Summary (Probabilistic Time)",
             subtitle = "December 7, 2021 False Treatment Date") %>%
  tab_footnote(footnote = note_placebo)

table_s12
save_table(table_s12, "table_s12_placebo", TABLE_SUBDIR)
```


## Table S13: Placebo Test, Russia-Aligned State Media (Dec 7, 2021)

```{r table-s13}
# Dec-7 placebo restricted to state-owned media in the Russia-aligned group,
# estimated separately per country (rdrobust on the source-level z-scored outcome;
# MSE-optimal bandwidth; default HC SEs). Countries are shown side-by-side as columns,
# with the pooled all-aligned estimate in a final column.
placebo_models <- results_align$placebo_aligned_models
placebo_pooled <- results_align$placebo_aligned_pooled

# Keep the aligned-country ordering; guard against any country that failed to estimate
placebo_country_order <- CSTO_COUNTRIES[CSTO_COUNTRIES %in% names(placebo_models)]

# Format one rdrobust model into a column of table statistics (in row order below)
format_placebo_col <- function(m) {
  stars <- case_when(m$pv[1] < 0.001 ~ "***",
                     m$pv[1] < 0.01 ~ "**",
                     m$pv[1] < 0.05 ~ "*",
                     TRUE ~ "")
  c(
    sprintf("%.3f%s", m$coef[1], stars),
    sprintf("(%.3f)", m$se[1]),
    sprintf("[%.3f, %.3f]", m$ci[1, 1], m$ci[1, 2]),
    sprintf("%.3f", m$pv[1]),
    sprintf("%.1f", m$bws[1, 1]),
    format(m$N_h[1] + m$N_h[2], big.mark = ",")
  )
}

# Rows = statistics; one column per aligned country
placebo_aligned_summary <- tibble(
  Statistic = c("Estimate", "Std. Error", "95% CI", "p-value", "Bandwidth", "N")
)
for (cntry in placebo_country_order) {
  placebo_aligned_summary[[cntry]] <- format_placebo_col(placebo_models[[cntry]])
}

# Pooled column: the same specification estimated across all four aligned countries
# at once. Reported with the same HC variance as the per-country columns so the
# columns are directly comparable; the source-clustered pooled variant is in
# figures/tables/prob/placebo_aligned_estimates.csv.
if (!is.null(placebo_pooled)) {
  placebo_aligned_summary[["All Aligned"]] <- format_placebo_col(placebo_pooled)
} else {
  warning("placebo_aligned_pooled not found in 06_alignment_results_prob.rds; ",
          "table S13 built without the pooled column.")
}

note_placebo_aligned <- str_wrap(paste(
  "Placebo tests using December 7, 2021 (US public warning of the buildup) as a false",
  "treatment date, restricted to state-owned media in the Russia-aligned countries,",
  "non-military topics, pre-invasion period (before Feb 19, 2022). Each column is a",
  "separate rdrobust fit on the source-level z-scored outcome with the MSE-optimal",
  "bandwidth. Columns 1-4 are estimated country by country; the final column pools all",
  "four aligned countries. Standard errors are rdrobust default (nearest-neighbor",
  "heteroskedasticity-robust); source clustering is not used, because each country has",
  "only 2-3 state-owned sources and the pooled column is reported on the same basis for",
  "comparability. Non-significant discontinuities indicate no pre-invasion jump at the",
  "warning date."
), 80)

table_s13 <- placebo_aligned_summary %>%
  gt() %>%
  cols_label(Statistic = "") %>%
  tab_header(title = paste("Placebo Test: Russia-Aligned State Media by Country and Pooled",
                           "(Probabilistic Time)"),
             subtitle = "December 7, 2021 False Treatment Date") %>%
  tab_footnote(footnote = note_placebo_aligned)

table_s13
save_table(table_s13, "table_s13_placebo_aligned", TABLE_SUBDIR)
```


## Table S14: Total Effect, No Topic Adjustment

The main specifications all condition on topic, so they identify the shift in
sentiment *within* topics. The total effect instead lets the topic mix move,
which is what a reader of these outlets experiences. It is a distinct estimand,
not a robustness check, and **it does not appear in the main paper** — each panel
below defines it explicitly.

Reported as three per-hypothesis panels rather than one wide table, because the
three carry different coefficients and, for H2 and H3a, different sample caveats.

Columns run **full sample, then total effect, then main**, so that the two
comparisons a reader needs are adjacent: column 1 against column 2 isolates the
effect of dropping the topic adjustment on a fixed sample, and column 2 against
column 3 shows what the sample restriction does. H1 has no separate full-sample
column, because its main specification already uses all articles; its two columns
are total then main, keeping the main specification last in every panel.

**The comparison is not symmetric across hypotheses.** For H1, main and total sit
on the same sample and the pair is like-for-like. For H2 and H3a the main
specification omits military coverage, which has no total-effect analogue by
construction: the largest post-invasion shift in topic composition is toward
military coverage, so a total effect that excluded it would drop most of the
channel it exists to measure. Those two panels therefore carry the full-sample
topic-adjusted column as a like-for-like comparator, and say so in the notes.

```{r table-s14}
# Shared note text, since all three panels describe the same estimand
S14_NOTE_CORE <- paste(
  "The total-effect model removes the topic adjustment. It is a distinct",
  "estimand, not a robustness check: it lets the topic composition of coverage",
  "move rather than holding it fixed. Outcome, source clustering and bandwidth",
  "procedure are otherwise unchanged, with the bandwidth re-selected without",
  "topic."
)

S14_NOTE_ASYMMETRY <- paste(
  "The main specification omits military coverage, so the total effect is",
  "estimated on the full sample and Model 1 is its like-for-like comparator.",
  "Model 1 against Model 2 isolates the topic adjustment; Model 2 against",
  "Model 3 shows the effect of the sample restriction."
)

# Effective N, since modelsummary reports the full sample for rdrobust but the
# bandwidth-restricted sample for feols
effective_n <- function(m) {
  if (inherits(m, "rdrobust")) format(m$N_h[1] + m$N_h[2], big.mark = ",")
  else format(nobs(m), big.mark = ",")
}

# --- Panel A: H1 -----------------------------------------------------------
s14a_models <- list(
  "(1) Total‡" = results_h1$model5_opt_total,
  "(2) Main‡"  = results_h1$model5_opt
)

rows_s14a <- tibble::tribble(
  ~term,                  ~c1, ~c2,
  "Topic FEs",            "-", "X",
  "Source Z-Score",       "X", "X",
  "N (within bandwidth)", effective_n(s14a_models[[1]]), effective_n(s14a_models[[2]]),
  "Clusters",             get_n_clusters(s14a_models[[1]]), get_n_clusters(s14a_models[[2]])
)
attr(rows_s14a, "position") <- NULL

table_s14a <- modelsummary(
  s14a_models,
  output = "gt", fmt = fmt_significant(2), stars = TRUE,
  coef_map = c("treatment" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE|R2 Within|R2 Within Adj.|Num.Obs.|nobs.left|nobs.right|bandwidth.left|bandwidth.right",
  title = "Total Effect Without Topic Adjustment — H1 (Probabilistic Time)",
  add_rows = rows_s14a,
  notes = str_wrap(paste(
    S14_NOTE_CORE,
    "Model 2 is Table 1 Model 5, the main H1 specification, which already uses",
    "all articles including military coverage, so both models share a sample and",
    "no separate comparator is needed.",
    SE_NOTE_RDROBUST), 80)
)

table_s14a
save_table(table_s14a, "table_s14a_total_effect_h1", TABLE_SUBDIR)

# --- Panel B: H2 -----------------------------------------------------------
s14b_models <- list(
  "(1) Full Sample†" = results_h2$model2d_z_alltopic,
  "(2) Total†"       = results_h2$model2d_z_total,
  "(3) Main†"        = results_h2$model2d_z
)
boot_s14b <- list(
  results_h2$bootstrap_se[["model2d_z_alltopic"]],
  results_h2$bootstrap_se[["model2d_z_total"]],
  results_h2$bootstrap_se[["model2d_z"]]
)
vcov_s14b <- setNames(
  lapply(seq_along(s14b_models), function(k)
    create_bootstrap_vcov(s14b_models[[k]], boot_s14b[[k]], "treatment:state_owned")),
  names(s14b_models))

rows_s14b <- tibble::tribble(
  ~term,                  ~c1, ~c2, ~c3,
  "Topic FEs",            "X", "-", "X",
  "Military Included",    "X", "X", "-",
  "Source Z-Score",       "X", "X", "X",
  "N (within bandwidth)", effective_n(s14b_models[[1]]), effective_n(s14b_models[[2]]),
                          effective_n(s14b_models[[3]]),
  "Clusters",             get_n_clusters(s14b_models[[1]]), get_n_clusters(s14b_models[[2]]),
                          get_n_clusters(s14b_models[[3]])
)
attr(rows_s14b, "position") <- NULL

table_s14b <- modelsummary(
  s14b_models,
  output = "gt", fmt = fmt_significant(2), stars = TRUE, vcov = vcov_s14b,
  coef_map = c("treatment" = "Invasion",
               "treatment:state_owned" = "State-Owned x Treat"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE|R2 Within|R2 Within Adj.|Num.Obs.",
  title = "Total Effect Without Topic Adjustment — H2 (Probabilistic Time)",
  add_rows = rows_s14b,
  notes = str_wrap(paste(
    S14_NOTE_CORE,
    "Model 1, the full sample model, is unreported in the main text. It is the",
    "hypothesis 2 interaction estimated on the non-NATO sample, but with all",
    "topics included.",
    "Model 3 is Table 2 Model 5, the main H2 specification.",
    S14_NOTE_ASYMMETRY,
    SE_NOTE_BOOT), 80)
)

table_s14b <- override_interaction_stars(table_s14b, boot_s14b, names(s14b_models))
table_s14b
save_table(table_s14b, "table_s14b_total_effect_h2", TABLE_SUBDIR)

# --- Panel C: H3a ----------------------------------------------------------
s14c_models <- list(
  "(1) Full Sample†" = results_align$model5a_opt_z,
  "(2) Total†"       = results_align$model5a_opt_z_total,
  "(3) Main†"        = results_align$model5a_opt_non_mil_z
)
boot_s14c <- list(
  results_align$bootstrap_se[["model5a_opt_z"]],
  results_align$bootstrap_se[["model5a_opt_z_total"]],
  results_align$bootstrap_se[["model5a_opt_non_mil_z"]]
)
vcov_s14c <- setNames(
  lapply(seq_along(s14c_models), function(k)
    create_bootstrap_vcov(s14c_models[[k]], boot_s14c[[k]], "treatment:csto")),
  names(s14c_models))

rows_s14c <- tibble::tribble(
  ~term,                  ~c1, ~c2, ~c3,
  "Topic FEs",            "X", "-", "X",
  "Military Included",    "X", "X", "-",
  "Source Z-Score",       "X", "X", "X",
  "N (within bandwidth)", effective_n(s14c_models[[1]]), effective_n(s14c_models[[2]]),
                          effective_n(s14c_models[[3]]),
  "Clusters",             get_n_clusters(s14c_models[[1]]), get_n_clusters(s14c_models[[2]]),
                          get_n_clusters(s14c_models[[3]])
)
attr(rows_s14c, "position") <- NULL

table_s14c <- modelsummary(
  s14c_models,
  output = "gt", fmt = fmt_significant(2), stars = TRUE, vcov = vcov_s14c,
  coef_map = c("treatment" = "Invasion",
               "treatment:csto" = "Russia-Aligned x Treat"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE|R2 Within|R2 Within Adj.|Num.Obs.",
  title = "Total Effect Without Topic Adjustment — H3a (Probabilistic Time)",
  add_rows = rows_s14c,
  notes = str_wrap(paste(
    S14_NOTE_CORE,
    "Sample is state-owned media in non-NATO countries.",
    "Model 1 is Table 4 Model 3; Model 3 is Table 4 Model 4, the main H3a",
    "specification.",
    S14_NOTE_ASYMMETRY,
    SE_NOTE_BOOT), 80)
)

table_s14c <- override_interaction_stars(table_s14c, boot_s14c, names(s14c_models))
table_s14c
save_table(table_s14c, "table_s14c_total_effect_h3a", TABLE_SUBDIR)
```

### Total Effect vs Main: Printed Comparison

Writes the paired comparison to CSV so the estimates, standard errors and sample
sizes behind the three panels are available without re-reading the tables. Rows
follow the same order as the panels.

```{r table-s14-comparison}
# rdrobust and fixest expose their estimates differently; one row-builder each
row_rd <- function(m, spec, kind) {
  tibble(spec = spec, kind = kind, term = "treatment",
         estimate = m$coef[1], std_error = m$se[1], p_value = m$pv[1],
         n_obs = m$N_h[1] + m$N_h[2], bandwidth = m$bws[1, 1],
         boot_p = NA_real_)
}
row_fe <- function(m, spec, kind, term, boot) {
  tibble(spec = spec, kind = kind, term = term,
         estimate = unname(coef(m)[term]),
         std_error = if (!is.null(boot$se)) boot$se else unname(se(m)[term]),
         p_value = unname(pvalue(m)[term]),
         n_obs = nobs(m), bandwidth = NA_real_,
         boot_p = if (!is.null(boot$p_val)) boot$p_val else NA_real_)
}

total_effect_comparison <- bind_rows(
  row_rd(results_h1$model5_opt_total, "H1", "total"),
  row_rd(results_h1$model5_opt,       "H1", "main"),

  row_fe(results_h2$model2d_z_alltopic, "H2", "full sample, topic-adjusted",
         "treatment:state_owned", results_h2$bootstrap_se[["model2d_z_alltopic"]]),
  row_fe(results_h2$model2d_z_total, "H2", "total",
         "treatment:state_owned", results_h2$bootstrap_se[["model2d_z_total"]]),
  row_fe(results_h2$model2d_z, "H2", "main",
         "treatment:state_owned", results_h2$bootstrap_se[["model2d_z"]]),

  row_fe(results_align$model5a_opt_z, "H3a", "full sample, topic-adjusted",
         "treatment:csto", results_align$bootstrap_se[["model5a_opt_z"]]),
  row_fe(results_align$model5a_opt_z_total, "H3a", "total",
         "treatment:csto", results_align$bootstrap_se[["model5a_opt_z_total"]]),
  row_fe(results_align$model5a_opt_non_mil_z, "H3a", "main",
         "treatment:csto", results_align$bootstrap_se[["model5a_opt_non_mil_z"]])
)

print(as.data.frame(total_effect_comparison), row.names = FALSE, digits = 4)

write_csv(total_effect_comparison,
          file.path(FIGURES_TABLES, TABLE_SUBDIR, "total_effect_comparison.csv"))
cat("\nSaved to:",
    file.path(FIGURES_TABLES, TABLE_SUBDIR, "total_effect_comparison.csv"), "\n")
```

## Table S15: Pre-Period Adjustment Variants, Matched Models

Both headline normalizations -- the pooled topic fixed effects and the source-level
z-score -- are fitted using data from both sides of the cutoff. If the invasion
changed what a topic label means, or changed a source's sentiment distribution, an
adjustment estimated across the cutoff absorbs part of the treatment effect. Table
S15 re-estimates each matched preferred model with each adjustment frozen at its
pre-invasion values, separately and together.

Reported as two panels, one per matched model, because the two carry different
interaction terms: S15a is Table 2 Model 6 (state ownership) and S15b is Table 4
Model 5 (Russia-aligned). Within each panel the matched sample, bandwidth
machinery and source clustering are identical across all four columns; only the
outcome and the fixed-effect structure change. The models are built in
`09_preperiod_diagnostics.Rmd`, which reproduces both headline estimates at
`|diff| = 0` before estimating any variant.

```{r table-s15}
# Rows shared by both panels: which adjustment each column uses
s15_rows <- function(models) {
  tibble::tribble(
    ~term,                    ~c1, ~c2, ~c3, ~c4,
    "Topic FEs",              "X", "-", "X", "-",
    "Pre-Period Topic Adj.",  "-", "X", "-", "X",
    "Pre-Period Z-Score",     "-", "-", "X", "X",
    "N (matched)",            format(nobs(models[[1]]), big.mark = ","),
                              format(nobs(models[[2]]), big.mark = ","),
                              format(nobs(models[[3]]), big.mark = ","),
                              format(nobs(models[[4]]), big.mark = ","),
    "Clusters",               get_n_clusters(models[[1]]), get_n_clusters(models[[2]]),
                              get_n_clusters(models[[3]]), get_n_clusters(models[[4]])
  )
}

s15_note <- function(model_desc, interaction_desc) {
  str_wrap(paste(
    "Model 1 is the published specification. Model 2 removes the topic fixed",
    "effects and demeans the outcome by its pre-invasion topic means. Model 3",
    "re-standardizes the outcome on pre-invasion source means and standard",
    "deviations, keeping topic fixed effects. Model 4 applies both.",
    model_desc,
    interaction_desc,
    "All four use the identical exact-matched sample, bandwidth and source",
    "clustering.",
    SE_NOTE_BOOT,
    "Bootstrap p-values use the fixed RNG seed from 00_setup.R and may differ in",
    "the third decimal from Tables 2 and 4 until those are re-rendered."
  ), 80)
}

s15_col_names <- c("(1) Main†", "(2) Topic†", "(3) Z-Score†", "(4) Both†")

build_s15 <- function(models, boots, param, coef_label, title, model_desc,
                      interaction_desc) {
  mods <- setNames(models[c("spec1", "spec2", "spec3", "spec4")], s15_col_names)
  boot_list <- boots[c("spec1", "spec2", "spec3", "spec4")]

  vcov_list <- setNames(
    lapply(seq_along(mods), function(i)
      create_bootstrap_vcov(mods[[i]], boot_list[[i]], param)),
    s15_col_names)

  tbl <- modelsummary(
    mods,
    output = "gt",
    fmt = fmt_significant(2),
    stars = TRUE,
    vcov = vcov_list,
    coef_map = setNames(c("Invasion", coef_label), c("treatment", param)),
    gof_omit = "BIC|AIC|RMSE|Std.Errors|FE|R2 Within|R2 Within Adj.|Num.Obs.",
    title = title,
    add_rows = s15_rows(mods),
    notes = s15_note(model_desc, interaction_desc)
  )

  override_interaction_stars(tbl, boot_list, s15_col_names)
}

table_s15a <- build_s15(
  results_prepd$h2_matched_models,
  results_prepd$bootstrap_se$h2_matched,
  "treatment:state_owned",
  "State-Owned x Treat",
  "Pre-Period Adjustment Variants — State Ownership, Matched (Probabilistic Time)",
  "Sample is the exact-matched non-NATO, non-military sample of Table 2 Model 6.",
  "The interaction is state-owned x invasion."
)

table_s15b <- build_s15(
  results_prepd$h3a_matched_models,
  results_prepd$bootstrap_se$h3a_matched,
  "treatment:csto",
  "Russia-Aligned x Treat",
  "Pre-Period Adjustment Variants — Russia-Aligned, Matched (Probabilistic Time)",
  paste("Sample is the exact-matched state-owned, non-NATO, non-military sample of",
        "Table 4 Model 5."),
  "The interaction is Russia-aligned x invasion."
)

table_s15a
table_s15b

save_table(table_s15a, "table_s15a_preperiod_matched_h2", TABLE_SUBDIR)
save_table(table_s15b, "table_s15b_preperiod_matched_h3a", TABLE_SUBDIR)
```

### Table S15: Printed Side-by-Side

The full comparison behind the two panels, including the analytic and bootstrap
p-values side by side. Computed in `09_preperiod_diagnostics.Rmd`; reprinted and
re-saved here so the numbers sit alongside the tables they support.

```{r table-s15-comparison}
s15_side_by_side <- results_prepd$section4_estimates %>%
  transmute(model = spec, variant, outcome,
            fixed_effects, estimate, std_error,
            analytic_p = p_value, boot_se, boot_p,
            n_obs, n_clusters)

print(as.data.frame(s15_side_by_side), row.names = FALSE, digits = 4)

write_csv(s15_side_by_side,
          file.path(FIGURES_TABLES, TABLE_SUBDIR, "table_s15_preperiod_matched.csv"))
cat("\nSaved to:",
    file.path(FIGURES_TABLES, TABLE_SUBDIR, "table_s15_preperiod_matched.csv"), "\n")
```

# Country-Level Clustering Check

Assembles the source-level versus country-level WCR comparison for the four
reported RDIDs into one side-by-side summary. The estimates are identical across
the two clustering levels by construction; only the p-values, confidence
intervals and cluster counts differ. This is an appendix/robustness artefact
rather than a numbered table, so it is written as CSV and text alongside the
tables it supports.

```{r country-cluster-check}
country_cluster_summary <- bind_rows(
  results_h2$country_cluster_check,
  results_align$country_cluster_check
)

if (is.null(country_cluster_summary) || nrow(country_cluster_summary) == 0) {
  warning("country_cluster_check not found in the H2/H3a results; ",
          "re-run 05a and 06a to generate it.")
} else {
  side_by_side <- country_cluster_summary %>%
    select(model, estimate, n_obs,
           source_domain_clusters, source_domain_p,
           source_domain_ci_lower, source_domain_ci_upper,
           country_clusters, country_p, country_ci_lower, country_ci_upper)

  print(as.data.frame(side_by_side), row.names = FALSE, digits = 4)

  out_dir <- file.path(FIGURES_TABLES, TABLE_SUBDIR)
  write_csv(country_cluster_summary,
            file.path(out_dir, "country_clustering_comparison.csv"))

  con <- file(file.path(out_dir, "country_clustering_comparison.txt"), open = "wt")
  writeLines(c(
    "Country-level clustering check, H2 and H3a RDID estimates",
    "=========================================================",
    "",
    "Wild cluster restricted (WCR) bootstrap: Webb six-point weights, null imposed,",
    "bootstrap_type = fnw11, B = 4999.",
    "",
    "Clustering affects inference only, so the point estimate is shared across the",
    "two clustering levels. Sources are nested within countries; country clustering",
    "is the more conservative level when shocks are country-wide.",
    "",
    "Side-by-side",
    "------------"
  ), con)
  writeLines(capture.output(print(as.data.frame(side_by_side),
                                  row.names = FALSE, digits = 4)), con)
  close(con)

  cat("\nSaved to:", file.path(out_dir, "country_clustering_comparison.{csv,txt}"), "\n")
}
```

# GT Caption Fix

```{r}
fix_gt_caption <- function(filepath) {
  tex <- readLines(filepath)
  text <- paste(tex, collapse = "\n")
  
  # Match the full gt caption block and extract the title
  text <- gsub(
    "\\\\caption\\*\\{\\s*\n\\{\\\\fontsize\\{[^}]+\\}\\{[^}]+\\}\\\\selectfont\\s+(.+?)\\\\fontsize\\{[^}]+\\}\\{[^}]+\\}\\\\selectfont\\s*\\}\\s*\n\\}",
    "\\\\caption{\\1}",
    text
  )
  
  writeLines(text, filepath)
}

gt_tables <- c("table_s06_h2_loo", "table_s10_h3a_loo",
               "table_s11_decomposition", "table_s12_placebo",
               "table_s13_placebo_aligned")
for (t in gt_tables) {
  fix_gt_caption(here::here(paste0("figures/tables/",TABLE_SUBDIR), paste0(t, ".tex")))
}
```


# Summary

```{r summary}
cat("=============================================================\n")
cat("08a Publication Outputs Complete (Probabilistic Time)\n")
cat("=============================================================\n")
cat("Tables saved to:", file.path(FIGURES_TABLES, TABLE_SUBDIR), "\n\n")
cat("Main Paper Tables:\n")
cat("  Table 1   table_01_main              H1 RDD hybrid FE + Z-score\n")
cat("  Table 2   table_02_main              H2 interaction Z-score\n")
cat("  Table 3   table_03_main              H2 by-topic Z-score\n")
cat("  Table 4   table_04_main              H3a interaction Z-score\n")
cat("  Table 5   table_05_main              H3b null result Z-score\n")
cat("  Table 7   table_07_classification    Country classification\n")
cat("\nSupplementary Tables:\n")
cat("  S1  table_s01_fe_robustness          H1 FE robustness\n")
cat("  S2  table_s02_h1_z_topic             H1 by-topic Z-score\n")
cat("  S3  table_s03_h2_fe_core             H2 FE interaction core\n")
cat("  S4  table_s04_h2_fe_robustness       H2 FE robustness\n")
cat("  S5  table_s05_h2_fe_topic            H2 by-topic Full Data\n")
cat("  S6  table_s06_h2_loo                 H2 LOO robustness\n")
cat("  S7  table_s07_h3a_fe_core            H3a FE interaction + robustness\n")
cat("  S8  table_s08_h3a_z_topic            H3a by-topic Z-score\n")
cat("  S9  table_s09_h3a_fe_topic           H3a by-topic Full Data\n")
cat("  S10 table_s10_h3a_loo               H3a LOO robustness\n")
cat("  S11 table_s11_h3a_hetero               H3a Hetero robustness\n")
cat("  S12 table_s12_placebo                Placebo test summary\n")
cat("  S13 table_s13_placebo_aligned        Placebo test, aligned state media by country (Dec 7)\n")
cat("=============================================================\n")
```

# Session Info

```{r session-info}
print_session_info()
```
