---
title: "10d - Publication Outputs (Drop No-Time Articles)"
author: "Donald Moratz"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

# Overview

This file generates publication-quality tables for the **drop no-time articles** data variant. All tables are saved to `FIGURES_TABLES/drop/`.

```{r setup}
source("00_setup.R")

TABLE_SUBDIR <- "drop"
```

# Data Loading

```{r load-data}
results_h1    <- readRDS(file.path(DATA_INTERMEDIATE, "04_h1_results_drop.rds"))
results_h2    <- readRDS(file.path(DATA_INTERMEDIATE, "05_h2_results_drop.rds"))
results_align <- readRDS(file.path(DATA_INTERMEDIATE, "06_alignment_results_drop.rds"))
results_ethnic <- readRDS(file.path(DATA_INTERMEDIATE, "07_ethnic_results_drop.rds"))
data <- readRDS(file.path(DATA_INTERMEDIATE, "02_cleaned_data.rds"))
```

# Model Verification

Confirms the five result files carry every object Tables 1-5 read. Since the
04-07 variants were slimmed to exactly this list, a WARNING here means the
producing script needs re-rendering, not that a model is missing by design.

```{r model-check}
check_model <- function(obj, name, obj_name) {
  exists <- !is.null(obj[[name]])
  status <- if (exists) "OK" else "WARNING: NOT FOUND"
  cat(sprintf("  %-45s %s\n", paste0(obj_name, "$", name), status))
  invisible(exists)
}

check_boot <- function(obj, name, obj_name) {
  exists <- !is.null(obj$bootstrap_se[[name]])
  status <- if (exists) "OK" else "WARNING: NOT FOUND"
  cat(sprintf("  %-45s %s\n", paste0(obj_name, "$bootstrap_se$", name), status))
  invisible(exists)
}

cat("=== H1 Models (Table 1) ===\n")
for (m in c("model1_opt", "model2_opt", "model3_opt", "model4_opt",
            "model5_opt", "model6a_nonmil", "model7a_nonnato")) {
  check_model(results_h1, m, "results_h1")
}

cat("\n=== H2 Models (Tables 2 and 3) ===\n")
for (m in c("model2_state_rdd_z", "model2_ind_rdd_z",
            "model2a_opt_z", "model2b_z", "model2d_z", "matched_model_z",
            "model2a_opt_pol", "model2a_opt_mil", "model2a_opt_econ",
            "model2a_opt_cult", "model2a_opt_oth")) {
  check_model(results_h2, m, "results_h2")
}

cat("\n=== H2 Bootstrap Keys ===\n")
for (m in c("model2a_opt_z", "model2b_z", "model2d_z", "matched_model_z",
            "model2a_opt_pol", "model2a_opt_mil", "model2a_opt_econ",
            "model2a_opt_cult", "model2a_opt_oth")) {
  check_boot(results_h2, m, "results_h2")
}

cat("\n=== H3a (Alignment) Models (Table 4) ===\n")
for (m in c("model5a_csto_z", "model5a_neutral_z",
            "model5a_opt_z", "model5a_opt_non_mil_z", "matched_model")) {
  check_model(results_align, m, "results_align")
}

cat("\n=== H3a Bootstrap Keys ===\n")
for (m in c("model5a_opt_z", "model5a_opt_non_mil_z", "matched_model")) {
  check_boot(results_align, m, "results_align")
}

cat("\n=== H3b (Ethnic) Models (Table 5) ===\n")
for (m in c("model6a_high_z", "model6a_low_z",
            "model6a_opt_z", "model6a_opt_non_mil_z", "matched_model_z")) {
  check_model(results_ethnic, m, "results_ethnic")
}

cat("\n=== H3b Bootstrap Keys ===\n")
for (m in c("model6a_opt_z", "model6a_opt_non_mil_z", "matched_model_z")) {
  check_boot(results_ethnic, m, "results_ethnic")
}
```

# Main Paper Tables

## Table 1: H1 RDD — Hybrid FE + Z-Score (Pattern A)

```{r table-01}
h1_models <- list(
  "(1)" = results_h1$model1_opt,
  "(2)" = results_h1$model2_opt,
  "(3)" = results_h1$model3_opt,
  "(4)" = results_h1$model4_opt,
  "(5)" = results_h1$model5_opt,
  "(6)" = results_h1$model6a_nonmil,
  "(7)" = results_h1$model7a_nonnato
)

n_cl_t1 <- sapply(h1_models, get_n_clusters)

rows_t1 <- tibble::tribble(
  ~term,            ~`(1)`, ~`(2)`, ~`(3)`, ~`(4)`, ~`(5)`, ~`(6)`, ~`(7)`,
  "Topic FEs",      "-",    "-",    "-",    "X",    "X",    "X",    "X",
  "State FEs",      "-",    "X",    "X",    "X",    "-",    "-",    "-",
  "Source FEs",     "-",    "-",    "X",    "X",    "-",    "-",    "-",
  "Source Z-Score", "-",    "-",    "-",    "-",    "X",    "X",    "X",
  "Clusters",       n_cl_t1[1], n_cl_t1[2], n_cl_t1[3], n_cl_t1[4], n_cl_t1[5], n_cl_t1[6], n_cl_t1[7]
)
attr(rows_t1, "position") <- c(3, 4, 5, 6, 7)

note_t1 <- str_wrap(paste(
  SE_NOTE_CLUSTER,
  "Models 1-4 use the optimal bandwidth.",
  "Models 5-7 use a Z-Score adjustment instead of fixed effects.",
  "Model 6 omits Military Topics. Model 7 omits NATO allies."
), 80)

table_1 <- modelsummary(
  h1_models,
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  coef_map = c("treatment" = "Invasion"),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE|R2 Within|R2 Within Adj.",
  title = "Table 1: H1 RDD — Effect of Russian Invasion on Media Sentiment (Drop No-Time Articles)",
  add_rows = rows_t1,
  notes = note_t1
)

table_1
save_table(table_1, "table_01_main", TABLE_SUBDIR)
```

## Table 2: H2 Interaction Z-Score — State Ownership (Pattern B)

```{r table-02}
# Define model list and bootstrap keys
h2_z_models <- list(
  "(1) State-Owned\u2021" = results_h2$model2_state_rdd_z,
  "(2) Ind.\u2021" = results_h2$model2_ind_rdd_z,
  "(3)\u2020" = results_h2$model2a_opt_z,
  "(4)\u2020" = results_h2$model2b_z,
  "(5)\u2020" = results_h2$model2d_z,
  "(6)\u2020" = results_h2$matched_model_z
)

boot_keys_t2 <- c("model2a_opt_z", "model2b_z", "model2d_z",
                  "matched_model_z")
boot_results_t2 <- lapply(boot_keys_t2, function(k) results_h2$bootstrap_se[[k]])

# Build vcov list: NULL for rdrobust, create_bootstrap_vcov for felm
vcov_t2 <- list(
  "(1) State-Owned\u2021" = NULL,
  "(2) Ind.\u2021" = NULL,
  "(3)\u2020" = create_bootstrap_vcov(results_h2$model2a_opt_z, boot_results_t2[[1]], "treatment:state_owned"),
  "(4)\u2020" = create_bootstrap_vcov(results_h2$model2b_z, boot_results_t2[[2]], "treatment:state_owned"),
  "(5)\u2020" = create_bootstrap_vcov(results_h2$model2d_z, boot_results_t2[[3]], "treatment:state_owned"),
  "(6)\u2020" = create_bootstrap_vcov(results_h2$matched_model_z, boot_results_t2[[4]], "treatment:state_owned")
)

n_cl_t2 <- map_chr(h2_z_models, get_n_clusters)

rows_t2 <- tibble::tribble(
  ~term,~row1, ~row2, ~row3, ~row4, ~row5, ~row6,
  "Source Z-Score", "X",    "X",    "X",    "X",    "X",    "X",
  "Clusters",       n_cl_t2[1], n_cl_t2[2], n_cl_t2[3], n_cl_t2[4], n_cl_t2[5], n_cl_t2[6]
)
attr(rows_t2, "position") <- c(5, 6)

note_t2 <- str_wrap(paste(
  "All models use a source-level Z-Score normalization.",
  "Models 1-2 show separate RDD estimates for state-owned and independent media, filtered to omit military topics.",
  "Models 3-6 estimate the state-owned x treatment interaction.",
  "Model 3 uses the optimal bandwidth on the full sample.",
  "Model 4 omits military topics.",
  "Model 5 omits military topics and NATO allies.",
  "Model 6 applies exact matching on topic and publication date to Model 5's sample.",
  SE_NOTE
), 80)

table_2 <- modelsummary(
  h2_z_models,
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  vcov = vcov_t2,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:state_owned" = "State-Owned x Treat"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE|R2 Within|R2 Within Adj.|bandwidth.left|bandwidth.right|nobs.left|nobs.right",
  title = "Table 2: H2 Diff-in-Disc — State Ownership Interaction, Z-Score (Drop No-Time Articles)",
  add_rows = rows_t2,
  notes = note_t2
)

boot_col_names_t2 <- c("(3)\u2020", "(4)\u2020", "(5)\u2020", "(6)\u2020")
table_2 <- override_interaction_stars(table_2, boot_results_t2, boot_col_names_t2)

table_2
save_table(table_2, "table_02_main", TABLE_SUBDIR)
```

## Table 3: H2 By-Topic Z-Score — State Ownership (Pattern C-z)

```{r table-03}
h2_topic_z_models <- list(
  "Political" = results_h2$model2a_opt_pol,
  "Military"  = results_h2$model2a_opt_mil,
  "Economic"  = results_h2$model2a_opt_econ,
  "Cultural"  = results_h2$model2a_opt_cult,
  "Other"     = results_h2$model2a_opt_oth
)

if (any(sapply(h2_topic_z_models, is.null))) {
  cat("WARNING: Some H2 by-topic Z-score models not found. Skipping Table 3.\n")
} else {
  boot_keys_t3 <- c("model2a_opt_pol", "model2a_opt_mil", "model2a_opt_econ",
                     "model2a_opt_cult", "model2a_opt_oth")
  boot_results_t3 <- lapply(boot_keys_t3, function(k) results_h2$bootstrap_se[[k]])

  vcov_t3 <- list(
    "Political" = create_bootstrap_vcov(h2_topic_z_models[["Political"]], boot_results_t3[[1]], "treatment:state_owned"),
    "Military"  = create_bootstrap_vcov(h2_topic_z_models[["Military"]],  boot_results_t3[[2]], "treatment:state_owned"),
    "Economic"  = create_bootstrap_vcov(h2_topic_z_models[["Economic"]],  boot_results_t3[[3]], "treatment:state_owned"),
    "Cultural"  = create_bootstrap_vcov(h2_topic_z_models[["Cultural"]],  boot_results_t3[[4]], "treatment:state_owned"),
    "Other"     = create_bootstrap_vcov(h2_topic_z_models[["Other"]],     boot_results_t3[[5]], "treatment:state_owned")
  )

  n_cl_t3 <- sapply(h2_topic_z_models, get_n_clusters)

  rows_t3 <- tibble::tribble(
    ~term,            ~Political, ~Military, ~Economic, ~Cultural, ~Other,
    "Source Z-Score", "X",        "X",       "X",       "X",       "X",
    "Clusters",       n_cl_t3[1], n_cl_t3[2], n_cl_t3[3], n_cl_t3[4], n_cl_t3[5]
  )
  attr(rows_t3, "position") <- c(5, 6)

  note_t3 <- str_wrap(paste(
    "All models use a source-level Z-Score normalization with the optimal bandwidth.",
    "Each column restricts to the indicated topic category.", SE_NOTE
  ), 80)

  table_3 <- modelsummary(
    h2_topic_z_models,
    output = "gt",
    fmt = fmt_significant(2),
    stars = TRUE,
    vcov = vcov_t3,
    coef_map = c(
      "treatment" = "Invasion",
      "treatment:state_owned" = "State Owned x Treatment"
    ),
    gof_omit = "BIC|AIC|RMSE|Std.Errors|FE|R2 Within|R2 Within Adj.|bandwidth.left|bandwidth.right|nobs.left|nobs.right",
    title = "Table 3: H2 Diff-in-Disc by Topic — Z-Score (Drop No-Time Articles)",
    add_rows = rows_t3,
    notes = note_t3
  )

  topic_col_names <- c("Political", "Military", "Economic", "Cultural", "Other")
  table_3 <- override_interaction_stars(table_3, boot_results_t3, topic_col_names)

  table_3
  save_table(table_3, "table_03_main", TABLE_SUBDIR)
}
```

## Table 4: H3a Interaction Z-Score — CSTO Alignment (Pattern B)

```{r table-04}
h3a_z_models <- list(
  "(1) CSTO\u2021" = results_align$model5a_csto_z,
  "(2) Neutral\u2021" = results_align$model5a_neutral_z,
  "(3)\u2020" = results_align$model5a_opt_z,
  "(4)\u2020" = results_align$model5a_opt_non_mil_z,
  "(5)\u2020" = results_align$matched_model
)

boot_keys_t4 <- c("model5a_opt_z", "model5a_opt_non_mil_z",
                  "matched_model")
boot_results_t4 <- lapply(boot_keys_t4, function(k) results_align$bootstrap_se[[k]])

vcov_t4 <- list(
  "(1) CSTO\u2021" = NULL,
  "(2) Neutral\u2021" = NULL,
  "(3)\u2020" = create_bootstrap_vcov(results_align$model5a_opt_z, boot_results_t4[[1]], "treatment:csto"),
  "(4)\u2020" = create_bootstrap_vcov(results_align$model5a_opt_non_mil_z, boot_results_t4[[2]], "treatment:csto"),
  "(5)\u2020" = create_bootstrap_vcov(results_align$matched_model, boot_results_t4[[3]], "treatment:csto")
)

n_cl_t4 <- sapply(h3a_z_models, get_n_clusters)

rows_t4 <- tibble::tribble(
  ~term,~row1, ~row2, ~row3, ~row4, ~row5,
  "Source Z-Score", "X",    "X",    "X",    "X",    "X",
  "Clusters",       n_cl_t4[1], n_cl_t4[2], n_cl_t4[3], n_cl_t4[4], n_cl_t4[5]
)
attr(rows_t4, "position") <- c(5, 6)

note_t4 <- str_wrap(paste(
  "All models use a source-level Z-Score normalization.",
  "Sample restricted to state-owned media in non-NATO countries.",
  "Models 1-2 show separate RDD estimates for CSTO-aligned and neutral countries, filtered to omit military topics.",
  "Models 3-5 estimate the CSTO x treatment interaction.",
  "Model 3 uses the optimal bandwidth.",
  "Model 4 omits military topics.",
  "Model 5 uses exact matching on topic and date of publication for the non-military data.",
  SE_NOTE
), 80)

table_4 <- modelsummary(
  h3a_z_models,
  output = "gt",
  fmt = fmt_significant(2),
  stars = TRUE,
  vcov = vcov_t4,
  coef_map = c(
    "treatment" = "Invasion",
    "treatment:csto" = "CSTO x Treatment"
  ),
  gof_omit = "BIC|AIC|RMSE|Std.Errors|FE|R2 Within|R2 Within Adj.|bandwidth.left|bandwidth.right|nobs.left|nobs.right",
  title = "Table 4: H3a Alignment Interaction — Z-Score (Drop No-Time Articles)",
  add_rows = rows_t4,
  notes = note_t4
)

boot_col_names_t4 <- c("(3)\u2020", "(4)\u2020", "(5)\u2020")
table_4 <- override_interaction_stars(table_4, boot_results_t4, boot_col_names_t4)

table_4
save_table(table_4, "table_04_main", TABLE_SUBDIR)
```

## Table 5: H3b Null Result Z-Score — Ethnic Russian Population (Pattern B)

```{r table-05b}
# NOTE: These H3b models likely do not exist yet
h3b_z_models_exist <- !is.null(results_ethnic$model6a_high_z) &&
                      !is.null(results_ethnic$model6a_low_z) &&
                      !is.null(results_ethnic$model6a_opt_z)

if (!h3b_z_models_exist) {
  cat("WARNING: H3b Z-score models not found. Skipping Table 5.\n")
} else {
  h3b_z_models <- list(
    "(1)\u2021" = results_ethnic$model6a_high_z,
    "(2)\u2021" = results_ethnic$model6a_low_z,
    "(3)\u2020" = results_ethnic$model6a_opt_z,
    "(4)\u2020" = results_ethnic$model6a_opt_non_mil_z,
    "(5)\u2020" = results_ethnic$matched_model_z
  )

  boot_keys_t6 <- c("model6a_opt_z", "model6a_opt_non_mil_z", "matched_model_z")
  boot_results_t6 <- lapply(boot_keys_t6, function(k) results_ethnic$bootstrap_se[[k]])

  vcov_t6 <- list(
    "(1)\u2021" = NULL,
    "(2)\u2021" = NULL,
    "(3)\u2020" = create_bootstrap_vcov(results_ethnic$model6a_opt_z, boot_results_t6[[1]], "treatment:high_russia"),
    "(4)\u2020" = create_bootstrap_vcov(results_ethnic$model6a_opt_non_mil_z, boot_results_t6[[2]], "treatment:high_russia"),
    "(5)\u2020" = create_bootstrap_vcov(results_ethnic$matched_model_z, boot_results_t6[[3]], "treatment:high_russia")
  )

  n_cl_t6 <- sapply(h3b_z_models, get_n_clusters)

  rows_t6 <- tibble::tribble(
    ~term,~row1, ~row2, ~row3, ~row4, ~row5,
    "Source Z-Score", "X",    "X",    "X",    "X",    "X",
    "Clusters",       n_cl_t6[1], n_cl_t6[2], n_cl_t6[3], n_cl_t6[4], n_cl_t6[5]
  )
  attr(rows_t6, "position") <- c(5, 6)

  note_t6 <- str_wrap(paste(
    "All models use a source-level Z-Score normalization.",
    "Models 1-2 show separate RDD estimates for high and low ethnic Russian population countries.",
    "Models 3-5 estimate the high Russian population x treatment interaction.",
    "Model 3 uses the optimal bandwidth. Model 4 omits military topics.",
    "Model 5 uses matched data.", SE_NOTE
  ), 80)

  table_6 <- modelsummary(
    h3b_z_models,
    output = "gt",
    fmt = fmt_significant(2),
    stars = TRUE,
    vcov = vcov_t6,
    coef_map = c(
      "treatment" = "Invasion",
      "treatment:high_russia" = "High Russian Pop x Treatment"
    ),
    gof_omit = "BIC|AIC|RMSE|Std.Errors|FE|R2 Within|R2 Within Adj.",
    title = "Table 5: H3b Ethnic Russian Population — Null Result, Z-Score (Drop No-Time Articles)",
    add_rows = rows_t6,
    notes = note_t6
  )

  boot_col_names_t6 <- c("(3)\u2020", "(4)\u2020", "(5)\u2020")
  table_6 <- override_interaction_stars(table_6, boot_results_t6, boot_col_names_t6)

  table_6
  save_table(table_6, "table_05_main", TABLE_SUBDIR)
}
```

## Table 7: Country Classification (Pattern E)

```{r table-07}
get_group <- function(russian_group, security_group) {
  paste(intersect(russian_group, security_group), collapse = ", ")
}

table_data_7 <- data.frame(
  `Ethnic Russian Population` = c("Low Ethnic", "High Ethnic"),
  `Low Russia Aligned` = c(
    get_group(LOW_RUSSIAN_POP, NEUTRAL_COUNTRIES),
    get_group(HIGH_RUSSIAN_POP, NEUTRAL_COUNTRIES)
  ),
  `High Russia Aligned` = c(
    get_group(LOW_RUSSIAN_POP, CSTO_COUNTRIES),
    get_group(HIGH_RUSSIAN_POP, CSTO_COUNTRIES)
  )
)

table_7 <- table_data_7 %>%
  gt() %>%
  tab_header(
    title = "Table 7: Ethnic Russian Population x Russia Security Alignment",
    subtitle = "Country Classification"
  ) %>%
  cols_label(
    Ethnic.Russian.Population = "",
    Low.Russia.Aligned = "Low Alignment (Neutral)",
    High.Russia.Aligned = "High Alignment (CSTO)"
  ) %>%
  tab_style(
    style = cell_borders(sides = "all", color = "black", weight = px(1)),
    locations = cells_body()
  )

table_7
save_table(table_7, "table_07_classification", TABLE_SUBDIR)
```

# Summary

```{r summary}
cat("=============================================================\n")
cat("10d Publication Outputs Complete (Drop No-Time Articles)\n")
cat("=============================================================\n")
cat("Tables saved to:", file.path(FIGURES_TABLES, TABLE_SUBDIR), "\n\n")
cat("Main Paper Tables:\n")
cat("  Table 1   table_01_main              H1 RDD hybrid FE + Z-score\n")
cat("  Table 2   table_02_main              H2 interaction Z-score\n")
cat("  Table 3   table_03_main              H2 by-topic Z-score\n")
cat("  Table 4   table_04_main              H3a interaction Z-score\n")
cat("  Table 5   table_05_main              H3b null result Z-score\n")
cat("  Table 7   table_07_classification    Country classification\n")
cat("\nAppendix tables for this variant are built by 11_typology_robustness.Rmd,\n")
cat("which compares all three time-assignment typologies in one place.\n")
cat("=============================================================\n")
```


# Session Info

```{r session-info}
print_session_info()
```
