---
title: "11 - Typology Robustness (Time-Assignment Variants)"
author: "Donald Moratz"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

# Overview

Every hypothesis is estimated three times, once under each time-assignment
typology: **probabilistic** (KDE-imputed publication times, the primary
analysis), **day** (the calendar day as the running variable), and **drop**
(articles without a recorded time discarded). The question this script answers is
narrow and specific: *does the headline result depend on which typology was
chosen?*

That question does not need the full appendix reproduced three times. It needs
one number per hypothesis per typology, side by side. This script reads the
serialized results of `04`-`07` for all three variants and reports exactly that.

**Scope.** For each hypothesis, two specifications are shown:

| Hypothesis | Main specification | Matched specification |
|---|---|---|
| H1 | Table 1, Model 5 (`model5_opt`) | — none in Table 1 |
| H2 | Table 2, Model 5 (`model2d_z`) | Table 2, Model 6 (`matched_model_z`) |
| H3a | Table 4, Model 4 (`model5a_opt_non_mil_z`) | Table 4, Model 5 (`matched_model`) |
| H3b | Table 5, Model 4 (`model6a_opt_non_mil_z`) | Table 5, Model 5 (`matched_model_z`) |

The matched specification is the preferred column in each case; the unmatched one
is shown alongside so a reader can see both move together.

**What is deliberately not here.** No appendix robustness objects, no by-topic
breakdowns, no leave-one-out, no placebos. Those are reported once, for the
primary probabilistic variant, in `10a_publication_outputs_prob.Rmd`. Repeating
them per typology is what this script replaces.

**Inputs** — twelve serialized result objects:

- `04_h1_results{_prob,,_drop}.rds`
- `05_h2_results{_prob,,_drop}.rds`
- `06_alignment_results{_prob,,_drop}.rds`
- `07_ethnic_results{_prob,,_drop}.rds`

**Outputs** — written to `figures/tables/prob/`, alongside the other appendix
tables, since this is an appendix object for the primary paper even though its
content spans all three variants:

- `table_s16a_typology_h1.{tex,html}`
- `table_s16b_typology_h2.{tex,html}`
- `table_s16c_typology_h3a.{tex,html}`
- `table_s16d_typology_h3b.{tex,html}`
- `typology_robustness_comparison.csv` — every cell in tidy form

```{r setup}
source("00_setup.R")

TABLE_SUBDIR <- "prob"
options(digits = 10)
```

# Specification Map

The one place that defines what is compared. Each entry names the serialized
object, the coefficient of interest, and the key under which its wild cluster
bootstrap result was stored. H1 has no matched sibling and no bootstrap: Table 1
Model 5 is an `rdrobust` fit reported with cluster-robust standard errors.

```{r spec-map}
# Suffixes on the intermediate files, in the order the tables display them
VARIANTS <- c(Probabilistic = "_prob", Day = "", Drop = "_drop")

TYPOLOGY_SPECS <- list(
  H1 = list(
    label   = "H1 — Effect of the invasion on sentiment",
    file    = "04_h1_results",
    term    = "treatment",
    coef    = "Invasion",
    specs   = list("Main (Table 1, Model 5)" = "model5_opt")
  ),
  H2 = list(
    label   = "H2 — State-owned vs independent media",
    file    = "05_h2_results",
    term    = "treatment:state_owned",
    coef    = "State-Owned x Treat",
    specs   = list("Main (Table 2, Model 5)"    = "model2d_z",
                   "Matched (Table 2, Model 6)" = "matched_model_z")
  ),
  H3a = list(
    label   = "H3a — Russia-aligned vs neutral state media",
    file    = "06_alignment_results",
    term    = "treatment:csto",
    coef    = "Russia-Aligned x Treat",
    specs   = list("Main (Table 4, Model 4)"    = "model5a_opt_non_mil_z",
                   "Matched (Table 4, Model 5)" = "matched_model")
  ),
  H3b = list(
    label   = "H3b — Ethnic Russian population",
    file    = "07_ethnic_results",
    term    = "treatment:high_russia",
    coef    = "High Russian Pop x Treat",
    specs   = list("Main (Table 5, Model 4)"    = "model6a_opt_non_mil_z",
                   "Matched (Table 5, Model 5)" = "matched_model_z")
  )
)
```

# Extraction

`rdrobust` and `feols` expose their estimates differently, and only the `feols`
models carry a wild cluster bootstrap, so one extractor handles both and returns
a common shape. A missing object yields a row of `NA` rather than an error: the
`drop` variant's `04` and `07` results were serialized before those scripts last
changed, so some cells are empty until those two are re-rendered. Which cells are
missing is reported explicitly below rather than passed over silently.

```{r extract}
# One tidy row: hypothesis x specification x variant
extract_cell <- function(res, obj_name, term, hyp, spec_label, variant) {
  blank <- tibble(hypothesis = hyp, spec = spec_label, variant = variant,
                  object = obj_name, estimate = NA_real_, std_error = NA_real_,
                  p_value = NA_real_, boot_se = NA_real_, boot_p = NA_real_,
                  n_obs = NA_real_, n_clusters = NA_character_, available = FALSE)

  m <- res[[obj_name]]
  if (is.null(m)) return(blank)

  boot <- if (!is.null(res$bootstrap_se)) res$bootstrap_se[[obj_name]] else NULL

  if (inherits(m, "rdrobust")) {
    # Table 1 Model 5: cluster-robust rdrobust, no bootstrap
    blank$estimate   <- m$coef[1]
    blank$std_error  <- m$se[1]
    blank$p_value    <- m$pv[1]
    blank$n_obs      <- m$N_h[1] + m$N_h[2]
    blank$n_clusters <- NA_character_
  } else {
    ct <- coeftable(m)
    if (!term %in% rownames(ct)) return(blank)
    blank$estimate   <- ct[term, "Estimate"]
    blank$std_error  <- ct[term, "Std. Error"]
    blank$p_value    <- ct[term, "Pr(>|t|)"]
    blank$n_obs      <- nobs(m)
    blank$n_clusters <- get_n_clusters(m)
    if (!is.null(boot)) {
      blank$boot_se <- boot$se
      blank$boot_p  <- boot$p_val
    }
  }
  blank$available <- TRUE
  blank
}

typology_cells <- map_df(names(TYPOLOGY_SPECS), function(hyp) {
  s <- TYPOLOGY_SPECS[[hyp]]
  map_df(names(VARIANTS), function(v) {
    path <- file.path(DATA_INTERMEDIATE, paste0(s$file, VARIANTS[[v]], ".rds"))
    if (!file.exists(path)) {
      return(map_df(names(s$specs), function(sl)
        extract_cell(list(), s$specs[[sl]], s$term, hyp, sl, v)))
    }
    res <- readRDS(path)
    map_df(names(s$specs), function(sl)
      extract_cell(res, s$specs[[sl]], s$term, hyp, sl, v))
  })
})

cat("Cells extracted:", nrow(typology_cells),
    "| available:", sum(typology_cells$available),
    "| missing:", sum(!typology_cells$available), "\n\n")

missing_cells <- typology_cells %>% filter(!available)
if (nrow(missing_cells) > 0) {
  cat("MISSING — these serialized objects were not found. The `drop` results for\n")
  cat("04 and 07 predate the current scripts; re-render those to fill them in.\n")
  print(as.data.frame(missing_cells %>% select(hypothesis, spec, variant, object)),
        row.names = FALSE)
} else {
  cat("All cells present.\n")
}
```

# Tables

One table per hypothesis, typologies as columns. Each specification occupies a
labelled block of rows so the same quantity can be read straight across the three
typologies. Significance stars follow the wild cluster bootstrap p-value where
one exists, matching Tables 2, 4 and 5; H1 uses its `rdrobust` p-value.

```{r build-tables}
# Format one specification x variant cell into the column of statistics below
format_cell <- function(row) {
  if (!row$available) return(rep("—", 5))
  p_for_stars <- if (!is.na(row$boot_p)) row$boot_p else row$p_value
  stars <- get_boot_stars(p_for_stars)
  c(
    sprintf("%.3f%s", row$estimate, stars),
    sprintf("(%.3f)", if (!is.na(row$boot_se)) row$boot_se else row$std_error),
    if (is.na(row$boot_p)) "—" else sprintf("%.3f", row$boot_p),
    format(round(row$n_obs), big.mark = ","),
    if (is.na(row$n_clusters)) "—" else as.character(row$n_clusters)
  )
}

STAT_LABELS <- c("Estimate", "Std. Error", "Bootstrap p", "N", "Clusters")

build_typology_table <- function(hyp) {
  s <- TYPOLOGY_SPECS[[hyp]]
  cells <- typology_cells %>% filter(hypothesis == hyp)

  body <- map_df(names(s$specs), function(sl) {
    tab <- tibble(Specification = sl, Statistic = STAT_LABELS)
    for (v in names(VARIANTS)) {
      row <- cells %>% filter(spec == sl, variant == v)
      tab[[v]] <- format_cell(row)
    }
    tab
  })

  note <- str_wrap(paste(
    "Each column re-estimates the same specification under a different",
    "time-assignment typology: probabilistic imputation of missing publication",
    "times (the primary analysis), the calendar day as the running variable, or",
    "articles without a recorded time dropped. Sample sizes differ across columns",
    "by construction, since the typologies retain different articles and select",
    "their own MSE-optimal bandwidths.",
    "The coefficient reported is", paste0(s$coef, "."),
    if (hyp == "H1")
      "Table 1 Model 5 is an rdrobust fit reported with cluster-robust standard errors, so no bootstrap p-value applies."
    else
      SE_NOTE_BOOT,
    "Stars follow the bootstrap p-value where one exists."
  ), 80)

  tbl <- body %>%
    gt(groupname_col = "Specification") %>%
    cols_label(Statistic = "") %>%
    tab_header(title = paste0("Typology Robustness — ", s$label),
               subtitle = "Same specification under each time-assignment variant") %>%
    tab_footnote(footnote = note)

  tbl
}

table_s16a <- build_typology_table("H1")
table_s16b <- build_typology_table("H2")
table_s16c <- build_typology_table("H3a")
table_s16d <- build_typology_table("H3b")

table_s16a
table_s16b
table_s16c
table_s16d

save_table(table_s16a, "table_s16a_typology_h1",  TABLE_SUBDIR, label = "tab:s16a")
save_table(table_s16b, "table_s16b_typology_h2",  TABLE_SUBDIR, label = "tab:s16b")
save_table(table_s16c, "table_s16c_typology_h3a", TABLE_SUBDIR, label = "tab:s16c")
save_table(table_s16d, "table_s16d_typology_h3b", TABLE_SUBDIR, label = "tab:s16d")
```

# Printed Comparison and CSV

The same content in tidy form, so the numbers behind the four tables are
available without parsing them.

```{r comparison-csv}
typology_comparison <- typology_cells %>%
  select(hypothesis, spec, variant, object, estimate, std_error, p_value,
         boot_se, boot_p, n_obs, n_clusters, available)

print(as.data.frame(typology_comparison %>%
        select(hypothesis, spec, variant, estimate, std_error, boot_p, n_obs)),
      row.names = FALSE, digits = 4)

write_csv(typology_comparison,
          file.path(FIGURES_TABLES, TABLE_SUBDIR, "typology_robustness_comparison.csv"))
cat("\nSaved to:",
    file.path(FIGURES_TABLES, TABLE_SUBDIR, "typology_robustness_comparison.csv"), "\n")
```

# Spread Across Typologies

A compact read on the actual question: how much does each estimate move when the
typology changes? Reported as the range across the available variants, in units
of the primary (probabilistic) standard error, so it is comparable across
hypotheses.

```{r spread}
typology_spread <- typology_cells %>%
  filter(available) %>%
  group_by(hypothesis, spec) %>%
  summarize(
    n_variants   = n(),
    prob_estimate = estimate[variant == "Probabilistic"][1],
    prob_se       = coalesce(boot_se[variant == "Probabilistic"][1],
                             std_error[variant == "Probabilistic"][1]),
    min_estimate = min(estimate), max_estimate = max(estimate),
    .groups = "drop"
  ) %>%
  mutate(spread = max_estimate - min_estimate,
         spread_in_prob_ses = spread / prob_se)

print(as.data.frame(typology_spread), row.names = FALSE, digits = 4)
```

# Session Info

```{r session-info}
print_session_info()
```
