---
title: "Russia Sentiment Analysis - Master Pipeline"
author: "Donald Moratz"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
---

# Analysis Pipeline Overview

This master script runs the entire analysis pipeline for the Russia sentiment paper.

Changes to make:
06C has updated analysis that needs to push to rest of 061
05C needs to be updated to match 06C
05 Files need to be updated to match 05C
08 tables need updating for 06 and full rework for 05 changes

## Workflow Diagram

```
┌─────────────────────────────────────────────────────────────────────────────┐
│                         RUSSIA SENTIMENT ANALYSIS PIPELINE                   │
└─────────────────────────────────────────────────────────────────────────────┘

  ┌──────────────────┐
  │   00_setup.R     │ ◄── Shared functions, packages, constants
  └────────┬─────────┘
           │
           ▼
  ┌──────────────────┐     ┌─────────────────────────────┐
  │ 01_data_loading  │────►│ data/intermediate/          │
  │     .Rmd         │     │   01_raw_data.rds           │
  └────────┬─────────┘     └─────────────────────────────┘
           │
           ▼
  ┌──────────────────┐     ┌─────────────────────────────┐
  │ 02_data_cleaning │────►│ data/intermediate/          │
  │     .Rmd         │     │   02_cleaned_data.rds       │
  └────────┬─────────┘     │   02_data_non_ukraine.rds   │
           │               │   02_data_non_ukraine_ind.rds│
           │               └─────────────────────────────┘
           │
     ┌─────┴─────┬──────────────────────────┐
     │           │                          │
     ▼           ▼                          ▼
┌─────────┐ ┌─────────┐ ┌──────────┐ ┌─────────┐ ┌──────────┐
│   03    │ │   04    │ │   04A    │ │   05    │ │   05A    │
│ Descrip │ │Main RDD │ │ RDD Cont │ │Diff-Disc│ │Disc Cont │
│ tive    │ │   H1    │ │  H1 Alt  │ │   H2    │ │  H2 Alt  │
└────┬────┘ └────┬────┘ └────┬─────┘ └────┬────┘ └────┬─────┘
     │           │           │            │            │
     │           │     ┌─────┴─────┐ ┌────┴────┐ ┌────┴────┐
     │           │     │  04B 04C  │ │ 05B 05C │ │         │
     │           │     │Drop  Prob │ │Drop Prob│ │         │
     │           │     └─────┬─────┘ └────┬────┘ │         │
     │           │           │            │      │         │
     │           ▼           ▼            ▼      ▼         │
     │      ┌──────────────────────────────────────────┐   │
     │      │  06: Russian Alignment (CSTO vs Neutral) │   │
     │      │  06A: Alignment Continuous               │   │
     │      │  06B: Alignment Drop No-Time             │   │
     │      │  06C: Alignment Probabilistic            │   │
     │      └───────────────────┬──────────────────────┘   │
     │                          │                          │
     │      ┌───────────────────▼──────────────────────┐   │
     │      │  07: Ethnic Russian Population           │   │
     │      │  07A: Ethnic Continuous                  │   │
     │      │  07B: Ethnic Drop No-Time                │   │
     │      │  07C: Ethnic Probabilistic               │   │
     │      └───────────────────┬──────────────────────┘   │
     │                          │                          │
     └──────────────────────────┼──────────────────────────┘
                                │
                                ▼
                   ┌─────────────────────┐
                   │         08          │
                   │    Publication      │────► figures/
                   │      Outputs        │      (tables & plots)
                   └─────────────────────┘
```

## File Descriptions

| Script | Purpose | Outputs |
|--------|---------|---------|
| `00_setup.R` | Packages, functions, constants | - |
| `01_data_loading.Rmd` | Load raw CSV data | `01_raw_data.rds` |
| `02_data_cleaning.Rmd` | Clean and create variables | `02_cleaned_data.rds`, etc. |
| `03_descriptive_analysis.Rmd` | Summary statistics, EDA | Tables, time series plots |
| `04_main_rdd_analysis.Rmd` | Hypothesis 1: RDD (day) | `04_h1_results.rds`, figures |
| `04A_main_rdd_analysis_continuous.Rmd` | Hypothesis 1: RDD (continuous) | `04_h1_results_continuous.rds`, figures |
| `04B_main_rdd_analysis_drop.Rmd` | H1: RDD (drop no-time articles) | `04_h1_results_drop.rds` |
| `04C_main_rdd_analysis_prob.Rmd` | H1: RDD (probabilistic time) | `04_h1_results_prob.rds` |
| `05_diff_in_disc_analysis.Rmd` | Hypothesis 2: Diff-in-disc (day) | `05_h2_results.rds`, figures |
| `05A_diff_in_disc_analysis_continuous.Rmd` | Hypothesis 2: Diff-in-disc (continuous) | `05_h2_results_continuous.rds`, figures |
| `05B_diff_in_disc_analysis_drop.Rmd` | H2: Diff-in-disc (drop no-time) | `05_h2_results_drop.rds` |
| `05C_diff_in_disc_analysis_prob.Rmd` | H2: Diff-in-disc (probabilistic time) | `05_h2_results_prob.rds` |
| `06_russian_alignment_analysis.Rmd` | CSTO vs Neutral alignment (day) | `06_alignment_results.rds` |
| `06A_russian_alignment_analysis_continuous.Rmd` | Alignment analysis (continuous) | `06_alignment_results_continuous.rds` |
| `06B_russian_alignment_analysis_drop.Rmd` | Alignment analysis (drop no-time) | `06_alignment_results_drop.rds` |
| `06C_russian_alignment_analysis_prob.Rmd` | Alignment analysis (probabilistic) | `06_alignment_results_prob.rds` |
| `07_ethnic_russian_analysis.Rmd` | Ethnic Russian population effects (day) | `07_ethnic_results.rds` |
| `07A_ethnic_russian_analysis_continuous.Rmd` | Ethnic Russian analysis (continuous) | `07_ethnic_results_continuous.rds` |
| `07B_ethnic_russian_analysis_drop.Rmd` | Ethnic Russian analysis (drop no-time) | `07_ethnic_results_drop.rds` |
| `07C_ethnic_russian_analysis_prob.Rmd` | Ethnic Russian analysis (probabilistic) | `07_ethnic_results_prob.rds` |
| `08a_publication_outputs.Rmd` | Publication tables (Probabilistic Time, primary) | Publication-ready outputs (.tex + .html) |
| `08b_publication_outputs_days.Rmd` | Publication tables (Day Running Variable) | Publication-ready outputs (.tex + .html) |
| `08c_publication_outputs_cont.Rmd` | Publication tables (Continuous Running Variable) | Publication-ready outputs (.tex + .html) |
| `08d_publication_outputs_drop.Rmd` | Publication tables (Drop No-Time Articles) | Publication-ready outputs (.tex + .html) |

# Run Pipeline

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

# Track timing
pipeline_start <- Sys.time()
```

## Step 1: Data Loading

```{r step1}
step1_start <- Sys.time()
cat("Running 01_data_loading.Rmd...\n")

rmarkdown::render(
  "01_data_loading.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step1_time <- difftime(Sys.time(), step1_start, units = "secs")
cat("Completed in", round(step1_time, 1), "seconds\n")
```

## Step 2: Data Cleaning

```{r step2}
step2_start <- Sys.time()
cat("Running 02_data_cleaning.Rmd...\n")

rmarkdown::render(
  "02_data_cleaning.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step2_time <- difftime(Sys.time(), step2_start, units = "secs")
cat("Completed in", round(step2_time, 1), "seconds\n")
```

## Step 3: Descriptive Analysis

```{r step3}
step3_start <- Sys.time()
cat("Running 03_descriptive_analysis.Rmd...\n")

rmarkdown::render(
  "03_descriptive_analysis.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step3_time <- difftime(Sys.time(), step3_start, units = "secs")
cat("Completed in", round(step3_time, 1), "seconds\n")
```

## Step 4: Main RDD Analysis

```{r step4}
step4_start <- Sys.time()
cat("Running 04_main_rdd_analysis.Rmd...\n")

rmarkdown::render(
  "04_main_rdd_analysis.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step4_time <- difftime(Sys.time(), step4_start, units = "secs")
cat("Completed in", round(step4_time, 1), "seconds\n")
```

## Step 4A: Main RDD Analysis (Continuous Running Variable)

```{r step4a}
step4a_start <- Sys.time()
cat("Running 04A_main_rdd_analysis_continuous.Rmd...\n")

rmarkdown::render(
  "04A_main_rdd_analysis_continuous.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step4a_time <- difftime(Sys.time(), step4a_start, units = "secs")
cat("Completed in", round(step4a_time, 1), "seconds\n")
```

## Step 5: Diff-in-Disc Analysis

```{r step5}
step5_start <- Sys.time()
cat("Running 05_diff_in_disc_analysis.Rmd...\n")

rmarkdown::render(
  "05_diff_in_disc_analysis.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step5_time <- difftime(Sys.time(), step5_start, units = "secs")
cat("Completed in", round(step5_time, 1), "seconds\n")
```

## Step 5A: Diff-in-Disc Analysis (Continuous Running Variable)

```{r step5a}
step5a_start <- Sys.time()
cat("Running 05A_diff_in_disc_analysis_continuous.Rmd...\n")

rmarkdown::render(
  "05A_diff_in_disc_analysis_continuous.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step5a_time <- difftime(Sys.time(), step5a_start, units = "secs")
cat("Completed in", round(step5a_time, 1), "seconds\n")
```

## Step 6: Russian Alignment Analysis

```{r step6}
step6_start <- Sys.time()
cat("Running 06_russian_alignment_analysis.Rmd...\n")

rmarkdown::render(
  "06_russian_alignment_analysis.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step6_time <- difftime(Sys.time(), step6_start, units = "secs")
cat("Completed in", round(step6_time, 1), "seconds\n")
```

## Step 6A: Russian Alignment Analysis (Continuous Running Variable)

```{r step6a}
step6a_start <- Sys.time()
cat("Running 06A_russian_alignment_analysis_continuous.Rmd...\n")

rmarkdown::render(
  "06A_russian_alignment_analysis_continuous.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step6a_time <- difftime(Sys.time(), step6a_start, units = "secs")
cat("Completed in", round(step6a_time, 1), "seconds\n")
```

## Step 4B: Main RDD Analysis (Drop No-Time Articles)

```{r step4b}
step4b_start <- Sys.time()
cat("Running 04B_main_rdd_analysis_drop.Rmd...\n")

rmarkdown::render(
  "04B_main_rdd_analysis_drop.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step4b_time <- difftime(Sys.time(), step4b_start, units = "secs")
cat("Completed in", round(step4b_time, 1), "seconds\n")
```

## Step 5B: Diff-in-Disc Analysis (Drop No-Time Articles)

```{r step5b}
step5b_start <- Sys.time()
cat("Running 05B_diff_in_disc_analysis_drop.Rmd...\n")

rmarkdown::render(
  "05B_diff_in_disc_analysis_drop.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step5b_time <- difftime(Sys.time(), step5b_start, units = "secs")
cat("Completed in", round(step5b_time, 1), "seconds\n")
```

## Step 6B: Russian Alignment Analysis (Drop No-Time Articles)

```{r step6b}
step6b_start <- Sys.time()
cat("Running 06B_russian_alignment_analysis_drop.Rmd...\n")

rmarkdown::render(
  "06B_russian_alignment_analysis_drop.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step6b_time <- difftime(Sys.time(), step6b_start, units = "secs")
cat("Completed in", round(step6b_time, 1), "seconds\n")
```

## Step 4C: Main RDD Analysis (Probabilistic Time)

```{r step4c}
step4c_start <- Sys.time()
cat("Running 04C_main_rdd_analysis_prob.Rmd...\n")

rmarkdown::render(
  "04C_main_rdd_analysis_prob.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step4c_time <- difftime(Sys.time(), step4c_start, units = "secs")
cat("Completed in", round(step4c_time, 1), "seconds\n")
```

## Step 5C: Diff-in-Disc Analysis (Probabilistic Time)

```{r step5c}
step5c_start <- Sys.time()
cat("Running 05C_diff_in_disc_analysis_prob.Rmd...\n")

rmarkdown::render(
  "05C_diff_in_disc_analysis_prob.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step5c_time <- difftime(Sys.time(), step5c_start, units = "secs")
cat("Completed in", round(step5c_time, 1), "seconds\n")
```

## Step 6C: Russian Alignment Analysis (Probabilistic Time)

```{r step6c}
step6c_start <- Sys.time()
cat("Running 06C_russian_alignment_analysis_prob.Rmd...\n")

rmarkdown::render(
  "06C_russian_alignment_analysis_prob.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step6c_time <- difftime(Sys.time(), step6c_start, units = "secs")
cat("Completed in", round(step6c_time, 1), "seconds\n")
```

## Step 7: Ethnic Russian Population Analysis

```{r step7}
step7_start <- Sys.time()
cat("Running 07_ethnic_russian_analysis.Rmd...\n")

rmarkdown::render(
  "07_ethnic_russian_analysis.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step7_time <- difftime(Sys.time(), step7_start, units = "secs")
cat("Completed in", round(step7_time, 1), "seconds\n")
```

## Step 7A: Ethnic Russian Population Analysis (Continuous Running Variable)

```{r step7a}
step7a_start <- Sys.time()
cat("Running 07A_ethnic_russian_analysis_continuous.Rmd...\n")

rmarkdown::render(
  "07A_ethnic_russian_analysis_continuous.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step7a_time <- difftime(Sys.time(), step7a_start, units = "secs")
cat("Completed in", round(step7a_time, 1), "seconds\n")
```

## Step 7B: Ethnic Russian Population Analysis (Drop No-Time Articles)

```{r step7b}
step7b_start <- Sys.time()
cat("Running 07B_ethnic_russian_analysis_drop.Rmd...\n")

rmarkdown::render(
  "07B_ethnic_russian_analysis_drop.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step7b_time <- difftime(Sys.time(), step7b_start, units = "secs")
cat("Completed in", round(step7b_time, 1), "seconds\n")
```

## Step 7C: Ethnic Russian Population Analysis (Probabilistic Time)

```{r step7c}
step7c_start <- Sys.time()
cat("Running 07C_ethnic_russian_analysis_prob.Rmd...\n")

rmarkdown::render(
  "07C_ethnic_russian_analysis_prob.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step7c_time <- difftime(Sys.time(), step7c_start, units = "secs")
cat("Completed in", round(step7c_time, 1), "seconds\n")
```

## Step 8a: Publication Outputs (Probabilistic Time)

```{r step8a}
step8a_start <- Sys.time()
cat("Running 08a_publication_outputs.Rmd...\n")

rmarkdown::render(
  "08a_publication_outputs.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step8a_time <- difftime(Sys.time(), step8a_start, units = "secs")
cat("Completed in", round(step8a_time, 1), "seconds\n")
```

## Step 8b: Publication Outputs (Day Running Variable)

```{r step8b}
step8b_start <- Sys.time()
cat("Running 08b_publication_outputs_days.Rmd...\n")

rmarkdown::render(
  "08b_publication_outputs_days.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step8b_time <- difftime(Sys.time(), step8b_start, units = "secs")
cat("Completed in", round(step8b_time, 1), "seconds\n")
```

## Step 8c: Publication Outputs (Continuous Running Variable)

```{r step8c}
step8c_start <- Sys.time()
cat("Running 08c_publication_outputs_cont.Rmd...\n")

rmarkdown::render(
  "08c_publication_outputs_cont.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step8c_time <- difftime(Sys.time(), step8c_start, units = "secs")
cat("Completed in", round(step8c_time, 1), "seconds\n")
```

## Step 8d: Publication Outputs (Drop No-Time Articles)

```{r step8d}
step8d_start <- Sys.time()
cat("Running 08d_publication_outputs_drop.Rmd...\n")

rmarkdown::render(
  "08d_publication_outputs_drop.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step8d_time <- difftime(Sys.time(), step8d_start, units = "secs")
cat("Completed in", round(step8d_time, 1), "seconds\n")
```

## Step 9: Bandwidth Sensitivity Analysis

```{r step9}
step9_start <- Sys.time()
cat("Running 09_bandwidth_sensitivity.Rmd...\n")

rmarkdown::render(
  "09_bandwidth_sensitivity.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step9_time <- difftime(Sys.time(), step9_start, units = "secs")
cat("Completed in", round(step9_time, 1), "seconds\n")
```

# Cleanup

```{r cleanup}
# Clean up temporary files
tmp_files <- list.files(".", pattern = "\\.Rmd\\.tmp\\.", full.names = TRUE)
if (length(tmp_files) > 0) {
  file.remove(tmp_files)
  cat("Removed", length(tmp_files), "temporary files\n")
}
```

# Pipeline Summary

```{r summary}
pipeline_total <- difftime(Sys.time(), pipeline_start, units = "mins")

cat("\n")
cat("=============================================================\n")
cat("PIPELINE COMPLETE\n")
cat("=============================================================\n")
cat("\nStep Timings:\n")
cat("  01_data_loading:         ", round(step1_time, 1), "s\n")
cat("  02_data_cleaning:        ", round(step2_time, 1), "s\n")
cat("  03_descriptive_analysis: ", round(step3_time, 1), "s\n")
cat("  04_main_rdd_analysis:    ", round(step4_time, 1), "s\n")
cat("  04A_rdd_continuous:      ", round(step4a_time, 1), "s\n")
cat("  04B_rdd_drop:            ", round(step4b_time, 1), "s\n")
cat("  04C_rdd_prob:            ", round(step4c_time, 1), "s\n")
cat("  05_diff_in_disc:         ", round(step5_time, 1), "s\n")
cat("  05A_disc_continuous:     ", round(step5a_time, 1), "s\n")
cat("  05B_disc_drop:           ", round(step5b_time, 1), "s\n")
cat("  05C_disc_prob:           ", round(step5c_time, 1), "s\n")
cat("  06_alignment:            ", round(step6_time, 1), "s\n")
cat("  06A_alignment_continuous:", round(step6a_time, 1), "s\n")
cat("  06B_alignment_drop:      ", round(step6b_time, 1), "s\n")
cat("  06C_alignment_prob:      ", round(step6c_time, 1), "s\n")
cat("  07_ethnic:               ", round(step7_time, 1), "s\n")
cat("  07A_ethnic_continuous:   ", round(step7a_time, 1), "s\n")
cat("  07B_ethnic_drop:         ", round(step7b_time, 1), "s\n")
cat("  07C_ethnic_prob:         ", round(step7c_time, 1), "s\n")
cat("  08a_pub_outputs_prob:    ", round(step8a_time, 1), "s\n")
cat("  08b_pub_outputs_days:    ", round(step8b_time, 1), "s\n")
cat("  08c_pub_outputs_cont:    ", round(step8c_time, 1), "s\n")
cat("  08d_pub_outputs_drop:    ", round(step8d_time, 1), "s\n")
cat("  09_bw_sensitivity:       ", round(step9_time, 1), "s\n")
cat("  ─────────────────────────────\n")
cat("  Total:                   ", round(pipeline_total, 2), "min\n")
cat("\n")
cat("Outputs saved to:\n")
cat("  - data/intermediate/  (RDS files)\n")
cat("  - figures/            (plots and tables)\n")
cat("  - output/             (HTML reports)\n")
cat("=============================================================\n")
```

# Session Info

```{r session}
sessionInfo()
```
