---
title: "Russia Sentiment Analysis - Master Pipeline"
author: "Donald Moratz"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
---

# Analysis Pipeline Overview

This master script runs the entire analysis pipeline for the Russia sentiment paper.

The **probabilistic (KDE) time-assignment** variant is the primary analysis. The **day** and
**drop-no-time** variants are supplementary robustness checks. The **continuous-time** variant
has been retired to `scripts/archive/` and is no longer part of the pipeline. Within each
analysis family the variants are numbered and run in the order **prob → days → drop**,
matching the publication-output (09) ordering.

## Variant Naming

| Suffix | Variant | Running variable | In pipeline? |
|--------|---------|------------------|--------------|
| `a` (`_prob`) | Probabilistic time (primary) | `running_probabilistic` | Yes |
| `b` (`_days`) | Day running variable | `running` | Yes |
| `c` (`_cont`) | Continuous time | `running_continuous` | **Archived** |
| `d` (`_drop`) | Drop no-time articles | `running_continuous` (has_time) | Yes |

## File Descriptions

| Script | Purpose | Outputs |
|--------|---------|---------|
| `00_setup.R` | Packages, functions, constants | - |
| `01_data_loading.Rmd` | Load raw CSV data | `01_raw_data.rds` |
| `02_data_cleaning.Rmd` | Clean and create variables | `02_cleaned_data.rds`, etc. |
| `03A_descriptive_analysis.Rmd` | Summary statistics, EDA | Tables, time series plots |
| `03B_coding_analysis.Rmd` | Confusion matrices, Krippendorff's alpha, region map | `figures/coding/` |
| `04a_main_rdd_analysis_prob.Rmd` | **H1**: RDD (probabilistic, primary) | `04_h1_results_prob.rds` |
| `04b_main_rdd_analysis_days.Rmd` | H1: RDD (day) | `04_h1_results.rds` |
| `04d_main_rdd_analysis_drop.Rmd` | H1: RDD (drop no-time) | `04_h1_results_drop.rds` |
| `05a_diff_in_disc_analysis_prob.Rmd` | **H2**: Diff-in-disc (probabilistic, primary) | `05_h2_results_prob.rds` |
| `05b_diff_in_disc_analysis_days.Rmd` | H2: Diff-in-disc (day) | `05_h2_results.rds` |
| `05d_diff_in_disc_analysis_drop.Rmd` | H2: Diff-in-disc (drop no-time) | `05_h2_results_drop.rds` |
| `06a_russian_alignment_analysis_prob.Rmd` | **H3a**: CSTO alignment (probabilistic, primary) | `06_alignment_results_prob.rds` |
| `06b_russian_alignment_analysis_days.Rmd` | H3a: alignment (day) | `06_alignment_results.rds` |
| `06d_russian_alignment_analysis_drop.Rmd` | H3a: alignment (drop no-time) | `06_alignment_results_drop.rds` |
| `07a_ethnic_russian_analysis_prob.Rmd` | **H3b**: ethnic Russian pop. (probabilistic, primary) | `07_ethnic_results_prob.rds` |
| `07b_ethnic_russian_analysis_days.Rmd` | H3b: ethnic (day) | `07_ethnic_results.rds` |
| `07d_ethnic_russian_analysis_drop.Rmd` | H3b: ethnic (drop no-time) | `07_ethnic_results_drop.rds` |
| `08_bandwidth_sensitivity.Rmd` | Bandwidth sensitivity analysis | Figures |
| `09a_publication_outputs_prob.Rmd` | Publication tables (probabilistic, primary) | `.tex` + `.html` |
| `09b_publication_outputs_days.Rmd` | Publication tables (day) | `.tex` + `.html` |
| `09d_publication_outputs_drop.Rmd` | Publication tables (drop no-time) | `.tex` + `.html` |

Archived continuous-time scripts live in `scripts/archive/` (`04c`/`05c`/`06c`/`07c` and
`08c_publication_outputs_cont.Rmd`, retired under the old numbering in which the
publication scripts were 08), alongside the lifted non-parametric saturation checks.

# Run Pipeline

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
pipeline_start <- Sys.time()
```

The pipeline renders each script in order. Scripts 01–02 build the data; 03 runs the
descriptive/coding analyses; 04–07 run the three variants (prob → days → drop) of each
hypothesis; 08 runs bandwidth sensitivity; 09 builds the publication outputs for each
variant.

```{r run-pipeline}
# Ordered list of pipeline scripts. Within each analysis family the variants run
# prob -> days -> drop. Continuous-time variants are archived and not run here.
pipeline_scripts <- c(
  "01_data_loading.Rmd",
  "02_data_cleaning.Rmd",
  "03A_descriptive_analysis.Rmd",
  "03B_coding_analysis.Rmd",

  "04a_main_rdd_analysis_prob.Rmd",
  "04b_main_rdd_analysis_days.Rmd",
  "04d_main_rdd_analysis_drop.Rmd",

  "05a_diff_in_disc_analysis_prob.Rmd",
  "05b_diff_in_disc_analysis_days.Rmd",
  "05d_diff_in_disc_analysis_drop.Rmd",

  "06a_russian_alignment_analysis_prob.Rmd",
  "06b_russian_alignment_analysis_days.Rmd",
  "06d_russian_alignment_analysis_drop.Rmd",

  "07a_ethnic_russian_analysis_prob.Rmd",
  "07b_ethnic_russian_analysis_days.Rmd",
  "07d_ethnic_russian_analysis_drop.Rmd",

  "08_bandwidth_sensitivity.Rmd",

  "09a_publication_outputs_prob.Rmd",
  "09b_publication_outputs_days.Rmd",
  "09d_publication_outputs_drop.Rmd"
)

timings <- data.frame(script = character(), seconds = numeric(), stringsAsFactors = FALSE)

for (s in pipeline_scripts) {
  cat("Running", s, "...\n")
  step_start <- Sys.time()

  rmarkdown::render(s, output_dir = "../output", quiet = TRUE)

  step_secs <- as.numeric(difftime(Sys.time(), step_start, units = "secs"))
  timings <- rbind(timings, data.frame(script = s, seconds = round(step_secs, 1),
                                        stringsAsFactors = FALSE))
  cat("  Completed in", round(step_secs, 1), "seconds\n")
}
```

# Cleanup

```{r cleanup}
# Clean up temporary files
tmp_files <- list.files(".", pattern = "\\.Rmd\\.tmp\\.", full.names = TRUE)
if (length(tmp_files) > 0) {
  file.remove(tmp_files)
  cat("Removed", length(tmp_files), "temporary files\n")
}
```

# Pipeline Summary

```{r summary}
pipeline_total <- difftime(Sys.time(), pipeline_start, units = "mins")

cat("\n")
cat("=============================================================\n")
cat("PIPELINE COMPLETE\n")
cat("=============================================================\n")
cat("\nStep Timings:\n")
for (i in seq_len(nrow(timings))) {
  cat(sprintf("  %-42s %6.1f s\n", timings$script[i], timings$seconds[i]))
}
cat("  ─────────────────────────────\n")
cat(sprintf("  %-42s %6.2f min\n", "Total:", as.numeric(pipeline_total)))
cat("\n")
cat("Outputs saved to:\n")
cat("  - data/intermediate/  (RDS files)\n")
cat("  - figures/            (plots and tables)\n")
cat("  - output/             (HTML reports)\n")
cat("=============================================================\n")
```

# Session Info

```{r session}
sessionInfo()
```
