---
title: "Russia Sentiment Analysis - Master Pipeline"
author: "Donald Moratz"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
---

# Analysis Pipeline Overview

This master script runs the entire analysis pipeline for the Russia sentiment paper.

## Workflow Diagram

```
┌─────────────────────────────────────────────────────────────────────────────┐
│                         RUSSIA SENTIMENT ANALYSIS PIPELINE                   │
└─────────────────────────────────────────────────────────────────────────────┘

  ┌──────────────────┐
  │   00_setup.R     │ ◄── Shared functions, packages, constants
  └────────┬─────────┘
           │
           ▼
  ┌──────────────────┐     ┌─────────────────────────────┐
  │ 01_data_loading  │────►│ data/intermediate/          │
  │     .Rmd         │     │   01_raw_data.rds           │
  └────────┬─────────┘     └─────────────────────────────┘
           │
           ▼
  ┌──────────────────┐     ┌─────────────────────────────┐
  │ 02_data_cleaning │────►│ data/intermediate/          │
  │     .Rmd         │     │   02_cleaned_data.rds       │
  └────────┬─────────┘     │   02_data_non_ukraine.rds   │
           │               │   02_data_non_ukraine_ind.rds│
           │               └─────────────────────────────┘
           │
     ┌─────┴─────┬──────────────────────────┐
     │           │                          │
     ▼           ▼                          ▼
┌─────────┐ ┌─────────┐ ┌──────────┐ ┌─────────┐ ┌──────────┐
│   03    │ │   04    │ │   04A    │ │   05    │ │   05A    │
│ Descrip │ │Main RDD │ │ RDD Cont │ │Diff-Disc│ │Disc Cont │
│ tive    │ │   H1    │ │  H1 Alt  │ │   H2    │ │  H2 Alt  │
└────┬────┘ └────┬────┘ └────┬─────┘ └────┬────┘ └────┬─────┘
     │           │           │            │            │
     │           │     ┌─────┴─────┐ ┌────┴────┐ ┌────┴────┐
     │           │     │  04B 04C  │ │ 05B 05C │ │         │
     │           │     │Drop  Prob │ │Drop Prob│ │         │
     │           │     └─────┬─────┘ └────┬────┘ │         │
     │           │           │            │      │         │
     │           ▼           ▼            ▼      ▼         │
     │      ┌─────────────┐ ┌──────────┐ ┌────────────┐   │
     │      │     06      │ │   06A    │ │  06B  06C  │   │
     │      │Heterogeneity│ │Het. Cont │ │Drop   Prob │   │
     │      └──────┬──────┘ └────┬─────┘ └─────┬──────┘   │
     │             │             │              │          │
     └─────────────┴─────┬───────┴──────────────┘          │
                         │                                 │
                         ▼                                 │
                ┌─────────────────┐                        │
                │       07        │◄───────────────────────┘
                │  Publication    │────► figures/
                │    Outputs      │      (tables & plots)
                └─────────────────┘
```

## File Descriptions

| Script | Purpose | Outputs |
|--------|---------|---------|
| `00_setup.R` | Packages, functions, constants | - |
| `01_data_loading.Rmd` | Load raw CSV data | `01_raw_data.rds` |
| `02_data_cleaning.Rmd` | Clean and create variables | `02_cleaned_data.rds`, etc. |
| `03_descriptive_analysis.Rmd` | Summary statistics, EDA | Tables, time series plots |
| `04_main_rdd_analysis.Rmd` | Hypothesis 1: RDD (day) | `04_h1_results.rds`, figures |
| `04A_main_rdd_analysis_continuous.Rmd` | Hypothesis 1: RDD (continuous) | `04_h1_results_continuous.rds`, figures |
| `05_diff_in_disc_analysis.Rmd` | Hypothesis 2: Diff-in-disc (day) | `05_h2_results.rds`, figures |
| `05A_diff_in_disc_analysis_continuous.Rmd` | Hypothesis 2: Diff-in-disc (continuous) | `05_h2_results_continuous.rds`, figures |
| `06_heterogeneity_analysis.Rmd` | Alignment, ethnic effects (day) | `06_heterogeneity_results.rds` |
| `06A_heterogeneity_analysis_continuous.Rmd` | Alignment, ethnic effects (continuous) | `06_heterogeneity_results_continuous.rds` |
| `04B_main_rdd_analysis_drop.Rmd` | H1: RDD (drop no-time articles) | `04_h1_results_drop.rds` |
| `05B_diff_in_disc_analysis_drop.Rmd` | H2: Diff-in-disc (drop no-time) | `05_h2_results_drop.rds` |
| `06B_heterogeneity_analysis_drop.Rmd` | Heterogeneity (drop no-time) | `06_heterogeneity_results_drop.rds` |
| `04C_main_rdd_analysis_prob.Rmd` | H1: RDD (probabilistic time) | `04_h1_results_prob.rds` |
| `05C_diff_in_disc_analysis_prob.Rmd` | H2: Diff-in-disc (probabilistic time) | `05_h2_results_prob.rds` |
| `06C_heterogeneity_analysis_prob.Rmd` | Heterogeneity (probabilistic time) | `06_heterogeneity_results_prob.rds` |
| `07_publication_outputs.Rmd` | Final tables and figures | Publication-ready outputs |

# Run Pipeline

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

# Track timing
pipeline_start <- Sys.time()
```

## Step 1: Data Loading

```{r step1}
step1_start <- Sys.time()
cat("Running 01_data_loading.Rmd...\n")

rmarkdown::render(
  "01_data_loading.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step1_time <- difftime(Sys.time(), step1_start, units = "secs")
cat("Completed in", round(step1_time, 1), "seconds\n")
```

## Step 2: Data Cleaning

```{r step2}
step2_start <- Sys.time()
cat("Running 02_data_cleaning.Rmd...\n")

rmarkdown::render(
  "02_data_cleaning.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step2_time <- difftime(Sys.time(), step2_start, units = "secs")
cat("Completed in", round(step2_time, 1), "seconds\n")
```

## Step 3: Descriptive Analysis

```{r step3}
step3_start <- Sys.time()
cat("Running 03_descriptive_analysis.Rmd...\n")

rmarkdown::render(
  "03_descriptive_analysis.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step3_time <- difftime(Sys.time(), step3_start, units = "secs")
cat("Completed in", round(step3_time, 1), "seconds\n")
```

## Step 4: Main RDD Analysis

```{r step4}
step4_start <- Sys.time()
cat("Running 04_main_rdd_analysis.Rmd...\n")

rmarkdown::render(
  "04_main_rdd_analysis.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step4_time <- difftime(Sys.time(), step4_start, units = "secs")
cat("Completed in", round(step4_time, 1), "seconds\n")
```

## Step 4A: Main RDD Analysis (Continuous Running Variable)

```{r step4a}
step4a_start <- Sys.time()
cat("Running 04A_main_rdd_analysis_continuous.Rmd...\n")

rmarkdown::render(
  "04A_main_rdd_analysis_continuous.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step4a_time <- difftime(Sys.time(), step4a_start, units = "secs")
cat("Completed in", round(step4a_time, 1), "seconds\n")
```

## Step 5: Diff-in-Disc Analysis

```{r step5}
step5_start <- Sys.time()
cat("Running 05_diff_in_disc_analysis.Rmd...\n")

rmarkdown::render(
  "05_diff_in_disc_analysis.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step5_time <- difftime(Sys.time(), step5_start, units = "secs")
cat("Completed in", round(step5_time, 1), "seconds\n")
```

## Step 5A: Diff-in-Disc Analysis (Continuous Running Variable)

```{r step5a}
step5a_start <- Sys.time()
cat("Running 05A_diff_in_disc_analysis_continuous.Rmd...\n")

rmarkdown::render(
  "05A_diff_in_disc_analysis_continuous.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step5a_time <- difftime(Sys.time(), step5a_start, units = "secs")
cat("Completed in", round(step5a_time, 1), "seconds\n")
```

## Step 6: Heterogeneity Analysis

```{r step6}
step6_start <- Sys.time()
cat("Running 06_heterogeneity_analysis.Rmd...\n")

rmarkdown::render(
  "06_heterogeneity_analysis.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step6_time <- difftime(Sys.time(), step6_start, units = "secs")
cat("Completed in", round(step6_time, 1), "seconds\n")
```

## Step 6A: Heterogeneity Analysis (Continuous Running Variable)

```{r step6a}
step6a_start <- Sys.time()
cat("Running 06A_heterogeneity_analysis_continuous.Rmd...\n")

rmarkdown::render(
  "06A_heterogeneity_analysis_continuous.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step6a_time <- difftime(Sys.time(), step6a_start, units = "secs")
cat("Completed in", round(step6a_time, 1), "seconds\n")
```

## Step 4B: Main RDD Analysis (Drop No-Time Articles)

```{r step4b}
step4b_start <- Sys.time()
cat("Running 04B_main_rdd_analysis_drop.Rmd...\n")

rmarkdown::render(
  "04B_main_rdd_analysis_drop.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step4b_time <- difftime(Sys.time(), step4b_start, units = "secs")
cat("Completed in", round(step4b_time, 1), "seconds\n")
```

## Step 5B: Diff-in-Disc Analysis (Drop No-Time Articles)

```{r step5b}
step5b_start <- Sys.time()
cat("Running 05B_diff_in_disc_analysis_drop.Rmd...\n")

rmarkdown::render(
  "05B_diff_in_disc_analysis_drop.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step5b_time <- difftime(Sys.time(), step5b_start, units = "secs")
cat("Completed in", round(step5b_time, 1), "seconds\n")
```

## Step 6B: Heterogeneity Analysis (Drop No-Time Articles)

```{r step6b}
step6b_start <- Sys.time()
cat("Running 06B_heterogeneity_analysis_drop.Rmd...\n")

rmarkdown::render(
  "06B_heterogeneity_analysis_drop.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step6b_time <- difftime(Sys.time(), step6b_start, units = "secs")
cat("Completed in", round(step6b_time, 1), "seconds\n")
```

## Step 4C: Main RDD Analysis (Probabilistic Time)

```{r step4c}
step4c_start <- Sys.time()
cat("Running 04C_main_rdd_analysis_prob.Rmd...\n")

rmarkdown::render(
  "04C_main_rdd_analysis_prob.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step4c_time <- difftime(Sys.time(), step4c_start, units = "secs")
cat("Completed in", round(step4c_time, 1), "seconds\n")
```

## Step 5C: Diff-in-Disc Analysis (Probabilistic Time)

```{r step5c}
step5c_start <- Sys.time()
cat("Running 05C_diff_in_disc_analysis_prob.Rmd...\n")

rmarkdown::render(
  "05C_diff_in_disc_analysis_prob.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step5c_time <- difftime(Sys.time(), step5c_start, units = "secs")
cat("Completed in", round(step5c_time, 1), "seconds\n")
```

## Step 6C: Heterogeneity Analysis (Probabilistic Time)

```{r step6c}
step6c_start <- Sys.time()
cat("Running 06C_heterogeneity_analysis_prob.Rmd...\n")

rmarkdown::render(
  "06C_heterogeneity_analysis_prob.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step6c_time <- difftime(Sys.time(), step6c_start, units = "secs")
cat("Completed in", round(step6c_time, 1), "seconds\n")
```

## Step 7: Publication Outputs

```{r step7}
step7_start <- Sys.time()
cat("Running 07_publication_outputs.Rmd...\n")

rmarkdown::render(
  "07_publication_outputs.Rmd",
  output_dir = "../output",
  quiet = TRUE
)

step7_time <- difftime(Sys.time(), step7_start, units = "secs")
cat("Completed in", round(step7_time, 1), "seconds\n")
```

# Cleanup

```{r cleanup}
# Clean up temporary files
tmp_files <- list.files(".", pattern = "\\.Rmd\\.tmp\\.", full.names = TRUE)
if (length(tmp_files) > 0) {
  file.remove(tmp_files)
  cat("Removed", length(tmp_files), "temporary files\n")
}
```

# Pipeline Summary

```{r summary}
pipeline_total <- difftime(Sys.time(), pipeline_start, units = "mins")

cat("\n")
cat("=============================================================\n")
cat("PIPELINE COMPLETE\n")
cat("=============================================================\n")
cat("\nStep Timings:\n")
cat("  01_data_loading:        ", round(step1_time, 1), "s\n")
cat("  02_data_cleaning:       ", round(step2_time, 1), "s\n")
cat("  03_descriptive_analysis:", round(step3_time, 1), "s\n")
cat("  04_main_rdd_analysis:   ", round(step4_time, 1), "s\n")
cat("  04A_rdd_continuous:     ", round(step4a_time, 1), "s\n")
cat("  04B_rdd_drop:           ", round(step4b_time, 1), "s\n")
cat("  04C_rdd_prob:           ", round(step4c_time, 1), "s\n")
cat("  05_diff_in_disc:        ", round(step5_time, 1), "s\n")
cat("  05A_disc_continuous:    ", round(step5a_time, 1), "s\n")
cat("  05B_disc_drop:          ", round(step5b_time, 1), "s\n")
cat("  05C_disc_prob:          ", round(step5c_time, 1), "s\n")
cat("  06_heterogeneity:       ", round(step6_time, 1), "s\n")
cat("  06A_het_continuous:     ", round(step6a_time, 1), "s\n")
cat("  06B_het_drop:           ", round(step6b_time, 1), "s\n")
cat("  06C_het_prob:           ", round(step6c_time, 1), "s\n")
cat("  07_publication_outputs: ", round(step7_time, 1), "s\n")
cat("  ─────────────────────────────\n")
cat("  Total:                  ", round(pipeline_total, 2), "min\n")
cat("\n")
cat("Outputs saved to:\n")
cat("  - data/intermediate/  (RDS files)\n")
cat("  - figures/            (plots and tables)\n")
cat("  - output/             (HTML reports)\n")
cat("=============================================================\n")
```

# Session Info

```{r session}
sessionInfo()
```
